### 2017-02-27 paper/proposal.Rmd
Description of hugo's data

---
title: "Pollen trade-offs"
author: "Fernando, Hugo, Jason & Daniel"
date: "27 February 2017"
output:
  html_document: default
  word_document: default
subtitle: Proposal
---

# Introduction

Interspecific pollen deposition is detrimental to plant fitness. 
This is particularly true if it's the first deposition.
Using specialization: trade offs
Plants can minimise interspecific pollen deposition using four distinct mechanisms:

1. By preferentially flowering on spatial clusters 
2. By flowering in missmatching phenologies
3. By harnessing individual level insect preferences
4. By depositing and receiving pollen on/from specific insect body parts

I aim to use

# Methods

## Individual based model

## Hugo's data

Data collected over 3 years, each year with 5 samplings from November to March. 
For each sampling, 3 sites were visited, each of them with 4 fragments (two restored and two agricultural). 
In each fragment, 2 transects were performed. 
For each transect x sampling, there is data on flower abundance, insect abbundance (# insects caught), plant-insect visitation(?) and pollen carried per individual insect (to the species level). 
In addition, there is data on the amount of interspecific/conspecific pollen in flower stigmas for year #2. (From November to March as well?)
It might be possible to gather information on plant and animal phenophases and traits either from available data or databases / published literature.

# Timeline

### 2017-03-20 paper/proposal.Rmd
Put larger introduction

@@
 ---
-title: "Pollen trade-offs"
+title: "The mutualistic trade-off"
 author: "Fernando, Hugo, Jason & Daniel"
-date: "27 February 2017"
 output:
-  html_document: default
-  word_document: default
-subtitle: Proposal
+  pdf_document: default
+subtitle: "Mini proposal"
+bibliography: references.bib
+csl: ecology-letters.csl
+header-includes:
+- \usepackage{setspace}
 ---
 
-# Introduction
+\onehalfspacing
 
-Interspecific pollen deposition is detrimental to plant fitness. 
-This is particularly true if it's the first deposition.
-Using specialization: trade offs
-Plants can minimise interspecific pollen deposition using four distinct mechanisms:
+The trade-off between the number of partners and the mutualistic benefit (mutualistic trade-off) has been shown to play an important role in the structuring of pollination networks [@Saavedra2013]. 
+The mutualistic trade-off arises primarily from the negative effects of interspecific pollen transfer on plant fitness (trough pollen limitation, for example). 
+When the trade-off is very low, plants that have a large number of interaction partners tend to be the ones that obtain the largest benefits.
+Contrastingly, when the mutualistic trade-off is very high, specialist plants (those with a small number of partners) would fare better because their pollen is not deposited on foreign stigmas, and similarly, their stigmas are not clogged by foreign pollen.
+Nevertheless, it has been shown that specialisation might be a dangerous strategy because it reduces the insurance effect against partner loss and volatility that generalism promotes.
 
-1. By preferentially flowering on spatial clusters 
-2. By flowering in missmatching phenologies
-3. By harnessing individual level insect preferences
-4. By depositing and receiving pollen on/from specific insect body parts
+As evidenced by a multitude of empirical studies, real mutualistic networks are somewhere in the middle—at intermediate levels of connectance. 
+This is means that plant communities and/or species employ strategies to minimise the mutualistic trade-offs.
 
-I aim to use
+## Effect of the trade-off mutualism\footnote{Not so sure about this one.
+I think it might be a good way to start this chapter because it seems relatively straightforward, sets the scenario for the things to come, and can come with useful lessons about how to follow.
+}
 
-# Methods
+It has been shown that mutualism maximises diversity [@Bastolla2009]. 
+Under a no trade-off scenario the largest biodiversity is achieved when the network is fully connected (the connectance *c = 1*). 
+For intermediate levels of connectance, it has also been shown that the performance of different structures differ such that a nested structure promotes biodiversity more efficiently than a modular and a random structure.
+It is unknown, however, which structures are more favourable when the mutualistic trade-off is included. 
+Empirical networks are far from being fully connected, and have neither completely modular or nested structure, but are somewhere in between. 
+The **first potential question** is to compare the performance of four different structures: random, nested, modular, and empirical, when the mutualistic trade-off is included.
 
-## Individual based model
+We will use the feasibility of the network as an indication of the extent to which the network structure facilitates species coexistence [@Saavedra2016]. 
+To compare the different structures, we will calculate the feasibility of an empirical network and compare it with the feasibility of a network that maintains the size and connectance, but that has a highly nested, highly modular, and random structure.
+We will do that under two scenarios. 
+In the first, assumes a homogeneous mutualistic trade-off for the community. 
+In this case, we will analyse the feasibility of the four structures for varying levels of trade-off.
+In the second scenario, we will assume that the trade-off is species dependent and correspond to the "neutral" assumption that the trade-off is inversely proportional to the species abundance. 
+This second scenario will require a modification of the existing feasibility code.
 
-## Hugo's data
+## Empirical networks minimise the trade-off
 
-Data collected over 3 years, each year with 5 samplings from November to March. 
-For each sampling, 3 sites were visited, each of them with 4 fragments (two restored and two agricultural). 
-In each fragment, 2 transects were performed. 
-For each transect x sampling, there is data on flower abundance, insect abbundance (# insects caught), plant-insect visitation(?) and pollen carried per individual insect (to the species level). 
-In addition, there is data on the amount of interspecific/conspecific pollen in flower stigmas for year #2. (From November to March as well?)
-It might be possible to gather information on plant and animal phenophases and traits either from available data or databases / published literature.
+We start from the premise that both efficiency and redundancy are desirable in pollination networks, but that there is a trade-off between those. 
+We follow with the assumption that the highest pollination efficiency is achieved when there is no interspecific pollen transfer. 
+At the community level, we expect that pollination communities are selected towards structures that minimise the efficiency/redundancy trade-off. 
+The first question is therefore whether the structure of empirical natural communities allows for higher levels of efficiency than what would be expected at random for its redundancy.
+
+```{r, echo = F, fig.width = 7, fig.height = 1.5, results='hide', fig.cap  = "Illustration of the mutualistic trade-off."}
+library(magrittr)
+r <- list(
+    matrix(1, ncol = 2, nrow = 2),
+    matrix(c(1, 1, 1, 0), ncol = 2, nrow = 2),
+    matrix(c(1, 0, 0, 1), ncol = 2, nrow = 2)
+)
+
+c(1, 1, 1, 2, 3, 4, 5, 5, 5) %>%
+    matrix(3, 3, byrow = T) %>%
+    layout(heights = c(1, 2.5, 1))
+par(mar = rep(0, 4))
+plot.new()
+text(0.5, 0.5, "redundancy", pos = 3)
+arrows(1, 0.5, 0, length = 0.1, angle = 15, col = "grey30")
+lapply(r, igraph::graph_from_incidence_matrix) %>%
+    lapply(igraph::plot.igraph, 
+                 layout = igraph::layout_as_bipartite, 
+                 vertex.color = NA, 
+                 vertex.label = NA,
+                 vertex.size = 50)
+
+plot.new()
+text(0.5, 0.5, "efficiency", pos = 1)
+arrows(0, 0.5, 1, length = 0.1, angle = 15, col = "grey30")
+```
+
+Efficiency will be measured by quantifying the pollen $\alpha$-diversity in pollination units and*the pollen $\beta$-diversity across pollination units. 
+Efficient pollination (low interspecific transfer) occurs when $\alpha$-diversity is minimal and $\beta$-diversity is maximal. 
+Here, a pollination unit is the one at which pollination effectively takes place.
+While most studies have studied pollination systems using species as the pollination unit, individuals or even body parts can be more meaningful units, as individuals are the ones moving from flower to flower, and the body parts are effectively where the pollen is attached to and retrieved from.
+Redundancy will be measured either by counting the incidence of more redundant 4 species motifs or by using the network's complementarity H2 [@Bluthgen2011]. 
+As the highest redundancy is achieved when plant species can harness the positive feedback loops characteristic in mutualistic communities, and the end effect of redundancy is to buffer against fluctuations in the populations of mutualistic partners, the relevant unit when evaluating the redundancy is species.
+
+The relationship between the $\alpha$ and $\beta$ diversity and *potential* interspecific pollen transfer can be shown by using a set of networks in which pollen loads and visitation data exists. 
+The proportion of potential interspecific pollen for plant species *i* is $$t_i = \frac{\sum{p_{ij}\frac{v_{ji}}{v_j}}}{\sum{p_{ij}}}$$, where $p_ij$ is the amount of pollen of plant *i* on pollinator unit *j*, $v_{ji}$ is the number of visits by pollinator *j* on plant *i* and $v_j$ is the total number of visits by pollinator *j*.
+Hopefully, the relationship agrees strongly enough with the diversity indices so that they can be used instead, and networks in which only pollen load data exists can be used (necessary at all?). 
+The neutral efficiency for a given redundancy will be calculated assuming that the pollen is distributed homogeneously among pollinator units in a way proportional to the overall abundance of pollen per species.
+A very rough pictorial description of this procedure can be found at the end.
+This analysis will take place when considering species or individual as the pollination units.
+
+The results will potentially explain why pollen transfer networks seem to be more specialised than visitation and provide evidence as to how plants can harness individual pollinator preferences to increase the functional complementarity of the pollination service without sacrificing the stability provided by interaction redundancy, effectively minimising interspecific competition.
+
+However, network structure and individual pollinator preferences are not the only way communities might employ to minimise the mutualistic trade-offs. 
+I identify four strategies, two that introduce mismatches and two that introduce pollinator granularity, that has been empirically recognised.
+
+1. A spatial mismatch: Animal mutualists have different home ranges. 
+The mutualistic trade-off can be minimised by plant species by growing in spatial clusters such that the likelihood that the following or previous visits on a focal plant occur on the same species. 
+2. A temporal mismatch: The trade-off can similarly be minimised by growing in distinct temporal clusters that cause a mismatch on plant phenologies. 
+This is so because when a time period is dominated by a particular plant species the likelyhood that the following or previous visits on a focal plant occur on the same species is increased too.
+3. Individual pollinator granularity: Although the reasons and mechanisms are still unclear, it has been shown that pollinators have preferences at the individual level. 
+This is, while a pollinator species might be a mutualist for several plant species, individuals concentrate their visits on a particular plant species. 
+This effectively reduces the amount of interspecific pollen transfer.
+4.
+Body part pollinator granularity: diving even further, plant reproductive organs can have shapes that preferentially attach (and receive), pollen in (from) particular body parts of the pollinator partner.
+
+Effectively, all these four strategies operate by achieving the same effect on patterns of $\alpha$ and $\beta$-diversity.
+The low pollen diversity has the largest benefit for the species with the largest *local abundance*.
+
+Although previous work indicates that all these strategies might operate to a certain degree in nature, it is unclear how prevalent they are in pollination systems. 
+A potential section of the chapter might be to use an individual-based model to compare the extent to which these mechanisms might contribute to the minimisation of the trade-off. 
+An IBM might be desirable because it allows modeling all these mechanisms within a unified framework.
+
+## Empirical individual & body part pollen partitioning constraint feasibility less than random
+
+In collaboration with Melissa, I will calculate the feasibility of the agricultural networks when using individual pollinators, and body parts as the pollination units. 
+I will then compare it with the feasibility of *i)* an scenario in which there is no individual or body part differentiation, and *ii)* random differentiation.
 
 # Timeline
+
+* March and April: Feasibility - Melissa. Potential reviews for control paper.
+* April, May and June: Empirical networks minimise trade-offs (analyse data using proposed methods, attempt to write a draft, keep on analysing data and decide if further analysis is necessary.
+Potential reviews for control paper.
+On holidays the last week of June
+* July: ICCB and Suspension
+* August: ESA and Suspension *or* Internship
+* September: Internship, iDiv summer school *or* suspension
+* October and November: Internship *or* Empirical networks minimise trade-offs (finish up writing and, follow up work in case results are not satisfactory)
+* December - June: Third chapter
+* Winter 2018: Internship *or* Data incubator
+* Summer 2018-2019: Third chapter and wrap up thesis
+
+# References

### 2017-03-22 paper/proposal.Rmd
Rewrite proposal to focus on Hugo's data

--- 2017-02-27 paper/proposal.Rmd
@@
 ---
-title: "Pollen trade-offs"
+title: "The mutualistic trade-off"
 author: "Fernando, Hugo, Jason & Daniel"
-date: "27 February 2017"
 output:
-  html_document: default
-  word_document: default
-subtitle: Proposal
+  pdf_document: default
+subtitle: "Mini proposal 2"
+bibliography: references.bib
+csl: ecology-letters.csl
+header-includes:
+- \usepackage{setspace}
 ---
 
-# Introduction
+\onehalfspacing
 
-Interspecific pollen deposition is detrimental to plant fitness. 
-This is particularly true if it's the first deposition.
-Using specialization: trade offs
-Plants can minimise interspecific pollen deposition using four distinct mechanisms:
+# Abstract (mock)
 
-1. By preferentially flowering on spatial clusters 
-2. By flowering in missmatching phenologies
-3. By harnessing individual level insect preferences
-4. By depositing and receiving pollen on/from specific insect body parts
+It is generally believed that there is a trade-off between the number of mutualistic parters a plant species has, and the strength of its interactions (mutualistic benefit).
+The trade-off arises from the premise that an increase on the number of mutualistic partners might increase facilitation, but might also increase competition for pollinators because it can lead to a reduction of the proportion of conspecific pollen deposited on the stigmas.
+Species properties and the environmental context seem to influence whether sharing pollinators leads to facilitation or competition [@Tur2016a], however the specific mechanisms behind these observations are poorly understood.
+Furthermore, recent theoretical advances that explicitly include the mutualistic trade-off in pollination models have highlighted its importance.
+Indeed, it has been shown that the trade-off is related to the feasibility and stability of mutualistic communities [@Rohr2014], the species' response to change [@Saavedra2013], the onset of critical transitions [@Dakos2014a], and the spread of perturbations [@Suweis2015].
+However, The extent to which the trade-off operates in nature and its relationship with facilitation-competition dynamics has not been empirically evaluated.
+Here, we used data on the quality and quantity of pollination in six pollination communities to quantify the empirical support for the mutualistic trade-off concept and identify the mechanisms that structure it.
+Contrasting to our initial expectation, we found that the mutualistic benefit is only weakly related to the number of pollination partners.
+We found that this relationship is weak because plants with a large number of shared partners are able to reduce the cost of sharing by increasing the niche partitioning.
+Importantly, the niche partitioning strategies are modulated by plant abundance and are not homogeneously employed by all plant species.
 
-I aim to use
+# Questions & hypotheses
 
-# Methods
+1. Is the trade-off between mutualistic benefit and the number of mutualistic partners observed in nature?
+    * _H1-null_: There is no relationship between the proportion of conspecific pollen deposited and the number of mutualistic partners.
+_H1-alternative 1_: The trade-off $\delta$ can be characterized at a community scale using the relationship $$\sum_j{\gamma_{ij}} = \sum{\gamma_0 y_{ij} / d_i^\delta} = \gamma_0 d_i^{1-\delta},$$ where $\sum_j{\gamma_{ij}}$ is the proportion of conspecific pollen, $\gamma_0$ represents the community level of mutualistic strength and $d_i$ is the number of mutualistic partners of species $i$.
+_H1-alternative 2_: the trade-off is species specific: $$\sum_j{\gamma_{ij}} = \gamma_0 d_i^{1-\delta_i}$$.
+    * _Methods_: We will use stigmatic pollen deposition data to fit a non linear regression for each of the hypothesis alternatives. We will then use AIC to determine the support for each of them.
+2. What is the relationship between the mutualistic trade-off and facilitation-competition dynamics?
+    * If support is found for H1-alternative 1.
+_H2-null_: there is no relationship between $\delta$  and the proportion of species that experience facilitation in the community.
+_H2-alternative_: there is a positive relationship.
+    * If support is found for H1-alternative 2.
+_H2-null_: there is no relationship between $\delta_i$ and the species specific slope of facilitation $\beta_i$.
+_H2-alternative_: there is a relationship.
+    * _Methods_: $\beta_i$ will be calculated following @Tur2016a - model 1.
+Which uses a poisson GLMM with number of conspecific pollen grains per stigma as response variable, total number of heterospecific pollen grains as predictor with plant receptor species as random slope and intercept.
+We will then use a simple linear regression to identify the relationship between $\delta_i$ and $\beta_i$ or $\delta$ and $\beta_f$ (which correspond to the proportion of plant species for which $\beta_i \pm 2SE > 0$).
+3. What is the relative importance of the strategies that plant can use to achieve high mutualistic strength while minimizing competition?
+    * _H3-null_: there is no relationship between abundance + niche partitioning due to shared pollinator species + niche partitioning due to individual pollinator variation + niche partitioning due to temporal overlap and the proportion of conspecific pollen.
+_H3-alternative 1_: there is a positive relationship between all these strategies and proportion of conspecific pollen, they operate at the community level (no important variation among plant species).
+_H3-alternative 2_: there is a positive relationship but plants are specific on their strategy (e.g.
+abundant species do not need to partition niche, less abundant species do need to do that but they either focus on avoiding phenological overlap or pollinator overlap).
+    * _Methods_: overall abundance will be calculated by adding the independent abundances obtained at different sample occasions; species level pollinator niche overlap will be calculated constructing an animal-individual/plant-species matrix and using normal $\beta$-diversity approaches, the overlap will be then partitioned between individual and species level by removing the overlap found in a animal-species/plant-species matrix, following the overlap will be partitioned between a nested and modular component; temporal overlap will be calculated using a similar approach but constructing abundance plant-species/month matrices.
+Because it is likely that there are large interactions between all these predictors, we will use random regression forests or boosted regression trees to quantify the relative importance of variables.
+To determine the extent to which plants employ different strategies we will use a PCA or similar to reduce the dimensionality and calculate the overlap in the hypervolume of strategies.
 
-## Individual based model
+# Dataset
 
-## Hugo's data
+The dataset is spatially structured in three sites.
+Each site has four fragments (two restored and one agricultural).
+In total there is 11 fragments because one of the restored sites was too small to accommodate two fragments.
+In each fragment two transects were performed.
+For the season 2010-2011 theres is data on:
 
-Data collected over 3 years, each year with 5 samplings from November to March. 
-For each sampling, 3 sites were visited, each of them with 4 fragments (two restored and two agricultural). 
-In each fragment, 2 transects were performed. 
-For each transect x sampling, there is data on flower abundance, insect abbundance (# insects caught), plant-insect visitation(?) and pollen carried per individual insect (to the species level). 
-In addition, there is data on the amount of interspecific/conspecific pollen in flower stigmas for year #2. (From November to March as well?)
-It might be possible to gather information on plant and animal phenophases and traits either from available data or databases / published literature.
+* Individual level pollen transfer networks (sampled one per month between November and March).
+* Stigmatic pollen deposition for 3-9 of the most abundant species in each fragment.
+This subset includes both generalist (~75%) and specialist (~25%) species.
+In total there are 26 species and 49 species-fragment estimations.
+Heterospecific pollen deposition was not further identified.
+Stigmas were collected only on December and February and the date was not recorded.
+* Visitation networks (sampled one per month between November and March).
+* Independent plant and insect abundance estimates in 50x2m random transects (abundance is therefore not available for species present in the interaction networks but not in the abundance transects; sampled one per month between November and March).
+
+In addition to this, there is also abundance and visitation data for the 2008-2009 season, and abundance, visitation, and pollen transfer data for the 2009-2010 season.
+
+Different components of this data set have been published by @Marrero2014, @Marrero2016, and @Marrero2017.
+@Marrero2014 used visitation data and determined that there were differences on the degree of specialization between land uses (agricultural vs.
+restored) as well as the richness of plants and pollinators.
+@Marrero2016 used pollen deposition data and determined that the pollination service (both the absolute number and the proportion of conspecific pollen deposited on stigmas) is reduced in agricultural communities when compared to restored communities.
+Finally, @Marrero2017 used pollen transfer networks and found that pollen diversity and pollination niche overlap (at the species level) is greater in agricultural communities.
+The increase on niche overlap was in turn positively associated with an increased abundance of exotic plants.
 
 # Timeline
+
+* April: Feasibility - Melissa. Potential reviews for control paper.
+* May and June: Empirical networks minimise trade-offs (analyse data using proposed methods, attempt to write a draft, keep on analysing data and decide if further analysis is necessary.
+Potential reviews for control paper might get on the way.
+On holidays the last week/mid of June
+* July: ICCB and Suspension
+* August: ESA and Suspension *or* Internship
+* September: Internship, iDiv summer school *or* suspension
+* October and November: Internship *or* Empirical networks minimise trade-offs (finish up writing and, follow up work in case results are not satisfactory)
+* December - June: Third chapter
+* Winter 2018: Internship *or* Data incubator
+* Summer 2018-2019: Third chapter and wrap up thesis
+
+# References

### 2017-03-27 paper/proposal.Rmd
put timeline into it's own document

@@
 
-# Timeline
-
-* April: Feasibility - Melissa. Potential reviews for control paper.
-* May and June: Empirical networks minimise trade-offs (analyse data using proposed methods, attempt to write a draft, keep on analysing data and decide if further analysis is necessary.
-Potential reviews for control paper might get on the way.
-On holidays the last week/mid of June
-* July: ICCB and Suspension
-* August: ESA and Suspension *or* Internship
-* September: Internship, iDiv summer school *or* suspension
-* October and November: Internship *or* Empirical networks minimise trade-offs (finish up writing and, follow up work in case results are not satisfactory)
-* December - June: Third chapter
-* Winter 2018: Internship *or* Data incubator
-* Summer 2018-2019: Third chapter and wrap up thesis
-
 # References

### 2017-03-27 paper/timeline.Rmd
put timeline into it's own document

---
title: "PhD Timeline"
author: "Fernando Cagua"
date: "27 March 2017"
output: html_document
---

The aim is to finish as close to the 3 year mark as possible. The timing of the mid year breaks is unfortunate because it is likely to interrupt the progress of the PhD projects, the time lost due to the lack of momentum will be offset by the extra funding time.

```{r, echo = FALSE, fig.height=1.9, message = FALSE, warning = FALSE, fig.cap= "Option A. Which includes a 3 month suspension during winter."}
source("../code/miscelaneous/schedule.R")
library(readr)

chart <- read_csv("../data/project_schedule_A.csv", 
									col_types = cols(start = col_date("%d/%m/%y"),
																	 mean = col_date("%d/%m/%y"),
																	 end = col_date("%d/%m/%y")))

plot_schedule(chart)
```

```{r, echo = FALSE, fig.height=2, message = FALSE, warning = FALSE, fig.cap= "Option B. Which includes 2 month break and 2 weeks at the iDiv school in Lepzig."}
chart <- read_csv("../data/project_schedule_B.csv", 
									col_types = cols(start = col_date("%d/%m/%y"),
																	 mean = col_date("%d/%m/%y"),
																	 end = col_date("%d/%m/%y")))

plot_schedule(chart)
```

```{r, echo = FALSE, fig.height=2.1, message = FALSE, warning = FALSE, , fig.cap= "Option A with a 6 month internship and a 2 month data camp."}
chart <- read_csv("../data/project_schedule_C.csv", 
									col_types = cols(start = col_date("%d/%m/%y"),
																	 mean = col_date("%d/%m/%y"),
																	 end = col_date("%d/%m/%y")))

plot_schedule(chart)
```

### 2017-04-05 paper/exploration.Rmd
Basic plot degree vs pollen

---
title: "The degre/benefit trade-off: deposition data"
author: "Fernando Cagua"
date: "4 April 2017"
output: 
  html_notebook: 
    code_folding: hide
    fig_caption: yes
---

```{r setup, message=FALSE, results='hide'}
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 7)

# read data
dep <- readRDS("../data/datasets/processed/all_deposition.rds")
dep_df <- plyr::ldply(dep, function(x){
  x$deposition %>%
    mutate(site = x$name, 
           study = x$study)
})

vis <- readRDS("../data/datasets/processed/all_visitation.rds")
vis_df <- plyr::ldply(vis, function(x){
  x$visitation %>%
    mutate(site = x$name, 
           study = x$study)
})
```

This is a preliminary analysis using Hugo's data. Here, species degree is independently calculated from the visitation network.

Particular to this study is the use of control flowers to account for the effect of self pollination. The treatment "closed" corresponds to when flowers were bagged, and the treatment "open" allowed for insects to come and pollinate the flower.

The follwing graph shows the number of grains as a function of the overall plant degree (the number of distinct partners across all sites) for both the open and closed treatment.

```{r}
# calculate degrees
degree_overall <- vis_df %>%
  rename(recipient = plant_name) %>%
  group_by(study, recipient) %>%
  summarise(degree = n_distinct(animal_name))

inner_join(degree_overall, dep_df) %>% 
  ggplot(aes(x = degree, y = n_grains/n_stigma + 1)) + 
  geom_point(aes(colour = recipient == donor),
             position = position_jitter(0.4),
             size = 1, 
             alpha = 0.7) +
  geom_smooth(aes(colour = recipient == donor),
              method = "lm") +
  facet_grid(~treatment) +
  scale_y_log10() +
  theme(legend.position = "top")
```

This seems to make sense.

### 2017-04-10 paper/exploration.Rmd
Initial data exploration

@@
 ---
-title: "The degre/benefit trade-off: deposition data"
+title: "The degree/benefit trade-off: deposition data"
 author: "Fernando Cagua"
@@
 library(ggplot2)
-knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 7)
+knitr::opts_chunk$set(warning = FALSE,
+                      message = FALSE,
+                      fig.width = 8, 
+                      fig.height = 4)
 
@@
            study = x$study)
-})
+}) %>%
+  mutate(pollen_category = recipient == donor,
+         pollen_category = if_else(pollen_category, 
+                                   "conspecific", 
+                                   "heterospecific"),
+         grain_density = n_grains/n_stigma)
 
@@
 The follwing graph shows the number of grains as a function of the overall plant degree (the number of distinct partners across all sites) for both the open and closed treatment.
+Some jitter was added to the x axis to facilitate visualisation.
 
 ```{r}
-# calculate degrees
+# calculate overall degree
 degree_overall <- vis_df %>%
@@
 inner_join(degree_overall, dep_df) %>% 
-  ggplot(aes(x = degree, y = n_grains/n_stigma + 1)) + 
-  geom_point(aes(colour = recipient == donor),
+  ggplot(aes(x = degree, y = grain_density + 1)) + 
+  geom_point(aes(colour = pollen_category),
              position = position_jitter(0.4),
@@
              alpha = 0.7) +
-  geom_smooth(aes(colour = recipient == donor),
+  geom_smooth(aes(colour = pollen_category),
               method = "lm") +
@@
   scale_y_log10() +
-  theme(legend.position = "top")
+  theme(legend.position = "top") +
+  ggtitle("Degree vs pollen count per stigma", "Overall degree")
+
+# inner_join(degree_overall, dep_df) %>% 
 ```
 
-This seems to make sense.
+This is opposite to what we expected, at least for the open treatment.
+But the fact that there is also a possitive relationship between conspecific pollen and degree in the closed treatment highlights the fact that there are differences between species that might need to be accounted for.
+Interestingly, for the open treatment, the relationship between hetrospecific pollen and degree is negative.
+
+Before dwelling into that, let's have a look if the pattern holds for when we look at the site level degrees.
+
+```{r}
+# calculate site degree
+degree_site <- vis_df %>%
+  rename(recipient = plant_name) %>%
+  group_by(study, site, recipient) %>%
+  summarise(degree = n_distinct(animal_name))
+
+inner_join(degree_site, dep_df) %>% 
+  ggplot(aes(x = degree, y = grain_density + 1)) + 
+  geom_point(aes(colour = pollen_category),
+             position = position_jitter(0.4),
+             size = 1, 
+             alpha = 0.7) +
+  geom_smooth(aes(colour = pollen_category),
+              method = "lm") +
+  facet_grid(~treatment) +
+  scale_y_log10() +
+  theme(legend.position = "top") +
+  ggtitle("Degree vs pollen count per stigma", "Site level degree")
+
+cons_prop <- inner_join(degree_site, dep_df) %>% 
+  group_by(study, plant) %>%
+  arrange(pollen_category) %>% 
+  summarise(conspecific = first(grain_density),
+            heterospecific = last(grain_density),
+            cons_prop = conspecific/(conspecific + heterospecific),
+            cons_log_dif = log(conspecific + 1) - log(heterospecific + 1))
+
+dep_df %>%
+  select(treatment, site, study, recipient, plant) %>%
+  distinct() %>% 
+  inner_join(cons_prop) %>% 
+  inner_join(degree_site) %>% 
+  ggplot(aes(x = degree, y = cons_prop)) + 
+  geom_point(aes(colour = recipient), 
+             position = position_jitter(0.3),
+             size = 1, 
+             alpha = 0.7) +
+  geom_smooth(method = "glm", color = "black", method.args = list(family = "binomial")) +
+  facet_grid(~treatment) +
+  theme(legend.position = "top") +
+  ggtitle("Degree vs conspecific/heterospecific proportion", "Site level degree")
+
+dep_df %>%
+  select(treatment, site, study, recipient, plant) %>%
+  distinct() %>% 
+  inner_join(cons_prop) %>% 
+  inner_join(degree_site) %>% 
+  ggplot(aes(x = degree, y = cons_log_dif)) + 
+  geom_point(aes(colour = recipient), 
+             position = position_jitter(0.3),
+             size = 1, 
+             alpha = 0.7) +
+  geom_smooth(method = "lm", color = "black", method.args = list(family = "gaussian")) +
+  facet_grid(~treatment) +
+  theme(legend.position = "top") +
+  ggtitle("Degree vs conspecific/heterospecific log-difference", "Site level degree")
+```
+
+It seems like yes, the unexpected pattern holds even when looking at the commity level degree.
+This pattern is also obvious when we visualise the proportion of conspecific-heterospecific pollen.
+We do that as a natural logarithm difference to improve normality.
+
+Now let's look into removing the effect of self pollination as a mean to approximate the amount of pollen contributed by pollinators.
+To do that I subtract the median (because pollen counts are non-normal) of the grain density in the closed treatment to the sampled grain density in the open treatment.
+I include only plants that had at least one heterospecific pollen grain in the open treatment to prevent the inclusion of those that might have not had any pollinator visit.
+In any case the proportion of plants without heterospecific pollen was very low (~4% for hugo's study).
+
+We look at the differences using both the absolute difference in pollen grains and in proportion. Using proportion has the advantage of reducing the differences between plants
+
+```{r, fig.height=6}
+dep_benefit <- dep_df %>%
+  filter(treatment == "closed") %>%
+  group_by(study, recipient,  pollen_category) %>%
+  summarise(grain_density_selfpol = median(grain_density)) %>% 
+  inner_join(dep_df) %>%
+  inner_join(degree_site) %>%
+  mutate(grain_density_surplus_prop =  grain_density/(grain_density_selfpol),
+         grain_density_surplus = grain_density - grain_density_selfpol)
+
+dep_benefit %>%
+  filter(treatment == "open") %>%
+  group_by(study, plant) %>%
+  mutate(has_heterospecific = !any(pollen_category == "heterospecific" &
+                                     n_grains == 0)) %>% 
+  filter(has_heterospecific) %>%
+  reshape2::melt(measure.vars = c("grain_density_surplus", "grain_density_surplus_prop")) %>%
+  ggplot(aes(x = degree, y = value)) +
+  geom_point(aes(colour = recipient), 
+             position = position_jitter(0.4),
+             size = 1, 
+             alpha = 0.7) +
+  geom_smooth(aes(x = degree, group = pollen_category), colour = "black") +
+  # geom_boxplot(aes(colour = pollen_category)) +
+  theme(legend.position = "top") +
+  facet_grid(variable~pollen_category, scales = "free_y") +
+  ggtitle("Degree vs. pollination contributed polllen density", 
+          "Degree & self-pollination baseline at the site level")
+```
+
+From the plot we can more or less infer that when we discount the effect of self-pollination, degree seems to have a negative effect on the ammount of conspecific pollen but only until a certain level, after which it flattens out.
+Similar patterns are observable for the heterospecific pollen.
+
+In terms of absolute numbers, plants receive more conspecific pollen grains than heterospecific pollen grains when pollinators enter the equation.
+In terms of proportion, as expected, the amount of heterospecific pollen that enters is greater than the amount of conspecific pollen.
+
+If everything is correct then this data seems to support the idea that raw number of conspecific pollen is more valuable for plants than the actual proportion.
+
+# Outstanding issues
+
+* I have estigmatic pollen from Tur, Emer and Barrero but only really have networks of some kind for the same time for Barrero. 
+* Is the sample size large enough? Doesn't look like it... Might need to change focus. Back to Visitation * Transport to predict deposition? 
+* I can integrate Emer data using visitation data from other year but there is no closed treatment. So What would be the insight there?
+* In any case why so many heterospecific pollen grains in the closed treatment? Flowers were supposedly bagged before anthesis
+* Why closed and open treatment, most people don't bother doing that.
+* I can use Kaiser-Bunbury data to relate degree and set seed. But I'm not convinced of the degree vs. benefit hypothesis anymore

### 2017-09-28 ABC-abstract.Rmd
Abc Abstract

---
title: "The relationship between generalism and the pollination benefit"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
output: html_document
---

The reproduction of angiosperms relies to a large extent on the service provided by pollinators. 
It has been shown that the quality of the pollination service in a plant community increases with the diversity of the pollinator species. 
However, it is generally believed that interacting with a large number of species is not exclusively beneficial. 
This is because plants that interact with a large number of species are more likely to suffer from interspecific pollen transfer, which reduces the quality of the pollination service. 
Although this trade-off has implicitly or explicitly incorporated in several models of pollination, it has never been empirically tested at the community level. 
Here I use visitation, abundance, and pollen deposition data from eleven pollination communities in the Argentinean pampa to test whether this trade-off is observable. 
Contrary to the expectation, we did not find a negative relationship between the number of partners of a plant and the proportion of conspecific pollen found in the flower's stigma. 
Instead, we found that generalist plants, which were generally more abundant, tend to produce greater amounts of pollen, were less dependent on animal pollination, and were less susceptible to receive heterospecific pollen. 
Overall our findings suggest that some traits have evolved to reduce the trade-off between generalism and pollination benefit observed in nature.

### 2017-09-28 ABC-abstract.Rmd
Daniel's feedback to ABC abstract

@@
 ---
-title: "The relationship between generalism and the pollination benefit"
+title: "The relationship between plant generalism and the benefit of pollination"
 author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
-output: html_document
+output:
+  word_document: default
+  html_document: default
 ---
@@
 It has been shown that the quality of the pollination service in a plant community increases with the diversity of the pollinator species. 
-However, it is generally believed that interacting with a large number of species is not exclusively beneficial. 
-This is because plants that interact with a large number of species are more likely to suffer from interspecific pollen transfer, which reduces the quality of the pollination service. 
-Although this trade-off has implicitly or explicitly incorporated in several models of pollination, it has never been empirically tested at the community level. 
-Here I use visitation, abundance, and pollen deposition data from eleven pollination communities in the Argentinean pampa to test whether this trade-off is observable. 
-Contrary to the expectation, we did not find a negative relationship between the number of partners of a plant and the proportion of conspecific pollen found in the flower's stigma. 
-Instead, we found that generalist plants, which were generally more abundant, tend to produce greater amounts of pollen, were less dependent on animal pollination, and were less susceptible to receive heterospecific pollen.
-Overall our findings suggest that some traits have evolved to reduce the trade-off between generalism and pollination benefit observed in nature.
+However, it is also true that interacting with a large number of pollinator species is not always beneficial. 
+One reason for this is that plants that interact with a large number of species are more likely to suffer from interspecific pollen transfer, which reduces the overall quality of the pollination service they receive.
+Although this trade-off has been implicitly or explicitly incorporated in several models of pollination, it has never been empirically tested at the community level. 
+Here I use visitation, abundance, and pollen-deposition data from eleven pollination communities in the Argentinean pampa to test whether this trade-off is observable. 
+Contrary to our expectation, we did not find a negative relationship between the number of partners of a plant and the proportion of conspecific pollen found in the flower's stigma. 
+Instead, we found that generalist plants—which were generally more abundant—tend to produce greater amounts of pollen, were less dependent on animal pollination, and were less susceptible to receive heterospecific pollen.
+Overall our findings suggest that plants have evolved traits or mechanisms that reduce the generalism-benefit trade-off observed in nature.

### 2017-11-16 paper/exploration.Rmd
Updates to the exploration of the phylogeny

--- 2017-04-05 paper/exploration.Rmd
@@
 library(ggplot2)
-knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 7)
+library(ape)
+knitr::opts_chunk$set(warning = FALSE,
+                      message = FALSE,
+                      fig.width = 8, 
+                      fig.height = 6)
 
@@
            study = x$study)
+}) %>%
+  mutate(pollen_category = recipient == donor,
+         pollen_category = if_else(pollen_category, 
+                                   "conspecific", 
+                                   "heterospecific"),
+         grain_density = n_grains/n_stigma)
+
+deg <- readRDS("../data/datasets/processed/all_degree.rds")
+deg_df <- plyr::ldply(deg, function(x){
+  x$degree %>%
+    mutate(study = x$study)
 })
-
-vis <- readRDS("../data/datasets/processed/all_visitation.rds")
-vis_df <- plyr::ldply(vis, function(x){
-  x$visitation %>%
-    mutate(site = x$name, 
-           study = x$study)
-})
+phylo <- readRDS("../data/datasets/processed/all_phylogeny.rds")
 ```
 
-This is a preliminary analysis using Hugo's data. Here, species degree is independently calculated from the visitation network.
+This is a preliminary analysis using Hugo's and Emer data. Here, species degree is independently calculated from a visitation network.
 
-Particular to this study is the use of control flowers to account for the effect of self pollination.
+In Hugo's data control flowers  were used to account for the effect of self pollination.
 The treatment "closed" corresponds to when flowers were bagged, and the treatment "open" allowed for insects to come and pollinate the flower.
@@
 The follwing graph shows the number of grains as a function of the overall plant degree (the number of distinct partners across all sites) for both the open and closed treatment.
+Some jitter was added to the x axis to facilitate visualisation.
 
 ```{r}
-# calculate degrees
-degree_overall <- vis_df %>%
-  rename(recipient = plant_name) %>%
-  group_by(study, recipient) %>%
-  summarise(degree = n_distinct(animal_name))
 
-inner_join(degree_overall, dep_df) %>% 
-  ggplot(aes(x = degree, y = n_grains/n_stigma + 1)) + 
-  geom_point(aes(colour = recipient == donor),
-             position = position_jitter(0.4),
+inner_join(deg_df, dep_df, by = c("plant_name" = "recipient", "study")) %>% 
+  filter(!is.na(pollen_category)) %>%
+  ggplot(aes(x = degree, y = grain_density + 1)) + 
+  geom_point(aes(colour = pollen_category),
+             position = position_jitter(0.01),
              size = 1, 
              alpha = 0.7) +
-  geom_smooth(aes(colour = recipient == donor),
+  geom_smooth(aes(colour = pollen_category),
               method = "lm") +
-  facet_grid(~treatment) +
+  facet_grid(study~treatment) +
   scale_y_log10() +
-  theme(legend.position = "top")
+  scale_x_log10() +
+  theme(legend.position = "top") +
+  ggtitle("Degree vs pollen count per stigma", "Overall degree")
+
+# inner_join(degree_overall, dep_df) %>% 
 ```
 
-This seems to make sense.
+Now looking at the proportion:
+
+```{r}
+cons_prop <- inner_join(deg_df, dep_df, by = c("plant_name" = "recipient", "study")) %>% 
+  group_by(study, plant) %>%
+  arrange(pollen_category) %>% 
+  summarise(conspecific = first(grain_density),
+            heterospecific = last(grain_density),
+            cons_prop = conspecific/(conspecific + heterospecific),
+            cons_log_dif = log(conspecific + 1) - log(heterospecific + 1))
+
+dep_df %>%
+  select(treatment, site, study, recipient, plant) %>%
+  distinct() %>% 
+  inner_join(cons_prop) %>% 
+  inner_join(deg_df, by = c("recipient" = "plant_name", "study")) %>% 
+  ggplot(aes(x = degree, y = cons_prop)) + 
+  geom_point(aes(colour = recipient), 
+             position = position_jitter(0.3),
+             size = 1, 
+             alpha = 0.7) +
+  geom_smooth(method = "glm", color = "black", method.args = list(family = "binomial")) +
+  facet_grid(study~treatment) +
+  theme(legend.position = "none") +
+  ggtitle("Degree vs conspecific/heterospecific proportion", "Site level degree")
+
+dep_df %>%
+  select(treatment, site, study, recipient, plant) %>%
+  distinct() %>% 
+  inner_join(cons_prop) %>% 
+  inner_join(deg_df, by = c("recipient" = "plant_name", "study")) %>% 
+  ggplot(aes(x = degree, y = cons_log_dif)) + 
+  geom_point(aes(colour = recipient), 
+             position = position_jitter(0.3),
+             size = 1, 
+             alpha = 0.7) +
+  geom_smooth(method = "lm", color = "black", method.args = list(family = "gaussian")) +
+  facet_grid(study~treatment) +
+  theme(legend.position = "none") +
+  ggtitle("Degree vs conspecific/heterospecific log-difference", "Site level degree")
+```
+
+## Phylogenies
+
+A quick & dirty phylogeny from phylomatic using the subset of species is shown here. To future versions a dated phylogeny based on sequence data will be generated.
+
+```{r}
+phylo_plants <- phylo$tip.label
+study_plants <- inner_join(deg_df, 
+                           dep_df, 
+                           by = c("plant_name" = "recipient", "study")) %$%
+  plant_name %>%
+  unique() %>% 
+  tolower() %>% 
+  gsub(" ", "_", .)
+
+trim_phylo <- drop.tip(phylo,phylo_plants[!phylo_plants %in% study_plants])
+plot(trim_phylo)
+```
+
+We check wether degree is phylogenetically conserved once we have branch lengths.
+
+```{r, eval = F}
+deg_df %>%
+  mutate(plant_name_phylo = tolower(plant_name), 
+         plant_name_phylo = gsub(" ", "_", plant_name_phylo)) %>%
+  right_join(data.frame(plant_name_phylo = trim_phylo$tip.label)) %>%
+  group_by(plant_name_phylo) %>%
+  summarise(degree = mean(degree)) %$%
+  degree %>% log() %>%
+  phytools::phylosig(trim_phylo, .)
+```
+
+Re weight degree -> 
+* Quality pollinator based on what they carry
+* Plant phenology (temporal overlap)
+* Strengt:degree
+* MCMCglmm

### 2017-11-16 paper/abc_analyses.Rmd
ABC Analyses and figures

---
title: "ABC Analyses"
author: "Fernando Cagua"
date: "24 October 2017"
output: html_document
---
```{r setup, message=FALSE, results='hide'}
library(dplyr)
library(ggplot2)
library(ape)
library(magrittr)
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.width = 8, 
                      fig.height = 6)

# read data
dep <- readRDS("../data/datasets/processed/all_deposition.rds")
dep_df <- plyr::ldply(dep, function(x){
  if(x$study == "marrero"){
    x$deposition %>%
    mutate(site = x$name, 
           study = x$study, 
           locality = x$locality, 
           land_use = x$land_use, 
           fragment = x$fragment)
  }

}) %>%
  mutate(pollen_category = recipient == donor,
         pollen_category = if_else(pollen_category, 
                                   "conspecific", 
                                   "heterospecific"),
         grain_density = n_grains/n_stigma)

deg <- readRDS("../data/datasets/processed/all_degree.rds")
deg_df <- plyr::ldply(deg, function(x){
  x$degree %>%
    mutate(study = x$study)
})
```

```{r}
theme_black = function(base_size = 12, base_family = "") {

  theme_grey(base_size = base_size, base_family = base_family) %+replace%

    theme(
      # Specify axis options
      axis.line = element_blank(),  
      axis.text.x = element_text(size = base_size*0.8, color = "white", lineheight = 0.9),  
      axis.text.y = element_text(size = base_size*0.8, color = "white", lineheight = 0.9),  
      axis.ticks = element_line(color = "white", size  =  0.2),  
      axis.title.x = element_text(size = base_size, color = "white", margin = margin(10, 0, 0, 0)),  
      axis.title.y = element_text(size = base_size, color = "white", angle = 90, margin = margin(0, 10, 0, 0)),  
      axis.ticks.length = unit(0.3, "lines"),   
      # Specify legend options
      legend.background = element_rect(color = NA, fill = "black"),  
      legend.key = element_rect(color = "white",  fill = "black"),  
      legend.key.size = unit(1.2, "lines"),  
      legend.key.height = NULL,  
      legend.key.width = NULL,      
      legend.text = element_text(size = base_size*0.8, color = "white"),  
      legend.title = element_text(size = base_size*0.8, face = "bold", hjust = 0, color = "white"),  
      legend.position = "right",  
      legend.text.align = NULL,  
      legend.title.align = NULL,  
      legend.direction = "vertical",  
      legend.box = NULL, 
      # Specify panel options
      panel.background = element_rect(fill = "black", color  =  NA),  
      panel.border = element_rect(fill = NA, color = "white"),  
      panel.grid.major = element_line(color = "grey35"),  
      panel.grid.minor = element_line(color = "grey20"),  
      panel.margin = unit(0.5, "lines"),   
      # Specify facetting options
      strip.background = element_rect(fill = "grey30", color = "grey10"),  
      strip.text = element_text(size = base_size, margin = margin(t = 4, b = 4, r = 4, l = 4)),
      strip.text.x = element_text(color = "white"),  
      strip.text.y = element_text(color = "white",angle = -90),  
      # Specify plot options
      plot.background = element_rect(color = "black", fill = "black"),  
      plot.title = element_text(size = base_size*1.2, color = "white"),  
      plot.margin = unit(rep(1, 4), "lines")

    )

}

```

```{r}
# Calculate mean grain density over a grouping
mean_grain_density <- function(df, ...){
  gb_treat <- quos(..., treatment)

  df %>%
  group_by(!!!gb_treat) %>%
  summarise(mean_grain_density = mean(grain_density),
            sd_grain_density = sd(grain_density))
}

# Calculate difference between open and closed treatment within a grouping
calc_grain_diff <- function(df, ...){
  gb_treat <- quos(..., treatment)
  gb <- quos(...)

  mean_grain_density(df, ...) %>%
  group_by(!!!gb) %>%
  add_count() %>%
  filter(n == 2) %>%
  arrange(!!!gb_treat) %>%
  summarise(mean_grain_difference = mean_grain_density[2] - mean_grain_density[1],
            sd_grain_difference = sqrt(sd_grain_density[2]^2 + sd_grain_density[1]^2))
}

fragment_grain_density <- mean_grain_density(dep_df, locality, land_use, fragment, pollen_category, recipient)

open_treatment <- fragment_grain_density %>%
  filter(treatment == "open") %>%
  select(-sd_grain_density)

# order of plants
plant_order <- open_treatment %>% 
  filter(pollen_category == "conspecific") %>%
  group_by(recipient) %>%
  summarise(mean_grain_density = median(mean_grain_density)) %>%
  arrange(desc(mean_grain_density)) %$%
  recipient

open_treatment %>%
  group_by() %>%
  mutate(recipient = factor(recipient, levels = plant_order)) %>%
  ggplot(aes(x = recipient, y = mean_grain_density)) +
  facet_grid(pollen_category~., scales = "free")+
  geom_boxplot(colour = "white", fill = "black") +
  scale_y_log10(name = "# pollen grains per stigma") +
  xlab("") +
  theme_black(base_size = 18) +
  theme(axis.text.x = element_text(angle= 90, face = "italic"))

ggsave(filename = "boxplots.png", width = 13.3, height = 7.5)

fragment_grain_density %>%
  group_by() %>%
  mutate(recipient = factor(recipient, levels = plant_order), 
         treatment = factor(treatment, levels = c("open", "closed"), labels = c("open flowers ", "bagged flowers "))) %>%
  filter(pollen_category == "conspecific", 
         !is.na(recipient)) %>%
  ggplot(aes(x = recipient, y = mean_grain_density)) + 
  geom_boxplot(aes(fill = treatment, colour = treatment), alpha = 0.5) +
  scale_y_log10(name = "# pollen grains per stigma") +
  scale_fill_brewer(palette = "Pastel1", name = "", guide = guide_legend(title = NULL, direction = 'horizontal')) +
  	scale_colour_brewer(palette = 'Pastel1', name = "", guide = guide_legend(title = NULL, direction = 'horizontal')) +
  xlab("") +
  theme_black(base_size = 18) +
  theme(axis.text.x = element_text(angle= 90, face = "italic"), 
        legend.position = "top")

ggsave(filename = "boxplots-openclosed.png", width = 13.3, height = 7.5)

fragment_grain_diff <- calc_grain_diff(dep_df, locality, land_use, fragment, pollen_category, recipient)

fragment_grain_diff %>%
  select(-sd_grain_difference) %>%
  tidyr::spread(pollen_category, mean_grain_difference) %>%
  ggplot(aes(x = conspecific, y = heterospecific)) +
  geom_point(colour = "white") +
  geom_smooth(method = "lm", colour = "white") +
  scale_x_log10(name = "conspecific pollen gained with animal pollination") +
  scale_y_log10(name = "heterospecific pollen") +
  theme_black(base_size = 18)

ggsave(filename = "scatterplot-conspecific-heterospecifiv.png", width = 13.3, height = 7.5)

locality_grain_diff <- calc_grain_diff(dep_df, locality, pollen_category, recipient)
species_grain_diff <- calc_grain_diff(dep_df, pollen_category, recipient)

```

```{r}
fragment_grain_diff %>% 
  select(-sd_grain_difference) %>%
  mutate(mean_grain_difference = if_else(mean_grain_difference < 0, 0, mean_grain_difference)) %>% 
  tidyr::spread(pollen_category, mean_grain_difference) %>%
  left_join(deg_df, by = c("recipient" = "plant_name")) %>% 
  mutate(relationship = conspecific/(heterospecific + conspecific)) %>% 
  filter(.id != "emer") %>% 
  ggplot(aes(x = degree, y = relationship)) +
  geom_point(colour = "white") +
  geom_smooth(method = "glm", color = "white") +
  scale_x_log10(name = "number of partners") + 
  scale_y_continuous(name = "quality of animal pollination", labels = scales::percent) +
  theme_black(base_size = 18)

ggsave(filename = "scatterplot-efficiency.png", width = 13.3, height = 7.5)

```
sd

### 2017-12-19 paper/manuscript.Rmd
Methods in a wrapping table

---
title: "Pollen competition"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
date: "19 December 2017"
output: pdf_document
bibliography: references.bib
csl: ecology-letters.csl
header-includes:
- \usepackage{booktabs}
- \usepackage{tabularx}
- \usepackage{setspace}
---

\doublespacing

```{r, echo = F, message = F}
library(magrittr)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE, 
  warning = FALSE
)
options("xtable.include.rownames" = FALSE,
        "xtable.comment" = FALSE,
        "xtable.size" = "small")
```

## Abstract

## Introduction

## Methods

### Data collection

We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas (Figure 1). 
The sampling locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and an drier as we move inland and westward towards the Pampean Grasslands.
Across all sites, annual mean temperatures range between 14.8 and 15.8 Celsius.

In each location, we sampled two restored and two agricultural fragments. 
However, due to the lack of available sites in the Flooding Pampas, it was only possible to sample one restored site.
We visited each fragment monthly between November and March between 2010 and 2011. 
In each visit we gathered information related to abundance, plant-pollinator visitation, pollen transfer, and pollen deposition.
For more information about the study sites and data collection protocols can be found in previous publications [@Marrero2014; @Marrero2016; @Marrero2017].

```{r, results='asis'}
readr::read_csv("variables_sampled.csv") %>%
  dplyr::rename(` ` = Var) %>%
  xtable::xtable(caption = "Variables sampled", align = c("l", "l", "X")) %>%
  print(booktabs = TRUE, tabular.environment = "tabularx", width = "\\linewidth")
```

### Data analysis

## Results

## Discussion

## References

### 2017-12-20 paper/manuscript.Rmd
Methods data collection

@@
 - \usepackage{booktabs}
-- \usepackage{tabularx}
 - \usepackage{setspace}
@@
 However, due to the lack of available sites in the Flooding Pampas, it was only possible to sample one restored site.
-We visited each fragment monthly between November and March between 2010 and 2011. 
-In each visit we gathered information related to abundance, plant-pollinator visitation, pollen transfer, and pollen deposition.
-For more information about the study sites and data collection protocols can be found in previous publications [@Marrero2014; @Marrero2016; @Marrero2017].
+We visited each fragment in November 2010 and February 2011. 
+In each of these visits we gathered information related to abundance, plant-pollinator visitation, pollen transfer, and pollen deposition.
 
-```{r, results='asis'}
-readr::read_csv("variables_sampled.csv") %>%
-  dplyr::rename(` ` = Var) %>%
-  xtable::xtable(caption = "Variables sampled", align = c("l", "l", "X")) %>%
-  print(booktabs = TRUE, tabular.environment = "tabularx", width = "\\linewidth")
-```
+Abbundance was estimated using two 50 m randomly located transects in each fragment.
+In a first sampling we counted all units of floral attraction taht were found in a 2 m wide strip.
+In a second sampling we counted and collected all floral visitors while walking at a pace of 10 m per minute [@Marrero2014; @Memmott1999].
+We constructed quantitative visitation networks using information about the floral visitors collected during abundance transects [@Marrero2014]. 
+In addition, we also constructed qualitative visitation networks during independent two hour observations of floral visits across each fragment.
+We estimated pollen transfer by examining the pollen loads present on the collected floral visitors [@Marrero2017]. 
+Where the pollen count on an individual was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 
+When the pollen count was above 2,000 grains, we clasified approx. 50% of pollen and total pollen counts were extrapollated [@Bosch2009]. 
+If more than 10 pollen grains from a plant species were identified, we assumed that pollination service between the plant and the pollinator existed. 
+Finally, we analised pollen deposition in a subset of the plant community [@Marrero2016]. 
+This subset comprised between three and nine of the most common entomophilus species that were flowering during the samplimg period while ensuring that the chosen species covered a wide range on a specialization-generalization gradient.
+In the selected plants we removed all flowers except buds that were expected to go into inflorecense on the next day. 
+A quarter of these buds were bagged to prevent animal pollination. 
+Two days after inflorecense, we analysed the pollen grains in the flowers' pistils and classified it between conspecific and heterospecific pollen.
+
+The reader can find more details about the study sites, the data collection, and laboratory protocols in Marrero *et al.* (2014, 2016, and 2017)
+\footnote{
+This paper is almost entirely based on data that has already been published in separate units in Marrero et al. 2014, 2016, and 2017. 
+Marrero et al. 2014 used visitation data and determined that land uses (agricultural vs. restored) was correlated to differences on the degree of specialization and richness of plants and pollinators.
+Marrero et al.
+2016 used pollen deposition data and determined that the pollination service (both the absolute number and the proportion of conspecific pollen deposited on stigmas) is reduced in agricultural communities when compared to restored communities.
+Finally, Marrero et al. 2017 used pollen transfer networks and found that pollen diversity and pollination plant niche overlap (at the species level) is greater in agricultural communities. 
+The increase on niche overlap was attributed to be positively associated with an increased abundance of exotic plants.
+}.
 

### 2018-02-09 paper/manuscript.Rmd
Just staging all shit so I can continue on the PC

@@
 
-The reader can find more details about the study sites, the data collection, and laboratory protocols in Marrero *et al.* (2014, 2016, and 2017)
-\footnote{
+The reader can find more details about the study sites, the data collection, and laboratory protocols in Marrero *et al.* (2014, 2016, and 2017)\footnote{
 This paper is almost entirely based on data that has already been published in separate units in Marrero et al. 2014, 2016, and 2017. 

### 2018-02-09 code/assemble.R

@@ -7,7 +7,9 @@ args <- commandArgs(trailingOnly = TRUE)
 # # testing defaults
 # args <- list.files("data/datasets/processed/deposition", full.names = T)
 
-input_files <- args[1:(length(args)-1)]
+input_files <- c("./data/datasets/processed/degree/marrero.rds", 
+                 "data/datasets/processed/deposition/marrero.rds", 
+                "data/datasets/processed/visitation/marrero.rds")
 output_file <- args[length(args)]
 
 data <- foreach(i=1:length(input_files), .combine = c) %do% {

### 2018-02-09 code/clean_marrero.R

@@ -271,7 +271,7 @@ data_dep <- plyr::llply(data_dep, change_names_site,
 
 qual_vis_file <- "data/datasets/raw/marrero2016/qualitative_visits.csv" 
 
-qua <- read_csv(qual_vis_file)
+qua <- readr::read_csv(qual_vis_file)
 qua %<>%
   rename(plant_name = plant,
          fragment_name = fragment, 
@@ -303,15 +303,37 @@ data_vis_qual <- foreach(i=1:n_distinct(site_data$site_name)) %do% {
   site
 }
 
-qua %>% arrange(date, locality,fragment_name) %>% filter(locality == "LC") %>% View()
+# ARMONISE DEPOSITION AND QUALITATIVE VISITS ------------------------------
+
+data_vis_qual <- plyr::llply(data_vis_qual, change_names_site, 
+                        affected_col = c("plant_name", "donor", "recipient"),
+                        from = "Descurania argentina", 
+                        to = "Descurainia argentina")
+
+data_vis_qual <- plyr::llply(data_vis_qual, change_names_site, 
+                        affected_col = c("plant_name", "donor", "recipient"),
+                        from = "Dipsacus sp.", 
+                        to = "Dipsacus sativus")
+
+data_vis_qual <- plyr::llply(data_vis_qual, change_names_site, 
+                        affected_col = c("plant_name", "donor", "recipient"),
+                        from = "Nothoscordum euosimum", 
+                        to = "Nothoscordum nudicaule")
+
+data_vis_qual <- plyr::llply(data_vis_qual, change_names_site, 
+                        affected_col = c("plant_name", "donor", "recipient"),
+                        from = "Thelesperma sp.", 
+                        to = "Thelesperma megapotamicum")
+
+# qua %>% arrange(date, locality,fragment_name) %>% filter(locality == "LC") %>% View()
 
 dep_plants <- plyr::ldply(data_dep, function(x) x$plant_data) %>%
   distinct()
-vis_plants <- plyr::ldply(data_vis, function(x) x$plant_data) %>%
+vis_plants <- plyr::ldply(data_vis_qual, function(x) x$visitation %>% group_by(plant_name) %>% summarise(a=1)) %>%
   distinct()
 
 full_join(dep_plants, vis_plants, by = "plant_name") %>%
-  arrange(plant_name) 
+  arrange(plant_name) %>% View
 
 saveRDS(data, output_file)
 

### 2018-02-09 code/construct_phylogenies.R

@@ -1,0 +1,51 @@
+library(dplyr)
+library(brranching)
+library(taxize)
+library(tibble)
+args <- commandArgs(trailingOnly = TRUE)
+dep <- readRDS(args[1])
+vis <- readRDS(args[2])
+deg <- readRDS(args[3])
+output_file <- args[4]
+# 
+deg <- readRDS("data/datasets/processed/all_degree.rds")
+dep <- readRDS("data/datasets/processed/all_deposition.rds")
+vis <- readRDS("data/datasets/processed/all_visitation.rds")
+
+dep_species <- dep %>%
+  plyr::llply(function(x) as.character(x$deposition$recipient)) %>% 
+  do.call(c, .) %>% as.data.frame() %>% rownames_to_column("net") %>%
+  mutate(net = gsub("[0-9]+", "", net), 
+         net = substr(net, 1, nchar(net)-1)) %>% 
+  distinct()
+
+hugo_dep_species <- dep %>%
+  plyr::llply(function(x) {
+    if(x$study == "marrero") x$deposition$recipient
+  }) %>%
+  do.call(c, .) %>% unique()
+deg_species <- deg %>%
+  plyr::llply(function(x) as.character(x$degree$plant_name)) %>% 
+  do.call(c, .) %>% as.data.frame() %>% rownames_to_column("net") %>%
+  mutate(net = gsub("[0-9]+", "", net), 
+         net = paste(net, "deg")) %>% 
+  distinct()
+vis_species <- vis %>%
+  plyr::llply(function(x) as.character(x$visitation$plant_name)) %>% 
+  do.call(c, .) %>% unique()
+
+plant_names <- dep_species %>% 
+  union(deg_species) %>%
+  union(vis_species)
+
+# fix misspelled names
+plant_names <- plant_names %>%
+  gsub('Descurania argentina', 'Descurainia argentina', .) %>%
+  gsub('Chiliotrichium rosmarinifolium', 'Chiliotrichum rosmarinifolium', .) 
+
+
+pt <- phylomatic(plant_names, get = 'POST')
+# in_hugos <- if_else(pt$tip.label %in% gsub(" ", "_", tolower(hugo_dep_species)),
+                    # "red", "black")
+
+saveRDS(pt, output_file)

### 2018-02-19 main.R
Add some analysis and reporting

@@ -1,9 +1,16 @@
+# basic R
+library(stats)
+library(utils)
+# additional packages
 library(dplyr)
 library(foreach)
 library(drake)
 library(tools)
 library(stringr)
 library(magrittr)
+library(knitr)
+library(rmarkdown)
+library(xtable)
 
 # load functions
 functions_folder <- './functions'
@@ -22,14 +29,30 @@ clean_data <- drake_plan(
 )
 
 format_data <- drake_plan(
-  pollination_gain = con_hetero_specific(armonised_data, sites)
+  dep_frame = extract_dep_frame(armonised_data),
+  # control_dep_plant = extract_closed_treatment_means(dep_frame, c("season", "site_name", "plant")),
+  # control_dep_site = extract_closed_treatment_means(dep_frame, c("season", "site_name")),
+  # control_dep_global = extract_closed_treatment_means(dep_frame, NULL), 
+  strings_in_dots = 'literals'
+)
+
+analysing <- drake_plan(
+  consp_self = model_conspecific_self(dep_frame),
+  significant_gain_global = mann_withney_part_df(dep_frame, by = 'recipient', var = 'treatment'),
+  significant_gain_site = mann_withney_part_df(dep_frame, by = c('recipient', 'site_name'), var = 'treatment'),
+  strings_in_dots = 'literals'
+)
+
+reporting <- drake_plan(
+  'publication/supp_info.pdf' = render('publication/supp_info.Rmd', quiet = TRUE),
+  file_targets = TRUE
 )
 
 # set up plan
-project_plan <- rbind(clean_data, format_data)
+project_plan <- rbind(clean_data, format_data, analysing, reporting)
 project_config <- drake_config(project_plan)
 vis_drake_graph_sml0(project_config)
 
 # execute plan
-make(clean_data)
+make(project_plan)
 vis_drake_graph_sml0(project_config)

### 2018-02-19 functions/plotting.R
Plotting functions

@@ -1,0 +1,8 @@
+pub_theme <- function(){
+  theme_bw() +
+    theme(text = element_text(size = 8), 
+          title = element_text(size = 8),
+          strip.background = element_blank(),
+          strip.text = element_text(hjust = 0),
+          legend.title = element_text(hjust = 0.5))
+}

### 2018-02-19 publication/supp_info.Rmd
Supplementary information

---
title: "Supplementary materials"
author: "Fernando Cagua"
output: pdf_document
header-includes:
  - \usepackage{booktabs}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(xtable.comment = FALSE, 
        xtable.caption.placement = 'bottom',
        booktabs = TRUE)
library(drake)
library(ggplot2)
library(xtable)
library(tidyr)
```

```{r}
loadd(dep_frame, sites, consp_self)
```

```{r variation across sites, results='asis'}
consp_self %>%
  anova(test = "Chisq")  %>%
  xtable(caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).  Density were modelled using a quasipoisson distribution. The model suggests that self-pollination rates are species dependent but not across.')
```

```{r make figures per site}
site_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>% 
  plyr::dlply('site_name', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = recipient_short,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() + 
      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Greys")
  })

legend <- cowplot::get_legend(site_plots_conspecific[[1]])

site_plots_conspecific <- site_plots_conspecific %>%
  plyr::llply(function(x) {
    x + theme(legend.position = 'none', 
              title = element_text(size = 6))
  })

site_plots_conspecific <- rlist::list.append(site_plots_conspecific, legend)
```

```{r plot conspecific per site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different sites."}
cowplot::plot_grid(plotlist = site_plots_conspecific, ncol = 3)
```

```{r figure per plant}
plant_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name)) %>%
  group_by() %>%
  filter(n_sites >= 2) %>%
  plyr::dlply('recipient', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = site_name,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() +
      ggtitle(paste(x$recipient[1])) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Greys")
  })

legend <- cowplot::get_legend(plant_plots_conspecific[[1]])

plant_plots_conspecific <- plant_plots_conspecific %>%
  plyr::llply(function(x) {
    x + theme(legend.position = 'none',
              title = element_text(size = 6))
  })

plant_plots_conspecific <- rlist::list.append(plant_plots_conspecific, legend)
```

```{r plot conspecific per plant, fig.height = 7, fig.cap="Conspecific pollen density across sites for different study species. Only species present in more than onse site are shown."}
cowplot::plot_grid(plotlist = plant_plots_conspecific, ncol = 3)
```

### 2018-02-19 publication/manuscript.Rmd
Manuscript initial commit

---
title: "Pollen competition"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
output: pdf_document
header-includes:
  - \usepackage{booktabs}
---

### 2018-02-19 publication/supp_info.Rmd
Smaller table text

@@
         xtable.caption.placement = 'bottom',
+        xtable.size = 'small',
         booktabs = TRUE)

### 2018-02-19 publication/manuscript.Rmd
Add previous text

@@
 author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
+bibliography: references.bib
+csl: ecology-letters.csl
 output: pdf_document
@@
   - \usepackage{booktabs}
+  - \usepackage{setspace}
 ---
+
+\doublespacing
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
+                      warning = FALSE)
+options(xtable.comment = FALSE, 
+        xtable.caption.placement = 'bottom',
+        xtable.size = 'small',
+        booktabs = TRUE)
+```
+
+## Abstract
+
+## Introduction
+
+## Methods
+
+### Data collection
+
+We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas (Figure 1). 
+The sampling locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and an drier as we move inland and westward towards the Pampean Grasslands.
+Across all sites, annual mean temperatures range between 14.8 and 15.8 Celsius.
+
+In each location, we sampled two restored and two agricultural fragments. 
+However, due to the lack of available sites in the Flooding Pampas, it was only possible to sample one restored site.
+We visited each fragment in November 2010 and February 2011. 
+In each of these visits we gathered information related to abundance, plant-pollinator visitation, pollen transfer, and pollen deposition.
+
+Abbundance was estimated using two 50 m randomly located transects in each fragment.
+In a first sampling we counted all units of floral attraction taht were found in a 2 m wide strip.
+In a second sampling we counted and collected all floral visitors while walking at a pace of 10 m per minute [@Marrero2014; @Memmott1999].
+We constructed quantitative visitation networks using information about the floral visitors collected during abundance transects [@Marrero2014]. 
+In addition, we also constructed qualitative visitation networks during independent two hour observations of floral visits across each fragment.
+We estimated pollen transfer by examining the pollen loads present on the collected floral visitors [@Marrero2017]. 
+Where the pollen count on an individual was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 
+When the pollen count was above 2,000 grains, we clasified approx. 50% of pollen and total pollen counts were extrapollated [@Bosch2009]. 
+If more than 10 pollen grains from a plant species were identified, we assumed that pollination service between the plant and the pollinator existed. 
+Finally, we analised pollen deposition in a subset of the plant community [@Marrero2016]. 
+This subset comprised between three and nine of the most common entomophilus species that were flowering during the samplimg period while ensuring that the chosen species covered a wide range on a specialization-generalization gradient.
+In the selected plants we removed all flowers except buds that were expected to go into inflorecense on the next day. 
+A quarter of these buds were bagged to prevent animal pollination. 
+Two days after inflorecense, we analysed the pollen grains in the flowers' pistils and classified it between conspecific and heterospecific pollen.
+
+The reader can find more details about the study sites, the data collection, and laboratory protocols in Marrero *et al.* (2014, 2016, and 2017)\footnote{
+This paper is almost entirely based on data that has already been published in separate units in Marrero et al. 2014, 2016, and 2017. 
+Marrero et al. 2014 used visitation data and determined that land uses (agricultural vs. restored) was correlated to differences on the degree of specialization and richness of plants and pollinators.
+Marrero et al.
+2016 used pollen deposition data and determined that the pollination service (both the absolute number and the proportion of conspecific pollen deposited on stigmas) is reduced in agricultural communities when compared to restored communities.
+Finally, Marrero et al. 2017 used pollen transfer networks and found that pollen diversity and pollination plant niche overlap (at the species level) is greater in agricultural communities. 
+The increase on niche overlap was attributed to be positively associated with an increased abundance of exotic plants.
+}.
+
+### Data analysis
+
+## Results
+
+## Discussion
+
+## References

### 2018-02-19 main.R
Add paper to workflow

@@ -45,6 +45,7 @@ analysing <- drake_plan(
 
 reporting <- drake_plan(
   'publication/supp_info.pdf' = render('publication/supp_info.Rmd', quiet = TRUE),
+  'publication/manuscript.pdf' = render('publication/manuscript.Rmd', quiet = TRUE),
   file_targets = TRUE
 )
 

### 2018-02-20 publication/supp_info.Rmd
Add wilcox results tables

@@
 
-```{r}
-loadd(dep_frame, sites, consp_self)
+```{r table species gain global, results = 'asis'}
+loadd(significant_gain_global, significant_gain_site, sites)
+glance_table(significant_gain_global) %>%
+  `rownames<-`(.$recipient) %>%
+  select(estimate, statistic, p.value) %>%
+  rename(`p value` = p.value,
+         `difference` = estimate) %>%
+  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. ") %>%
+  print(sanitize.rownames.function = function(x) paste0('{\\emph{ ', x, '}}'))
+```
+
+```{r table species gain site, results = 'asis'}
+loadd(significant_gain_global, significant_gain_site, sites)
+glance_table(significant_gain_site) %>%
+  inner_join(sites, by = "site_name") %>%
+  mutate(site_name = paste(locality_name, land_use, fragment, sep = ' - '),
+         rowname = paste0('{\\emph{ ', recipient, '}} - ', site_name)) %>%
+  `rownames<-`(.$rowname) %>%
+  select(estimate, statistic, p.value) %>%
+  rename(`p value` = p.value,
+         `difference` = estimate) %>%
+  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. ") %>%
+  print(sanitize.rownames.function = function(x) x)
 ```
@@
 ```{r variation across sites, results='asis'}
+loadd(consp_self)
 consp_self %>%

### 2018-02-20 publication/supp_info.Rmd
Make chunks selfsufficient

@@
 
-```{r make figures per site}
+```{r plot conspecific per site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different sites."}
+loadd(dep_frame, sites)
 site_plots_conspecific <- dep_frame %>%
@@
 site_plots_conspecific <- rlist::list.append(site_plots_conspecific, legend)
+
+cowplot::plot_grid(plotlist = site_plots_conspecific, ncol = 3)
+
 ```
 
-```{r plot conspecific per site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different sites."}
-cowplot::plot_grid(plotlist = site_plots_conspecific, ncol = 3)
-```
-
-```{r figure per plant}
+```{r plot conspecific per plant, fig.height = 7, fig.cap="Conspecific pollen density across sites for different study species. Only species present in more than onse site are shown."}
+loadd(dep_frame, sites)
 plant_plots_conspecific <- dep_frame %>%
@@
 plant_plots_conspecific <- rlist::list.append(plant_plots_conspecific, legend)
-```
 
-```{r plot conspecific per plant, fig.height = 7, fig.cap="Conspecific pollen density across sites for different study species. Only species present in more than onse site are shown."}
 cowplot::plot_grid(plotlist = plant_plots_conspecific, ncol = 3)

### 2018-02-20 publication/manuscript.Rmd
Wilcox tests methods

@@
 
+First, we explored wether animal pollination resulted, as expected, in an increase in the pollination service.
+To do that, we compared the conspecific pollen density on flower stigmas of flowers that were open to pollination and that of flowers that were bagged.
+We performed this comparisons using a non parametric Wilcoxon test both at the species level and at the species-site level.
+
 ## Results

### 2018-02-20 main.R
Updates to main

@@ -19,7 +19,7 @@ list_files_with_exts(functions_folder, 'R') %>%
 
 # plan to clean data
 clean_data <- drake_plan(
-  sites = site_data('./data/raw/marrero-estigmatic_pollen.csv'),
+  sites = site_data('./data/raw/marrero-estigmatic_pollen.csv', './data/raw/site_names.csv'),
   deposition = clean_deposition('./data/raw/marrero-estigmatic_pollen.csv', sites),
   visitation_quant = clean_visitation_quant('./data/raw/marrero-quantitative_visits.csv', sites),
   visitation_qual = clean_visitation_qual('./data/raw/marrero-qualitative_visits.csv', sites),
@@ -38,8 +38,8 @@ format_data <- drake_plan(
 
 analysing <- drake_plan(
   consp_self = model_conspecific_self(dep_frame),
-  significant_gain_global = mann_withney_part_df(dep_frame, by = 'recipient', var = 'treatment'),
-  significant_gain_site = mann_withney_part_df(dep_frame, by = c('recipient', 'site_name'), var = 'treatment'),
+  significant_gain_global = mann_withney_part_df(dep_frame, by = 'recipient', var = 'treatment', conf.int = T),
+  significant_gain_site = mann_withney_part_df(dep_frame, by = c('recipient', 'site_name'), var = 'treatment', conf.int = T),
   strings_in_dots = 'literals'
 )
 

### 2018-02-20 main.R
Remove ineccessary workflow visualisation

@@ -52,7 +52,6 @@ reporting <- drake_plan(
 # set up plan
 project_plan <- rbind(clean_data, format_data, analysing, reporting)
 project_config <- drake_config(project_plan)
-vis_drake_graph_sml0(project_config)
 
 # execute plan
 make(project_plan)

### 2018-02-20 publication/supp_info.Rmd
Modify counter of supplementary to include the S
Fix tables

@@
 ---
+
+\renewcommand\thefigure{S\arabic{figure}}    
+\setcounter{figure}{0}
+
+\renewcommand\thetable{S\arabic{table}}    
+\setcounter{table}{0}
 
@@
 glance_table(significant_gain_global) %>%
-  `rownames<-`(.$recipient) %>%
-  select(estimate, statistic, p.value) %>%
+  select(recipient, estimate, statistic, p.value) %>%
+  mutate(recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
   rename(`p value` = p.value,
-         `difference` = estimate) %>%
-  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. ") %>%
-  print(sanitize.rownames.function = function(x) paste0('{\\emph{ ', x, '}}'))
+         `difference` = estimate,
+         `plant species` = recipient) %>%
+  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
+Tests were performed at the species level (across communities).") %>%
+  print.xtable(sanitize.text.function = function(x) x)
 ```
@@
   inner_join(sites, by = "site_name") %>%
+  group_by(recipient) %>%
+  mutate(n_sites = n_distinct(site_name)) %>%
+  filter(n_sites > 1) %>%
+  group_by() %>%
   mutate(site_name = paste(locality_name, land_use, fragment, sep = ' - '),
-         rowname = paste0('{\\emph{ ', recipient, '}} - ', site_name)) %>%
-  `rownames<-`(.$rowname) %>%
-  select(estimate, statistic, p.value) %>%
+         recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
+  select(recipient, site_name, estimate, statistic, p.value) %>%
   rename(`p value` = p.value,
-         `difference` = estimate) %>%
-  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. ") %>%
-  print(sanitize.rownames.function = function(x) x)
+         `difference` = estimate,
+         `plant species` = recipient, 
+         `community` = site_name) %>%
+  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
+Tests were performed at the community level.
+Only species present in more than one community are shown.") %>%
+  print(sanitize.text.function = function(x) x)
 ```

### 2018-02-20 functions/models.R
Change variable names in model to ease visualisation

@@ -1,6 +1,9 @@
 model_conspecific_self <- function(x){
-  glm(pollen_density ~ recipient * site_name, 
-             data = x, 
+  x %>%
+    rename(species = recipient, 
+           community = site_name) %>%
+    glm(pollen_density ~ species * community, 
+             data = ., 
              subset = treatment == 'closed', 
              family = 'quasipoisson')
 }

### 2018-02-20 publication/manuscript.Rmd
Include significance testing in the manuscript

--- 2018-02-19 publication/manuscript.Rmd
@@
         booktabs = TRUE)
+library(broom)
 ```
@@
 
+First, we explored wether animal pollination resulted in a quantitative increase in the pollination service.
+To do that, we compared the conspecific pollen density on flower stigmas of flowers that were open to animal pollination and that of flowers that were bagged, where only self-pollination ocurred.
+We performed this comparisons using a non parametric Wilcoxon test both at the species level and at the community level.
+
 ## Results
+
+```{r}
+loadd(significant_gain_global, significant_gain_site)
+
+sgg <- glance_table(significant_gain_global)
+prop_sig_global <- sum(sgg$p.value < 0.05) /
+  length(significant_gain_global)
+sgs <- glance_table(significant_gain_site)
+prop_sig_site <- sum(sgs$p.value < 0.05) /
+  length(significant_gain_site)
+
+consistency <- inner_join(sgg, sgs, by = 'recipient') %>% 
+  mutate_at(.vars = c('p.value.x', 'p.value.y'), 
+            .funs = function(x) x < 0.05) %>%
+  mutate(consistent = p.value.x == p.value.y) %>%
+  group_by(recipient) %>%
+  summarise(p.value.x = mean(p.value.x), 
+            consistent = all(consistent),
+            n_sites = n_distinct(site_name)) %>% 
+  filter(n_sites > 1)
+prop_consistency <- sum(consistency$consistent)/
+  nrow(consistency)
+```
+
+Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table S1).
+When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table S2; Figure S1 and S2).
+Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table S3).
 

### 2018-02-21 publication/supp_info.Rmd
Fix plot legends and labels

@@
 library(tidyr)
+library(stringr)
 ```
@@
 
-```{r plot conspecific per site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different sites."}
+```{r plot conspecific per site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities.
+Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
 loadd(dep_frame, sites)
@@
 
-```{r plot conspecific per plant, fig.height = 7, fig.cap="Conspecific pollen density across sites for different study species. Only species present in more than onse site are shown."}
+```{r plot conspecific per plant, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species.
+Only species present in more than onse site are shown.
+Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio; A, and R indicate that the community corresponded to an agricultural or reserve site respectively."}
 loadd(dep_frame, sites)
@@
   group_by(recipient) %>%
-  mutate(n_sites = n_distinct(site_name)) %>%
+  mutate(n_sites = n_distinct(site_name), 
+         site_name = `str_sub<-`(site_name, 1, 3, ''), 
+         site_name = str_replace_all(site_name, '_', ' - ')) %>%
   group_by() %>%

### 2018-02-22 publication/supp_info.Rmd
Calculate abundances and phenology overlap

@@
 ```
+
+```{r abundance logtransformed or not, fig.height = 3, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
+loadd(plant_rel_abu, sites)
+
+p1 <- plant_rel_abu %>%
+  inner_join(sites, by = 'site_name') %>%
+  ggplot() +
+  stat_density(aes(x = abu_com_rel_log, colour = locality_name),
+               position = position_identity(), geom = 'line') +
+  # stat_density(aes(x = abu_tot_rel_log), geom = 'line') +
+  scale_color_brewer(palette = "Set1") +
+  pub_theme() +
+  # guides(colour = guide_legend(title = 'locality'), linetype = guide_legend(title = 'land use')) +
+  labs(colour = 'locality', x = 'relative abundance')
+
+p2 <- plant_rel_abu %>%
+  inner_join(sites, by = 'site_name') %>%
+  ggplot(aes(x = abu_tot)) +
+  stat_density(position = position_identity(), geom = 'line') +
+  scale_color_brewer(palette = "Set1") +
+  pub_theme() +
+  labs(x = 'abundance (floral units)')
+
+cowplot::plot_grid(p2, p1, rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
+
+```

### 2018-02-22 main.R

@@ -11,6 +11,9 @@ library(magrittr)
 library(knitr)
 library(rmarkdown)
 library(xtable)
+library(spaa)
+library(purrr)
+library(tidyr)
 
 # load functions
 functions_folder <- './functions'
@@ -31,6 +34,8 @@ clean_data <- drake_plan(
 format_data <- drake_plan(
   dep_frame = extract_dep_frame(armonised_data),
   abu_frame = extract_abu_frame(armonised_data),
+  plant_rel_abu = calculate_relative_abundance(abu_frame),
+  plant_pheno_overlap = calculate_phenology_overlap(abu_frame),
   # control_dep_plant = extract_closed_treatment_means(dep_frame, c("season", "site_name", "plant")),
   # control_dep_site = extract_closed_treatment_means(dep_frame, c("season", "site_name")),
   # control_dep_global = extract_closed_treatment_means(dep_frame, NULL), 

### 2018-02-22 publication/manuscript.Rmd
Enable cross referencing accross tex files
This one took a while...

@@
 csl: ecology-letters.csl
-output: pdf_document
+output: 
+  bookdown::pdf_document2: 
+    keep_tex: yes
+    number_sections: false
+toc: false
 header-includes:
@@
   - \usepackage{setspace}
+  - \usepackage{xr}
+  - \externaldocument{supp_info}
 ---
@@
 
-Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table S1).
-When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table S2; Figure S1 and S2).
-Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table S3).
+Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table \@ref(tab:table-species-gain-global)).
+When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(tab:table-species-gain-site); Figure \@ref(fig:fig-conspecific-per-site) and \@ref(fig:fig-conspecific-per-plant)).
+Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table \@ref(tab:table-variation-across-sites)).
 

### 2018-02-22 publication/supp_info.Rmd
Enable cross referencing accross tex files
This one took a while...

@@
 author: "Fernando Cagua"
-output: pdf_document
+output: 
+  bookdown::pdf_document2: 
+    keep_tex: yes
+    toc: false
 header-includes:
@@
 
-```{r table species gain global, results = 'asis'}
+```{r table-species-gain-global, results = 'asis'}
 loadd(significant_gain_global, significant_gain_site, sites)
@@
          `plant species` = recipient) %>%
-  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
+  xtable(caption = "\\label{tab:table-species-gain-global} Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
 Tests were performed at the species level (across communities).") %>%
@@
 
-```{r table species gain site, results = 'asis'}
+```{r table-species-gain-site, results = 'asis'}
 loadd(significant_gain_global, significant_gain_site, sites)
@@
 Tests were performed at the community level.
-Only species present in more than one community are shown.") %>%
+Only species present in more than one community are shown.",
+         label= "tab:table-species-gain-site") %>%
   print(sanitize.text.function = function(x) x)
@@
 
-```{r variation across sites, results='asis'}
+```{r table-variation-across-sites, results='asis'}
 loadd(consp_self)
@@
 Density were modelled using a quasipoisson distribution.
-The model suggests that self-pollination rates are species dependent but not across.')
+The model suggests that self-pollination rates are species dependent but not across.',
+         label = 'tab:table-variation-across-sites')
 ```
 
-```{r plot conspecific per site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities.
+```{r fig-conspecific-per-site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities.
 Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
@@
 
-```{r plot conspecific per plant, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species.
+```{r fig-conspecific-per-plant, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species.
 Only species present in more than onse site are shown.
@@
   mutate(n_sites = n_distinct(site_name), 
-         site_name = `str_sub<-`(site_name, 1, 3, ''), 
+         site_name = `str_sub<-`(site_name, 1, 3, value = ''), 
          site_name = str_replace_all(site_name, '_', ' - ')) %>%
@@
 
-```{r abundance logtransformed or not, fig.height = 3, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
+```{r fig-abundance-logtransformed-or-not, fig.height = 3, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
 loadd(plant_rel_abu, sites)

### 2018-02-22 main.R

@@ -14,6 +14,8 @@ library(xtable)
 library(spaa)
 library(purrr)
 library(tidyr)
+library(bookdown)
+library(tinytex)
 
 # load functions
 functions_folder <- './functions'
@@ -49,9 +51,12 @@ analysing <- drake_plan(
   strings_in_dots = 'literals'
 )
 
+
 reporting <- drake_plan(
-  'publication/supp_info.pdf' = render('publication/supp_info.Rmd', quiet = TRUE),
-  'publication/manuscript.pdf' = render('publication/manuscript.Rmd', quiet = TRUE),
+  'publication/supp_info.tex' = render('publication/supp_info.Rmd', quiet = TRUE),
+  'publication/supp_info.pdf' = latexmk('publication/supp_info.tex', clean = FALSE),
+  'publication/manuscript.tex' = render('publication/manuscript.Rmd', quiet = TRUE),
+  'publication/manuscript.pdf' = latexmk('publication/manuscript.tex', clean = FALSE),
   file_targets = TRUE
 )
 

### 2018-02-23 publication/manuscript.Rmd
Move packages from reports to main script

@@
         booktabs = TRUE)
-library(broom) 
 ```

### 2018-02-23 publication/supp_info.Rmd
Move packages from reports to main script

@@
         booktabs = TRUE)
-library(drake)
-library(ggplot2)
-library(xtable)
-library(tidyr)
-library(stringr)
 ```

### 2018-02-23 main.R

@@ -11,11 +11,13 @@ library(magrittr)
 library(knitr)
 library(rmarkdown)
 library(xtable)
-library(spaa)
+library(spaa)  # niche overlap
 library(purrr)
 library(tidyr)
-library(bookdown)
+library(bookdown)  # figure and table references in reports
 library(tinytex)
+library(ggplot2)
+library(broom) 
 
 # load functions
 functions_folder <- './functions'

### 2018-02-23 publication/manuscript.Rmd
Minor changes to data collection methods

@@
 
-We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas (Figure 1). 
+We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas (Figure XX). 
 The sampling locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and an drier as we move inland and westward towards the Pampean Grasslands.
@@
 A quarter of these buds were bagged to prevent animal pollination. 
-Two days after inflorecense, we analysed the pollen grains in the flowers' pistils and classified it between conspecific and heterospecific pollen.
+Two days after inflorecense, we analysed the pollen grains in the flowers' pistils and classified them between conspecific and heterospecific pollen.
 
-The reader can find more details about the study sites, the data collection, and laboratory protocols in Marrero *et al.* (2014, 2016, and 2017)\footnote{
+More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014, 2016, and 2017)\footnote{
 This paper is almost entirely based on data that has already been published in separate units in Marrero et al. 2014, 2016, and 2017. 
@@
 
-```{r}
+```{r  differences-in-self-pollination}
 loadd(significant_gain_global, significant_gain_site)

### 2018-02-23 publication/manuscript.Rmd
Initial description of models and approach

@@
 First, we explored wether animal pollination resulted in a quantitative increase in the pollination service.
-To do that, we compared the conspecific pollen density on flower stigmas of flowers that were open to animal pollination and that of flowers that were bagged, where only self-pollination ocurred.
-We performed this comparisons using a non parametric Wilcoxon test both at the species level and at the community level.
+To do that, we compared the amount of conspecific pollen on stigmas from flowers open to animal pollination and that from flowers that were bagged, where only autogamus self-pollination ocurred.
+The difference between these two counts is not directly equivalent to the pollen deposited by animals because self-pollination is an adaptive trait [@Kalisz2003]. 
+Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output.
+We performed this comparisons using a set of non parametric Wilcoxon tests both at the community and the the species level (grouping species across communities).
+
+We then examined the extent to which the pollination service was influenced by the number of pollination partners while accounting for other metrics that describe the plant's pollination niche and community composition.
+To do so, we fitted two sets of generalised linear models (GLM) with deposited pollen density (pollen count per stigma) as the response variable. 
+The first model focused on the conspecific pollen deposited on stigmas while the second model focused on the heterospecific pollen. 
+In this approach, the coefficients of both models as well as their relationship, provide an indication of the quantity and the quality of animal pollination as well as the trade-off between these two.
+
+In both models we expect animal pollination to be
 
@@
 
+Relative small difference between conspecific animal and self pollination is conservative because crossing is better than cloning ()
+
 ## References

### 2018-02-23 publication/supp_info.Rmd
Make abundance plot smaller

@@
 
-```{r fig-abundance-logtransformed-or-not, fig.height = 3, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
+```{r fig-abundance-logtransformed-or-not, fig.height = 2.5, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
 loadd(plant_rel_abu, sites)

### 2018-02-23 publication/supp_info.Rmd
Improve plot legends

@@
   mutate(recipient_short = shorten_sp_name(recipient)) %>%
+  mutate(pollen_category = paste(pollen_category, "pollen"), 
+         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>% 
   plyr::dlply('site_name', function(x){
@@
   mutate(recipient_short = shorten_sp_name(recipient)) %>%
+  mutate(pollen_category = paste(pollen_category, "pollen"), 
+         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>%
   group_by(recipient) %>%

### 2018-02-23 publication/supp_info.Rmd
Plot of deposition

@@
 
+```{r fig-deposition-logtransformed-or-not, fig.height = 2.5, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown)."}
+loadd(dep_frame, sites)
+
+p1 <- dep_frame %>%
+  mutate(pollen_category = paste(pollen_category, "pollen"), 
+         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>%
+  ggplot(aes(x = pollen_density, colour = treatment)) + 
+  stat_density(geom = "line") +
+  facet_wrap( ~ pollen_category, scales = "free") +
+  pub_theme() +
+  scale_color_brewer(palette = "Blues") +
+  labs(x = "pollen density (grains per stigma)", 
+       colour = "flower treatment") +
+  theme(legend.position = "top")
+
+p2 <- p1 +
+  scale_x_log10()
+
+leg <- cowplot::get_legend(p1)
+
+cowplot::plot_grid(remove_legend(p1), remove_legend(p2), 
+                   labels = LETTERS[1:2], 
+                   label_size = 8) %>%
+  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
+```
+
 ```{r fig-abundance-logtransformed-or-not, fig.height = 2.5, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}

### 2018-02-23 publication/supp_info.Rmd
Change color pallete to Set1

@@
       ylab('pollen density') +
-      scale_fill_brewer(palette = "Greys")
+      scale_fill_brewer(palette = "Blues")
   })
@@
   # stat_density(aes(x = abu_tot_rel_log), geom = 'line') +
-  scale_color_brewer(palette = "Set1") +
+  scale_color_brewer(palette = "Blues") +
   pub_theme() +
@@
   stat_density(position = position_identity(), geom = 'line') +
-  scale_color_brewer(palette = "Set1") +
+  scale_color_brewer(palette = "Blues") +
   pub_theme() +

### 2018-02-25 publication/supp_info.Rmd
Adapt plot to tidy frames

@@
 p1 <- plant_rel_abu %>%
+  filter(scale == 'community', 
+         var_trans == 'log') %>%
   inner_join(sites, by = 'site_name') %>%
   ggplot() +
-  stat_density(aes(x = abu_com_rel_log, colour = locality_name),
+  stat_density(aes(x = rab, colour = locality_name),
                position = position_identity(), geom = 'line') +
@@
 p2 <- plant_rel_abu %>%
+  filter(scale == 'global', 
+         var_trans == 'log') %>%
+  distinct() %>%
   inner_join(sites, by = 'site_name') %>%
-  ggplot(aes(x = abu_tot)) +
+  ggplot(aes(x = abu)) +
   stat_density(position = position_identity(), geom = 'line') +

### 2018-02-25 main.R
Gather models twice one with tidy and other with glance

@@ -47,7 +47,7 @@ format_data <- drake_plan(
   strings_in_dots = 'literals'
 )
 
-n_replicates <- 3
+n_replicates <- 100
 transformation <- function(x) log(x + 1)
 
 boot_replicates <- drake_plan(
@@ -60,9 +60,15 @@ boot_replicates <- drake_plan(
 ) %>%
   evaluate_plan(rules = list(N = 1:n_replicates)) 
 
-gather_replicates <- boot_replicates %>%
+glance_replicates <- boot_replicates %>%
   filter(grepl("mod", target)) %>%
-  gather_plan(., gather = "tidy_glance")
+  gather_plan(., gather = "glance_models", target = "glanced_models")
+
+tidy_replicates <- boot_replicates %>%
+  filter(grepl("mod", target)) %>%
+  gather_plan(., gather = "tidy_models", target = "tidied_models")
+
+
 
 analysing <- drake_plan(
   consp_self = model_conspecific_self(dep_frame),
@@ -81,10 +87,12 @@ reporting <- drake_plan(
 
 # set up plan
 project_plan <- rbind(clean_data, format_data,
-                      boot_replicates, gather_replicates,
+                      boot_replicates, 
+                      glance_replicates,
+                      tidy_replicates,
                       analysing, reporting)
 project_config <- drake_config(project_plan)
 
 # execute plan
 make(project_plan)
-vis_drake_graph(project_config, split_columns = F, targets_only = T)
+vis_drake_graph(project_config, split_columns = T, targets_only = T)

### 2018-02-25 publication/manuscript.Rmd
Plot of coefficient estimations

@@
 
+```{r model-results, fig.height = 2.5, fig.cap = "Model coefficients"}
+loadd(tidied_models)
+
+tidied_models %>%
+  filter(term != "(Intercept)", 
+         var_trans == 'log') %>%
+  group_by(pollen_category,scale, model, term) %>%
+  summarise(estimate = first(estimate)) %>%
+  ggplot(aes(x = estimate, 
+             colour = pollen_category, 
+             fill = pollen_category)) +
+  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
+  geom_freqpoly(geom = 'area',
+               # alpha = 0.25,
+               position = position_identity(),
+               draw_quantiles = c(0.5, 0.95, 0.05), 
+               trim = F, 
+               scale = "count",
+               bins = 15) +
+  pub_theme() +
+  facet_grid(scale ~ term, scales = "free_x") +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1")
+```
+
 ## Discussion

### 2018-02-25 publication/manuscript.Rmd
Include all model iterations

--- 2018-02-23 publication/manuscript.Rmd
@@
 
+```{r model-results, fig.height = 3, fig.cap = "Model coefficients"}
+loadd(tidied_models)
+
+tidied_models %>%
+  filter(term != "(Intercept)" #, 
+         # var_trans == 'log'
+         ) %>%
+  group_by(pollen_category,scale, model, var_trans, term) %>%
+  summarise(estimate = first(estimate)) %>%
+  ggplot(aes(x = estimate, 
+             colour = pollen_category, 
+             fill = pollen_category)) +
+  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
+  geom_freqpoly(geom = 'area',
+               # alpha = 0.25,
+               position = position_identity(),
+               draw_quantiles = c(0.5, 0.95, 0.05), 
+               trim = F, 
+               scale = "count",
+               bins = 15) +
+  pub_theme() +
+  facet_grid(scale ~ term + var_trans, scales = "free_x") +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```
+
 ## Discussion

### 2018-02-27 publication/manuscript.Rmd
Compare models global vs community

@@
 Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table \@ref(tab:table-variation-across-sites)). 
+When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better predicted by the community level models, while the gain in heterospecific pollen was better predicted by the study-wide models (Table \@ref(S-tab:table-global-vs-community-models).
 

### 2018-02-27 publication/supp_info.Rmd
Compare models global vs community

@@
 cowplot::plot_grid(p2, p1, rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
+```{r table-global-vs-community-models, results = 'asis'}
+loadd(wilcox_glo_com)
 
+wilcox_glo_com %>%
+  filter(quality %in% c("rmse", "sigma"), 
+         var_trans == "log") %>%
+  select(quality, pollen_category, min_scale, estimate, p.value) %>%
+  rename(`model metric` = quality,
+         `pollen type` = pollen_category, 
+         `best model set` = min_scale,
+         `shift estimate` = estimate, 
+         `p value` = p.value) %>%
+  xtable(digits = -1, caption = "Results of two sample paired Wilcoxon signed rank test comparing the root mean square error and the residual standard deviation of the model sets constructed using predictors computed at the community or study level.",
+         label = "tab:table-global-vs-community-models")
 ```

### 2018-02-27 functions/compare_models.R

@@ -1,0 +1,27 @@
+#' Determine wether global looks better than community level
+#'
+#' @param glanced_models_table glanced_XXX
+#'
+#' @return a data frame with wilcoxong comparisons
+#' 
+global_vs_community <- function(glanced_models_table){
+  
+  test_table <- function(x){
+    glanced_models_table %>%
+      rename_at(x, function(x) "metric") %>%
+      select(pollen_category, model, scale, var_trans, metric) %>% 
+      spread(scale, metric) %>%
+      split(list(.$pollen_category, .$var_trans)) %>%
+      map(~ wilcox.test(.$community, .$global, paired = T, conf.int = T, alternative = "two.sided")) %>%
+      map_df(~ tidy(.), .id = "m") %>%
+      separate(m, c("pollen_category", "var_trans"))
+  }
+  
+  list(rmse = "rmse", sigma = "sigma", r2 = "r2", o2 = "o2", r2c = "r2c") %>%
+    map_df(~test_table(.), .id = "quality") %>%
+    mutate(min_scale = if_else(estimate < 0, "community", "global"))
+}
+
+best_random_effects <- function(x){
+  
+}

### 2018-02-27 main.R

@@ -91,6 +91,8 @@ models <- rbind(
   fixed_models, glanced_fixed_models, tidied_fixed_models
 )
 
+model_summaries <- drake_plan(
+  wilcox_glo_com = global_vs_community(glanced_fixed)
 )
 
 reporting <- drake_plan(

### 2018-02-27 publication/manuscript.Rmd
Add prefix for references to the supplementary info

@@
 ---
-title: "Pollen competition"
+title: "The pollination trade-off"
 author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
@@
   - \usepackage{xr}
-  - \externaldocument{supp_info}
+  - \externaldocument[S-]{supp_info}
 ---
@@
 Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output.
-We performed this comparisons using a set of non parametric Wilcoxon tests both at the community and the the species level (grouping species across communities).
+We performed this comparisons using a set of non parametric Mann-Whitney tests both at the community and the the species level (grouping species across communities).
 
-We then examined the extent to which the pollination service was influenced by the number of pollination partners while accounting for other metrics that describe the plant's pollination niche and community composition.
-To do so, we fitted two sets of generalised linear models (GLM) with deposited pollen density (pollen count per stigma) as the response variable. 
-The first model focused on the conspecific pollen deposited on stigmas while the second model focused on the heterospecific pollen. 
-In this approach, the coefficients of both models as well as their relationship, provide an indication of the quantity and the quality of animal pollination as well as the trade-off between these two.
+Our main aim was to examine the extent to which the pollination service was influenced by the number of pollination partners while accounting for other metrics that describe the plant's pollination niche and community composition.
+To do so, we fitted two sets of linear mixed models (R package `nlme 3.1-131`, @nlme2017] focusing on conspecific and heterospecific pollen respectively. 
+In both models, our response variable was the difference between pollen density (pollen counts per stigma) in open and bagged flowers. 
+The coefficients obtained in both sets as well as their relationship, provide an indication of the quantity and the quality of animal pollination as well as the trade-off between these two.
 
-In both models we expect animal pollination to be
+Each set was comprised by models of one twhousand bootstrap resampled replicates of the depositoin data. 
+We used bootstrap replicates because, as open and bagged flowers were not paired, this allowed us to model the *gain* in pollen density rather than density itself. 
+This strategy, not only simplified the model specification and intepretation, but also allowed us to easily evaluate the uncertainity of the model effects. 
+In each replicate we randomly sampled a number of open flowers within each community-species combination and an equal number of closed flowers. 
+We then log-transformed densities to improve normality of the data and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-logtransformed-or-not) and \@ref(S-fig:fig-deposition-gain-logtransformed-or-not)).
+Finally, we calculated the difference between the pollen density among treatmemts. 
+This difference was the response variable in all our models. 
+As predictors, we included the species/degree (number of animal partners), the plants' relative abundance and the temporal niche overlap [others variables will be added]. 
+To calculate the plant's relative abbundance we simply aggregated the flower counts in a community over the study period. 
+As with the deposition data, we found that log-transforming the abundance counts drastically improved normality (Figure \@ref(S-fig:fig-abundance-logtransformed-or-not)).
+We then the log-transformed abundance counts for each month between November 2010 and March 2011 to calculate the temporal niche overlap between plants. 
+Specifically, we used the Pianka's niche overlap index [@Pianka1973; `spaa 0.2.2` R package @Zhang2016] which calculates an overlap index for each pair of species in the community. 
+To calculate an overlap metric per species, we simply averaged the pairwise indices for a species. 
+To faciliate comparison across model estimates, we scaled all independent variables to have a mean of zero and a standard deviation of one. 
+In both set of models we evaluated a set of random effects which included plant species, community, wether the site was in an agricultural or restored fragment, and the locality. 
+We selected the best random structure by comparing the Akaike Information Criterion (AIC) of evaluated models fitted using restricted maximum likelyhood.
+
+Aditionally, we repeated the procedure but instead of calculating the independent variables for each plant species at the community level, we did so across sites. 
+This served two purposes. 
+First, and most importantly, it allowed us to examine wether indeed community level information is necessary to explain the observed patterms or whether less granular data is sufficient. 
+Second, it had the added benefit that it allowed us to include some species for which not all data necessary to calculate the independent variables was available at the community level. 
+We assessed
 
@@
 
-Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table \@ref(tab:table-species-gain-global)).
-When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(tab:table-species-gain-site); Figure \@ref(fig:fig-conspecific-per-site) and \@ref(fig:fig-conspecific-per-plant)).
-Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table \@ref(tab:table-variation-across-sites)). 
+Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
+When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(S-tab:table-species-gain-site); Figure \@ref(S-fig:fig-conspecific-per-site) and \@ref(S-fig:fig-conspecific-per-plant)).
+Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table \@ref(S-tab:table-variation-across-sites)).
+
+We found that the random structure that was best supported the data was consistently the one that included plant species grouped in communities as random effect (Table \@ref(S-tab:table-aic-random-models)).
 When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better predicted by the community level models, while the gain in heterospecific pollen was better predicted by the study-wide models (Table \@ref(S-tab:table-global-vs-community-models).

### 2018-02-27 publication/manuscript.Rmd
Remove reference to map
Improve figure

@@
 
-We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas (Figure XX). 
+We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas. 
 The sampling locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and an drier as we move inland and westward towards the Pampean Grasslands.
@@
 
-```{r model-results, fig.height = 3, fig.cap = "Model coefficients"}
-loadd(tidied_models)
+```{r fig-model-results, fig.height = 3, fig.width = 3.4, fig.cap = "Model coefficients"}
+loadd(tidied_fixed, sites)
 
-tidied_models %>%
-  filter(term != "(Intercept)" #, 
-         # var_trans == 'log'
+tidied_fixed %>%
+  filter(term != "(Intercept)" , 
+         var_trans == 'log', 
+         scale == "community"
          ) %>%
@@
   summarise(estimate = first(estimate)) %>%
+  group_by() %>%
+  humanize() %>%
   ggplot(aes(x = estimate, 
@@
   pub_theme() +
-  facet_grid(scale ~ term + var_trans, scales = "free_x") +
+  facet_wrap( ~ term, scales = "free_x", ncol = 1) +
   scale_color_brewer(palette = "Set1") +

### 2018-02-27 publication/manuscript.Rmd
Add questions and observations to manuscript

@@
 ```
+
+## Questions & Observations
+
+* Is there a better way to obtain a plant metric of temporal overlap? --- *Will use decomposition and distance metrics for this instead of the Pianka method*
+* Results shown here use `r n_distinct(readd(glanced_random)$model)` bootstrap replicates. Will scale up to 1000 models once methods are nailed down. 
+* Should I include the analysis of global models at all?
 

### 2018-02-27 publication/supp_info.Rmd
Move figures and tables arround to match order of manuscript references

@@
 ---
-title: "Supplementary materials"
-author: "Fernando Cagua"
+title: "The pollination trade-off"
+subtitle: "Supplementary materials"
+author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
+documentclass: book
 output: 
@@
         booktabs = TRUE)
+```
+
+```{r fig-deposition-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown)."}
+loadd(dep_frame, sites)
+
+p1 <- dep_frame %>%
+  mutate(pollen_category = paste(pollen_category, "pollen"), 
+         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>%
+  ggplot(aes(x = pollen_density, colour = treatment)) + 
+  stat_density(geom = "line") +
+  facet_wrap( ~ pollen_category, scales = "free") +
+  pub_theme() +
+  scale_color_brewer(palette = "Set1") +
+  labs(x = "pollen density (grains per stigma)", 
+       colour = "flower treatment") +
+  theme(legend.position = "top")
+
+p2 <- p1 +
+  scale_x_log10()
+
+leg <- cowplot::get_legend(p1)
+
+cowplot::plot_grid(remove_legend(p1), remove_legend(p2), 
+                   labels = LETTERS[1:2], 
+                   label_size = 8) %>%
+  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
+```
+
+```{r fig-deposition-gain-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of the difference on stigmatic pollen density between open and closed flowers for one of the bootstrap replicates used in the model sets.
+When (A) using directly the gain in pollen density and (B) when pollen density is log transormed prior to calculating the gain.
+"}
+loadd(rep_1)
+
+plot_dist <- function(fun){
+    rep_1 %>%
+      filter(scale == 'global', 
+             var_trans == 'lin') %>%
+      mutate_at(c('open', 'closed'), fun) %>% 
+      ggplot(aes(x = open - closed, colour = pollen_category)) +
+      stat_density(position = position_identity(), geom = "line") +
+      pub_theme() +
+      scale_color_brewer(palette = "Set1") +
+    theme(legend.position = "top") + 
+    labs(x = "gain in pollen density (open-closed)", 
+         colour = "pollen type")
+}
+
+p <- list(function(x) exp(x)-1, I) %>%
+  plyr::llply(plot_dist)
+
+leg <- cowplot::get_legend(p[[1]])
+cowplot::plot_grid(remove_legend(p[[1]]), remove_legend(p[[2]]), 
+                   labels = LETTERS[1:2], 
+                   label_size = 8,
+                   ncol = 2) %>%
+  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
+```
+
+```{r fig-abundance-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
+loadd(plant_rel_abu, sites)
+
+p1 <- plant_rel_abu %>%
+  filter(scale == 'community', 
+         var_trans == 'log') %>%
+  inner_join(sites, by = 'site_name') %>%
+  ggplot() +
+  stat_density(aes(x = rab, colour = locality_name),
+               position = position_identity(), geom = 'line') +
+  # stat_density(aes(x = abu_tot_rel_log), geom = 'line') +
+  scale_color_brewer(palette = "Set1") +
+  pub_theme() +
+  # guides(colour = guide_legend(title = 'locality'), linetype = guide_legend(title = 'land use')) +
+  labs(colour = 'locality', x = 'relative abundance')
+
+p2 <- plant_rel_abu %>%
+  filter(scale == 'global', 
+         var_trans == 'log') %>%
+  distinct() %>%
+  inner_join(sites, by = 'site_name') %>%
+  ggplot(aes(x = abu)) +
+  stat_density(position = position_identity(), geom = 'line') +
+  scale_color_brewer(palette = "Set1") +
+  pub_theme() +
+  labs(x = 'abundance (floral units)')
+
+cowplot::plot_grid(p2, p1, rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
 ```
@@
       ylab('pollen density') +
-      scale_fill_brewer(palette = "Blues")
+      scale_fill_brewer(palette = "Set1")
   })
@@
 
-```{r fig-deposition-logtransformed-or-not, fig.height = 2.5, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown)."}
-loadd(dep_frame, sites)
+```{r fig-model-results, fig.height = 3, fig.cap = "Model coefficients"}
+loadd(tidied_fixed)
 
-p1 <- dep_frame %>%
-  mutate(pollen_category = paste(pollen_category, "pollen"), 
-         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>%
-  ggplot(aes(x = pollen_density, colour = treatment)) + 
-  stat_density(geom = "line") +
-  facet_wrap( ~ pollen_category, scales = "free") +
+tidied_fixed %>%
+  filter(term != "(Intercept)" #, 
+         # var_trans == 'log'
+         ) %>%
+  group_by(pollen_category,scale, model, var_trans, term) %>%
+  summarise(estimate = first(estimate)) %>%
+  group_by() %>%
+  humanize() %>%
+  ggplot(aes(x = estimate, 
+             colour = pollen_category)) +
+  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
+  geom_freqpoly(# alpha = 0.25,
+               position = position_identity(),
+               draw_quantiles = c(0.5, 0.95, 0.05), 
+               trim = F, 
+               scale = "count",
+               binwidth = 0.05, 
+               geom = "line") +
   pub_theme() +
-  scale_color_brewer(palette = "Blues") +
-  labs(x = "pollen density (grains per stigma)", 
-       colour = "flower treatment") +
-  theme(legend.position = "top")
-
-p2 <- p1 +
-  scale_x_log10()
-
-leg <- cowplot::get_legend(p1)
-
-cowplot::plot_grid(remove_legend(p1), remove_legend(p2), 
-                   labels = LETTERS[1:2], 
-                   label_size = 8) %>%
-  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
+  facet_grid(scale ~ term + var_trans, scales = "free_x") +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
 ```
 
-```{r fig-abundance-logtransformed-or-not, fig.height = 2.5, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
-loadd(plant_rel_abu, sites)
+```{r fig-random-intercepts, fig.height= 3, fig.cap = "Random effect intercepts"}
+loadd(tidied_fixed, sites)
 
-p1 <- plant_rel_abu %>%
-  filter(scale == 'community', 
-         var_trans == 'log') %>%
-  inner_join(sites, by = 'site_name') %>%
-  ggplot() +
-  stat_density(aes(x = rab, colour = locality_name),
-               position = position_identity(), geom = 'line') +
-  # stat_density(aes(x = abu_tot_rel_log), geom = 'line') +
-  scale_color_brewer(palette = "Blues") +
+tidied_fixed %>%
+  separate("level", c("site_name", "plant_name"), sep = "/", remove = F) %>%
+  filter(term == "(Intercept)" ,
+         var_trans == 'log',
+         scale == "community", 
+         pollen_category == 'heterospecific'
+         ) %>%
+  humanize(sites) %>%
+  ggplot(aes(x = estimate, colour = plant_name, group = level)) +
+  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
+  geom_freqpoly(size = 0.25) +
+  facet_grid(locality_name + fragment ~ land_use) +
   pub_theme() +
-  # guides(colour = guide_legend(title = 'locality'), linetype = guide_legend(title = 'land use')) +
-  labs(colour = 'locality', x = 'relative abundance')
+  theme(legend.position = 'none')
+```
 
-p2 <- plant_rel_abu %>%
-  filter(scale == 'global', 
-         var_trans == 'log') %>%
-  distinct() %>%
-  inner_join(sites, by = 'site_name') %>%
-  ggplot(aes(x = abu)) +
-  stat_density(position = position_identity(), geom = 'line') +
-  scale_color_brewer(palette = "Blues") +
-  pub_theme() +
-  labs(x = 'abundance (floral units)')
+```{r table-aic-random-models, results= 'asis'}
+loadd(glanced_random)
 
-cowplot::plot_grid(p2, p1, rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
+summ <- glanced_random %>%
+  filter(var_trans == "log") %>%
+  group_by(pollen_category, scale, var_trans, model) %>%
+  mutate(delta_AIC = AIC - min(AIC)) %>%
+  group_by(pollen_category, scale, var_trans, random_effect) %>%
+  summarise(AIC_50 = median(delta_AIC), 
+            AIC_05 = quantile(delta_AIC, 0.05),
+            AIC_95 = quantile(delta_AIC, 0.95)) %>% 
+  mutate_if(is.numeric, round, digits = 1) %>% 
+  mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "]")) %>%
+  group_by() %>%
+  humanize() %>%
+  arrange(pollen_category, scale, random_effect) %>%
+  rename(`pollen category` = pollen_category, 
+         `random structure` = random_effect)
+
+contingency_table <- summ %>%
+  # select(-var_trans) %>%
+  ftable(row.vars = 4, col.vars = c(1, 2))
+
+contingency_table[1:nrow(summ)] <- summ$delta_AIC
+
+xtableFtable(contingency_table, method = "col.compact", 
+             caption = paste('Comparison of the different random structures we considered.
+The table shows median delta AIC values of', n_distinct(glanced_random$model), "bootsrap resamples of the data.
+The 5th and 95th percentile are shown inside square brackets.
+Communities are defined by individual fragments but ignore the hierarchical arrangement of sampling sites."),
+         label = 'tab:table-aic-random-models')
+```
+
 ```{r table-global-vs-community-models, results = 'asis'}

### 2018-02-27 publication/supp_info.Rmd
Use a data frame of random effects instead of hard coding it

@@
 ```{r table-aic-random-models, results= 'asis'}
-loadd(glanced_random)
+loadd(glanced_random, random_effects)
 
@@
   group_by() %>%
-  humanize() %>%
-  arrange(pollen_category, scale, random_effect) %>%
+  humanize(random_effects = random_effects) %>%
+  arrange(pollen_category, scale, random_name) %>%
   rename(`pollen category` = pollen_category, 
-         `random structure` = random_effect)
+         `random structure` = random_name)
 
@@
   # select(-var_trans) %>%
-  ftable(row.vars = 4, col.vars = c(1, 2))
+  ftable(row.vars = 10, col.vars = c(1, 2))
 

### 2018-02-27 functions/bootstraping.R

@@ -68,18 +68,11 @@ get_deposition_sampled_data <- function(x, category, transformation){
 #'
 #' @return a list of models
 #' 
-run_random_models <- function(d, method = "REML"){
-  
-  random_effects <- list(
-    c("plant", "~ 1 | plant_name"), 
-    c("plantINlocality",  "~ 1 | locality / plant_name"), 
-    c("plantINlanduse", "~ 1 | locality / land_use / plant_name"),
-    c("plantINfragment", "~ 1 | locality / land_use / fragment / plant_name"),
-    c("plantINcommunity", "~ 1 | site_name / plant_name")
-  )
+run_random_models <- function(d, random_effects, method = "REML"){
   
   rem <- random_effects %>%
-    map_df(~ mutate(d, random_formula = .[2], random_effect = .[1])) %>% 
+    split(.$random_effect) %>%
+    map_df(~ mutate(d, random_formula = .$random_formula, random_effect = .$random_effect)) %>% 
     split(list(.$pollen_category, .$scale, .$var_trans, .$random_effect)) %>%
     map(~ try(lme(pollen_gain ~ rab + tov, random = as.formula(.$random_formula[1]), na.action = na.omit, method = method, data = .)))
 }

### 2018-02-27 functions/plotting.R

@@ -18,10 +18,8 @@ remove_legend <- function(x){
 #' @param sites 
 #'
 #' @return
-#' @export
-#'
-#' @examples
-humanize <- function(x, sites = NA){
+#' 
+humanize <- function(x, sites = NA, random_effects = NA){
   if('site_name' %in% names(x)){
     x <- inner_join(x, sites, by = 'site_name')
   }
@@ -34,14 +32,7 @@ humanize <- function(x, sites = NA){
       ))
   }
   if('random_effect' %in% names(x)){
-    x <- x %>%
-      mutate(random_effect = case_when(
-        random_effect == 'plantINcommunity' ~ '1 | comunity / plant sp.',
-        random_effect == 'plantINfragment' ~ '1 | locality / land use / fragment / plant sp.',
-        random_effect == 'plantINlanduse' ~ '1 | locality / land use / plant sp.',
-        random_effect == 'plantINlocality' ~ '1 | locality / plant sp.', 
-        TRUE ~ '1 | plant sp.'
-      ))
+    x <- inner_join(x, random_effects, by = "random_effect")
   }
   x
 }

### 2018-02-28 publication/manuscript.Rmd
Move questions and observations to the end

@@
 ```
-
-## Questions & Observations
-
-* Is there a better way to obtain a plant metric of temporal overlap? --- *Will use decomposition and distance metrics for this instead of the Pianka method*
-* Results shown here use `r n_distinct(readd(glanced_random)$model)` bootstrap replicates. Will scale up to 1000 models once methods are nailed down. 
-* Should I include the analysis of global models at all?
 
@@
 
+## Questions & Observations
+
+* Is there a better way to obtain a plant metric of temporal overlap? --- *Will use decomposition and distance metrics for this instead of the Pianka method*
+* Results shown here use `r n_distinct(readd(glanced_random)$model)` bootstrap replicates.
+Thinking about scale up to 1000 models once methods are nailed down but it doesn't seem to make much difference at all.
+* Results about whether the community and global explanatory variables are better are inconclusive.
+Different indices of model quality suggest different things.
+While RMSE and $\sigma$ suggest that the global models explain better the gain in pollen, $R^2$ and $\omega^2$ suggest the opposite.
+What is the appropiate metric?
+Needs to be one that is unsensitive to sample size.
+* Or, should I include the analysis of global models at all? Not sure it brings much to the discussion and might just make things confusing.
+* Currently there are three explanatory variables.
+I'm planning to add more but I'm currently unsure about which ones to include.
+I'm particularly interested in variables that involve the data found in pollen transfer networks and that potentially involve the abbundance of pollinators.
+I can think on many but it's easy to get carried away and want to include only variables that tell something new and have a clear rationale.
+
+## Awknoledgements
+
 ## References

### 2018-02-28 publication/manuscript.Rmd
Improve publication plot

@@
 
-```{r fig-model-results, fig.height = 3, fig.width = 3.4, fig.cap = "Model coefficients"}
+```{r fig-model-results, fig.height = 2, fig.cap = "Model coefficients"}
 loadd(tidied_fixed, sites)
@@
   geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
-  geom_freqpoly(geom = 'area',
-               # alpha = 0.25,
+  stat_density(geom = 'area',
+               alpha = 0.15,
                position = position_identity(),
@@
   pub_theme() +
-  facet_wrap( ~ term, scales = "free_x", ncol = 1) +
-  scale_color_brewer(palette = "Set1") +
-  scale_fill_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
+  facet_grid( ~ term, scales = "free_x", space = "free_x") +
+  scale_color_manual(values = two_colour_scale_values) +
+  scale_fill_manual(values = two_colour_scale_values) +
+  scale_x_continuous(breaks = seq(-2,2, by = 0.25)) + 
+  theme(legend.position = "top") +
+  labs(colour = "", fill = "")
 ```

### 2018-02-28 publication/manuscript.Rmd
Improve methods

@@
 Our main aim was to examine the extent to which the pollination service was influenced by the number of pollination partners while accounting for other metrics that describe the plant's pollination niche and community composition.
-To do so, we fitted two sets of linear mixed models (R package `nlme 3.1-131`, @nlme2017] focusing on conspecific and heterospecific pollen respectively. 
-In both models, our response variable was the difference between pollen density (pollen counts per stigma) in open and bagged flowers. 
-The coefficients obtained in both sets as well as their relationship, provide an indication of the quantity and the quality of animal pollination as well as the trade-off between these two.
+To do so, we fitted two sets of linear mixed models [using the R package `nlme 3.1-131`, @nlme2017] focusing on conspecific and heterospecific pollen respectively. 
+In both set of models, our response variable was the difference between pollen density (pollen counts per stigma) in open and bagged flowers. 
+We then used the coefficients fitted by both model sets—and the relationship between them—to provide an indication of the quantity and quality of animal pollination, and the potential trade-off between these two.
 
-Each set was comprised by models of one twhousand bootstrap resampled replicates of the depositoin data. 
-We used bootstrap replicates because, as open and bagged flowers were not paired, this allowed us to model the *gain* in pollen density rather than density itself. 
+Each model set was based on one thousand bootstrap resamples of the deposition data. 
+We used bootstrap resampling because, as open and bagged flowers were not paired, this allowed us to directly model the *gain* in pollen density rather than density itself. 
 This strategy, not only simplified the model specification and intepretation, but also allowed us to easily evaluate the uncertainity of the model effects. 
 In each replicate we randomly sampled a number of open flowers within each community-species combination and an equal number of closed flowers. 
-We then log-transformed densities to improve normality of the data and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-logtransformed-or-not) and \@ref(S-fig:fig-deposition-gain-logtransformed-or-not)).
+We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-logtransformed-or-not) and \@ref(S-fig:fig-deposition-gain-logtransformed-or-not)).
 Finally, we calculated the difference between the pollen density among treatmemts. 
 This difference was the response variable in all our models.
-As predictors, we included the species/degree (number of animal partners), the plants' relative abundance and the temporal niche overlap [others variables will be added]. 
+
+As predictors, we included the species/degree (number of animal partners) as well as other factors that could influence the trade-off. 
+Specifically, we included the plants' relative abundance and the temporal niche overlap. 
 To calculate the plant's relative abbundance we simply aggregated the flower counts in a community over the study period. 
@@
 To faciliate comparison across model estimates, we scaled all independent variables to have a mean of zero and a standard deviation of one.
-In both set of models we evaluated a set of random effects which included plant species, community, wether the site was in an agricultural or restored fragment, and the locality. 
-We selected the best random structure by comparing the Akaike Information Criterion (AIC) of evaluated models fitted using restricted maximum likelyhood.
 
-Aditionally, we repeated the procedure but instead of calculating the independent variables for each plant species at the community level, we did so across sites. 
+In both set of models we first evaluated a set of candidate random effects which included random intercepts for plant species as well as random slopes for the relationship between degree and pollen gain.
+In addition we also tested intercepts assuming that the plant species grouping was hierachically nested in either their community, the land use, and the locality. 
+We selected the best random structure by comparing the median Akaike Information Criterion (AIC) of evaluated models fitted using restricted maximum likelyhood.
+
+After determining the best random structure, we then focused on the model's fixed structure where we fitted the fixed effect coefficients using maximum likelyhood. 
+Because our purpose was to perform inter-model comparisons across multiple data resamples, we did not performed model selection. 
+Instead, in all model sets, we obtained the estimates for all the fixed effects we considered and then evaluated their relevance by examining their distribution.
+
+In addition to the two main model sets we described, we repeated the procedure but instead of calculating the independent variables for each plant species at the community level, we did so across sites.
 This served two purposes. 
@@
 Second, it had the added benefit that it allowed us to include some species for which not all data necessary to calculate the independent variables was available at the community level.
-We assessed
+
+Finally, to examine the relationship between both models we sampled from the posterior
 

### 2018-02-28 publication/manuscript.Rmd
A bit more results

@@
 Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
-When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(S-tab:table-species-gain-site); Figure \@ref(S-fig:fig-conspecific-per-site) and \@ref(S-fig:fig-conspecific-per-plant)).
+When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(S-tab:table-species-gain-site)).
 Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table \@ref(S-tab:table-variation-across-sites)).
@@
 We found that the random structure that was best supported the data was consistently the one that included plant species grouped in communities as random effect (Table \@ref(S-tab:table-aic-random-models)).
-When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better predicted by the community level models, while the gain in heterospecific pollen was better predicted by the study-wide models (Table \@ref(S-tab:table-global-vs-community-models).
+When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better predicted by the community level models, while the gain in heterospecific pollen was better predicted by the study-wide models (Table \@ref(S-tab:table-global-vs-community-models)).
+This was so despite the fact that the model predictors calculated at the community level were highly correlated to those at the study wide level (Figure \@ref(S-fig:fig-global-community-correlations)).
+
+We found evidence that indicates that the number of species a plant interacts with (the species degree) is positively correlated with the heterospecific pollen density deposited. 
+To a smaller extent, degree is also negatively correlated with the density of conspecific pollen.
 

### 2018-02-28 publication/supp_info.Rmd
Do not show deposited plant boxplots. They are ugly

@@
 
-```{r fig-conspecific-per-site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities.
+```{r fig-conspecific-per-site, eval = FALSE, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities.
 Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
@@
 
-```{r fig-conspecific-per-plant, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species.
+```{r fig-conspecific-per-plant, eval = FALSE, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species.
 Only species present in more than onse site are shown.

### 2018-02-28 publication/supp_info.Rmd
plot correlation between community and global

@@
 
+```{r fig-global-community-correlations, fig.height = 2.5, fig.cap = "Relationship between the model's independent variables calculated at the community level and at the study-wide level."}
+loadd(plant_rel_abu, plant_pheno_overlap, degree, sites)
+
+ab <- plant_rel_abu %>%
+  select(-abu) %>%
+  rename(value = rab) %>%
+  mutate(term = "rab")
+
+ph <- plant_pheno_overlap %>%
+  rename(value = tov) %>%
+  mutate(term = "tov")
+
+k <- degree %>%
+  select(-kn) %>%
+  rename(value = k) %>%
+  mutate(term = "k")
+
+bind_rows(ab, ph, k) %>%
+  filter(var_trans == "log") %>%
+  spread(scale, value) %>%
+  humanize(sites) %>%
+  ggplot(aes(x = community, y = global)) +
+  geom_smooth(method = "lm", colour = "black", size = 0.75) +
+  geom_hline(yintercept = 0, size = 0.25, linetype = 2) +
+  geom_vline(xintercept = 0, size = 0.25, linetype = 2) +
+  geom_point(shape = 21, size = 1) +
+  facet_wrap( ~ term, scales = "free") +
+  coord_equal() +
+  pub_theme()
+```
+
 ```{r fig-model-results, fig.height = 3, fig.cap = "Model coefficients"}

### 2018-02-28 publication/supp_info.Rmd
New best random effect is separated by a dot

@@
 tidied_fixed %>%
-  separate("level", c("site_name", "plant_name"), sep = "/", remove = F) %>%
+  separate("level", c("plant_name", "site_name"), sep = "\\.", remove = F) %>%
   filter(term == "(Intercept)" ,

### 2018-02-28 publication/supp_info.Rmd
Improve best random effect contingency table
This time it includes more model metrics and the sample size (n models)

@@
             AIC_05 = quantile(delta_AIC, 0.05),
-            AIC_95 = quantile(delta_AIC, 0.95)) %>% 
+            AIC_95 = quantile(delta_AIC, 0.95), 
+            n = n()) %>% 
+  group_by() %>%
+  select(-var_trans) %>%
+  right_join(expand.grid(pollen_category = unique(.$pollen_category),
+                        scale = unique(.$scale),
+                        random_effect = unique(.$random_effect))) %>% 
   mutate_if(is.numeric, round, digits = 1) %>% 
-  mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "]")) %>%
+  mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "], n = ", n), 
+         delta_AIC = if_else(grepl("NA", delta_AIC), "---", delta_AIC)) %>%
   group_by() %>%
   humanize(random_effects = random_effects) %>%
-  arrange(pollen_category, scale, random_name) %>%
+  arrange(pollen_category, random_name, scale) %>%
   rename(`pollen category` = pollen_category, 
@@
 
-contingency_table <- summ %>%
-  # select(-var_trans) %>%
-  ftable(row.vars = 10, col.vars = c(1, 2))
+contingency_table <- xtabs( ~ `random structure` + `scale` + `pollen category` , data = summ) %>% ftable()
+
+# contingency_table <- summ %>%
+  # ftable.formula(`random structure` ~ `scale` + `pollen category`)
 

### 2018-02-28 publication/supp_info.Rmd
Model comparisons with references

@@
 author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
+bibliography: references.bib
+csl: ecology-letters.csl
 documentclass: book
+nocite: | 
+  @Xu2003, @Nakagawa2013
 output: 
@@
 wilcox_glo_com %>%
-  filter(quality %in% c("rmse", "sigma"), 
+  filter(quality %in% c("rmse", "sigma", "r2c", "o2"),
          var_trans == "log") %>%
@@
          `p value` = p.value) %>% 
-  xtable(digits = -1, caption = "Results of two sample paired Wilcoxon signed rank test comparing the root mean square error and the residual standard deviation of the model sets constructed using predictors computed at the community or study level.",
+  xtable(digits = -1, caption = "Results of two sample paired Wilcoxon signed rank test comparing the root mean square error (rmse), the residual standard deviation (sigma), the conditional r-squared approximation as proposed by Nakagawa and Schielzeth (2013), and the omega-squared value as suggested by Xu (2003) of the model sets constructed using predictors computed at the community or study level.",
          label = "tab:table-global-vs-community-models")
 ```
+
+# References

### 2018-02-28 main.R
Make things serial for now

@@ -123,5 +123,5 @@ project_config <- drake_config(project_plan)
 # vis_drake_graph(project_config, split_columns = T, targets_only = T)
 
 # execute plan
-make(project_plan, parallelism = "parLapply", jobs = 4)
-# make(project_plan)
+# make(project_plan, parallelism = "parLapply", jobs = 2)
+make(project_plan)

### 2018-03-01 publication/manuscript.Rmd
Move questions and observations to its own file

@@
 
-More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014, 2016, and 2017)\footnote{
-This paper is almost entirely based on data that has already been published in separate units in Marrero et al. 2014, 2016, and 2017. 
-Marrero et al. 2014 used visitation data and determined that land uses (agricultural vs. restored) was correlated to differences on the degree of specialization and richness of plants and pollinators.
-Marrero et al.
-2016 used pollen deposition data and determined that the pollination service (both the absolute number and the proportion of conspecific pollen deposited on stigmas) is reduced in agricultural communities when compared to restored communities.
-Finally, Marrero et al. 2017 used pollen transfer networks and found that pollen diversity and pollination plant niche overlap (at the species level) is greater in agricultural communities. 
-The increase on niche overlap was attributed to be positively associated with an increased abundance of exotic plants.
-}.
+More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014, 2016, and 2017).
 
@@
 
-## Questions & Observations
-
-* Is there a better way to obtain a plant metric of temporal overlap? --- *Will use decomposition and distance metrics for this instead of the Pianka method*
-* Results shown here use `r n_distinct(readd(glanced_random)$model)` bootstrap replicates.
-Thinking about scale up to 1000 models once methods are nailed down but it doesn't seem to make much difference at all.
-* Results about whether the community and global explanatory variables are better are inconclusive.
-Different indices of model quality suggest different things.
-While RMSE and $\sigma$ suggest that the global models explain better the gain in pollen, $R^2$ and $\omega^2$ suggest the opposite.
-What is the appropiate metric?
-Needs to be one that is unsensitive to sample size.
-* Or, should I include the analysis of global models at all? Not sure it brings much to the discussion and might just make things confusing.
-* Currently there are three explanatory variables.
-I'm planning to add more but I'm currently unsure about which ones to include.
-I'm particularly interested in variables that involve the data found in pollen transfer networks and that potentially involve the abbundance of pollinators.
-I can think on many but it's easy to get carried away and want to include only variables that tell something new and have a clear rationale.
-
 ## Awknoledgements

### 2018-03-01 publication/questions_observations_todo.Rmd
Move questions and observations to its own file

---
title: "The pollination trade-off"
subtitle: "Questions & Observations"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
date: "3/1/2018"
output: 
  bookdown::pdf_document2: 
    keep_tex: no
    number_sections: false
toc: false
---

1. This paper is almost entirely based on data that has already been published in separate units in Marrero et al. 2014, 2016, and 2017. 
Marrero et al. 2014 used visitation data and determined that land uses (agricultural vs. restored) was correlated to differences on the degree of specialization and richness of plants and pollinators.
Marrero et al. 2016 used pollen deposition data and determined that the pollination service (both the absolute number and the proportion of conspecific pollen deposited on stigmas) is reduced in agricultural communities when compared to restored communities.
Finally, Marrero et al. 2017 used pollen transfer networks and found that pollen diversity and pollination plant niche overlap (at the species level) is greater in agricultural communities. 
The increase on niche overlap was attributed to be positively associated with an increased abundance of exotic plants.
2. Is there a better way to obtain a plant metric of temporal overlap? --- *Will use decomposition and distance metrics for this instead of the Pianka method*
3. Results shown here use `r n_distinct(readd(glanced_random)$model)` bootstrap replicates. Thinking about scale up to 1000 models once methods are nailed down but it doesn't seem to make much difference at all. 
4. Results about whether the community and global explanatory variables are better are inconclusive. Different indices of model quality suggest different things. While RMSE and $\sigma$ suggest that the global models explain better the gain in pollen, $R^2$ and $\omega^2$ suggest the opposite. What is the appropiate metric? Options shown in the supplementary info. At the end it needs to be a metric that is unsensitive to sample size. 
5. Or, should I include the analysis of global models at all? Not sure it brings much to the discussion and might just make things confusing.
6. Currently there are three explanatory variables. I'm planning to add more but I'm currently unsure about which ones to include. I'm particularly interested in variables that involve the data found in pollen transfer networks and that potentially involve the abbundance of pollinators. I can think on many but it's easy to get carried away and want to include only variables that tell something new and have a clear rationale. 
7. Figure \@ref(fig:fig-trade-off-predictions) needs to be improved. Right now it has estimates based on random estimations at different points, it needs to be based on different model predictions (averaging lines as opposed to points). Story won't change though.

### 2018-03-01 main.R

@@ -111,6 +111,7 @@ reporting <- drake_plan(
   'publication/supp_info.pdf' = latexmk('publication/supp_info.tex', clean = FALSE),
   'publication/manuscript.tex' = render('publication/manuscript.Rmd', quiet = TRUE),
   'publication/manuscript.pdf' = latexmk('publication/manuscript.tex', clean = FALSE),
+  'publication/questions_observations_todo.pdf' = render('publication/questions_observations_todo.Rmd', quiet = TRUE),
   file_targets = TRUE
 )
 

### 2018-03-01 publication/manuscript.Rmd
Add line numbers

@@
   - \usepackage{setspace}
+  - \usepackage{lineno}
   - \usepackage{xr}
@@
 
+\linenumbers
 \doublespacing

### 2018-03-01 publication/manuscript.Rmd
Nail down methods

@@
 Our main aim was to examine the extent to which the pollination service was influenced by the number of pollination partners while accounting for other metrics that describe the plant's pollination niche and community composition.
-To do so, we fitted two sets of linear mixed models [using the R package `nlme 3.1-131`, @nlme2017] focusing on conspecific and heterospecific pollen respectively. 
-In both set of models, our response variable was the difference between pollen density (pollen counts per stigma) in open and bagged flowers. 
-We then used the coefficients fitted by both model sets—and the relationship between them—to provide an indication of the quantity and quality of animal pollination, and the potential trade-off between these two.
+To do so, we fitted four sets of linear mixed models [using the R package `nlme 3.1-131`, @nlme2017] which differed on whether the pollen deposited was conspecific or heterospecific and on wether independent variables were calculated across communities or independently within each community.
+In all set of models, our response variable was the difference between pollen density (pollen counts per stigma) between open and bagged flowers. 
+All together the results from each model set—and the relationship between them—provide with two important pieces of information. 
+First,  they provide indication of both the quantity and quality of animal pollination, and the potential trade-off between these two. 
+Second, it allowed us to examine wether indeed community level information is necessary to explain the observed patterms or whether less granular data is sufficient.
 
-Each model set was based on one thousand bootstrap resamples of the deposition data. 
+All model sets were based on the same one hundred bootstrap resamples of the deposition data. 
 We used bootstrap resampling because, as open and bagged flowers were not paired, this allowed us to directly model the *gain* in pollen density rather than density itself. 
-This strategy, not only simplified the model specification and intepretation, but also allowed us to easily evaluate the uncertainity of the model effects. 
-In each replicate we randomly sampled a number of open flowers within each community-species combination and an equal number of closed flowers. 
+This strategy, not only simplified the model specification and intepretation, but also allowed us to easily evaluate the uncertainity of the model results.  
+In each replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
 We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-logtransformed-or-not) and \@ref(S-fig:fig-deposition-gain-logtransformed-or-not)).
@@
 Specifically, we included the plants' relative abundance and the temporal niche overlap. 
-To calculate the plant's relative abbundance we simply aggregated the flower counts in a community over the study period. 
+To calculate the plant's relative abbundance we simply aggregated the flower counts over the study period—either across communities of for each community depending on the model set. 
 As with the deposition data, we found that log-transforming the abundance counts drastically improved normality (Figure \@ref(S-fig:fig-abundance-logtransformed-or-not)).
 We then the log-transformed abundance counts for each month between November 2010 and March 2011 to calculate the temporal niche overlap between plants. 
-Specifically, we used the Pianka's niche overlap index [@Pianka1973; `spaa 0.2.2` R package @Zhang2016] which calculates an overlap index for each pair of species in the community. 
+Specifically, we used the Pianka's niche overlap index [@Pianka1973; `spaa 0.2.2` R package @Zhang2016] which calculates an overlap index for each pair of species—again, across and within  communities depending on the model set.
 To calculate an overlap metric per species, we simply averaged the pairwise indices for a species. 
@@
 
-In both set of models we first evaluated a set of candidate random effects which included random intercepts for plant species as well as random slopes for the relationship between degree and pollen gain.
-In addition we also tested intercepts assuming that the plant species grouping was hierachically nested in either their community, the land use, and the locality. 
+In all set of models we first evaluated a set of candidate random effects which included random intercepts for plant species as well as random slopes for the relationship between degree and pollen gain.
+In addition we also tested random intercepts assuming that the plant species grouping was hierachically nested in either their community, the land use, and the locality. 
 We selected the best random structure by comparing the median Akaike Information Criterion (AIC) of evaluated models fitted using restricted maximum likelyhood. 
-
 After determining the best random structure, we then focused on the model's fixed structure where we fitted the fixed effect coefficients using maximum likelyhood. 
-Because our purpose was to perform inter-model comparisons across multiple data resamples, we did not performed model selection. 
+Because our purpose was to perform inter-model comparisons across multiple data resamples, we did not perform model selection. 
 Instead, in all model sets, we obtained the estimates for all the fixed effects we considered and then evaluated their relevance by examining their distribution.
 
-In addition to the two main model sets we described, we repeated the procedure but instead of calculating the independent variables for each plant species at the community level, we did so across sites.
-This served two purposes. 
-First, and most importantly, it allowed us to examine wether indeed community level information is necessary to explain the observed patterms or whether less granular data is sufficient. 
-Second, it had the added benefit that it allowed us to include some species for which not all data necessary to calculate the independent variables was available at the community level.
+We compared the performance of the within and across communities model sets using the root-mean-square error normalised by the interquartile range (NRMSE). 
+We tested the significance of this difference using a two sample paired Wilcoxon signed rank test for conspecific and heterospecific pollen models. 
+We chosed NRMSE because it provides an easily interpretable metric related to the quality of the predictions while being farily insensitive to sample size. 
+This inensitivity was desirable because the across communities models had often slightly larger sample sizes owing to the fact of some species not having all data necessary to calculate the independent variables at the community level.
 
-Finally, to examine the relationship between both models we sampled from the posterior
+Finally, we focused on how the pollination trade-off was related to our explanatory variables. 
+To do so, we harnessed the results from the conspecific and heterospecific pollen models that performed best (across or within communities). 
+To examine the relationship between these model sets, we sampled 100 estimates from the distribution of coefficients in each set. 
+For each of the samples, we then calculated the difference between the gain in conspecific and heterospecific pollen that would be predicted assuming mean values for the random intercepts and the other predictors.
 

### 2018-03-01 publication/manuscript.Rmd
Change colour palette

@@
   facet_grid( ~ term, scales = "free_x", space = "free_x") +
-  scale_color_manual(values = two_colour_scale_values) +
-  scale_fill_manual(values = two_colour_scale_values) +
+  scale_color_manual(values = colour_scale_values) +
+  scale_fill_manual(values = colour_scale_values) +
   scale_x_continuous(breaks = seq(-2,2, by = 0.25)) + 

### 2018-03-01 publication/supp_info.Rmd
Change colour palette

@@
   pub_theme() +
-  scale_color_brewer(palette = "Set1") +
+  scale_color_manual(values = colour_scale_values) +
   labs(x = "pollen density (grains per stigma)", 
@@
       pub_theme() +
-      scale_color_brewer(palette = "Set1") +
+      scale_color_manual(values = colour_scale_values) +
     theme(legend.position = "top") + 
@@
   # stat_density(aes(x = abu_tot_rel_log), geom = 'line') +
-  scale_color_brewer(palette = "Set1") +
+  scale_color_manual(values = colour_scale_values) +
   pub_theme() +
@@
   stat_density(position = position_identity(), geom = 'line') +
-  scale_color_brewer(palette = "Set1") +
+  scale_color_manual(values = colour_scale_values) +
   pub_theme() +
@@
       ylab('pollen density') +
-      scale_fill_brewer(palette = "Set1")
+      scale_fill_manual(values = colour_scale_values)
   })

### 2018-03-01 functions/plotting.R

@@ -40,4 +40,4 @@ humanize <- function(x, sites = NA, random_effects = NA){
   x
 }
 
-two_colour_scale_values <- c("#f1a340", "#998ec3")
+colour_scale_values <- c("#d7301f", "#fdcc8a", "#fc8d59", "#fef0d9")

### 2018-03-01 publication/manuscript.Rmd
Figure with model predictions

@@
 
+```{r fig-trade-off-predictions, fig.width=3.5, fig.height= 2.5, fig.cap = "Trade off predictions"}
+loadd(trade_off_predictions)
+
+trade_off_predictions %>%
+  mutate_at(c("conspecific", "heterospecific"), exp) %>%
+  mutate(gain = conspecific / (conspecific + heterospecific)) %>%
+  filter(!(value > 2.2 & term == "k")) %>%
+  humanize() %>%
+  ggplot(aes(x = value, y = gain, colour = term)) +
+  geom_hline(yintercept = 0.5, size = 0.25, linetype = 2) + 
+  geom_point(shape = 21, alpha = 0.5, size = 1) +
+  geom_smooth(aes(fill = term), 
+              se = F, size = 0.5, method = "glm", 
+              method.args = list(family = "binomial"), alpha = 0.1)+
+  pub_theme() +
+  scale_color_manual(values = colour_scale_values) +  
+  scale_fill_manual(values = colour_scale_values) +
+  theme(legend.position = "top") +
+  labs(colour = "", fill = "", 
+       y = "scaled trade-off\nconspecific - heterospecific pollen gain", 
+       x = "scaled variable value")
+```
+
 ## Discussion
+
+This is, the data is best modelled when ignoring the hierarchical nature of the experiment (communities nested in agricultural or restored fragments nested in localities).
+Similarly, the relationship between degre and pollen gain does not seem to be species or community dependent.
 
@@
 
-## Awknoledgements
+## Awknowledgements
 

### 2018-03-01 publication/manuscript.Rmd
Results show global results

@@
 
-```{r fig-model-results, fig.height = 2, fig.cap = "Model coefficients"}
+```{r fig-model-results-global, fig.height = 2, fig.cap = "Model coefficients"}
 loadd(tidied_fixed, sites)
@@
          var_trans == 'log',
-         scale == "community"
+         scale == "global"
          ) %>%

### 2018-03-01 publication/manuscript.Rmd
Improve results

@@
 
-We found that the random structure that was best supported the data was consistently the one that included plant species grouped in communities as random effect (Table \@ref(S-tab:table-aic-random-models)).
-When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better predicted by the community level models, while the gain in heterospecific pollen was better predicted by the study-wide models (Table \@ref(S-tab:table-global-vs-community-models)).
+We found that the random structure that was best supported the data was consistently the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
+When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better approximated by the model sets using predictors calculated across communities (Table \@ref(S-tab:table-global-vs-community-models)).
 This was so despite the fact that the model predictors calculated at the community level were highly correlated to those at the study wide level (Figure \@ref(S-fig:fig-global-community-correlations)).
+Nevertheless, results from the within community models are similar both qualitatively and quantitatively (with the exception of phenology overlap, but that might change once I use a better metric, Figure \@ref(S-fig:fig-model-results)).
 
-We found evidence that indicates that the number of species a plant interacts with (the species degree) is positively correlated with the heterospecific pollen density deposited. 
+We found that the number of species a plant interacts with (the species degree) is positively correlated with the heterospecific pollen density deposited.
 To a smaller extent, degree is also negatively correlated with the density of conspecific pollen.

### 2018-03-01 publication/supp_info.Rmd
Add nrmse in supp info table

@@
 wilcox_glo_com %>%
-  filter(quality %in% c("rmse", "sigma", "r2c", "o2"),
+  filter(quality %in% c("rmse", "sigma", "r2c", "o2", "nrmse"),
          var_trans == "log") %>%
@@
          `p value` = p.value) %>% 
-  xtable(digits = -1, caption = "Results of two sample paired Wilcoxon signed rank test comparing the root mean square error (rmse), the residual standard deviation (sigma), the conditional r-squared approximation as proposed by Nakagawa and Schielzeth (2013), and the omega-squared value as suggested by Xu (2003) of the model sets constructed using predictors computed at the community or study level.",
+  xtable(digits = -1, caption = "Results of two sample paired Wilcoxon signed rank test comparing different model quality metrics of the model sets using predictors computed across or within communities.
+Metrics are the root mean square error (rmse), the residual standard deviation (sigma), the conditional r-squared approximation as proposed by Nakagawa and Schielzeth (2013), the omega-squared value as suggested by Xu (2003), and the normalised root-mean-square error of the model sets constructed using predictors computed at the community or study level.",
          label = "tab:table-global-vs-community-models")

### 2018-03-01 publication/supp_info.Rmd
adapt to new best random effect

@@
 
-```{r fig-random-intercepts, fig.height= 3, fig.cap = "Random effect intercepts"}
+```{r fig-random-intercepts, eval = F, fig.height= 3, fig.cap = "Random effect intercepts"}
 loadd(tidied_fixed, sites)
@@
 tidied_fixed %>%
-  separate("level", c("plant_name", "site_name"), sep = "\\.", remove = F) %>%
+  separate("level", c("site_name", "plant_name"), sep = "/", remove = F) %>%
   filter(term == "(Intercept)" ,

### 2018-03-01 publication/supp_info.Rmd
Improve model results figure in supp info

@@
 
-```{r fig-model-results, fig.height = 3, fig.cap = "Model coefficients"}
-loadd(tidied_fixed)
+```{r fig-model-results, fig.height = 3.5, fig.cap = "Model coefficients"}
+loadd(tidied_fixed, sites)
 
 tidied_fixed %>%
-  filter(term != "(Intercept)" #, 
-         # var_trans == 'log'
+  filter(term != "(Intercept)" , 
+         var_trans == 'log'
+         # scale == "community"
          ) %>%
@@
   ggplot(aes(x = estimate, 
-             colour = pollen_category)) +
+             colour = pollen_category, 
+             fill = pollen_category)) +
   geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
-  geom_freqpoly(# alpha = 0.25,
+  stat_density(geom = 'area',
+               alpha = 0.15,
                position = position_identity(),
@@
                scale = "count",
-               binwidth = 0.05, 
-               geom = "line") +
+               bins = 15) +
   pub_theme() +
-  facet_grid(scale ~ term + var_trans, scales = "free_x") +
-  scale_color_brewer(palette = "Set1") +
-  scale_fill_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
+  facet_grid(scale ~ term, scales = "free_x", space = "free_x") +
+  scale_color_manual(values = colour_scale_values) +
+  scale_fill_manual(values = colour_scale_values) +
+  scale_x_continuous(breaks = seq(-2,2, by = 0.25)) + 
+  theme(legend.position = "top") +
+  labs(colour = "", fill = "")
 ```

### 2018-03-01 publication/questions_observations_todo.Rmd
Double spacing

@@
 toc: false
+header-includes:
+  - \usepackage{setspace}
 ---
+
+\onehalfspacing
 

### 2018-03-01 publication/manuscript.Rmd
Minor change results

@@
 
-We found that the number of species a plant interacts with (the species degree) is positively correlated with the heterospecific pollen density deposited.
-To a smaller extent, degree is also negatively correlated with the density of conspecific pollen.
+We found that the gain in conspecific pollen is negatively affected by the plants relative abbundance and to a smaller extent by the species' degree (Figure \@ref(fig:fig-model-results-global). 
+The gain in heterospecific pollen was instead positively affected by degree and the plant's phenology overlap, but was also strongly negatively affected by the plant's relative abbundance.
 
-```{r fig-model-results-global, fig.height = 2, fig.cap = "Model coefficients"}
+```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain"}
 loadd(tidied_fixed, sites)
@@
   theme(legend.position = "top") +
-  labs(colour = "", fill = "")
+  labs(colour = "", fill = "", x = "estimated effect on pollen gain")
 ```

### 2018-03-01 publication/manuscript.Rmd
Initial introduction

@@
 ## Introduction
+
+Pollination systems play a disproportionally important role in food production and maintenance of global biodiversity. 
+In the context of animal pollination, the support to biodiversity is fundamentally achieved by virtue of intra-species facilition—the positive feedback loops that exist between plants that share pollinators or pollinators that share plants.
+Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources. 
+Indeed, studies that are fundamental to our current knowledge of mutualism predict that an upper limit to biodiversity is achieved when the number of mutualistic partners is maximised in a community. 
+And yet, fully connected natural pollination communities do not exist.
+
+This is so, because sharing a mutualistic partner also has costs. 
+The end result is that, when the cummulative costs have negative impact on fitnessis, species also start competeing for mutualistic partners. 
+For the 88% of flowering plants that rely on animal pollination, there are two mechanisms trough which competition for pollinators might arrise. 
+The first is competition for visits, where plants with more atractive flowers reduce the pollination service for those less atractive. 
+The second is interspecific pollen transfer, where even receiving a visit might not translate into net facilitation. 
+A focal plant might receive pollen from a different species, or conversely pollen from the focal plan might be lost to different species. 
+Here we focus on this second mechanism.
+
+The potential negative effects of competition for pollinators have been long recognised and widely documented. 
+It is currently clear that they have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies as well as driving ecological diferentiation. 
+Indeed there is considerable evidence demonstrating the effects that interspecific pollen transfer in two-species systems. 
+However, these competitive interactions between species pairs do not occur in isolation. 
+Instead, plants often ocurr in communities in which multiple competitive interactions operate simultaneusly and lead to emergent phenomena not observed at smaller scales.
+
+Nevertheless, only a handful of studies have examined interspecific pollen transfer at the community level, and therefore we still understand little about how compeition for pollinators operates at this scale.
+All together, the few existing studies show that, as expected, the effective result of mutualistic interactions is, in most cases, one of facilitation. 
+Importantly, they also show a large variability in this result—both across species and across communities. 
+However, the driving factors behind this variability are currently not understood.
+
+But understanding what makes species and communities different is important not only because the ecological and evolutionary implications. 
+It is also important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. 
+An important proportion of widely used theoretical models of pollination account for the negative effects of mutualisim by shaping the benefits
+
+It is generally believed that there is a trade-off between the number of mutualistic parters a plant species has, and the strength of its interactions (mutualistic benefit).
+The trade-off arises from the premise that an increase on the number of mutualistic partners might increase facilitation, but might also increase competition for pollinators because it can lead to a reduction of the proportion of conspecific pollen deposited on the stigmas.
+Species properties and the environmental context seem to influence whether sharing pollinators leads to facilitation or competition [@Tur2016a], however the specific mechanisms behind these observations are poorly understood.
+Furthermore, recent theoretical advances that explicitly include the mutualistic trade-off in pollination models have highlighted its importance.
+Indeed, it has been shown that the trade-off is related to the feasibility and stability of mutualistic communities [@Rohr2014], the species' response to change [@Saavedra2013], the onset of critical transitions [@Dakos2014a], and the spread of perturbations [@Suweis2015].
+However, The extent to which the trade-off operates in nature and its relationship with facilitation-competition dynamics has not been empirically evaluated.
+Here, we used data on the quality and quantity of pollination in six pollination communities to quantify the empirical support for the mutualistic trade-off concept and identify the mechanisms that structure it.
+Contrasting to our initial expectation, we found that the mutualistic benefit is only weakly related to the number of pollination partners.
+We found that this relationship is weak because plants with a large number of shared partners are able to reduce the cost of sharing by increasing the niche partitioning.
+Importantly, the niche partitioning strategies are modulated by plant abundance and are not homogeneously employed by all plant species.
 
@@
 
-```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain"}
+```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
+Results are shown for models with explanatory var"}
 loadd(tidied_fixed, sites)
@@
   geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
-  stat_density(geom = 'area',
-               alpha = 0.15,
+  stat_density(geom = 'line',
+               # alpha = 0.15,
                position = position_identity(),
                draw_quantiles = c(0.5, 0.95, 0.05), 
-               trim = F, 
+               trim = T, 
                scale = "count",
@@
 
-```{r fig-trade-off-predictions, fig.width=3.5, fig.height= 2.5, fig.cap = "Trade off predictions"}
-loadd(trade_off_predictions)
+The gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 
+The slope of the relationship is such that it is more likely that the gain on heterospecific pollen increases faster than the gain on conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)A).
+In addition, we found that from all the explanatory variables examined, only the plant's relative abbundance has a positive effect on the proportion of conspecific pollen gained (Figure \@ref(fig:fig-trade-off-predictions)B).
+For most of the parameter space plants obtain a larger proportion of heteropspecific than conspecific pollen. 
+However, plants can obtain a larger proportion of conspecific pollen when they have high abundance and to a smaller extent when they have a low degree.
 
-trade_off_predictions %>%
+```{r fig-trade-off-predictions, fig.height= 2.5, fig.cap = "Trade off predictions j."}
+loadd(trade_off_predictions, model_linear_fits, tidied_fixed)
+# loadd(model_correlations)
+
+# p1 <- model_correlations %>%
+#   filter(var_trans == "log", 
+#          scale == "global") %>%
+#   ggplot(aes(x = pearson_slope)) + 
+#   geom_vline(xintercept = 0.5, size = 0.25, linetype = 2) +
+#   stat_density(trim = F, geom = "line") +
+#   pub_theme() +
+#   labs(x = "slope\n(heterospecific ~ conspecific pollen gain)")
+# 
+get_pred_range <- function(x){
+  tidied_fixed %>% filter(pollen_category == x, var_trans == "log", scale == "global") %$% estimate %>% range()
+}
+
+ab_lines <- model_linear_fits %>%
+  filter(var_trans == "log",
+         scale == "global") %>%
+  spread(sma_parameter, value)
+
+p1 <- data_frame(x = get_pred_range("heterospecific"),
+                 y = get_pred_range("conspecific")) %>%
+  ggplot(aes(x, y)) +
+  geom_abline(data = ab_lines, 
+              aes(slope = slope, intercept = elevation), 
+              size = 0.1, linetype = 1, colour = "grey", 
+              alpha = 0.5) +
+  geom_abline(data = summarise_if(ab_lines, is.numeric, median), 
+              aes(slope = slope, intercept = elevation), 
+              size = 0.5, linetype = 1, colour = "black") +
+  geom_abline(slope = 1, intercept = 0, size = 0.25, linetype = 2) +
+  geom_point(alpha = 0) +
+  coord_equal(xlim = get_pred_range("heterospecific"),
+                  ylim = get_pred_range("conspecific")) +
+  pub_theme() +
+  labs(x = "gain in heterospecific pollen", y = "gain in conspecific pollen")
+
+p2 <- trade_off_predictions %>%
   mutate_at(c("conspecific", "heterospecific"), exp) %>%
@@
   scale_fill_manual(values = colour_scale_values) +
+  scale_y_continuous(labels = scales::percent) +
   theme(legend.position = "top") +
   labs(colour = "", fill = "", 
-       y = "scaled trade-off\nconspecific - heterospecific pollen gain", 
+       y = "proportion conspecific pollen gain", 
        x = "scaled variable value")
+
+cowplot::plot_grid(p1, p2, align = "h", axis = "tb", ncol = 2, labels = LETTERS[1:2], label_size = 8, rel_widths = c(0.35, 0.65))
 ```

### 2018-03-01 publication/questions_observations_todo.Rmd
Reference figures from the MS in the questions document

--- 2018-03-01 publication/questions_observations_todo.Rmd
@@
 toc: false
+header-includes:
+  - \usepackage{setspace}
+  - \usepackage{xr}
+  - \externaldocument[M-]{manuscript}
 ---
+
+\onehalfspacing
 
@@
 7.
-Figure \@ref(fig:fig-trade-off-predictions) needs to be improved.
+Figure \@ref(M-fig:fig-trade-off-predictions) needs to be improved.
 Right now it has estimates based on random estimations at different points, it needs to be based on different model predictions (averaging lines as opposed to points).

### 2018-03-02 publication/manuscript.Rmd
Continue introduction

@@
 
+TBC
+
 ## Introduction
@@
 Nevertheless, only a handful of studies have examined interspecific pollen transfer at the community level, and therefore we still understand little about how compeition for pollinators operates at this scale.
-All together, the few existing studies show that, as expected, the effective result of mutualistic interactions is, in most cases, one of facilitation. 
+All together, existing studies show that, as expected, the effective result of mutualistic interactions is, in most cases, one of facilitation. 
 Importantly, they also show a large variability in this result—both across species and across communities. 
@@
 
-But understanding what makes species and communities different is important not only because the ecological and evolutionary implications. 
+Understanding what makes species and communities different is important not only because of its ecological and evolutionary implications. 
 It is also important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. 
-An important proportion of widely used theoretical models of pollination account for the negative effects of mutualisim by shaping the benefits
+Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree.
+The extent to which species degree affects the benefit is called *mutualistic trade-off*. 
+This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
+At the same time it is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
+Although, the mutualistic trade-off has been shown to play a determining role on the stability and diversity of mutualistic communities, empirical evidence is scarce, to say the least.
 
-It is generally believed that there is a trade-off between the number of mutualistic parters a plant species has, and the strength of its interactions (mutualistic benefit).
-The trade-off arises from the premise that an increase on the number of mutualistic partners might increase facilitation, but might also increase competition for pollinators because it can lead to a reduction of the proportion of conspecific pollen deposited on the stigmas.
-Species properties and the environmental context seem to influence whether sharing pollinators leads to facilitation or competition [@Tur2016a], however the specific mechanisms behind these observations are poorly understood.
-Furthermore, recent theoretical advances that explicitly include the mutualistic trade-off in pollination models have highlighted its importance.
-Indeed, it has been shown that the trade-off is related to the feasibility and stability of mutualistic communities [@Rohr2014], the species' response to change [@Saavedra2013], the onset of critical transitions [@Dakos2014a], and the spread of perturbations [@Suweis2015].
-However, The extent to which the trade-off operates in nature and its relationship with facilitation-competition dynamics has not been empirically evaluated.
-Here, we used data on the quality and quantity of pollination in six pollination communities to quantify the empirical support for the mutualistic trade-off concept and identify the mechanisms that structure it.
-Contrasting to our initial expectation, we found that the mutualistic benefit is only weakly related to the number of pollination partners.
-We found that this relationship is weak because plants with a large number of shared partners are able to reduce the cost of sharing by increasing the niche partitioning.
-Importantly, the niche partitioning strategies are modulated by plant abundance and are not homogeneously employed by all plant species.
+Elucidating how the mechanisms and drivers of facilitation scales to the community level and its theoretical concequences has been elusive in part because of the large amounts of data required.
+Previous studies focus on the final picture of interspecific pollen transfer that is obtained by examining the pollen deposited on flower stigmas. 
+However, teasing appart the competition for pollinators also requires data that describes the structure of the interactions and the pollen flows that ocurr within it, while accounting for the traits of the species that integrate the community.
+Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas.
+Specifically, we ask first wether there is empirical support for the hipotezised relationship between the species degree and the quantity and quality of the pollination service.
 

### 2018-03-02 publication/manuscript.Rmd
Small changes to figure legends

@@
 loadd(trade_off_predictions, model_linear_fits, tidied_fixed)
-# loadd(model_correlations)
 
-# p1 <- model_correlations %>%
-#   filter(var_trans == "log", 
-#          scale == "global") %>%
-#   ggplot(aes(x = pearson_slope)) + 
-#   geom_vline(xintercept = 0.5, size = 0.25, linetype = 2) +
-#   stat_density(trim = F, geom = "line") +
-#   pub_theme() +
-#   labs(x = "slope\n(heterospecific ~ conspecific pollen gain)")
-# 
 get_pred_range <- function(x){
-  tidied_fixed %>% filter(pollen_category == x, var_trans == "log", scale == "global") %$% estimate %>% range()
+  tidied_fixed %>% 
+    filter(pollen_category == x, var_trans == "log", scale == "global") %$% 
+    estimate %>% range()
 }
@@
   pub_theme() +
-  labs(x = "gain in heterospecific pollen", y = "gain in conspecific pollen")
+  labs(x = "gain in heterospecific pollen", 
+       y = "gain in conspecific pollen")
 
@@
 
-cowplot::plot_grid(p1, p2, align = "h", axis = "tb", ncol = 2, labels = LETTERS[1:2], label_size = 8, rel_widths = c(0.35, 0.65))
+cowplot::plot_grid(p1, p2, 
+                   align = "h", axis = "tb", ncol = 2, labels = LETTERS[1:2], 
+                   label_size = 8, rel_widths = c(0.35, 0.65))
 ```
@@
 
-## Awknowledgements
-
 ## References

### 2018-03-20 publication/manuscript.Rmd
Final paragraph introduction

@@
 Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas.
-Specifically, we ask first wether there is empirical support for the hipotezised relationship between the species degree and the quantity and quality of the pollination service.
+Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
+Second, we investigate wether there is a relationship between this gain and a suite of variables that describe both the role of the plant species and the ecological context. 
+Here, we pay special attention to the role of species degree because of its ramifications to theoretical ecology. 
+At the same time, we examine wether the plant role and ecological context is best infered from dynamics occurring at the community level, or wether it can be well approximated using information available from all sites in which a species ocurr.
+Third, and finaly, we explore how plant species differ on the extent to which competition for pollinators shapes facilitation.
 

### 2018-03-20 publication/manuscript.Rmd
Trade-off methods

@@
 
-Finally, we focused on how the pollination trade-off was related to our explanatory variables. 
+Finally, we focused on how the relationship between conspecific and heterospecific pollen gain. 
+First we examined wether the pollination trade-off was related to our explanatory variables. 
 To do so, we harnessed the results from the conspecific and heterospecific pollen models that performed best (across or within communities). 
@@
 For each of the samples, we then calculated the difference between the gain in conspecific and heterospecific pollen that would be predicted assuming mean values for the random intercepts and the other predictors.
+
+Second, we calulated the the extent of facilitation. 
+For this purpose, as in @Tur2016a, we used the relationship between heterospecific and conspecific pollen. 
+We calculated an overal relationship by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair [we used the R package `smatr 3.4-3`, @Warton2012a].
+We followed a similar procedure to calculate a relationship per species but instead of fitting a SMA per model pair, we did so across the 100 models for each species independently.
 

### 2018-03-20 publication/manuscript.Rmd
Small changes to results

@@
 However, plants can obtain a larger proportion of conspecific pollen when they have high abundance and to a smaller extent when they have a low degree. 
+When examining the extent of facilitation at the species level, we found that XXX (Figure \@ref(fig:fig-trade-off-predictions)B).
 
-```{r fig-trade-off-predictions, fig.height= 2.5, fig.cap = "Trade off predictions j."}
+```{r fig-trade-off-predictions, fig.height= 2.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
+(A) Overall and species-level relationship.
+Grey lines indicate the relationship in each of the samples, the median is indicated with a black solid line.
+Dotted lines show the relationship for each species.
+Invasive species are shown in red.
+(B) The proportion of conspecific pollen relative to the total amount of pollen gained trough animal pollination and its relationship to our set of explanatory variables."}
 loadd(trade_off_predictions, model_linear_fits, tidied_fixed)
@@
   theme(legend.position = "top") +
-  labs(colour = "", fill = "", 
+  labs(colour = "", fill = "", linetype = "", 
        y = "proportion conspecific pollen gain", 

### 2018-03-20 publication/manuscript.Rmd
Bulletpoint discussion

@@
 
-This is, the data is best modelled when ignoring the hierarchical nature of the experiment (communities nested in agricultural or restored fragments nested in localities).
-Similarly, the relationship between degre and pollen gain does not seem to be species or community dependent.
-
-Relative small difference between conspecific animal and self pollination is conservative because crossing is better than cloning ()
+* We found that animal pollination only brings a small amount of extra conspecific pollen (compared to selfing) if any.
+This relatively small difference is probably very important though because crossing has been shown to be evolutionary better than cloning in the long term.
+* The relationship between conspecific and heterospecific pollen is positive which indicates than net facilitation is the dominant outcome.
+This agrees with previous findings.
+However the amount of added conspecific pollen is in average smaller than the amount of added heterospecific pollen.
+* Despite finding that facilitation is the most common outcome. We also were able to find clear signature of competition for pollinators at the community level.
+* We found that, as assumed in pollination models, the mutualistic benefit is modulated by the species degree and therefore there is indeed evidence for a trade-off.
+Moreover, the trade off does not depend on the species or the community.
+Which is a good thing because we tend to simplify models by assuming a common trade-off for the whole community.
+* However the mutualistic benefit was not just modulated by the degree but other factors also played significant roles. 
+* These factors, in particular the plant relative abundance, was important at explaining the differences between plants. 
+* We found that models performed better when explanatory variables were constructed so that they take into account information across all the communities in which a species was present.
+This means that despite the particularities of each community (random effects acounted for a large proportion of the variance) we can still predict general outcomes by knowing some general traits about the plant species and how it relates to other plants in their community.
 

### 2018-06-30 paper/questions_observations_todo.Rmd
Change folder name publication to paper

---
title: "The pollination trade-off"
subtitle: "Workng doccument - questions & observations"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
date: "3/1/2018"
output: 
  bookdown::pdf_document2: 
    keep_tex: no
    number_sections: false
toc: false
header-includes:
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
---

\onehalfspacing

## Summary of previous research using this data

This paper is almost entirely based on data that has already been published in separate units in Marrero et al. 2014, 2016, and 2017. 
Marrero et al. 2014 used visitation data and determined that land uses (agricultural vs. restored) was correlated to differences on the degree of specialization and richness of plants and pollinators.
Marrero et al. 2016 used pollen deposition data and determined that the pollination service (both the absolute number and the proportion of conspecific pollen deposited on stigmas) is reduced in agricultural communities when compared to restored communities.
Finally, Marrero et al. 2017 used pollen transfer networks and found that pollen diversity and pollination plant niche overlap (at the species level) is greater in agricultural communities. 
The increase on niche overlap was attributed to be positively associated with an increased abundance of exotic plants.

## To do

* Include more explanatory variables to the model. In particular I want to include i. visitation rates, ii. uniqueness on flower traits (as it's been hypothesized that coflowering species with similar traits facilitate each other more), iii. the overlap in the pollen transfer space (pollinator pollen loads), and maybe something related to pollinator preferences. What do you think? Should I ditch one of this, should I include more? I want to keep it as simple as possible though. 
* Calculate degree of facilitation per species and include it in Figure 2A
* References to the introduction
* Correlation between explanatory variables to make sure they are not colinear
* Nail down discussion

## Questions

* Is the framing in the introduction appropiate? Should I highlight some other things? Mute down others? I wrote it thinking about a general audience reading a multidisciplinary journal. We should be able to improve it more once we decide on potential outlets 
* Which aspects from the results you think are more noteworthy? What should I empasize in the discussion? 
* Current analyses are done using 100 randomisations. Should I scale it up to 1000? Increasing from 30 to 100 did not change things much.
* I'm not convinced about the relevance of including the "within community/across communities" dimension to the study. I'm not sure it brings much to the story at all. Perhaps is just distracting? If not I'm also dubious about the way I'm comparing model sets. I used NRMSE, which agrees with other indices like $R^2$ and $\omega^2$. Other indices like $\sigma$ and RMSE provide different results and agree with previous results that show that heterospecific pollen deposition is more related to species specific trats than to community level variables. Any suggestion? 
* Unsure about the way I'm estimating temporal overlap between plant species? Daniel suggested to use some decomposition method and similar approaches to the ones used on trait analysis and estimate indices like originality and differentiation. There are only five surveys, so few "traits" so I'm not sure the data is suitable. Plus it's a more complicated method than Pianka's.

### 2018-06-30 paper/supp_info.Rmd
Change folder name publication to paper

--- 2018-03-01 publication/supp_info.Rmd
@@
 title: "The pollination trade-off"
-subtitle: "Supplementary materials"
+subtitle: "Supplementary information"
 author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"

### 2018-06-30 main.R

@@ -124,11 +124,11 @@ model_plans <- rbind(
 )
 
 reporting <- drake_plan(
-  'publication/supp_info.tex' = render('publication/supp_info.Rmd', quiet = TRUE),
-  'publication/supp_info.pdf' = latexmk('publication/supp_info.tex', clean = FALSE),
-  'publication/manuscript.tex' = render('publication/manuscript.Rmd', quiet = TRUE),
-  'publication/manuscript.pdf' = latexmk('publication/manuscript.tex', clean = FALSE),
-  'publication/questions_observations_todo.pdf' = my_render('publication/questions_observations_todo.Rmd', quiet = TRUE, depends_on = 'publication/manuscript.pdf'),
+  'paper/supp_info.tex' = render('paper/supp_info.Rmd', quiet = TRUE),
+  'paper/supp_info.pdf' = latexmk('paper/supp_info.tex', clean = FALSE),
+  'paper/manuscript.tex' = render('paper/manuscript.Rmd', quiet = TRUE),
+  'paper/manuscript.pdf' = latexmk('paper/manuscript.tex', clean = FALSE),
+  'paper/questions_observations_todo.pdf' = my_render('paper/questions_observations_todo.Rmd', quiet = TRUE, depends_on = 'paper/manuscript.pdf'),
   file_targets = TRUE
 )
 

### 2018-07-01 paper/manuscript.Rmd
Main model plot is now made in a separate function

@@
 ---
-title: "Pollen competition"
+title: "The pollination trade-off"
 author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
-date: "19 December 2017"
-output: pdf_document
 bibliography: references.bib
 csl: ecology-letters.csl
+output: 
+  bookdown::pdf_document2: 
+    keep_tex: yes
+    number_sections: false
+toc: false
 header-includes:
@@
   - \usepackage{setspace}
+  - \usepackage{lineno}
+  - \usepackage{xr}
+  - \externaldocument[S-]{supp_info}
 ---
 
+\linenumbers
 \doublespacing
 
-```{r, echo = F, message = F}
-library(magrittr)
-knitr::opts_chunk$set(
-  echo = FALSE,
-  message = FALSE, 
-  warning = FALSE
-)
-options("xtable.include.rownames" = FALSE,
-        "xtable.comment" = FALSE,
-        "xtable.size" = "small")
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
+                      warning = FALSE)
+options(xtable.comment = FALSE, 
+        xtable.caption.placement = 'bottom',
+        xtable.size = 'small',
+        booktabs = TRUE)
 ```
@@
 
+TBC
+
 ## Introduction
+
+Pollination systems play a disproportionally important role in food production and maintenance of global biodiversity. 
+In the context of animal pollination, the support to biodiversity is fundamentally achieved by virtue of intra-species facilition—the positive feedback loops that exist between plants that share pollinators or pollinators that share plants.
+Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources. 
+Indeed, studies that are fundamental to our current knowledge of mutualism predict that an upper limit to biodiversity is achieved when the number of mutualistic partners is maximised in a community. 
+And yet, fully connected natural pollination communities do not exist.
+
+This is so, because sharing a mutualistic partner also has costs. 
+The end result is that, when the cummulative costs have negative impact on fitnessis, species also start competeing for mutualistic partners. 
+For the 88% of flowering plants that rely on animal pollination, there are two mechanisms trough which competition for pollinators might arrise. 
+The first is competition for visits, where plants with more atractive flowers reduce the pollination service for those less atractive. 
+The second is interspecific pollen transfer, where even receiving a visit might not translate into net facilitation. 
+A focal plant might receive pollen from a different species, or conversely pollen from the focal plan might be lost to different species. 
+Here we focus on this second mechanism.
+
+The potential negative effects of competition for pollinators have been long recognised and widely documented. 
+It is currently clear that they have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies as well as driving ecological diferentiation. 
+Indeed there is considerable evidence demonstrating the effects that interspecific pollen transfer in two-species systems. 
+However, these competitive interactions between species pairs do not occur in isolation. 
+Instead, plants often ocurr in communities in which multiple competitive interactions operate simultaneusly and lead to emergent phenomena not observed at smaller scales.
+
+Nevertheless, only a handful of studies have examined interspecific pollen transfer at the community level, and therefore we still understand little about how compeition for pollinators operates at this scale.
+All together, existing studies show that, as expected, the effective result of mutualistic interactions is, in most cases, one of facilitation. 
+Importantly, they also show a large variability in this result—both across species and across communities. 
+However, the driving factors behind this variability are currently not understood.
+
+Understanding what makes species and communities different is important not only because of its ecological and evolutionary implications. 
+It is also important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. 
+Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree.
+The extent to which species degree affects the benefit is called *mutualistic trade-off*. 
+This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
+At the same time it is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
+Although, the mutualistic trade-off has been shown to play a determining role on the stability and diversity of mutualistic communities, empirical evidence is scarce, to say the least.
+
+Elucidating how the mechanisms and drivers of facilitation scales to the community level and its theoretical concequences has been elusive in part because of the large amounts of data required.
+Previous studies focus on the final picture of interspecific pollen transfer that is obtained by examining the pollen deposited on flower stigmas. 
+However, teasing appart the competition for pollinators also requires data that describes the structure of the interactions and the pollen flows that ocurr within it, while accounting for the traits of the species that integrate the community.
+Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas.
+Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
+Second, we investigate wether there is a relationship between this gain and a suite of variables that describe both the role of the plant species and the ecological context. 
+Here, we pay special attention to the role of species degree because of its ramifications to theoretical ecology. 
+At the same time, we examine wether the plant role and ecological context is best infered from dynamics occurring at the community level, or wether it can be well approximated using information available from all sites in which a species ocurr.
+Third, and finaly, we explore how plant species differ on the extent to which competition for pollinators shapes facilitation.
 
@@
 
-We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas (Figure 1). 
+We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas. 
 The sampling locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and an drier as we move inland and westward towards the Pampean Grasslands.
@@
 A quarter of these buds were bagged to prevent animal pollination. 
-Two days after inflorecense, we analysed the pollen grains in the flowers' pistils and classified it between conspecific and heterospecific pollen.
+Two days after inflorecense, we analysed the pollen grains in the flowers' pistils and classified them between conspecific and heterospecific pollen.
 
-The reader can find more details about the study sites, the data collection, and laboratory protocols in Marrero *et al.* (2014, 2016, and 2017)\footnote{
-This paper is almost entirely based on data that has already been published in separate units in Marrero et al. 2014, 2016, and 2017. 
-Marrero et al. 2014 used visitation data and determined that land uses (agricultural vs. restored) was correlated to differences on the degree of specialization and richness of plants and pollinators.
-Marrero et al.
-2016 used pollen deposition data and determined that the pollination service (both the absolute number and the proportion of conspecific pollen deposited on stigmas) is reduced in agricultural communities when compared to restored communities.
-Finally, Marrero et al. 2017 used pollen transfer networks and found that pollen diversity and pollination plant niche overlap (at the species level) is greater in agricultural communities. 
-The increase on niche overlap was attributed to be positively associated with an increased abundance of exotic plants.
-}.
+More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014, 2016, and 2017).
 
@@
 
+First, we explored wether animal pollination resulted in a quantitative increase in the pollination service.
+To do that, we compared the amount of conspecific pollen on stigmas from flowers open to animal pollination and that from flowers that were bagged, where only autogamus self-pollination ocurred.
+The difference between these two counts is not directly equivalent to the pollen deposited by animals because self-pollination is an adaptive trait [@Kalisz2003]. 
+Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output.
+We performed this comparisons using a set of non parametric Mann-Whitney tests both at the community and the the species level (grouping species across communities).
+
+Our main aim was to examine the extent to which the pollination service was influenced by the number of pollination partners while accounting for other metrics that describe the plant's pollination niche and community composition.
+To do so, we fitted four sets of linear mixed models [using the R package `nlme 3.1-131`, @nlme2017] which differed on whether the pollen deposited was conspecific or heterospecific and on wether independent variables were calculated across communities or independently within each community.
+In all set of models, our response variable was the difference between pollen density (pollen counts per stigma) between open and bagged flowers. 
+All together the results from each model set—and the relationship between them—provide with two important pieces of information. 
+First,  they provide indication of both the quantity and quality of animal pollination, and the potential trade-off between these two. 
+Second, it allowed us to examine wether indeed community level information is necessary to explain the observed patterms or whether less granular data is sufficient.
+
+All model sets were based on the same one hundred bootstrap resamples of the deposition data. 
+We used bootstrap resampling because, as open and bagged flowers were not paired, this allowed us to directly model the *gain* in pollen density rather than density itself. 
+This strategy, not only simplified the model specification and intepretation, but also allowed us to easily evaluate the uncertainity of the model results.  
+In each replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
+We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-logtransformed-or-not) and \@ref(S-fig:fig-deposition-gain-logtransformed-or-not)).
+Finally, we calculated the difference between the pollen density among treatmemts. 
+This difference was the response variable in all our models.
+
+As predictors, we included the species/degree (number of animal partners) as well as other factors that could influence the trade-off. 
+Specifically, we included the plants' relative abundance and the temporal niche overlap. 
+To calculate the plant's relative abbundance we simply aggregated the flower counts over the study period—either across communities of for each community depending on the model set. 
+As with the deposition data, we found that log-transforming the abundance counts drastically improved normality (Figure \@ref(S-fig:fig-abundance-logtransformed-or-not)).
+We then the log-transformed abundance counts for each month between November 2010 and March 2011 to calculate the temporal niche overlap between plants. 
+Specifically, we used the Pianka's niche overlap index [@Pianka1973; `spaa 0.2.2` R package @Zhang2016] which calculates an overlap index for each pair of species—again, across and within  communities depending on the model set.
+To calculate an overlap metric per species, we simply averaged the pairwise indices for a species. 
+To faciliate comparison across model estimates, we scaled all independent variables to have a mean of zero and a standard deviation of one.
+
+In all set of models we first evaluated a set of candidate random effects which included random intercepts for plant species as well as random slopes for the relationship between degree and pollen gain.
+In addition we also tested random intercepts assuming that the plant species grouping was hierachically nested in either their community, the land use, and the locality. 
+We selected the best random structure by comparing the median Akaike Information Criterion (AIC) of evaluated models fitted using restricted maximum likelyhood. 
+After determining the best random structure, we then focused on the model's fixed structure where we fitted the fixed effect coefficients using maximum likelyhood. 
+Because our purpose was to perform inter-model comparisons across multiple data resamples, we did not perform model selection. 
+Instead, in all model sets, we obtained the estimates for all the fixed effects we considered and then evaluated their relevance by examining their distribution.
+
+We compared the performance of the within and across communities model sets using the root-mean-square error normalised by the interquartile range (NRMSE). 
+We tested the significance of this difference using a two sample paired Wilcoxon signed rank test for conspecific and heterospecific pollen models. 
+We chosed NRMSE because it provides an easily interpretable metric related to the quality of the predictions while being farily insensitive to sample size. 
+This inensitivity was desirable because the across communities models had often slightly larger sample sizes owing to the fact of some species not having all data necessary to calculate the independent variables at the community level.
+
+Finally, we focused on how the relationship between conspecific and heterospecific pollen gain. 
+First we examined wether the pollination trade-off was related to our explanatory variables. 
+To do so, we harnessed the results from the conspecific and heterospecific pollen models that performed best (across or within communities). 
+To examine the relationship between these model sets, we sampled 100 estimates from the distribution of coefficients in each set. 
+For each of the samples, we then calculated the difference between the gain in conspecific and heterospecific pollen that would be predicted assuming mean values for the random intercepts and the other predictors.
+
+Second, we calulated the the extent of facilitation. 
+For this purpose, as in @Tur2016a, we used the relationship between heterospecific and conspecific pollen. 
+We calculated an overal relationship by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair [we used the R package `smatr 3.4-3`, @Warton2012a].
+We followed a similar procedure to calculate a relationship per species but instead of fitting a SMA per model pair, we did so across the 100 models for each species independently.
+
 ## Results
+
+```{r differences-in-self-pollination}
+loadd(significant_gain_global, significant_gain_site)
+
+sgg <- glance_table(significant_gain_global)
+prop_sig_global <- sum(sgg$p.value < 0.05) /
+  length(significant_gain_global)
+sgs <- glance_table(significant_gain_site)
+prop_sig_site <- sum(sgs$p.value < 0.05) /
+  length(significant_gain_site)
+
+consistency <- inner_join(sgg, sgs, by = 'recipient') %>% 
+  mutate_at(.vars = c('p.value.x', 'p.value.y'), 
+            .funs = function(x) x < 0.05) %>%
+  mutate(consistent = p.value.x == p.value.y) %>%
+  group_by(recipient) %>%
+  summarise(p.value.x = mean(p.value.x), 
+            consistent = all(consistent),
+            n_sites = n_distinct(site_name)) %>% 
+  filter(n_sites > 1)
+prop_consistency <- sum(consistency$consistent)/
+  nrow(consistency)
+```
+
+Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
+When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(S-tab:table-species-gain-site)).
+Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table \@ref(S-tab:table-variation-across-sites)).
+
+We found that the random structure that was best supported the data was consistently the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
+When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better approximated by the model sets using predictors calculated across communities (Table \@ref(S-tab:table-global-vs-community-models)).
+This was so despite the fact that the model predictors calculated at the community level were highly correlated to those at the study wide level (Figure \@ref(S-fig:fig-global-community-correlations)).
+Nevertheless, results from the within community models are similar both qualitatively and quantitatively (with the exception of phenology overlap, but that might change once I use a better metric, Figure \@ref(S-fig:fig-model-results)).
+
+We found that the gain in conspecific pollen is negatively affected by the plants relative abbundance and to a smaller extent by the species' degree (Figure \@ref(fig:fig-model-results-global). 
+The gain in heterospecific pollen was instead positively affected by degree and the plant's phenology overlap, but was also strongly negatively affected by the plant's relative abbundance.
+
+```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
+Results are shown for models with explanatory var"}
+drake::readd(fig_model_results_global)
+```
+
+The gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 
+The slope of the relationship is such that it is more likely that the gain on heterospecific pollen increases faster than the gain on conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)A).
+In addition, we found that from all the explanatory variables examined, only the plant's relative abbundance has a positive effect on the proportion of conspecific pollen gained (Figure \@ref(fig:fig-trade-off-predictions)B).
+For most of the parameter space plants obtain a larger proportion of heteropspecific than conspecific pollen. 
+However, plants can obtain a larger proportion of conspecific pollen when they have high abundance and to a smaller extent when they have a low degree. 
+When examining the extent of facilitation at the species level, we found that XXX (Figure \@ref(fig:fig-trade-off-predictions)B).
+
+```{r fig-trade-off-predictions, fig.height= 2.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
+(A) Overall and species-level relationship.
+Grey lines indicate the relationship in each of the samples, the median is indicated with a black solid line.
+Dotted lines show the relationship for each species.
+Invasive species are shown in red.
+(B) The proportion of conspecific pollen relative to the total amount of pollen gained trough animal pollination and its relationship to our set of explanatory variables."}
+loadd(trade_off_predictions, model_linear_fits, tidied_fixed)
+
+get_pred_range <- function(x){
+  tidied_fixed %>% 
+    filter(pollen_category == x, var_trans == "log", scale == "global") %$% 
+    estimate %>% range()
+}
+
+ab_lines <- model_linear_fits %>%
+  filter(var_trans == "log",
+         scale == "global") %>%
+  spread(sma_parameter, value)
+
+p1 <- data_frame(x = get_pred_range("heterospecific"),
+                 y = get_pred_range("conspecific")) %>%
+  ggplot(aes(x, y)) +
+  geom_abline(data = ab_lines, 
+              aes(slope = slope, intercept = elevation), 
+              size = 0.1, linetype = 1, colour = "grey", 
+              alpha = 0.5) +
+  geom_abline(data = summarise_if(ab_lines, is.numeric, median), 
+              aes(slope = slope, intercept = elevation), 
+              size = 0.5, linetype = 1, colour = "black") +
+  geom_abline(slope = 1, intercept = 0, size = 0.25, linetype = 2) +
+  geom_point(alpha = 0) +
+  coord_equal(xlim = get_pred_range("heterospecific"),
+              ylim = get_pred_range("conspecific")) +
+  pub_theme() +
+  labs(x = "gain in heterospecific pollen", 
+       y = "gain in conspecific pollen")
+
+p2 <- trade_off_predictions %>%
+  mutate_at(c("conspecific", "heterospecific"), exp) %>%
+  mutate(gain = conspecific / (conspecific + heterospecific)) %>%
+  filter(!(value > 2.2 & term == "k")) %>%
+  humanize() %>%
+  ggplot(aes(x = value, y = gain, colour = term)) +
+  geom_hline(yintercept = 0.5, size = 0.25, linetype = 2) + 
+  geom_point(shape = 21, alpha = 0.5, size = 1) +
+  geom_smooth(aes(fill = term), 
+              se = F, size = 0.5, method = "glm", 
+              method.args = list(family = "binomial"), alpha = 0.1)+
+  pub_theme() +
+  scale_color_manual(values = colour_scale_values) +  
+  scale_fill_manual(values = colour_scale_values) +
+  scale_y_continuous(labels = scales::percent) +
+  theme(legend.position = "top") +
+  labs(colour = "", fill = "", linetype = "", 
+       y = "proportion conspecific pollen gain", 
+       x = "scaled variable value")
+
+cowplot::plot_grid(p1, p2, 
+                   align = "h", axis = "tb", ncol = 2, labels = LETTERS[1:2], 
+                   label_size = 8, rel_widths = c(0.35, 0.65))
+```
 
@@
 
+* We found that animal pollination only brings a small amount of extra conspecific pollen (compared to selfing) if any.
+This relatively small difference is probably very important though because crossing has been shown to be evolutionary better than cloning in the long term.
+* The relationship between conspecific and heterospecific pollen is positive which indicates than net facilitation is the dominant outcome.
+This agrees with previous findings.
+However the amount of added conspecific pollen is in average smaller than the amount of added heterospecific pollen.
+* Despite finding that facilitation is the most common outcome. We also were able to find clear signature of competition for pollinators at the community level.
+* We found that, as assumed in pollination models, the mutualistic benefit is modulated by the species degree and therefore there is indeed evidence for a trade-off.
+Moreover, the trade off does not depend on the species or the community.
+Which is a good thing because we tend to simplify models by assuming a common trade-off for the whole community.
+* However the mutualistic benefit was not just modulated by the degree but other factors also played significant roles. 
+* These factors, in particular the plant relative abundance, was important at explaining the differences between plants. 
+* We found that models performed better when explanatory variables were constructed so that they take into account information across all the communities in which a species was present.
+This means that despite the particularities of each community (random effects acounted for a large proportion of the variance) we can still predict general outcomes by knowing some general traits about the plant species and how it relates to other plants in their community.
+
 ## References

### 2018-07-01 code/fig_pollen_density_gain.R

@@ -1,0 +1,36 @@
+
+make_fig_model_results_global <- function(tidied_fixed) {
+  
+  require(ggplot2)
+  
+  tidied_fixed %>%
+    dplyr::filter(
+      term != "(Intercept)" , 
+      var_trans == 'log',
+      scale == "global") %>%
+    dplyr::group_by(pollen_category,scale, model, var_trans, term) %>%
+    dplyr::summarise(estimate = dplyr::first(estimate)) %>%
+    dplyr::group_by() %>%
+    humanize() %>%
+    ggplot(aes(
+      x = estimate, 
+      colour = pollen_category, 
+      fill = pollen_category)) +
+    geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
+    stat_density(
+      geom = 'line',
+      # alpha = 0.15,
+      position = position_identity(),
+      # draw_quantiles = c(0.5, 0.95, 0.05), 
+      trim = T 
+      # scale = "count"
+      ) +
+    pub_theme() +
+    facet_grid( ~ term, scales = "free_x", space = "free_x") +
+    scale_color_manual(values = c_scale()) +
+    scale_fill_manual(values = c_scale()) +
+    scale_x_continuous(breaks = seq(-2,2, by = 0.25)) + 
+    theme(legend.position = "top") +
+    labs(colour = "", fill = "", x = "estimated effect on pollen gain")
+
+}

### 2018-07-01 main.R

@@ -117,23 +117,24 @@ model_plans <- rbind(
 
 # Plots -------------------------------------------------------------------
 
-reporting <- drake::drake_plan(
-  'paper/supp_info.tex' = render('paper/supp_info.Rmd', quiet = TRUE),
-  'paper/supp_info.pdf' = latexmk('paper/supp_info.tex', clean = FALSE),
-  'paper/manuscript.tex' = render('paper/manuscript.Rmd', quiet = TRUE),
-  'paper/manuscript.pdf' = latexmk('paper/manuscript.tex', clean = FALSE),
-  'paper/questions_observations_todo.pdf' = my_render('paper/questions_observations_todo.Rmd', quiet = TRUE, depends_on = 'paper/manuscript.pdf'),
-  file_targets = TRUE
+figure_plan <- drake::drake_plan(
+  fig_model_results_global = make_fig_model_results_global(tidied_fixed)
 )
 
 # Reporting ---------------------------------------------------------------
 # Make all ----------------------------------------------------------------
 
 # set up plan
-project_plan <- rbind(clean_data, format_data,
-                      boot_replicates, 
-                      model_plans,
-                      analysing, reporting)
+project_plan <- rbind(
+  clean_data_plan, 
+  format_data_plan,
+  boot_replicates, 
+  model_plans,
+  basic_analyses_plan,
+  figure_plan#, 
+  #reporting_plan
+  )
+# project_plan <- rbind(clean_data_plan, format_data_plan, basic_analyses_plan)
 project_config <- drake::drake_config(project_plan)
 drake::vis_drake_graph(project_config, targets_only = T)
 

### 2018-07-01 main.R
Minor style changes to main script

@@ -61,30 +61,24 @@ boot_replicates <- drake::drake_plan(
     degree, 
     sites, 
     transformation, 
-    N)
-) %>%
+    N)) %>%
   drake::evaluate_plan(rules = list(N = 1:n_replicates)) 
 
 random_models <- drake::drake_plan(
   random_mod = run_random_models(rep_N, random_effects)
 ) %>%
   drake::evaluate_plan(rules = list(N = 1:n_replicates)) 
-
 glanced_random_models <- random_models %>%
   drake::gather_plan(., gather = "glance_random_models", target = "glanced_random")
-
 random_summaries <- drake::drake_plan(
   best_random = best_random_effect(glanced_random, random_effects)
 )
 
 fixed_models <- drake::drake_plan(
-  fixed_mod = run_model(rep_N, best_random)
-) %>%
+  fixed_mod = run_model(rep_N, best_random)) %>%
   drake::evaluate_plan(rules = list(N = 1:n_replicates)) 
-
 glanced_fixed_models <- fixed_models %>%
     drake::gather_plan(., gather = "glance_fixed_models", target = "glanced_fixed")
-
 tidied_fixed_models <- fixed_models %>%
   drake::gather_plan(., gather = "tidy_fixed_models", target = "tidied_fixed")
 

### 2018-07-01 paper/manuscript.Rmd
Figures are now constructed in their own functions

@@
 (B) The proportion of conspecific pollen relative to the total amount of pollen gained trough animal pollination and its relationship to our set of explanatory variables."}
-loadd(trade_off_predictions, model_linear_fits, tidied_fixed)
-
-get_pred_range <- function(x){
-  tidied_fixed %>% 
-    filter(pollen_category == x, var_trans == "log", scale == "global") %$% 
-    estimate %>% range()
-}
-
-ab_lines <- model_linear_fits %>%
-  filter(var_trans == "log",
-         scale == "global") %>%
-  spread(sma_parameter, value)
-
-p1 <- data_frame(x = get_pred_range("heterospecific"),
-                 y = get_pred_range("conspecific")) %>%
-  ggplot(aes(x, y)) +
-  geom_abline(data = ab_lines, 
-              aes(slope = slope, intercept = elevation), 
-              size = 0.1, linetype = 1, colour = "grey", 
-              alpha = 0.5) +
-  geom_abline(data = summarise_if(ab_lines, is.numeric, median), 
-              aes(slope = slope, intercept = elevation), 
-              size = 0.5, linetype = 1, colour = "black") +
-  geom_abline(slope = 1, intercept = 0, size = 0.25, linetype = 2) +
-  geom_point(alpha = 0) +
-  coord_equal(xlim = get_pred_range("heterospecific"),
-              ylim = get_pred_range("conspecific")) +
-  pub_theme() +
-  labs(x = "gain in heterospecific pollen", 
-       y = "gain in conspecific pollen")
-
-p2 <- trade_off_predictions %>%
-  mutate_at(c("conspecific", "heterospecific"), exp) %>%
-  mutate(gain = conspecific / (conspecific + heterospecific)) %>%
-  filter(!(value > 2.2 & term == "k")) %>%
-  humanize() %>%
-  ggplot(aes(x = value, y = gain, colour = term)) +
-  geom_hline(yintercept = 0.5, size = 0.25, linetype = 2) + 
-  geom_point(shape = 21, alpha = 0.5, size = 1) +
-  geom_smooth(aes(fill = term), 
-              se = F, size = 0.5, method = "glm", 
-              method.args = list(family = "binomial"), alpha = 0.1)+
-  pub_theme() +
-  scale_color_manual(values = colour_scale_values) +  
-  scale_fill_manual(values = colour_scale_values) +
-  scale_y_continuous(labels = scales::percent) +
-  theme(legend.position = "top") +
-  labs(colour = "", fill = "", linetype = "", 
-       y = "proportion conspecific pollen gain", 
-       x = "scaled variable value")
-
-cowplot::plot_grid(p1, p2, 
+cowplot::plot_grid(
+  drake::readd(fig_con_hetero_gain), 
+  drake::readd(fig_proportion_vs_variables), 
   align = "h", axis = "tb", ncol = 2, labels = LETTERS[1:2], 

### 2018-07-01 code/make_fig_con_hetero_gain.R

@@ -1,0 +1,36 @@
+make_fig_con_hetero_gain <- function(tidied_fixed, model_linear_fits) {
+  require(ggplot2)
+  ab_lines <- model_linear_fits %>%
+    dplyr::filter(var_trans == "log",
+                  scale == "global") %>%
+    tidyr::spread(data = ., key = sma_parameter, value = value)
+  
+  dplyr::data_frame(x = get_pred_range(tidied_fixed, "heterospecific"),
+                   y = get_pred_range(tidied_fixed, "conspecific")) %>%
+    ggplot(aes(x, y)) +
+    geom_abline(data = ab_lines, 
+                aes(slope = slope, intercept = elevation), 
+                size = 0.1, linetype = 1, colour = "grey", 
+                alpha = 0.5) +
+    geom_abline(data = dplyr::summarise_if(ab_lines, is.numeric, median), 
+                aes(slope = slope, intercept = elevation), 
+                size = 0.5, linetype = 1, colour = "black") +
+    geom_abline(slope = 1, intercept = 0, size = 0.25, linetype = 2) +
+    geom_point(alpha = 0) +
+    coord_equal(xlim = get_pred_range(tidied_fixed, "heterospecific"),
+                ylim = get_pred_range(tidied_fixed, "conspecific")) +
+    pub_theme() +
+    labs(x = "gain in heterospecific pollen", 
+         y = "gain in conspecific pollen")
+}
+
+# function just to get the range of preditions
+get_pred_range <- function(tidied_fixed, x, var_trans = "log", scale = "global"){
+  tidied_fixed %>% 
+    dplyr::filter(
+      pollen_category == x,
+      var_trans == var_trans, 
+      scale == scale) %$% 
+    estimate %>% 
+    range()
+}

### 2018-07-01 code/make_fig_proportion_vs_variables.R

@@ -1,0 +1,22 @@
+make_fig_proportion_vs_variables <- function(trade_off_predictions) {
+  require(ggplot2)
+  trade_off_predictions %>%
+    dplyr::mutate_at(c("conspecific", "heterospecific"), exp) %>%
+    dplyr::mutate(gain = conspecific / (conspecific + heterospecific)) %>%
+    dplyr::filter(!(value > 2.2 & term == "k")) %>%
+    humanize() %>%
+    ggplot(aes(x = value, y = gain, colour = term)) +
+    geom_hline(yintercept = 0.5, size = 0.25, linetype = 2) + 
+    geom_point(shape = 21, alpha = 0.5, size = 1) +
+    geom_smooth(aes(fill = term), 
+                se = F, size = 0.5, method = "glm", 
+                method.args = list(family = "binomial"), alpha = 0.1)+
+    pub_theme() +
+    scale_color_manual(values = c_scale()) +  
+    scale_fill_manual(values = c_scale()) +
+    scale_y_continuous(labels = scales::percent) +
+    theme(legend.position = "top") +
+    labs(colour = "", fill = "", linetype = "", 
+         y = "proportion conspecific pollen gain", 
+         x = "scaled variable value")
+}

### 2018-07-01 main.R

@@ -112,7 +112,9 @@ model_plans <- rbind(
 # Plots -------------------------------------------------------------------
 
 figure_plan <- drake::drake_plan(
-  fig_model_results_global = make_fig_model_results_global(tidied_fixed)
+  fig_model_results_global = make_fig_model_results_global(tidied_fixed), 
+  fig_con_hetero_gain = make_fig_con_hetero_gain(tidied_fixed, model_linear_fits), 
+  fig_proportion_vs_variables = make_fig_proportion_vs_variables(trade_off_predictions)
 )
 
 # Reporting ---------------------------------------------------------------

### 2018-07-01 paper/manuscript.Rmd
Explicit namespace in manuscript

@@
 
-consistency <- inner_join(sgg, sgs, by = 'recipient') %>% 
+consistency <- dplyr::inner_join(sgg, sgs, by = 'recipient') %>% 
   mutate_at(.vars = c('p.value.x', 'p.value.y'), 
             .funs = function(x) x < 0.05) %>%
-  mutate(consistent = p.value.x == p.value.y) %>%
-  group_by(recipient) %>%
-  summarise(p.value.x = mean(p.value.x), 
+  dplyr::mutate(consistent = p.value.x == p.value.y) %>%
+  dplyr::group_by(recipient) %>%
+  dplyr::summarise(p.value.x = mean(p.value.x), 
             consistent = all(consistent),
-            n_sites = n_distinct(site_name)) %>% 
-  filter(n_sites > 1)
+            n_sites = dplyr::n_distinct(site_name)) %>% 
+  dplyr::filter(n_sites > 1)
 prop_consistency <- sum(consistency$consistent)/

### 2018-07-01 paper/manuscript.Rmd
Remove xtable from manuscript (will likely use kable extra)

@@
                       warning = FALSE)
-options(xtable.comment = FALSE, 
-        xtable.caption.placement = 'bottom',
-        xtable.size = 'small',
-        booktabs = TRUE)
 ```

### 2018-07-01 paper/questions_observations_todo.Rmd
Keep tex so I can use the same function to compile this as the others

@@
   bookdown::pdf_document2: 
-    keep_tex: no
+    keep_tex: yes
     number_sections: false
@@
 
-This paper is almost entirely based on data that has already been published in separate units in Marrero et al. 2014, 2016, and 2017. 
+This paper is almost entirely based on data that has already been published intidyr::separate units in Marrero et al. 2014, 2016, and 2017. 
 Marrero et al. 2014 used visitation data and determined that land uses (agricultural vs. restored) was correlated to differences on the degree of specialization and richness of plants and pollinators.

### 2018-07-01 paper/manuscript.Rmd
Some functions didnt have explicit namespace

@@
 ```{r differences-in-self-pollination}
-loadd(significant_gain_global, significant_gain_site)
+drake::loadd(significant_gain_global, significant_gain_site)
 
@@
 consistency <- dplyr::inner_join(sgg, sgs, by = 'recipient') %>% 
-  mutate_at(.vars = c('p.value.x', 'p.value.y'), 
+  dplyr::mutate_at(.vars = c('p.value.x', 'p.value.y'), 
             .funs = function(x) x < 0.05) %>%

### 2018-07-01 main.R
Render manuscript and questions file

@@ -118,6 +118,12 @@ figure_plan <- drake::drake_plan(
 )
 
 # Reporting ---------------------------------------------------------------
+
+reporting_plan <- drake::drake_plan(
+  # render_pdf(drake::knitr_in('paper/supp-info.Rmd'), drake::file_out('paper/supp-info.pdf'), clean_md = FALSE),
+  render_pdf(drake::knitr_in('paper/manuscript.Rmd'), drake::file_out('paper/manuscript.pdf'), clean_md = FALSE),
+  render_pdf(drake::file_in('paper/questions_observations_todo.Rmd'), drake::file_out('paper/questions_observations_todo.pdf'), clean_md = FALSE))
+
 # Make all ----------------------------------------------------------------
 
 # set up plan
@@ -127,10 +133,10 @@ project_plan <- rbind(
   boot_replicates, 
   model_plans,
   basic_analyses_plan,
-  figure_plan#, 
-  #reporting_plan
+  figure_plan, 
+  reporting_plan
   )
-# project_plan <- rbind(clean_data_plan, format_data_plan, basic_analyses_plan)
+
 project_config <- drake::drake_config(project_plan)
 drake::vis_drake_graph(project_config, targets_only = T)
 

### 2018-07-02 paper/supp-info.Rmd
Supp info works now

---
title: "The pollination trade-off"
subtitle: "Supplementary information"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
# bibliography: references.bib
csl: ecology-letters.csl
documentclass: book
nocite: | 
  @Xu2003, @Nakagawa2013
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
---

\renewcommand\thefigure{S\arabic{figure}}    
\setcounter{figure}{0}

\renewcommand\thetable{S\arabic{table}}    
\setcounter{table}{0}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(xtable.comment = FALSE, 
        xtable.caption.placement = 'bottom',
        xtable.size = 'small',
        booktabs = TRUE)
```

```{r fig-deposition-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown)."}
drake::loadd(fig_pollen_density)

leg <- cowplot::get_legend(fig_pollen_density[[1]])
cowplot::plot_grid(
  remove_legend(fig_pollen_density[[1]]),
  remove_legend(fig_pollen_density[[2]]), 
  labels = LETTERS[1:2], 
  label_size = 8) %>%
  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
```

```{r fig-deposition-gain-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of the difference on stigmatic pollen density between open and closed flowers for one of the bootstrap replicates used in the model sets. When (A) using directly the gain in pollen density and (B) when pollen density is log transormed prior to calculating the gain. "}
drake::loadd(fig_pollen_density_diff)

leg <- cowplot::get_legend(fig_pollen_density_diff[[1]])
cowplot::plot_grid(
  remove_legend(fig_pollen_density_diff[[1]]), 
  remove_legend(fig_pollen_density_diff[[2]]), 
  labels = LETTERS[1:2], 
  label_size = 8,
  ncol = 2) %>%
  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
```

```{r fig-abundance-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
drake::loadd(fig_abundance)

cowplot::plot_grid(
  fig_abundance[[2]], 
  fig_abundance[[2]],
  rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
```

```{r table-species-gain-global, results = 'asis'}
drake::loadd(significant_gain_global, significant_gain_site, sites)
glance_table(significant_gain_global) %>%
  dplyr::select(recipient, estimate, statistic, p.value) %>%
  dplyr::mutate(recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
  dplyr::rename(`p value` = p.value,
         `difference` = estimate,
         `plant species` = recipient) %>%
  knitr::kable(
    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. Tests were performed at the species level (across communities).", 
    escape = FALSE)
```

```{r table-species-gain-site, results = 'asis'}
drake::loadd(significant_gain_global, significant_gain_site, sites)
glance_table(significant_gain_site) %>%
 dplyr::inner_join(sites, by = "site_name") %>%
  dplyr::group_by(recipient) %>%
  dplyr::mutate(n_sites = dplyr::n_distinct(site_name)) %>%
  dplyr::filter(n_sites > 1) %>%
  dplyr::group_by() %>%
  dplyr::mutate(site_name = paste(locality_name, land_use, fragment, sep = ' - '),
         recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
  dplyr::select(recipient, site_name, estimate, statistic, p.value) %>%
  dplyr::rename(`p value` = p.value,
         `difference` = estimate,
         `plant species` = recipient, 
         `community` = site_name) %>%
  knitr::kable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. Tests were performed at the community level. Only species present in more than one community are shown.")
```

```{r table-variation-across-sites, results='asis'}
drake::loadd(consp_self)
consp_self %>%
  anova(test = "Chisq")  %>%
  xtable::xtable(caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).  Density were modelled using a quasipoisson distribution. The model suggests that self-pollination rates are species dependent but not across.',
         label = 'tab:table-variation-across-sites')
```

```{r fig-conspecific-per-site, eval = FALSE, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
drake::loadd(dep_frame, sites)
library(ggplot2)
site_plots_conspecific <- dep_frame %>%
  dplyr::filter(pollen_category == 'conspecific') %>%
 dplyr::inner_join(sites, by = 'site_name') %>%
  dplyr::mutate(recipient_short = shorten_sp_name(recipient)) %>%
  dplyr::mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = dplyr::if_else(treatment == 'closed', 'bagged', treatment)) %>% 
  plyr::dlply('site_name', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = recipient_short,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() + 
      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_manual(values = c_scale())
  })

legend <- cowplot::get_legend(site_plots_conspecific[[1]])

site_plots_conspecific <- site_plots_conspecific %>%
  plyr::llply(function(x) {
    x + theme(legend.position = 'none', 
              title = element_text(size = 6))
  })

site_plots_conspecific <- rlist::list.append(site_plots_conspecific, legend)

cowplot::plot_grid(plotlist = site_plots_conspecific, ncol = 3)

```

```{r fig-conspecific-per-plant, eval = FALSE, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species. Only species present in more than onse site are shown. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio; A, and R indicate that the community corresponded to an agricultural or reserve site respectively."}
drake::loadd(dep_frame, sites)
plant_plots_conspecific <- dep_frame %>%
  dplyr::filter(pollen_category == 'conspecific') %>%
 dplyr::inner_join(sites, by = 'site_name') %>%
  dplyr::mutate(recipient_short = shorten_sp_name(recipient)) %>%
  dplyr::mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = dplyr::if_else(treatment == 'closed', 'bagged', treatment)) %>%
  dplyr::group_by(recipient) %>%
  dplyr::mutate(n_sites = dplyr::n_distinct(site_name), 
         site_name = `str_sub<-`(site_name, 1, 3, value = ''), 
         site_name = str_replace_all(site_name, '_', ' - ')) %>%
  dplyr::group_by() %>%
  dplyr::filter(n_sites >= 2) %>%
  plyr::dlply('recipient', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = site_name,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() +
      ggtitle(paste(x$recipient[1])) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_manual(values = c_scale())
  })

legend <- cowplot::get_legend(plant_plots_conspecific[[1]])

plant_plots_conspecific <- plant_plots_conspecific %>%
  plyr::llply(function(x) {
    x + theme(legend.position = 'none',
              title = element_text(size = 6))
  })

plant_plots_conspecific <- rlist::list.append(plant_plots_conspecific, legend)

cowplot::plot_grid(plotlist = plant_plots_conspecific, ncol = 3)
```

```{r fig-global-community-correlations, fig.height = 2.5, fig.cap = "Relationship between the model's independent variables calculated at the community level and at the study-wide level."}
drake::loadd(plant_rel_abu, plant_pheno_overlap, degree, sites)

ab <- plant_rel_abu %>%
  dplyr::select(-abu) %>%
  dplyr::rename(value = rab) %>%
  dplyr::mutate(term = "rab")

ph <- plant_pheno_overlap %>%
  dplyr::rename(value = tov) %>%
  dplyr::mutate(term = "tov")

k <- degree %>%
  dplyr::select(-kn) %>%
  dplyr::rename(value = k) %>%
  dplyr::mutate(term = "k")

dplyr::bind_rows(ab, ph, k) %>%
  dplyr::filter(var_trans == "log") %>%
  tidyr::spread(scale, value) %>%
  humanize(sites) %>%
  ggplot(aes(x = community, y = global)) +
  geom_smooth(method = "lm", colour = "black", size = 0.75) +
  geom_hline(yintercept = 0, size = 0.25, linetype = 2) +
  geom_vline(xintercept = 0, size = 0.25, linetype = 2) +
  geom_point(shape = 21, size = 1) +
  facet_wrap( ~ term, scales = "free") +
  coord_equal() +
  pub_theme()
```

```{r fig-model-results, fig.height = 3.5, fig.cap = "Model coefficients"}
drake::loadd(tidied_fixed, sites)

tidied_fixed %>%
  dplyr::filter(term != "(Intercept)" , 
         var_trans == 'log'
         # scale == "community"
         ) %>%
  dplyr::group_by(pollen_category,scale, model, var_trans, term) %>%
  dplyr::summarise(estimate = first(estimate)) %>%
  dplyr::group_by() %>%
  humanize() %>%
  ggplot(aes(x = estimate, 
             colour = pollen_category, 
             fill = pollen_category)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
  stat_density(geom = 'area',
               alpha = 0.15,
               position = position_identity(),
               draw_quantiles = c(0.5, 0.95, 0.05), 
               trim = F, 
               scale = "count",
               bins = 15) +
  pub_theme() +
  facet_grid(scale ~ term, scales = "free_x", space = "free_x") +
  scale_color_manual(values = c_scale()) +
  scale_fill_manual(values = c_scale()) +
  scale_x_continuous(breaks = seq(-2,2, by = 0.25)) + 
  theme(legend.position = "top") +
  labs(colour = "", fill = "")
```

```{r fig-random-intercepts, eval = F, fig.height= 3, fig.cap = "Random effect intercepts"}
drake::loadd(tidied_fixed, sites)

tidied_fixed %>%
 tidyr::separate("level", c("site_name", "plant_name"), sep = "/", remove = F) %>%
  dplyr::filter(term == "(Intercept)" ,
         var_trans == 'log',
         scale == "community", 
         pollen_category == 'heterospecific'
         ) %>%
  humanize(sites) %>%
  ggplot(aes(x = estimate, colour = plant_name, group = level)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
  geom_freqpoly(size = 0.25) +
  facet_grid(locality_name + fragment ~ land_use) +
  pub_theme() +
  theme(legend.position = 'none')
```

```{r eval = FALSE, table-aic-random-models, results= 'asis'}
drake::loadd(glanced_random, random_effects)

summ <- glanced_random %>%
  dplyr::filter(var_trans == "log") %>%
  dplyr::group_by(pollen_category, scale, var_trans, model) %>%
  dplyr::mutate(delta_AIC = AIC - min(AIC)) %>%
  dplyr::group_by(pollen_category, scale, var_trans, random_effect) %>%
  dplyr::summarise(AIC_50 = median(delta_AIC), 
            AIC_05 = quantile(delta_AIC, 0.05),
            AIC_95 = quantile(delta_AIC, 0.95), 
            n = n()) %>% 
  dplyr::group_by() %>%
  dplyr::select(-var_trans) %>%
  dplyr::right_join(expand.grid(pollen_category = unique(.$pollen_category),
                        scale = unique(.$scale),
                        random_effect = unique(.$random_effect))) %>% 
  dplyr::mutate_if(is.numeric, round, digits = 1) %>% 
  dplyr::mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "], n = ", n), 
         delta_AIC = dplyr::if_else(grepl("NA", delta_AIC), "---", delta_AIC)) %>%
  dplyr::group_by() %>%
  humanize(random_effects = random_effects) %>%
  dplyr::arrange(pollen_category, random_name, scale) %>%
  dplyr::rename(`pollen category` = pollen_category, 
         `random structure` = random_name)

contingency_table <- xtabs( ~ `random structure` + `scale` + `pollen category` , data = summ) %>% ftable()

# contingency_table <- summ %>%
  # ftable.formula(`random structure` ~ `scale` + `pollen category`)

contingency_table[1:nrow(summ)] <- summ$delta_AIC

xtable::xtableFtable(contingency_table, method = "col.compact", 
             caption = paste('Comparison of the different random structures we considered. The table shows median delta AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data. The 5th and 95th percentile are shown inside square brackets. Communities are defined by individual fragments but ignore the hierarchical arrangement of sampling sites."), 
         label = 'tab:table-aic-random-models')
```

```{r table-global-vs-community-models, results = 'asis'}
drake::loadd(wilcox_glo_com)

wilcox_glo_com %>%
  dplyr::filter(quality %in% c("rmse", "sigma", "r2c", "o2", "nrmse"),
         var_trans == "log") %>%
  dplyr::select(quality, pollen_category, min_scale, estimate, p.value) %>%
  dplyr::rename(`model metric` = quality,
         `pollen type` = pollen_category, 
         `best model set` = min_scale,
         `shift estimate` = estimate, 
         `p value` = p.value) %>% 
  xtable::xtable(digits = -1, caption = "Results of two sample paired Wilcoxon signed rank test comparing different model quality metrics of the model sets using predictors computed across or within communities. Metrics are the root mean square error (rmse), the residual standard deviation (sigma), the conditional r-squared approximation as proposed by Nakagawa and Schielzeth (2013), the omega-squared value as suggested by Xu (2003), and the normalised root-mean-square error of the model sets constructed using predictors computed at the community or study level.", 
         label = "tab:table-global-vs-community-models")
```

# References

### 2018-07-09 paper/manuscript.Rmd
Disable bibliography temporarly until fixing Zotero for this project

@@
 author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
-bibliography: references.bib
+#bibliography: references.bib
 csl: ecology-letters.csl

### 2018-07-20 paper/manuscript.Rmd
Edit intro to add motivation about traits, pollen and abundance

@@
 
-## Introduction
+# Introduction
 
@@
 This is so, because sharing a mutualistic partner also has costs. 
-The end result is that, when the cummulative costs have negative impact on fitnessis, species also start competeing for mutualistic partners. 
-For the 88% of flowering plants that rely on animal pollination, there are two mechanisms trough which competition for pollinators might arrise. 
-The first is competition for visits, where plants with more atractive flowers reduce the pollination service for those less atractive. 
-The second is interspecific pollen transfer, where even receiving a visit might not translate into net facilitation. 
-A focal plant might receive pollen from a different species, or conversely pollen from the focal plan might be lost to different species. 
-Here we focus on this second mechanism.
+The end result is that, when the cummulative costs have a negative impact on fitness, species also start competing for mutualistic partners. 
+The possible negative effects of competition for pollinators have been long recognised and widely documented.
+Based mainly on two-species systems, it is currently clear that they have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies as well as driving ecological diferentiation.
+However, these competitive interactions between species pairs do not occur in isolation. 
+Plants often ocurr in communities in which multiple competitive interactions operate simultaneusly and lead to emergent phenomena not observed at smaller scales. 
+Here, we explore the signatures competition for pollinators in diverse natural communities, where empirical data is more scarce.
 
-The potential negative effects of competition for pollinators have been long recognised and widely documented. 
-It is currently clear that they have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies as well as driving ecological diferentiation. 
-Indeed there is considerable evidence demonstrating the effects that interspecific pollen transfer in two-species systems. 
-However, these competitive interactions between species pairs do not occur in isolation. 
-Instead, plants often ocurr in communities in which multiple competitive interactions operate simultaneusly and lead to emergent phenomena not observed at smaller scales.
+At the community scale, competition for pollination might arrise from changes in the quantity and quality of pollination. 
+Quantity is mainly affected by competition for visits, where plants with more atractive flowers reduce the number of visits for those less atractive and therefore they may experience a reduction in the amount of conspecific pollen received.
+Quality is mainly affected by a more subtle but perhaps more important mechanism—interspecific pollen transfer, where even receiving a visit might not translate into net facilitation. 
+This is so because focal plant might receive pollen from a different species, or conversely pollen from the focal plant might be lost to different species. 
+Generally speaking the larger the proportion of conspecific relative to heterospecific pollen the higher the quality of the pollination service.
 
-Nevertheless, only a handful of studies have examined interspecific pollen transfer at the community level, and therefore we still understand little about how compeition for pollinators operates at this scale.
-All together, existing studies show that, as expected, the effective result of mutualistic interactions is, in most cases, one of facilitation. 
+Only a handful of studies have examined interspecific pollen transfer at the community level, and therefore we still understand little about how compeition for pollinators operates at this scale. 
+All together, existing studies at the community scale show that, as expected, the effective result of mutualistic interactions is, in most cases, one of facilitation. 
 Importantly, they also show a large variability in this result—both across species and across communities. 
@@
 
-Understanding what makes species and communities different is important not only because of its ecological and evolutionary implications. 
-It is also important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. 
-Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree.
-The extent to which species degree affects the benefit is called *mutualistic trade-off*. 
-This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
-At the same time it is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
-Although, the mutualistic trade-off has been shown to play a determining role on the stability and diversity of mutualistic communities, empirical evidence is scarce, to say the least.
+One of the most intuitive drivers of this variability, and therefore widely used in theoretical models of mutualism to account for the neggative effects of mutualism is the species degree---the number of mutualistic partners.
+It is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
+Recent empirical evidence suggest that other factors might also play an important role shaping the competition for pollination. 
+For instance, species with original traits (far from the community centroid) have been shown to generally have fewer interaction partners. 
+If evolutionary specialisation occur by changing traits to focus on fewer but better partners, we should expect a reduction of competition for pollination in species with original traits. 
+Similarly, it might also be the case that density is the dominant force driving pollen transfer. 
+Abundant species might experience a dilution of the available pollinators but might also comprise a greater component of the pollen source pool being transported by pollinators.  
+In this case a potential reduction in the quantity of pollination could be compensated by an increase in the quality of pollination.
 
@@
 Previous studies focus on the final picture of interspecific pollen transfer that is obtained by examining the pollen deposited on flower stigmas. 
-However, teasing appart the competition for pollinators also requires data that describes the structure of the interactions and the pollen flows that ocurr within it, while accounting for the traits of the species that integrate the community.
+However, as we have described, teasing appart competition for pollinators also requires data that describes the structure of the interactions and the pollen flows that ocurr within it, while accounting for the traits of the species that integrate the community.
 Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas.
-Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
-Second, we investigate wether there is a relationship between this gain and a suite of variables that describe both the role of the plant species and the ecological context. 
-Here, we pay special attention to the role of species degree because of its ramifications to theoretical ecology. 
-At the same time, we examine wether the plant role and ecological context is best infered from dynamics occurring at the community level, or wether it can be well approximated using information available from all sites in which a species ocurr.
-Third, and finaly, we explore how plant species differ on the extent to which competition for pollinators shapes facilitation.
 
 ## Methods
+First, we estimate the gain on pollen that can be attributed to the mutualistic interactions. 
+Second, we investigate wether there is a relationship between this gain and a a suite of variables that together describe the role of the plant species and the ecological context. 
+Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.
+**TODO: Mini conclusion here**
 

### 2018-07-27 paper/manuscript.Rmd
Rewrite intro with better story

@@
 Plants often ocurr in communities in which multiple competitive interactions operate simultaneusly and lead to emergent phenomena not observed at smaller scales.
-Here, we explore the signatures competition for pollinators in diverse natural communities, where empirical data is more scarce.
 
-At the community scale, competition for pollination might arrise from changes in the quantity and quality of pollination. 
-Quantity is mainly affected by competition for visits, where plants with more atractive flowers reduce the number of visits for those less atractive and therefore they may experience a reduction in the amount of conspecific pollen received.
-Quality is mainly affected by a more subtle but perhaps more important mechanism—interspecific pollen transfer, where even receiving a visit might not translate into net facilitation. 
-This is so because focal plant might receive pollen from a different species, or conversely pollen from the focal plant might be lost to different species. 
-Generally speaking the larger the proportion of conspecific relative to heterospecific pollen the higher the quality of the pollination service.
+The most obvious ecological factor influencing the cost of sharing pollinators is the species degree---the number of interaction partners. 
+The extent to which species degree affects the benefit is called mutualistic trade-off. 
+This trade-off is fundamental to the way we model and mathematically represent mutualistic systems because it considerably simplifies the mathematical treatment of competition for pollinators. 
+Furthermore the mutualistic trade-off has been shown to play a determining role on the stability and diversity of mutualistic communities. 
+Yet, empirical evidence of the trade-off at the community scale is scarce, to say the least.
 
-Only a handful of studies have examined interspecific pollen transfer at the community level, and therefore we still understand little about how compeition for pollinators operates at this scale. 
-All together, existing studies at the community scale show that, as expected, the effective result of mutualistic interactions is, in most cases, one of facilitation. 
-Importantly, they also show a large variability in this result—both across species and across communities. 
-However, the driving factors behind this variability are currently not understood.
+Although the relationship between degree and the costs of the pollination service is intuitive, elucidating the magnitude of the trade-off at the community scale has been elusive because multiple other factors like traits, abundance, and the share of the pollen pool lmight be involved.
+For instance, recent empirical evidence suggest that species with original traits (far from the community centroid) generally have fewer interaction partners. 
+This evidence is aligned with the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
+If evolutionary specialisation occur by changing traits to focus on fewer but better partners, we should expect a reduction of competition for pollination in species with original traits. 
+Alternatively, it might also be the case that density is the dominant force driving pollen transfer. 
+Abundant species might experience a dilution of the available pollinators but might also comprise a greater component of the pollen source pool being transported by pollinators.  
+In this case, a potential reduction in the quantity of pollination could be compensated by an increase in the quality of pollination.
 
-One of the most intuitive drivers of this variability, and therefore widely used in theoretical models of mutualism to account for the neggative effects of mutualism is the species degree---the number of mutualistic partners.
-It is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
-Recent empirical evidence suggest that other factors might also play an important role shaping the competition for pollination. 
-For instance, species with original traits (far from the community centroid) have been shown to generally have fewer interaction partners. 
-If evolutionary specialisation occur by changing traits to focus on fewer but better partners, we should expect a reduction of competition for pollination in species with original traits. 
-Similarly, it might also be the case that density is the dominant force driving pollen transfer. 
-Abundant species might experience a dilution of the available pollinators but might also comprise a greater component of the pollen source pool being transported by pollinators.  
-In this case a potential reduction in the quantity of pollination could be compensated by an increase in the quality of pollination.
-
-Elucidating how the mechanisms and drivers of facilitation scales to the community level and its theoretical concequences has been elusive in part because of the large amounts of data required.
-Previous studies focus on the final picture of interspecific pollen transfer that is obtained by examining the pollen deposited on flower stigmas. 
-However, as we have described, teasing appart competition for pollinators also requires data that describes the structure of the interactions and the pollen flows that ocurr within it, while accounting for the traits of the species that integrate the community.
-Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas.
-
-## Methods
-First, we estimate the gain on pollen that can be attributed to the mutualistic interactions. 
-Second, we investigate wether there is a relationship between this gain and a a suite of variables that together describe the role of the plant species and the ecological context. 
+Here, we explore the signature of the mutualistic trade-off in diverse natural communities. 
+To tease appart the multiple factors that operate at the community scale we use data that describes both the structure of the interactions and the pollen flows that ocurr within it, all while accounting for the traits of the species that integrate the community.
+Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
+Second, we investigate wether there is a relationship between this gain and the species degree, trait originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context.
 Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.
@@
 ### Data collection
+# Methods
 

### 2018-07-27 paper/manuscript.Rmd
Simplify degree even more in introduction

@@
 
-The most obvious ecological factor influencing the cost of sharing pollinators is the species degree---the number of interaction partners. 
-The extent to which species degree affects the benefit is called mutualistic trade-off. 
-This trade-off is fundamental to the way we model and mathematically represent mutualistic systems because it considerably simplifies the mathematical treatment of competition for pollinators. 
-Furthermore the mutualistic trade-off has been shown to play a determining role on the stability and diversity of mutualistic communities. 
-Yet, empirical evidence of the trade-off at the community scale is scarce, to say the least.
-
-Although the relationship between degree and the costs of the pollination service is intuitive, elucidating the magnitude of the trade-off at the community scale has been elusive because multiple other factors like traits, abundance, and the share of the pollen pool lmight be involved.
+Perhaps the most obvious ecological factor influencing the cost of sharing pollinators is the species degree---the number of interaction partners. 
+Yet, evidence at the community scale of **the mutualistic trade-off**---the extent to which species degree affects the benefit---is scarce, to say the least. 
+Furthermore, although the relationship between degree and the costs of the pollination service is relatively intuitive, elucidating the magnitude of the trade-off at the community scale has been elusive because multiple other factors like traits, abundance, and the share of the pollen pool lmight be involved.
 For instance, recent empirical evidence suggest that species with original traits (far from the community centroid) generally have fewer interaction partners. 

### 2018-07-27 paper/manuscript.Rmd
Tentative author affiliation

@@
 title: "The pollination trade-off"
-author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
+author: "Fernando Cagua^1^, Hugo Marrero^2^, Jason Tylianakis^1^, Daniel Stouffer^1^"
 #bibliography: references.bib
@@
 \doublespacing
+
+^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand
+
+^2^ Hugo's address
+
+**Author for correspondence:** E.
+Fernando Cagua (efc29@uclive.ac.nz) - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
 

### 2018-07-27 paper/manuscript.Rmd
Specify hetero and conspecific pollen in the intro

@@
 Yet, evidence at the community scale of **the mutualistic trade-off**---the extent to which species degree affects the benefit---is scarce, to say the least. 
-Furthermore, although the relationship between degree and the costs of the pollination service is relatively intuitive, elucidating the magnitude of the trade-off at the community scale has been elusive because multiple other factors like traits, abundance, and the share of the pollen pool lmight be involved.
+Furthermore, although the relationship between degree and the costs of the pollination service is relatively intuitive, elucidating the magnitude of the trade-off at the community scale has been elusive because multiple other factors like traits, abundance, and the share of the pollen pool might be involved.
 For instance, recent empirical evidence suggest that species with original traits (far from the community centroid) generally have fewer interaction partners. 
@@
 Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
-Second, we investigate wether there is a relationship between this gain and the species degree, trait originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context.
+Second, we investigate wether there is a relationship between this gain (of both conspecific and heterospecific pollen and by extension the quantity and quality of pollination) and the species degree, trait originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context.
 Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators. 
+We hypothezise that XX??
 **TODO: Mini conclusion here**
@@
 
+Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas.
 We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas. 

### 2018-07-27 paper/manuscript.Rmd
Intro to methods

@@
 
+Elucidating how the mechanisms and drivers of facilitation scales to the community level and its theoretical concequences has been elusive in part because of the large amounts of data required.
+Previous studies focus on the final picture of interspecific pollen transfer that is obtained by examining the pollen deposited on flower stigmas. 
+However, as we have described, teasing appart competition for pollinators also requires data that describes the structure of the interactions and the pollen flows that ocurr within it, while accounting for the traits of the species that integrate the community.
 Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas.

### 2018-07-29 paper/manuscript.Rmd
remove community stuff and add methods for traits and quality/quantity

@@
 
-## Abstract
+\clearpage
+
+# Abstract
 
 TBC
+
+\clearpage
 
@@
 Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
-Second, we investigate wether there is a relationship between this gain (of both conspecific and heterospecific pollen and by extension the quantity and quality of pollination) and the species degree, trait originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context.
+Second, we investigate wether there is a relationship between this gain (of both conspecific and heterospecific pollen and by extension the quantity and quality of pollination) and the species degree, functional originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context.
 Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators. 
@@
 
-### Data collection
 # Methods
@@
 Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas.
+
+## Data collection
+
 We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas. 
@@
 
-### Data analysis
+## Data analysis
 
@@
 
-Our main aim was to examine the extent to which the pollination service was influenced by the number of pollination partners while accounting for other metrics that describe the plant's pollination niche and community composition.
-To do so, we fitted four sets of linear mixed models [using the R package `nlme 3.1-131`, @nlme2017] which differed on whether the pollen deposited was conspecific or heterospecific and on wether independent variables were calculated across communities or independently within each community.
-In all set of models, our response variable was the difference between pollen density (pollen counts per stigma) between open and bagged flowers. 
-All together the results from each model set—and the relationship between them—provide with two important pieces of information. 
-First,  they provide indication of both the quantity and quality of animal pollination, and the potential trade-off between these two. 
-Second, it allowed us to examine wether indeed community level information is necessary to explain the observed patterms or whether less granular data is sufficient.
+Second, we examine wether there is a relationship between this gain and several ecological variables that can affect the mutualistic trade-off.
+To do so, we fitted two sets of linear mixed models [using the R package `nlme 3.1-131`, @nlme2017] which differed on whether the pollen deposited was conspecific or heterospecific.
+In both set of models, our response variable was the difference between pollen density (pollen counts per stigma) between open and bagged flowers. 
+Both model sets were based on the same one hundred bootstrap resamples of the deposition data.
 
-All model sets were based on the same one hundred bootstrap resamples of the deposition data. 
 We used bootstrap resampling because, as open and bagged flowers were not paired, this allowed us to directly model the *gain* in pollen density rather than density itself. 
@@
 In each replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
-We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-logtransformed-or-not) and \@ref(S-fig:fig-deposition-gain-logtransformed-or-not)).
+We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-logtransformed-or-not) and \@ref(S-fig:fig-deposition-gain-logtransformed-or-not)), this generally offered better results that a generalised linear model with poisson (or quasiposson) error structure.
 Finally, we calculated the difference between the pollen density among treatmemts. 
@@
 
-As predictors, we included the species/degree (number of animal partners) as well as other factors that could influence the trade-off. 
-Specifically, we included the plants' relative abundance and the temporal niche overlap. 
-To calculate the plant's relative abbundance we simply aggregated the flower counts over the study period—either across communities of for each community depending on the model set. 
+As predictors, we included species degree, the species' functional originality, the plant relative abbundance, and the plant species' share on the pollen pool. 
+Species degree was calculated from combining the quantitative and qualitative visitation networks and corresponds to the number of animal species that were observed to visit the plant species in the community where it was sampled.
+Functional originality is defined as the distance of a species from the community trait average--the centroid of functional space of the community [LEGENDGRE; @coux_linking_2016-1]. 
+Specifically, we recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perenial), flower coloration, and whether the species is native in the study region or not.
+As phenology has been shown to be a key mechanisms of niche diferentiation among plants, we also included the plant abundance in each of the survey months (November to March) as an additional trait in our analysis.
+This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits. 
+All traits were scaled to have a mean of zero and a standard deviation of one prior to calculating the centroid of the functional space. 
+The species-specific functional coordinates were calculated using the R package `FD 1.0-12` [@laliberte_distance-based_2010]. 
+To calculate the plant's relative abbundance we simply aggregated the flower counts for each plant species in the community.
 As with the deposition data, we found that log-transforming the abundance counts drastically improved normality (Figure \@ref(S-fig:fig-abundance-logtransformed-or-not)). 
-We then the log-transformed abundance counts for each month between November 2010 and March 2011 to calculate the temporal niche overlap between plants. 
-Specifically, we used the Pianka's niche overlap index [@Pianka1973; `spaa 0.2.2` R package @Zhang2016] which calculates an overlap index for each pair of species—again, across and within  communities depending on the model set.
-To calculate an overlap metric per species, we simply averaged the pairwise indices for a species. 
+Finally the species' share of the pollen pool was calculated as the proportion of pollen of that species in the pollen counts being carried by pollinators from the community. 
 To faciliate comparison across model estimates, we scaled all independent variables to have a mean of zero and a standard deviation of one.
@@
 Instead, in all model sets, we obtained the estimates for all the fixed effects we considered and then evaluated their relevance by examining their distribution. 
+Nevertheless, because some of our independent variables might be colinear, we also looked at how the effect of each predictor changed when each of them were removed once at a time.
 
-We compared the performance of the within and across communities model sets using the root-mean-square error normalised by the interquartile range (NRMSE). 
-We tested the significance of this difference using a two sample paired Wilcoxon signed rank test for conspecific and heterospecific pollen models. 
-We chosed NRMSE because it provides an easily interpretable metric related to the quality of the predictions while being farily insensitive to sample size. 
-This inensitivity was desirable because the across communities models had often slightly larger sample sizes owing to the fact of some species not having all data necessary to calculate the independent variables at the community level.
+At the community scale, sharing mutualistic partners might induce competition for pollination mainly trough two mechanisms. 
+The first is competition for visits, where plants with more atractive flowers reduce the number of visits for those less atractive. 
+Competition for visits affects the *quantity* of the pollination service as it induces a reduction in the amount of conspecific pollen received by flowers. 
+The second, more subtle, mechanism is interspecific pollen transfer, where even receiving a visit might not translate into net facilitation. 
+Interspecific pollen transfer affects the *quality* of the pollination service because a focal plant might receive pollen from a different species, or conversely pollen from the focal plant might be lost to different species.
+Generally speaking the larger the proportion of conspecific relative to heterospecific pollen the higher the quality of the pollination service.
+
+The results from both model set—and the relationship between them—provide indication of both the quantity and quality of animal pollination, and the potential trade-off between these two.
 
@@
 
-## Results
+# Results
 

### 2018-07-29 paper/manuscript.Rmd
More methods. Remove extent of facilitation

@@
 Instead, in all model sets, we obtained the estimates for all the fixed effects we considered and then evaluated their relevance by examining their distribution. 
-Nevertheless, because some of our independent variables might be colinear, we also looked at how the effect of each predictor changed when each of them were removed once at a time.
+Nevertheless, because we expect some of our independent variables to be related to each other, we also looked at how the effect of each predictor changed when each of them were removed once at a time.
 
@@
 The results from both model set—and the relationship between them—provide indication of both the quantity and quality of animal pollination, and the potential trade-off between these two. 
-
-Finally, we focused on how the relationship between conspecific and heterospecific pollen gain. 
-First we examined wether the pollination trade-off was related to our explanatory variables. 
-To do so, we harnessed the results from the conspecific and heterospecific pollen models that performed best (across or within communities). 
-To examine the relationship between these model sets, we sampled 100 estimates from the distribution of coefficients in each set. 
+To examine the relationship between our explanatory variables and the quantity of pollination we simply examine the results of the models of conspecific pollen gain. 
+To examine the relationship with the quality of pollination, we sampled 100 estimates from the distribution of coefficients in each of the two model sets. 
 For each of the samples, we then calculated the difference between the gain in conspecific and heterospecific pollen that would be predicted assuming mean values for the random intercepts and the other predictors.
-
-Second, we calulated the the extent of facilitation. 
-For this purpose, as in @Tur2016a, we used the relationship between heterospecific and conspecific pollen. 
-We calculated an overal relationship by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair [we used the R package `smatr 3.4-3`, @Warton2012a].
-We followed a similar procedure to calculate a relationship per species but instead of fitting a SMA per model pair, we did so across the 100 models for each species independently.
+This allowed us to estimate the proportion between heterospecific and conspecific pollen gain which we use as a proxy of the quality of pollination.
 

### 2018-08-08 paper/manuscript.Rmd
Use appropiate heading levels
Add biblio

@@
 author: "Fernando Cagua^1^, Hugo Marrero^2^, Jason Tylianakis^1^, Daniel Stouffer^1^"
-#bibliography: references.bib
+bibliography: phd-bibliography/pollen-competition.bib
 csl: ecology-letters.csl
@@
 
-## Discussion
+# Discussion
 
@@
 
-## References
+# References

### 2018-08-08 paper/manuscript.Rmd
Add some refs

@@
 In a first sampling we counted all units of floral attraction taht were found in a 2 m wide strip.
-In a second sampling we counted and collected all floral visitors while walking at a pace of 10 m per minute [@Marrero2014; @Memmott1999].
-We constructed quantitative visitation networks using information about the floral visitors collected during abundance transects [@Marrero2014]. 
+In a second sampling we counted and collected all floral visitors while walking at a pace of 10 m per minute [@marrero_effect_2014; @memmott_structure_1999].
+We constructed quantitative visitation networks using information about the floral visitors collected during abundance transects [@marrero_effect_2014]. 
 In addition, we also constructed qualitative visitation networks during independent two hour observations of floral visits across each fragment.
-We estimated pollen transfer by examining the pollen loads present on the collected floral visitors [@Marrero2017]. 
+We estimated pollen transfer by examining the pollen loads present on the collected floral visitors [@marrero_exotic_2017]. 
 Where the pollen count on an individual was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 

### 2018-08-08 paper/manuscript.Rmd
Chacha in the discussion

@@
 
+Understanding what makes species and communities different is important not only because of its ecological and evolutionary implications. 
+It is also important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. 
+Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree.
+The extent to which species degree affects the benefit is called *mutualistic trade-off*. 
+This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
+At the same time it is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
+Although, the mutualistic trade-off has been shown to play a determining role on the stability and diversity of mutualistic communities, empirical evidence is scarce, to say the least.
+
+It is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
+
+At the community scale, understanding the costs of sharing mutualistic partners at the community scale is important not only because of its ecological and evolutionary implications.
+It is also important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems.
+Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners—the species degree.
+The extent to which species degree affects the benefit is called mutualistic trade-off. This approach,
+37 considerably simplifies the mathematical treatment of competition for pollinators. At the same time it is
+38 based on the intuitive rationale that a species that interacts with few species benefits strongly from each
+39 of them, whereas a species that interacts with a large number of species does so comparatively weakly.
+40 Although, the mutualistic trade-off has been shown to play a determining role on the stability and diversity
+41 of mutualistic communities, empirical evidence is scarce, to say the least.
+
+At the community scale other factors we would expect
+
+Here, we explore the signatures competition for pollinators in diverse natural communities, where empirical data is more scarce.
+
+Here we examine the signature, at the community scale, that sharing mutualistic partners has in the quality and quantity of pollination. 
+Although seeimgly a simple question, teasing appart the signature of this "trade-off" has been elusive in part because of the large amounts of data required. 
+Most studies that have examined competition for pollinators are based the pollen deposited on flower stigmas. 
+However
+
+All together, existing studies at the community scale show that, as expected, the effective result of sharing mutualistic partners, in most cases, one of facilitation. 
+We hipothezise that 
+Recent empirical evidence suggest that the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
+However, they also show a large variability in this result—both across species and across communities. 
+One of the most intuitive drivers of the variability in competition, and therefore widely used in theoretical models of mutualism to account for the neggative effects of mutualism, is the species degree---the number of mutualistic partners.
+It is based on the intuitive rationale 
+ that other factors might also play an important role shaping the competition for pollination.
+
+First, we estimate the gain on pollen that can be attributed to the mutualistic interactions. 
+Second, we investigate wether there is a relationship between this gain and a a suite of variables that together describe the role of the plant species and the ecological context. 
+Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.
+**TODO: Mini conclusion here**
+
 # References

### 2018-08-08 code/try-traits.R
White spaces

@@ -98,10 +98,9 @@ make_trait_matrices <- function(plant_traits, abu_frame, remove_na_traits = TRUE
     dplyr::mutate(site_name = "global") %>%
     dplyr::full_join(plant_traits, ., by = "plant_name") %>% 
     dplyr::mutate_at(dplyr::vars(dplyr::contains("2011"), dplyr::contains("2010")), scale) %>%
-    dplyr::mutate_at(dplyr::vars(dplyr::contains("2011"), dplyr::contains("2010")), as.numeric) %>% 
+    dplyr::mutate_at(dplyr::vars(dplyr::contains("2011"), dplyr::contains("2010")), as.numeric) %>%
     list(.)
-  # NEED TO SCALE THIS
-  
+
   community_and_global_traits <- list(community = per_community, 
        global = global)
   

### 2018-08-08 paper/manuscript.Rmd
Update refs

@@
 Where the pollen count on an individual was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 
-When the pollen count was above 2,000 grains, we clasified approx. 50% of pollen and total pollen counts were extrapollated [@Bosch2009]. 
+When the pollen count was above 2,000 grains, we clasified approx. 50% of pollen and total pollen counts were extrapollated [@bosch_plant-pollinator_2009]. 
 If more than 10 pollen grains from a plant species were identified, we assumed that pollination service between the plant and the pollinator existed. 
-Finally, we analised pollen deposition in a subset of the plant community [@Marrero2016]. 
+Finally, we analised pollen deposition in a subset of the plant community [@marrero_agricultural_2016]. 
 This subset comprised between three and nine of the most common entomophilus species that were flowering during the samplimg period while ensuring that the chosen species covered a wide range on a specialization-generalization gradient.
@@
 To do that, we compared the amount of conspecific pollen on stigmas from flowers open to animal pollination and that from flowers that were bagged, where only autogamus self-pollination ocurred.
-The difference between these two counts is not directly equivalent to the pollen deposited by animals because self-pollination is an adaptive trait [@Kalisz2003]. 
+The difference between these two counts is not directly equivalent to the pollen deposited by animals because self-pollination is an adaptive trait [@kalisz_benefits_2003]. 
 Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output.
@@
 Second, we examine wether there is a relationship between this gain and several ecological variables that can affect the mutualistic trade-off.
-To do so, we fitted two sets of linear mixed models [using the R package `nlme 3.1-131`, @nlme2017] which differed on whether the pollen deposited was conspecific or heterospecific.
+To do so, we fitted two sets of linear mixed models [using the R package `nlme 3.1-131`, @pinheiro_nlme_2018] which differed on whether the pollen deposited was conspecific or heterospecific.
 In both set of models, our response variable was the difference between pollen density (pollen counts per stigma) between open and bagged flowers. 

### 2018-08-17 paper/supp-info.Rmd
Use kable and fix supp info tables
Issue #5

@@
 Tests were performed at the species level (across communities).",
-    escape = FALSE)
+    escape = FALSE, 
+    booktabs = TRUE, 
+    linesep = c("")) %>%
+  kableExtra::kable_styling(font_size = 8)
 ```
@@
 drake::loadd(significant_gain_global, significant_gain_site, sites)
-glance_table(significant_gain_site) %>%
+table_frame <- glance_table(significant_gain_site) %>%
  dplyr::inner_join(sites, by = "site_name") %>%
@@
          `plant species` = recipient, 
-         `community` = site_name) %>%
-  knitr::kable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
+         `community` = site_name)
+
+seps <-dplyr::if_else(table_frame$`plant species` == 
+  dplyr::lag(table_frame$`plant species`), "", "\\addlinespace") %>%
+  na.omit()
+
+table_frame %>%
+  knitr::kable(
+    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
 Tests were performed at the community level.
-Only species present in more than one community are shown.")
+Only species present in more than one community are shown.",
+    escape = FALSE, 
+    booktabs = TRUE, 
+    linesep = seps, 
+    digits = 3) %>%
+  kableExtra::kable_styling(font_size = 8)
 ```
@@
   anova(test = "Chisq")  %>%
-  xtable::xtable(caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).
+  knitr::kable(
+    caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).
 Density were modelled using a quasipoisson distribution.
 The model suggests that self-pollination rates are species dependent but not across.',
-         label = 'tab:table-variation-across-sites')
+    booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8)
 ```

### 2018-08-17 paper/manuscript.Rmd
Include references from supp info

@@
   - \usepackage{xr}
-  - \externaldocument[S-]{supp_info}
+  - \externaldocument[S-]{supp-info}
 ---

### 2018-08-17 paper/manuscript.Rmd
Add extra references
Issue #12

@@
 Species degree was calculated from combining the quantitative and qualitative visitation networks and corresponds to the number of animal species that were observed to visit the plant species in the community where it was sampled.
-Functional originality is defined as the distance of a species from the community trait average--the centroid of functional space of the community [LEGENDGRE; @coux_linking_2016-1]. 
+Functional originality is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016-1].
 Specifically, we recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perenial), flower coloration, and whether the species is native in the study region or not.
@@
 All traits were scaled to have a mean of zero and a standard deviation of one prior to calculating the centroid of the functional space. 
-The species-specific functional coordinates were calculated using the R package `FD 1.0-12` [@laliberte_distance-based_2010]. 
+The species-specific functional coordinates were calculated using the R package `FD 1.0-12` [@laliberte_distance-based_2010; @laliberte_fd_2014]. 
 To calculate the plant's relative abbundance we simply aggregated the flower counts for each plant species in the community.

### 2018-08-17 paper/supp-info.Rmd
Fix figure of relative abundance
Close #13

@@
 
-```{r fig-abundance-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
+```{r fig-abundance-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been log transformed and scaled to have a mean of zero and a standard deviation of one."}
 drake::loadd(fig_abundance)
@@
   fig_abundance[[2]], 
-  fig_abundance[[2]],
+  fig_abundance[[1]],
   rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
@@
 drake::loadd(significant_gain_global, significant_gain_site, sites)
+
 glance_table(significant_gain_global) %>%
@@
 cowplot::plot_grid(plotlist = site_plots_conspecific, ncol = 3)
-
 ```

### 2018-08-19 paper/supp-info.Rmd
Move scatter plot community vs global to its own function
Issue #6

@@
 
-```{r fig-global-community-correlations, fig.height = 2.5, fig.cap = "Relationship between the model's independent variables calculated at the community level and at the study-wide level."}
-drake::loadd(plant_rel_abu, plant_pheno_overlap, degree, sites)
-
-ab <- plant_rel_abu %>%
-  dplyr::select(-abu) %>%
-  dplyr::rename(value = rab) %>%
-  dplyr::mutate(term = "rab")
-
-ph <- plant_pheno_overlap %>%
-  dplyr::rename(value = tov) %>%
-  dplyr::mutate(term = "tov")
-
-k <- degree %>%
-  dplyr::select(-kn) %>%
-  dplyr::rename(value = k) %>%
-  dplyr::mutate(term = "k")
-
-dplyr::bind_rows(ab, ph, k) %>%
-  dplyr::filter(var_trans == "log") %>%
-  tidyr::spread(scale, value) %>%
-  humanize(sites) %>%
-  ggplot(aes(x = community, y = global)) +
-  geom_smooth(method = "lm", colour = "black", size = 0.75) +
-  geom_hline(yintercept = 0, size = 0.25, linetype = 2) +
-  geom_vline(xintercept = 0, size = 0.25, linetype = 2) +
-  geom_point(shape = 21, size = 1) +
-  facet_wrap( ~ term, scales = "free") +
-  coord_equal() +
-  pub_theme()
+```{r fig-global-community-correlations, fig.height = 2, fig.cap = "Relationship between the model's independent variables calculated at the community level and at the study-wide level."}
+drake::readd(fig_community_global_scatter)
 ```

### 2018-08-19 code/fig_community_global_scatter.R

@@ -1,0 +1,39 @@
+
+# make figure that shows relationship between global and community variables
+
+make_fig_community_global_scatter <- function(plant_rel_abu, org_frame, degree, sites, pollen_contribution){
+  require(ggplot2)
+  
+  ab <- plant_rel_abu %>%
+    dplyr::select(-abu) %>%
+    dplyr::rename(value = rab) %>%
+    dplyr::mutate(term = "rab") 
+  
+  or <- org_frame %>%
+    dplyr::select(-originality) %>%
+    dplyr::rename(value = org) %>%
+    dplyr::mutate(term = "org")
+  
+  k <- degree %>%
+    dplyr::select(-kn) %>%
+    dplyr::rename(value = k) %>%
+    dplyr::mutate(term = "k")
+  
+  pc <- pollen_contribution %>%
+    dplyr::select(-grain) %>%
+    dplyr::rename(value = poc) %>%
+    dplyr::mutate(term = "poc")
+  
+  dplyr::bind_rows(ab, or, k, pc) %>%  
+    dplyr::filter(var_trans == "log") %>% 
+    tidyr::spread(scale, value) %>%
+    humanize(sites) %>%
+    ggplot(aes(x = community, y = global)) +
+    geom_smooth(method = "lm", colour = "black", size = 0.75) +
+    geom_hline(yintercept = 0, size = 0.25, linetype = 2) +
+    geom_vline(xintercept = 0, size = 0.25, linetype = 2) +
+    geom_point(shape = 21, size = 1) +
+    facet_wrap( ~ term, scales = "free", ncol = 4) +
+    coord_equal() +
+    pub_theme()
+}

### 2018-08-19 main.R

@@ -141,7 +141,8 @@ figure_plan <- drake::drake_plan(
   fig_proportion_vs_variables = make_fig_proportion_vs_variables(trade_off_predictions),
   fig_pollen_density = make_fig_pollen_density(dep_frame), 
   fig_pollen_density_diff = make_fig_pollen_density_diff(rep_1), 
-  fig_abundance = make_fig_abundance(plant_rel_abu, sites)
+  fig_abundance = make_fig_abundance(plant_rel_abu, sites), 
+  fig_community_global_scatter = make_fig_community_global_scatter(plant_rel_abu, org_frame, degree, sites, pollen_contribution)
 )
 
 # Reporting ---------------------------------------------------------------

### 2018-08-19 paper/supp-info.Rmd
All model results to its own function. Show only best models
Issue #6

@@
 
-```{r fig-model-results, fig.height = 3.5, fig.cap = "Model coefficients"}
-drake::loadd(tidied_fixed, sites)
-
-tidied_fixed %>%
-  dplyr::filter(term != "(Intercept)" , 
-         var_trans == 'log'
-         # scale == "community"
-         ) %>%
-  dplyr::group_by(pollen_category,scale, model, var_trans, term) %>%
-  dplyr::summarise(estimate = first(estimate)) %>%
-  dplyr::group_by() %>%
-  humanize() %>%
-  ggplot(aes(x = estimate, 
-             colour = pollen_category, 
-             fill = pollen_category)) +
-  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
-  stat_density(geom = 'area',
-               alpha = 0.15,
-               position = position_identity(),
-               draw_quantiles = c(0.5, 0.95, 0.05), 
-               trim = F, 
-               scale = "count",
-               bins = 15) +
-  pub_theme() +
-  facet_grid(scale ~ term, scales = "free_x", space = "free_x") +
-  scale_color_manual(values = c_scale()) +
-  scale_fill_manual(values = c_scale()) +
-  scale_x_continuous(breaks = seq(-2,2, by = 0.25)) + 
-  theme(legend.position = "top") +
-  labs(colour = "", fill = "")
+```{r fig-model-results, fig.height = 5, fig.cap = "Model coefficients"}
+drake::readd(fig_all_model_results)
 ```

### 2018-08-19 code/fig_all_model_results.R

@@ -1,0 +1,45 @@
+# drake::loadd(tidied_fixed, sites)
+# Make the figure that shows all results in one
+make_fig_all_model_results <- function(tidied_fixed, sites, model_formula_ranking){
+  require(ggplot2)
+  # only keep models that make up to 95% of the evidence
+  best_models <- model_formula_ranking$by_model_set %>%
+    dplyr::group_by(scale, pollen_category) %>%
+    dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC), 
+                  weights = get_weights(likelyhood)) %>% 
+    dplyr::arrange(delta_AIC) %>% 
+    dplyr::mutate(cum_weight = cumsum(weights), 
+                  best_set = dplyr::lag(cum_weight) < 0.95, 
+                  best_set = dplyr::if_else(is.na(best_set), TRUE, best_set)) %>%
+    dplyr::filter(best_set) 
+  
+  best_model_formulas <- best_models %$%
+    fixed_formula %>%
+    unique()
+  
+  tidied_fixed %>%
+    dplyr::filter(term != "(Intercept)" , 
+                  var_trans == 'log', 
+                  fixed_formula %in% best_model_formulas
+                  # scale == "community"
+    ) %>%
+    dplyr::group_by(pollen_category,scale, model, var_trans, term, fixed_formula) %>%
+    dplyr::summarise(estimate = dplyr::first(estimate)) %>%
+    dplyr::group_by() %>%
+    humanize() %>%
+    ggplot(aes(x = estimate, 
+               colour = pollen_category, 
+               fill = pollen_category)) +
+    geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
+    stat_density(geom = 'area',
+                 alpha = 0.15,
+                 position = position_identity(),
+                 trim = F) +
+    pub_theme() +
+    facet_grid(fixed_formula   + scale ~ term, scales = "free_x", space = "free_x") +
+    scale_color_manual(values = c_scale()) +
+    scale_fill_manual(values = c_scale()) +
+    scale_x_continuous(breaks = seq(-2,2, by = 0.25)) + 
+    theme(legend.position = "top") +
+    labs(colour = "", fill = "")
+}

### 2018-08-19 main.R

@@ -103,6 +103,10 @@ glanced_fixed_models <- fixed_models %>%
 tidied_fixed_models <- fixed_models %>%
   drake::gather_plan(., gather = "tidy_fixed_models", target = "tidied_fixed")
 
+aic_plan <- drake::drake_plan(
+  model_formula_ranking = get_best_fixed_model_formula(glanced_fixed)
+)
+
 model_corr <- fixed_models %>%
   drake::gather_plan(., gather = "get_model_correlations", target = "model_correlations")
 
@@ -142,6 +146,7 @@ figure_plan <- drake::drake_plan(
   fig_pollen_density = make_fig_pollen_density(dep_frame), 
   fig_pollen_density_diff = make_fig_pollen_density_diff(rep_1), 
   fig_abundance = make_fig_abundance(plant_rel_abu, sites), 
+  fig_all_model_results = make_fig_all_model_results(tidied_fixed, sites, model_formula_ranking), 
   fig_community_global_scatter = make_fig_community_global_scatter(plant_rel_abu, org_frame, degree, sites, pollen_contribution)
 )
 
@@ -162,6 +167,7 @@ project_plan <- rbind(
   imputation_plan,
   boot_replicates,
   model_plans,
+  aic_plan,
   basic_analyses_plan,
   figure_plan,
   reporting_plan

### 2018-08-19 paper/supp-info.Rmd
Plots of pollen per species or community not necessary

@@
 
-```{r fig-conspecific-per-site, eval = FALSE, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities.
-Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
-drake::loadd(dep_frame, sites)
-library(ggplot2)
-site_plots_conspecific <- dep_frame %>%
-  dplyr::filter(pollen_category == 'conspecific') %>%
- dplyr::inner_join(sites, by = 'site_name') %>%
-  dplyr::mutate(recipient_short = shorten_sp_name(recipient)) %>%
-  dplyr::mutate(pollen_category = paste(pollen_category, "pollen"), 
-         treatment = dplyr::if_else(treatment == 'closed', 'bagged', treatment)) %>% 
-  plyr::dlply('site_name', function(x){
-    x %>%
-      ggplot(aes(y = pollen_density + 1, x = recipient_short,
-                 fill = treatment)) +
-      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
-      scale_y_log10(breaks = c(10,100,1000)) +
-      coord_flip() + 
-      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
-      pub_theme() +
-      xlab(NULL) +
-      ylab('pollen density') +
-      scale_fill_manual(values = c_scale())
-  })
-
-legend <- cowplot::get_legend(site_plots_conspecific[[1]])
-
-site_plots_conspecific <- site_plots_conspecific %>%
-  plyr::llply(function(x) {
-    x + theme(legend.position = 'none', 
-              title = element_text(size = 6))
-  })
-
-site_plots_conspecific <- rlist::list.append(site_plots_conspecific, legend)
-
-cowplot::plot_grid(plotlist = site_plots_conspecific, ncol = 3)
-```
-
-```{r fig-conspecific-per-plant, eval = FALSE, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species.
-Only species present in more than onse site are shown.
-Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio; A, and R indicate that the community corresponded to an agricultural or reserve site respectively."}
-drake::loadd(dep_frame, sites)
-plant_plots_conspecific <- dep_frame %>%
-  dplyr::filter(pollen_category == 'conspecific') %>%
- dplyr::inner_join(sites, by = 'site_name') %>%
-  dplyr::mutate(recipient_short = shorten_sp_name(recipient)) %>%
-  dplyr::mutate(pollen_category = paste(pollen_category, "pollen"), 
-         treatment = dplyr::if_else(treatment == 'closed', 'bagged', treatment)) %>%
-  dplyr::group_by(recipient) %>%
-  dplyr::mutate(n_sites = dplyr::n_distinct(site_name), 
-         site_name = `str_sub<-`(site_name, 1, 3, value = ''), 
-         site_name = str_replace_all(site_name, '_', ' - ')) %>%
-  dplyr::group_by() %>%
-  dplyr::filter(n_sites >= 2) %>%
-  plyr::dlply('recipient', function(x){
-    x %>%
-      ggplot(aes(y = pollen_density + 1, x = site_name,
-                 fill = treatment)) +
-      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
-      scale_y_log10(breaks = c(10,100,1000)) +
-      coord_flip() +
-      ggtitle(paste(x$recipient[1])) +
-      pub_theme() +
-      xlab(NULL) +
-      ylab('pollen density') +
-      scale_fill_manual(values = c_scale())
-  })
-
-legend <- cowplot::get_legend(plant_plots_conspecific[[1]])
-
-plant_plots_conspecific <- plant_plots_conspecific %>%
-  plyr::llply(function(x) {
-    x + theme(legend.position = 'none',
-              title = element_text(size = 6))
-  })
-
-plant_plots_conspecific <- rlist::list.append(plant_plots_conspecific, legend)
-
-cowplot::plot_grid(plotlist = plant_plots_conspecific, ncol = 3)
-```
-
 ```{r fig-global-community-correlations, fig.height = 2, fig.cap = "Relationship between the model's independent variables calculated at the community level and at the study-wide level."}

### 2018-08-19 main.R
Plant pheno overlap is not necessary anymore

@@ -27,7 +27,7 @@ format_data_plan <- drake::drake_plan(
   dep_frame = extract_dep_frame(armonised_data),
   abu_frame = extract_abu_frame(armonised_data),
   plant_rel_abu = calculate_relative_abundance(abu_frame, dep_frame),
-  plant_pheno_overlap = calculate_phenology_overlap(abu_frame, dep_frame),
+  # plant_pheno_overlap = calculate_phenology_overlap(abu_frame, dep_frame),
   vis_frame = extract_vis_frame(armonised_data),
   degree = get_degree(vis_frame, dep_frame), 
   tra_frame = extract_tra_frame(armonised_data), 

### 2018-08-22 paper/supp-info.Rmd
Move model results for the end of the supp
Close #6

@@
 
-```{r fig-model-results, fig.height = 5, fig.cap = "Model coefficients"}
-drake::readd(fig_all_model_results)
-```
-
-```{r fig-random-intercepts, eval = F, fig.height= 3, fig.cap = "Random effect intercepts"}
-drake::loadd(tidied_fixed, sites)
-
-tidied_fixed %>%
- tidyr::separate("level", c("site_name", "plant_name"), sep = "/", remove = F) %>%
-  dplyr::filter(term == "(Intercept)" ,
-         var_trans == 'log',
-         scale == "community", 
-         pollen_category == 'heterospecific'
-         ) %>%
-  humanize(sites) %>%
-  ggplot(aes(x = estimate, colour = plant_name, group = level)) +
-  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
-  geom_freqpoly(size = 0.25) +
-  facet_grid(locality_name + fragment ~ land_use) +
-  pub_theme() +
-  theme(legend.position = 'none')
-```
-
 ```{r eval = FALSE, table-aic-random-models, results= 'asis'}
@@
          label = "tab:table-global-vs-community-models")
+```{r fig-model-results, fig.height = 3.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
+Only results for the models with the most parsimonous fixed effects.
+"}
+drake::readd(fig_all_model_results)
 ```

### 2018-08-22 paper/supp-info.Rmd
Remove comparison community and imputed models

@@
 
-```{r table-global-vs-community-models, results = 'asis'}
-drake::loadd(wilcox_glo_com)
-
-wilcox_glo_com %>%
-  dplyr::filter(quality %in% c("rmse", "sigma", "r2c", "o2", "nrmse"),
-         var_trans == "log") %>%
-  dplyr::select(quality, pollen_category, min_scale, estimate, p.value) %>%
-  dplyr::rename(`model metric` = quality,
-         `pollen type` = pollen_category, 
-         `best model set` = min_scale,
-         `shift estimate` = estimate, 
-         `p value` = p.value) %>% 
-  xtable::xtable(digits = -1, caption = "Results of two sample paired Wilcoxon signed rank test comparing different model quality metrics of the model sets using predictors computed across or within communities.
-Metrics are the root mean square error (rmse), the residual standard deviation (sigma), the conditional r-squared approximation as proposed by Nakagawa and Schielzeth (2013), the omega-squared value as suggested by Xu (2003), and the normalised root-mean-square error of the model sets constructed using predictors computed at the community or study level.",
-         label = "tab:table-global-vs-community-models")
 ```{r fig-model-results, fig.height = 3.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.

### 2018-08-22 paper/supp-info.Rmd
Add variable importance table
Issue #5

@@
 
+```{r table-variable-importance, results='asis'}
+drake::loadd(model_formula_ranking)
+
+# get the terms in the models
+terms <- model_formula_ranking$aggregated$fixed_formula %>%
+  stringr::str_remove("pollen_gain ~  ") %>%
+  stringr::str_split(stringr::fixed(" + ")) %>%
+  unlist() %>%
+  unique() 
+# remove the null model
+terms <- terms[terms != "1"]
+
+model_weights <- model_formula_ranking$by_model_set %>%
+  dplyr::filter(scale == "community") %>%
+  dplyr::group_by(pollen_category) %>%
+  dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
+                weight = get_weights(likelyhood))
+
+crosses <- purrr::cross2(terms, c("conspecific", "heterospecific"))
+crosses %>%
+  purrr::map(~model_weights$weight[stringr::str_detect(model_weights$fixed_formula, .[[1]]) & model_weights$pollen_category == .[[2]]]) %>%
+  purrr::map(sum) %>%
+  purrr::map2_df(crosses, 
+              ~ dplyr::data_frame(
+                var = .y[[1]],
+                pollen_category = .y[[2]], 
+                importance = .x)
+              ) %>%
+  dplyr::mutate(importance = round(importance, digits = 3)) %>%
+  dplyr::rename(term = var) %>%
+  humanize() %>%
+  tidyr::spread(pollen_category, importance) %>%
+  dplyr::arrange(dplyr::desc(conspecific), heterospecific) %>%
+  dplyr::rename(`fixed effect`= term, 
+                `conspecific pollen` = conspecific, 
+                `heterospecific pollen` = heterospecific) %>%
+  knitr::kable(caption = "Relative variable impotance of the four vaariables included as fixed effects.
+Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{tab:table-aic-fixed-models}) of each candidate model set that includes the variable.",
+               booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::add_header_above(c(" ", "variable importance" = 2))
+```
+
 ```{r fig-model-results, fig.height = 3.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.

### 2018-08-22 paper/supp-info.Rmd
AIC fixed models tables
Issue #5

@@
 contingency_table[1:nrow(summ)] <- summ$delta_AIC
+```{r table-aic-fixed-models, results= 'asis'}
+drake::loadd(model_formula_ranking)
 
@@
          label = 'tab:table-aic-random-models')
+model_formula_ranking$by_model_set %>% 
+  dplyr::filter(scale == "community") %>%
+  dplyr::mutate(delta_AIC = paste0(round(delta_AIC, 1), 
+                                  " [", 
+                                  round(delta_AIC_quantile_05, 1),
+                                  " ,", 
+                                  round(delta_AIC_quantile_95, 1),
+                                  "]")) %>% 
+  dplyr::group_by() %>%
+  humanize(formula_long = TRUE) %>% 
+  dplyr::mutate(fixed_formula = paste("~", fixed_formula)) %>%
+  dplyr::arrange(pollen_category, delta_AIC_rank) %>%
+  dplyr::select(pollen_category, fixed_formula, delta_AIC) %>%
+  dplyr::rename(`pollen type` = pollen_category, 
+                `fixed structure` = fixed_formula) %>%
+  knitr::kable(caption = paste('Comparison of the different fixed structures we considered.
+The table shows median delta AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data.
+The 5th and 95th percentile are shown inside square brackets."),
+               booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::column_spec(column = 1, bold=T) %>%
+  kableExtra::collapse_rows(columns = 1, latex_hline = "major", valign = "middle")
 ```

### 2018-08-22 paper/supp-info.Rmd
Finish migrating to kable in supp
Close #5

--- 2018-08-22 paper/supp-info.Rmd
@@
 
-```{r eval = FALSE, table-aic-random-models, results= 'asis'}
+```{r table-aic-random-models, results= 'asis'}
 drake::loadd(glanced_random, random_effects)
@@
 summ <- glanced_random %>%
-  dplyr::filter(var_trans == "log") %>%
+  dplyr::filter(var_trans == "log", 
+                scale == "community") %>%
   dplyr::group_by(pollen_category, scale, var_trans, model) %>%
@@
   dplyr::mutate_if(is.numeric, round, digits = 1) %>% 
-  dplyr::mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "], n = ", n), 
+  dplyr::mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "]"), 
          delta_AIC = dplyr::if_else(grepl("NA", delta_AIC), "---", delta_AIC)) %>%
@@
   dplyr::arrange(pollen_category, random_name, scale) %>%
-  dplyr::rename(`pollen category` = pollen_category, 
+  dplyr::rename(`pollen type` = pollen_category, 
          `random structure` = random_name)
 
-contingency_table <- xtabs( ~ `random structure` + `scale` + `pollen category` , data = summ) %>% ftable()
-
-# contingency_table <- summ %>%
-  # ftable.formula(`random structure` ~ `scale` + `pollen category`)
-
-contingency_table[1:nrow(summ)] <- summ$delta_AIC
-
-xtable::xtableFtable(contingency_table, method = "col.compact", 
-             caption = paste('Comparison of the different random structures we considered.
+summ %>%
+  dplyr::select(`pollen type`, `random structure`, delta_AIC) %>%
+  knitr::kable(caption = paste('Comparison of the different random structures we considered.
 The table shows median delta AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data.
@@
 Communities are defined by individual fragments but ignore the hierarchical arrangement of sampling sites."),
-         label = 'tab:table-aic-random-models')
+               booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::column_spec(column = 1, bold=T) %>%
+  kableExtra::collapse_rows(columns = 1, latex_hline = "major", valign = "middle")
+```
+
+```{r table-aic-fixed-models, results= 'asis'}
+drake::loadd(model_formula_ranking)
+
+model_formula_ranking$by_model_set %>% 
+  dplyr::filter(scale == "community") %>%
+  dplyr::mutate(delta_AIC = paste0(round(delta_AIC, 1), 
+                                  " [", 
+                                  round(delta_AIC_quantile_05, 1),
+                                  " ,", 
+                                  round(delta_AIC_quantile_95, 1),
+                                  "]")) %>% 
+  dplyr::group_by() %>%
+  humanize(formula_long = TRUE) %>% 
+  dplyr::mutate(fixed_formula = paste("~", fixed_formula)) %>%
+  dplyr::arrange(pollen_category, delta_AIC_rank) %>%
+  dplyr::select(pollen_category, fixed_formula, delta_AIC) %>%
+  dplyr::rename(`pollen type` = pollen_category, 
+                `fixed structure` = fixed_formula) %>%
+  knitr::kable(caption = paste('Comparison of the different fixed structures we considered.
+The table shows median delta AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data.
+The 5th and 95th percentile are shown inside square brackets."),
+               booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::column_spec(column = 1, bold=T) %>%
+  kableExtra::collapse_rows(columns = 1, latex_hline = "major", valign = "middle")
 ```

### 2018-08-24 paper/manuscript.Rmd
Add figures results models quantity and quality
Close #16

@@
 
-```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
+```{r fig-model-results-global, fig.height = 1.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
 Results are shown for models with explanatory var"}
-drake::readd(fig_model_results_global)
+drake::readd(fig_coefficient_averages)
 ```
 
+```{r fig-average-qual-quant, fig.height=2, fig.width=3.5, fig.cap="asd"}
+drake::readd(fig_average_qual_quant)
+```
 The gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 

### 2018-08-24 paper/supp-info.Rmd
Add figures results models quantity and quality
Close #16

@@
 drake::loadd(model_formula_ranking)
+```{r fig-model-results, fig.height = 3.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
+Only results for the models with the most parsimonous fixed effects.
+"}
+drake::readd(fig_all_model_results)
+```
 
@@
 model_weights <- model_formula_ranking$by_model_set %>%
-  dplyr::filter(scale == "community") %>%
   dplyr::group_by(pollen_category) %>%
@@
 ```
+```{r fig_effect_quant_qual, fig.height=3.5, fig.cap="asd"}
+drake::loadd(fig_effect_quant_qual)
 
@@
 drake::readd(fig_all_model_results)
+cowplot::plot_grid(
+ fig_effect_quant_qual[[1]], 
+ fig_effect_quant_qual[[2]],
+  labels = LETTERS[1:2], 
+  label_size = 8, ncol = 2)
 ```

### 2018-08-24 code/coefficient_averages.R

@@ -1,0 +1,29 @@
+get_coefficient_averages <- function(tidied_fixed, model_formula_ranking, N = 99){
+  model_weights <- model_formula_ranking$by_model_set %>%
+    dplyr::group_by(pollen_category, scale) %>%
+    dplyr::mutate(l = get_likelyhoods(delta_AIC_median), 
+                  w = get_weights(l)) %>% 
+    dplyr::select(pollen_category, scale, fixed_formula, w)
+    
+  1:N %>%
+    purrr::map_df(get_coeficient_estimate_sample, tidied_fixed, model_weights, N)
+  
+}
+
+get_coeficient_estimate_sample <- function(sample_n, tidied_fixed, model_weights, N){
+  # consider cases with zero
+  
+  tidied_fixed %>%
+    dplyr::filter(term != "(Intercept)") %>% 
+    dplyr::group_by(model, pollen_category, scale, fixed_formula, term) %>%
+    dplyr::summarise(estimate = unique(estimate)) %>% 
+    dplyr::group_by() %>% 
+    # complete cases. The estimate of the term for the models in which it wasn't present is zero
+    tidyr::complete(model, pollen_category, scale, fixed_formula, term, fill = list(estimate = 0)) %>% 
+    dplyr::inner_join(model_weights, 
+                      by = c("pollen_category", "scale", "fixed_formula")) %>% 
+    dplyr::group_by(pollen_category, scale, term) %>%
+    dplyr::sample_n(size = N, replace = T, weight = w) %>% 
+    # dplyr::summarise(estimate = weighted.mean(estimate, w)) %>%
+    dplyr::mutate(sample_n = sample_n)
+}

### 2018-08-24 code/fig_average_quant_qual.R

@@ -1,0 +1,53 @@
+make_fig_average_quant_qual <- function(coefficient_averages){
+  require(ggplot2)
+  
+  quant_qual <- coefficient_averages %>%
+    dplyr::group_by(scale, pollen_category, term, sample_n) %>%
+    dplyr::mutate(sample_n2 = 1:n()) %>% 
+    dplyr::select(pollen_category, term, sample_n, sample_n2, estimate) %>%
+    tidyr::spread(pollen_category, estimate) %>% 
+    dplyr::mutate(quantity = conspecific, 
+                  quality = conspecific - heterospecific) %>%
+    dplyr::select(scale, term, sample_n, quantity, quality) %>%
+    tidyr::gather("var", "estimate", quantity, quality) %>% 
+    dplyr::group_by(scale, term, sample_n, var) %>%
+    dplyr::summarise_at("estimate", mean) %>% 
+    dplyr::group_by(scale, term, var) %>%
+    dplyr::summarise_at("estimate", dplyr::funs(mean, quantile_05, quantile_95))
+  params <- list(
+    tile_width = 0.95,
+    scale_length = 5
+  )
+  params$scale = scales::brewer_pal(palette = "RdYlGn")(params$scale_length)
+
+  quant_qual %>%
+    dplyr::filter(scale == "community") %>%
+    dplyr::group_by() %>%
+    humanize() %>%
+   dplyr::mutate(label1 = round(mean, 3), 
+                 label2 = paste0("[", round(quantile_05, 3), ", ", round(quantile_95, 3), "]"), 
+                 var = forcats::fct_relevel(var, c("quantity", "quality")), 
+                 term = forcats::fct_relevel(term, c("degree", "abundance", "trait originality"))) %>%
+    ggplot(aes(x = term, y = var)) +
+    geom_tile(aes(fill = mean), 
+              width = params$tile_width, 
+              height = params$tile_width) +
+    geom_text(aes(label = label1), 
+              nudge_x = 0.15, 
+              size = 2.8) +
+    geom_text(aes(label = label2), 
+              nudge_x = -0.15, 
+              size = 2.5) +
+    scale_fill_gradient2(name = "mean\neffect", 
+                         high = params$scale[params$scale_length], 
+                         mid = params$scale[3],
+                         low = params$scale[1]) +
+    pub_theme() +
+    coord_flip() +
+   scale_y_discrete(position= "top", name = "") +
+   scale_x_discrete(name = "") +
[…]

### 2018-08-24 code/fig_coefficient_averages.R

@@ -1,0 +1,43 @@
+make_fig_coefficient_avarages <- function(coefficient_averages){
+  require(ggplot2)
+  require(ggridges)
+  coefficient_averages %>% 
+    dplyr::filter(scale == "community") %>%
+    dplyr::group_by(pollen_category, scale, term, sample_n) %>%
+    # dplyr::summarise(estimate = mean(estimate)) %>%
+    dplyr::group_by() %>%
+    humanize() %>%
+    dplyr::mutate(term = forcats::fct_relevel(term, c("abundance", "degree"), after = 2), 
+                  pollen_category = dplyr::if_else(pollen_category == "conspecific", 
+                                                   "conspecific pollen  ", 
+                                                   "heterospecific pollen")) %>%
+    ggplot(aes(x = estimate,
+               y = term,
+               colour = pollen_category, 
+               # vline_color = pollen_category, 
+               fill = pollen_category)) +
+    geom_vline(xintercept = 0, linetype = 1, size = 0.25, color = "grey75") +
+    geom_density_ridges(alpha = 0.25, 
+                        panel_scaling = T, 
+                        scale = 1.5, 
+                        quantile_lines = F, quantiles = 2, 
+                        vline_linetype = 1, 
+                        vline_size = 0.25, 
+                        rel_min_height = 0) +
+    # coord_flip() +
+    pub_theme() +
+    facet_grid(~ pollen_category, space = "free_x", scales = "free_x") +
+    scale_color_manual(values = c_scale()) +
+    scale_fill_manual(values = c_scale()) +
+    # scale_discrete_manual("vline_color", values = c_scale()) +
+    theme(legend.position = "none", 
+          legend.direction = "vertical",
+          panel.border = element_blank(), 
+          panel.grid.major.x = element_line(size = 0.25)) +
+    labs(colour = "", fill = "", x = "estimated effect on pollen gain", y = "")
+
+}
+
+c_scale_discrete <- function(x){
+  c_scale()[x]
+}

### 2018-08-24 code/fig_effect_quant_qual.R

@@ -1,0 +1,50 @@
+make_fig_effect_quant_qual <- function(summary_effects, model_formula_ranking){
+  require(ggplot2)
+  best_models <- model_formula_ranking$by_model_set %>%
+    dplyr::group_by(scale, pollen_category) %>%
+    dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC), 
+                  weights = get_weights(likelyhood)) %>% 
+    dplyr::arrange(delta_AIC) %>% 
+    dplyr::mutate(cum_weight = cumsum(weights), 
+                  best_set = dplyr::lag(cum_weight) < 0.95, 
+                  best_set = dplyr::if_else(is.na(best_set), TRUE, best_set)) %>%
+    dplyr::filter(scale == "community") 
+  
+  best_model_formulas <- best_models %$%
+    fixed_formula %>%
+    unique()
+  
+  agg_formulas <- model_formula_ranking$aggregated %>%
+    dplyr::mutate(len = stringr::str_length(fixed_formula)) %>%
+    humanize(formula_long = TRUE) %>%
+    dplyr::arrange(len, fixed_formula)
+  
+  params <- list(
+    tile_width = 0.9,
+    scale_length = 5
+  )
+  params$scale = scales::brewer_pal(palette = "RdBu")(params$scale_length)
+  
+  summary_effects %>%
+    dplyr::filter(scale == "community", 
+                  fixed_formula %in% best_model_formulas) %>%
+    tidyr::gather(key = "response", value = "value", quantity_median, quality_median) %>%
+    dplyr::group_by() %>%
+    humanize(formula_long = TRUE) %>% 
+    split(.$response) %>%
+    purrr::map(plot_for_one_response, agg_formulas, params)
+}
+
+plot_for_one_response <- function(x, agg_formulas, params){
+  x %>%
+    dplyr::inner_join(agg_formulas, by = "fixed_formula") %>%
+    dplyr::mutate(fixed_formula = forcats::fct_reorder(fixed_formula, len, .desc = FALSE)) %>%
+    ggplot(aes(y = fixed_formula, x = term)) + 
+    geom_tile(aes(fill = value), height = params$tile_width, width = params$tile_width) +
+    geom_text(aes(label = round(value, 2)), size = 2.5) +
+    scale_fill_gradient2(high = params$scale[params$scale_length], 
+                         low = params$scale[1]) +
+    pub_theme() +
+    coord_equal() +
+    theme(axis.text.x = element_text(angle = 60, hjust = 1))
+}

### 2018-08-24 code/get_summary_effects.R

@@ -1,0 +1,44 @@
+
+# calculate the effect that each term has on the quantity and quality of pollination
+get_summary_effects <- function(tidied_fixed){
+  tidied_fixed %>%
+    dplyr::filter(term != "(Intercept)") %>%
+    dplyr::group_by(pollen_category, scale, fixed_formula, term, model) %>%
+    dplyr::summarise(estimate = unique(estimate)) %>%
+    dplyr::group_by(pollen_category, scale, fixed_formula, term) %>%
+    dplyr::sample_n(size = 999, replace = TRUE) %>% 
+    dplyr::mutate(sample_n = 1:n()) %>% 
+    dplyr::select(-model) %>%
+    tidyr::spread(key = pollen_category, value = estimate) %>% 
+    dplyr::mutate(quantity = conspecific, 
+                  quality = conspecific - heterospecific) %>% 
+    dplyr::group_by(scale, fixed_formula, term) %>%
+    dplyr::summarise_at(dplyr::vars(quantity, quality), dplyr::funs(freq_t, parametric_t, median))
+}
+
+# see if the quantiles of a vector cross zero in a parametric way
+parametric_t <- function(x){
+  quant <- quantile(x, probs = c(0.05, 0.95))
+  if (0 > quant[1] & 0 < quant[2]) {
+    return(0)
+  } else if (0 < quant[1]) {
+    return(1)
+  } else {
+    return(-1)
+  }
+}
+
+# see if the mean is different to zero using a t-test
+freq_t <- function(x){
+  t1 <- t.test(x, alternative = "two.sided")
+  if (t1$p.value > 0.05) {
+    return(0)
+  } else {
+    t2 <- t.test(x, alternative = "greater")
+    if (t2$p.value < 0.05) {
+      return(1)
+    } else {
+      return(-1)
+    }
+  }
+}

### 2018-08-24 code/plotting.R

@@ -23,7 +23,7 @@ remove_legend <- function(x){
 #'
 #' @return
 #' 
-humanize <- function(x, sites = NA, random_effects = NA, formula_long = FALSE){
+humanize <- function(x, sites = NA, random_effects = NA, formula_long = FALSE, term_long = TRUE){
   if ('site_name' %in% names(x)) {
     x <- dplyr::inner_join(x, sites, by = 'site_name')
   }
@@ -31,11 +31,11 @@ humanize <- function(x, sites = NA, random_effects = NA, formula_long = FALSE){
     x <- x %>%
       dplyr::mutate(term = dplyr::case_when(
         grepl('org', term) ~ 'trait originality',
-        grepl('abn', term) ~ 'relative abundance',
-        grepl('rab', term) ~ 'relative abundance',
+        grepl('abn', term) ~ 'abundance',
+        grepl('rab', term) ~ 'abundance',
         grepl('deg', term) ~ 'degree',
         grepl('k', term) ~ 'degree',
-        grepl('poc', term) ~ 'share pollen pool',
+        grepl('poc', term) ~ 'share pollen',
         TRUE ~ term
       ))
   }

### 2018-08-24 main.R

@@ -116,7 +116,9 @@ het_con_linear_fit <- fixed_models %>%
 best_model_formula <- "pollen_gain ~  abn + poc + deg + org"
 
 fixed_summaries <- drake::drake_plan(
-  wilcox_glo_com = global_vs_community(glanced_fixed, model_formula = best_model_formula)
+  wilcox_glo_com = global_vs_community(glanced_fixed, model_formula = best_model_formula), 
+  summary_effects = get_summary_effects(tidied_fixed), 
+  coefficient_averages = get_coefficient_averages(tidied_fixed, model_formula_ranking, N = 99)
 )
 predictions <- drake::drake_plan(
   trade_off_predictions = trade_off_pred(
@@ -147,7 +149,10 @@ figure_plan <- drake::drake_plan(
   fig_pollen_density_diff = make_fig_pollen_density_diff(rep_1), 
   fig_abundance = make_fig_abundance(plant_rel_abu, sites), 
   fig_all_model_results = make_fig_all_model_results(tidied_fixed, sites, model_formula_ranking), 
-  fig_community_global_scatter = make_fig_community_global_scatter(plant_rel_abu, org_frame, degree, sites, pollen_contribution)
+  fig_community_global_scatter = make_fig_community_global_scatter(plant_rel_abu, org_frame, degree, sites, pollen_contribution),
+  fig_effect_quant_qual = make_fig_effect_quant_qual(summary_effects, model_formula_ranking), 
+  fig_coefficient_averages = make_fig_coefficient_avarages(coefficient_averages), 
+  fig_average_qual_quant = make_fig_average_quant_qual(coefficient_averages)
 )
 
 # Reporting ---------------------------------------------------------------

### 2018-08-24 paper/manuscript.Rmd
Table var importance to main text

@@
 After determining the best random structure, we then focused on the model's fixed structure where we fitted the fixed effect coefficients using maximum likelyhood. 
-Because our purpose was to perform inter-model comparisons across multiple data resamples, we did not perform model selection. 
-Instead, in all model sets, we obtained the estimates for all the fixed effects we considered and then evaluated their relevance by examining their distribution. 
-Nevertheless, because we expect some of our independent variables to be related to each other, we also looked at how the effect of each predictor changed when each of them were removed once at a time.
+In all model sets, we obtained the estimates for all the fixed effects we considered and then evaluated their relevance by examining their distribution. 
+Nevertheless, we obtained the calculated the relative importance of the explanatory variables by comparing the sum the Akaike weights of the models that include each variable. 
+In addition, because we expect some of our independent variables to be related to each other, we also looked at how the effect of each predictor changed when each of them were removed once at a time.
 
@@
 We found that the random structure that was best supported the data was consistently the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
+We also found that the models AIC story
+
+```{r table-variable-importance, results='asis'}
+drake::loadd(model_formula_ranking)
+
+# get the terms in the models
+terms <- model_formula_ranking$aggregated$fixed_formula %>%
+  stringr::str_remove("pollen_gain ~  ") %>%
+  stringr::str_split(stringr::fixed(" + ")) %>%
+  unlist() %>%
+  unique() 
+# remove the null model
+terms <- terms[terms != "1"]
+
+model_weights <- model_formula_ranking$by_model_set %>%
+  dplyr::filter(scale == "community") %>%
+  dplyr::group_by(pollen_category) %>%
+  dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
+                weight = get_weights(likelyhood))
+
+crosses <- purrr::cross2(terms, c("conspecific", "heterospecific"))
+crosses %>%
+  purrr::map(~model_weights$weight[stringr::str_detect(model_weights$fixed_formula, .[[1]]) & model_weights$pollen_category == .[[2]]]) %>%
+  purrr::map(sum) %>%
+  purrr::map2_df(crosses, 
+              ~ dplyr::data_frame(
+                var = .y[[1]],
+                pollen_category = .y[[2]], 
+                importance = .x)
+              ) %>%
+  dplyr::mutate(importance = round(importance, digits = 3)) %>%
+  dplyr::rename(term = var) %>%
+  humanize() %>%
+  tidyr::spread(pollen_category, importance) %>%
+  dplyr::arrange(dplyr::desc(conspecific), heterospecific) %>%
+  dplyr::rename(`fixed effect`= term, 
+                `conspecific pollen` = conspecific, 
+                `heterospecific pollen` = heterospecific) %>%
+  knitr::kable(caption = "Relative variable impotance of the four vaariables included as fixed effects.
+Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{tab:table-aic-fixed-models}) of each candidate model set that includes the variable.",
+               booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::add_header_above(c(" ", "variable importance" = 2))
+```
+
 When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better approximated by the model sets using predictors calculated across communities (Table \@ref(S-tab:table-global-vs-community-models)).
@@
 
-We found that the gain in conspecific pollen is negatively affected by the plants relative abbundance and to a smaller extent by the species' degree (Figure \@ref(fig:fig-model-results-global). 
+We found that the gain in conspecific pollen is negatively affected by the plants relative abbundance and to a smaller extent by the species' degree (Figure \@ref(fig:fig-model-results-global)). 
 The gain in heterospecific pollen was instead positively affected by degree and the plant's phenology overlap, but was also strongly negatively affected by the plant's relative abbundance.
@@
 ```
+
 The gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 
@@
 
-```{r fig-trade-off-predictions, fig.height= 2.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
+```{r fig-trade-off-predictions, fig.height= 2, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
 (A) Overall and species-level relationship.

### 2018-08-24 paper/supp-info.Rmd
Table var importance to main text

--- 2018-08-22 paper/supp-info.Rmd
@@
 
-```{r table-variable-importance, results='asis'}
-drake::loadd(model_formula_ranking)
-
-# get the terms in the models
-terms <- model_formula_ranking$aggregated$fixed_formula %>%
-  stringr::str_remove("pollen_gain ~  ") %>%
-  stringr::str_split(stringr::fixed(" + ")) %>%
-  unlist() %>%
-  unique() 
-# remove the null model
-terms <- terms[terms != "1"]
-
-model_weights <- model_formula_ranking$by_model_set %>%
-  dplyr::filter(scale == "community") %>%
-  dplyr::group_by(pollen_category) %>%
-  dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
-                weight = get_weights(likelyhood))
-
-crosses <- purrr::cross2(terms, c("conspecific", "heterospecific"))
-crosses %>%
-  purrr::map(~model_weights$weight[stringr::str_detect(model_weights$fixed_formula, .[[1]]) & model_weights$pollen_category == .[[2]]]) %>%
-  purrr::map(sum) %>%
-  purrr::map2_df(crosses, 
-              ~ dplyr::data_frame(
-                var = .y[[1]],
-                pollen_category = .y[[2]], 
-                importance = .x)
-              ) %>%
-  dplyr::mutate(importance = round(importance, digits = 3)) %>%
-  dplyr::rename(term = var) %>%
-  humanize() %>%
-  tidyr::spread(pollen_category, importance) %>%
-  dplyr::arrange(dplyr::desc(conspecific), heterospecific) %>%
-  dplyr::rename(`fixed effect`= term, 
-                `conspecific pollen` = conspecific, 
-                `heterospecific pollen` = heterospecific) %>%
-  knitr::kable(caption = "Relative variable impotance of the four vaariables included as fixed effects.
-Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{tab:table-aic-fixed-models}) of each candidate model set that includes the variable.",
-               booktabs = TRUE) %>%
-  kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::add_header_above(c(" ", "variable importance" = 2))
-```
-
 ```{r fig-model-results, fig.height = 3.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
@@
 
+```{r fig_effect_quant_qual, fig.height=3.5, fig.cap="asd"}
+drake::loadd(fig_effect_quant_qual)
+
+cowplot::plot_grid(
+ fig_effect_quant_qual[[1]], 
+ fig_effect_quant_qual[[2]],
+  labels = LETTERS[1:2], 
+  label_size = 8, ncol = 2)
+```
+
 # References

### 2018-08-26 code/fig_correlation.R
Figure of correlation between explanatory variables
Close #17

@@ -1,0 +1,39 @@
+ make_fig_correlation <- function(rep_1){
+   require(ggplot2)
+   
+   r <- rep_1 %>%
+     dplyr::group_by() %>%
+     dplyr::filter(scale == "community") %>%
+     dplyr::select(abn, poc, deg, org)
+   # tidyr::gather(key = "var", value = "value", abn, poc, deg, org) %>% 
+   
+   cols <- expand.grid(x = c("abn", "poc", "deg", "org"), y = c("abn", "poc", "deg", "org")) %>%
+     dplyr::mutate_all(as.character) %>%
+     dplyr::filter(x != y)
+   
+   pl <-  plyr::ddply(cols, c("x", "y"), function(x, r){
+     tibble::data_frame(
+       x_values = r[x$x][[1]], 
+       y_values = r[x$y][[1]])
+   }, r) %>% 
+     dplyr::rename(term = x) %>%
+     humanize() %>%
+     dplyr::rename(x = term, 
+                   term = y) %>%
+   humanize() %>%
+   dplyr::rename(y = term) 
+ 
+ cors <- pl %>%
+   dplyr::group_by(x, y) %>%
+   dplyr::summarise(cor = cor(x_values, y_values, use = "pairwise")) %>%
+   dplyr::mutate(cor = paste0("Cor: ", round(cor, 3)))
+ 
+ pl %>% 
+   ggplot(aes(x = x_values, y = y_values)) +
+   geom_point(shape = 21, size = 1) +
+   geom_smooth(method = "lm", colour = "black", size = 0.5, se = FALSE) +
+   geom_text(data = cors, aes(label = cor), x = -1.65, y = 2.5, size = 2.5) +
+   facet_grid(x ~ y) + 
+   pub_theme() +
+   labs(x = "", y = "")
+ }

### 2018-08-26 main.R

@@ -152,7 +152,8 @@ figure_plan <- drake::drake_plan(
   fig_community_global_scatter = make_fig_community_global_scatter(plant_rel_abu, org_frame, degree, sites, pollen_contribution),
   fig_effect_quant_qual = make_fig_effect_quant_qual(summary_effects, model_formula_ranking), 
   fig_coefficient_averages = make_fig_coefficient_avarages(coefficient_averages), 
-  fig_average_qual_quant = make_fig_average_quant_qual(coefficient_averages)
+  fig_average_qual_quant = make_fig_average_quant_qual(coefficient_averages), 
+  fig_correlation = make_fig_correlation(rep_1)
 )
 
 # Reporting ---------------------------------------------------------------

### 2018-08-26 paper/manuscript.Rmd
Variable importance goes to its own function

@@
 ```{r table-variable-importance, results='asis'}
-drake::loadd(model_formula_ranking)
+drake::loadd(variable_importance)
 
-# get the terms in the models
-terms <- model_formula_ranking$aggregated$fixed_formula %>%
-  stringr::str_remove("pollen_gain ~  ") %>%
-  stringr::str_split(stringr::fixed(" + ")) %>%
-  unlist() %>%
-  unique() 
-# remove the null model
-terms <- terms[terms != "1"]
-
-model_weights <- model_formula_ranking$by_model_set %>%
-  dplyr::filter(scale == "community") %>%
-  dplyr::group_by(pollen_category) %>%
-  dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
-                weight = get_weights(likelyhood))
-
-crosses <- purrr::cross2(terms, c("conspecific", "heterospecific"))
-crosses %>%
-  purrr::map(~model_weights$weight[stringr::str_detect(model_weights$fixed_formula, .[[1]]) & model_weights$pollen_category == .[[2]]]) %>%
-  purrr::map(sum) %>%
-  purrr::map2_df(crosses, 
-              ~ dplyr::data_frame(
-                var = .y[[1]],
-                pollen_category = .y[[2]], 
-                importance = .x)
-              ) %>%
-  dplyr::mutate(importance = round(importance, digits = 3)) %>%
-  dplyr::rename(term = var) %>%
-  humanize() %>%
-  tidyr::spread(pollen_category, importance) %>%
-  dplyr::arrange(dplyr::desc(conspecific), heterospecific) %>%
+variable_importance %>%
   dplyr::rename(`fixed effect`= term, 
@@
   knitr::kable(caption = "Relative variable impotance of the four vaariables included as fixed effects.
-Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{tab:table-aic-fixed-models}) of each candidate model set that includes the variable.",
+Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{S-tab:table-aic-fixed-models}) of each candidate model set that includes the variable.",
                booktabs = TRUE) %>%

### 2018-08-26 code/get_variable_importance.R

@@ -1,0 +1,33 @@
+get_variable_importance <- function(model_formula_ranking){
+  
+  # get the terms in the models
+  terms <- model_formula_ranking$aggregated$fixed_formula %>%
+    stringr::str_remove("pollen_gain ~  ") %>%
+    stringr::str_split(stringr::fixed(" + ")) %>%
+    unlist() %>%
+    unique() 
+  # remove the null model
+  terms <- terms[terms != "1"]
+  
+  model_weights <- model_formula_ranking$by_model_set %>%
+    dplyr::filter(scale == "community") %>%
+    dplyr::group_by(pollen_category) %>%
+    dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
+                  weight = get_weights(likelyhood))
+  
+  crosses <- purrr::cross2(terms, c("conspecific", "heterospecific"))
+  crosses %>%
+    purrr::map(~model_weights$weight[stringr::str_detect(model_weights$fixed_formula, .[[1]]) & model_weights$pollen_category == .[[2]]]) %>%
+    purrr::map(sum) %>%
+    purrr::map2_df(crosses, 
+                   ~ dplyr::data_frame(
+                     var = .y[[1]],
+                     pollen_category = .y[[2]], 
+                     importance = .x)
+    ) %>%
+    dplyr::mutate(importance = round(importance, digits = 3)) %>%
+    dplyr::rename(term = var) %>%
+    humanize() %>%
+    tidyr::spread(pollen_category, importance) %>%
+    dplyr::arrange(dplyr::desc(conspecific), heterospecific)
+}

### 2018-08-26 main.R

@@ -118,7 +118,8 @@ best_model_formula <- "pollen_gain ~  abn + poc + deg + org"
 fixed_summaries <- drake::drake_plan(
   wilcox_glo_com = global_vs_community(glanced_fixed, model_formula = best_model_formula), 
   summary_effects = get_summary_effects(tidied_fixed), 
-  coefficient_averages = get_coefficient_averages(tidied_fixed, model_formula_ranking, N = 99)
+  coefficient_averages = get_coefficient_averages(tidied_fixed, model_formula_ranking, N = 99), 
+  variable_importance = get_variable_importance(model_formula_ranking)
 )
 predictions <- drake::drake_plan(
   trade_off_predictions = trade_off_pred(

### 2018-08-26 paper/manuscript.Rmd
FIgure coefficient averages includes relative variable importance

@@
 
+```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
+Results are shown for models with explanatory var"}
+drake::readd(fig_coefficient_averages)
+```
+
 When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better approximated by the model sets using predictors calculated across communities (Table \@ref(S-tab:table-global-vs-community-models)).
@@
 The gain in heterospecific pollen was instead positively affected by degree and the plant's phenology overlap, but was also strongly negatively affected by the plant's relative abbundance.
-
-```{r fig-model-results-global, fig.height = 1.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
-Results are shown for models with explanatory var"}
-drake::readd(fig_coefficient_averages)
-```
 

### 2018-08-26 code/fig_coefficient_averages.R

@@ -1,7 +1,7 @@
-make_fig_coefficient_avarages <- function(coefficient_averages){
+make_fig_coefficient_avarages <- function(coefficient_averages, variable_importance){
   require(ggplot2)
   require(ggridges)
-  coefficient_averages %>% 
+  dist <- coefficient_averages %>% 
     dplyr::filter(scale == "community") %>%
     dplyr::group_by(pollen_category, scale, term, sample_n) %>%
     # dplyr::summarise(estimate = mean(estimate)) %>%
@@ -11,6 +11,32 @@ make_fig_coefficient_avarages <- function(coefficient_averages){
                   pollen_category = dplyr::if_else(pollen_category == "conspecific", 
                                                    "conspecific pollen  ", 
                                                    "heterospecific pollen")) %>%
+    # add fake point lower so that I can include the importance labels
+    dplyr::group_by(pollen_category) %>%
+    dplyr::mutate(estimate = dplyr::if_else(min(estimate) == estimate,
+                                            estimate - 0.1, 
+                                            estimate))
+  
+  # to get the x aesthetic for the importance labels
+  min_values <- dist %>%
+    dplyr::summarise(x = min(estimate)) %>%
+    dplyr::mutate(x = dplyr::if_else(pollen_category == "heterospecific pollen", 
+                                     x + 0.03, 
+                                     x), 
+                  title = "relative\nimportance")
+  
+  imp <- variable_importance %>%
+    tidyr::gather(key = "pollen_category", value = "importance", conspecific, heterospecific) %>%
+    dplyr::mutate(term = forcats::fct_relevel(term, c("abundance", "degree"), after = 2), 
+                  pollen_category = dplyr::if_else(pollen_category == "conspecific", 
+                                                   "conspecific pollen  ", 
+                                                   "heterospecific pollen"), 
+                  importance = round(importance, 2), 
+                  label = sprintf("%.2f", importance)) %>%
+    dplyr::inner_join(min_values, by = "pollen_category")
+  
+  
+  p <- dist %>%
     ggplot(aes(x = estimate,
                y = term,
                colour = pollen_category, 
@@ -24,18 +50,40 @@ make_fig_coefficient_avarages <- function(coefficient_averages){
                         vline_linetype = 1, 
                         vline_size = 0.25, 
                         rel_min_height = 0) +
+    geom_text(data = imp, 
[…]

### 2018-08-26 main.R

@@ -152,7 +152,7 @@ figure_plan <- drake::drake_plan(
   fig_all_model_results = make_fig_all_model_results(tidied_fixed, sites, model_formula_ranking), 
   fig_community_global_scatter = make_fig_community_global_scatter(plant_rel_abu, org_frame, degree, sites, pollen_contribution),
   fig_effect_quant_qual = make_fig_effect_quant_qual(summary_effects, model_formula_ranking), 
-  fig_coefficient_averages = make_fig_coefficient_avarages(coefficient_averages), 
+  fig_coefficient_averages = make_fig_coefficient_avarages(coefficient_averages, variable_importance), 
   fig_average_qual_quant = make_fig_average_quant_qual(coefficient_averages), 
   fig_correlation = make_fig_correlation(rep_1)
 )

### 2018-08-26 paper/supp-info.Rmd
Figure of correlation between explanatory variables
Close #17
Make figure all results larger

@@
 
-```{r fig-model-results, fig.height = 3.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
+```{r fig-correlation, fig.height = 4.5, fig.cap = "Corelation between the explanatory variables included in the statistical models."}
+drake::readd(fig_correlation)
+```
+
+```{r fig-model-results, fig.height = 7, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
 Only results for the models with the most parsimonous fixed effects.

### 2018-08-28 paper/manuscript.Rmd
Explain multimodel approach in the methods

@@
 
+### Pollen gain from animal pollination
+
 First, we explored wether animal pollination resulted in a quantitative increase in the pollination service.
@@
 We performed this comparisons using a set of non parametric Mann-Whitney tests both at the community and the the species level (grouping species across communities).
+
+### Conspeficic and heterospecific pollen gain
 
@@
 In addition we also tested random intercepts assuming that the plant species grouping was hierachically nested in either their community, the land use, and the locality. 
-We selected the best random structure by comparing the median Akaike Information Criterion (AIC) of evaluated models fitted using restricted maximum likelyhood. 
-After determining the best random structure, we then focused on the model's fixed structure where we fitted the fixed effect coefficients using maximum likelyhood. 
-In all model sets, we obtained the estimates for all the fixed effects we considered and then evaluated their relevance by examining their distribution. 
-Nevertheless, we obtained the calculated the relative importance of the explanatory variables by comparing the sum the Akaike weights of the models that include each variable. 
-In addition, because we expect some of our independent variables to be related to each other, we also looked at how the effect of each predictor changed when each of them were removed once at a time.
+We selected the best random structure by comparing the median Akaike Information Criterion for small samples (AICc) of evaluated models fitted using restricted maximum likelyhood. 
+After determining the best random structure, we then focused on the model's fixed structure. 
+First we fitted all possible combinations of explanatory variables to the same bootstrap resamples used previously. 
+Similar to the random models, we then determined the likelyhood of each candidate model set by calculating the median AICc of each candidate model set.
+
+We used multi-model inference to calculate the relative importance of each variable and its mean effect on pollen gain.
+The relative importance of the explanatory variables was calculated by adding the median weight of the candidate models that included the variable. 
+Then, to calculate the effect that each variable had on the gain of conspecific and heterospecific pollen we sampled 100 times from the estimated coefficients in each candidate model set proportional to the median likelyhood of each set.
+This sampling allowed us to build a model averaged distribution of the effect that each predictor had on pollen gain. 
+If a variable was not included in a model set we setted the estimate of its coefficient in the model to zero. 
+Estimating the models using multiple combinations of the variables allowed us to evaluate how the effect of each predictor changed when each of them were removed once at a time. 
+This is important because we expect some of our predictors to be related to each other.
+
+### Quantity and quality of pollination
 
@@
 
-The results from both model set—and the relationship between them—provide indication of both the quantity and quality of animal pollination, and the potential trade-off between these two. 
-To examine the relationship between our explanatory variables and the quantity of pollination we simply examine the results of the models of conspecific pollen gain. 
-To examine the relationship with the quality of pollination, we sampled 100 estimates from the distribution of coefficients in each of the two model sets. 
-For each of the samples, we then calculated the difference between the gain in conspecific and heterospecific pollen that would be predicted assuming mean values for the random intercepts and the other predictors.
-This allowed us to estimate the proportion between heterospecific and conspecific pollen gain which we use as a proxy of the quality of pollination.
+The mean effects we calculated from the model sets of conspecific and heterospecific pollen—and the relationship between them—provide indication of both the quantity and quality of animal pollination.
+To examine the relationship between our explanatory variables and the quantity of pollination, we repeated the sampling used to estimate the distribution of the effects of conspecific and heterospecific gain.
+The effects were then calculated from the mean effects on the gain on cospecific pollen. 
+To examine the quality of pollination we while the effects on the quality of pollination were calculated from the mean difference between the effects on the gain on consspecific and heterospecific pollen.
+
+Finally facilitation XX
 

### 2018-08-31 paper/manuscript.Rmd
More details of modelling strategy in methods

@@
 
-### Pollen gain from animal pollination
-
-First, we explored wether animal pollination resulted in a quantitative increase in the pollination service.
-To do that, we compared the amount of conspecific pollen on stigmas from flowers open to animal pollination and that from flowers that were bagged, where only autogamus self-pollination ocurred.
-The difference between these two counts is not directly equivalent to the pollen deposited by animals because self-pollination is an adaptive trait [@kalisz_benefits_2003]. 
-Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output.
-We performed this comparisons using a set of non parametric Mann-Whitney tests both at the community and the the species level (grouping species across communities).
-
 ### Conspeficic and heterospecific pollen gain
 
-Second, we examine wether there is a relationship between this gain and several ecological variables that can affect the mutualistic trade-off.
-To do so, we fitted two sets of linear mixed models [using the R package `nlme 3.1-131`, @pinheiro_nlme_2018] which differed on whether the pollen deposited was conspecific or heterospecific.
+First, we examine wether there is a relationship between the gain of pollen induced by animal pollination and several ecological variables that can affect the mutualistic trade-off. 
+To do so, we used a combination of multi-model inferencewe and bootstrap resampling of the data sets. 
+In summary we fitted two sets of linear mixed models [using the R package `nlme 3.1-131`, @pinheiro_nlme_2018] which differed on whether the pollen deposited was conspecific or heterospecific. 
 In both set of models, our response variable was the difference between pollen density (pollen counts per stigma) between open and bagged flowers. 
-Both model sets were based on the same one hundred bootstrap resamples of the deposition data.
+Each model set was based on the same one hundred bootstrap resamples of the deposition data.
 
 We used bootstrap resampling because, as open and bagged flowers were not paired, this allowed us to directly model the *gain* in pollen density rather than density itself. 
-This strategy, not only simplified the model specification and intepretation, but also allowed us to easily evaluate the uncertainity of the model results.  
-In each replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
+This strategy, not only simplified the model specification and intepretation, but most importantly it also allowed us to easily evaluate the uncertainity of the model results. 
+In each data replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
 We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-logtransformed-or-not) and \@ref(S-fig:fig-deposition-gain-logtransformed-or-not)), this generally offered better results that a generalised linear model with poisson (or quasiposson) error structure.
@@
 
-As predictors, we included species degree, the species' functional originality, the plant relative abbundance, and the plant species' share on the pollen pool. 
+As predictors, we included species degree, the plant relative abbundance, the plant species' share on the pollen pool, and the species' functional originality. 
 Species degree was calculated from combining the quantitative and qualitative visitation networks and corresponds to the number of animal species that were observed to visit the plant species in the community where it was sampled.
+The plant's relative abbundance we simply aggregated the flower counts for each plant species in the community.
+As with the deposition data, we found that log-transforming the abundance counts drastically improved normality (Figure \@ref(S-fig:fig-abundance-logtransformed-or-not)). 
+The species' share of the pollen pool was calculated as the proportion of pollen of that species in the pollen counts being carried by pollinators from the community.
+
 Functional originality is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016-1].
@@
 The species-specific functional coordinates were calculated using the R package `FD 1.0-12` [@laliberte_distance-based_2010; @laliberte_fd_2014]. 
-To calculate the plant's relative abbundance we simply aggregated the flower counts for each plant species in the community.
-As with the deposition data, we found that log-transforming the abundance counts drastically improved normality (Figure \@ref(S-fig:fig-abundance-logtransformed-or-not)). 
-Finally the species' share of the pollen pool was calculated as the proportion of pollen of that species in the pollen counts being carried by pollinators from the community. 
 To faciliate comparison across model estimates, we scaled all independent variables to have a mean of zero and a standard deviation of one.
 
-In all set of models we first evaluated a set of candidate random effects which included random intercepts for plant species as well as random slopes for the relationship between degree and pollen gain.
-In addition we also tested random intercepts assuming that the plant species grouping was hierachically nested in either their community, the land use, and the locality. 
-We selected the best random structure by comparing the median Akaike Information Criterion for small samples (AICc) of evaluated models fitted using restricted maximum likelyhood. 
-After determining the best random structure, we then focused on the model's fixed structure. 
+In both set of models we first evaluated a set of candidate random effects which included random intercepts for plant species as well as random slopes for the relationship between degree and pollen gain.
+In addition we also tested for random intercepts that assumed that the plant species grouping was hierachically nested in either their community, the land use, and the locality. 
+We selected the best random structure by comparing the median Akaike Information Criterion (AIC) of evaluated models. 
+After determining the best random structure, we then focused on the model's fixed structure composed by our explanatory variables. 
+We used multi-model inference to calculate the relative importance of each variable and its mean effect on pollen gain.
 First we fitted all possible combinations of explanatory variables to the same bootstrap resamples used previously. 
-Similar to the random models, we then determined the likelyhood of each candidate model set by calculating the median AICc of each candidate model set.
+This yielded one hundred models for each "candidate formula"---a particular combination of explanatory variables. 
+We then determined the likelyhood of each candidate formula and its relative wheight by calculating the median $\Delta$AIC of the one hundred models that constitute it. 
+As AIC is only useful to compare models with the same response variable, the $\Delta$AIC of each candidate formula was calculated indepenently for each bootstrap resample.
+Calculating the median value of each candidate formula allowed us to estimate the relative importance of the explanatory variables  using the standard methods of adding the median weight of the candidate models that included the variable.
 
-We used multi-model inference to calculate the relative importance of each variable and its mean effect on pollen gain.
-The relative importance of the explanatory variables was calculated by adding the median weight of the candidate models that included the variable. 
-Then, to calculate the effect that each variable had on the gain of conspecific and heterospecific pollen we sampled 100 times from the estimated coefficients in each candidate model set proportional to the median likelyhood of each set.
-This sampling allowed us to build a model averaged distribution of the effect that each predictor had on pollen gain. 
-If a variable was not included in a model set we setted the estimate of its coefficient in the model to zero. 
-Estimating the models using multiple combinations of the variables allowed us to evaluate how the effect of each predictor changed when each of them were removed once at a time. 
-This is important because we expect some of our predictors to be related to each other.
+To calculate the effect that each variable had on the gain of conspecific and heterospecific pollen we sampled from the estimated coefficients in each candidate model proportional to the median likelyhood of each set.
+In other words, the estimated coefficients from more likely candidate constitute a larger share of the distribution of coefficients. 
+When a variable was not included in a model set we setted the estimate of its coefficient in the model to zero. 
+We expect some of our predictors to be correlated to each other.
+Estimating the models using multiple combinations of explanatory variables also allowed us to evaluate the potential collinearity between them.
+To do so we inspect how the effect of the explanatory variables changed across candidate formulaes, when one or more of them were removed in turns.
 

### 2018-08-31 paper/manuscript.Rmd
Move conspefiic pollen comparison to quantity quality section

@@
 
-The mean effects we calculated from the model sets of conspecific and heterospecific pollen—and the relationship between them—provide indication of both the quantity and quality of animal pollination.
-To examine the relationship between our explanatory variables and the quantity of pollination, we repeated the sampling used to estimate the distribution of the effects of conspecific and heterospecific gain.
-The effects were then calculated from the mean effects on the gain on cospecific pollen. 
-To examine the quality of pollination we while the effects on the quality of pollination were calculated from the mean difference between the effects on the gain on consspecific and heterospecific pollen.
+To evaluate the quantity of pollination we first, we explored wether animal pollination resulted in a quantitative increase in the amount of conspeific pollen. 
+To do that, we compared the amount of conspecific pollen on stigmas from flowers open to animal pollination and that from flowers that were bagged, where only autogamus self-pollination ocurred. 
+The difference between these two counts is not directly equivalent to the pollen deposited by animals because self-pollination is an adaptive trait [@kalisz_benefits_2003].  
+Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output. 
+We performed this comparisons using a set of non parametric Mann-Whitney tests both at the community and the the species level (grouping species across communities). 
+Second, we calculated the relationship between the ecological variables included in the models of pollen gain and the quantity of pollination. 
+To do so, we simply calculated the mean value of the distribution of the effects of conspecific pollen gain. 
+Again, we used bootstrap resampling from the coefficient distributions to calculate the confidence intervals of the mean.
 
-Finally facilitation XX
+The quality of pollination can be estimated by the relationship that exists between the gain in conspecific and heterospecific pollen. 
+First, we calculated an overal relationship by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al.
+2012).
+We then followed a similar procedure to calculate a relationship per species in a community but instead of fitting a SMA per model pair, we did this across the 100 models for each random intercept independently.
+This allowed us to estimate the extent of facilitation for each plant species in its community. 
+We also calculated the relationship between the ecological variables and the quality of pollination. 
+To do so we calculated the mean difference between a sample of the distribution of the effects of conspecific pollen gain and a sample of those of heterospecific pollen gain. 
+Similar to the mean effects on the quantity of pollination, we used bootstrap resamplong to calculate confidence intervals of the means.
 

### 2018-08-31 paper/manuscript.Rmd
Rewrite model results

@@
 
+### Conspeficic and heterospecific pollen gain
+
+We found that, for both the model sets of conspecific and heterospecific pollen, the random structure that was best supported the data was the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
+In addition, AIC scores of the candidate model sets indicated that the species' share in the pollen pool and the functional originality were the most important variables determining the gain in both conspecific and heterospecific pollen (Figure \@ref(fig:fig-model-results-global)).
+In addition to these two variables, the species relative abundance was also important for predicting the gain in heterospecific pollen (Figure \@ref(fig:fig-model-results-global)). 
+Surprisingly, the species degree was comparatively less important as it was only included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
+
+```{r table-variable-importance, results='asis', eval = F}
+drake::loadd(variable_importance)
+
+variable_importance %>%
+  dplyr::rename(`fixed effect`= term, 
+                `conspecific pollen` = conspecific, 
+                `heterospecific pollen` = heterospecific) %>%
+  knitr::kable(caption = "Relative variable impotance of the four vaariables included as fixed effects.
+Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{S-tab:table-aic-fixed-models}) of each candidate model set that includes the variable.",
+               booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::add_header_above(c(" ", "variable importance" = 2))
+```
+
+```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
+Results are shown for models with explanatory var"}
+drake::readd(fig_coefficient_averages)
+```
+
+Overall we observed that species degree, abundance, and share of the pollen pool had a neggative effect on the gain of conspecific pollen, while functional originality had a positive effect. 
+This 
+These, three explanatory variables were positively correlated (Figure \@ref(S-fig:fig-correlation)). 
+Neverthelsess, the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
+The effects of the explanatory variables on the heterospecific pollen was more nuanced. 
+When inspecting the most likely models, those with the lowest AIC scores, we observed that the gain in heterospecific pollen was neggatively related to the species abundance but positively correlated the species' share in the pollen pool, functional originality, and to a lesser extent, degree.
+We, however observe that when not accounting for a species abundance, both a species' share in the pollen pool and its functional originality have a negative relationship with the gain in heterospecific pollen (Figure \@ref(S-fig:fig-model-results)).
+
+### Quantity and quality of pollination
+
 ```{r differences-in-self-pollination}

### 2018-08-31 paper/manuscript.Rmd
Remove proportion subfigure, leave only relationship one

@@
 
-```{r fig-trade-off-predictions, fig.height= 2, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
+```{r fig-trade-off-predictions, fig.height= 3.1, fig.width = 3.25, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
 (A) Overall and species-level relationship.
@@
 Dotted lines show the relationship for each species.
-Invasive species are shown in red.
-(B) The proportion of conspecific pollen relative to the total amount of pollen gained trough animal pollination and its relationship to our set of explanatory variables."}
-cowplot::plot_grid(
-  drake::readd(fig_con_hetero_gain), 
-  drake::readd(fig_proportion_vs_variables), 
-  align = "h", axis = "tb", ncol = 2, labels = LETTERS[1:2], 
-  label_size = 8, rel_widths = c(0.35, 0.65))
+Invasive species are shown in red."}
+# pdf(width = 3.25, height = 3.1)
+  drake::readd(fig_con_hetero_gain)
+  # dev.off()
 ```

### 2018-08-31 paper/manuscript.Rmd
QUantity quality figure is narrower
Restructure results of quantity quality

@@
 
-Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
+Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
 When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(S-tab:table-species-gain-site)).
-Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table \@ref(S-tab:table-variation-across-sites)).
+In addition, using the results from the models of conspecific pollen gain, we found that from all the explanatory variables examined, only the plant's functional originality has a positive effect on the quantity of pollination (Figure \@ref(fig:fig-average-qual-quant)).
 
-We found that the random structure that was best supported the data was consistently the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
-We also found that the models AIC story
-
-```{r table-variable-importance, results='asis'}
-drake::loadd(variable_importance)
-
-variable_importance %>%
-  dplyr::rename(`fixed effect`= term, 
-                `conspecific pollen` = conspecific, 
-                `heterospecific pollen` = heterospecific) %>%
-  knitr::kable(caption = "Relative variable impotance of the four vaariables included as fixed effects.
-Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{S-tab:table-aic-fixed-models}) of each candidate model set that includes the variable.",
-               booktabs = TRUE) %>%
-  kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::add_header_above(c(" ", "variable importance" = 2))
-```
-
-```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
-Results are shown for models with explanatory var"}
-drake::readd(fig_coefficient_averages)
-```
-
-When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better approximated by the model sets using predictors calculated across communities (Table \@ref(S-tab:table-global-vs-community-models)).
-This was so despite the fact that the model predictors calculated at the community level were highly correlated to those at the study wide level (Figure \@ref(S-fig:fig-global-community-correlations)).
-Nevertheless, results from the within community models are similar both qualitatively and quantitatively (with the exception of phenology overlap, but that might change once I use a better metric, Figure \@ref(S-fig:fig-model-results)).
-
-We found that the gain in conspecific pollen is negatively affected by the plants relative abbundance and to a smaller extent by the species' degree (Figure \@ref(fig:fig-model-results-global)). 
-The gain in heterospecific pollen was instead positively affected by degree and the plant's phenology overlap, but was also strongly negatively affected by the plant's relative abbundance.
-
-```{r fig-average-qual-quant, fig.height=2, fig.width=3.5, fig.cap="asd"}
+```{r fig-average-qual-quant, fig.height=1.1, fig.width=3.25, fig.cap="asd"}
 drake::readd(fig_average_qual_quant)
@@
 
-The gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 
+We then examined the quality of pollination, which is given by the relationship between conspecific and heterospecific pollen.
+We found that, overall, the gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 
 The slope of the relationship is such that it is more likely that the gain on heterospecific pollen increases faster than the gain on conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)A).
-In addition, we found that from all the explanatory variables examined, only the plant's relative abbundance has a positive effect on the proportion of conspecific pollen gained (Figure \@ref(fig:fig-trade-off-predictions)B).
-For most of the parameter space plants obtain a larger proportion of heteropspecific than conspecific pollen. 
-However, plants can obtain a larger proportion of conspecific pollen when they have high abundance and to a smaller extent when they have a low degree. 
-When examining the extent of facilitation at the species level, we found that XXX (Figure \@ref(fig:fig-trade-off-predictions)B).
+At the species level, we found that XXX (Figure \@ref(fig:fig-trade-off-predictions)B). 
+Furthermore, by examining the difference between the conspecific and heterospecific pollen gain, we found that the species abundance has an important positive effect in the quality of pollination, while the share in the pollen pool and, to an smaller extent, the species degree have a negative effect.
 

### 2018-08-31 paper/supp-info.Rmd
Do not show table comparing wether community makes a difference
On the gain of conspecific pollen transfer

@@
 
-```{r table-variation-across-sites, results='asis'}
+```{r table-variation-across-sites, eval=FALSE, results='asis'}
 drake::loadd(consp_self)

### 2018-09-04 paper/manuscript.Rmd
Add to do and question section to the manuscript
Small changes to intro

@@
 
+### To do
+
+* References to the introduction
+* Settle on analyses
+* Nail down discussion
+* Abstract
+
+### Questions
+
+* Should I separate the "phenology originality" from the "functional originality"?
+* Gain in pollen vs. absolute amount of pollen?
+
+\clearpage
+
 # Abstract
@@
 
-Here, we explore the signature of the mutualistic trade-off in diverse natural communities. 
+Here, we explore the role that competition for pollinators plays on the quantity and quality of the pollination service and look for the signature of the mutualistic trade-off in diverse natural communities.
 To tease appart the multiple factors that operate at the community scale we use data that describes both the structure of the interactions and the pollen flows that ocurr within it, all while accounting for the traits of the species that integrate the community.
@@
 Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.
-We hypothezise that XX??
-**TODO: Mini conclusion here**
 

### 2018-09-04 paper/manuscript.Rmd
Explain quantity and quality first

@@
 
-### Conspeficic and heterospecific pollen gain
+At the community scale, sharing mutualistic partners might induce competition for pollination mainly trough two mechanisms. 
+The first is competition for visits, where plants with more atractive flowers reduce the number of visits for those less atractive. 
+Competition for visits affects the *quantity* of the pollination service as it induces a reduction in the amount of conspecific pollen received by flowers. 
+The second, more subtle, mechanism is interspecific pollen transfer, where even receiving a visit might not translate into net facilitation. 
+Interspecific pollen transfer affects the *quality* of the pollination service because a focal plant might receive pollen from a different species, or conversely pollen from the focal plant might be lost to different species.
+Generally speaking the larger the proportion of conspecific relative to heterospecific pollen the higher the quality of the pollination service.
 
-First, we examine wether there is a relationship between the gain of pollen induced by animal pollination and several ecological variables that can affect the mutualistic trade-off. 
-To do so, we used a combination of multi-model inferencewe and bootstrap resampling of the data sets. 
-In summary we fitted two sets of linear mixed models [using the R package `nlme 3.1-131`, @pinheiro_nlme_2018] which differed on whether the pollen deposited was conspecific or heterospecific. 
-In both set of models, our response variable was the difference between pollen density (pollen counts per stigma) between open and bagged flowers. 
-Each model set was based on the same one hundred bootstrap resamples of the deposition data.
+We explore the quantity of pollination service by examining two metrics. 
+First, we use the absolute amount of conspecific pollen (pollen counts per stigma) deposited on flowers open to animal pollination. 
+Second, we use the relative amount of conspecific pollen—the difference between the absolute amount and the that from flowers that were bagged. 
+We use both metrics simultaneously because, in the one hand, the relative amount acknowledges that autogamus self-pollination can ocurr and hence might be a better indication of the pollen that has been actually deposited by mutualistic partners.
+On the other, self-pollination is an adaptive trait [@kalisz_benefits_2003] and some plants are not self-fertile, even if their pollen gets deposited on the stigma. 
+Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output. 
+Both metrics complement each other and provide a more complete picture of the quantitative aspect of pollination service. 
+Similarly, to explore the quality of pollination we examine the relationship that exists between both the absolute and relative amount of conspecific pollen and heterospecific pollen. 
+We use the relative amount of heterospecific pollen for our calculations. 
+However, because the amount of heterospecific pollen in bagged flowers was negligible, results are almost identical if we use the absolute amounts.
 
@@
 
-### Quantity and quality of pollination
-
-At the community scale, sharing mutualistic partners might induce competition for pollination mainly trough two mechanisms. 
-The first is competition for visits, where plants with more atractive flowers reduce the number of visits for those less atractive. 
-Competition for visits affects the *quantity* of the pollination service as it induces a reduction in the amount of conspecific pollen received by flowers. 
-The second, more subtle, mechanism is interspecific pollen transfer, where even receiving a visit might not translate into net facilitation. 
-Interspecific pollen transfer affects the *quality* of the pollination service because a focal plant might receive pollen from a different species, or conversely pollen from the focal plant might be lost to different species.
-Generally speaking the larger the proportion of conspecific relative to heterospecific pollen the higher the quality of the pollination service.
-
-To evaluate the quantity of pollination we first, we explored wether animal pollination resulted in a quantitative increase in the amount of conspeific pollen. 
-To do that, we compared the amount of conspecific pollen on stigmas from flowers open to animal pollination and that from flowers that were bagged, where only autogamus self-pollination ocurred. 
-The difference between these two counts is not directly equivalent to the pollen deposited by animals because self-pollination is an adaptive trait [@kalisz_benefits_2003].  
-Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output. 
-We performed this comparisons using a set of non parametric Mann-Whitney tests both at the community and the the species level (grouping species across communities). 
-Second, we calculated the relationship between the ecological variables included in the models of pollen gain and the quantity of pollination. 
-To do so, we simply calculated the mean value of the distribution of the effects of conspecific pollen gain. 
+After calculating the effects of the ecological variables in heterospecific and conspecific pollen densities, we can now evaluate their effect in the quality and quantity of pollination. 
+For the quantity of pollination, we simply calculated the mean value of the distribution of the effect for both the absolute and relative conspecific pollen densities. 
 Again, we used bootstrap resampling from the coefficient distributions to calculate the confidence intervals of the mean. 
-
-The quality of pollination can be estimated by the relationship that exists between the gain in conspecific and heterospecific pollen. 
-First, we calculated an overal relationship by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al.
-2012).
-We then followed a similar procedure to calculate a relationship per species in a community but instead of fitting a SMA per model pair, we did this across the 100 models for each random intercept independently.
-This allowed us to estimate the extent of facilitation for each plant species in its community. 
-We also calculated the relationship between the ecological variables and the quality of pollination. 
-To do so we calculated the mean difference between a sample of the distribution of the effects of conspecific pollen gain and a sample of those of heterospecific pollen gain. 
-Similar to the mean effects on the quantity of pollination, we used bootstrap resamplong to calculate confidence intervals of the means.
+For the quality of pollination, we calculated the mean difference between a sample of the distribution of the effects of conspecific pollen and a sample of those of heterospecific pollen gain.
+Similar to the mean effects on the quantity of pollination, we used bootstrap resamplong to calculate confidence intervals of the means.estimated by the relationship that exists between the gain in cspecific and heterospecific pollen.
 

### 2018-09-04 paper/manuscript.Rmd
Adapt methods to absolute and relative pollen densities

@@
 Previous studies focus on the final picture of interspecific pollen transfer that is obtained by examining the pollen deposited on flower stigmas. 
-However, as we have described, teasing appart competition for pollinators also requires data that describes the structure of the interactions and the pollen flows that ocurr within it, while accounting for the traits of the species that integrate the community.
+However, as we have described, teasing appart competition for pollinators and evaluating wether there is a trade-off between the number of partners and the mutualistic benefit also requires data that describes the structure of the interactions and the pollen flows that ocurr within it, while accounting for the traits of the species that integrate the community.
 Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas.
@@
 
+To study the amounts of deposited pollen, which are needed to construct our metrics of pollination quantity and quality, we use three sets of linear fixed models [using the R package `nlme 3.1-131`, @pinheiro_nlme_2018]—two for conspecific pollen (absolute and relative) and one for heterospecific pollen.
+This modelling approach allowed us to simultaneously explore wether there is a relationship between the benefit of animal pollination and several ecological variables that can affect the mutualistic trade-off.
+In addition, to estimate and incorporate the uncertainity associated to our results we used a combination of multi-model inference and bootstrap resampling.
+
+Each model set was based on the same one hundred bootstrap resamples of the deposition data. 
 We used bootstrap resampling because, as open and bagged flowers were not paired, this allowed us to directly model the *gain* in pollen density rather than density itself. 
-This strategy, not only simplified the model specification and intepretation, but most importantly it also allowed us to easily evaluate the uncertainity of the model results. 
 In each data replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
 We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-logtransformed-or-not) and \@ref(S-fig:fig-deposition-gain-logtransformed-or-not)), this generally offered better results that a generalised linear model with poisson (or quasiposson) error structure.
-Finally, we calculated the difference between the pollen density among treatmemts. 
-This difference was the response variable in all our models.
+Finally, for the models of the relative amounts of pollen we calculated the difference between the pollen density among treatmemts.
 
-As predictors, we included species degree, the plant relative abbundance, the plant species' share on the pollen pool, and the species' functional originality. 
+As predictors in all model sets, we included species degree, the plant relative abbundance, the plant species' share on the pollen pool, and the species' functional originality. 
 Species degree was calculated from combining the quantitative and qualitative visitation networks and corresponds to the number of animal species that were observed to visit the plant species in the community where it was sampled.
@@
 
-In both set of models we first evaluated a set of candidate random effects which included random intercepts for plant species as well as random slopes for the relationship between degree and pollen gain.
+In all three sets of models we first evaluated a set of candidate random effects which included random intercepts for plant species as well as random slopes for the relationship between degree and pollen gain.
 In addition we also tested for random intercepts that assumed that the plant species grouping was hierachically nested in either their community, the land use, and the locality. 
@@
 After determining the best random structure, we then focused on the model's fixed structure composed by our explanatory variables. 
-We used multi-model inference to calculate the relative importance of each variable and its mean effect on pollen gain.
+We used multi-model inference to calculate the relative importance of each variable and its mean effect on pollen density.
 First we fitted all possible combinations of explanatory variables to the same bootstrap resamples used previously. 

### 2018-09-04 paper/manuscript.Rmd
Put figures together and improve captions

@@
 
-```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
-Results are shown for models with explanatory var"}
-drake::readd(fig_coefficient_averages)
-```
-
 Overall we observed that species degree, abundance, and share of the pollen pool had a neggative effect on the gain of conspecific pollen, while functional originality had a positive effect. 
@@
 
-```{r fig-average-qual-quant, fig.height=1.1, fig.width=3.25, fig.cap="asd"}
-drake::readd(fig_average_qual_quant)
-```
-
 We then examined the quality of pollination, which is given by the relationship between conspecific and heterospecific pollen.
@@
 
-```{r fig-trade-off-predictions, fig.height= 3.1, fig.width = 3.25, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
-(A) Overall and species-level relationship.
-Grey lines indicate the relationship in each of the samples, the median is indicated with a black solid line.
-Dotted lines show the relationship for each species.
-Invasive species are shown in red."}
+```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates of models of conspecific and heterospecific pollen density gained with animal pollination.
+Results are shown for models that included explanatory variable.
+The median relative variable impotance of the four variables for each model set is shown next to each distribution.
+Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{S-tab:table-aic-fixed-models}) of each candidate model set that includes the variable."}
+drake::readd(fig_coefficient_averages)
+```
+
+```{r fig-trade-off-predictions, fig.height= 2.3, fig.width = 3.25, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
+Each dot indicates the corresponding gains for a species in its community (which corresponded to the random effects in our models).
+Grey lines indicate the overall relationship in each of the bootstrap replicates and were calculated by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al.
+2012)."}
 # pdf(width = 3.25, height = 3.1)
@@
   # dev.off()
+```
+
+```{r fig-average-qual-quant, fig.height=1.1, fig.width=3.25, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
+Confidence intervals of the mean (at the 0.05 level) are shown in square brackets.
+"}
+drake::readd(fig_average_qual_quant)
 ```

### 2018-09-14 paper/manuscript.Rmd
Rewrite results
Close #11

@@
 
-### Conspeficic and heterospecific pollen gain
+We found that, for both the model sets of conspecific and heterospecific pollen, the random structure that was best supported by the data was the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
+We observed a positive relationship between the gain in heterospecific pollen and both the relative and absolute gain of conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)). 
+The slope of the relationship is such that across plant species in their communitues heterospecific pollen is gained slower than the absolute amount of conspecific pollen but faster than the amount of conspecific pollen relative to the potential selfing.
 
-We found that, for both the model sets of conspecific and heterospecific pollen, the random structure that was best supported the data was the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
-In addition, AIC scores of the candidate model sets indicated that the species' share in the pollen pool and the functional originality were the most important variables determining the gain in both conspecific and heterospecific pollen (Figure \@ref(fig:fig-model-results-global)).
-In addition to these two variables, the species relative abundance was also important for predicting the gain in heterospecific pollen (Figure \@ref(fig:fig-model-results-global)). 
-Surprisingly, the species degree was comparatively less important as it was only included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
-
-```{r table-variable-importance, results='asis', eval = F}
-drake::loadd(variable_importance)
-
-variable_importance %>%
-  dplyr::rename(`fixed effect`= term, 
-                `conspecific pollen` = conspecific, 
-                `heterospecific pollen` = heterospecific) %>%
-  knitr::kable(caption = "Relative variable impotance of the four vaariables included as fixed effects.
-Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{S-tab:table-aic-fixed-models}) of each candidate model set that includes the variable.",
-               booktabs = TRUE) %>%
-  kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::add_header_above(c(" ", "variable importance" = 2))
+```{r fig-trade-off-predictions, fig.height= 2.3, fig.width = 3.25, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
+Each dot indicates the predicted median gains for a species in its community (which correspons to the selected random effects in all of our models).
+The horizontal and vertical bars under each dot indicate the 95% credible intervals of the estimates.
+The solid lines indicate the overall relationship in each of the bootstrap replicates and were calculated by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al.
+2012).
+The dashed line indicates the isoline at which heterospecific pollen is gained at the same rate than conspecific pollen."}
+# pdf(width = 3.25, height = 3.1)
+  drake::readd(fig_con_hetero_gain)
+  # dev.off()
 ```
 
-Overall we observed that species degree, abundance, and share of the pollen pool had a neggative effect on the gain of conspecific pollen, while functional originality had a positive effect. 
-This 
-These, three explanatory variables were positively correlated (Figure \@ref(S-fig:fig-correlation)). 
-Neverthelsess, the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
-The effects of the explanatory variables on the heterospecific pollen was more nuanced. 
-When inspecting the most likely models, those with the lowest AIC scores, we observed that the gain in heterospecific pollen was neggatively related to the species abundance but positively correlated the species' share in the pollen pool, functional originality, and to a lesser extent, degree.
-We, however observe that when not accounting for a species abundance, both a species' share in the pollen pool and its functional originality have a negative relationship with the gain in heterospecific pollen (Figure \@ref(S-fig:fig-model-results)).
+In addition, AIC scores of the candidate model sets indicated that the species' share in the pollen pool, the functional originality, and the species relative abundance were the most important variables determining the gain in both conspecific and heterospecific pollen (Figure \@ref(fig:fig-model-results-global)).
+Note that relative abundance plays a more important role determining the gain in heterospecific pollen than the gain in both the absolute and relative amounts of conspecific pollen.
+Surprisingly, the species degree was comparatively less important for predicting pollen gain as it was only included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
 
-### Quantity and quality of pollination
+```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates of models of conspecific (absolute and relative to the potential selfing) and heterospecific pollen density gain.
+Results are only shown for models that included explanatory variable.
+The median relative variable impotance of the four variables for each model set is shown next to each distribution.
+Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{S-tab:table-aic-fixed-models}) of each candidate model set that includes the variable."}
+drake::readd(fig_coefficient_averages)
+```
+
+Overall we observed that species degree and abundance had a neggative relationship with the gain of both absolute and relative conspecific pollen. 
+Functional originallity had a weak negative relationship with the absolute gain of conspecific pollen but a small positive effect on the relative gain. 
+The plant's share in the community pollen pool, had opposite effects, with a  positive relationship with the absolute gain and a negative relationship with the relative gain of conspecific pollen.
+Although relative abundance, degree, and the share in the pollen pool were positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
+
+The gain in heterospecific pollen was negatively related to the species abundance but positively to the species' share in the pollen pool, functional originality, and degree. 
+Compared to the models of conspecific pollen, the collinearity in the explanatory variables had a larger impact in the models of heterospecific pollen. 
+For instance, when the species abundance was not accounted for, both the species' share in the pollen pool and its functional originality have a negative relationship with the gain in heterospecific pollen (Figure \@ref(S-fig:fig-model-results)).
 
@@
 
-Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
-When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(S-tab:table-species-gain-site)).
-In addition, using the results from the models of conspecific pollen gain, we found that from all the explanatory variables examined, only the plant's functional originality has a positive effect on the quantity of pollination (Figure \@ref(fig:fig-average-qual-quant)).
+<!-- Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
+-->
+<!-- When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(S-tab:table-species-gain-site)).
+-->
+Using the results from the models of conspecific and heterospecific pollen gain we then examined the relationship between the explanatory variables and the quantity and quality of pollination (Figure \@ref(fig:fig-average-qual-quant)).
+Degree, had a neggative, albeit relativelly small, effect on both the quantity and quality of pollination. 
+The species relative abbundance has a large possitive effect to the quality of pollination accompained by a relatively smaller negative impact on the quantity. 
+Finally, the plant's functional originallity and its share in the pollen pool have a moderate positive impact on its quantity but also a negative impact on the quality.
 
-We then examined the quality of pollination, which is given by the relationship between conspecific and heterospecific pollen.
-We found that, overall, the gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 
-The slope of the relationship is such that it is more likely that the gain on heterospecific pollen increases faster than the gain on conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)A).
-At the species level, we found that XXX (Figure \@ref(fig:fig-trade-off-predictions)B). 
-Furthermore, by examining the difference between the conspecific and heterospecific pollen gain, we found that the species abundance has an important positive effect in the quality of pollination, while the share in the pollen pool and, to an smaller extent, the species degree have a negative effect.
-
-```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates of models of conspecific and heterospecific pollen density gained with animal pollination.
-Results are shown for models that included explanatory variable.
-The median relative variable impotance of the four variables for each model set is shown next to each distribution.
-Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{S-tab:table-aic-fixed-models}) of each candidate model set that includes the variable."}
-drake::readd(fig_coefficient_averages)
-```
-
-```{r fig-trade-off-predictions, fig.height= 2.3, fig.width = 3.25, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
-Each dot indicates the corresponding gains for a species in its community (which corresponded to the random effects in our models).
-Grey lines indicate the overall relationship in each of the bootstrap replicates and were calculated by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al.
-2012)."}
-# pdf(width = 3.25, height = 3.1)
-  drake::readd(fig_con_hetero_gain)
-  # dev.off()
-```
-
-```{r fig-average-qual-quant, fig.height=1.1, fig.width=3.25, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
+```{r fig-average-qual-quant, fig.height=2, fig.width=3.25, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
 Confidence intervals of the mean (at the 0.05 level) are shown in square brackets.

### 2018-09-17 paper/manuscript.Rmd
Adjust discussion
Close #22

@@
 
-* We found that animal pollination only brings a small amount of extra conspecific pollen (compared to selfing) if any.
-This relatively small difference is probably very important though because crossing has been shown to be evolutionary better than cloning in the long term.
-* The relationship between conspecific and heterospecific pollen is positive which indicates than net facilitation is the dominant outcome.
-This agrees with previous findings.
-However the amount of added conspecific pollen is in average smaller than the amount of added heterospecific pollen.
-* Despite finding that facilitation is the most common outcome. We also were able to find clear signature of competition for pollinators at the community level.
-* We found that, as assumed in pollination models, the mutualistic benefit is modulated by the species degree and therefore there is indeed evidence for a trade-off.
-Moreover, the trade off does not depend on the species or the community.
-Which is a good thing because we tend to simplify models by assuming a common trade-off for the whole community.
-* However the mutualistic benefit was not just modulated by the degree but other factors also played significant roles. 
-* These factors, in particular the plant relative abundance, was important at explaining the differences between plants. 
-* We found that models performed better when explanatory variables were constructed so that they take into account information across all the communities in which a species was present.
-This means that despite the particularities of each community (random effects acounted for a large proportion of the variance) we can still predict general outcomes by knowing some general traits about the plant species and how it relates to other plants in their community.
-
-Understanding what makes species and communities different is important not only because of its ecological and evolutionary implications. 
-It is also important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. 
+* We did find a trade-off between the number of partners a species interacts with and the mutualistic service.
+Interacting with more species alone is often accompained by a decreasse in both the quantity and quality of pollination.
+* However, the effect and importance of this trade-off is comparatively small when considering other factors that describe the species niche and its ecological settings. 
+* We found that animal pollination only brings a small amount of extra conspecific pollen (compared selfing) if any.
+This relatively small difference is probably very important because, first, some plants simply aren't self-fertile, even if their pollen gets deposited on the stigma.
+Second, in some flowers there is temporary separation in the maturation of the sexes (dichogamy) that favors cross-pollination as, evolutonary, it has been shown to be a better strategy than cloning.
+* Overal it seems like density seems to be a dominant force behind pollen transfer.
+If you have many individuals of your species, you get fewer visits (dilution of the pollinators flying around), which is relfected in a smaller amount of deposited pollen.
+We show that abundant plants also tend to comprise a greater component of the pollen source pool and so the end result is that get more conspecific pollen per visit than heterospecific pollen.
+* Our result of the comparatively weak effect of the mutualistic trade-off is important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. 
 Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree.
-The extent to which species degree affects the benefit is called *mutualistic trade-off*. 
 This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
-At the same time it is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
-Although, the mutualistic trade-off has been shown to play a determining role on the stability and diversity of mutualistic communities, empirical evidence is scarce, to say the least.
-
-It is based on the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
-
-At the community scale, understanding the costs of sharing mutualistic partners at the community scale is important not only because of its ecological and evolutionary implications.
-It is also important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems.
-Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners—the species degree.
-The extent to which species degree affects the benefit is called mutualistic trade-off. This approach,
-37 considerably simplifies the mathematical treatment of competition for pollinators. At the same time it is
-38 based on the intuitive rationale that a species that interacts with few species benefits strongly from each
-39 of them, whereas a species that interacts with a large number of species does so comparatively weakly.
-40 Although, the mutualistic trade-off has been shown to play a determining role on the stability and diversity
-41 of mutualistic communities, empirical evidence is scarce, to say the least.
-
-At the community scale other factors we would expect
-
-Here, we explore the signatures competition for pollinators in diverse natural communities, where empirical data is more scarce.
-
-Here we examine the signature, at the community scale, that sharing mutualistic partners has in the quality and quantity of pollination. 
-Although seeimgly a simple question, teasing appart the signature of this "trade-off" has been elusive in part because of the large amounts of data required. 
-Most studies that have examined competition for pollinators are based the pollen deposited on flower stigmas. 
-However
-
-All together, existing studies at the community scale show that, as expected, the effective result of sharing mutualistic partners, in most cases, one of facilitation. 
-We hipothezise that 
-Recent empirical evidence suggest that the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
-However, they also show a large variability in this result—both across species and across communities. 
-One of the most intuitive drivers of the variability in competition, and therefore widely used in theoretical models of mutualism to account for the neggative effects of mutualism, is the species degree---the number of mutualistic partners.
-It is based on the intuitive rationale 
- that other factors might also play an important role shaping the competition for pollination.
-
-First, we estimate the gain on pollen that can be attributed to the mutualistic interactions. 
-Second, we investigate wether there is a relationship between this gain and a a suite of variables that together describe the role of the plant species and the ecological context. 
-Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.
-**TODO: Mini conclusion here**
+However we show that care must be taken because the neggative effects of the mutualistic trade-off in both the quantity and quality of pollinaton can be offset by density mechanisms.
+Species with large degrees also tend be abundant and prolific pollen producers.
 

### 2018-09-17 paper/manuscript.Rmd
Recheck text methods
Close #20

@@
 We explore the quantity of pollination service by examining two metrics. 
-First, we use the absolute amount of conspecific pollen (pollen counts per stigma) deposited on flowers open to animal pollination. 
+First, we use the absolute amount of conspecific pollen (pollen counts per stigma) found on flowers open to animal pollination. 
 Second, we use the relative amount of conspecific pollen—the difference between the absolute amount and the that from flowers that were bagged. 
@@
 On the other, self-pollination is an adaptive trait [@kalisz_benefits_2003] and some plants are not self-fertile, even if their pollen gets deposited on the stigma. 
-Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output. 
-Both metrics complement each other and provide a more complete picture of the quantitative aspect of pollination service. 
+<!-- Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output.  -->
+Both metrics complement each other and provide a complete picture of the quantitative aspect of pollination service. 
 Similarly, to explore the quality of pollination we examine the relationship that exists between both the absolute and relative amount of conspecific pollen and heterospecific pollen. 

### 2018-09-17 paper/manuscript.Rmd
Other changes to results

@@
 
+```{r differences-in-self-pollination}
+drake::loadd(significant_gain_global, significant_gain_site)
+
+sgg <- glance_table(significant_gain_global)
+prop_sig_global <- sum(sgg$p.value < 0.05) /
+  length(significant_gain_global)
+sgs <- glance_table(significant_gain_site)
+prop_sig_site <- sum(sgs$p.value < 0.05) /
+  length(significant_gain_site)
+
+consistency <- dplyr::inner_join(sgg, sgs, by = 'recipient') %>% 
+  dplyr::mutate_at(.vars = c('p.value.x', 'p.value.y'), 
+            .funs = function(x) x < 0.05) %>%
+  dplyr::mutate(consistent = p.value.x == p.value.y) %>%
+  dplyr::group_by(recipient) %>%
+  dplyr::summarise(p.value.x = mean(p.value.x), 
+            consistent = all(consistent),
+            n_sites = dplyr::n_distinct(site_name)) %>% 
+  dplyr::filter(n_sites > 1)
+prop_consistency <- sum(consistency$consistent)/
+  nrow(consistency)
+```
+
 We found that, for both the model sets of conspecific and heterospecific pollen, the random structure that was best supported by the data was the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
-We observed a positive relationship between the gain in heterospecific pollen and both the relative and absolute gain of conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)). 
+When looking at the relative amount of conspecific pollen gained, we observe that only `r round(prop_sig_global*100)`% of species in their communities observed a significant increasse in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
+We also observed a positive relationship between the gain in heterospecific pollen and both the relative and absolute gain of conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)). 
 The slope of the relationship is such that across plant species in their communitues heterospecific pollen is gained slower than the absolute amount of conspecific pollen but faster than the amount of conspecific pollen relative to the potential selfing.
@@
 Each dot indicates the predicted median gains for a species in its community (which correspons to the selected random effects in all of our models).
-The horizontal and vertical bars under each dot indicate the 95% credible intervals of the estimates.
+The horizontal and vertical bars under each dot indicate the 0.05 bootstrap confidence intervals of the estimates.
 The solid lines indicate the overall relationship in each of the bootstrap replicates and were calculated by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al.
@@
 
-```{r differences-in-self-pollination}
-drake::loadd(significant_gain_global, significant_gain_site)
-
-sgg <- glance_table(significant_gain_global)
-prop_sig_global <- sum(sgg$p.value < 0.05) /
-  length(significant_gain_global)
-sgs <- glance_table(significant_gain_site)
-prop_sig_site <- sum(sgs$p.value < 0.05) /
-  length(significant_gain_site)
-
-consistency <- dplyr::inner_join(sgg, sgs, by = 'recipient') %>% 
-  dplyr::mutate_at(.vars = c('p.value.x', 'p.value.y'), 
-            .funs = function(x) x < 0.05) %>%
-  dplyr::mutate(consistent = p.value.x == p.value.y) %>%
-  dplyr::group_by(recipient) %>%
-  dplyr::summarise(p.value.x = mean(p.value.x), 
-            consistent = all(consistent),
-            n_sites = dplyr::n_distinct(site_name)) %>% 
-  dplyr::filter(n_sites > 1)
-prop_consistency <- sum(consistency$consistent)/
-  nrow(consistency)
-```
-
 <!-- Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
@@
 ```{r fig-average-qual-quant, fig.height=2, fig.width=3.25, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
-Confidence intervals of the mean (at the 0.05 level) are shown in square brackets.
+Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.).
+Bootstrap confidence intervals of the mean (at the 0.05 level) are shown in square brackets.
 "}

### 2018-09-17 paper/manuscript.Rmd
Questions & todo
Close #25

@@
 * References to the introduction
-* Settle on analyses
-* Nail down discussion
-* Abstract
+* Discussion from bulletpoints to actual paragraphs. I will do that once we all agree with the quantitative methodology and getting some contributions for the interpretation of the results
+* Spellcheck everything
+* Finish off the supplementary materials
+* Write the abstract
 
@@
 
-* Should I separate the "phenology originality" from the "functional originality"?
-* Gain in pollen vs. absolute amount of pollen?
+Feel free to come back here after you've read the manuscript. Thanks!
 
-\clearpage
-
-# Abstract
-
-TBC
+* __Originality__: Currently the plants phenology are included in the traits.
+The relative abundance of the plant in each of the five a survey months is included as a trait.
+This allows to maintain the model simple and it could be easily argued that phenological strategy can be considered as another trait.
+However I'm not convinced that it is a good idea to keep them together, especially because differences in phenology is a rather intuitive factor/strategy to overcome competition for pollination.
+Do you think I should separate traits from phenology?
+If yes, should I use the same "originality" approach to determine how different each species is?
+* __Traits__: Currently I don't mention much traits in the discussion.
+I think the trait component is valuable and interesting but sadly at the moment the data quality is poor.
+Only 4 traits have been compiled: growth form, longevity, flower colour, and wether the plant is native to the region.
+It won't be possible to gather all of the traits used by @coux_linking_2016-1 from the literature but hopefully it is for a good proportion of them.
+Daniel and Jason, could we discuss options here?
+* __Conspecific pollen__: Previously I used, as Hugo did in his papers, the gain in conspecific pollen in open flowers relative to the amount of in bagged flowers as the indication of the "quantity" of the pollination service.
+After thinking more about the limitations of this metric (pollinatorsalso take pollen from stigmas, some plants are not self-fertile, different maturation times for male/female organs, etc) I decided it would be best to include both the total and the relative pollen amounts in the mansucript.
+This add more nuance to the story and interpretation which is not cool, but I think together they overcome each other's problems.
+What do you think about it?
+* __Naming__: I currently use absolute and relative pollen gain as names for the two previous metrics. I think it's OK but I feel there might be better options. Any ideas?
+* __Quantity & quality__: This version of the paper uses quantity/quality to frame the results.
+I think that's pretty neat.
+However, different studies define quantity and quality in different ways.
+Hugo for example used the relative amount of conspecific pollen as an indication of quantity and the amount of heterospecific pollen for quality.
+We discussed earlier that a good indication could be the _proportion_ of heterospecific pollen instead.
+What do you think?
+Should I ditch quantity/quality and stick to conspecific/heterospecific pollen instead?
+Should I stay with the current definitions of quantity and quality of pollination?
+This probably needs meeting/skype, but it would be good to think about it.
+* __Pollen transfer__: Currently all I'm using from the pollen transfer networks is the share of a plant in the pollen pool.
+That fits nice with the density hypothesis but its rather simplistic.
+Any ideas?
+* __Pollen in bagged flowers__: Jason, you mentioned that pollen in bagged flowers can be due to selfing or wind.
+You meant wind moving flowers and that causing pollen to be deposited on stigmas?
+Wouldnt that count as selfing too?
 

### 2018-09-17 paper/manuscript.Rmd
Spellcheck with Rstudio
Issue #23

@@
 * References to the introduction
-* Discussion from bulletpoints to actual paragraphs. I will do that once we all agree with the quantitative methodology and getting some contributions for the interpretation of the results
-* Spellcheck everything
+* Discussion from bullet-points to actual paragraphs. I will do that once we all agree with the quantitative methodology and getting some contributions for the interpretation of the results
+* Spell-check everything
 * Finish off the supplementary materials
@@
 I think the trait component is valuable and interesting but sadly at the moment the data quality is poor.
-Only 4 traits have been compiled: growth form, longevity, flower colour, and wether the plant is native to the region.
+Only 4 traits have been compiled: growth form, longevity, flower colour, and whether the plant is native to the region.
 It won't be possible to gather all of the traits used by @coux_linking_2016-1 from the literature but hopefully it is for a good proportion of them.
@@
 * __Conspecific pollen__: Previously I used, as Hugo did in his papers, the gain in conspecific pollen in open flowers relative to the amount of in bagged flowers as the indication of the "quantity" of the pollination service.
-After thinking more about the limitations of this metric (pollinatorsalso take pollen from stigmas, some plants are not self-fertile, different maturation times for male/female organs, etc) I decided it would be best to include both the total and the relative pollen amounts in the mansucript.
+After thinking more about the limitations of this metric (pollinators also take pollen from stigmas, some plants are not self-fertile, different maturation times for male/female organs, etc.) I decided it would be best to include both the total and the relative pollen amounts in the manuscript.
 This add more nuance to the story and interpretation which is not cool, but I think together they overcome each other's problems.
@@
 Should I stay with the current definitions of quantity and quality of pollination?
-This probably needs meeting/skype, but it would be good to think about it.
+This probably needs meeting/Skype, but it would be good to think about it.
 * __Pollen transfer__: Currently all I'm using from the pollen transfer networks is the share of a plant in the pollen pool.
@@
 You meant wind moving flowers and that causing pollen to be deposited on stigmas?
-Wouldnt that count as selfing too?
+Wouldn't that count as selfing too?
 
@@
 Pollination systems play a disproportionally important role in food production and maintenance of global biodiversity. 
-In the context of animal pollination, the support to biodiversity is fundamentally achieved by virtue of intra-species facilition—the positive feedback loops that exist between plants that share pollinators or pollinators that share plants.
+In the context of animal pollination, the support to biodiversity is fundamentally achieved by virtue of intra-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plants.
 Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources. 
@@
 This is so, because sharing a mutualistic partner also has costs. 
-The end result is that, when the cummulative costs have a negative impact on fitness, species also start competing for mutualistic partners. 
+The end result is that, when the cumulative costs have a negative impact on fitness, species also start competing for mutualistic partners. 
 The possible negative effects of competition for pollinators have been long recognised and widely documented.
-Based mainly on two-species systems, it is currently clear that they have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies as well as driving ecological diferentiation.
+Based mainly on two-species systems, it is currently clear that they have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies as well as driving ecological differentiation.
 However, these competitive interactions between species pairs do not occur in isolation. 
-Plants often ocurr in communities in which multiple competitive interactions operate simultaneusly and lead to emergent phenomena not observed at smaller scales.
+Plants often occur in communities in which multiple competitive interactions operate simultaneously and lead to emergent phenomena not observed at smaller scales.
 
@@
 Here, we explore the role that competition for pollinators plays on the quantity and quality of the pollination service and look for the signature of the mutualistic trade-off in diverse natural communities.
-To tease appart the multiple factors that operate at the community scale we use data that describes both the structure of the interactions and the pollen flows that ocurr within it, all while accounting for the traits of the species that integrate the community.
+To tease apart the multiple factors that operate at the community scale we use data that describes both the structure of the interactions and the pollen flows that occur within it, all while accounting for the traits of the species that integrate the community.
 Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
-Second, we investigate wether there is a relationship between this gain (of both conspecific and heterospecific pollen and by extension the quantity and quality of pollination) and the species degree, functional originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context.
-Third, and finaly, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.
+Second, we investigate whether there is a relationship between this gain (of both conspecific and heterospecific pollen and by extension the quantity and quality of pollination) and the species degree, functional originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context.
+Third, and finally, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.
 
@@
 
-Elucidating how the mechanisms and drivers of facilitation scales to the community level and its theoretical concequences has been elusive in part because of the large amounts of data required.
+Elucidating how the mechanisms and drivers of facilitation scales to the community level and its theoretical consequences has been elusive in part because of the large amounts of data required.
 Previous studies focus on the final picture of interspecific pollen transfer that is obtained by examining the pollen deposited on flower stigmas. 
-However, as we have described, teasing appart competition for pollinators and evaluating wether there is a trade-off between the number of partners and the mutualistic benefit also requires data that describes the structure of the interactions and the pollen flows that ocurr within it, while accounting for the traits of the species that integrate the community.
-Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinean Pampas.
+However, as we have described, teasing apart competition for pollinators and evaluating whether there is a trade-off between the number of partners and the mutualistic benefit also requires data that describes the structure of the interactions and the pollen flows that occur within it, while accounting for the traits of the species that integrate the community.
+Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinian Pampas.
 
@@
 
-We performed sampling in three locations, each located in a distinct phytogeograohic region of the Argentinean Pampas. 
+We performed sampling in three locations, each located in a distinct region of the Argentinian Pampas. 
 The sampling locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and an drier as we move inland and westward towards the Pampean Grasslands.
@@
 
-Abbundance was estimated using two 50 m randomly located transects in each fragment.
-In a first sampling we counted all units of floral attraction taht were found in a 2 m wide strip.
+Abundance was estimated using two 50 m randomly located transects in each fragment.
+In a first sampling we counted all units of floral attraction that were found in a 2 m wide strip.
 In a second sampling we counted and collected all floral visitors while walking at a pace of 10 m per minute [@marrero_effect_2014; @memmott_structure_1999].
@@
 Where the pollen count on an individual was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 
-When the pollen count was above 2,000 grains, we clasified approx. 50% of pollen and total pollen counts were extrapollated [@bosch_plant-pollinator_2009]. 
+When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
 If more than 10 pollen grains from a plant species were identified, we assumed that pollination service between the plant and the pollinator existed. 
-Finally, we analised pollen deposition in a subset of the plant community [@marrero_agricultural_2016]. 
-This subset comprised between three and nine of the most common entomophilus species that were flowering during the samplimg period while ensuring that the chosen species covered a wide range on a specialization-generalization gradient.
-In the selected plants we removed all flowers except buds that were expected to go into inflorecense on the next day. 
+Finally, we analysed pollen deposition in a subset of the plant community [@marrero_agricultural_2016]. 
+This subset comprised between three and nine of the most common entomophilus species that were flowering during the sampling period while ensuring that the chosen species covered a wide range on a specialization-generalization gradient.
+In the selected plants we removed all flowers except buds that were expected to go into inflorescence on the next day. 
 A quarter of these buds were bagged to prevent animal pollination. 
-Two days after inflorecense, we analysed the pollen grains in the flowers' pistils and classified them between conspecific and heterospecific pollen.
+Two days after inflorescence, we analysed the pollen grains in the flowers' pistils and classified them between conspecific and heterospecific pollen.
 
@@
 At the community scale, sharing mutualistic partners might induce competition for pollination mainly trough two mechanisms. 
-The first is competition for visits, where plants with more atractive flowers reduce the number of visits for those less atractive. 
+The first is competition for visits, where plants with more attractive flowers reduce the number of visits for those less attractive. 
 Competition for visits affects the *quantity* of the pollination service as it induces a reduction in the amount of conspecific pollen received by flowers. 
@@
 Second, we use the relative amount of conspecific pollen—the difference between the absolute amount and the that from flowers that were bagged. 
-We use both metrics simultaneously because, in the one hand, the relative amount acknowledges that autogamus self-pollination can ocurr and hence might be a better indication of the pollen that has been actually deposited by mutualistic partners.
+We use both metrics simultaneously because, in the one hand, the relative amount acknowledges that autogamus self-pollination can occur and hence might be a better indication of the pollen that has been actually deposited by mutualistic partners.
 On the other, self-pollination is an adaptive trait [@kalisz_benefits_2003] and some plants are not self-fertile, even if their pollen gets deposited on the stigma. 
@@
 To study the amounts of deposited pollen, which are needed to construct our metrics of pollination quantity and quality, we use three sets of linear fixed models [using the R package `nlme 3.1-131`, @pinheiro_nlme_2018]—two for conspecific pollen (absolute and relative) and one for heterospecific pollen.
-This modelling approach allowed us to simultaneously explore wether there is a relationship between the benefit of animal pollination and several ecological variables that can affect the mutualistic trade-off.
-In addition, to estimate and incorporate the uncertainity associated to our results we used a combination of multi-model inference and bootstrap resampling.
+This modelling approach allowed us to simultaneously explore whether there is a relationship between the benefit of animal pollination and several ecological variables that can affect the mutualistic trade-off.
+In addition, to estimate and incorporate the uncertainty associated to our results we used a combination of multi-model inference and bootstrap resampling.
 
@@
 In each data replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
-We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-logtransformed-or-not) and \@ref(S-fig:fig-deposition-gain-logtransformed-or-not)), this generally offered better results that a generalised linear model with poisson (or quasiposson) error structure.
-Finally, for the models of the relative amounts of pollen we calculated the difference between the pollen density among treatmemts.
+We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-log-transformed-or-not) and \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)), this generally offered better results that a generalised linear model with poisson (or quasiposson) error structure.
+Finally, for the models of the relative amounts of pollen we calculated the difference between the pollen density among treatments.
 
-As predictors in all model sets, we included species degree, the plant relative abbundance, the plant species' share on the pollen pool, and the species' functional originality. 
+As predictors in all model sets, we included species degree, the plant relative abundance, the plant species' share on the pollen pool, and the species' functional originality. 
 Species degree was calculated from combining the quantitative and qualitative visitation networks and corresponds to the number of animal species that were observed to visit the plant species in the community where it was sampled.
-The plant's relative abbundance we simply aggregated the flower counts for each plant species in the community.
-As with the deposition data, we found that log-transforming the abundance counts drastically improved normality (Figure \@ref(S-fig:fig-abundance-logtransformed-or-not)). 
+The plant's relative abundance we simply aggregated the flower counts for each plant species in the community.
+As with the deposition data, we found that log-transforming the abundance counts drastically improved normality (Figure \@ref(S-fig:fig-abundance-log-transformed-or-not)). 
 The species' share of the pollen pool was calculated as the proportion of pollen of that species in the pollen counts being carried by pollinators from the community.
@@
 Functional originality is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016-1].
-Specifically, we recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perenial), flower coloration, and whether the species is native in the study region or not.
-As phenology has been shown to be a key mechanisms of niche diferentiation among plants, we also included the plant abundance in each of the survey months (November to March) as an additional trait in our analysis.
+Specifically, we recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region or not.
+As phenology has been shown to be a key mechanisms of niche differentiation among plants, we also included the plant abundance in each of the survey months (November to March) as an additional trait in our analysis.
 This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits. 
@@
 The species-specific functional coordinates were calculated using the R package `FD 1.0-12` [@laliberte_distance-based_2010; @laliberte_fd_2014]. 
-To faciliate comparison across model estimates, we scaled all independent variables to have a mean of zero and a standard deviation of one.
+To facilitate comparison across model estimates, we scaled all independent variables to have a mean of zero and a standard deviation of one.
 
 In all three sets of models we first evaluated a set of candidate random effects which included random intercepts for plant species as well as random slopes for the relationship between degree and pollen gain.
-In addition we also tested for random intercepts that assumed that the plant species grouping was hierachically nested in either their community, the land use, and the locality. 
+In addition we also tested for random intercepts that assumed that the plant species grouping was hierarchically nested in either their community, the land use, and the locality. 
 We selected the best random structure by comparing the median Akaike Information Criterion (AIC) of evaluated models. 
@@
 This yielded one hundred models for each "candidate formula"---a particular combination of explanatory variables. 
-We then determined the likelyhood of each candidate formula and its relative wheight by calculating the median $\Delta$AIC of the one hundred models that constitute it. 
-As AIC is only useful to compare models with the same response variable, the $\Delta$AIC of each candidate formula was calculated indepenently for each bootstrap resample.
+We then determined the likelihood of each candidate formula and its relative weight by calculating the median $\Delta$AIC of the one hundred models that constitute it. 
+As AIC is only useful to compare models with the same response variable, the $\Delta$AIC of each candidate formula was calculated independently for each bootstrap resample.
 Calculating the median value of each candidate formula allowed us to estimate the relative importance of the explanatory variables  using the standard methods of adding the median weight of the candidate models that included the variable.
 
-To calculate the effect that each variable had on the gain of conspecific and heterospecific pollen we sampled from the estimated coefficients in each candidate model proportional to the median likelyhood of each set.
+To calculate the effect that each variable had on the gain of conspecific and heterospecific pollen we sampled from the estimated coefficients in each candidate model proportional to the median likelihood of each set.
 In other words, the estimated coefficients from more likely candidate constitute a larger share of the distribution of coefficients. 
@@
 Estimating the models using multiple combinations of explanatory variables also allowed us to evaluate the potential collinearity between them.
-To do so we inspect how the effect of the explanatory variables changed across candidate formulaes, when one or more of them were removed in turns.
+To do so we inspect how the effect of the explanatory variables changed across candidate formulae, when one or more of them were removed in turns.
 
@@
 For the quality of pollination, we calculated the mean difference between a sample of the distribution of the effects of conspecific pollen and a sample of those of heterospecific pollen gain.
-Similar to the mean effects on the quantity of pollination, we used bootstrap resamplong to calculate confidence intervals of the means.estimated by the relationship that exists between the gain in cspecific and heterospecific pollen.
+Similar to the mean effects on the quantity of pollination, we used bootstrap resampling to calculate confidence intervals of the means.estimated by the relationship that exists between the gain in conspecific and heterospecific pollen.
 
@@
 We found that, for both the model sets of conspecific and heterospecific pollen, the random structure that was best supported by the data was the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
-When looking at the relative amount of conspecific pollen gained, we observe that only `r round(prop_sig_global*100)`% of species in their communities observed a significant increasse in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
+When looking at the relative amount of conspecific pollen gained, we observe that only `r round(prop_sig_global*100)`% of species in their communities observed a significant increase in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
 We also observed a positive relationship between the gain in heterospecific pollen and both the relative and absolute gain of conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)). 
-The slope of the relationship is such that across plant species in their communitues heterospecific pollen is gained slower than the absolute amount of conspecific pollen but faster than the amount of conspecific pollen relative to the potential selfing.
+The slope of the relationship is such that across plant species in their communities heterospecific pollen is gained slower than the absolute amount of conspecific pollen but faster than the amount of conspecific pollen relative to the potential selfing.
 
@@
 
-Overall we observed that species degree and abundance had a neggative relationship with the gain of both absolute and relative conspecific pollen. 
-Functional originallity had a weak negative relationship with the absolute gain of conspecific pollen but a small positive effect on the relative gain. 
+Overall we observed that species degree and abundance had a negative relationship with the gain of both absolute and relative conspecific pollen. 
+Functional originality had a weak negative relationship with the absolute gain of conspecific pollen but a small positive effect on the relative gain. 
 The plant's share in the community pollen pool, had opposite effects, with a  positive relationship with the absolute gain and a negative relationship with the relative gain of conspecific pollen.
@@
 Using the results from the models of conspecific and heterospecific pollen gain we then examined the relationship between the explanatory variables and the quantity and quality of pollination (Figure \@ref(fig:fig-average-qual-quant)).
-Degree, had a neggative, albeit relativelly small, effect on both the quantity and quality of pollination. 
-The species relative abbundance has a large possitive effect to the quality of pollination accompained by a relatively smaller negative impact on the quantity. 
-Finally, the plant's functional originallity and its share in the pollen pool have a moderate positive impact on its quantity but also a negative impact on the quality.
+Degree, had a negative, albeit relatively small, effect on both the quantity and quality of pollination. 
+The species relative abundance has a large positive effect to the quality of pollination accompanied by a relatively smaller negative impact on the quantity. 
+Finally, the plant's functional originality and its share in the pollen pool have a moderate positive impact on its quantity but also a negative impact on the quality.
 
@@
 * We did find a trade-off between the number of partners a species interacts with and the mutualistic service.
-Interacting with more species alone is often accompained by a decreasse in both the quantity and quality of pollination.
+Interacting with more species alone is often accompanied by a decreases in both the quantity and quality of pollination.
 * However, the effect and importance of this trade-off is comparatively small when considering other factors that describe the species niche and its ecological settings. 
@@
 This relatively small difference is probably very important because, first, some plants simply aren't self-fertile, even if their pollen gets deposited on the stigma.
-Second, in some flowers there is temporary separation in the maturation of the sexes (dichogamy) that favors cross-pollination as, evolutonary, it has been shown to be a better strategy than cloning.
-* Overal it seems like density seems to be a dominant force behind pollen transfer.
-If you have many individuals of your species, you get fewer visits (dilution of the pollinators flying around), which is relfected in a smaller amount of deposited pollen.
+Second, in some flowers there is temporary separation in the maturation of the sexes (dichogamy) that favours cross-pollination as, evolutionary, it has been shown to be a better strategy than cloning.
+* Overall it seems like density seems to be a dominant force behind pollen transfer.
+If you have many individuals of your species, you get fewer visits (dilution of the pollinators flying around), which is reflected in a smaller amount of deposited pollen.
 We show that abundant plants also tend to comprise a greater component of the pollen source pool and so the end result is that get more conspecific pollen per visit than heterospecific pollen.
-* Our result of the comparatively weak effect of the mutualistic trade-off is important because it is fundamentaly related to the way we understand and mathematically represent mutualistic systems. 
-Some of the most widely used theoretical models of pollination account for the negative effects of mutualisim by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree.
+* Our result of the comparatively weak effect of the mutualistic trade-off is important because it is fundamentally related to the way we understand and mathematically represent mutualistic systems. 
+Some of the most widely used theoretical models of pollination account for the negative effects of mutualism by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree.
 This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
-However we show that care must be taken because the neggative effects of the mutualistic trade-off in both the quantity and quality of pollinaton can be offset by density mechanisms.
+However we show that care must be taken because the negative effects of the mutualistic trade-off in both the quantity and quality of pollination can be offset by density mechanisms.
 Species with large degrees also tend be abundant and prolific pollen producers.

### 2018-09-19 paper/manuscript.Rmd
Remove figure pollen density from supplementary.
Not necessary as the second figure takes care of the whole deal

@@
 In each data replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
-We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-log-transformed-or-not) and \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)), this generally offered better results that a generalised linear model with poisson (or quasiposson) error structure.
+We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)), this generally offered better results that a generalised linear model with poisson (or quasiposson) error structure.
 Finally, for the models of the relative amounts of pollen we calculated the difference between the pollen density among treatments.

### 2018-09-19 paper/supp-info.Rmd
Remove figure pollen density from supplementary.
Not necessary as the second figure takes care of the whole deal

@@
 
-```{r fig-deposition-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown)."}
+```{r fig-deposition-log-transformed-or-not, fig.height = 2, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown).", eval=F}
 drake::loadd(fig_pollen_density)

### 2018-09-19 paper/supp-info.Rmd
Improve caption from density figure supplementary
It was not OK for absolute and relative pollen gains. Issue #24

@@
 
-```{r fig-deposition-gain-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of the difference on stigmatic pollen density between open and closed flowers for one of the bootstrap replicates used in the model sets.
-When (A) using directly the gain in pollen density and (B) when pollen density is log transormed prior to calculating the gain.
-"}
+```{r fig-deposition-gain-log-transformed-or-not, fig.height = 1.9, fig.cap = "Distribution of the stigmatic pollen density for one of the bootstrap replicates used in the model sets.
+When (A) using directly the gain in pollen density and (B) when pollen density is log transormed (for the relative amount of conspecific pollen, density was log-transformed prior to calculating the gain).", eval=T}
 drake::loadd(fig_pollen_density_diff)

### 2018-09-19 paper/manuscript.Rmd
Add figure references to main text

@@
 
-Overall we observed that species degree and abundance had a negative relationship with the gain of both absolute and relative conspecific pollen. 
+Overall we observed that species degree and abundance had a negative relationship with the gain of both absolute and relative conspecific pollen (Figure \@ref(fig:fig-model-results-global)). 
 Functional originality had a weak negative relationship with the absolute gain of conspecific pollen but a small positive effect on the relative gain. 
@@
 
-The gain in heterospecific pollen was negatively related to the species abundance but positively to the species' share in the pollen pool, functional originality, and degree. 
+The gain in heterospecific pollen was negatively related to the species abundance but positively to the species' share in the pollen pool, functional originality, and degree (Figure \@ref(fig:fig-model-results-global)).
 Compared to the models of conspecific pollen, the collinearity in the explanatory variables had a larger impact in the models of heterospecific pollen. 

### 2018-09-19 paper/supp-info.Rmd
Adjust figure heights

@@
 
-```{r fig-deposition-gain-log-transformed-or-not, fig.height = 1.9, fig.cap = "Distribution of the stigmatic pollen density for one of the bootstrap replicates used in the model sets.
+```{r fig-deposition-gain-log-transformed-or-not, fig.height = 1.8, fig.cap = "Distribution of the stigmatic pollen density for one of the bootstrap replicates used in the model sets.
 When (A) using directly the gain in pollen density and (B) when pollen density is log transormed (for the relative amount of conspecific pollen, density was log-transformed prior to calculating the gain).", eval=T}
@@
 
-```{r fig-abundance-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been log transformed and scaled to have a mean of zero and a standard deviation of one."}
+```{r fig-abundance-logtransformed-or-not, fig.height = 1.65, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been log transformed and scaled to have a mean of zero and a standard deviation of one."}
 drake::loadd(fig_abundance)

### 2018-09-19 paper/supp-info.Rmd
Shuffle code blocks to the right positions
Close #24

@@
 
-```{r table-species-gain-global, results = 'asis'}
-drake::loadd(significant_gain_global, significant_gain_site, sites)
-
-glance_table(significant_gain_global) %>%
-  dplyr::select(recipient, estimate, statistic, p.value) %>%
-  dplyr::mutate(recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
-  dplyr::rename(`p value` = p.value,
-         `difference` = estimate,
-         `plant species` = recipient) %>%
-  knitr::kable(
-    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
-Tests were performed at the species level (across communities).",
-    escape = FALSE, 
-    booktabs = TRUE, 
-    linesep = c("")) %>%
-  kableExtra::kable_styling(font_size = 8)
-```
-
-```{r table-species-gain-site, results = 'asis'}
-drake::loadd(significant_gain_global, significant_gain_site, sites)
-table_frame <- glance_table(significant_gain_site) %>%
- dplyr::inner_join(sites, by = "site_name") %>%
-  dplyr::group_by(recipient) %>%
-  dplyr::mutate(n_sites = dplyr::n_distinct(site_name)) %>%
-  dplyr::filter(n_sites > 1) %>%
-  dplyr::group_by() %>%
-  dplyr::mutate(site_name = paste(locality_name, land_use, fragment, sep = ' - '),
-         recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
-  dplyr::select(recipient, site_name, estimate, statistic, p.value) %>%
-  dplyr::rename(`p value` = p.value,
-         `difference` = estimate,
-         `plant species` = recipient, 
-         `community` = site_name)
-
-seps <-dplyr::if_else(table_frame$`plant species` == 
-  dplyr::lag(table_frame$`plant species`), "", "\\addlinespace") %>%
-  na.omit()
-
-table_frame %>%
-  knitr::kable(
-    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
-Tests were performed at the community level.
-Only species present in more than one community are shown.",
-    escape = FALSE, 
-    booktabs = TRUE, 
-    linesep = seps, 
-    digits = 3) %>%
-  kableExtra::kable_styling(font_size = 8)
-```
-
-```{r table-variation-across-sites, eval=FALSE, results='asis'}
-drake::loadd(consp_self)
-consp_self %>%
-  anova(test = "Chisq")  %>%
-  knitr::kable(
-    caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).
-Density were modelled using a quasipoisson distribution.
-The model suggests that self-pollination rates are species dependent but not across.',
-    booktabs = TRUE) %>%
-  kableExtra::kable_styling(font_size = 8)
-```
-
-```{r fig-global-community-correlations, fig.height = 2, fig.cap = "Relationship between the model's independent variables calculated at the community level and at the study-wide level."}
-drake::readd(fig_community_global_scatter)
-```
-
-```{r table-aic-random-models, results= 'asis'}
+```{r table-aic-random-models, results= 'asis', eval=T}
 drake::loadd(glanced_random, random_effects)
@@
 
-```{r table-aic-fixed-models, results= 'asis'}
+```{r table-species-gain-global, results = 'asis', eval=T}
+drake::loadd(significant_gain_global, significant_gain_site, sites)
+
+glance_table(significant_gain_global) %>%
+  dplyr::select(recipient, estimate, statistic, p.value) %>%
+  dplyr::mutate(recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
+  dplyr::rename(`p value` = p.value,
+         `difference` = estimate,
+         `plant species` = recipient) %>%
+  knitr::kable(
+    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
+Tests were performed at the species level (across communities).",
+    escape = FALSE, 
+    booktabs = TRUE, 
+    linesep = c("")) %>%
+  kableExtra::kable_styling(font_size = 8)
+```
+
+```{r table-aic-fixed-models, results= 'asis', eval=T}
 drake::loadd(model_formula_ranking)
@@
 
-```{r fig-correlation, fig.height = 4.5, fig.cap = "Corelation between the explanatory variables included in the statistical models."}
+```{r fig-correlation, fig.height = 4.5, fig.cap = "Corelation between the explanatory variables included in the statistical models.", eval=T}
 drake::readd(fig_correlation)
@@
 ```{r fig-model-results, fig.height = 7, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
-Only results for the models with the most parsimonous fixed effects.
-"}
+Only results for the models with the most parsimonous fixed effects.", eval=T}
 drake::readd(fig_all_model_results)
@@
 
-```{r fig_effect_quant_qual, fig.height=3.5, fig.cap="asd"}
+```{r table-species-gain-site, results = 'asis', eval=F}
+drake::loadd(significant_gain_global, significant_gain_site, sites)
+table_frame <- glance_table(significant_gain_site) %>%
+ dplyr::inner_join(sites, by = "site_name") %>%
+  dplyr::group_by(recipient) %>%
+  dplyr::mutate(n_sites = dplyr::n_distinct(site_name)) %>%
+  dplyr::filter(n_sites > 1) %>%
+  dplyr::group_by() %>%
+  dplyr::mutate(site_name = paste(locality_name, land_use, fragment, sep = ' - '),
+         recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
+  dplyr::select(recipient, site_name, estimate, statistic, p.value) %>%
+  dplyr::rename(`p value` = p.value,
+         `difference` = estimate,
+         `plant species` = recipient, 
+         `community` = site_name)
+
+seps <-dplyr::if_else(table_frame$`plant species` == 
+  dplyr::lag(table_frame$`plant species`), "", "\\addlinespace") %>%
+  na.omit()
+
+table_frame %>%
+  knitr::kable(
+    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
+Tests were performed at the community level.
+Only species present in more than one community are shown.",
+    escape = FALSE, 
+    booktabs = TRUE, 
+    linesep = seps, 
+    digits = 3) %>%
+  kableExtra::kable_styling(font_size = 8)
+```
+
+```{r table-variation-across-sites, eval=FALSE, results='asis', eval=F}
+drake::loadd(consp_self)
+consp_self %>%
+  anova(test = "Chisq")  %>%
+  knitr::kable(
+    caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).
+Density were modelled using a quasipoisson distribution.
+The model suggests that self-pollination rates are species dependent but not across.',
+    booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8)
+```
+
+```{r fig-global-community-correlations, fig.height = 2, fig.cap = "Relationship between the model's independent variables calculated at the community level and at the study-wide level.", eval=F}
+drake::readd(fig_community_global_scatter)
+```
+
+```{r fig_effect_quant_qual, fig.height=3.5, fig.cap="asd", eval=F}
 drake::loadd(fig_effect_quant_qual)
@@
 ```
-
-# References

### 2018-09-19 paper/manuscript.Rmd
Update paper's TODO

@@
 * Spell-check everything
-* Finish off the supplementary materials
 * Write the abstract

### 2018-10-16 paper/manuscript.Rmd
Add hugo's address
Close #28
Add Fer's Hugo's and Daniel's awknowledgements
Issue #29

@@
 
-^2^ Hugo's address
+^2^ Centro de Recursos Naturales Renovables de las Zonas Semiáridas, CONICET, Camino de la Carrindanga Km. 7, 8000 Bahía Blanca, Argentina
 
@@
 
+# Acknowledgements
+
+We thank  Cátedra de Botánica General, Facultad de Agronomía, Universidad de Buenos Aires. 
+The Agrasar and Bordeu families, and the University of Buenos Aires, for logistical support and permission to conduct this study at estancias Anquilóo, Las Chilcas and San Claudio, respectively.  
+Field work was supported by grants PICT 08–12504 and 0851. 
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, and a New Zealand International Doctoral Research Scholarship.
+DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society Te Aparangi.
+
 # References

### 2018-10-18 paper/manuscript.Rmd
remove extra space in awknoledgements
Add Jason's funding
Close #29
list changes to the manuscript

@@
 \clearpage
+
+### Changes
+
+* Use AICc instead of AIC (no change in results)
+* To keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances
+* Columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits
+* Boostraping resampling worked
 
@@
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, and a New Zealand International Doctoral Research Scholarship.
-DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society Te Aparangi.
+DBS and JMT acknowledge the support of a Rutherford Discovery Fellowship. 
+DBS also awknoledges the Marsden Fund Council from New Zealand Government funding.
 

### 2018-10-22 paper/manuscript.Rmd
Add figure con-con
Close #39

@@
 
-```{r fig-trade-off-predictions, fig.height= 2.3, fig.width = 3.25, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
+```{r fig-trade-off-predictions, fig.height= 3, fig.width = 6.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
 Each dot indicates the predicted median gains for a species in its community (which correspons to the selected random effects in all of our models).
@@
 The dashed line indicates the isoline at which heterospecific pollen is gained at the same rate than conspecific pollen."}
-# pdf(width = 3.25, height = 3.1)
-  drake::readd(fig_con_hetero_gain)
+# pdf(width = 6.5, height = 3.25)
+  cowplot::plot_grid(
+    drake::readd(fig_con_con),
+    drake::readd(fig_con_hetero_gain))
   # dev.off()

### 2018-10-22 code/make_fig_con_hetero_gain.R

@@ -108,3 +108,84 @@ get_pred_range <- function(tidied_fixed, x, var_trans = "log", scale = "global")
     estimate %>% 
     range()
 }
+
+make_fig_con_con <- function(model_formula_ranking, model_linear_fits_species){
+  
+  require(ggplot2)
+  
+  major_labs <- c(0,10,100, 1000, 10000)
+  minor_labs <- c(0, 5, 10, 50, 100, 500, 1000, 10000)
+  major_breaks <- log(major_labs + 1)
+  minor_breaks <- log(minor_labs + 1)
+  
+  model_weights <- model_formula_ranking$aggregated %>%
+    # dplyr::filter(scale == "community") %>%
+    # dplyr::group_by(pollen_category) %>%
+    dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
+                  weight = get_weights(likelyhood)) %>%
+    dplyr::select(fixed_formula, weight)
+  
+  points_sp <- model_linear_fits_species %>%
+    dplyr::filter(var_trans == "log",
+                  scale == "community") %>% 
+    #   tidyr::spread(data = ., key = sma_parameter, value = value) %>% 
+    dplyr::inner_join(model_weights, by = "fixed_formula") %>% 
+    dplyr::group_by(site_name, plant_name, scale, model) %>%
+    dplyr::sample_n(size = 1, weight = weight) %>%
+    dplyr::group_by() %>%
+    tidyr::gather("con_type", "conspecific", dplyr::contains("conspecific")) 
+  
+  points_sp_con <- points_sp %>%
+    tidyr::spread(con_type, conspecific)
+  
+  points_sp_summarised_con <- points_sp_con  %>%
+    dplyr::group_by(plant_name, site_name) %>%
+    dplyr::summarise_at(dplyr::vars(dplyr::contains("specific")), 
+                        dplyr::funs(median, quantile_05,quantile_95), na.rm = T) %>%
+    dplyr::mutate_if(is.numeric, I)
+  
+  # conspecific abs vs control
+  points_sp_con  %>% 
+    ggplot() +
+    geom_abline(slope = 1, intercept = 0, size = 0.25, linetype = 2) +
+    geom_errorbar(data = points_sp_summarised_con,
+                  aes(x = conspecific_ctr_median,
+                      ymin = conspecific_abs_quantile_05,
+                      ymax = conspecific_abs_quantile_95),
+                  show.legend = F, alpha = 0.25) +
[…]

### 2018-10-22 main.R

@@ -160,6 +160,7 @@ analyses_plan <- rbind(
 figure_plan <- drake::drake_plan(
   fig_model_results_global = make_fig_model_results_global(tidied_fixed), 
   fig_con_hetero_gain = make_fig_con_hetero_gain(tidied_fixed, model_linear_fits, model_formula_ranking, model_linear_fits_species), 
+  fig_con_con = make_fig_con_con(model_formula_ranking, model_linear_fits_species),
   fig_proportion_vs_variables = make_fig_proportion_vs_variables(trade_off_predictions),
   fig_pollen_density = make_fig_pollen_density(dep_frame), 
   fig_pollen_density_diff = make_fig_pollen_density_diff(rep_1), 

### 2018-11-06 paper/manuscript.Rmd
Add some refs to intro
Issue #12

@@
 
-Pollination systems play a disproportionally important role in food production and maintenance of global biodiversity. 
+Pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
 In the context of animal pollination, the support to biodiversity is fundamentally achieved by virtue of intra-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plants.
-Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources. 
-Indeed, studies that are fundamental to our current knowledge of mutualism predict that an upper limit to biodiversity is achieved when the number of mutualistic partners is maximised in a community. 
+Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources [@stachowicz_mutualism_2001]. 
+Indeed, studies that are fundamental to our current knowledge of mutualism predict that an upper limit to biodiversity is achieved when the number of mutualistic partners is maximised in a community [@bastolla_architecture_2009].
 And yet, fully connected natural pollination communities do not exist.

### 2018-11-06 paper/manuscript.Rmd
Update changelog

@@
 * Columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits
-* Boostraping resampling worked
+* Only modeling open and bagged pollen counts, using the bagged as a control. So not showing the results of the relative pollen count (open vs bagged flowers) anymore
+* Introduced visit efficiency instead of share in the pollen pool as it is a better predictor. 
+* Use a PCA of the explanatory variables to understand different plant strategies
 

### 2018-11-06 paper/manuscript.Rmd
Add info drivers of competition for pollination

@@
 
-This is so, because sharing a mutualistic partner also has costs. 
+This is so, because sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
 The end result is that, when the cumulative costs have a negative impact on fitness, species also start competing for mutualistic partners.   
-The possible negative effects of competition for pollinators have been long recognised and widely documented.
-Based mainly on two-species systems, it is currently clear that they have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies as well as driving ecological differentiation.
-However, these competitive interactions between species pairs do not occur in isolation. 
+The possible negative effects of competition for pollinators have been long recognised [@robertson_philosophy_1895] and widely documented both experimentally [@lewis_experimental_1961] and theoretically [@levin_competition_1970].
+Multiple factors (like the number of shared pollinators, the plants relative abundance, the visitator fidelity, and phenology and other traits) have been shown to modulate the strength of competition and in turn the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_pollinationiscommunity_1987; @campbell_pollinator_1985].
+It is currently clear that they have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as driving ecological differentiation [@mitchell_new_2009].
+With few exceptions [@rathcke_interactions_1988; lopezaraizamikel_impact_2007], these findings are based on two-species systems, nevertheless, competitive interactions between species pairs do not occur in isolation.
 Plants often occur in communities in which multiple competitive interactions operate simultaneously and lead to emergent phenomena not observed at smaller scales.

### 2018-11-06 paper/manuscript.Rmd
Minor text amendments to second paragraph of intro

@@
 Multiple factors (like the number of shared pollinators, the plants relative abundance, the visitator fidelity, and phenology and other traits) have been shown to modulate the strength of competition and in turn the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_pollinationiscommunity_1987; @campbell_pollinator_1985].
-It is currently clear that they have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as driving ecological differentiation [@mitchell_new_2009].
-With few exceptions [@rathcke_interactions_1988; lopezaraizamikel_impact_2007], these findings are based on two-species systems, nevertheless, competitive interactions between species pairs do not occur in isolation.
-Plants often occur in communities in which multiple competitive interactions operate simultaneously and lead to emergent phenomena not observed at smaller scales.
+It is currently clear that these neghative effects on fitness have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as driving ecological differentiation [@mitchell_new_2009].
+With few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007], these findings are based on two-species systems, nevertheless, competitive interactions between species pairs do not occur in isolation.
+Instead, plants often occur in communities in which multiple competitive interactions operate simultaneously and lead to emergent phenomena not observed at smaller scales.
 

### 2018-11-08 paper/manuscript.Rmd
Minor edits second paraphraph intro

--- 2018-11-06 paper/manuscript.Rmd
@@
 The possible negative effects of competition for pollinators have been long recognised [@robertson_philosophy_1895] and widely documented both experimentally [@lewis_experimental_1961] and theoretically [@levin_competition_1970].
-Multiple factors (like the number of shared pollinators, the plants relative abundance, the visitator fidelity, and phenology and other traits) have been shown to modulate the strength of competition and in turn the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_pollinationiscommunity_1987; @campbell_pollinator_1985].
-It is currently clear that they have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as driving ecological differentiation [@mitchell_new_2009].
-With few exceptions [@rathcke_interactions_1988; lopezaraizamikel_impact_2007], these findings are based on two-species systems, nevertheless, competitive interactions between species pairs do not occur in isolation.
-Plants often occur in communities in which multiple competitive interactions operate simultaneously and lead to emergent phenomena not observed at smaller scales.
+Multiple factors (like the number of shared pollinators, the plants' relative abundance, visitator fidelity, and traits) have been shown to modulate the strength of competition and in turn the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_pollinationiscommunity_1987; @campbell_pollinator_1985].
+It is currently clear that these neghative effects on fitness have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as driving ecological differentiation [@mitchell_new_2009; @caruso_competition_2000].
+With few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007], these findings are based mostly on two-species systems.
+However, competitive interactions between species pairs do not occur in isolation.
 

### 2018-11-08 paper/manuscript.Rmd
Adapt third paragraph intro with references

@@
 
+Instead, plants often occur in communities in which multiple intertwined factors operate simultaneously and lead to emergent phenomena not observed at smaller scales. 
+For instance, recent empirical evidence suggest that species with original traits generally have fewer interaction partners [@coux_linking_2016]. 
+This evidence is aligned with the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
+If evolutionary specialisation occur by changing traits to focus on fewer but better partners, we should expect a reduction of competition for pollination in species with original traits and an increasse in species with a large number of interaction partners.
+Alternatively, it might also be the case that density is the dominant force driving pollen transfer. 
+Abundant species might experience a dilution of the available pollinators but might also comprise a greater component of the pollen source pool being transported by pollinators. 
+In this case, a potential reduction in the quantity of pollination (the amount of conspecific pollen received) could be compensated by an increase in the quality of pollination (the amount of conspecific relative to heterospecific pollen received).
+When we take into account the fact that for example a species' generalism and its relative abundance are likely to be positively associated [@sargent_role_2006], distinguishing the strategies that plants might adopt to minimise competition becomes even harder because coorelated factors might lead to competing costs.
+
+Elucidating competition for pollination at the community scale and the plants strategies to minimise it has been elusive is the sheer amount of data necessary to dissentangle them.
+
 Perhaps the most obvious ecological factor influencing the cost of sharing pollinators is the species degree---the number of interaction partners. 
@@
 Furthermore, although the relationship between degree and the costs of the pollination service is relatively intuitive, elucidating the magnitude of the trade-off at the community scale has been elusive because multiple other factors like traits, abundance, and the share of the pollen pool might be involved.
-For instance, recent empirical evidence suggest that species with original traits (far from the community centroid) generally have fewer interaction partners. 
-This evidence is aligned with the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
-If evolutionary specialisation occur by changing traits to focus on fewer but better partners, we should expect a reduction of competition for pollination in species with original traits. 
-Alternatively, it might also be the case that density is the dominant force driving pollen transfer. 
-Abundant species might experience a dilution of the available pollinators but might also comprise a greater component of the pollen source pool being transported by pollinators. 
-In this case, a potential reduction in the quantity of pollination could be compensated by an increase in the quality of pollination.
 

### 2018-11-10 paper/manuscript.Rmd
Updated change summary and to-do list

@@
 
-* Use AICc instead of AIC (no change in results)
-* To keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances
-* Columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits
-* Only modeling open and bagged pollen counts, using the bagged as a control. So not showing the results of the relative pollen count (open vs bagged flowers) anymore
-* Introduced visit efficiency instead of share in the pollen pool as it is a better predictor. 
-* Use a PCA of the explanatory variables to understand different plant strategies
+* Now using AICc instead of AIC to evaluate models (no change in results)
+* Changes to traits: (*a*) to keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances.
+Also, now (*b*) columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits.
+* The absolute/relative/gain terminology was confusing. Now  I'm modeling open and bagged pollen counts directly, using the bagged as a sort of control.
+* Introduced visit efficacy instead of share in the pollen pool as a predictor in the model.
+Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models.
+* Now I use a PCA of the explanatory variables to understand different plant strategies. 
+* Introduction has been rewritten to be more *hypothesis* oriented. The manuscript also includes references thorughout.
+* Added abstract
 
@@
 
-* References to the introduction
-* Discussion from bullet-points to actual paragraphs. I will do that once we all agree with the quantitative methodology and getting some contributions for the interpretation of the results
 * Spell-check everything
-* Write the abstract
+* Decide on a journal. Manuscript is currently written for an interdisciplinary one.
 
@@
 
-* __Originality__: Currently the plants phenology are included in the traits.
-The relative abundance of the plant in each of the five a survey months is included as a trait.
-This allows to maintain the model simple and it could be easily argued that phenological strategy can be considered as another trait.
-However I'm not convinced that it is a good idea to keep them together, especially because differences in phenology is a rather intuitive factor/strategy to overcome competition for pollination.
-Do you think I should separate traits from phenology?
-If yes, should I use the same "originality" approach to determine how different each species is?
 * __Traits__: Currently I don't mention much traits in the discussion.
@@
 Only 4 traits have been compiled: growth form, longevity, flower colour, and whether the plant is native to the region.
-It won't be possible to gather all of the traits used by @coux_linking_2016-1 from the literature but hopefully it is for a good proportion of them.
+It won't be possible to gather all of the traits used by @coux_linking_2016 from the literature but hopefully it is for a good proportion of them.
 Daniel and Jason, could we discuss options here?
-* __Conspecific pollen__: Previously I used, as Hugo did in his papers, the gain in conspecific pollen in open flowers relative to the amount of in bagged flowers as the indication of the "quantity" of the pollination service.
-After thinking more about the limitations of this metric (pollinators also take pollen from stigmas, some plants are not self-fertile, different maturation times for male/female organs, etc.) I decided it would be best to include both the total and the relative pollen amounts in the manuscript.
-This add more nuance to the story and interpretation which is not cool, but I think together they overcome each other's problems.
-What do you think about it?
-* __Naming__: I currently use absolute and relative pollen gain as names for the two previous metrics. I think it's OK but I feel there might be better options. Any ideas?
-* __Quantity & quality__: This version of the paper uses quantity/quality to frame the results.
-I think that's pretty neat.
-However, different studies define quantity and quality in different ways.
-Hugo for example used the relative amount of conspecific pollen as an indication of quantity and the amount of heterospecific pollen for quality.
-We discussed earlier that a good indication could be the _proportion_ of heterospecific pollen instead.
-What do you think?
-Should I ditch quantity/quality and stick to conspecific/heterospecific pollen instead?
-Should I stay with the current definitions of quantity and quality of pollination?
-This probably needs meeting/Skype, but it would be good to think about it.
-* __Pollen transfer__: Currently all I'm using from the pollen transfer networks is the share of a plant in the pollen pool.
-That fits nice with the density hypothesis but its rather simplistic.
-Any ideas?
-* __Pollen in bagged flowers__: Jason, you mentioned that pollen in bagged flowers can be due to selfing or wind.
-You meant wind moving flowers and that causing pollen to be deposited on stigmas?
-Wouldn't that count as selfing too?
 

### 2018-11-11 paper/manuscript.Rmd
Add last paragraph intro

@@
 
-Elucidating competition for pollination at the community scale and the plants strategies to minimise it has been elusive is the sheer amount of data necessary to dissentangle them.
-
-Perhaps the most obvious ecological factor influencing the cost of sharing pollinators is the species degree---the number of interaction partners. 
-Yet, evidence at the community scale of **the mutualistic trade-off**---the extent to which species degree affects the benefit---is scarce, to say the least. 
-Furthermore, although the relationship between degree and the costs of the pollination service is relatively intuitive, elucidating the magnitude of the trade-off at the community scale has been elusive because multiple other factors like traits, abundance, and the share of the pollen pool might be involved.
-
-Here, we explore the role that competition for pollinators plays on the quantity and quality of the pollination service and look for the signature of the mutualistic trade-off in diverse natural communities.
-To tease apart the multiple factors that operate at the community scale we use data that describes both the structure of the interactions and the pollen flows that occur within it, all while accounting for the traits of the species that integrate the community.
-Specifically, we first estimate the gain on pollen that can be attributed to the mutualistic interactions. 
-Second, we investigate whether there is a relationship between this gain (of both conspecific and heterospecific pollen and by extension the quantity and quality of pollination) and the species degree, functional originality, abundance, and contribution to the pollen pool, which together describe the role of the plant species and the ecological context.
-Third, and finally, we explore how these variables shape the quantity and quality of pollination and ultimately the competition for pollinators.
+Here, we explore competiton for pollination at the community scale using comprehensive empirical data from eleven plant-pollinator communities in the Argentinean Pampas. 
+First, we ask the extent to which the outcome of animal mediated pollination is facilitation or competition. 
+If facilitation is the primary outcome we would expect (*i*) a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than that due to self-pollination and (*ii*) an overall positive relationship between the amount of conspecific pollen deposited in stigmas and that that would be achieved [@tur_evaluating_2016].
+Second, we investigate the relative contribution that four ecological factors, that together, describe the role of the plant species and the ecological context, have on competition for pollination. 
+We hypothesize that competition for pollination at the community level should increasse as the number of pollination partners a plant has increasses (species degree).
+However, other factors like the plant's functional originality, its relative abbundance, and the visit effectiveness, should have the potential to compensate this increasse in competition by improving either the quality or the quality of pollination.
+Third, and finally, we explore how plants differ on how they use these factors to minimise competition. 
+Although some plant species might be widespread across multiple locations, competition for pollinators ocurrs at the community level and are hence defined by the ecologica context. 
+If plant species adopt comparable roles across different communities we should expect plant strategies to be more similar within species than across species in the study. 
+On the contrary, if species role is flexible, we should expect plants to be able to adopt different strategies in each community such that competition is more optimaly minimised depending on the context.
 

### 2018-11-11 paper/manuscript.Rmd
Reorganise references intro

@@
 The possible negative effects of competition for pollinators have been long recognised [@robertson_philosophy_1895] and widely documented both experimentally [@lewis_experimental_1961] and theoretically [@levin_competition_1970].
-Multiple factors (like the number of shared pollinators, the plants' relative abundance, visitator fidelity, and traits) have been shown to modulate the strength of competition and in turn the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_pollinationiscommunity_1987; @campbell_pollinator_1985].
-It is currently clear that these neghative effects on fitness have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as driving ecological differentiation [@mitchell_new_2009; @caruso_competition_2000].
-With few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007], these findings are based mostly on two-species systems.
+Multiple factors (like the number of shared pollinators, the plants' relative abundance, visitator fidelity, and traits) have been shown to modulate the strength of competition and in turn the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_effects_1987; @campbell_pollinator_1985].
+It is currently clear that the effects of these factors on fitness have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as driving ecological differentiation [@mitchell_new_2009; @caruso_competition_2000].
+
+The main two mechanisms through which these ecological factors can affect plant fertilization are (i) by reducing the amount of conspecific pollen loads on stigmas or (ii) by increassing the deposition of heterospecific pollen [@morales_interspecific_2008].
+For example, plants with more atrtactive flowers might reduce the number of visits---and hence the amount of conspecific pollen---for those less attractive [@yang_pollinator_2011]. 
+We denote this as the the *quantity* of the pollination service. 
+More subtly, when plants share pollination partners, even receiving a visit might not translate into fertilization due to interspecific pollen transfer [@campbell_mechanism_1985]. 
+Interspecific pollen transfer affects the pollination service because a focal plant might receive pollen from a different species, or conversely pollen from the focal plant might be lost to different species.
+Generally speaking, the higher the proportion of conspecific relative to heterospecific pollen the higher the *quality* of the pollination service. 
+With few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about competition vs.
+facilitation in pollination systems and its relationship to the quantity and quality of pollination is based mostly on two-species systems.
 However, competitive interactions between species pairs do not occur in isolation.
@@
 This evidence is aligned with the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
-If evolutionary specialisation occur by changing traits to focus on fewer but better partners, we should expect a reduction of competition for pollination in species with original traits and an increasse in species with a large number of interaction partners.
-Alternatively, it might also be the case that density is the dominant force driving pollen transfer. 
-Abundant species might experience a dilution of the available pollinators but might also comprise a greater component of the pollen source pool being transported by pollinators. 
+If evolutionary specialisation occur by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollination in species with original traits and an increasse in species with a large number of interaction partners [@gibson_can_2012].
+Alternatively, it might also be the case that density is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
+Abundant species might experience a dilution of the available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both the pollen being transported by pollinators and animal visits compared to other species.
 In this case, a potential reduction in the quantity of pollination (the amount of conspecific pollen received) could be compensated by an increase in the quality of pollination (the amount of conspecific relative to heterospecific pollen received).
-When we take into account the fact that for example a species' generalism and its relative abundance are likely to be positively associated [@sargent_role_2006], distinguishing the strategies that plants might adopt to minimise competition becomes even harder because coorelated factors might lead to competing costs.
+To complicate things more, autonomus self-pollination can also influence a plant sensitivity to competition for pollination because it can ensure reproduction even in the absense of outcross pollen [@kalisz_benefits_2003].
+As multiple, potentially correlated, factors may act simultaneously, understanding their relative importance and how plant species harness them to minimise competition for pollination within their communities requires extensive data describing both the structure of the interactions and the pollen flows that occur within it.
 

### 2018-11-11 paper/manuscript.Rmd
Move quantity/quality from methods to intro

@@
 ## Data analysis
-
-At the community scale, sharing mutualistic partners might induce competition for pollination mainly trough two mechanisms. 
-The first is competition for visits, where plants with more attractive flowers reduce the number of visits for those less attractive. 
-Competition for visits affects the *quantity* of the pollination service as it induces a reduction in the amount of conspecific pollen received by flowers. 
-The second, more subtle, mechanism is interspecific pollen transfer, where even receiving a visit might not translate into net facilitation. 
-Interspecific pollen transfer affects the *quality* of the pollination service because a focal plant might receive pollen from a different species, or conversely pollen from the focal plant might be lost to different species.
-Generally speaking the larger the proportion of conspecific relative to heterospecific pollen the higher the quality of the pollination service.
 

### 2018-11-11 paper/manuscript.Rmd
Spellcheck to changes section

@@
 Also, now (*b*) columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits.
-* The absolute/relative/gain terminology was confusing. Now  I'm modeling open and bagged pollen counts directly, using the bagged as a sort of control.
-* Introduced visit efficacy instead of share in the pollen pool as a predictor in the model.
+* The absolute/relative/gain terminology was confusing. Now  I'm modelling open and bagged pollen counts directly, using the bagged as a sort of control.
+* Introduced visit efficacy instead of the share in the pollen pool as a predictor in the model.
 Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models.
 * Now I use a PCA of the explanatory variables to understand different plant strategies. 
-* Introduction has been rewritten to be more *hypothesis* oriented. The manuscript also includes references thorughout.
+* Introduction has been rewritten to be more *hypothesis* oriented. The manuscript also includes references throughout.
 * Added abstract
@@
 * Spell-check everything
-* Decide on a journal. Manuscript is currently written for an interdisciplinary one.
+* Decide on a journal. The manuscript is currently written for an interdisciplinary one. 
+* Check reference list
 
@@
 
-* __Traits__: Currently I don't mention much traits in the discussion.
-I think the trait component is valuable and interesting but sadly at the moment the data quality is poor.
+* __Traits__: Currently I don't mention traits in the discussion.
+I think the trait component is valuable and interesting but sadly at the moment, the data quality is poor.
 Only 4 traits have been compiled: growth form, longevity, flower colour, and whether the plant is native to the region.
-It won't be possible to gather all of the traits used by @coux_linking_2016 from the literature but hopefully it is for a good proportion of them.
+It won't be possible to gather all of the traits used by @coux_linking_2016 from the literature but hopefully, it is for a good proportion of them.
 Daniel and Jason, could we discuss options here?

### 2018-11-11 paper/manuscript.Rmd
Spellcheck intro

@@
 
-This is so, because sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
+This is so because sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
 The end result is that, when the cumulative costs have a negative impact on fitness, species also start competing for mutualistic partners.   
 The possible negative effects of competition for pollinators have been long recognised [@robertson_philosophy_1895] and widely documented both experimentally [@lewis_experimental_1961] and theoretically [@levin_competition_1970].
-Multiple factors (like the number of shared pollinators, the plants' relative abundance, visitator fidelity, and traits) have been shown to modulate the strength of competition and in turn the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_effects_1987; @campbell_pollinator_1985].
+Multiple factors (like the number of shared pollinators, the plants' relative abundance, visitor fidelity, and traits) have been shown to modulate the strength of competition and in turn the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_effects_1987; @campbell_pollinator_1985].
 It is currently clear that the effects of these factors on fitness have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as driving ecological differentiation [@mitchell_new_2009; @caruso_competition_2000].
 
-The main two mechanisms through which these ecological factors can affect plant fertilization are (i) by reducing the amount of conspecific pollen loads on stigmas or (ii) by increassing the deposition of heterospecific pollen [@morales_interspecific_2008].
-For example, plants with more atrtactive flowers might reduce the number of visits---and hence the amount of conspecific pollen---for those less attractive [@yang_pollinator_2011]. 
-We denote this as the the *quantity* of the pollination service. 
+The main two mechanisms through which these ecological factors can affect plant fertilization are (i) by reducing the number of conspecific pollen grains on stigmas or (ii) by increasing the deposition of heterospecific pollen [@morales_interspecific_2008].
+For example, plants with more attractive flowers might reduce the number of visits---and hence the amount of conspecific pollen---for those less attractive [@yang_pollinator_2011]. 
+We denote this as the *quantity* of the pollination service. 
 More subtly, when plants share pollination partners, even receiving a visit might not translate into fertilization due to interspecific pollen transfer [@campbell_mechanism_1985]. 
-Interspecific pollen transfer affects the pollination service because a focal plant might receive pollen from a different species, or conversely pollen from the focal plant might be lost to different species.
+Interspecific pollen transfer affects the pollination service because a focal plant might receive pollen from a different species, or conversely, pollen from the focal plant might be lost to different species.
 Generally speaking, the higher the proportion of conspecific relative to heterospecific pollen the higher the *quality* of the pollination service. 
@@
 Instead, plants often occur in communities in which multiple intertwined factors operate simultaneously and lead to emergent phenomena not observed at smaller scales. 
-For instance, recent empirical evidence suggest that species with original traits generally have fewer interaction partners [@coux_linking_2016]. 
+For instance, recent empirical evidence suggests that species with original traits generally have fewer interaction partners [@coux_linking_2016]. 
 This evidence is aligned with the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
-If evolutionary specialisation occur by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollination in species with original traits and an increasse in species with a large number of interaction partners [@gibson_can_2012].
+If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollination in species with original traits and an increase in species with a large number of interaction partners [@gibson_can_2012].
 Alternatively, it might also be the case that density is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
@@
 In this case, a potential reduction in the quantity of pollination (the amount of conspecific pollen received) could be compensated by an increase in the quality of pollination (the amount of conspecific relative to heterospecific pollen received).
-To complicate things more, autonomus self-pollination can also influence a plant sensitivity to competition for pollination because it can ensure reproduction even in the absense of outcross pollen [@kalisz_benefits_2003].
+To complicate things more, autonomous self-pollination can also influence a plant sensitivity to competition for pollination because it can ensure reproduction even in the absence of outcross pollen [@kalisz_benefits_2003].
 As multiple, potentially correlated, factors may act simultaneously, understanding their relative importance and how plant species harness them to minimise competition for pollination within their communities requires extensive data describing both the structure of the interactions and the pollen flows that occur within it.
 
-Here, we explore competiton for pollination at the community scale using comprehensive empirical data from eleven plant-pollinator communities in the Argentinean Pampas. 
-First, we ask the extent to which the outcome of animal mediated pollination is facilitation or competition. 
+Here, we explore competition for pollination at the community scale using comprehensive empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
+First, we ask the extent to which the outcome of animal-mediated pollination is facilitation or competition. 
 If facilitation is the primary outcome we would expect (*i*) a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than that due to self-pollination and (*ii*) an overall positive relationship between the amount of conspecific pollen deposited in stigmas and that that would be achieved [@tur_evaluating_2016].
 Second, we investigate the relative contribution that four ecological factors, that together, describe the role of the plant species and the ecological context, have on competition for pollination. 
-We hypothesize that competition for pollination at the community level should increasse as the number of pollination partners a plant has increasses (species degree).
-However, other factors like the plant's functional originality, its relative abbundance, and the visit effectiveness, should have the potential to compensate this increasse in competition by improving either the quality or the quality of pollination.
-Third, and finally, we explore how plants differ on how they use these factors to minimise competition. 
-Although some plant species might be widespread across multiple locations, competition for pollinators ocurrs at the community level and are hence defined by the ecologica context. 
+We hypothesize that competition for pollination at the community level should increase as the number of pollination partners a plant has increases (species degree).
+However, other factors like the plant's functional originality, its relative abundance, and the visit effectiveness, should have the potential to compensate this increase in competition by improving either the quality or the quality of pollination.
+Third, and finally, we explore how plants differ in how they use these factors to minimise competition. 
+Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and are hence defined by the ecological context. 
 If plant species adopt comparable roles across different communities we should expect plant strategies to be more similar within species than across species in the study. 
-On the contrary, if species role is flexible, we should expect plants to be able to adopt different strategies in each community such that competition is more optimaly minimised depending on the context.
+On the contrary, if species role is flexible, we should expect plants to be able to adopt different strategies in each community such that competition is more optimally minimised depending on the context.
 

### 2018-11-11 paper/manuscript.Rmd
Finish Hugo's comments to intro

@@
 Pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
-In the context of animal pollination, the support to biodiversity is fundamentally achieved by virtue of intra-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plants.
+In the context of animal pollination, the support to biodiversity is fundamentally achieved by virtue of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plants.
 Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources [@stachowicz_mutualism_2001]. 

### 2018-11-11 paper/manuscript.Rmd
Finish Jason's comments to intro

@@
 Indeed, studies that are fundamental to our current knowledge of mutualism predict that an upper limit to biodiversity is achieved when the number of mutualistic partners is maximised in a community [@bastolla_architecture_2009].
-And yet, fully connected natural pollination communities do not exist.
+And yet, not every species of pollinator in natural communities interacts with every species of plant.
 
 This is so because sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
-The end result is that, when the cumulative costs have a negative impact on fitness, species also start competing for mutualistic partners.   
+As soon as there are costs plant start competing for mutualistic partners, even if this competition is not strong enough to produce a **net** negative effect in fitness.
 The possible negative effects of competition for pollinators have been long recognised [@robertson_philosophy_1895] and widely documented both experimentally [@lewis_experimental_1961] and theoretically [@levin_competition_1970].
@@
 
-The main two mechanisms through which these ecological factors can affect plant fertilization are (i) by reducing the number of conspecific pollen grains on stigmas or (ii) by increasing the deposition of heterospecific pollen [@morales_interspecific_2008].
+The main two mechanisms through which these ecological factors can affect plant fertilization are (*i*) by reducing the number of conspecific pollen grains on stigmas or (*ii*) by increasing the deposition of heterospecific pollen [@morales_interspecific_2008].
 For example, plants with more attractive flowers might reduce the number of visits---and hence the amount of conspecific pollen---for those less attractive [@yang_pollinator_2011]. 

### 2018-11-11 paper/manuscript.Rmd
Add Daniel's feedback to Intro

@@
 
-Pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
-In the context of animal pollination, the support to biodiversity is fundamentally achieved by virtue of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plants.
+Animal pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011].
+Alongside the direct mutualisms between plants and their pollinators, the support to biodiversity is substantially achieved as a result of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plants [HelpWithRefPlease].
 Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources [@stachowicz_mutualism_2001]. 
@@
 
-This is so because sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
+One of many possible explanations for why this is true is because sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
 As soon as there are costs plant start competing for mutualistic partners, even if this competition is not strong enough to produce a **net** negative effect in fitness.
-The possible negative effects of competition for pollinators have been long recognised [@robertson_philosophy_1895] and widely documented both experimentally [@lewis_experimental_1961] and theoretically [@levin_competition_1970].
+The possible detrimental effects of competition for pollinators have been long recognised [@robertson_philosophy_1895] and widely documented both experimentally [@lewis_experimental_1961] and theoretically [@levin_competition_1970].
 Multiple factors (like the number of shared pollinators, the plants' relative abundance, visitor fidelity, and traits) have been shown to modulate the strength of competition and in turn the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_effects_1987; @campbell_pollinator_1985].
-It is currently clear that the effects of these factors on fitness have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as driving ecological differentiation [@mitchell_new_2009; @caruso_competition_2000].
+It is currently clear that the effects of these factors on fitness have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as ecological differentiation [@mitchell_new_2009; @caruso_competition_2000].
 
@@
 With few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about competition vs.
-facilitation in pollination systems and its relationship to the quantity and quality of pollination is based mostly on two-species systems.
+facilitation in pollination systems and its relationship to the quantity and quality of pollination is based mostly on two-plant-species systems.
 However, competitive interactions between species pairs do not occur in isolation.
@@
 For instance, recent empirical evidence suggests that species with original traits generally have fewer interaction partners [@coux_linking_2016]. 
-This evidence is aligned with the intuitive rationale that a species that interacts with few species benefits strongly from each of them, whereas a species that interacts with a large number of species does so comparatively weakly.
+This evidence is aligned with the notion that a species that interacts with few species benefits strongly from each of them; in contrast, a species that interacts with a large number of species does so comparatively weakly.
 If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollination in species with original traits and an increase in species with a large number of interaction partners [@gibson_can_2012].
-Alternatively, it might also be the case that density is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
-Abundant species might experience a dilution of the available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both the pollen being transported by pollinators and animal visits compared to other species.
+Alternatively, it might also be the case that flower/pollen density is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
+Abundant plant species might experience a dilution of the available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both the pollen being transported by pollinators and animal visits compared to other species.
 In this case, a potential reduction in the quantity of pollination (the amount of conspecific pollen received) could be compensated by an increase in the quality of pollination (the amount of conspecific relative to heterospecific pollen received).

### 2018-11-11 paper/manuscript.Rmd
Insert ABC abstract

@@
 Daniel and Jason, could we discuss options here?
+
+\clearpage
+
+## Abstract
+
+In the context of animal-mediated pollination, sharing pollinators between plant species creates a balancing act between two ecological opposites: mutualism and competition. 
+Sharing pollinators can be beneficial because it allows plant species to harness positive feedback loops between populations. 
+It can also be detrimental to co-flowering plants because pollen can be lost to foreign flowers and stigma surface can be occupied by foreign pollen.
+However, these detrimental effects of sharing pollinators are poorly understood at the community level because, at this scale, many other factors play a role in shaping species interactions. 
+Specifically, here we quantify the potential negative impact that the number of interacting species can play on the pollination service while accounting for the structure of the interactions, the pollen flows that occur within it, and the traits of the species that integrate the community.
+We found that there is indeed a trade-off between the number of interacting partners and both the quantity and quality of pollination received by different flowering plants. 
+However, the trade-off's role on pollination service is relatively small when compared to other ecological factors. 
+In particular, competition for pollinators is more strongly shaped by density effects caused by the species abundance and the amount of pollen the plant produces, as well as its functional originality.
+While sharing pollinators can be detrimental for plant fitness, when scaling up to empirical communities, we show that plants can compensate for these detrimental effects using other ecological mechanisms.
+
+### Keywords
+
+X, Y, Z
 

### 2018-11-11 paper/manuscript.Rmd
Feedback from Peter to legibility

@@
 Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources [@stachowicz_mutualism_2001]. 
-Indeed, studies that are fundamental to our current knowledge of mutualism predict that an upper limit to biodiversity is achieved when the number of mutualistic partners is maximised in a community [@bastolla_architecture_2009].
-And yet, not every species of pollinator in natural communities interacts with every species of plant.
+Indeed, studies that are fundamental to our current knowledge of mutualism predict that the maximum number of coexisting species---an upper limit to biodiversity---is achieved when the number of mutualistic partners is maximised in a community [@bastolla_architecture_2009].
+And yet, not every pollinator species in natural communities interacts with every species of plant.
 
-One of many possible explanations for why this is true is because sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
-As soon as there are costs plant start competing for mutualistic partners, even if this competition is not strong enough to produce a **net** negative effect in fitness.
+One of the possible explanations is that sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
+As soon as there are costs, plants start competing for mutualistic partners, even if this competition is not strong enough to produce a **net** negative effect in fitness.
 The possible detrimental effects of competition for pollinators have been long recognised [@robertson_philosophy_1895] and widely documented both experimentally [@lewis_experimental_1961] and theoretically [@levin_competition_1970].
-Multiple factors (like the number of shared pollinators, the plants' relative abundance, visitor fidelity, and traits) have been shown to modulate the strength of competition and in turn the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_effects_1987; @campbell_pollinator_1985].
+Multiple factors (like the number of shared pollinators, the plants' relative abundance, visitor fidelity, and traits) have been shown to modulate the strength of competition and, in turn, the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_effects_1987; @campbell_pollinator_1985].
 It is currently clear that the effects of these factors on fitness have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as ecological differentiation [@mitchell_new_2009; @caruso_competition_2000].
 
-The main two mechanisms through which these ecological factors can affect plant fertilization are (*i*) by reducing the number of conspecific pollen grains on stigmas or (*ii*) by increasing the deposition of heterospecific pollen [@morales_interspecific_2008].
-For example, plants with more attractive flowers might reduce the number of visits---and hence the amount of conspecific pollen---for those less attractive [@yang_pollinator_2011]. 
-We denote this as the *quantity* of the pollination service. 
+The main two mechanisms through which these ecological factors can affect plant fertilization are: (*i*) by reducing the number of conspecific pollen grains on stigmas or (*ii*) by increasing the deposition of heterospecific pollen [@morales_interspecific_2008].
+For example, plants with more attractive flowers might reduce the number of visits---and hence the amount of conspecific pollen deposited by animals---for those less attractive [@yang_pollinator_2011].
+We denote [] this as the *quantity* of the pollination service. 
 More subtly, when plants share pollination partners, even receiving a visit might not translate into fertilization due to interspecific pollen transfer [@campbell_mechanism_1985]. 
@@
 Generally speaking, the higher the proportion of conspecific relative to heterospecific pollen the higher the *quality* of the pollination service. 
-With few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about competition vs.
-facilitation in pollination systems and its relationship to the quantity and quality of pollination is based mostly on two-plant-species systems.
+With few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the quantity and quality of pollination---and its relationship to competition vs.
+facilitation in pollination systems---is based mostly on studies of two plant species.
 However, competitive interactions between species pairs do not occur in isolation.
 
-Instead, plants often occur in communities in which multiple intertwined factors operate simultaneously and lead to emergent phenomena not observed at smaller scales. 
-For instance, recent empirical evidence suggests that species with original traits generally have fewer interaction partners [@coux_linking_2016]. 
-This evidence is aligned with the notion that a species that interacts with few species benefits strongly from each of them; in contrast, a species that interacts with a large number of species does so comparatively weakly.
+Instead, co-flowering plants often occur in communities in which multiple intertwined factors operate simultaneously and lead to emergent phenomena not observed at smaller scales. 
+For instance, recent empirical evidence suggests that plants with flowering traits that are original relative to others in the community have generally fewer interaction partners [@coux_linking_2016].
+This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them; in contrast, a species that interacts with a large number of species does so comparatively weakly.
 If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollination in species with original traits and an increase in species with a large number of interaction partners [@gibson_can_2012].
 Alternatively, it might also be the case that flower/pollen density is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
-Abundant plant species might experience a dilution of the available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both the pollen being transported by pollinators and animal visits compared to other species.
+Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both the pollen being transported by pollinators and their visits compared to other species.
 In this case, a potential reduction in the quantity of pollination (the amount of conspecific pollen received) could be compensated by an increase in the quality of pollination (the amount of conspecific relative to heterospecific pollen received).
 To complicate things more, autonomous self-pollination can also influence a plant sensitivity to competition for pollination because it can ensure reproduction even in the absence of outcross pollen [@kalisz_benefits_2003].
-As multiple, potentially correlated, factors may act simultaneously, understanding their relative importance and how plant species harness them to minimise competition for pollination within their communities requires extensive data describing both the structure of the interactions and the pollen flows that occur within it.
+Altogether, multiple, potentially correlated, factors may act simultaneously.
+Therefore, understanding the relative importance of these factors and how plant species harness them to minimise competition for pollination within their communities requires extensive data. 
+Both describing the structure of the interactions and the pollen flows that occur within it.
 
@@
 First, we ask the extent to which the outcome of animal-mediated pollination is facilitation or competition. 
-If facilitation is the primary outcome we would expect (*i*) a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than that due to self-pollination and (*ii*) an overall positive relationship between the amount of conspecific pollen deposited in stigmas and that that would be achieved [@tur_evaluating_2016].
+If facilitation is the primary outcome we would expect (*i*) a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than that due to self-pollination and (*ii*) an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the heterospecific pollen [@tur_evaluating_2016].
 Second, we investigate the relative contribution that four ecological factors, that together, describe the role of the plant species and the ecological context, have on competition for pollination. 
@@
 Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and are hence defined by the ecological context. 
-If plant species adopt comparable roles across different communities we should expect plant strategies to be more similar within species than across species in the study. 
-On the contrary, if species role is flexible, we should expect plants to be able to adopt different strategies in each community such that competition is more optimally minimised depending on the context.
+If plant species adopt comparable roles across different communities, we should expect plant strategies to be more similar within species than across species in the study. 
+On the contrary, if species role is flexible, we should expect plants to be able to adopt different strategies in each community such that competition is minimised depending on the context.
 

### 2018-11-11 paper/manuscript.Rmd
Add support for line number referencing

@@
   - \usepackage{xr}
+  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
+  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
   - \externaldocument[S-]{supp-info}

### 2018-11-11 paper/manuscript.Rmd
Add questions to coauthors for intro

@@
 
+* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops}?
+* I got feedback that "denote" in \lr{denote} might be overly formal?
+
 * __Traits__: Currently I don't mention traits in the discussion.
@@
 Animal pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011].
-Alongside the direct mutualisms between plants and their pollinators, the support to biodiversity is substantially achieved as a result of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plants [HelpWithRefPlease].
+Alongside the direct mutualisms between plants and their pollinators, \R{ref-needed-possitive-loops} the support to biodiversity is substantially achieved as a result of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plant.
 Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources [@stachowicz_mutualism_2001]. 
@@
 For example, plants with more attractive flowers might reduce the number of visits---and hence the amount of conspecific pollen deposited by animals---for those less attractive [@yang_pollinator_2011].
-We denote [] this as the *quantity* of the pollination service. 
+We denote \R{denote} this as the *quantity* of the pollination service. 
 More subtly, when plants share pollination partners, even receiving a visit might not translate into fertilization due to interspecific pollen transfer [@campbell_mechanism_1985]. 

### 2018-11-12 paper/manuscript.Rmd
Count words manuscript

@@
                       warning = FALSE)
+drake::loadd(msc_wordcount)
 ```
+
+**Manuscript length:** approx. `r format(msc_wordcount$n_words_stri, big.mark = ",")` words including abstract and awknoledgements, `r msc_wordcount$reading_time_stri` reading time.
 

### 2018-11-12 main.R

@@ -184,6 +184,7 @@ figure_plan <- drake::drake_plan(
 )
 
 reporting_plan <- drake::drake_plan(
+  msc_wordcount = wordcount.lite::text_stats(drake::file_in('paper/manuscript.Rmd')),
   render_pdf(drake::knitr_in('paper/supp-info.Rmd'), drake::file_out('paper/supp-info.pdf'), clean_md = FALSE),
   render_pdf(drake::knitr_in('paper/manuscript.Rmd'), drake::file_out('paper/manuscript.pdf'), clean_md = FALSE)
   )

### 2018-11-13 paper/manuscript.Rmd
Separate abstract

@@
 
-## Abstract
+# Abstract
 
-In the context of animal-mediated pollination, sharing pollinators between plant species creates a balancing act between two ecological opposites: mutualism and competition. 
-Sharing pollinators can be beneficial because it allows plant species to harness positive feedback loops between populations. 
-It can also be detrimental to co-flowering plants because pollen can be lost to foreign flowers and stigma surface can be occupied by foreign pollen.
-However, these detrimental effects of sharing pollinators are poorly understood at the community level because, at this scale, many other factors play a role in shaping species interactions. 
-Specifically, here we quantify the potential negative impact that the number of interacting species can play on the pollination service while accounting for the structure of the interactions, the pollen flows that occur within it, and the traits of the species that integrate the community.
-We found that there is indeed a trade-off between the number of interacting partners and both the quantity and quality of pollination received by different flowering plants. 
-However, the trade-off's role on pollination service is relatively small when compared to other ecological factors. 
-In particular, competition for pollinators is more strongly shaped by density effects caused by the species abundance and the amount of pollen the plant produces, as well as its functional originality.
-While sharing pollinators can be detrimental for plant fitness, when scaling up to empirical communities, we show that plants can compensate for these detrimental effects using other ecological mechanisms.
+`r paste(drake::readd(abstract), collapse = "")`
 
-### Keywords
-
-X, Y, Z
+**Keywords:** X, Y, Z
 

### 2018-11-13 paper/manuscript.Rmd
Separate awknoledgements

@@
 
-We thank  Cátedra de Botánica General, Facultad de Agronomía, Universidad de Buenos Aires. 
-The Agrasar and Bordeu families, and the University of Buenos Aires, for logistical support and permission to conduct this study at estancias Anquilóo, Las Chilcas and San Claudio, respectively. 
-Field work was supported by grants PICT 08–12504 and 0851. 
-EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, and a New Zealand International Doctoral Research Scholarship.
-DBS and JMT acknowledge the support of a Rutherford Discovery Fellowship. 
-DBS also awknoledges the Marsden Fund Council from New Zealand Government funding.
+`r paste(drake::readd(acknowledgements), collapse = "")`
 

### 2018-11-13 paper/manuscript.Rmd
Count also words in abstract

@@
                       warning = FALSE)
-drake::loadd(msc_wordcount)
 ```
 
-**Manuscript length:** approx. `r format(msc_wordcount$n_words_stri, big.mark = ",")` words including abstract and awknoledgements, `r msc_wordcount$reading_time_stri` reading time.
+```{r draft-details}
+drake::loadd(msc_wordcount, abs_wordcount)
+```
+
+**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters; approx.
+`r format(round(msc_wordcount$n_words_stri/10)*10-90, big.mark = ",")` words (includes draft info, excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` reading time.
+
+**Abstract length:** `r abs_wordcount$n_words_stri` words.
 

### 2018-11-13 main.R

@@ -186,6 +186,7 @@ figure_plan <- drake::drake_plan(
 reporting_plan <- drake::drake_plan(
   abstract = readLines(drake::file_in("./paper/abstract.md")),
   acknowledgements = readLines(drake::file_in("./paper/acknowledgements.md")),
+  abs_wordcount = wordcount.lite::text_stats(drake::file_in("paper/abstract.md")),
   msc_wordcount = wordcount.lite::text_stats(drake::file_in('paper/manuscript.Rmd')),
   render_pdf(drake::knitr_in('paper/supp-info.Rmd'), drake::file_out('paper/supp-info.pdf'), clean_md = FALSE),
   render_pdf(drake::knitr_in('paper/manuscript.Rmd'), drake::file_out('paper/manuscript.pdf'), clean_md = FALSE)

### 2018-11-13 paper/manuscript.Rmd
Initial methods competition vs facilitation

@@
 Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinian Pampas.
+## Competition vs. facilitation
+
+Our first objective is to identify whether, at the community level, the net outcome of animal-mediated pollination is facilitation or competition. 
+A first line of evidence can be found in the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
+This is so, because heterospecific pollen can be seen as the cost that plants must pay for receiving conspecific pollen from shared pollinators. 
+A neggative relationship (when shared pollinators increasse heterospecific pollen loads and decreasse conspecific loads) may indicate that competition for pollination is strong. 
+This negative relationship could arrise, for example, when other, more dominant species, monopolizes a limited number of pollinators [@ref], when heterospecific pollen deposited in the stigma interfers with deposition of conspecific pollen [@ref], or when conspecific pollen is lost to heterospecific stigmas [@ref].
+In contrast, a positive relationship (when sharing pollinators increasses heterospecfic pollen loads but also conspecific pollen deposition) is what should be observed if facilitation is the dominant outcome.
+For example when the abbundance of shared pollinators is positively influenced by floral resources and the positive effects ripple trough the mutualistic network [@ref].
+
+A second line of evidence could be obtained by examining the difference between the amount conspecific pollen deposited in flower stigmas *with* and *without* animal mediated pollination. 
+It has been shown that self-pollination is favorable to plant reproduction when competition for pollination is strong because it provides insurance against a poor pollination service [@ref]. 
+If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented would be higher than the amount deposited when floral visits are allowed.
+The opposite pattern, may indicate that plants benefit from animal mediated pollination, as even a small difference between outcross and self pollen may be important to plant fitness [@ref], particularly so for non-self-fertile species or those in which there is temporary separation in the maturation of the sexes (dichogamy).
+
+### Data collection
+
+In each of the studied communities, we quantified pollen deposition in a subset of plant species. 
+This subset comprised between three and nine of the most common entomophilus species that were flowering during the sampling period while ensuring that the chosen species covered a wide range on a specialization-generalization gradient.
+Briefly, in each of the selected plants, we removed all flowers except buds that were expected to go into inflorescence on the next day. 
+Approximately a quarter of these buds were bagged to prevent animal pollination. 
+Two days after inflorescence, we counted the pollen grains in the flowers' pistils, classified them between conspecific and heterospecific pollen, and calculated the number of pollen grains per stigma in each flower.
+More details about the study sites and data colletion and laboratory protocols can be found in @marrero_agricultural_2016.
+
+### Data analysis
+
+Similar to @tur_evaluating_2016, to evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution in each of our communities.
+In these models, the number conspecific pollen grains per stigma was the response variable and the number of heterospecific grains the predictor. 
+The slope and intercept of this relationship was allowed to differ between plant species, which were included as a random effect. 
+Models were fitted using the function `lmer` from the R package `lme4 1.1-19` [@ref]
+To compare the conspecific pollen deposited with and without animal mediated pollination, we performed a Mann-Withney U test of the number of conspecific pollen grains per stigma in un-bagged and bagged flowers for each of the studied species in a community.
 

### 2018-11-13 paper/manuscript.Rmd
Update draft info (questions, todo, and changes)

@@
 
-### Changes
+# Draft Info
+
+## Changes
 
 * Now using AICc instead of AIC to evaluate models (no change in results)
-* Changes to traits: (*a*) to keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances.
+* Traits: (*a*) to keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances.
 Also, now (*b*) columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits.
@@
 Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models.
-* Now I use a PCA of the explanatory variables to understand different plant strategies. 
-* Introduction has been rewritten to be more *hypothesis* oriented. The manuscript also includes references throughout.
-* Added abstract
+* Now I use a PCA of the explanatory variables to understand different plant strategies and give a deeper teratment to the facilitation/competition question.
 
-### To do
+## To do
 
-* Spell-check everything
-* Decide on a journal. The manuscript is currently written for an interdisciplinary one. 
-* Check reference list
+* Spell-check everything & check that reference list is correct.
+* Choose journal (the manuscript is written for an interdisciplinary journal).
 
-### Questions
+## Questions
 
@@
 * I got feedback that "denote" in \lr{denote} might be overly formal? 
-
-* __Traits__: Currently I don't mention traits in the discussion.
-I think the trait component is valuable and interesting but sadly at the moment, the data quality is poor.
-Only 4 traits have been compiled: growth form, longevity, flower colour, and whether the plant is native to the region.
-It won't be possible to gather all of the traits used by @coux_linking_2016 from the literature but hopefully, it is for a good proportion of them.
-Daniel and Jason, could we discuss options here?
+* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you preffer to keep data private?
 

### 2018-11-13 paper/manuscript.Rmd
Intro to methods

@@
 
-Elucidating how the mechanisms and drivers of facilitation scales to the community level and its theoretical consequences has been elusive in part because of the large amounts of data required.
-Previous studies focus on the final picture of interspecific pollen transfer that is obtained by examining the pollen deposited on flower stigmas. 
-However, as we have described, teasing apart competition for pollinators and evaluating whether there is a trade-off between the number of partners and the mutualistic benefit also requires data that describes the structure of the interactions and the pollen flows that occur within it, while accounting for the traits of the species that integrate the community.
-Here, we examine a comprehensive data set that includes information about pollen deposition, transfer, visitation, species abundance, and species traits across diverse communities in the Argentinian Pampas.
+We collected data from eleven coflowering plant communities and their pollinators distributed across three locations, each in a distinct reagion of the Argentinian Pampas. 
+These locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and a climate drier as we move inland and westward towards the Pampean Grasslands.
+Annual mean temperatures range between 14.8 and 15.8 Celsius. 
+In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where due to the lack of available sites, we were only able to sample one restored fragment.
+We visited fragments between December 2010 and February 2011.
+
 ## Competition vs. facilitation

### 2018-11-13 paper/manuscript.Rmd
Swap order hypothesis 1 in intro
It's clearer to explain order of expected things for question one in the reverse order, i.e. first conspecific/heterospecific relationship and then bagged/open difference

@@
 First, we ask the extent to which the outcome of animal-mediated pollination is facilitation or competition. 
-If facilitation is the primary outcome we would expect (*i*) a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than that due to self-pollination and (*ii*) an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the heterospecific pollen [@tur_evaluating_2016].
+If facilitation is the primary outcome we would expect (*i*) an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the heterospecific pollen [@tur_evaluating_2016] and (*ii*) a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than that due to self-pollination.
 Second, we investigate the relative contribution that four ecological factors, that together, describe the role of the plant species and the ecological context, have on competition for pollination. 

### 2018-11-14 paper/manuscript.Rmd
Improve wording data collection methods for first objective

@@
 
-In each of the studied communities, we quantified pollen deposition in a subset of plant species. 
-This subset comprised between three and nine of the most common entomophilus species that were flowering during the sampling period while ensuring that the chosen species covered a wide range on a specialization-generalization gradient.
+In each of the studied communities, we quantified pollen deposition in a subset of plant species between December 2010 and February 2011. 
+This subset comprised between three and nine common entomophilus species that were flowering during the sampling period. 
+We chosed plant species such that they cover a wide range on a specialization-generalization gradient and a wide range of abundances. 
 Briefly, in each of the selected plants, we removed all flowers except buds that were expected to go into inflorescence on the next day. 

### 2018-11-14 paper/manuscript.Rmd
Intro to second objective

@@
 
-## Data collection
+## Effect of ecological factors in the pollination service
 
-We performed sampling in three locations, each located in a distinct region of the Argentinian Pampas. 
-The sampling locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and an drier as we move inland and westward towards the Pampean Grasslands.
-Across all sites, annual mean temperatures range between 14.8 and 15.8 Celsius.
+Our second objetive is to investigate the relative contribution that different factors that describe the plants' role and its ecological context have on the pollination service. 
+Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the plants functional originality, and (*iv*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them.
+Here, we define visit efectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
+
+### Data collection
 

### 2018-11-14 paper/manuscript.Rmd
Write data collection protocols for second objective
(ecological variables)

@@
 In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where due to the lack of available sites, we were only able to sample one restored fragment.
-We visited fragments between December 2010 and February 2011.
 
@@
 
-In each location, we sampled two restored and two agricultural fragments. 
-However, due to the lack of available sites in the Flooding Pampas, it was only possible to sample one restored site.
-We visited each fragment in November 2010 and February 2011. 
+To obtain data about (*i*) the number of shared pollinators for each species we pooled data from quantitative and qualitative polination networks. 
+Qualitative networks were constructed based on two hour observations of floral visits in each fragment. 
+Quantitative networks were constructed using two 50 m randomly located transects in each transect. 
+We counted and collected all floral visitors found in a 2 m wide strip while walking at a pace of 10 m per minute [@marrero_effect_2014; @memmott_structure_1999]. 
+We visited the transects each month between November 2010 and March 2011. 
+To obtain(*ii*) plant abundance, we counted all units of floral atraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
+We also recorded (*iii*) morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region.
+In addition we used data from the abundance counts 
+Finally, to estimate the (*iv*) visit effectiveness, in addition to the visitation networks we need to construct pollen transfer networks. 
+To construct the transfer networks we examined the pollen loads present on the collected floral visitors [@marrero_exotic_2017]. 
+When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 
+When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
+More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014 and 2017).
 In each of these visits we gathered information related to abundance, plant-pollinator visitation, pollen transfer, and pollen deposition.

### 2018-11-15 paper/manuscript.Rmd
Swap order of predictors methods

@@
 Our second objetive is to investigate the relative contribution that different factors that describe the plants' role and its ecological context have on the pollination service. 
-Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the plants functional originality, and (*iv*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them.
+Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them, and (*iv*) the plants functional originality.
 Here, we define visit efectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
@@
 
-To obtain data about (*i*) the number of shared pollinators for each species we pooled data from quantitative and qualitative polination networks. 
+To obtain the number of shared pollinators for each species (*i*), we collected data to construct qualitative and quantitative polination networks. 
 Qualitative networks were constructed based on two hour observations of floral visits in each fragment. 
@@
 We visited the transects each month between November 2010 and March 2011. 
-To obtain(*ii*) plant abundance, we counted all units of floral atraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
-We also recorded (*iii*) morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region.
-In addition we used data from the abundance counts 
-Finally, to estimate the (*iv*) visit effectiveness, in addition to the visitation networks we need to construct pollen transfer networks. 
+To obtain plant abundance (*ii*), we counted all units of floral atraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
+To estimate visit effectiveness (*iii*), in addition to the visitation networks we need to construct pollen transfer networks. 
 To construct the transfer networks we examined the pollen loads present on the collected floral visitors [@marrero_exotic_2017]. 
@@
 When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
+Finally, We also recorded morphological traits (*iv*) that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region.
+Finally, 
 More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014 and 2017).
-In each of these visits we gathered information related to abundance, plant-pollinator visitation, pollen transfer, and pollen deposition.
 

### 2018-11-17 paper/manuscript.Rmd
Data analysis methods for second objective

@@
 
-Abundance was estimated using two 50 m randomly located transects in each fragment.
-In a first sampling we counted all units of floral attraction that were found in a 2 m wide strip.
-In a second sampling we counted and collected all floral visitors while walking at a pace of 10 m per minute [@marrero_effect_2014; @memmott_structure_1999].
-We constructed quantitative visitation networks using information about the floral visitors collected during abundance transects [@marrero_effect_2014]. 
-In addition, we also constructed qualitative visitation networks during independent two hour observations of floral visits across each fragment.
-We estimated pollen transfer by examining the pollen loads present on the collected floral visitors [@marrero_exotic_2017]. 
-Where the pollen count on an individual was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 
-When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
-If more than 10 pollen grains from a plant species were identified, we assumed that pollination service between the plant and the pollinator existed. 
-Finally, we analysed pollen deposition in a subset of the plant community [@marrero_agricultural_2016]. 
-This subset comprised between three and nine of the most common entomophilus species that were flowering during the sampling period while ensuring that the chosen species covered a wide range on a specialization-generalization gradient.
-In the selected plants we removed all flowers except buds that were expected to go into inflorescence on the next day. 
-A quarter of these buds were bagged to prevent animal pollination. 
-Two days after inflorescence, we analysed the pollen grains in the flowers' pistils and classified them between conspecific and heterospecific pollen.
+### Data analysis
 
-More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014, 2016, and 2017).
+We investigate the impact of the ecological factors on the pollination services usingf two metrics: the quantity and the quality of pollination. 
+Generally speaking, here we define the quatity of pollinaton as the amount of conspecific pollen and the quality of pollination as the amount of conspecific pollen *relative* to heterospecific pollen.
+To construct these metrics we use two sets of linear mixed models (LMM) in which the response variables are the number of conspecifc and heterospecific pollen grains deposited per stigma in flowers open to animal mediated pollination.
+In general, using LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) offered better results than a GLMM with poisson (or quasipoisson) error structure.
+Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].
+
+Because the amount of deposited pollen can vary widely across species, and potentially also across communities, we evaluated two possible structures for the random effects: one that includes a random intercept for plant species, and one that also includes a random intercept for community.
+We selected the best random structure by comparing the median Akaike Information Criterion for small samples (AICc).
+
+As predictors in the models we included the four ecological variables described above. 
+We calculated the number of shared pollinators for each plant species (*i*) by pooling data from the qualitative and quantitative pollination networks. 
+This variable is strongly correlated to the number of animal species a plant interacts with (the species degree). 
+To calculate the plants relative abbundance in their community (*ii*), we simply aggregated floral counts for each species. 
+We then calculated the mean visit effectiveness (*iii*); as explained before, we define thevisit effectiveness of pollinator species *i* for plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
+Because both the number of interacting species (and therefore the number of shared pollinators), floral abundance, visitation, and pollen production roughly to followed a power-law distribution, we log-transformed these three predictors before including them in the model.
+
+Finally, functional originality (*iv*) is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016].
+As phenology has been shown to be a key mechanisms of niche differentiation among plants, we also included the plant abundance in each of the survey months (November to March) as an additional trait in our analysis.
+This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits. 
+However, because floral counts across months are not independent, we asigned them a weight of 1/5 such that phenology has an equal weight as other traits. 
+All traits were scaled prior to calculating the centroid of the functional space and the species-specific functional coordinates were calculated using the R package `FD 1.0-12` [@laliberte_distance-based_2010; @laliberte_fd_2014].
+To facilitate comparison across variables, we rescaled all predictors to have a zero mean and unitary variance.
+
+To estimate the coefficients and to perform model selection and the associated uncertainity, we used a combination of multi-model inference and bootstrap resampling with one hundred replicates. 
+First, we preformed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc within boostrap resamples.
+As we wanted model coefficients from more likely candidante models to carry more weight in our results, we sampled the coefficients for our variables proportional to the likelyhood of its candidate model.
+We "shrinked" the estimates coefficient of potentially unimportant variables by setting its estimate to 0 when the variable was not included in the model. 
+Finally, we used these distributions of the model coefficients to estimate their impact on the quantity and quality of pollination. 
+For the quantity of pollination, we simply calculated the mean value of a sample of the conspecific pollen loads. 
+For the quality of pollination, we calculated the mean difference between a sample of the distribution of the effects of conspecific pollen and a sample of those of heterospecific pollen gain.
+Again, here we used bootstrap resampling to estimate the uncertainity arround these means.
+
+## Plant strategies
 

### 2018-11-17 paper/manuscript.Rmd
Methods for third objective

@@
 
-## Data analysis
+Or last objective is to tease appart the strategies that plants might use to reduce competition and, importantly, how the community context influences these strategies. 
+If community context plays a relatively small role, we should expect plants to adopt similar strategies across different communities. 
+Alternatively, if community plays a large role, we should be able to observe differences in the strategy a plant species across communities. 
+We first use a principal component analysis (PCA) of the four ecological variables. 
+We define the species strategy in a community as its coordinates in PCA space. 
+For each species that was present in two or more communities, we then calculate (*i*) the median distance between the strategies that the species uses different communities, and (*ii*) the area of the convex hull defined by these points in the first two principal components.
+We then compare these two metrics to those obtained with 99 Monte Carlo randomisations of plant strategies that replace the focal plant strategy by one of another species in its community.
 

### 2018-11-17 paper/manuscript.Rmd
Tidy up methods

@@
 
-We explore the quantity of pollination service by examining two metrics. 
-First, we use the absolute amount of conspecific pollen (pollen counts per stigma) found on flowers open to animal pollination. 
-Second, we use the relative amount of conspecific pollen—the difference between the absolute amount and the that from flowers that were bagged. 
-We use both metrics simultaneously because, in the one hand, the relative amount acknowledges that autogamus self-pollination can occur and hence might be a better indication of the pollen that has been actually deposited by mutualistic partners.
-On the other, self-pollination is an adaptive trait [@kalisz_benefits_2003] and some plants are not self-fertile, even if their pollen gets deposited on the stigma. 
-<!-- Nevertheless, this difference still provides valuable indication of what the animal contribution to reproductive output.  -->
-Both metrics complement each other and provide a complete picture of the quantitative aspect of pollination service. 
-Similarly, to explore the quality of pollination we examine the relationship that exists between both the absolute and relative amount of conspecific pollen and heterospecific pollen. 
-We use the relative amount of heterospecific pollen for our calculations. 
-However, because the amount of heterospecific pollen in bagged flowers was negligible, results are almost identical if we use the absolute amounts.
-
-To study the amounts of deposited pollen, which are needed to construct our metrics of pollination quantity and quality, we use three sets of linear fixed models [using the R package `nlme 3.1-131`, @pinheiro_nlme_2018]—two for conspecific pollen (absolute and relative) and one for heterospecific pollen.
-This modelling approach allowed us to simultaneously explore whether there is a relationship between the benefit of animal pollination and several ecological variables that can affect the mutualistic trade-off.
-In addition, to estimate and incorporate the uncertainty associated to our results we used a combination of multi-model inference and bootstrap resampling.
-
-Each model set was based on the same one hundred bootstrap resamples of the deposition data. 
-We used bootstrap resampling because, as open and bagged flowers were not paired, this allowed us to directly model the *gain* in pollen density rather than density itself. 
-In each data replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
-We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)), this generally offered better results that a generalised linear model with poisson (or quasiposson) error structure.
-Finally, for the models of the relative amounts of pollen we calculated the difference between the pollen density among treatments.
-
-As predictors in all model sets, we included species degree, the plant relative abundance, the plant species' share on the pollen pool, and the species' functional originality. 
-Species degree was calculated from combining the quantitative and qualitative visitation networks and corresponds to the number of animal species that were observed to visit the plant species in the community where it was sampled.
-The plant's relative abundance we simply aggregated the flower counts for each plant species in the community.
-As with the deposition data, we found that log-transforming the abundance counts drastically improved normality (Figure \@ref(S-fig:fig-abundance-log-transformed-or-not)). 
-The species' share of the pollen pool was calculated as the proportion of pollen of that species in the pollen counts being carried by pollinators from the community.
-
-Functional originality is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016-1].
-Specifically, we recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region or not.
-As phenology has been shown to be a key mechanisms of niche differentiation among plants, we also included the plant abundance in each of the survey months (November to March) as an additional trait in our analysis.
-This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits. 
-All traits were scaled to have a mean of zero and a standard deviation of one prior to calculating the centroid of the functional space. 
-The species-specific functional coordinates were calculated using the R package `FD 1.0-12` [@laliberte_distance-based_2010; @laliberte_fd_2014]. 
-To facilitate comparison across model estimates, we scaled all independent variables to have a mean of zero and a standard deviation of one.
-
-In all three sets of models we first evaluated a set of candidate random effects which included random intercepts for plant species as well as random slopes for the relationship between degree and pollen gain.
-In addition we also tested for random intercepts that assumed that the plant species grouping was hierarchically nested in either their community, the land use, and the locality. 
-We selected the best random structure by comparing the median Akaike Information Criterion (AIC) of evaluated models. 
-After determining the best random structure, we then focused on the model's fixed structure composed by our explanatory variables. 
-We used multi-model inference to calculate the relative importance of each variable and its mean effect on pollen density.
-First we fitted all possible combinations of explanatory variables to the same bootstrap resamples used previously. 
-This yielded one hundred models for each "candidate formula"---a particular combination of explanatory variables. 
-We then determined the likelihood of each candidate formula and its relative weight by calculating the median $\Delta$AIC of the one hundred models that constitute it. 
-As AIC is only useful to compare models with the same response variable, the $\Delta$AIC of each candidate formula was calculated independently for each bootstrap resample.
-Calculating the median value of each candidate formula allowed us to estimate the relative importance of the explanatory variables  using the standard methods of adding the median weight of the candidate models that included the variable.
-
-To calculate the effect that each variable had on the gain of conspecific and heterospecific pollen we sampled from the estimated coefficients in each candidate model proportional to the median likelihood of each set.
-In other words, the estimated coefficients from more likely candidate constitute a larger share of the distribution of coefficients. 
-When a variable was not included in a model set we setted the estimate of its coefficient in the model to zero. 
-We expect some of our predictors to be correlated to each other.
-Estimating the models using multiple combinations of explanatory variables also allowed us to evaluate the potential collinearity between them.
-To do so we inspect how the effect of the explanatory variables changed across candidate formulae, when one or more of them were removed in turns.
-
-After calculating the effects of the ecological variables in heterospecific and conspecific pollen densities, we can now evaluate their effect in the quality and quantity of pollination. 
-For the quantity of pollination, we simply calculated the mean value of the distribution of the effect for both the absolute and relative conspecific pollen densities. 
-Again, we used bootstrap resampling from the coefficient distributions to calculate the confidence intervals of the mean. 
-For the quality of pollination, we calculated the mean difference between a sample of the distribution of the effects of conspecific pollen and a sample of those of heterospecific pollen gain.
-Similar to the mean effects on the quantity of pollination, we used bootstrap resampling to calculate confidence intervals of the means.estimated by the relationship that exists between the gain in conspecific and heterospecific pollen.
-
 # Results

### 2018-11-17 paper/manuscript.Rmd
Community influence is the focus of third objective
Small change of wording in the introduction re. the third objective. The focus is on evidencing the role of the community

@@
 However, other factors like the plant's functional originality, its relative abundance, and the visit effectiveness, should have the potential to compensate this increase in competition by improving either the quality or the quality of pollination.
-Third, and finally, we explore how plants differ in how they use these factors to minimise competition. 
-Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and are hence defined by the ecological context. 
+Third, and finally, we explore how community influences the way plants use these factors to minimise competition. 
+Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and are hence is likely to be defined by the ecological context. 
 If plant species adopt comparable roles across different communities, we should expect plant strategies to be more similar within species than across species in the study. 

### 2018-11-17 paper/manuscript.Rmd
Spellcheck methods

@@
 
-We collected data from eleven coflowering plant communities and their pollinators distributed across three locations, each in a distinct reagion of the Argentinian Pampas. 
-These locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and a climate drier as we move inland and westward towards the Pampean Grasslands.
+We collected data from eleven co-flowering plant communities and their pollinators distributed across three locations, each in a distinct region of the Argentinian Pampas. 
+These locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and drier as we move inland and westward towards the Pampean Grasslands.
 Annual mean temperatures range between 14.8 and 15.8 Celsius. 
@@
 Our first objective is to identify whether, at the community level, the net outcome of animal-mediated pollination is facilitation or competition. 
-A first line of evidence can be found in the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
-This is so, because heterospecific pollen can be seen as the cost that plants must pay for receiving conspecific pollen from shared pollinators. 
-A neggative relationship (when shared pollinators increasse heterospecific pollen loads and decreasse conspecific loads) may indicate that competition for pollination is strong. 
-This negative relationship could arrise, for example, when other, more dominant species, monopolizes a limited number of pollinators [@ref], when heterospecific pollen deposited in the stigma interfers with deposition of conspecific pollen [@ref], or when conspecific pollen is lost to heterospecific stigmas [@ref].
-In contrast, a positive relationship (when sharing pollinators increasses heterospecfic pollen loads but also conspecific pollen deposition) is what should be observed if facilitation is the dominant outcome.
-For example when the abbundance of shared pollinators is positively influenced by floral resources and the positive effects ripple trough the mutualistic network [@ref].
+The first line of evidence can be found in the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
+This is so because heterospecific pollen can be seen as the cost that plants must pay for receiving conspecific pollen from shared pollinators. 
+A negative relationship (when shared pollinators increase heterospecific pollen loads and decrease conspecific loads) may indicate that competition for pollination is strong. 
+This negative relationship could arise, for example, when other, more dominant species, monopolizes a limited number of pollinators [@ref], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@ref], or when conspecific pollen is lost to heterospecific stigmas [@ref].
+In contrast, a positive relationship (when sharing pollinators increases heterospecific pollen loads but also conspecific pollen deposition) is what should be observed if facilitation is the dominant outcome.
+For example, when the abundance of shared pollinators is positively influenced by floral resources and these positive effects ripple through the mutualistic network [@ref].
 
-A second line of evidence could be obtained by examining the difference between the amount conspecific pollen deposited in flower stigmas *with* and *without* animal mediated pollination. 
-It has been shown that self-pollination is favorable to plant reproduction when competition for pollination is strong because it provides insurance against a poor pollination service [@ref]. 
-If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented would be higher than the amount deposited when floral visits are allowed.
-The opposite pattern, may indicate that plants benefit from animal mediated pollination, as even a small difference between outcross and self pollen may be important to plant fitness [@ref], particularly so for non-self-fertile species or those in which there is temporary separation in the maturation of the sexes (dichogamy).
+The second line of evidence could be obtained by examining the difference between the amount conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination. 
+It has been shown that self-pollination is favourable to plant reproduction when competition for pollination is strong because it provides insurance against a poor pollination service [@ref]. 
+If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented could be higher than the amount deposited when floral visits are allowed.
+In contrast, the opposite pattern may indicate that plants benefit from animal-mediated pollination---even a small difference between outcross and self-pollen may be important to plant fitness [@ref].
+This is particularly so for non-self-fertile species or those in which there is a temporary separation in the maturation of the sexes (dichogamy).
 
@@
 In each of the studied communities, we quantified pollen deposition in a subset of plant species between December 2010 and February 2011. 
-This subset comprised between three and nine common entomophilus species that were flowering during the sampling period. 
-We chosed plant species such that they cover a wide range on a specialization-generalization gradient and a wide range of abundances. 
+This subset comprised of between three and nine common insect-pollinated (entomophilous) species that were flowering during the sampling period. 
+We choose plant species so that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
 Briefly, in each of the selected plants, we removed all flowers except buds that were expected to go into inflorescence on the next day. 
@@
 Two days after inflorescence, we counted the pollen grains in the flowers' pistils, classified them between conspecific and heterospecific pollen, and calculated the number of pollen grains per stigma in each flower.
-More details about the study sites and data colletion and laboratory protocols can be found in @marrero_agricultural_2016.
+More details about the study sites and data collection and laboratory protocols can be found in @marrero_agricultural_2016.
 
@@
 In these models, the number conspecific pollen grains per stigma was the response variable and the number of heterospecific grains the predictor. 
-The slope and intercept of this relationship was allowed to differ between plant species, which were included as a random effect. 
+The slope and intercept of this relationship were allowed to differ between plant species, which were modelled as a random effect. 
 Models were fitted using the function `lmer` from the R package `lme4 1.1-19` [@ref]
-To compare the conspecific pollen deposited with and without animal mediated pollination, we performed a Mann-Withney U test of the number of conspecific pollen grains per stigma in un-bagged and bagged flowers for each of the studied species in a community.
+To compare the conspecific pollen deposited with and without animal-mediated pollination, we performed a Mann-Withney U test of the number of conspecific pollen grains per stigma between un-bagged and bagged flowers for each of the studied species in a community.
 
@@
 
-Our second objetive is to investigate the relative contribution that different factors that describe the plants' role and its ecological context have on the pollination service. 
+Our second objective is to investigate the relative contribution that different factors that describe the plants' role and its ecological context have on the pollination service. 
 Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them, and (*iv*) the plants functional originality.
-Here, we define visit efectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
+Here, we define visit effectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
 
@@
 
-To obtain the number of shared pollinators for each species (*i*), we collected data to construct qualitative and quantitative polination networks. 
-Qualitative networks were constructed based on two hour observations of floral visits in each fragment. 
+To obtain the number of shared pollinators for each species (*i*), we collected data to construct qualitative and quantitative pollination networks. 
+Qualitative networks were constructed based on two-hour observations of floral visits in each fragment. 
 Quantitative networks were constructed using two 50 m randomly located transects in each transect. 
@@
 We visited the transects each month between November 2010 and March 2011. 
-To obtain plant abundance (*ii*), we counted all units of floral atraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
+To obtain plant abundance (*ii*), we counted all units of floral attraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
 To estimate visit effectiveness (*iii*), in addition to the visitation networks we need to construct pollen transfer networks. 
@@
 Finally, We also recorded morphological traits (*iv*) that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region.
-Finally, 
 More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014 and 2017).
@@
 
-We investigate the impact of the ecological factors on the pollination services usingf two metrics: the quantity and the quality of pollination. 
-Generally speaking, here we define the quatity of pollinaton as the amount of conspecific pollen and the quality of pollination as the amount of conspecific pollen *relative* to heterospecific pollen.
-To construct these metrics we use two sets of linear mixed models (LMM) in which the response variables are the number of conspecifc and heterospecific pollen grains deposited per stigma in flowers open to animal mediated pollination.
-In general, using LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) offered better results than a GLMM with poisson (or quasipoisson) error structure.
+We investigate the impact of the ecological factors on the pollination services using two metrics: the quantity and the quality of pollination. 
+Here we define the quality of pollination as the amount of conspecific pollen and the quality of pollination as the amount of conspecific pollen *relative* to heterospecific pollen. 
+To construct these metrics we use two sets of linear mixed models (LMM) in which the response variables are the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination.
+In general, using LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) offered better results than a GLMM with Poisson (or quasipoisson) error structure.
 Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].
 
-Because the amount of deposited pollen can vary widely across species, and potentially also across communities, we evaluated two possible structures for the random effects: one that includes a random intercept for plant species, and one that also includes a random intercept for community.
+Because the amount of deposited pollen can vary widely across species, and potentially also across communities, we evaluated two possible structures for the random effects: one that includes a random intercept for plant species, and one that treats species across different communities independently.
 We selected the best random structure by comparing the median Akaike Information Criterion for small samples (AICc).
 
-As predictors in the models we included the four ecological variables described above. 
-We calculated the number of shared pollinators for each plant species (*i*) by pooling data from the qualitative and quantitative pollination networks. 
+As predictors in the models, we included the four ecological variables described above. 
+Specifically, we calculated the number of shared pollinators for each plant species (*i*) by pooling data from the qualitative and quantitative pollination networks. 
 This variable is strongly correlated to the number of animal species a plant interacts with (the species degree). 
-To calculate the plants relative abbundance in their community (*ii*), we simply aggregated floral counts for each species. 
-We then calculated the mean visit effectiveness (*iii*); as explained before, we define thevisit effectiveness of pollinator species *i* for plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
+To calculate the plants' relative abundance in their community (*ii*), we simply aggregated floral counts for each species. 
+We then calculated the mean visit effectiveness (*iii*). 
+As explained before, we define the effectiveness of a visit of pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
 Because both the number of interacting species (and therefore the number of shared pollinators), floral abundance, visitation, and pollen production roughly to followed a power-law distribution, we log-transformed these three predictors before including them in the model.
@@
 Finally, functional originality (*iv*) is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016].
-As phenology has been shown to be a key mechanisms of niche differentiation among plants, we also included the plant abundance in each of the survey months (November to March) as an additional trait in our analysis.
+As phenology has been shown to be a key mechanism of niche differentiation among plants, we also included the plant abundance in each of the survey months (November to March) as an additional trait in our analysis.
 This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits. 
-However, because floral counts across months are not independent, we asigned them a weight of 1/5 such that phenology has an equal weight as other traits. 
-All traits were scaled prior to calculating the centroid of the functional space and the species-specific functional coordinates were calculated using the R package `FD 1.0-12` [@laliberte_distance-based_2010; @laliberte_fd_2014].
-To facilitate comparison across variables, we rescaled all predictors to have a zero mean and unitary variance.
+However, because floral counts across months are not independent, we assigned them a weight of 1/5 such that phenology has an equal weight as other traits. 
+We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_distance-based_2010; @laliberte_fd_2014].
+To facilitate comparison across the four explanatory variables in our models, we rescaled them all to have a zero mean and unitary variance.
 
-To estimate the coefficients and to perform model selection and the associated uncertainity, we used a combination of multi-model inference and bootstrap resampling with one hundred replicates. 
-First, we preformed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc within boostrap resamples.
-As we wanted model coefficients from more likely candidante models to carry more weight in our results, we sampled the coefficients for our variables proportional to the likelyhood of its candidate model.
-We "shrinked" the estimates coefficient of potentially unimportant variables by setting its estimate to 0 when the variable was not included in the model. 
+To estimate the coefficients and to perform model selection and the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with one hundred replicates. 
+First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc for each bootstrap sample.
+As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our variables proportional to the likelihood of its candidate model.
+We "shrank" the estimates coefficient of potentially unimportant variables by setting its estimate to 0 when the variable was not included in the model. 
 Finally, we used these distributions of the model coefficients to estimate their impact on the quantity and quality of pollination. 
@@
 For the quality of pollination, we calculated the mean difference between a sample of the distribution of the effects of conspecific pollen and a sample of those of heterospecific pollen gain.
-Again, here we used bootstrap resampling to estimate the uncertainity arround these means.
+Again, here we used bootstrap resampling to estimate the uncertainty around these means.
 
@@
 
-Or last objective is to tease appart the strategies that plants might use to reduce competition and, importantly, how the community context influences these strategies. 
+Our last objective is to tease apart the strategies that plants might use to reduce competition and, importantly, how the community context influences these strategies. 
 If community context plays a relatively small role, we should expect plants to adopt similar strategies across different communities. 
-Alternatively, if community plays a large role, we should be able to observe differences in the strategy a plant species across communities. 
+Alternatively, if the community plays a large role, we should be able to observe differences in the strategy a plant species across communities. 
 We first use a principal component analysis (PCA) of the four ecological variables. 
@@
 For each species that was present in two or more communities, we then calculate (*i*) the median distance between the strategies that the species uses different communities, and (*ii*) the area of the convex hull defined by these points in the first two principal components.
-We then compare these two metrics to those obtained with 99 Monte Carlo randomisations of plant strategies that replace the focal plant strategy by one of another species in its community.
+We then compare these two metrics to those obtained with 99 Monte Carlo randomizations of plant strategies that replace the focal plant strategy by one of another species in its community.
 

### 2018-11-17 paper/manuscript.Rmd
Refs to methods

@@
 
-* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops}?
+* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}?
 * I got feedback that "denote" in \lr{denote} might be overly formal? 
@@
 A negative relationship (when shared pollinators increase heterospecific pollen loads and decrease conspecific loads) may indicate that competition for pollination is strong. 
-This negative relationship could arise, for example, when other, more dominant species, monopolizes a limited number of pollinators [@ref], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@ref], or when conspecific pollen is lost to heterospecific stigmas [@ref].
+This negative relationship could arise, for example, when other, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
 In contrast, a positive relationship (when sharing pollinators increases heterospecific pollen loads but also conspecific pollen deposition) is what should be observed if facilitation is the dominant outcome.
-For example, when the abundance of shared pollinators is positively influenced by floral resources and these positive effects ripple through the mutualistic network [@ref].
+For example, when the abundance of shared pollinators is positively influenced by floral resources and these positive effects ripple through the mutualistic network [@liao_presence_2011].
 
 The second line of evidence could be obtained by examining the difference between the amount conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination. 
-It has been shown that self-pollination is favourable to plant reproduction when competition for pollination is strong because it provides insurance against a poor pollination service [@ref]. 
+It has been shown that self-pollination is favourable to plant reproduction when competition for pollination is strong because it provides insurance against a poor pollination service [@kalisz_benefits_2003].
 If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented could be higher than the amount deposited when floral visits are allowed.
-In contrast, the opposite pattern may indicate that plants benefit from animal-mediated pollination---even a small difference between outcross and self-pollen may be important to plant fitness [@ref].
+In contrast, the opposite pattern may indicate that plants benefit from animal-mediated pollination---even a small difference between outcross and self-pollen may be important to plant fitness \R{ref2}[@ref].
 This is particularly so for non-self-fertile species or those in which there is a temporary separation in the maturation of the sexes (dichogamy).
@@
 The slope and intercept of this relationship were allowed to differ between plant species, which were modelled as a random effect. 
-Models were fitted using the function `lmer` from the R package `lme4 1.1-19` [@ref]
+Models were fitted using the function `lmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]
 To compare the conspecific pollen deposited with and without animal-mediated pollination, we performed a Mann-Withney U test of the number of conspecific pollen grains per stigma between un-bagged and bagged flowers for each of the studied species in a community.

### 2018-11-18 paper/manuscript.Rmd
Extra refs to intro

@@
 Animal pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011].
-Alongside the direct mutualisms between plants and their pollinators, \R{ref-needed-possitive-loops} the support to biodiversity is substantially achieved as a result of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plant.
+Alongside the direct mutualisms between plants and their pollinators, \R{ref-needed-possitive-loops} the support to biodiversity can be achieved as a result of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plant [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008].
 Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources [@stachowicz_mutualism_2001]. 
@@
 
-Instead, co-flowering plants often occur in communities in which multiple intertwined factors operate simultaneously and lead to emergent phenomena not observed at smaller scales. 
+Instead, co-flowering plants often occur in communities in which multiple intertwined factors operate simultaneously and lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
 For instance, recent empirical evidence suggests that plants with flowering traits that are original relative to others in the community have generally fewer interaction partners [@coux_linking_2016].

### 2018-11-18 paper/manuscript.Rmd
Add some bibliography that might be useful for the discussion

@@
 
+Interspecific pollen transfer is the most important factor underpining competition for pollinators [@campbell_mechanism_1985]
+
+Traits are determined by competition for pollination -- Caruso 2000
+
+, all while accounting for the traits of the species that integrate the community.  extent to which plants employ  relative contribution and the interplay of each factor requires
+First, that plants might use different strategies to reduce competition for pollination. 
+Second that the effect of coorelated factors in the quality and quantity of pollination [like generalism, its relative abundance, and visitation frequency; @sargent_role_2006] might balance each other.
+
+Interspecific pollen transfer was responsible for reduction in set set for one species but loss of conspecific pollen was responsible for another -- Campbell and Motten 1985
+
+Plant species vary greatly on the extent to which each of these two mechanisms can affect fertilisation [@campbell_mechanism_1985], a large plant
+
+Competition can also be mediated by pollinator density, not just plant density [@ye_competition_2014]
+
+Check @flanagan_effects_2011 for discussion on the effects when one thinks about communities.
+
+Traits can have a role only with High abundances, where being dominant can be bad for other plants in communities. Abbundance is important in small species number systems [@munoz_presence_2008]
+
+Plants have mechanishms that prevent heterospecific pollen deposition.
+@bartomeus_high_2008 show that even when a plant dominates the pollen transfer network opther species might not receive lots of heterospecific pollen [@bartomeus_high_2008; @flanagan_increased_2010]
+
+Pollen limitation is inversely related to abundance, but high abundance is also related to mate limitation [@moeller_facilitative_2004]
+
+Competition also depends on the spatial extent [@cariveau_spatially_2009]
+
+Facilitation is still controversial? [@feldman_when_2004]
+
 # Acknowledgements

### 2018-11-18 paper/manuscript.Rmd
Jason's comments to methods

@@
 However, because floral counts across months are not independent, we assigned them a weight of 1/5 such that phenology has an equal weight as other traits. 
-We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_distance-based_2010; @laliberte_fd_2014].
+We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
 To facilitate comparison across the four explanatory variables in our models, we rescaled them all to have a zero mean and unitary variance.
@@
 To estimate the coefficients and to perform model selection and the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with one hundred replicates. 
-First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc for each bootstrap sample.
+First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc (relative to the most likely model) for each bootstrap sample.
 As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our variables proportional to the likelihood of its candidate model.

### 2018-11-18 paper/manuscript.Rmd
Daniel's feedback to methods

@@
 We collected data from eleven co-flowering plant communities and their pollinators distributed across three locations, each in a distinct region of the Argentinian Pampas. 
-These locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and drier as we move inland and westward towards the Pampean Grasslands.
+These locations are distributed across a precipitation gradient with a humid temperate climate in the eastward Flooding Pampas and becoming drier as one moves inland and westward towards the Pampean Grasslands.
 Annual mean temperatures range between 14.8 and 15.8 Celsius. 
@@
 This subset comprised of between three and nine common insect-pollinated (entomophilous) species that were flowering during the sampling period. 
-We choose plant species so that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
-Briefly, in each of the selected plants, we removed all flowers except buds that were expected to go into inflorescence on the next day. 
+We choose plant species such that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
+Briefly, in each of the selected plants, we removed all flowers leaving only buds that were expected to go into inflorescence on the next day. 
 Approximately a quarter of these buds were bagged to prevent animal pollination. 
-Two days after inflorescence, we counted the pollen grains in the flowers' pistils, classified them between conspecific and heterospecific pollen, and calculated the number of pollen grains per stigma in each flower.
+Two days after inflorescence, we counted the pollen grains in the remaining flowers' pistils, classified them between conspecific and heterospecific pollen, and calculated the number of pollen grains per stigma in each flower.
 More details about the study sites and data collection and laboratory protocols can be found in @marrero_agricultural_2016.
@@
 To construct the transfer networks we examined the pollen loads present on the collected floral visitors [@marrero_exotic_2017]. 
-When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 
+When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible, and to pollen complexes when it was not. 
 When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
@@
 We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
-To facilitate comparison across the four explanatory variables in our models, we rescaled them all to have a zero mean and unitary variance.
+Finally, to facilitate comparison across the four continuous explanatory variables in our models, we rescaled them all to have a zero mean and unitary variance.
 

### 2018-11-21 paper/manuscript.Rmd
Insert figure question 2 in paper

@@
 
-```{r fig-average-qual-quant, fig.height=2, fig.width=3.25, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
+```{r fig-average-qual-quant, fig.height=1.5, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
 Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.).
@@
 "}
-drake::readd(fig_average_qual_quant)
+# height1 <- 1.25
+# height2 <- 1.65
+# pdf(width = 3.25 * 2, height = 1.5)
+# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
+width_imp <- 1
+mult <- 1.5
+# fig_var_importance <- plot_variable_importance(variable_importance)
+drake::loadd(fig_var_importance)
+drake::loadd(fig_coef_avg)
+cowplot::plot_grid(
+  fig_var_importance[[1]],
+  fig_var_importance[[2]],
+  fig_coef_avg[[1]],
+  fig_coef_avg[[2]],
+  ncol = 4, 
+  rel_widths = c(width_imp,width_imp, width_imp*mult, width_imp * mult * 1.45), 
+  align = "h"
+  )
+# dev.off()
 ```
@@
 * We found that animal pollination only brings a small amount of extra conspecific pollen (compared selfing) if any.
-This relatively small difference is probably very important because, first, some plants simply aren't self-fertile, even if their pollen gets deposited on the stigma.
+This relatively small difference is probably very important because, first, some plants simply aren't self-fertile, even if their own pollen gets deposited on the stigma.
 Second, in some flowers there is temporary separation in the maturation of the sexes (dichogamy) that favours cross-pollination as, evolutionary, it has been shown to be a better strategy than cloning.

### 2018-11-21 main.R

@@ -193,6 +193,7 @@ figure_plan <- drake::drake_plan(
   fig_coefficient_averages = make_fig_coefficient_avarages(coefficient_averages, variable_importance), 
   fig_average_qual_quant = make_fig_average_quant_qual(coefficient_averages), 
   fig_correlation = make_fig_correlation(rep_1), 
+  fig_var_importance = plot_variable_importance(variable_importance), 
   fig_coef_avg = plot_coefficient_averages(coefficient_averages, variable_importance)
 )
 

### 2018-11-21 paper/manuscript.Rmd
Insert figure question 1 in paper

@@
 
-```{r fig-trade-off-predictions, fig.height= 3, fig.width = 6.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
+```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
 Each dot indicates the predicted median gains for a species in its community (which correspons to the selected random effects in all of our models).
@@
 The dashed line indicates the isoline at which heterospecific pollen is gained at the same rate than conspecific pollen."}
-# pdf(width = 6.5, height = 3.25)
-  cowplot::plot_grid(
-    drake::readd(fig_con_con),
-    drake::readd(fig_con_hetero_gain))
+
+# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
+# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
+# pdf(width = 6.5, height = 4)
+drake::loadd(fig_random_slopes)
+drake::loadd(fig_con_con)
+drake::loadd(fig_hetero_con)
+# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
+rw <- c(9,1.2, 6.5,1.2)
+
+left <- cowplot::plot_grid(
+  fig_con_con[[1]],
+  fig_con_con[[2]],
+  fig_hetero_con, 
+  ncol = 2, 
+  rel_widths = rw[c(3,4)], 
+  align = "h"
+)
+
+right <- cowplot::plot_grid(
+  fig_random_slopes[[1]],
+  fig_random_slopes[[2]], 
+  ncol = 2, 
+  align = "h", 
+  rel_widths = rw[1:2]
+)
+
+slopes_plot <- cowplot::plot_grid(
+  right,
+  left,
+  ncol = 2,
+  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
+)
+slopes_plot
 # dev.off()
+
+# pdf(width = 3.25, height = 3)
+# plot_bagged_vs_open_conspecific(dep_frame)
+# dev.off()
+
+  # cowplot::plot_grid(
+  #   slopes_plot, 
+  #   drake::readd(fig_con_con),
+  #   drake::readd(fig_con_hetero_gain), 
+  #   ncol = 1, 
+  #   rel_heights = c(1/2, 1/2, 1/4))
+
 ```
@@
 
-```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates of models of conspecific (absolute and relative to the potential selfing) and heterospecific pollen density gain.
+```{r fig-model-results-global, eval = F, fig.height = 2, fig.cap = "Distribution of effect estimates of models of conspecific (absolute and relative to the potential selfing) and heterospecific pollen density gain.
 Results are only shown for models that included explanatory variable.

### 2018-11-22 paper/manuscript.Rmd
add figure question 3 to paper

@@
 
-  # cowplot::plot_grid(
+## Plant strategies
   #   slopes_plot, 
@@
 
+```{r, fig.width=3.25, fig.height=5.1}
+# fig_pca <- plot_pca(pcas, chosen_threshold = 0)
+# fig_distances <- plot_permanova_dist(permanova_plant_distances, permanova_site_distances)
+height1 <- 2.7
+height2 <- 2.4
+# pdf(width = 3.25, height = sum(height1, height2))
+drake::loadd(fig_pca)
+drake::loadd(fig_distances)
+cowplot::plot_grid(
+  fig_pca, 
+  fig_distances,
+  ncol = 1, 
+  rel_heights = c(height1, height2), 
+  align = "v"
+)
+# dev.off()
 ```

### 2018-11-22 main.R

@@ -154,7 +154,10 @@ pca_plan <- drake::drake_plan(
   random_plant_distances = all_randomisations_plant_name(pcas, 99), 
   random_site_distances = all_randomisations_site_name(pcas, 99), 
   permanova_plant_distances = get_permanova(random_plant_distances, "plant_name"),
-  permanova_site_distances = get_permanova(random_site_distances, "site_name")
+  permanova_site_distances = get_permanova(random_site_distances, "site_name"),
+  fig_pca = plot_pca(pcas, chosen_threshold = 0), 
+  fig_distances = plot_permanova_dist(permanova_plant_distances, permanova_site_distances)
+  
 )
 
 facilitation_plan <- drake::drake_plan(

### 2018-11-22 paper/manuscript.Rmd
Add pca variable contribution to manuscript

--- 2018-11-21 paper/manuscript.Rmd
@@
 
-  # cowplot::plot_grid(
-  #   slopes_plot, 
-  #   drake::readd(fig_con_con),
-  #   drake::readd(fig_con_hetero_gain), 
-  #   ncol = 1, 
-  #   rel_heights = c(1/2, 1/2, 1/4))
+## Plant strategies
 
+```{r strategy-fig-height}
+height0 <- 1.55
+height1 <- 2.7
+height2 <- 2.4
+strategy_fig_height <- sum(height0, height1, height2)
+```
+
+```{r, fig.width=3.25, fig.height=strategy_fig_height, fig.cap="PCA results."}
+# fig_pca <- plot_pca(pcas, chosen_threshold = 0)
+# fig_distances <- plot_permanova_dist(permanova_plant_distances, permanova_site_distances)
+# fig_pca_contrib <- plot_pca_variances_and_contributions(pcas, chosen_threshold = 0)
+# pdf(width = 3.25, height = strategy_fig_height)
+drake::loadd(fig_pca_contrib)
+drake::loadd(fig_pca)
+drake::loadd(fig_distances)
+cowplot::plot_grid(
+  fig_pca_contrib,
+  fig_pca, 
+  fig_distances,
+  ncol = 1, 
+  rel_heights = c(height0, height1, height2), 
+  align = "v"
+)
+# dev.off()
 ```

### 2018-11-22 main.R

@@ -162,6 +162,7 @@ pca_plan <- drake::drake_plan(
 
 facilitation_plan <- drake::drake_plan(
   facilitation_models = model_facilitation(dep_frame), 
+  fig_pca_contrib = plot_pca_variances_and_contributions(pcas, chosen_threshold = 0),
   facilitation_random_effects = extract_random_effects(facilitation_models), 
   fig_random_slopes = plot_random_slopes(facilitation_random_effects, dep_frame)
 )

### 2018-11-24 paper/manuscript.Rmd
make slopes plot wider

@@
 # fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
+# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
 # pdf(width = 6.5, height = 4)
@@
 drake::loadd(fig_hetero_con)
-# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
-rw <- c(9,1.2, 6.5,1.2)
+width_left <- 6.5*3/5
+bar_plot_width <- 0.325
+rw <- c(width_left - bar_plot_width,
+        bar_plot_width, 
+        6.5 - width_left - bar_plot_width,
+        bar_plot_width)
 

### 2018-11-24 paper/manuscript.Rmd
Do not need to define and call plot name
Improve looks of quant qual plot and move it to corresponding subsection

@@
 
-We found that, for both the model sets of conspecific and heterospecific pollen, the random structure that was best supported by the data was the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
-When looking at the relative amount of conspecific pollen gained, we observe that only `r round(prop_sig_global*100)`% of species in their communities observed a significant increase in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
-We also observed a positive relationship between the gain in heterospecific pollen and both the relative and absolute gain of conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)). 
-The slope of the relationship is such that across plant species in their communities heterospecific pollen is gained slower than the absolute amount of conspecific pollen but faster than the amount of conspecific pollen relative to the potential selfing.
-
 ```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
@@
 
-slopes_plot <- cowplot::plot_grid(
+cowplot::plot_grid(
   right,
@@
 )
-slopes_plot
+
 # dev.off()
+```
 
@@
 # plot_bagged_vs_open_conspecific(dep_frame)
+```{r fig-average-qual-quant, fig.height=1.29, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
+Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.).
+Bootstrap confidence intervals of the mean (at the 0.05 level) are shown in square brackets."}
+# height1 <- 1.25
+# height2 <- 1.65
+# pdf(width = 3.25 * 2, height = 1.29)
+# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
+width_imp <- 6.5/3
+mult <- 2.125
+width_coef_1 <- (6.5 - width_imp) / (1 + mult)
+width_coef_2 <- 5.6 - width_imp - width_coef_1
+# fig_var_importance <- plot_variable_importance(variable_importance)
+drake::loadd(fig_var_importance)
+drake::loadd(fig_coef_avg)
+cowplot::plot_grid(
+  fig_var_importance[[1]],
+  fig_var_importance[[2]],
+  fig_coef_avg[[1]],
+  fig_coef_avg[[2]],
+  ncol = 4, 
+  rel_widths = c(width_imp/2, width_imp/2,width_coef_1, width_coef_2), 
+  align = "h"
+  )
 # dev.off()
+```
 
@@
 
+We found that, for both the model sets of conspecific and heterospecific pollen, the random structure that was best supported by the data was the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
+When looking at the relative amount of conspecific pollen gained, we observe that only `r round(prop_sig_global*100)`% of species in their communities observed a significant increase in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
+We also observed a positive relationship between the gain in heterospecific pollen and both the relative and absolute gain of conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)). 
+The slope of the relationship is such that across plant species in their communities heterospecific pollen is gained slower than the absolute amount of conspecific pollen but faster than the amount of conspecific pollen relative to the potential selfing.
+
 In addition, AIC scores of the candidate model sets indicated that the species' share in the pollen pool, the functional originality, and the species relative abundance were the most important variables determining the gain in both conspecific and heterospecific pollen (Figure \@ref(fig:fig-model-results-global)).
@@
 Finally, the plant's functional originality and its share in the pollen pool have a moderate positive impact on its quantity but also a negative impact on the quality.
-
-```{r fig-average-qual-quant, fig.height=1.5, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
-Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.).
-Bootstrap confidence intervals of the mean (at the 0.05 level) are shown in square brackets.
-"}
-# height1 <- 1.25
-# height2 <- 1.65
-# pdf(width = 3.25 * 2, height = 1.5)
-# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
-width_imp <- 1
-mult <- 1.5
-# fig_var_importance <- plot_variable_importance(variable_importance)
-drake::loadd(fig_var_importance)
-drake::loadd(fig_coef_avg)
-cowplot::plot_grid(
-  fig_var_importance[[1]],
-  fig_var_importance[[2]],
-  fig_coef_avg[[1]],
-  fig_coef_avg[[2]],
-  ncol = 4, 
-  rel_widths = c(width_imp,width_imp, width_imp*mult, width_imp * mult * 1.45), 
-  align = "h"
-  )
-# dev.off()
-```
 

### 2018-11-24 paper/manuscript.Rmd
Add headings to results

@@
 
+## Competition vs. facilitation
+
 ```{r differences-in-self-pollination}
@@
 
-# pdf(width = 3.25, height = 3)
-# plot_bagged_vs_open_conspecific(dep_frame)
+## Effect of ecological factors in the pollination service
+
 ```{r fig-average-qual-quant, fig.height=1.29, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.

### 2018-11-25 paper/manuscript.Rmd
Include Peter's feedback to methods

@@
 
-We collected data from eleven co-flowering plant communities and their pollinators distributed across three locations, each in a distinct region of the Argentinian Pampas. 
-These locations are distributed across a precipitation gradient with a humid temperate climate in the eastward Flooding Pampas and becoming drier as one moves inland and westward towards the Pampean Grasslands.
-Annual mean temperatures range between 14.8 and 15.8 Celsius. 
+We collected data from eleven co-flowering plant communities and their pollinators in three locations, each in a distinct region of the Argentinian Pampas. 
+These locations are distributed across a precipitation gradient with a humid temperate climate in the eastern Flooding Pampas and becoming drier as one moves inland and westward towards the Pampean Grasslands.
+Annual mean temperatures range between 14.8 and $44.9^\circ$C. 
 In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where due to the lack of available sites, we were only able to sample one restored fragment.
@@
 The first line of evidence can be found in the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
-This is so because heterospecific pollen can be seen as the cost that plants must pay for receiving conspecific pollen from shared pollinators. 
+This is so because heterospecific pollen can be seen as a cost that plants must pay for receiving conspecific pollen from shared pollinators. 
 A negative relationship (when shared pollinators increase heterospecific pollen loads and decrease conspecific loads) may indicate that competition for pollination is strong. 
-This negative relationship could arise, for example, when other, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
-In contrast, a positive relationship (when sharing pollinators increases heterospecific pollen loads but also conspecific pollen deposition) is what should be observed if facilitation is the dominant outcome.
-For example, when the abundance of shared pollinators is positively influenced by floral resources and these positive effects ripple through the mutualistic network [@liao_presence_2011].
+This negative relationship could arise, for example, when another, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
+In contrast, a positive relationship is what should be observed if facilitation is the dominant outcome. 
+For example, when the abundance of shared pollinators is positively influenced by floral resources and these positive effects ripple through the mutualistic network in a chain of positive feedback loops [@liao_presence_2011].
 
 The second line of evidence could be obtained by examining the difference between the amount conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination. 
-It has been shown that self-pollination is favourable to plant reproduction when competition for pollination is strong because it provides insurance against a poor pollination service [@kalisz_benefits_2003].
-If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented could be higher than the amount deposited when floral visits are allowed.
+Self-pollination can be favourable to plant reproduction when competition for pollination is strong because it provides insurance against a poor pollination service [@kalisz_benefits_2003]. 
+If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented could be higher than when floral visits are allowed.
 In contrast, the opposite pattern may indicate that plants benefit from animal-mediated pollination---even a small difference between outcross and self-pollen may be important to plant fitness \R{ref2}[@ref].
-This is particularly so for non-self-fertile species or those in which there is a temporary separation in the maturation of the sexes (dichogamy).
+This is particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy).
 
@@
 In each of the studied communities, we quantified pollen deposition in a subset of plant species between December 2010 and February 2011. 
-This subset comprised of between three and nine common insect-pollinated (entomophilous) species that were flowering during the sampling period. 
-We choose plant species such that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
-Briefly, in each of the selected plants, we removed all flowers leaving only buds that were expected to go into inflorescence on the next day. 
+This subset comprised of between three and nine common insect-pollinated (entomophilous) species that were flowering during the sampling period (see Figure \@ref(fig:fig-trade-off-predictions)a). 
+We chose plant species such that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
+Briefly, in each of the selected plants, we removed all flowers leaving only buds that were expected to go into florescence on the next day. 
 Approximately a quarter of these buds were bagged to prevent animal pollination. 
@@
 
-Similar to @tur_evaluating_2016, to evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution in each of our communities.
+To evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution in each of our communities [@tur_evaluating_2016].
 In these models, the number conspecific pollen grains per stigma was the response variable and the number of heterospecific grains the predictor. 
@@
 We then calculated the mean visit effectiveness (*iii*). 
-As explained before, we define the effectiveness of a visit of pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
-Because both the number of interacting species (and therefore the number of shared pollinators), floral abundance, visitation, and pollen production roughly to followed a power-law distribution, we log-transformed these three predictors before including them in the model.
+As explained before, we define the effectiveness of a visit by pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
+Because the number of interacting species (and therefore the number of shared pollinators), floral abundance, visitation, and pollen production roughly followed a power-law distribution, we log-transformed these three predictors before including them in the model.
 
@@
 For each species that was present in two or more communities, we then calculate (*i*) the median distance between the strategies that the species uses different communities, and (*ii*) the area of the convex hull defined by these points in the first two principal components.
-We then compare these two metrics to those obtained with 99 Monte Carlo randomizations of plant strategies that replace the focal plant strategy by one of another species in its community.
+We then compare these two metrics to those obtained with 99 Monte Carlo randomizations in which we replace the strategy of the focal plant species by one of another species in the dataset.
 

### 2018-11-25 paper/manuscript.Rmd
Switch order of subplots in figure 1

@@
 The dashed line indicates the isoline at which heterospecific pollen is gained at the same rate than conspecific pollen."}
-
 # fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
@@
         bar_plot_width)
-
 left <- cowplot::plot_grid(
+  fig_hetero_con,
+  NULL,
   fig_con_con[[1]],
   fig_con_con[[2]],
-  fig_hetero_con, 
   ncol = 2, 
@@
 )
-
 right <- cowplot::plot_grid(
@@
 )
-
 cowplot::plot_grid(

### 2018-11-25 code/make_fig_con_hetero_gain.R

@@ -196,7 +196,7 @@ plot_bagged_vs_open_conspecific <- function(dep_frame){
     scale_fill_manual(values = pal, na.value = "white") +
     labs(x = "closed to animal pollination", 
          y = "open to animal pollination", 
-         title = "(b) self- vs. animal-mediated pollination", 
+         title = "(c) self- vs. animal-mediated pollination", 
          subtitle = "mean pollen grains per stigma") +
     pub_theme() +
     theme(legend.position = "none") 
@@ -324,6 +324,7 @@ make_fig_con_con <- function(model_formula_ranking, model_linear_fits_species){
 }
 
 make_fig_con_hetero_empirical <- function(dep_frame){
+  require(ggplot2)
   axis_breaks <-  cgm()$log1p_axis_breaks_10
   
   dep_frame %>%
@@ -353,7 +354,7 @@ make_fig_con_hetero_empirical <- function(dep_frame){
     scale_y_continuous(trans = "log1p", breaks = axis_breaks) +
     labs(x = "heterospecific", 
          y = "conspecific", 
-         title = "(c) hetero- vs. conspecific pollen", 
+         title = "(b) hetero- vs. conspecific pollen", 
          subtitle = "mean pollen grains per stigma") +
     pub_theme()
 }

### 2018-11-25 paper/manuscript.Rmd
Explain slope facilitation analysis

--- 2018-11-25 paper/manuscript.Rmd
@@
 
+```{r facilitation-stats, echo = F}
+drake::loadd(facilitation_plot_df)
+counts_facilitation_slope <- facilitation_plot_df %>%
+  dplyr::group_by(effect_category) %>%
+  dplyr::count() %>%
+  dplyr::group_by() %>%
+  dplyr::mutate(np = nn/sum(nn), 
+                np = round(np*100))
+
+# equal number of negative and positive?
+equal_pos_neg <- counts_facilitation_slope$nn[1] == counts_facilitation_slope$nn[3]
+```
+
+When examining the pollen deposited on stigmas of a species in a community we found that in a majority of cases either there was no significant relationship between heterospecific and conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)a).
+Although the overall relationship between between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was equal to the number with a negative relationship (`r if(equal_pos_neg) {counts_facilitation_slope$nn[1]} else {stop("unequal")}`, `r counts_facilitation_slope$np[3]`%).
+This large variation among species was accompained by moderate variation within species (for those sampled in multiple communities). 
+Indeed, *Cypella herbertii*, *Hirschfeldia incana*, and *Carduus acanthoides*, showed significantly positive relationships in some communities and negative in others. 
+Furthermore, although neither a positive or negative was dominant, we found that, in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
+
+```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
+Each dot indicates the predicted median gains for a species in its community (which correspons to the selected random effects in all of our models).
+The horizontal and vertical bars under each dot indicate the 0.05 bootstrap confidence intervals of the estimates.
+The solid lines indicate the overall relationship in each of the bootstrap replicates and were calculated by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al.
+2012).
+The dashed line indicates the isoline at which heterospecific pollen is gained at the same rate than conspecific pollen."}
+# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
+# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
+# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
+# pdf(width = 6.5, height = 4)
+drake::loadd(fig_random_slopes)
+drake::loadd(fig_con_con)
+drake::loadd(fig_hetero_con)
+width_left <- 6.5*3/5
+bar_plot_width <- 0.325
+rw <- c(width_left - bar_plot_width,
+        bar_plot_width, 
+        6.5 - width_left - bar_plot_width,
+        bar_plot_width)
+left <- cowplot::plot_grid(
+  fig_hetero_con,
+  NULL,
+  fig_con_con[[1]],
+  fig_con_con[[2]],
+  ncol = 2, 
+  rel_widths = rw[c(3,4)], 
+  align = "h"
+)
+right <- cowplot::plot_grid(
+  fig_random_slopes[[1]],
+  fig_random_slopes[[2]], 
+  ncol = 2, 
+  align = "h", 
+  rel_widths = rw[1:2]
+)
+cowplot::plot_grid(
+  right,
+  left,
+  ncol = 2,
+  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
+)
+# dev.off()
+```
+
 ```{r differences-in-self-pollination}
@@
   nrow(consistency)
-```
-
-```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
-Each dot indicates the predicted median gains for a species in its community (which correspons to the selected random effects in all of our models).
-The horizontal and vertical bars under each dot indicate the 0.05 bootstrap confidence intervals of the estimates.
-The solid lines indicate the overall relationship in each of the bootstrap replicates and were calculated by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al.
-2012).
-The dashed line indicates the isoline at which heterospecific pollen is gained at the same rate than conspecific pollen."}
-
-# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
-# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
-# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
-# pdf(width = 6.5, height = 4)
-drake::loadd(fig_random_slopes)
-drake::loadd(fig_con_con)
-drake::loadd(fig_hetero_con)
-width_left <- 6.5*3/5
-bar_plot_width <- 0.325
-rw <- c(width_left - bar_plot_width,
-        bar_plot_width, 
-        6.5 - width_left - bar_plot_width,
-        bar_plot_width)
-
-left <- cowplot::plot_grid(
-  fig_con_con[[1]],
-  fig_con_con[[2]],
-  fig_hetero_con, 
-  ncol = 2, 
-  rel_widths = rw[c(3,4)], 
-  align = "h"
-)
-
-right <- cowplot::plot_grid(
-  fig_random_slopes[[1]],
-  fig_random_slopes[[2]], 
-  ncol = 2, 
-  align = "h", 
-  rel_widths = rw[1:2]
-)
-
-cowplot::plot_grid(
-  right,
-  left,
-  ncol = 2,
-  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
-)
-
-# dev.off()
 ```

### 2018-11-25 paper/manuscript.Rmd
Count number of species automatically
Those with positive and negative effects

@@
 drake::loadd(facilitation_plot_df)
+
+# count number of species with positive and negative slopes
 counts_facilitation_slope <- facilitation_plot_df %>%
@@
 
+# species with both positive and negative relationships
+sp_both_pos_neg <- facilitation_plot_df %>%
+  dplyr::filter(effect_category != "neutral") %>%
+  dplyr::group_by(plant_name) %>%
+  dplyr::summarise(both = dplyr::n_distinct(effect_category) > 1) %>%
+  dplyr::filter(both)
+
 # equal number of negative and positive?
@@
 When examining the pollen deposited on stigmas of a species in a community we found that in a majority of cases either there was no significant relationship between heterospecific and conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)a).
-Although the overall relationship between between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was equal to the number with a negative relationship (`r if(equal_pos_neg) {counts_facilitation_slope$nn[1]} else {stop("unequal")}`, `r counts_facilitation_slope$np[3]`%).
+Although the overall relationship between between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was equal to those with a negative relationship (`r if(equal_pos_neg) {counts_facilitation_slope$nn[1]} else {stop("unequal")}`, `r counts_facilitation_slope$np[3]`%).
 This large variation among species was accompained by moderate variation within species (for those sampled in multiple communities). 
-Indeed, *Cypella herbertii*, *Hirschfeldia incana*, and *Carduus acanthoides*, showed significantly positive relationships in some communities and negative in others. 
+Indeed, `r nrow(sp_both_pos_neg)` species  (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed significantly positive relationships in some communities and negative in others.
 Furthermore, although neither a positive or negative was dominant, we found that, in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

### 2018-11-25 paper/manuscript.Rmd
Add numbers to words function

@@
 This large variation among species was accompained by moderate variation within species (for those sampled in multiple communities). 
-Indeed, `r nrow(sp_both_pos_neg)` species  (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed significantly positive relationships in some communities and negative in others.
-Furthermore, although neither a positive or negative was dominant, we found that, in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
+Indeed, `r numbers2words(nrow(sp_both_pos_neg))` species  (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed significantly positive relationships in some communities and negative in others.
+Furthermore, although neither a positive or negative relationship was dominant, we found that, in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
 

### 2018-11-25 code/plotting_and_formatting.R

@@ -109,3 +109,56 @@ humanize <- function(x, sites = NA, random_effects = NA, formula_long = FALSE, t
 c_scale <- function() {
   c("#d7301f", "#fdcc8a", "#fc8d59", "#fef0d9")
 }
+
+
+# numbers to words
+numbers2words <- function(x){
+  ## Function by John Fox found here: 
+  ## http://tolstoy.newcastle.edu.au/R/help/05/04/2715.html
+  ## Tweaks by AJH to add commas and "and"
+  helper <- function(x){
+    
+    digits <- rev(strsplit(as.character(x), "")[[1]])
+    nDigits <- length(digits)
+    if (nDigits == 1) as.vector(ones[digits])
+    else if (nDigits == 2)
+      if (x <= 19) as.vector(teens[digits[1]])
+    else trim(paste(tens[digits[2]],
+                    Recall(as.numeric(digits[1]))))
+    else if (nDigits == 3) trim(paste(ones[digits[3]], "hundred and", 
+                                      Recall(makeNumber(digits[2:1]))))
+    else {
+      nSuffix <- ((nDigits + 2) %/% 3) - 1
+      if (nSuffix > length(suffixes)) stop(paste(x, "is too large!"))
+      trim(paste(Recall(makeNumber(digits[
+        nDigits:(3*nSuffix + 1)])),
+        suffixes[nSuffix],"," ,
+        Recall(makeNumber(digits[(3*nSuffix):1]))))
+    }
+  }
+  trim <- function(text){
+    #Tidy leading/trailing whitespace, space before comma
+    text=gsub("^\ ", "", gsub("\ *$", "", gsub("\ ,",",",text)))
+    #Clear any trailing " and"
+    text=gsub(" and$","",text)
+    #Clear any trailing comma
+    gsub("\ *,$","",text)
+  }  
+  makeNumber <- function(...) as.numeric(paste(..., collapse=""))     
+  #Disable scientific notation
+  opts <- options(scipen=100) 
+  on.exit(options(opts)) 
+  ones <- c("", "one", "two", "three", "four", "five", "six", "seven",
+            "eight", "nine") 
+  names(ones) <- 0:9 
+  teens <- c("ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen",
+             "sixteen", " seventeen", "eighteen", "nineteen")
+  names(teens) <- 0:9 
[…]

### 2018-11-27 paper/manuscript.Rmd
Use percentage addition instead of normal rounding

@@
   dplyr::mutate(np = nn/sum(nn), 
-                np = round(np*100))
+                np = round_preserve_sum(np, 2)*100)
 

### 2018-11-27 paper/manuscript.Rmd
Update text to include significancy of only one SE

@@
 
-When examining the pollen deposited on stigmas of a species in a community we found that in a majority of cases either there was no significant relationship between heterospecific and conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)a).
-Although the overall relationship between between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was equal to those with a negative relationship (`r if(equal_pos_neg) {counts_facilitation_slope$nn[1]} else {stop("unequal")}`, `r counts_facilitation_slope$np[3]`%).
+We first examined the relationship between the heterospecific and conspecifi  pollen deposited on stigmas of a species in a community. 
+We found that in a majority of cases there was either no significant relationship between heterospecific and conspecific pollen or there was a negative relationship (Figure \@ref(fig:fig-trade-off-predictions)a).
+Although the overall relationship between between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was slightly smaller to those with a negative relationship (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`% respectively).
 This large variation among species was accompained by moderate variation within species (for those sampled in multiple communities). 

### 2018-11-27 paper/manuscript.Rmd
Rename chunk of facilitation slopes
Update figure 1 caption

@@
 
-```{r facilitation-stats, echo = F}
+```{r facilitation-random-model-stats, echo = F}
 drake::loadd(facilitation_plot_df)
@@
 
-```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "The interplay between the gain on heterospecific and conspecific pollen.
-Each dot indicates the predicted median gains for a species in its community (which correspons to the selected random effects in all of our models).
-The horizontal and vertical bars under each dot indicate the 0.05 bootstrap confidence intervals of the estimates.
-The solid lines indicate the overall relationship in each of the bootstrap replicates and were calculated by sampling the predictions from 100 conspecific/heterospecific model pairs and estimated the relationship by fitting an standardised major axis (SMA) to each pair (we used the R package smatr 3.4-3, Warton et al.
-2012).
-The dashed line indicates the isoline at which heterospecific pollen is gained at the same rate than conspecific pollen."}
+```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "**Competition vs.
+facilitation at the community level**.
+(a) Some species experience more competition for pollination than others.
+Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities.
+Negative slopes indicate that plants experience competition for animal-mediated pollination, while positive slopes indicate that facilitation is the predominant outcome.
+The number of of plants analised for each species is shown within brakets next to the species name.
+(b) Despite the variety of slopes, overall plants had have more conspecific than heterospecific pollen deposited in their stigmas.
+(c) Generally, plants also had more pollen depositied in their stigmas when they were open to animal-mediated pollination than when they were closed.
+However in the majority of cases the difference is not large enough to be statistically significant at the 0.05 level.
+In all plots, erro bars correspond to ± the standard error (SE)."}
 # fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)

### 2018-11-27 paper/manuscript.Rmd
Remove old chunk of significancy and replace with new one using raw data

@@
 
-```{r differences-in-self-pollination}
-drake::loadd(significant_gain_global, significant_gain_site)
+```{r facilitation-conspecific-stats}
+drake::loadd(con_con_plot_df)
 
-sgg <- glance_table(significant_gain_global)
-prop_sig_global <- sum(sgg$p.value < 0.05) /
-  length(significant_gain_global)
-sgs <- glance_table(significant_gain_site)
-prop_sig_site <- sum(sgs$p.value < 0.05) /
-  length(significant_gain_site)
-
-consistency <- dplyr::inner_join(sgg, sgs, by = 'recipient') %>% 
-  dplyr::mutate_at(.vars = c('p.value.x', 'p.value.y'), 
-            .funs = function(x) x < 0.05) %>%
-  dplyr::mutate(consistent = p.value.x == p.value.y) %>%
-  dplyr::group_by(recipient) %>%
-  dplyr::summarise(p.value.x = mean(p.value.x), 
-            consistent = all(consistent),
-            n_sites = dplyr::n_distinct(site_name)) %>% 
-  dplyr::filter(n_sites > 1)
-prop_consistency <- sum(consistency$consistent)/
-  nrow(consistency)
+sp_con_con <- con_con_plot_df %>%
+  dplyr::group_by(effect_category) %>%
+  dplyr::count() %>%
+  dplyr::group_by() %>%
+  dplyr::mutate(np = n/sum(n), 
+                np = round_preserve_sum(np, 2)*100)
 ```

### 2018-11-27 paper/manuscript.Rmd
Add paragraph of conspecific bagged vs open flowers

@@
 
+We then compared the amount of conspecific pollen deposited on flowers open to animal-mediated pollinators and those that were closed. 
+We found that, generally most species had more conspecific pollen deposited in their stigmas when animal-mediated pollination took place, although for most species the difference was not significant at the 0.05 level (Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c).
+Specifically, the difference weas non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of species in a community, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open.
+
 ## Effect of ecological factors in the pollination service

### 2018-11-28 paper/manuscript.Rmd
Put figures of question two together in the manuscript

@@
 
-```{r fig-average-qual-quant, fig.height=1.29, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
+By examining the AICc scores of a set of linear mixed effect models, we found that the visit efficay and the plants abbundance were the most important ecological variables predicting the amount of conspecific and heterospecific pollen deposited in the plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
+The plants functional originality had an intermediate importance, while, surprisingly, the number of shared pollinators was comparatively less unimportant as it was only included in models with relatively large AICc values.
+
+```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
 Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.).
 Bootstrap confidence intervals of the mean (at the 0.05 level) are shown in square brackets."}
-# height1 <- 1.25
-# height2 <- 1.65
-# pdf(width = 3.25 * 2, height = 1.29)
+height1 <- 1
+height2 <- 1.29
+# pdf(width = 3.25 * 2, height = sum(c(height1, height2)))
 # fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
-width_imp <- 6.5/3
-mult <- 2.125
+width_imp <- 6.5/5*2
+mult <- 2.355 # for 2/3 is 2.125, for 3/5 is 2.355
 width_coef_1 <- (6.5 - width_imp) / (1 + mult)
@@
 drake::loadd(fig_coef_avg)
-cowplot::plot_grid(
+drake::loadd(fig_coefficient_averages)
+
+left_top <- cowplot::plot_grid(
   fig_var_importance[[1]],
   fig_var_importance[[2]],
+  ncol = 2, 
+  align = "h"
+)
+
+left_bottom <- cowplot::plot_grid(
   fig_coef_avg[[1]],
   fig_coef_avg[[2]],
-  ncol = 4, 
-  rel_widths = c(width_imp/2, width_imp/2,width_coef_1, width_coef_2), 
+  rel_widths = c(width_coef_1, width_coef_2), 
   align = "h"
+)
+
+left <- cowplot::plot_grid(
+  left_top, 
+  left_bottom, 
+  ncol = 1, 
+  rel_heights = c(height1, height2)
+)
+
+cowplot::plot_grid(
+  left,
+  fig_coefficient_averages, 
+  ncol = 2,
+  rel_widths = c(sum(c(width_coef_1, width_coef_2)), width_imp)
 )

### 2018-11-28 code/coefficient_averages.R

@@ -145,7 +145,7 @@ plot_coefficient_averages <- function(coefficient_averages, variable_importance)
             plot.margin = margin(t = 5.5, r = 0, b = 5.5, l = 5.5, unit = "pt"),
             plot.title = element_text(margin = margin(b = 5.5, unit = "pt")),
             axis.line.x = element_line(size = 0.25)) +
-      labs(title = "(b) mean effect on pollination service")
+      labs(title = "(c) mean effect on pollination service")
     plots[[2]] <- plots[[2]] + theme(plot.subtitle = element_text(hjust = 1),
                                      axis.line.x = element_line(size = 0.25), 
                                      axis.text.y = element_text(size = 6.5, colour = "black"))

### 2018-11-28 code/get_variable_importance.R

@@ -36,7 +36,7 @@ plot_variable_importance <- function(variable_importance) {
   require(ggplot2)
   
   plot_importance <- function(x){
-    middle_space <- -0.525
+    middle_space <- -0.33  # for 1/3 is -0.525
     x %>% ggplot(aes(x = term, y = value)) +
       # geom_segment(aes(xend = term, yend = 0)) +
       # geom_point(shape = 21, fill = cgm()$pal_rb3[2], size = 6) +

### 2018-11-29 paper/manuscript.Rmd
Add paragraph about model fit

@@
 
+```{r model-fit-statistics}
+drake::loadd(model_formula_ranking, glanced_fixed)
+
+r2_values <- model_formula_ranking$by_model_set %>%
+  dplyr::filter(grepl("abs", pollen_category)) %>% 
+  dplyr::group_by(pollen_category) %>%
+  dplyr::filter(delta_AIC_median == min(delta_AIC_median)) %>%
+  dplyr::select(fixed_formula, pollen_category, scale) %>%
+  dplyr::left_join(glanced_fixed) %>% 
+  dplyr::select(r2m, r2c) %>%
+  dplyr::summarise_all(dplyr::funs(min, median, mean, max)) %>%
+  dplyr::mutate_if(is.numeric, round, digits = 2)
+```
+
+Our models of pollen deposition had relatively high explanatory power. 
+The conditional coefficient of determination R^2^~(c)~ [@nakagawa_general_2013] for the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the models of conspecific pollen and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen.
+A large portion of the explanatory power came from the random effects, in particular for the conspecific pollen models. 
+Indeed, the marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained for the fixed variables alone, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models.
 By examining the AICc scores of a set of linear mixed effect models, we found that the visit efficay and the plants abbundance were the most important ecological variables predicting the amount of conspecific and heterospecific pollen deposited in the plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).

### 2018-11-29 paper/manuscript.Rmd
Add discourse of random effects and improve start of paragraph quest. 2

@@
 
-Our models of pollen deposition had relatively high explanatory power. 
-The conditional coefficient of determination R^2^~(c)~ [@nakagawa_general_2013] for the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the models of conspecific pollen and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen.
+Using a set of LMM, we then examined the role that four ecological variables play on pollen deposition and, by extension, in the quantity and quality of pollination. 
+We found that our models of pollen deposition had relatively high explanatory power. 
+The conditional coefficient of determination R^2^~(c)~ [@nakagawa_general_2013] for the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the bootstrap replicates of theconspecific pollen models and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen.
 A large portion of the explanatory power came from the random effects, in particular for the conspecific pollen models. 
 Indeed, the marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained for the fixed variables alone, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models.
-By examining the AICc scores of a set of linear mixed effect models, we found that the visit efficay and the plants abbundance were the most important ecological variables predicting the amount of conspecific and heterospecific pollen deposited in the plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
-The plants functional originality had an intermediate importance, while, surprisingly, the number of shared pollinators was comparatively less unimportant as it was only included in models with relatively large AICc values.
+As determined by the AICc, the random structure best supported by the data was the one that fits an intercept for each species in a community independently (as opposed to an intercept for each species irrespective of the community they belong to).
+This was so for both the models of conspecific and heterospecific pollen (Table SXX).
 

### 2018-12-01 paper/manuscript.Rmd
Change plant strategies subheading to flexibility of plant strategies
Add paragraph effect of each variable results

@@
 
-## Plant strategies
+## Flexibility of plant strategies
 
@@
 
-```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination.
-Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.).
-Bootstrap confidence intervals of the mean (at the 0.05 level) are shown in square brackets."}
+Out of the four variables we explored, we found that the plants' mean visit efficacy and its abundance were the most important ecological variables predicting the amount of conspecific and heterospecific pollen deposited in the plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
+Surprisingly, the number of shared pollinators was comparatively unimportant as it was only included in models with relatively large AICc values. 
+We found that the sign of the relationship between our ecological factors and pollen deposition tended to be the same for both conspecific and heterospecific pollen. 
+This is, factors that were associated with an increase (or a decrease) in conspecific pollen, were also associated with an increase (or a decrease) in heterospecific pollen deposition. 
+The plants' mean visit efficacy had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
+The positive association with conspecific pollen indicates a positive effect of visit efficacy on the quantity of pollination. 
+However, the difference between the coefficient that relates visit effectiveness to heterospecific and conspecific pollen deposition suggests a marginal negative relationship of this variable and our definition of the quality of the pollination service (Figure \@ref(fig:fig-average-qual-quant)c).
+Contrastingly, the plants' relative abundance had a negative effect in pollen deposition (and consequently the quantity of pollination), but the difference between the coefficients in the models of conspecific and heterospecific pollen indicates a considerable positive impact on the quality of pollination.
+Functional originality had a positive, although comparatively smaller, association with both the quantity and quality of pollination. 
+And, finally, the number of shared pollinators had a negative association with the quantity and quality of pollination, but these impacts were small when compared to all other ecological factors. 
+Although relative abundance, the number of shared pollinators, and the visit effectiveness were positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
+
+```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="**Effect of ecological factors in the pollination service**.
+(a) The plant's visit efficacy and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
+Meanwhile, the number of shared pollinators was relatively unimportant.
+The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable (b) The association of ecological variables on heterospecific pollen tended to be aligned with its association on conspecific pollen.
+Visit efficacy and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association.
+The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific (top panel) and heterospecific pollen (bottom panel).
+Results are only shown for models that included explanatory variable.
+(c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and quality of pollination.
+The plot shows the mean effect (± SE) of the four analysed ecological variables in the quantity and quality of pollination."}
 height1 <- 1

### 2018-12-01 paper/manuscript.Rmd
Add paragraph flexibility of plant strategies question results

@@
 
+```{r pca-stats}
+drake::loadd(pcas)
+chosen_threshold <- 0
+this_pca <- pcas %>%
+    purrr::keep(~ .$call$X$pca_type[1] == "across") %>%
+    purrr::keep(~ .$call$X$threshold[1] == chosen_threshold) %>%
+    extract2(1)
+```
+
+We used a PCA of the analysed species to investigate whether species conserve the strategy they use to minimise competition for pollination. 
+The first two components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
+The first component was dominated by changes on the visit efficacy and the relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality.
+When we plot species that were sampled in more than one community  (Figure \@ref(fig:fig-pca)b), we observe that the plant's strategies do not seem to be clustered per species. 
+Indeed, when we measure the median distance between the plants coordinates in PCA space we found that this distance was significantly smaller than that of randomisations for only one of the analysed species (Figure \@ref(fig:fig-pca)c).
+
 ```{r strategy-fig-height}

### 2018-12-01 paper/manuscript.Rmd
Remove old results

@@
 
-We found that, for both the model sets of conspecific and heterospecific pollen, the random structure that was best supported by the data was the one that included plant species nested in community as the grouping factors (Table \@ref(S-tab:table-aic-random-models)).
-When looking at the relative amount of conspecific pollen gained, we observe that only `r round(prop_sig_global*100)`% of species in their communities observed a significant increase in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
-We also observed a positive relationship between the gain in heterospecific pollen and both the relative and absolute gain of conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)). 
-The slope of the relationship is such that across plant species in their communities heterospecific pollen is gained slower than the absolute amount of conspecific pollen but faster than the amount of conspecific pollen relative to the potential selfing.
-
-In addition, AIC scores of the candidate model sets indicated that the species' share in the pollen pool, the functional originality, and the species relative abundance were the most important variables determining the gain in both conspecific and heterospecific pollen (Figure \@ref(fig:fig-model-results-global)).
-Note that relative abundance plays a more important role determining the gain in heterospecific pollen than the gain in both the absolute and relative amounts of conspecific pollen.
-Surprisingly, the species degree was comparatively less important for predicting pollen gain as it was only included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
-
-```{r fig-model-results-global, eval = F, fig.height = 2, fig.cap = "Distribution of effect estimates of models of conspecific (absolute and relative to the potential selfing) and heterospecific pollen density gain.
-Results are only shown for models that included explanatory variable.
-The median relative variable impotance of the four variables for each model set is shown next to each distribution.
-Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{S-tab:table-aic-fixed-models}) of each candidate model set that includes the variable."}
-drake::readd(fig_coefficient_averages)
-```
-
-Overall we observed that species degree and abundance had a negative relationship with the gain of both absolute and relative conspecific pollen (Figure \@ref(fig:fig-model-results-global)). 
-Functional originality had a weak negative relationship with the absolute gain of conspecific pollen but a small positive effect on the relative gain. 
-The plant's share in the community pollen pool, had opposite effects, with a  positive relationship with the absolute gain and a negative relationship with the relative gain of conspecific pollen.
-Although relative abundance, degree, and the share in the pollen pool were positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
-
-The gain in heterospecific pollen was negatively related to the species abundance but positively to the species' share in the pollen pool, functional originality, and degree (Figure \@ref(fig:fig-model-results-global)).
-Compared to the models of conspecific pollen, the collinearity in the explanatory variables had a larger impact in the models of heterospecific pollen. 
-For instance, when the species abundance was not accounted for, both the species' share in the pollen pool and its functional originality have a negative relationship with the gain in heterospecific pollen (Figure \@ref(S-fig:fig-model-results)).
-
-<!-- Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in conspecific pollen density when comparing open and bagged flowers (Table \@ref(S-tab:table-species-gain-global)).
--->
-<!-- When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(S-tab:table-species-gain-site)).
--->
-Using the results from the models of conspecific and heterospecific pollen gain we then examined the relationship between the explanatory variables and the quantity and quality of pollination (Figure \@ref(fig:fig-average-qual-quant)).
-Degree, had a negative, albeit relatively small, effect on both the quantity and quality of pollination. 
-The species relative abundance has a large positive effect to the quality of pollination accompanied by a relatively smaller negative impact on the quantity. 
-Finally, the plant's functional originality and its share in the pollen pool have a moderate positive impact on its quantity but also a negative impact on the quality.
-
 # Discussion

### 2018-12-01 paper/manuscript.Rmd
Caption figure pca

@@
 
-```{r, fig.width=3.25, fig.height=strategy_fig_height, fig.cap="PCA results."}
+```{r fig-pca, fig.width=3.25, fig.height=strategy_fig_height, fig.cap="**The flexibility of plant strategies**.
+(a) The two first components explain a large proportion of the total variance.
+(b) When plants that were sampled in more than one community are plotted with these two components, we observe that points, which represent the strategy (the particular combination of ecological variables) of a species in a community do not seem to be grouped by plant species.
+(c) This was confirmed using Monte Carlo randomizations of the median distance between strategies of a plant species.
+Only one of the examined species had strategies that were more tightly connected than what would be expected at random."}
 # fig_pca <- plot_pca(pcas, chosen_threshold = 0)

### 2018-12-01 paper/manuscript.Rmd
Fix typos results

@@
 
-We first examined the relationship between the heterospecific and conspecifi  pollen deposited on stigmas of a species in a community. 
+We first examined the relationship between the heterospecific and conspecific pollen deposited on stigmas of a species in a community. 
 We found that in a majority of cases there was either no significant relationship between heterospecific and conspecific pollen or there was a negative relationship (Figure \@ref(fig:fig-trade-off-predictions)a).
-Although the overall relationship between between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was slightly smaller to those with a negative relationship (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`% respectively).
-This large variation among species was accompained by moderate variation within species (for those sampled in multiple communities). 
+Although the overall relationship between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was slightly smaller to those with a negative relationship (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`% respectively).
+This large variation among species was accompanied by moderate variation within species (for those sampled in multiple communities). 
 Indeed, `r numbers2words(nrow(sp_both_pos_neg))` species  (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed significantly positive relationships in some communities and negative in others.
-Furthermore, although neither a positive or negative relationship was dominant, we found that, in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
+Furthermore, although neither a positive or negative relationship was dominant, we found that in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
 
@@
 Negative slopes indicate that plants experience competition for animal-mediated pollination, while positive slopes indicate that facilitation is the predominant outcome.
-The number of of plants analised for each species is shown within brakets next to the species name.
-(b) Despite the variety of slopes, overall plants had have more conspecific than heterospecific pollen deposited in their stigmas.
-(c) Generally, plants also had more pollen depositied in their stigmas when they were open to animal-mediated pollination than when they were closed.
-However in the majority of cases the difference is not large enough to be statistically significant at the 0.05 level.
-In all plots, erro bars correspond to ± the standard error (SE)."}
+The number of plants analysed for each species is shown within brackets next to the species name.
+(b) Despite the variety of slopes, overall plants had more conspecific than heterospecific pollen deposited in their stigmas.
+(c) Generally, plants also had more pollen deposited in their stigmas when they were open to animal-mediated pollination than when they were closed.
+However, in the majority of cases, the difference is not large enough to be statistically significant at the 0.05 level.
+In all plots, error bars correspond to ± the standard error (SE)."}
 # fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
@@
 We then compared the amount of conspecific pollen deposited on flowers open to animal-mediated pollinators and those that were closed. 
-We found that, generally most species had more conspecific pollen deposited in their stigmas when animal-mediated pollination took place, although for most species the difference was not significant at the 0.05 level (Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c).
+We found that generally, most species had more conspecific pollen deposited in their stigmas when animal-mediated pollination took place, although for most species the difference was not significant at the 0.05 level (Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c).
 Specifically, the difference weas non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of species in a community, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open.

### 2018-12-01 paper/manuscript.Rmd
Typos in draft info

@@
 
-**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters; approx.
-`r format(round(msc_wordcount$n_words_stri/10)*10-90, big.mark = ",")` words (includes draft info, excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` reading time.
+**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters, approx.
+`r format(round(msc_wordcount$n_words_stri/10)*10-340, big.mark = ",")` words (includes draft info, excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` reading time.
 
@@
 Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models.
-* Now I use a PCA of the explanatory variables to understand different plant strategies and give a deeper teratment to the facilitation/competition question.
+* Now I use a PCA of the explanatory variables to understand different plant strategies and give a deeper treatment to the facilitation/competition question.
 
-## To do
+## Todo
 
@@
 * I got feedback that "denote" in \lr{denote} might be overly formal? 
-* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you preffer to keep data private?
+* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private?
 

### 2018-12-01 paper/manuscript.Rmd
Using effectiveness instead of efficacy throughout the ms

@@
 * The absolute/relative/gain terminology was confusing. Now  I'm modelling open and bagged pollen counts directly, using the bagged as a sort of control.
-* Introduced visit efficacy instead of the share in the pollen pool as a predictor in the model.
+* Introduced visit effectiveness instead of the share in the pollen pool as a predictor in the model.
 Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models.
@@
 
+* Polish discussion. 
 * Spell-check everything & check that reference list is correct.
-* Choose journal (the manuscript is written for an interdisciplinary journal).
 
@@
 
+* Journal?
 * Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}?
@@
 * Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private?
+* In Figure \@ref(fig:fig-trade-off-predictions)a, I determine if the slope is significantly positive or negative by checking whether the standard errors cross 0.
+Should it be 2 times SE?
+Should all other error bars in Figure \@ref(fig:fig-trade-off-predictions) be 2 times SE?
+* What do you think about the quantity/quality discourse now?
+I'm still unconvinced.
+Maybe I should just go for relationship conspecific/heterospecific instead of quality?
+That would mean that Figure \@ref(fig:fig-average-qual-quant)c would just need the right panel.
+Cause the left is just almost the same as Figure \@ref(fig:fig-average-qual-quant)b, except that it includes models in which the variable was not present and hence "shrinks" the model averaged estimate.
+* Unsure of whether in Figure \@ref(fig:fig-pca)a, it would be better to display the contribution of each component to total variance instead of the cummulative contribution.
 

### 2018-12-01 code/get_variable_importance.R

@@ -36,7 +36,7 @@ plot_variable_importance <- function(variable_importance) {
   require(ggplot2)
   
   plot_importance <- function(x){
-    middle_space <- -0.33  # for 1/3 is -0.525
+    middle_space <- -0.4  # for 1/3 is -0.525
     x %>% ggplot(aes(x = term, y = value)) +
       # geom_segment(aes(xend = term, yend = 0)) +
       # geom_point(shape = 21, fill = cgm()$pal_rb3[2], size = 6) +

### 2018-12-01 code/pca.R

@@ -367,8 +367,8 @@ plot_pca_variances_and_contributions <- function(pcas, chosen_threshold){
     dplyr::rename(term = rowname)
   
   contributions_data %>%
-    humanize() %>% 
-    dplyr::mutate(term = forcats::fct_relevel(term, "visit efficacy", "abundance", "func. originality")) %>%
+    humanize(term_long = F) %>% 
+    dplyr::mutate(term = forcats::fct_relevel(term, "visit effectiv.", "abundance", "func. originality")) %>%
     ggplot(aes(x = as.numeric(dim), y = contribution)) +
     geom_col(aes(fill = term), alpha = 0.75, 
              position = position_stack(reverse = TRUE)) +

### 2018-12-01 code/plotting_and_formatting.R

@@ -56,19 +56,36 @@ humanize <- function(x, sites = NA, random_effects = NA, formula_long = FALSE, t
     x <- dplyr::inner_join(x, sites, by = 'site_name')
   }
   if ('term' %in% names(x)) {
-    x <- x %>%
-      dplyr::mutate(term = dplyr::case_when(
-        grepl('org', term) ~ 'func. originality',
-        grepl('originality', term) ~ 'func. originality',
-        grepl('abn', term) ~ 'abundance',
-        grepl('abu', term) ~ 'abundance',
-        grepl('rab', term) ~ 'abundance',
-        grepl('deg', term) ~ '# shared pol.',
-        grepl('k', term) ~ '# shared pol.',
-        grepl('poc', term) ~ 'visit efficacy',
-        grepl('pollen_cont', term) ~ 'visit efficacy',
-        TRUE ~ term
-      ))
+    if (term_long) {
+      x <- x %>%
+        dplyr::mutate(term = dplyr::case_when(
+          grepl('org', term) ~ 'func. originality',
+          grepl('originality', term) ~ 'func. originality',
+          grepl('abn', term) ~ 'abundance',
+          grepl('abu', term) ~ 'abundance',
+          grepl('rab', term) ~ 'abundance',
+          grepl('deg', term) ~ '# shared pol.',
+          grepl('k', term) ~ '# shared pol.',
+          grepl('poc', term) ~ 'visit effectiveness',
+          grepl('pollen_cont', term) ~ 'visit effectiveness',
+          TRUE ~ term
+        ))
+    } else {
+      x <- x %>%
+        dplyr::mutate(term = dplyr::case_when(
+          grepl('org', term) ~ 'func. originality',
+          grepl('originality', term) ~ 'func. originality',
+          grepl('abn', term) ~ 'abundance',
+          grepl('abu', term) ~ 'abundance',
+          grepl('rab', term) ~ 'abundance',
+          grepl('deg', term) ~ '# shared pol.',
+          grepl('k', term) ~ '# shared pol.',
+          grepl('poc', term) ~ 'visit effectiv.',
+          grepl('pollen_cont', term) ~ 'visit effectiv.',
+          TRUE ~ term
+        ))
+    }
+    
   }
   if ('fixed_formula' %in% names(x)) {
     if (formula_long == TRUE) {

### 2018-12-01 paper/manuscript.Rmd
Changing degree for shared pol. in intro
Close #48

@@
 Second, we investigate the relative contribution that four ecological factors, that together, describe the role of the plant species and the ecological context, have on competition for pollination. 
-We hypothesize that competition for pollination at the community level should increase as the number of pollination partners a plant has increases (species degree).
+We hypothesize that competition for pollination at the community level should increase as the number of shared pollination partners a plant has increases.
 However, other factors like the plant's functional originality, its relative abundance, and the visit effectiveness, should have the potential to compensate this increase in competition by improving either the quality or the quality of pollination.

### 2018-12-01 paper/manuscript.Rmd
Show number of contrasting species for conspecific pollen criteria too

@@
 # species with both positive and negative relationships
-sp_both_pos_neg <- facilitation_plot_df %>%
+get_sp_with_both_pos_neg <- . %>%
   dplyr::filter(effect_category != "neutral") %>%
@@
   dplyr::filter(both)
+sp_both_pos_neg <- facilitation_plot_df %>%
+  get_sp_with_both_pos_neg()
 
@@
                 np = round_preserve_sum(np, 2)*100)
+# species with contrasting behaviours
+sp_con_both_pos_neg <- con_con_plot_df %>%
+  get_sp_with_both_pos_neg()
 ```
@@
 Specifically, the difference weas non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of species in a community, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open.
+Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (*H. incana* and *C. acanthoides*) had both significantly positive and negative differences.
 

### 2018-12-01 paper/manuscript.Rmd
Edit results with a fresh mind. Ready for a first check

@@
 We first examined the relationship between the heterospecific and conspecific pollen deposited on stigmas of a species in a community. 
-We found that in a majority of cases there was either no significant relationship between heterospecific and conspecific pollen or there was a negative relationship (Figure \@ref(fig:fig-trade-off-predictions)a).
-Although the overall relationship between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was slightly smaller to those with a negative relationship (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`% respectively).
-This large variation among species was accompanied by moderate variation within species (for those sampled in multiple communities). 
-Indeed, `r numbers2words(nrow(sp_both_pos_neg))` species  (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed significantly positive relationships in some communities and negative in others.
-Furthermore, although neither a positive or negative relationship was dominant, we found that in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
+We found that the overall slope of the relationship was positive (Table SXX), but a large proportion of plants experienced a negative or no significant relationship or a between heterospecific and conspecific pollen (`r counts_facilitation_slope$np[1]`% and `r counts_facilitation_slope$np[2]`% respectively; Figure \@ref(fig:fig-trade-off-predictions)a).
+Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species, however, we also observed some important differences *within* species. 
+For instance, `r numbers2words(nrow(sp_both_pos_neg))` of species sampled in multiple communities (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed evidence that facilitation (positive relationships) predominates in some communities while competition (negative relationships) predominates in others.
+Furthermore, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, plants, in almost all cases, had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
 
@@
 drake::loadd(con_con_plot_df)
-
+# overall counts of possitive/negative
 sp_con_con <- con_con_plot_df %>%
@@
 
-We then compared the amount of conspecific pollen deposited on flowers open to animal-mediated pollinators and those that were closed. 
-We found that generally, most species had more conspecific pollen deposited in their stigmas when animal-mediated pollination took place, although for most species the difference was not significant at the 0.05 level (Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c).
-Specifically, the difference weas non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of species in a community, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open.
+Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with those that were closed. 
+Here again, we found large differences between plants. 
+Specifically, the difference was non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of plants, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open ($\alpha = 0.05$, Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c).
 Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (*H. incana* and *C. acanthoides*) had both significantly positive and negative differences.
@@
 
-Using a set of LMM, we then examined the role that four ecological variables play on pollen deposition and, by extension, in the quantity and quality of pollination. 
-We found that our models of pollen deposition had relatively high explanatory power. 
-The conditional coefficient of determination R^2^~(c)~ [@nakagawa_general_2013] for the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the bootstrap replicates of theconspecific pollen models and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen.
-A large portion of the explanatory power came from the random effects, in particular for the conspecific pollen models. 
-Indeed, the marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained for the fixed variables alone, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models.
+We then examined the role that four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality) play on pollen deposition and, by extension, in the quantity and quality of pollination.
+We found that the linear mixed models of pollen deposition used had high explanatory power. 
+The conditional coefficient of determination R^2^~(c)~ of the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean of `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the bootstrap replicates of the conspecific pollen models and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen [@nakagawa_general_2013].
+A large portion of this explanatory power came from the random effects, particularly for models of conspecific pollen. 
+The marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained for the fixed variables alone, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models.
+
+We tested two random structures. 
 As determined by the AICc, the random structure best supported by the data was the one that fits an intercept for each species in a community independently (as opposed to an intercept for each species irrespective of the community they belong to).
-This was so for both the models of conspecific and heterospecific pollen (Table SXX).
+This structure was best for both the models of conspecific and heterospecific pollen (Table SXX).
 
-Out of the four variables we explored, we found that the plants' mean visit efficacy and its abundance were the most important ecological variables predicting the amount of conspecific and heterospecific pollen deposited in the plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
-Surprisingly, the number of shared pollinators was comparatively unimportant as it was only included in models with relatively large AICc values. 
-We found that the sign of the relationship between our ecological factors and pollen deposition tended to be the same for both conspecific and heterospecific pollen. 
+Out of the four variables we explored, we found that the plants' mean visit effectiveness and its abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
+Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only included in models with relatively large AICc values.
+
+We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
 This is, factors that were associated with an increase (or a decrease) in conspecific pollen, were also associated with an increase (or a decrease) in heterospecific pollen deposition. 
-The plants' mean visit efficacy had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
-The positive association with conspecific pollen indicates a positive effect of visit efficacy on the quantity of pollination. 
-However, the difference between the coefficient that relates visit effectiveness to heterospecific and conspecific pollen deposition suggests a marginal negative relationship of this variable and our definition of the quality of the pollination service (Figure \@ref(fig:fig-average-qual-quant)c).
+Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
+The positive association with conspecific pollen indicates a positive effect on the quantity of pollination. 
+However, the difference between the coefficient that relates visit effectiveness to heterospecific and conspecific pollen deposition suggests a negative, but marginal, relationship of this variable and our definition of the quality of the pollination service (Figure \@ref(fig:fig-average-qual-quant)c).
 Contrastingly, the plants' relative abundance had a negative effect in pollen deposition (and consequently the quantity of pollination), but the difference between the coefficients in the models of conspecific and heterospecific pollen indicates a considerable positive impact on the quality of pollination.
-Functional originality had a positive, although comparatively smaller, association with both the quantity and quality of pollination. 
-And, finally, the number of shared pollinators had a negative association with the quantity and quality of pollination, but these impacts were small when compared to all other ecological factors. 
+The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and quality of pollination. 
+Finally, the number of shared pollinators had a negative association with the quantity and quality of pollination, but these impacts were small when compared to all other ecological factors. 
 Although relative abundance, the number of shared pollinators, and the visit effectiveness were positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
@@
 ```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="**Effect of ecological factors in the pollination service**.
-(a) The plant's visit efficacy and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
+(a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
 Meanwhile, the number of shared pollinators was relatively unimportant.
 The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable (b) The association of ecological variables on heterospecific pollen tended to be aligned with its association on conspecific pollen.
-Visit efficacy and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association.
+Visit effectiveness and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association.
 The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific (top panel) and heterospecific pollen (bottom panel).
@@
 (c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and quality of pollination.
-The plot shows the mean effect (± SE) of the four analysed ecological variables in the quantity and quality of pollination."}
+The plot shows the model averaged mean effect (± SE) of the four analysed ecological variables in the quantity and quality of pollination."}
 height1 <- 1
@@
 width_imp <- 6.5/5*2
-mult <- 2.355 # for 2/3 is 2.125, for 3/5 is 2.355
+mult <- 2.455 # for 2/3 is xx, for 3/5 is 2.355
 width_coef_1 <- (6.5 - width_imp) / (1 + mult)
@@
 
-We used a PCA of the analysed species to investigate whether species conserve the strategy they use to minimise competition for pollination. 
-The first two components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
-The first component was dominated by changes on the visit efficacy and the relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality.
-When we plot species that were sampled in more than one community  (Figure \@ref(fig:fig-pca)b), we observe that the plant's strategies do not seem to be clustered per species. 
-Indeed, when we measure the median distance between the plants coordinates in PCA space we found that this distance was significantly smaller than that of randomisations for only one of the analysed species (Figure \@ref(fig:fig-pca)c).
+We used a PCA of the analysed species to investigate whether plants strategy are similar across communities or whether they are flexible, and therefore able to adapt to the community context. 
+The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
+The first component was dominated by changes on the visit effectiveness and the relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality.
+When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the strategies of a species do not seem to be close to each other.
+Indeed, when we measured the median distance between the plants coordinates we found that it was significantly smaller than that of randomisations for only one of all analysed species (Figure \@ref(fig:fig-pca)c).
 

### 2018-12-03 paper/manuscript.Rmd
Improve story-telling in mid paragraphs of intro

@@
 
-One of the possible explanations is that sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
-As soon as there are costs, plants start competing for mutualistic partners, even if this competition is not strong enough to produce a **net** negative effect in fitness.
-The possible detrimental effects of competition for pollinators have been long recognised [@robertson_philosophy_1895] and widely documented both experimentally [@lewis_experimental_1961] and theoretically [@levin_competition_1970].
-Multiple factors (like the number of shared pollinators, the plants' relative abundance, visitor fidelity, and traits) have been shown to modulate the strength of competition and, in turn, the fitness outcome [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_effects_1987; @campbell_pollinator_1985].
-It is currently clear that the effects of these factors on fitness have the potential to drive the evolution of flower phenologies, morphologies and reproductive strategies, as well as ecological differentiation [@mitchell_new_2009; @caruso_competition_2000].
+One explanation is that sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
+As soon as there are costs, plants start competing for mutualistic partners, even if this competition is not strong enough to produce a net negative effect in fitness. 
+It has been clear for a long time [@robertson_philosophy_1895; both experimentally @lewis_experimental_1961 and theoretically @levin_competition_1970] that when competition is strong enough, it can be detrimental to plants' fitness.
+So much so that competition for pollination has been shown to drive ecological differentiation [for example by driving the evolution of of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000].
+It is less clear, however, how exactly these strategies of differentiation, in turn, modulate the strength of competition for pollinators. 
+<!-- The ecological factors that modulate the strength of competition, andfactors  -->
+<!-- In addition, it has been shown that the strength of competition for pollinator can be modulated by multiple ecological factors factors (like the number of shared pollinators, the plants' relative abundance, visitor fidelity, and traits) [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_effects_1987; @campbell_pollinator_1985].
+-->
 
-The main two mechanisms through which these ecological factors can affect plant fertilization are: (*i*) by reducing the number of conspecific pollen grains on stigmas or (*ii*) by increasing the deposition of heterospecific pollen [@morales_interspecific_2008].
-For example, plants with more attractive flowers might reduce the number of visits---and hence the amount of conspecific pollen deposited by animals---for those less attractive [@yang_pollinator_2011].
-We denote \R{denote} this as the *quantity* of the pollination service. 
-More subtly, when plants share pollination partners, even receiving a visit might not translate into fertilization due to interspecific pollen transfer [@campbell_mechanism_1985]. 
-Interspecific pollen transfer affects the pollination service because a focal plant might receive pollen from a different species, or conversely, pollen from the focal plant might be lost to different species.
+There are two main mechanisms through which factors of ecological differentiation can affect plant fertilization [@morales_interspecific_2008]. 
+The first mechanism, is by reducing the number of conspecific pollen grains on stigmas. 
+For example, plants with distinctively attractive flowers might reduce the number of visits---and hence the amount of conspecific pollen deposited by animals---for those less attractive [@yang_pollinator_2011].
+This can be seen as the *quantity* of the pollination service.
+More subtly, when plants employ reproductive strategies that imply sharing pollination partners, even receiving a visit might not translate into fertilization.
+This so because a focal plant might receive pollen from a different species, or conversely, pollen from the focal plant might be lost to different species. 
+This second mechanism, is called interspecific pollen transfer [@campbell_mechanism_1985]. 
 Generally speaking, the higher the proportion of conspecific relative to heterospecific pollen the higher the *quality* of the pollination service. 
@@
 
-Instead, co-flowering plants often occur in communities in which multiple intertwined factors operate simultaneously and lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
+Instead, co-flowering plants often occur in communities in which the factors that determine differentiation are tightly intertwined,  operate simultaneously, and may lead to phenomena not observed at smaller scales [@flanagan_effects_2011].
 For instance, recent empirical evidence suggests that plants with flowering traits that are original relative to others in the community have generally fewer interaction partners [@coux_linking_2016].
 This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them; in contrast, a species that interacts with a large number of species does so comparatively weakly.
-If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollination in species with original traits and an increase in species with a large number of interaction partners [@gibson_can_2012].
-Alternatively, it might also be the case that flower/pollen density is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
+If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with original traits and an increase in species with a large number of interaction partners [@gibson_can_2012].
+Alternatively, based on evidence from two/three species systems, it might also be the case that flower/pollen density is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
 Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both the pollen being transported by pollinators and their visits compared to other species.
 In this case, a potential reduction in the quantity of pollination (the amount of conspecific pollen received) could be compensated by an increase in the quality of pollination (the amount of conspecific relative to heterospecific pollen received).
-To complicate things more, autonomous self-pollination can also influence a plant sensitivity to competition for pollination because it can ensure reproduction even in the absence of outcross pollen [@kalisz_benefits_2003].
-Altogether, multiple, potentially correlated, factors may act simultaneously.
-Therefore, understanding the relative importance of these factors and how plant species harness them to minimise competition for pollination within their communities requires extensive data. 
+<!-- To complicate things more, autonomous self-pollination can also influence a plant sensitivity to competition for pollination because it can ensure reproduction even in the absence of outcross pollen [@kalisz_benefits_2003].
+-->
+<!-- Altogether, multiple, potentially correlated, factors may act simultaneously.  -->
+The effect and relative importance that the factors of ecological differentiation in the plants' communities play on the pollination service has not yet been empirically evaluated in natural communities.
 Both describing the structure of the interactions and the pollen flows that occur within it.

### 2018-12-03 paper/manuscript.Rmd
Reshape intro to frame factors as strategy differentiation

@@
 The effect and relative importance that the factors of ecological differentiation in the plants' communities play on the pollination service has not yet been empirically evaluated in natural communities.
-Both describing the structure of the interactions and the pollen flows that occur within it.
 
-Here, we explore competition for pollination at the community scale using comprehensive empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
-First, we ask the extent to which the outcome of animal-mediated pollination is facilitation or competition. 
+Here, we investigate competition for pollination at the community scale using comprehensive empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
+First, we need to understand the extent to which the outcome of animal-mediated pollination is facilitation or competition. 
 If facilitation is the primary outcome we would expect (*i*) an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the heterospecific pollen [@tur_evaluating_2016] and (*ii*) a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than that due to self-pollination.
-Second, we investigate the relative contribution that four ecological factors, that together, describe the role of the plant species and the ecological context, have on competition for pollination. 
+Second, we investigate the relative contribution that four ecological factors, that together describe the strategies of ecological differentiation, have on competition for pollination. 
 We hypothesize that competition for pollination at the community level should increase as the number of shared pollination partners a plant has increases.
 However, other factors like the plant's functional originality, its relative abundance, and the visit effectiveness, should have the potential to compensate this increase in competition by improving either the quality or the quality of pollination.
-Third, and finally, we explore how community influences the way plants use these factors to minimise competition. 
-Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and are hence is likely to be defined by the ecological context. 
+Third, and finally, we explore how community context influences the way plants use these factors to minimise competition. 
+\R{third-hypothesis}Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and are hence is likely to be defined by the local context.
 If plant species adopt comparable roles across different communities, we should expect plant strategies to be more similar within species than across species in the study. 

### 2018-12-03 paper/manuscript.Rmd
cosmetic changes to intro

@@
 Alongside the direct mutualisms between plants and their pollinators, \R{ref-needed-possitive-loops} the support to biodiversity can be achieved as a result of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plant [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008].
-Facilitation is able to promote species coexistence because it offsets the effects of direct competition for resources [@stachowicz_mutualism_2001]. 
-Indeed, studies that are fundamental to our current knowledge of mutualism predict that the maximum number of coexisting species---an upper limit to biodiversity---is achieved when the number of mutualistic partners is maximised in a community [@bastolla_architecture_2009].
+In sum, inter-species facilitation is able to promote species coexistence because it is able to offset the effects of direct competition for resources [@stachowicz_mutualism_2001]. 
+What is more, studies that are fundamental to our current knowledge of mutualism predict that the maximum number of coexisting species---effectively an upper limit to biodiversity---is achieved when the number of shared mutualistic partners is maximised in a community [@bastolla_architecture_2009].
 And yet, not every pollinator species in natural communities interacts with every species of plant.

### 2018-12-03 paper/manuscript.Rmd
cosmetic changes to methods

@@
 The slope and intercept of this relationship were allowed to differ between plant species, which were modelled as a random effect. 
-Models were fitted using the function `lmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]
+Models were fitted using the function `lmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]. 
 To compare the conspecific pollen deposited with and without animal-mediated pollination, we performed a Mann-Withney U test of the number of conspecific pollen grains per stigma between un-bagged and bagged flowers for each of the studied species in a community.
@@
 Our second objective is to investigate the relative contribution that different factors that describe the plants' role and its ecological context have on the pollination service. 
-Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them, and (*iv*) the plants functional originality.
+Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them (see Data Analysis section below for more details), and (*iv*) the plants functional originality.
 Here, we define visit effectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.

### 2018-12-03 paper/manuscript.Rmd
add key idea of discussion

@@
 
+We found that the community context plays a central role at determining competition for pollination and in turn the quantity and quality of pollination. 
+Although the factors that previous studies with a small number of species are identify as important, are still relevant at the community level, we identify some phenomena that may not be observable in systems with two or three species.
+Specifically, XX
+
 * We did find a trade-off between the number of partners a species interacts with and the mutualistic service.

### 2018-12-08 paper/manuscript.Rmd
request feedback question three framing in intro
Improved first paragraph of discussion

--- 2018-12-03 paper/manuscript.Rmd
@@
 * Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}?
-* I got feedback that "denote" in \lr{denote} might be overly formal? 
 * Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private?
@@
 * Unsure of whether in Figure \@ref(fig:fig-pca)a, it would be better to display the contribution of each component to total variance instead of the cummulative contribution.
+* I'm not very happy with the way the third hypothesis is described in the intro (\lr{third-hypothesis}). I would appreciate ideas to rephrase it clearly
 
@@
 
+Our results suggest that the community context plays a central role at determining competition for pollination. 
+First, we found that the costs of pollinator sharing are pervasive.
+In particular, we found that a significant proportion of species undergoes overall neutral or competitive effects from animal mediated pollination.
+Second, we found that plants are able to minimise the intensity of this competition using multiple strategies, however, conspecific and heterospecific pollen deposition are tightly coupled and threfore these strategies are likely to involve a trade-off between the quantity and quality of pollination.
+Third, we found that these strategies are strongly shaped by the community context, this is, the same plant species can adopt dramatically different strategies depending on the comminity it belongs to.
+
 * We did find a trade-off between the number of partners a species interacts with and the mutualistic service.

### 2018-12-08 paper/manuscript.Rmd
Second paragraph of discussion: trade-offs

@@
 
+\R{disc-facil-comp}Both of the tests used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community.
+Althouh a recent study already suggested a wide range of outcomes in multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood.
+Here we show that prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.  
 * We did find a trade-off between the number of partners a species interacts with and the mutualistic service.

### 2018-12-08 paper/manuscript.Rmd
Third and fourth paragraph of discussion: abundance and visit effectiv

@@
 Here we show that prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.
+
+These trade-offs were most evident precisely in the strategies that most strongly modulate pollen deposition. 
+We found that the strategies that increased the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition. 
+Adopting a strategy of high visitation increasses the rates of conspecific pollen deposition at the expense of a reduction in the quality of pollination even when the visitors carry a high proportion of conspecific pollen.
+Similarly, adopting a strategy of high abundance reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen.
+
+Our results corroborate the importance that previous studies have attributed to the role that visitation and abundance play at determining competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008].
+The fact that they also involve a trade-off between the quantity and quality of pollination might explain the often contrasting results that these studies, based on two or three species systems obtained.
+Simultaneously, because visitation, pollen production and abundance are correlated, these trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between these factors to increasse conspecific pollen and reduce heterospecific pollen deposition.
+The relative wide range of in our model coefficients might be explained by the wide variation of the extent to which plant species are affected by pollen deposition. 
+While some species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
 * We did find a trade-off between the number of partners a species interacts with and the mutualistic service.

### 2018-12-08 paper/manuscript.Rmd
Paragraph functional originality and #shared pol

@@
 Interacting with more species alone is often accompanied by a decreases in both the quantity and quality of pollination.
-* However, the effect and importance of this trade-off is comparatively small when considering other factors that describe the species niche and its ecological settings. 
+Two other strategies involved a much smaller trade-off than the abundance or visit efficacy. 
+Specifically, having high functional originality relative to other species in the community or sharing few pollinators is benetitial to both the quantity and quality of pollination.
+Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
+This is not to say that these variables are actually unimportant to pollen deposition, rather it suggest that the processes that underlay them might be more complex than what our metrics are able to capture.
+Especially in what relates to conspecific pollen deposition, which was harder to model than heterospecific pollen. 
+On the one hand these two variables are more tighly related to the understanding of competition at the community scale than metrics of dominance. 
+On the other, having distinct traits, for example trough phenology differentiation, has a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities [@ye_competition_2014].
+In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
+Similarly, other factors, not meassured in our study, like pollinator behaviour and densities [@ye_competition_2014; ref to Melissa's paper?] or the spatial context [@cariveau_spatially_2009] can also shape the way sharing pollinators affects the pollination service.
+
 * We found that animal pollination only brings a small amount of extra conspecific pollen (compared selfing) if any.

### 2018-12-08 paper/manuscript.Rmd
Strategies paragraph

@@
 Especially in what relates to conspecific pollen deposition, which was harder to model than heterospecific pollen. 
+\R{strategies}Regardless of the specific factors involved it is clear, however, that the community context has a very important effect on the way plant species respond to competition for pollination. 
+First, in the models of pollen deposition, the random structure that allowed plants of the same species to have different intercepts across communities was much better supported by the data than the structure that fixed the intercept for a plant species irrespective of the community.
+Second, in a large majority of cases, the strategies that a species uses across communities are not more similar to each other than what would be expected at random. 
+Lit? Context?
 On the one hand these two variables are more tighly related to the understanding of competition at the community scale than metrics of dominance. 

### 2018-12-08 paper/manuscript.Rmd
Changes to ¶ about # shared pol. and func. originality

@@
 Two other strategies involved a much smaller trade-off than the abundance or visit efficacy. 
-Specifically, having high functional originality relative to other species in the community or sharing few pollinators is benetitial to both the quantity and quality of pollination.
+The two other strategies we analysed involved a smaller trade-off than the abundance or visit efficacy. 
+Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be benetitial to both the quantity and quality of pollination.
 Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
-This is not to say that these variables are actually unimportant to pollen deposition, rather it suggest that the processes that underlay them might be more complex than what our metrics are able to capture.
-Especially in what relates to conspecific pollen deposition, which was harder to model than heterospecific pollen. 
+This does not necessarily implies that these variables are unimportant to pollen deposition. 
+Instead, it is also possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
+Particularly so for conspecific pollen deposition, which was harder to predict than heterospecific pollen. 
+For instance, having distinct traits, for example through phenology differentiation, might have a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities (ref).
+In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
+Alternatively, other factors that we were unable to meassure, like pollinator behaviour and densities [@ye_competition_2014; @flanagan_effects_2011; @melissas_2019?] or the spatial context [@cariveau_spatially_2009], can also shape the way sharing pollinators affect the pollination service.
 \R{strategies}Regardless of the specific factors involved it is clear, however, that the community context has a very important effect on the way plant species respond to competition for pollination. 

### 2018-12-08 paper/manuscript.Rmd
Split ¶ about dominance into two

@@
 Similarly, adopting a strategy of high abundance reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
-
 Our results corroborate the importance that previous studies have attributed to the role that visitation and abundance play at determining competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008].
 The fact that they also involve a trade-off between the quantity and quality of pollination might explain the often contrasting results that these studies, based on two or three species systems obtained.
-Simultaneously, because visitation, pollen production and abundance are correlated, these trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between these factors to increasse conspecific pollen and reduce heterospecific pollen deposition.
-The relative wide range of in our model coefficients might be explained by the wide variation of the extent to which plant species are affected by pollen deposition. 
-While some species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
-* We did find a trade-off between the number of partners a species interacts with and the mutualistic service.
-Interacting with more species alone is often accompanied by a decreases in both the quantity and quality of pollination.
-Two other strategies involved a much smaller trade-off than the abundance or visit efficacy. 
+
+Simultaneously, because visitation, pollen production and abundance are correlated, the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increassing conspecific pollen and reduce heterospecific pollen deposition.
+The relative wide range of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
+While some plant species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
+
 The two other strategies we analysed involved a smaller trade-off than the abundance or visit efficacy. 

### 2018-12-09 paper/manuscript.Rmd
Minor edits to discussion

@@
 
-\R{disc-facil-comp}Both of the tests used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community.
+\R{disc-facil-comp}Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community.
 Althouh a recent study already suggested a wide range of outcomes in multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood.
@@
 
-Simultaneously, because visitation, pollen production and abundance are correlated, the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increassing conspecific pollen and reduce heterospecific pollen deposition.
+Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increassing conspecific pollen and reduce heterospecific pollen deposition.
 The relative wide range of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
@@
 This does not necessarily implies that these variables are unimportant to pollen deposition. 
-Instead, it is also possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
+Instead, it is possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
 Particularly so for conspecific pollen deposition, which was harder to predict than heterospecific pollen. 

### 2018-12-09 paper/manuscript.Rmd
Remove old discussion

@@
 Alternatively, other factors that we were unable to meassure, like pollinator behaviour and densities [@ye_competition_2014; @flanagan_effects_2011; @melissas_2019?] or the spatial context [@cariveau_spatially_2009], can also shape the way sharing pollinators affect the pollination service.
+
 \R{strategies}Regardless of the specific factors involved it is clear, however, that the community context has a very important effect on the way plant species respond to competition for pollination. 
@@
 Lit? Context?
-On the one hand these two variables are more tighly related to the understanding of competition at the community scale than metrics of dominance. 
-On the other, having distinct traits, for example trough phenology differentiation, has a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities [@ye_competition_2014].
-In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
-Similarly, other factors, not meassured in our study, like pollinator behaviour and densities [@ye_competition_2014; ref to Melissa's paper?] or the spatial context [@cariveau_spatially_2009] can also shape the way sharing pollinators affects the pollination service.
 
-* We found that animal pollination only brings a small amount of extra conspecific pollen (compared selfing) if any.
-This relatively small difference is probably very important because, first, some plants simply aren't self-fertile, even if their own pollen gets deposited on the stigma.
-Second, in some flowers there is temporary separation in the maturation of the sexes (dichogamy) that favours cross-pollination as, evolutionary, it has been shown to be a better strategy than cloning.
-* Overall it seems like density seems to be a dominant force behind pollen transfer.
-If you have many individuals of your species, you get fewer visits (dilution of the pollinators flying around), which is reflected in a smaller amount of deposited pollen.
-We show that abundant plants also tend to comprise a greater component of the pollen source pool and so the end result is that get more conspecific pollen per visit than heterospecific pollen.
-* Our result of the comparatively weak effect of the mutualistic trade-off is important because it is fundamentally related to the way we understand and mathematically represent mutualistic systems. 
-Some of the most widely used theoretical models of pollination account for the negative effects of mutualism by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree.
-This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
-However we show that care must be taken because the negative effects of the mutualistic trade-off in both the quantity and quality of pollination can be offset by density mechanisms.
-Species with large degrees also tend be abundant and prolific pollen producers.
-
-Interspecific pollen transfer is the most important factor underpining competition for pollinators [@campbell_mechanism_1985]
-
-Traits are determined by competition for pollination -- Caruso 2000
-
-, all while accounting for the traits of the species that integrate the community.  extent to which plants employ  relative contribution and the interplay of each factor requires
-First, that plants might use different strategies to reduce competition for pollination. 
-Second that the effect of coorelated factors in the quality and quantity of pollination [like generalism, its relative abundance, and visitation frequency; @sargent_role_2006] might balance each other.
-
-Interspecific pollen transfer was responsible for reduction in set set for one species but loss of conspecific pollen was responsible for another -- Campbell and Motten 1985
-
-Plant species vary greatly on the extent to which each of these two mechanisms can affect fertilisation [@campbell_mechanism_1985], a large plant
-
-Competition can also be mediated by pollinator density, not just plant density [@ye_competition_2014]
-
-Check @flanagan_effects_2011 for discussion on the effects when one thinks about communities.
-
-Traits can have a role only with High abundances, where being dominant can be bad for other plants in communities. Abbundance is important in small species number systems [@munoz_presence_2008]
-
-Plants have mechanishms that prevent heterospecific pollen deposition.
-@bartomeus_high_2008 show that even when a plant dominates the pollen transfer network opther species might not receive lots of heterospecific pollen [@bartomeus_high_2008; @flanagan_increased_2010]
-
-Pollen limitation is inversely related to abundance, but high abundance is also related to mate limitation [@moeller_facilitative_2004]
-
-Competition also depends on the spatial extent [@cariveau_spatially_2009]
-
-Facilitation is still controversial? [@feldman_when_2004]
+## Conclusion
 

### 2018-12-09 paper/manuscript.Rmd
Questions to discussion

@@
 * I'm not very happy with the way the third hypothesis is described in the intro (\lr{third-hypothesis}). I would appreciate ideas to rephrase it clearly
+* Does the paragraph in \lr{disc-facil-comp} needs more meat? Any suggestions?
+* My background in the topic is limited, would be grateful if you could point me out to key papers that could be used to put some context to the finding of the "flexibility" of plants strategies (paragraph in \lr{strategies})
+* Part of the discussion before revolved about the fact that degree is commonly used in theoretical models of mutualism to adjust the mutualistic benefit of generalist species.
+I've removed it because I think the discussion is already a bit long and didn't fit that nicely in the story.
+You think it should be included?
 

### 2018-12-09 paper/manuscript.Rmd
Fix word count in front matter

@@
 **Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters, approx.
-`r format(round(msc_wordcount$n_words_stri/10)*10-340, big.mark = ",")` words (includes draft info, excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` reading time.
+`r format(round(msc_wordcount$n_words_stri/10)*10, big.mark = ",")` words (excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` min.
+reading time.
 

### 2018-12-09 paper/manuscript.Rmd
Minor edits to results
Close #51

@@
 We first examined the relationship between the heterospecific and conspecific pollen deposited on stigmas of a species in a community. 
-We found that the overall slope of the relationship was positive (Table SXX), but a large proportion of plants experienced a negative or no significant relationship or a between heterospecific and conspecific pollen (`r counts_facilitation_slope$np[1]`% and `r counts_facilitation_slope$np[2]`% respectively; Figure \@ref(fig:fig-trade-off-predictions)a).
+We found that the overall slope of the relationship was positive (Table SXX), but a large proportion of plants experienced a negative or no significant relationship between heterospecific and conspecific pollen (`r counts_facilitation_slope$np[1]`% and `r counts_facilitation_slope$np[2]`% respectively; Figure \@ref(fig:fig-trade-off-predictions)a).
 Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species, however, we also observed some important differences *within* species. 
 For instance, `r numbers2words(nrow(sp_both_pos_neg))` of species sampled in multiple communities (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed evidence that facilitation (positive relationships) predominates in some communities while competition (negative relationships) predominates in others.
-Furthermore, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, plants, in almost all cases, had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
+Furthermore, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen, plants, in almost all cases, had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
 
@@
 
-We tested two random structures. 
+We tested two structures for the random effects. 
 As determined by the AICc, the random structure best supported by the data was the one that fits an intercept for each species in a community independently (as opposed to an intercept for each species irrespective of the community they belong to).
@@
 The positive association with conspecific pollen indicates a positive effect on the quantity of pollination. 
-However, the difference between the coefficient that relates visit effectiveness to heterospecific and conspecific pollen deposition suggests a negative, but marginal, relationship of this variable and our definition of the quality of the pollination service (Figure \@ref(fig:fig-average-qual-quant)c).
+However, the mean of the coefficients that relates visit effectiveness to heterospecific pollen deposition is slightly larger than that of conspecific pollen. 
+This suggest a negative, albeit marginal, relationship of visit effectiveness and our definition of the quality of the pollination service (Figure \@ref(fig:fig-average-qual-quant)c). 
 Contrastingly, the plants' relative abundance had a negative effect in pollen deposition (and consequently the quantity of pollination), but the difference between the coefficients in the models of conspecific and heterospecific pollen indicates a considerable positive impact on the quality of pollination.
@@
 Meanwhile, the number of shared pollinators was relatively unimportant.
-The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable (b) The association of ecological variables on heterospecific pollen tended to be aligned with its association on conspecific pollen.
+The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable.
+(b) The association of ecological variables on heterospecific pollen tended to be aligned with its association on conspecific pollen.
 Visit effectiveness and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association.
@@
 
-We used a PCA of the analysed species to investigate whether plants strategy are similar across communities or whether they are flexible, and therefore able to adapt to the community context. 
+We used a PCA of the analysed species to investigate whether plants strategies are similar across communities or whether they are flexible, and therefore able to adapt to the community context. 
 The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
-The first component was dominated by changes on the visit effectiveness and the relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality.
+The first component was dominated by changes in the visit effectiveness and the relative abundance, while the second component was dominated by the number of shared pollinators and the plant's functional originality.
 When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the strategies of a species do not seem to be close to each other.
-Indeed, when we measured the median distance between the plants coordinates we found that it was significantly smaller than that of randomisations for only one of all analysed species (Figure \@ref(fig:fig-pca)c).
+Indeed, when we measured the median distance between the plants coordinates, we found that it was significantly smaller than that of randomisations for only one of all analysed species (Figure \@ref(fig:fig-pca)c).
 

### 2018-12-09 paper/manuscript.Rmd
Add items to questions/todo

@@
 * Spell-check everything & check that reference list is correct.
+* I think its not supper clear in the manuscript what is meant by a plant strategy. Need to re-check in the next iteration.
 
@@
 * Journal?
+* I think the story is still a bit disperse.
+Will appreciate feedback on identifying the most important/exciting findings to tie the others around it.
+So far the central topic is scaling up of competition to the community level.
 * Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}?

### 2018-12-09 paper/manuscript.Rmd
Changes from factors to strategies in methods/results
Close #53

@@
 
-## Effect of ecological factors in the pollination service
+## Effect of plant strategies in the pollination service
 
-Our second objective is to investigate the relative contribution that different factors that describe the plants' role and its ecological context have on the pollination service. 
+Our second objective is to investigate the relative contribution that different factors that describe the plants' strategies to minimise competition have on the pollination service. 
 Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them (see Data Analysis section below for more details), and (*iv*) the plants functional originality.
@@
 
-We investigate the impact of the ecological factors on the pollination services using two metrics: the quantity and the quality of pollination. 
+We investigate the impact of the ecological strategies on the pollination services using two metrics: the quantity and the quality of pollination. 
 Here we define the quality of pollination as the amount of conspecific pollen and the quality of pollination as the amount of conspecific pollen *relative* to heterospecific pollen. 
@@
 
-## Effect of ecological factors in the pollination service
+## Effect of ecological strategies in the pollination service
 
@@
 We then examined the role that four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality) play on pollen deposition and, by extension, in the quantity and quality of pollination.
+These variables define the strategies that plants use to minimise competition for pollination. 
 We found that the linear mixed models of pollen deposition used had high explanatory power. 
@@
 
-We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
-This is, factors that were associated with an increase (or a decrease) in conspecific pollen, were also associated with an increase (or a decrease) in heterospecific pollen deposition. 
+We found that the relationship between each of the strategies and pollen deposition was similar for both conspecific and heterospecific pollen. 
+This is, strategies that were associated with an increase (or a decrease) in conspecific pollen, were also associated with an increase (or a decrease) in heterospecific pollen deposition. 
 Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
@@
 The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and quality of pollination. 
-Finally, the number of shared pollinators had a negative association with the quantity and quality of pollination, but these impacts were small when compared to all other ecological factors. 
+Finally, the number of shared pollinators had a negative association with the quantity and quality of pollination, but these impacts were small when compared to the other variables. 
 Although relative abundance, the number of shared pollinators, and the visit effectiveness were positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
 
-```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="**Effect of ecological factors in the pollination service**.
+```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
 (a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.

### 2018-12-09 paper/manuscript.Rmd
Spellcheck discussion

@@
 
-Our results suggest that the community context plays a central role at determining competition for pollination. 
+Our results suggest that the community context plays a central role in determining competition for pollination. 
 First, we found that the costs of pollinator sharing are pervasive.
-In particular, we found that a significant proportion of species undergoes overall neutral or competitive effects from animal mediated pollination.
-Second, we found that plants are able to minimise the intensity of this competition using multiple strategies, however, conspecific and heterospecific pollen deposition are tightly coupled and threfore these strategies are likely to involve a trade-off between the quantity and quality of pollination.
-Third, we found that these strategies are strongly shaped by the community context, this is, the same plant species can adopt dramatically different strategies depending on the comminity it belongs to.
+In particular, we found that a significant proportion of species undergoes overall neutral or competitive effects from animal-mediated pollination.
+Second, we found that plants are able to minimise the intensity of this competition using multiple strategies, however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these strategies are likely to involve a trade-off between the quantity and quality of pollination.
+Third, we found that these strategies are strongly shaped by the community context, this is, the same plant species can adopt dramatically different strategies depending on the community it belongs to.
 
 \R{disc-facil-comp}Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community.
-Althouh a recent study already suggested a wide range of outcomes in multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood.
-Here we show that prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.
+Although a recent study already suggested a wide range of outcomes in a multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood.
+Here we show that the prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.
 
@@
 We found that the strategies that increased the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition. 
-Adopting a strategy of high visitation increasses the rates of conspecific pollen deposition at the expense of a reduction in the quality of pollination even when the visitors carry a high proportion of conspecific pollen.
+Adopting a strategy of high visitation increases the rates of conspecific pollen deposition at the expense of a reduction in the quality of pollination even when the visitors carry a high proportion of conspecific pollen.
 Similarly, adopting a strategy of high abundance reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
@@
 
-Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increassing conspecific pollen and reduce heterospecific pollen deposition.
-The relative wide range of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
+Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition.
+The relatively wide range of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
 While some plant species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
@@
 The two other strategies we analysed involved a smaller trade-off than the abundance or visit efficacy. 
-Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be benetitial to both the quantity and quality of pollination.
+Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be beneficial to both the quantity and quality of pollination.
 Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
-This does not necessarily implies that these variables are unimportant to pollen deposition. 
+This does not necessarily imply that these variables are unimportant to pollen deposition. 
 Instead, it is possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
@@
 In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
-Alternatively, other factors that we were unable to meassure, like pollinator behaviour and densities [@ye_competition_2014; @flanagan_effects_2011; @melissas_2019?] or the spatial context [@cariveau_spatially_2009], can also shape the way sharing pollinators affect the pollination service.
+Alternatively, other factors that we were unable to measure, like pollinator behaviour and densities [@ye_competition_2014; @flanagan_effects_2011; @melissas_2019?] or the spatial context [@cariveau_spatially_2009], can also shape the way sharing pollinators affect the pollination service.
 

### 2018-12-09 paper/manuscript.Rmd
Beautiful conclusion

@@
 
+Here we show that competition for pollination is pervasive in ecological communities and that its effect on plant species strongly influenced by the community context. 
+Our results suggest that at the community level, the strategies that plants adopt to minimise competition require reaching a fine balancing act between the quantity and quality of pollination. 
+In particular, strategies that promote dominance of the species in its community (in terms of abundance, visitation and participation in the pollen pool) had the largest impacts on pollen deposition but also the largest trade-offs between increasing deposition of conspecific pollen and reducing that of heterospecific pollen.
+Contrastingly, strategies that increase niche differentiation (functional originality and specialization) were positive to both the quantity and quality of pollination, but its effect was comparatively small compared to strategies of dominance.
+Remarkably, the particular strategy a plant uses is strongly shaped by its context and hence can be dramatically different in each of the communities it is part of. 
+[Wider application? Catchy closing line ideas?]
+
 # Acknowledgements

### 2018-12-09 main.R
Small fixes to questions

@@ -207,7 +207,7 @@ reporting_plan <- drake::drake_plan(
   abstract = readLines(drake::file_in("./paper/abstract.md")),
   acknowledgements = readLines(drake::file_in("./paper/acknowledgements.md")),
   abs_wordcount = count_words(drake::file_in("paper/abstract.md")),
-  msc_wordcount = count_words(drake::file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:85),
+  msc_wordcount = count_words(drake::file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:89),
   render_pdf(drake::knitr_in('paper/supp-info.Rmd'), drake::file_out('paper/supp-info.pdf'), clean_md = FALSE),
   render_pdf(drake::knitr_in('paper/manuscript.Rmd'), drake::file_out('paper/manuscript.pdf'), clean_md = FALSE)
   )

### 2018-12-09 paper/manuscript.Rmd
Small fixes to questions
Fix figure 2

@@
 
-* Polish discussion. 
+* Polish discussion, will appreciate input here. 
+* Polish supp. info.
 * Spell-check everything & check that reference list is correct.
@@
 In all plots, error bars correspond to ± the standard error (SE)."}
-# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
+# fig_random_slopes <- plot_random_slopes(facilitation_plot_df)
 # fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)

### 2018-12-09 code/coefficient_averages.R

@@ -59,7 +59,8 @@ plot_coefficient_averages <- function(coefficient_averages, variable_importance)
       abs_larger <-  function(x,y) {if (abs(x) < abs(y)) return(y) ; x}
       
       line_offset <- 0.25
-      x %>%
+      p <- x %>%
+        dplyr::filter(metric == this_metric) %>%
         dplyr::rowwise() %>%
         dplyr::mutate(label_y = dplyr::if_else(abs(estimate_mid) < 0.25, 
                                                abs_larger(mean_estimate_quantile_025, mean_estimate_quantile_975),
@@ -103,8 +104,8 @@ plot_coefficient_averages <- function(coefficient_averages, variable_importance)
                   # size = 2) +
         pub_theme() +
         labs(y = "effect size") +
-        coord_flip(clip = "off") +
         scale_x_discrete(expand = c(0,0)) +
+        coord_flip(clip = "off") +
         theme(legend.position = "none", 
               axis.title.y = element_blank(), 
               axis.ticks.y = element_blank(),
@@ -112,6 +113,11 @@ plot_coefficient_averages <- function(coefficient_averages, variable_importance)
               panel.border = element_blank(), 
               axis.line.x = element_line(size = 0.25)) +
         scale_alpha_manual(values = c(0,1))
+      
+      if (this_metric == "quality") {
+        p <- p + scale_y_continuous(limits = c(-0.24, 0.35))
+      }
+      p
     }
     
     dodge_width <- 0

### 2018-12-09 code/get_summary_effects.R
Calculate less stuff?

@@ -13,7 +13,7 @@ get_summary_effects <- function(tidied_fixed){
     dplyr::mutate(quantity = conspecific_abs, 
                   quality = conspecific_abs - heterospecific_abs) %>% 
     dplyr::group_by(scale, fixed_formula, term) %>%
-    dplyr::summarise_at(dplyr::vars(quantity, quality), dplyr::funs(freq_t, parametric_t, median))
+    dplyr::summarise_at(dplyr::vars(quantity, quality), dplyr::funs(parametric_t, median))
 }
 
 # see if the quantiles of a vector cross zero in a parametric way

### 2019-02-23 paper/manuscript.Rmd
Add some feedback in the MSC

@@
 
-* Now using AICc instead of AIC to evaluate models (no change in results)
-* Traits: (*a*) to keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances.
-Also, now (*b*) columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits.
-* The absolute/relative/gain terminology was confusing. Now  I'm modelling open and bagged pollen counts directly, using the bagged as a sort of control.
-* Introduced visit effectiveness instead of the share in the pollen pool as a predictor in the model.
-Turns out to be a better predictor and also incorporates quantitative visitation data which was missing from the previous models.
-* Now I use a PCA of the explanatory variables to understand different plant strategies and give a deeper treatment to the facilitation/competition question.
-
 ## Todo
@@
 
-* Journal?
+* Journal? --- *Hugo says PNAS, Proceedings B and Science. No answer from other coauthors*
 * I think the story is still a bit disperse.
@@
 So far the central topic is scaling up of competition to the community level.
-* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}?
+--- *No particular feedback received*
+* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}? --- *No particicular feedback received*
 * Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private?
@@
 Animal pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011].
-Alongside the direct mutualisms between plants and their pollinators, \R{ref-needed-possitive-loops} the support to biodiversity can be achieved as a result of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plant [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008].
+<!-- FDO: Asked coauthors for a reference for the following statement but no-one provided. Therefore removing -->
+Alongside the direct mutualisms between plants and their pollinators, the support to biodiversity can be achieved as a result of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plant [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008].
 In sum, inter-species facilitation is able to promote species coexistence because it is able to offset the effects of direct competition for resources [@stachowicz_mutualism_2001]. 
@@
 If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented could be higher than when floral visits are allowed.
-In contrast, the opposite pattern may indicate that plants benefit from animal-mediated pollination---even a small difference between outcross and self-pollen may be important to plant fitness \R{ref2}[@ref].
+In contrast, the opposite pattern may indicate that plants benefit from animal-mediated pollination---even a small difference between outcross and self-pollen may be important to plant fitness. 
+<!-- FDO: Asked coauthors for a reference for the previous statement and no-one provided feedback, so removing it -->
 This is particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy).

### 2019-02-24 paper/manuscript.Rmd
Use lightweight version of latex and install required packages independently

@@
   - \usepackage{xr}
+  - \usepackage[utf8]{inputenc}
   - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
@@
 However, in the majority of cases, the difference is not large enough to be statistically significant at the 0.05 level.
-In all plots, error bars correspond to ± the standard error (SE)."}
+In all plots, error bars correspond to $\\pm$ the standard error (SE)."}
 # fig_random_slopes <- plot_random_slopes(facilitation_plot_df)
@@
 (c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and quality of pollination.
-The plot shows the model averaged mean effect (± SE) of the four analysed ecological variables in the quantity and quality of pollination."}
+The plot shows the model averaged mean effect ($\\pm$ SE) of the four analysed ecological variables in the quantity and quality of pollination."}
 height1 <- 1

### 2019-02-24 code/compile_pdf.R

@@ -1,30 +1,32 @@
 render_pdf <- function(rmd_file, output_file, clean_md = FALSE, clean_tex = FALSE, quiet = TRUE){
-  
+
   output_tex <- paste0(tools::file_path_sans_ext(rmd_file), ".tex")
-  rmarkdown::render(rmd_file, 
-                    output_file = output_tex,
-                    output_dir = dirname(rmd_file),
-                    intermediates_dir = dirname(rmd_file),
-                    clean = clean_md,
-                    quiet = quiet)
-  
+  try({
+    rmarkdown::render(rmd_file,
+                      output_file = output_tex,
+                      output_dir = dirname(rmd_file),
+                      intermediates_dir = dirname(rmd_file),
+                      clean = clean_md,
+                      quiet = quiet)
+  })
+
   compile_pdf(output_tex,
               output_file,
               clean = clean_tex)
 }
 
 compile_pdf <- function(file_in, file_out, clean) {
-  
+
   tinytex.output_dir <- getOption("tinytex.output_dir")
   tinytex.engine_args <- getOption("tinytex.engine_args")
   on.exit({
-    options(tinytex.output_dir = tinytex.output_dir, 
+    options(tinytex.output_dir = tinytex.output_dir,
             tinytex.engine_args = tinytex.engine_args)
   })
-  
-  options(tinytex.output_dir = "paper", 
+
+  options(tinytex.output_dir = "paper",
           tinytex.engine_args = "'--output-directory=paper'")
-  
+
   tinytex::latexmk(file_in,
                    pdf_file = file_out,
                    clean = clean)

### 2019-02-25 paper/manuscript.Rmd
add answers to specific questions before and add docker to the changelog

@@
 
+* Now using docker to manage project dependencies. Image is now available on dockerhub efcaguab/pollen-competition
+
 ## Todo
@@
 * Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}? --- *No particicular feedback received*
-* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private?
+* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private? --- *It is OK*
 * In Figure \@ref(fig:fig-trade-off-predictions)a, I determine if the slope is significantly positive or negative by checking whether the standard errors cross 0.
@@
 Should all other error bars in Figure \@ref(fig:fig-trade-off-predictions) be 2 times SE?
+--- *No particular feedback received*
 * What do you think about the quantity/quality discourse now?
@@
 Cause the left is just almost the same as Figure \@ref(fig:fig-average-qual-quant)b, except that it includes models in which the variable was not present and hence "shrinks" the model averaged estimate.
+--- *Daniel advocates for getting rid of quantity/quality and go for conspecific/conspecific proportion*
 * Unsure of whether in Figure \@ref(fig:fig-pca)a, it would be better to display the contribution of each component to total variance instead of the cummulative contribution.
+--- *Add info to left of the figure*
 * I'm not very happy with the way the third hypothesis is described in the intro (\lr{third-hypothesis}). I would appreciate ideas to rephrase it clearly
 * Does the paragraph in \lr{disc-facil-comp} needs more meat? Any suggestions?
-* My background in the topic is limited, would be grateful if you could point me out to key papers that could be used to put some context to the finding of the "flexibility" of plants strategies (paragraph in \lr{strategies})
+* My background in the topic is limited, would be grateful if you could point me out to key papers that could be used to put some context to the finding of the "flexibility" of plants strategies (paragraph in \lr{strategies}) --- *DBS argues that I say that strategies minimise competition but I never show that, only show that strategies change.
+Need to think about that*
 * Part of the discussion before revolved about the fact that degree is commonly used in theoretical models of mutualism to adjust the mutualistic benefit of generalist species.
@@
 You think it should be included?
+--- *DBS says is OK to leave it out*
 

### 2019-02-25 paper/manuscript.Rmd
Add initials for authors Middle names

@@
 title: "The pollination trade-off"
-author: "Fernando Cagua^1^, Hugo Marrero^2^, Jason Tylianakis^1^, Daniel Stouffer^1^"
+author: "Fernando Cagua^1^, Hugo J. Marrero^2^, Jason M. Tylianakis^1^, Daniel B. Stouffer^1^"
 bibliography: phd-bibliography/pollen-competition.bib

### 2019-02-26 paper/manuscript.Rmd
remove some trailing whitespace in manuscript
tinker with the idea of using a PNAS template

@@
   bookdown::pdf_document2:
+    # base_format: rticles::peerj_article
     keep_tex: yes

### 2019-02-27 paper/manuscript.Rmd
Changes to first three paragraphs of intro

@@
 <!-- FDO: Asked coauthors for a reference for the following statement but no-one provided. Therefore removing -->
-Alongside the direct mutualisms between plants and their pollinators, the support to biodiversity can be achieved as a result of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plant [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008].
-In sum, inter-species facilitation is able to promote species coexistence because it is able to offset the effects of direct competition for resources [@stachowicz_mutualism_2001]. 
-What is more, studies that are fundamental to our current knowledge of mutualism predict that the maximum number of coexisting species---effectively an upper limit to biodiversity---is achieved when the number of shared mutualistic partners is maximised in a community [@bastolla_architecture_2009].
-And yet, not every pollinator species in natural communities interacts with every species of plant.
+Alongside the direct mutualisms between plants and their pollinators, biodiversity can be supported as a result of inter-species "facilitation"—the positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008].
+This inter-species facilitation is able to promote species coexistence by offsetting the effects of direct resource competition [@stachowicz_mutualism_2001]. 
+Indeed, studies at the core of our current theoretical knowledge of mutualisms predict that the maximum number of coexisting species is achieved when the number of shared mutualistic partners is maximised in a community [@bastolla_architecture_2009].
 
-One explanation is that sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
-As soon as there are costs, plants start competing for mutualistic partners, even if this competition is not strong enough to produce a net negative effect in fitness. 
-It has been clear for a long time [@robertson_philosophy_1895; both experimentally @lewis_experimental_1961 and theoretically @levin_competition_1970] that when competition is strong enough, it can be detrimental to plants' fitness.
-So much so that competition for pollination has been shown to drive ecological differentiation [for example by driving the evolution of of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000].
-It is less clear, however, how exactly these strategies of differentiation, in turn, modulate the strength of competition for pollinators. 
-<!-- The ecological factors that modulate the strength of competition, andfactors  -->
-<!-- In addition, it has been shown that the strength of competition for pollinator can be modulated by multiple ecological factors factors (like the number of shared pollinators, the plants' relative abundance, visitor fidelity, and traits) [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_effects_1987; @campbell_pollinator_1985].
--->
+However, in natural communities, plants rarely share all available pollinators.
+One explanation is that plants are effectively competing for mutualistic partners because there is a *trade-off* between the benefits gained from maximising the number of mutualistic partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
+It has been clear for a long time [both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970] that when competition for pollination is strong enough, it can be detrimental to plants' fitness.
+In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000]. 
+It is less clear, however, how exactly ecological differentiation, in turn, affect the trade-off between facilitation and competition that is involved in the pollination service.
 
-There are two main mechanisms through which factors of ecological differentiation can affect plant fertilization [@morales_interspecific_2008]. 
-The first mechanism, is by reducing the number of conspecific pollen grains on stigmas. 
-For example, plants with distinctively attractive flowers might reduce the number of visits---and hence the amount of conspecific pollen deposited by animals---for those less attractive [@yang_pollinator_2011].
+There are two main mechanisms through which competition for pollinators can affect plant fertilization [@morales_interspecific_2008]. 
+The first, is by reducing the number of conspecific pollen grains on stigmas. 
+For example, plants with distinctively attractive flowers might reduce the number of visits---and hence the amount of *conspecific* pollen deposited by animals---to those less attractive neighbouring plants [@yang_pollinator_2011].
 This can be seen as the *quantity* of the pollination service.

### 2019-02-28 paper/manuscript.Rmd
edit third and fourth paragraph of the intro, still need to find a better way to connect parargraphs 4 and 5

@@
 There are two main mechanisms through which competition for pollinators can affect plant fertilization [@morales_interspecific_2008]. 
-The first, is by reducing the number of conspecific pollen grains on stigmas. 
-For example, plants with distinctively attractive flowers might reduce the number of visits---and hence the amount of *conspecific* pollen deposited by animals---to those less attractive neighbouring plants [@yang_pollinator_2011].
-This can be seen as the *quantity* of the pollination service.
-More subtly, when plants employ reproductive strategies that imply sharing pollination partners, even receiving a visit might not translate into fertilization.
-This so because a focal plant might receive pollen from a different species, or conversely, pollen from the focal plant might be lost to different species. 
-This second mechanism, is called interspecific pollen transfer [@campbell_mechanism_1985]. 
-Generally speaking, the higher the proportion of conspecific relative to heterospecific pollen the higher the *quality* of the pollination service. 
-With few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the quantity and quality of pollination---and its relationship to competition vs.
-facilitation in pollination systems---is based mostly on studies of two plant species.
-However, competitive interactions between species pairs do not occur in isolation.
+The first is intraspecific pollen transfer. 
+This happens, for example, when plants with distinctively attractive flowers might reduce the number of visits---and hence the amount of *conspecific pollen* deposited by animals---to those less attractive neighbouring plants [@yang_pollinator_2011].
+The second is intraspecific pollen transfer and occurs when plants share pollination partners. 
+In that case, even receiving a visit might not necessarly translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or pollen from the focal plant might be lost to different species.
+Generally speaking, the higher the amount of conspecific pollen (both in absulute terms and relative to heterospecific pollen) the better the pollination service received by the focal plant.
+These two mechanisms of competition, by definition, occur at the community scale. 
+However, with few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the deposition of conspecific and heterospecific pollen---and its relationship to competition vs.
+facilitation in pollination systems---is based on studies of two plant species.
 
-Instead, co-flowering plants often occur in communities in which the factors that determine differentiation are tightly intertwined,  operate simultaneously, and may lead to phenomena not observed at smaller scales [@flanagan_effects_2011].
-For instance, recent empirical evidence suggests that plants with flowering traits that are original relative to others in the community have generally fewer interaction partners [@coux_linking_2016].
-This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them; in contrast, a species that interacts with a large number of species does so comparatively weakly.
-If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with original traits and an increase in species with a large number of interaction partners [@gibson_can_2012].
-Alternatively, based on evidence from two/three species systems, it might also be the case that flower/pollen density is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
-Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both the pollen being transported by pollinators and their visits compared to other species.
-In this case, a potential reduction in the quantity of pollination (the amount of conspecific pollen received) could be compensated by an increase in the quality of pollination (the amount of conspecific relative to heterospecific pollen received).
+At the community scale the factors that determine the patterns of conspecific and heterospecific pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
+For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016].
+This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly (TODO: ref needed).
+If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase in species with a large number of interaction partners [@gibson_can_2012].
+Alternatively, it might also be the case that density (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
+Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both visits and pollinator "real state".
+In this case, a potential reduction the absolute amount of conspecific pollen received could be compensated by an increase amount relative to heterospecific pollen. 
 <!-- To complicate things more, autonomous self-pollination can also influence a plant sensitivity to competition for pollination because it can ensure reproduction even in the absence of outcross pollen [@kalisz_benefits_2003].
@@
 <!-- Altogether, multiple, potentially correlated, factors may act simultaneously.  -->
-The effect and relative importance that the factors of ecological differentiation in the plants' communities play on the pollination service has not yet been empirically evaluated in natural communities.
+All these factors (generalim, traits, abundance, visitation) The relative importance of these factors, which together define a sort of competition niche, has not yet been empirically evaluated in natural plantcommunities.
 

### 2019-03-01 paper/manuscript.Rmd
finished with edits to the Introduction, dealt a bit with Issue #56

@@
 
-* Now using docker to manage project dependencies. Image is now available on dockerhub efcaguab/pollen-competition
+* Now using `docker` to manage project dependencies. Image is now available on dockerhub efcaguab/pollen-competition
+* Removing *quantity* and *quality* of pollination in favour of the plain metrics of *conspecific* and *heterospecific* pollen deposition. 
+* Rewording the plant strategies idea as it was confussing.
+Now The combination of ecological variables (number shared pol., abundance, visitation patterns, and traits) define a species *realised niche* (this was previoulsy called the plant strategy).
+Plants that can have very different realised niches across different communities have a *flexible strategy* (this was previously called strategy as well).
+* Format taylored for submission to Ecology Letters
 
@@
 <!-- Altogether, multiple, potentially correlated, factors may act simultaneously.  -->
-All these factors (generalim, traits, abundance, visitation) The relative importance of these factors, which together define a sort of competition niche, has not yet been empirically evaluated in natural plantcommunities.
+ <!-- factors (number of shared pollinators, traits, abundance, visitation patterns) -->
+Altogether, it is clear that some ecological factors can influence pollen deposition. 
+<!-- We can think on , hence, together may carry enough information to roughly define the species *realised niche* in the context of competition for pollination.  -->
+However, the intertwined nature of these factors makes it hard to determine wether they favour or hinder the pollination service at the community level. 
+Moreover, their relative importance has not yet been empirically evaluated in natural plant communities.
 
-Here, we investigate competition for pollination at the community scale using comprehensive empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
-First, we need to understand the extent to which the outcome of animal-mediated pollination is facilitation or competition. 
-If facilitation is the primary outcome we would expect (*i*) an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the heterospecific pollen [@tur_evaluating_2016] and (*ii*) a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than that due to self-pollination.
-Second, we investigate the relative contribution that four ecological factors, that together describe the strategies of ecological differentiation, have on competition for pollination. 
-We hypothesize that competition for pollination at the community level should increase as the number of shared pollination partners a plant has increases.
-However, other factors like the plant's functional originality, its relative abundance, and the visit effectiveness, should have the potential to compensate this increase in competition by improving either the quality or the quality of pollination.
-Third, and finally, we explore how community context influences the way plants use these factors to minimise competition. 
-\R{third-hypothesis}Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and are hence is likely to be defined by the local context.
-If plant species adopt comparable roles across different communities, we should expect plant strategies to be more similar within species than across species in the study. 
-On the contrary, if species role is flexible, we should expect plants to be able to adopt different strategies in each community such that competition is minimised depending on the context.
+Here, we investigate competition for pollination at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
+**First**, we estimate the extent to which the net outcome of plants sharing polinators is facilitation or competition. 
+If facilitation is the primary outcome, we could expect two tings. 
+On the one hand, we could expect an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the amount of heterospecific pollen [@tur_evaluating_2016]. 
+The higher the deposition of conspecific pollen relative to heterospecific, the larger the slope of that relationship.
+On the other, we could also expect a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than is deposited due to self-pollination. 
+**Second**, we investigate the relative contribution that four ecological factors have on competition for pollination. 
+These factors, in the specific context of pollination, may carry enough information to roughly define a species *realised niche* in their community. 
+Sepecifically, we hypothesize that competition (measured as absolute and relative conspecific pollen deposition) should increase for plants that share many pollination partners.
+However, we also hypothesize that other factors like the plant's functional originality, its relative abundance, and the visit effectiveness should have the potential to compensate for this increase in competition by improving either the quality or the quality of pollination.
+**Third**, we examine how community context influences the way plants use these factors to minimise competition. 
+Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict niche to be influenced by the local context. 
+If plant strategy is not flexible across communities, we could expect niches to be more similar within species than across species in the study. 
+On the contrary, if a species' strategy is flexible, we should expect plants to be able to occupy different niches in each community such that competition could be minimised regardless of the context.
 

### 2019-03-01 paper/manuscript.Rmd
minor changes to methods and a couple edits in intro

@@
 * Format taylored for submission to Ecology Letters
+* Sticking to past tense throughout the methods
 
@@
 In this case, a potential reduction the absolute amount of conspecific pollen received could be compensated by an increase amount relative to heterospecific pollen. 
-<!-- To complicate things more, autonomous self-pollination can also influence a plant sensitivity to competition for pollination because it can ensure reproduction even in the absence of outcross pollen [@kalisz_benefits_2003].
--->
-<!-- Altogether, multiple, potentially correlated, factors may act simultaneously.  -->
- <!-- factors (number of shared pollinators, traits, abundance, visitation patterns) -->
 Altogether, it is clear that some ecological factors can influence pollen deposition. 
-<!-- We can think on , hence, together may carry enough information to roughly define the species *realised niche* in the context of competition for pollination.  -->
 However, the intertwined nature of these factors makes it hard to determine wether they favour or hinder the pollination service at the community level. 
@@
 On the other, we could also expect a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than is deposited due to self-pollination. 
-**Second**, we investigate the relative contribution that four ecological factors have on competition for pollination. 
+**Second**, we investigate the relative contribution that four ecological factors have on the pollination service. 
 These factors, in the specific context of pollination, may carry enough information to roughly define a species *realised niche* in their community. 
 Sepecifically, we hypothesize that competition (measured as absolute and relative conspecific pollen deposition) should increase for plants that share many pollination partners.
-However, we also hypothesize that other factors like the plant's functional originality, its relative abundance, and the visit effectiveness should have the potential to compensate for this increase in competition by improving either the quality or the quality of pollination.
+However, we also hypothesize that other factors like the plant's functional originality, its relative abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
 **Third**, we examine how community context influences the way plants use these factors to minimise competition. 
 Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict niche to be influenced by the local context. 
-If plant strategy is not flexible across communities, we could expect niches to be more similar within species than across species in the study. 
+If plant strategy is not flexible across communities (TODO: ref needed), we could expect niches to be more similar within species than across species in the study. 
 On the contrary, if a species' strategy is flexible, we should expect plants to be able to occupy different niches in each community such that competition could be minimised regardless of the context.
@@
 
-We collected data from eleven co-flowering plant communities and their pollinators in three locations, each in a distinct region of the Argentinian Pampas. 
+We collected data from eleven co-flowering plant communities and their pollinators in three locations in the Argentinian Pampas. 
 These locations are distributed across a precipitation gradient with a humid temperate climate in the eastern Flooding Pampas and becoming drier as one moves inland and westward towards the Pampean Grasslands.
-Annual mean temperatures range between 14.8 and $44.9^\circ$C. 
-In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where due to the lack of available sites, we were only able to sample one restored fragment.
+This precipitation gradient generatesd a natural gradient of network architecture which allowed us to examine the generality of our findings. 
+In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where we were only able to sample one restored fragment due to the lack of available sites.
 
@@
 
-Our first objective is to identify whether, at the community level, the net outcome of animal-mediated pollination is facilitation or competition. 
-The first line of evidence can be found in the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
-This is so because heterospecific pollen can be seen as a cost that plants must pay for receiving conspecific pollen from shared pollinators. 
+Our first objective was to identify whether the outcome of plants sharing polinators, at the community level, is facilitation or competition. 
+The first line of evidence can be found via the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
+This is because heterospecific pollen can be seen as an unavoidable cost that plants must pay for receiving conspecific pollen from shared pollinators. 
 A negative relationship (when shared pollinators increase heterospecific pollen loads and decrease conspecific loads) may indicate that competition for pollination is strong. 
-This negative relationship could arise, for example, when another, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
-In contrast, a positive relationship is what should be observed if facilitation is the dominant outcome. 
-For example, when the abundance of shared pollinators is positively influenced by floral resources and these positive effects ripple through the mutualistic network in a chain of positive feedback loops [@liao_presence_2011].
+This negative relationship could arise, for example, when another, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
+In contrast, a positive relationship is what would be observed when facilitation is the dominant outcome. 
+For example, when the abundance of shared pollinators is positively influenced by floral resources, these positive effects ripple through the mutualistic network in a chain of positive feedback loops [@liao_presence_2011].
 
-The second line of evidence could be obtained by examining the difference between the amount conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination. 
-Self-pollination can be favourable to plant reproduction when competition for pollination is strong because it provides insurance against a poor pollination service [@kalisz_benefits_2003]. 
+The second line of evidence caN be obtained by examining the difference between the amount of conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination. 
+Self-pollination can be favourable to plant reproduction when competition for pollination is strong because it provides insurance against poor pollination service [@kalisz_benefits_2003]. 
 If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented could be higher than when floral visits are allowed.

### 2019-03-01 paper/manuscript.Rmd
continue edits through first two pragraphs of methods

@@
 Feel free to come back here after you've read the manuscript. Thanks!
+
+* Minor point: DBS thinks that normally one would use the technical word and then put the definition in parenthesis.
+In a previous revision I got from JMT that it's better to lead with the concept and then add the jargon last.
+Examples: *"...due to a temporary separation in the maturation of sexes (dichogamy)"*, *"...common insect-pollinated (entomophilous) species"*.
 
@@
 
-The second line of evidence caN be obtained by examining the difference between the amount of conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination. 
+The second line of evidence can be obtained by examining the difference between the amount of conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination. 
 Self-pollination can be favourable to plant reproduction when competition for pollination is strong because it provides insurance against poor pollination service [@kalisz_benefits_2003]. 
 If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented could be higher than when floral visits are allowed.
-In contrast, the opposite pattern may indicate that plants benefit from animal-mediated pollination---even a small difference between outcross and self-pollen may be important to plant fitness. 
-<!-- FDO: Asked coauthors for a reference for the previous statement and no-one provided feedback, so removing it -->
-This is particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy).
+In contrast, the opposite pattern may indicate that plants benefit from having pollen delivered directly to the stigma by animals. 
+We do not specifically test the effect of pollen viability or the extent to which self-pollen vs.
+pollen from a conspecific may differ in their value for fertilization which can be important factors (TODO: ref needed).
+However, it is reasonable to expect that the difference between outcross and self-pollen may be generally relevant and particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy) (TODO: ref needed).
 
@@
 In each of the studied communities, we quantified pollen deposition in a subset of plant species between December 2010 and February 2011. 
-This subset comprised of between three and nine common insect-pollinated (entomophilous) species that were flowering during the sampling period (see Figure \@ref(fig:fig-trade-off-predictions)a). 
+This subset comprised between three and nine common insect-pollinated (entomophilous) plant species that were flowering during the sampling period (see Figure \@ref(fig:fig-trade-off-predictions)a). 
 We chose plant species such that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
@@
 Two days after inflorescence, we counted the pollen grains in the remaining flowers' pistils, classified them between conspecific and heterospecific pollen, and calculated the number of pollen grains per stigma in each flower.
-More details about the study sites and data collection and laboratory protocols can be found in @marrero_agricultural_2016.
+More details about the study sites, data collection, and laboratory protocols can be found in @marrero_agricultural_2016.
 

### 2019-03-04 paper/manuscript.Rmd
Correct models of facilitation. Now specifying that we're using one model for the whole study ( I was already doing that but didn't updated the paper). Also including the number of stigma as an offset which allows to correctly use a Poisson distribution

@@
 
-To evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution in each of our communities [@tur_evaluating_2016].
-In these models, the number conspecific pollen grains per stigma was the response variable and the number of heterospecific grains the predictor. 
+To evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution [@tur_evaluating_2016]. 
+In this model, the number conspecific pollen grains per stigma was the response variable and the number of heterospecific grains the predictor (the number of stigmas sampled from the flower was added as an offset term).
 The slope and intercept of this relationship were allowed to differ between plant species, which were modelled as a random effect. 
-Models were fitted using the function `lmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]. 
+Models were fitted using the function `glmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]. 
 To compare the conspecific pollen deposited with and without animal-mediated pollination, we performed a Mann-Withney U test of the number of conspecific pollen grains per stigma between un-bagged and bagged flowers for each of the studied species in a community.
@@
   fig_random_slopes[[2]], 
-  ncol = 2, 
+  # ncol = 2, 
   align = "h", 

### 2019-03-04 code/facilitation.R

@@ -3,21 +3,25 @@
 model_facilitation <- function(dep_frame){
   dep_frame %>%
     dplyr::filter(treatment == "open") %>%
-    dplyr::select(plant, plant_name, site_name, pollen_density, pollen_category) %>%
-    tidyr::spread(key = "pollen_category", value = "pollen_density") %>% 
-    dplyr::mutate(conspecific = ceiling(conspecific)) %>%
-    lme4::glmer(conspecific ~ heterospecific + (heterospecific | plant_name : site_name), family = "poisson", data = .)
+    dplyr::select(plant, plant_name, site_name, n_grains, n_stigma, pollen_category) %>%
+    tidyr::spread(key = "pollen_category", value = "n_grains") %>%
+    # dplyr::mutate(conspecific = ceiling(conspecific)) %>%
+    lme4::glmer(conspecific ~
+                  heterospecific + (heterospecific | plant_name : site_name),
+                family = "poisson",
+                offset = log(n_stigma),
+                data = .)
 }
 
-# extract the random effects from facilitation models 
+# extract the random effects from facilitation models
 # also gets the error using the conditional variance stored as an attribute in the model
 extract_random_effects <- function(facilitation_models){
   facilitation_models %>%
-    coef() %>% 
-    extract2(1) %>% 
+    coef() %>%
+    extract2(1) %>%
     tibble::rownames_to_column() %>%
     dplyr::mutate(error = get_error_random_effects(facilitation_models)) %>%
-    tidyr::separate("rowname", into = c("plant_name", "site_name"), sep = ":", remove = F) 
+    tidyr::separate("rowname", into = c("plant_name", "site_name"), sep = ":", remove = F)
 }
 
 # helpef function to extract the error from the model
@@ -27,7 +31,7 @@ get_error_random_effects <- function(x) {
     extract2(1) %>%
     attr("postVar") %>%
     extract(2,2,) %>%
-    sqrt() 
+    sqrt()
 }
 
 get_facilitation_plot_df <- function(dep_frame, facilitation_random_effects){
@@ -35,145 +39,145 @@ get_facilitation_plot_df <- function(dep_frame, facilitation_random_effects){
     dplyr::filter(treatment == "open") %>%
     dplyr::group_by(plant_name) %>%
     dplyr::summarise(n = dplyr::n_distinct(plant))
-  
+
   facilitation_random_effects %>%
     dplyr::full_join(n_obs) %>%
[…]

### 2019-03-04 code/make_fig_con_hetero_gain.R

@@ -1,35 +1,35 @@
 make_fig_con_hetero_gain <- function(tidied_fixed, model_linear_fits, model_formula_ranking, model_linear_fits_species) {
   require(ggplot2)
-  
+
   model_weights <- model_formula_ranking$aggregated %>%
     # dplyr::filter(scale == "community") %>%
     # dplyr::group_by(pollen_category) %>%
-    dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
+    dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median),
                   weight = get_weights(likelyhood)) %>%
     dplyr::select(fixed_formula, weight)
-  
+
   points_sp <- model_linear_fits_species %>%
     dplyr::filter(var_trans == "log",
-                  scale == "community") %>% 
-  #   tidyr::spread(data = ., key = sma_parameter, value = value) %>% 
-    dplyr::inner_join(model_weights, by = "fixed_formula") %>% 
+                  scale == "community") %>%
+  #   tidyr::spread(data = ., key = sma_parameter, value = value) %>%
+    dplyr::inner_join(model_weights, by = "fixed_formula") %>%
     dplyr::group_by(site_name, plant_name, scale, model) %>%
     dplyr::sample_n(size = 1, weight = weight) %>%
     dplyr::group_by() %>%
-    tidyr::gather("con_type", "conspecific", dplyr::contains("conspecific")) 
-  
+    tidyr::gather("con_type", "conspecific", dplyr::contains("conspecific"))
+
   exp_minus_one <- function(x){
     exp(x)-1
   }
-  
+
   points_sp_summarised <- points_sp %>%
     dplyr::group_by(plant_name, site_name, con_type) %>%
-    dplyr::summarise_at(dplyr::vars(dplyr::contains("specific")), 
+    dplyr::summarise_at(dplyr::vars(dplyr::contains("specific")),
                         dplyr::funs(median, quantile_05,quantile_95), na.rm = T) %>%
     dplyr::mutate_if(is.numeric, I) %>%
     dplyr::group_by() %>%
-    dplyr::rename(rel = "con_type") 
-  
+    dplyr::rename(rel = "con_type")
+
   pa <- RColorBrewer::brewer.pal(4, "OrRd")
   major_labs <- c(0,10,100, 1000, 10000)
   minor_labs <- c(0, 5, 10, 50, 100, 500, 1000, 10000)
[…]

### 2019-03-04 paper/manuscript.Rmd
Using a GLMM to compare conspecific pollen in bagged vs unbagged flowers. Close #59

@@
 
-* Now using `docker` to manage project dependencies. Image is now available on dockerhub efcaguab/pollen-competition
+* Now using `docker` to manage project dependencies. Image is now available on dockerhub efcaguab/pollen-competition.
 * Removing *quantity* and *quality* of pollination in favour of the plain metrics of *conspecific* and *heterospecific* pollen deposition. 
 * Rewording the plant strategies idea as it was confussing.
-Now The combination of ecological variables (number shared pol., abundance, visitation patterns, and traits) define a species *realised niche* (this was previoulsy called the plant strategy).
+Now the combination of ecological variables (number shared pol., abundance, visitation patterns, and traits) define a species *realised niche* (this was previoulsy called the plant strategy).
 Plants that can have very different realised niches across different communities have a *flexible strategy* (this was previously called strategy as well).
-* Format taylored for submission to Ecology Letters
-* Sticking to past tense throughout the methods
+* Manuscript formatted for submission to Ecology Letters.
+* Sticking to past tense throughout the methods.
+* GLMM to fit slope of heterospecific-conspecific pollen relationship tests all communities at once (it was a model per community).
+Response variable is the number of grains (it was number of grains per stigma) and the (log) number of stigmas in the flowers has been included as an offset term.
+* Using a similar approach to compare conspecific pollen deposited in open and bagged flowers (I used a series of Mann-Withney U tests before)
 
@@
 A negative relationship (when shared pollinators increase heterospecific pollen loads and decrease conspecific loads) may indicate that competition for pollination is strong. 
-This negative relationship could arise, for example, when another, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
+This negative relationship could arise, for example, when another, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; @lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
 In contrast, a positive relationship is what would be observed when facilitation is the dominant outcome. 
@@
 In this model, the number conspecific pollen grains per stigma was the response variable and the number of heterospecific grains the predictor (the number of stigmas sampled from the flower was added as an offset term).
-The slope and intercept of this relationship were allowed to differ between plant species, which were modelled as a random effect. 
+The slope and intercept of this relationship were allowed to differ between plant species within each community, which were modelled as a random effect. 
 Models were fitted using the function `glmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]. 
-To compare the conspecific pollen deposited with and without animal-mediated pollination, we performed a Mann-Withney U test of the number of conspecific pollen grains per stigma between un-bagged and bagged flowers for each of the studied species in a community.
+To compare the conspecific pollen deposited with and without animal-mediated pollination, we followed the same approach as above. 
+In this case, however, the predictor was the treatment (wether the flower was bagged or unbagged) instead of the number of heterospecific grains.
 

### 2019-03-04 code/make_fig_con_hetero_gain.R

@@ -149,23 +149,28 @@ get_pred_range <- function(tidied_fixed, x, var_trans = "log", scale = "global")
 }
 
 get_con_con_plot_df <- function(dep_frame){
-  a <- dep_frame %>%
+  # Check wether the difference in conspecific pollen between bagged and
+  # unbagged flowers is significant
+  significancy <- dep_frame %>%
+    dplyr::filter(pollen_category == "conspecific") %>%
+    models_open_bagged()
+
+  dep_frame %>%
     dplyr::filter(pollen_category == "conspecific") %>%
     tidyr::complete(site_name, plant_name, treatment) %>%
     dplyr::group_by(site_name, plant_name, treatment) %>%
     dplyr::mutate(n_obs_treatment = n()) %>%
     dplyr::group_by(site_name, plant_name) %>%
-    dplyr::mutate(effect_category = wilcox_open_closed(pollen_density, treatment)) %>%
     dplyr::group_by(site_name, plant_name, treatment) %>%
     dplyr::summarise(mid = mean(pollen_density, na.rm = T),
                      upper = mid + se(pollen_density),
-                     lower = mid - se(pollen_density),
-                     effect_category = effect_category[1]) %>%
+                     lower = mid - se(pollen_density)) %>%
     dplyr::group_by() %>%
     tidyr::gather(variable, value, mid:lower) %>%
     tidyr::unite(temp, treatment, variable, sep = "_") %>%
     tidyr::spread(temp, value) %>%
-    dplyr::filter(!is.na(closed_mid), !is.na(open_mid))
+    dplyr::filter(!is.na(closed_mid), !is.na(open_mid)) %>%
+    dplyr::full_join(significancy)
 
 }
 
@@ -227,12 +232,18 @@ plot_bagged_vs_open_conspecific <- function(con_df){
   list(scatter_plot, bar_plot)
 }
 
-models_open_bagged <- function(df){
-  b <- a %>%
-    dplyr::mutate(pollen_density = round(pollen_density))
 
-  m <- lme4::glmer(pollen_density ~ treatment + (treatment | plant_name : site_name),
-                   data = b,
+# Check wether the difference in conspecific pollen between bagged and
+# unbagged flowers is significant
+models_open_bagged <- function(df){
+
+  # Using a GLMM with the number of grains as a predictor and the treatment
+  # (bagged/unbagged) as the predictor. Allow a random itercept and slope for
+  # each species nested in the community
+  m <- lme4::glmer(n_grains ~
[…]

### 2019-03-04 paper/manuscript.Rmd
Move niche discourse from the last paragraph to the second to last paragraph of the introduction

@@
 In this case, a potential reduction the absolute amount of conspecific pollen received could be compensated by an increase amount relative to heterospecific pollen. 
-Altogether, it is clear that some ecological factors can influence pollen deposition. 
+Altogether, it is clear that some ecological factors can influence pollen deposition and that these factors, in the specific context of pollination, could be used to roughly define a species *realised niche* in their community.
 However, the intertwined nature of these factors makes it hard to determine wether they favour or hinder the pollination service at the community level. 
@@
 **Second**, we investigate the relative contribution that four ecological factors have on the pollination service. 
-These factors, in the specific context of pollination, may carry enough information to roughly define a species *realised niche* in their community. 
 Sepecifically, we hypothesize that competition (measured as absolute and relative conspecific pollen deposition) should increase for plants that share many pollination partners.

### 2019-03-04 paper/manuscript.Rmd
Further edits on the methods

@@
 
-Our first objective was to identify whether the outcome of plants sharing polinators, at the community level, is facilitation or competition. 
+Our first objective was to identify whether the outcome of plants sharing polinators at the community level is facilitation or competition. 
 The first line of evidence can be found via the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
@@
 In contrast, the opposite pattern may indicate that plants benefit from having pollen delivered directly to the stigma by animals. 
-We do not specifically test the effect of pollen viability or the extent to which self-pollen vs.
+We did not specifically test the effect of pollen viability or the extent to which self-pollen vs.
 pollen from a conspecific may differ in their value for fertilization which can be important factors (TODO: ref needed).
@@
 
-## Effect of plant strategies in the pollination service
+## Ecological constraints the pollination service
 
-Our second objective is to investigate the relative contribution that different factors that describe the plants' strategies to minimise competition have on the pollination service. 
-Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them (see Data Analysis section below for more details), and (*iv*) the plants functional originality.
-Here, we define visit effectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
+Our second objective was to investigate the relative contribution of different factors that describe the plant competition for pollination niche to the pollination service. 
+Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plants abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them (see *Data Analysis* section below for more details), and (*iv*) the plants functional originality (add ref).
+<!-- Here, we define visit effectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
+-->
 
@@
 
-To obtain the number of shared pollinators for each species (*i*), we collected data to construct qualitative and quantitative pollination networks. 
+To obtain the number of shared pollinators for each species, we collected data to construct qualitative and quantitative pollination networks. 
 Qualitative networks were constructed based on two-hour observations of floral visits in each fragment. 
-Quantitative networks were constructed using two 50 m randomly located transects in each transect. 
+Quantitative networks were constructed using two 50 m randomly located transects in each fragment. 
 We counted and collected all floral visitors found in a 2 m wide strip while walking at a pace of 10 m per minute [@marrero_effect_2014; @memmott_structure_1999]. 
 We visited the transects each month between November 2010 and March 2011. 
-To obtain plant abundance (*ii*), we counted all units of floral attraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
-To estimate visit effectiveness (*iii*), in addition to the visitation networks we need to construct pollen transfer networks. 
-To construct the transfer networks we examined the pollen loads present on the collected floral visitors [@marrero_exotic_2017]. 
-When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible, and to pollen complexes when it was not. 
+To obtain plant abundance, we counted all units of floral attraction found during an independent sampling of the transects used to construct the quantitative visitation networks. 
+To estimate visit effectiveness we need to construct pollen transfer networks in addition to the visitation networks. 
+To construct the transfer networks, we examined the pollen loads present on the floral visitors collected [@marrero_exotic_2017]. 
+When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level when possible and to pollen complexes when it was not. 
 When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
-Finally, We also recorded morphological traits (*iv*) that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region.
+Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region.
+
 More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014 and 2017).
@@
 
-We investigate the impact of the ecological strategies on the pollination services using two metrics: the quantity and the quality of pollination. 
+We investigated the impact of the ecological strategies on the pollination services using two metrics: the quantity and the quality of pollination. 
 Here we define the quality of pollination as the amount of conspecific pollen and the quality of pollination as the amount of conspecific pollen *relative* to heterospecific pollen. 

### 2019-03-04 paper/manuscript.Rmd
finish off edits for subsection 2 of methods

@@
 When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
-Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region.
-
+Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region.
+We used those traits because they were the only ones available... (TODO: Add a better justification for the traits used)
 More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014 and 2017).
@@
 
-We investigated the impact of the ecological strategies on the pollination services using two metrics: the quantity and the quality of pollination. 
-Here we define the quality of pollination as the amount of conspecific pollen and the quality of pollination as the amount of conspecific pollen *relative* to heterospecific pollen. 
-To construct these metrics we use two sets of linear mixed models (LMM) in which the response variables are the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination.
-In general, using LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) offered better results than a GLMM with Poisson (or quasipoisson) error structure.
+We investigated the impact of the ecological factors on pollination services.
+Generally speaking, the more conspecific pollen deposited in stigmas, both absolutely and relative to heterospecific pollen, the better the pollination service. 
+Specifically, we used two sets of linear mixed models (LMM) in which the response variables are the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination.
+In general, using LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) offered better fit than a GLMM with Poisson (or quasipoisson) error structure.
 Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].
 
-Because the amount of deposited pollen can vary widely across species, and potentially also across communities, we evaluated two possible structures for the random effects: one that includes a random intercept for plant species, and one that treats species across different communities independently.
+Because the amount of deposited pollen can vary widely across species, and potentially also across communities, we evaluated two possible structures for the random effects: one that includes a random intercept for plant species, and one that treats measures from species across different communities as independent.
 We selected the best random structure by comparing the median Akaike Information Criterion for small samples (AICc).
@@
 As predictors in the models, we included the four ecological variables described above. 
-Specifically, we calculated the number of shared pollinators for each plant species (*i*) by pooling data from the qualitative and quantitative pollination networks. 
-This variable is strongly correlated to the number of animal species a plant interacts with (the species degree). 
-To calculate the plants' relative abundance in their community (*ii*), we simply aggregated floral counts for each species. 
-We then calculated the mean visit effectiveness (*iii*). 
-As explained before, we define the effectiveness of a visit by pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
-Because the number of interacting species (and therefore the number of shared pollinators), floral abundance, visitation, and pollen production roughly followed a power-law distribution, we log-transformed these three predictors before including them in the model.
+Specifically, we calculated the number of shared pollinators for each plant species by pooling data from the qualitative and quantitative pollination networks. 
+<!-- This variable is strongly correlated to the number of animal species a plant interacts with (the species degree).  -->
+To calculate the plants' relative abundance in their community, we simply aggregated floral counts for each species. 
+We then calculated the mean visit effectiveness. 
+We define the effectiveness of a visit by pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
+Because the number of shared pollinators, floral abundance, visitation, and pollen production roughly followed a power-law distribution, we log-transformed these three predictors before including them in the model.
 
-Finally, functional originality (*iv*) is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016].
-As phenology has been shown to be a key mechanism of niche differentiation among plants, we also included the plant abundance in each of the survey months (November to March) as an additional trait in our analysis.
-This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits. 
-However, because floral counts across months are not independent, we assigned them a weight of 1/5 such that phenology has an equal weight as other traits. 
+Finally, functional originality is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016].
+<!-- As phenology has been shown to be a key mechanism of niche differentiation among plants, we also  -->
+To include phenology we treated plant abundance in each of the survey months (November to March) as a "trait" in our analysis. 
+<!-- This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits.  -->
+Then we assigned the abundances a weight of 1/5 compared to other functional traits, this accounted for the non-independence of floral counts across months and effectively weights phenology equally to other traits.
 We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
@@
 
-To estimate the coefficients and to perform model selection and the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with one hundred replicates. 
+To estimate the coefficients and to perform model selection and quantify the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with one hundred replicates.
 First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc (relative to the most likely model) for each bootstrap sample.
 As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our variables proportional to the likelihood of its candidate model.
-We "shrank" the estimates coefficient of potentially unimportant variables by setting its estimate to 0 when the variable was not included in the model. 
-Finally, we used these distributions of the model coefficients to estimate their impact on the quantity and quality of pollination. 
-For the quantity of pollination, we simply calculated the mean value of a sample of the conspecific pollen loads. 
-For the quality of pollination, we calculated the mean difference between a sample of the distribution of the effects of conspecific pollen and a sample of those of heterospecific pollen gain.
+We "shrank" the estimated coefficient of potentially unimportant variables by setting their estimate to 0 when the variable was not included in the model. 
+Finally, we used these distributions of the model coefficients to estimate their mean impact on the pollination service (in terms of absoulte and relative conspecific pollen deposition). 
 Again, here we used bootstrap resampling to estimate the uncertainty around these means.

### 2019-03-04 paper/manuscript.Rmd
make figure 2 one-column(ed). Issue #52

@@
 
-```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
+```{r fig-average-qual-quant, fig.height= 2.29*2, fig.width=6.5/3*2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
 (a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
@@
 height2 <- 1.29
-# pdf(width = 3.25 * 2, height = sum(c(height1, height2)))
+# pdf(width = 3.25 * 2 / 3 * 2, height = sum(c(height1, height2))*2)
 # fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
@@
 
-left <- cowplot::plot_grid(
+cowplot::plot_grid(
   left_top, 
+  fig_coefficient_averages,
   left_bottom, 
   ncol = 1, 
-  rel_heights = c(height1, height2)
+  rel_heights = c(height1, height1 + height2, height2)
 )
 
-cowplot::plot_grid(
-  left,
-  fig_coefficient_averages, 
-  ncol = 2,
-  rel_widths = c(sum(c(width_coef_1, width_coef_2)), width_imp)
-)
 # dev.off()

### 2019-03-04 paper/manuscript.Rmd
finish edits to methods

@@
 **Third**, we examine how community context influences the way plants use these factors to minimise competition. 
-Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict niche to be influenced by the local context. 
+Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict the competition for pollination niche to be influenced by the local context.
 If plant strategy is not flexible across communities (TODO: ref needed), we could expect niches to be more similar within species than across species in the study. 
@@
 
-Our last objective is to tease apart the strategies that plants might use to reduce competition and, importantly, how the community context influences these strategies. 
-If community context plays a relatively small role, we should expect plants to adopt similar strategies across different communities. 
-Alternatively, if the community plays a large role, we should be able to observe differences in the strategy a plant species across communities. 
-We first use a principal component analysis (PCA) of the four ecological variables. 
-We define the species strategy in a community as its coordinates in PCA space. 
-For each species that was present in two or more communities, we then calculate (*i*) the median distance between the strategies that the species uses different communities, and (*ii*) the area of the convex hull defined by these points in the first two principal components.
-We then compare these two metrics to those obtained with 99 Monte Carlo randomizations in which we replace the strategy of the focal plant species by one of another species in the dataset.
+Our last objective was to tease apart the plant strategies that might reduce competition and, importantly, how the community context influences these strategies. 
+If community context plays a relatively small role or the species strategy is inflexible we would expect plants of the same species to fill similar competition for pollination niches across different communities.
+Alternatively, if the community plays a large role and plants sttrategies are flexible, we should be able to observe differences in the niche a plant species occupies across communities. 
+First, we used a principal component analysis (PCA) of the four ecological variables. 
+We scaled variables across the whole study to ensure that the PCA space does not change acording to the species present in each community. 
+We define a species' niche in a community as its coordinates in PCA space. 
+For each species that was present in two or more communities, we then calculated (*i*) the median distance between the strategies that the species uses in different communities and (*ii*) the area of the convex hull defined by these points in the first two principal components (only for species present in three or more communities).
+We then compared the magnitude of these two metrics to those obtained with 99 Monte Carlo randomizations in which we replaced the strategy of the focal plant species by that of another randomly selected species in the dataset.
 

### 2019-03-04 code/pca.R

@@ -210,7 +210,8 @@ get_permanova <- function(x, col){
     dplyr::group_by()
 }
 
-plot_permanova_dist <- function(permanova_plant_distances, permanova_site_distances){
+plot_permanova_dist <- function(permanova_plant_distances,
+                                permanova_site_distances){
   require(ggplot2)
 
   perma_data <- permanova_plant_distances %>%
@@ -281,6 +282,7 @@ plot_permanova_dist <- function(permanova_plant_distances, permanova_site_distan
 
 }
 
+# Plot the PCA, scaled globally (across communities)
 plot_pca <- function(pcas, chosen_threshold){
 
   require(ggplot2)

### 2019-03-05 paper/manuscript.Rmd
Plot open vs bagged deposition using standard errors from the model

@@
 Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities.
-Negative slopes indicate that plants experience competition for animal-mediated pollination, while positive slopes indicate that facilitation is the predominant outcome.
+Significantly negative slopes (dark grey) indicate that plants experience competition for animal-mediated pollination, while significantly positive slopes (light grey) indicate that facilitation is the predominant outcome.
 The number of plants analysed for each species is shown within brackets next to the species name.
@@
 (c) Generally, plants also had more pollen deposited in their stigmas when they were open to animal-mediated pollination than when they were closed.
-However, in the majority of cases, the difference is not large enough to be statistically significant at the 0.05 level.
 In all plots, error bars correspond to $\\pm$ the standard error (SE)."}

### 2019-03-05 code/make_fig_con_hetero_gain.R

@@ -151,27 +151,19 @@ get_pred_range <- function(tidied_fixed, x, var_trans = "log", scale = "global")
 get_con_con_plot_df <- function(dep_frame){
   # Check wether the difference in conspecific pollen between bagged and
   # unbagged flowers is significant
-  significancy <- dep_frame %>%
-    dplyr::filter(pollen_category == "conspecific") %>%
-    models_open_bagged()
-
   dep_frame %>%
     dplyr::filter(pollen_category == "conspecific") %>%
-    tidyr::complete(site_name, plant_name, treatment) %>%
-    dplyr::group_by(site_name, plant_name, treatment) %>%
-    dplyr::mutate(n_obs_treatment = n()) %>%
-    dplyr::group_by(site_name, plant_name) %>%
-    dplyr::group_by(site_name, plant_name, treatment) %>%
-    dplyr::summarise(mid = mean(pollen_density, na.rm = T),
-                     upper = mid + se(pollen_density),
-                     lower = mid - se(pollen_density)) %>%
-    dplyr::group_by() %>%
-    tidyr::gather(variable, value, mid:lower) %>%
-    tidyr::unite(temp, treatment, variable, sep = "_") %>%
-    tidyr::spread(temp, value) %>%
-    dplyr::filter(!is.na(closed_mid), !is.na(open_mid)) %>%
-    dplyr::full_join(significancy)
-
+    models_open_bagged() %>%
+    dplyr::mutate(open_mid = open,
+                  open_lower = open - error,
+                  open_upper = open + error,
+                  closed_mid = closed,
+                  closed_lower = closed - error,
+                  closed_upper = closed + error) %>%
+    dplyr::mutate_at(.vars = dplyr::vars(tidyselect::contains("mid"),
+                                         tidyselect::contains("upper"),
+                                         tidyselect::contains("lower")),
+                     exp)
 }
 
 plot_bagged_vs_open_conspecific <- function(con_df){
@@ -205,7 +197,7 @@ plot_bagged_vs_open_conspecific <- function(con_df){
     labs(x = "closed to animal pollination",
          y = "open to animal pollination",
          title = "(c) self- vs. animal-mediated pollination",
-         subtitle = "mean pollen grains per stigma") +
+         subtitle = "conspecific pollen grains") +
     pub_theme() +
     theme(legend.position = "none")
           #axis.line = element_line(size = 0.25))

### 2019-03-05 paper/manuscript.Rmd
Edits in the first subsection of the results. Now species names included in the manuscript are generated dynamically. Human readable lists are obtained using the  package

@@
   dplyr::filter(both)
+
+# Get list of species with both positive and negative slopes
 sp_both_pos_neg <- facilitation_plot_df %>%
-  get_sp_with_both_pos_neg()
+  get_sp_with_both_pos_neg() %>%
+  dplyr::mutate(plant_name = as.character(plant_name)) %>%
+  dplyr::arrange(plant_name) %>%
+  dplyr::mutate(plant_name = stringr::str_extract(plant_name,
+                                                  "[A-Z]\\w+\\s[a-z]\\w+"), 
+                plant_label = paste0("*", plant_name, "*")) 
+# Human readable list of species with both positive and negative slopes
+sp_both_pos_neg_names <- sp_both_pos_neg %$%
+  glue::collapse(plant_label, sep = ", ", last = ", and ")
 
@@
 
-We first examined the relationship between the heterospecific and conspecific pollen deposited on stigmas of a species in a community. 
-We found that the overall slope of the relationship was positive (Table SXX), but a large proportion of plants experienced a negative or no significant relationship between heterospecific and conspecific pollen (`r counts_facilitation_slope$np[1]`% and `r counts_facilitation_slope$np[2]`% respectively; Figure \@ref(fig:fig-trade-off-predictions)a).
-Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species, however, we also observed some important differences *within* species. 
-For instance, `r numbers2words(nrow(sp_both_pos_neg))` of species sampled in multiple communities (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed evidence that facilitation (positive relationships) predominates in some communities while competition (negative relationships) predominates in others.
-Furthermore, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen, plants, in almost all cases, had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
+We first examined the degree of facilitation/competition in natural communities.
+Specifically, we examined the slope of the relationship between the heterospecific and conspecific pollen deposited on stigmas of each species in a community.
+We found that overall neither facilitation nor competition dominates. 
+Indeed, we found that the proportion of species that experienced a significantly positive or neggative relationship between heterospecific and conspecific pollen than neggative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a).
+Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
+For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that facilitation (positive relationships) predominated in some communities while competition (negative relationships) predominated in others.
+Interestingly, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
 
@@
 sp_con_both_pos_neg <- con_con_plot_df %>%
-  get_sp_with_both_pos_neg()
+  get_sp_with_both_pos_neg() %>%
+  dplyr::arrange(plant_name) %>%
+  dplyr::mutate(plant_label = dplyr::if_else(plant_name %in% sp_both_pos_neg$plant_name, shorten_sp_name(plant_name), plant_name),
+                plant_label = paste0("*", plant_label, "*"))
 ```
 
-Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with those that were closed. 
-Here again, we found large differences between plants. 
-Specifically, the difference was non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of plants, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open ($\alpha = 0.05$, Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c).
-Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (*H. incana* and *C. acanthoides*) had both significantly positive and negative differences.
+Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with that of those that were closed. 
+Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers. 
+Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had significantly more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open (the difference was non-signifcant for the remainding `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c).
+Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both significantly positive and negative differences.
 

### 2019-03-05 paper/manuscript.Rmd
some changes to second subsection of the results

@@
 
-## Effect of ecological strategies in the pollination service
+## Ecological constraints in the pollination service
 
@@
 
-We then examined the role that four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality) play on pollen deposition and, by extension, in the quantity and quality of pollination.
-These variables define the strategies that plants use to minimise competition for pollination. 
-We found that the linear mixed models of pollen deposition used had high explanatory power. 
+We then examined the potential roles played by four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality) play in pollen deposition and, by extension, in the quantity and quality of pollination.
+Together these variables can describe the niche that plants might occupy in the context of competition for pollination. 
+We found that our linear mixed models of pollen deposition had high explanatory power. 
 The conditional coefficient of determination R^2^~(c)~ of the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean of `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the bootstrap replicates of the conspecific pollen models and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen [@nakagawa_general_2013].
 A large portion of this explanatory power came from the random effects, particularly for models of conspecific pollen. 
-The marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained for the fixed variables alone, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models.
+The marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained by just the fixed effects, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models.
 
 We tested two structures for the random effects. 
-As determined by the AICc, the random structure best supported by the data was the one that fits an intercept for each species in a community independently (as opposed to an intercept for each species irrespective of the community they belong to).
+As determined by AICc, the random structure best supported by the data was the one that fit an intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community they belong to).
 This structure was best for both the models of conspecific and heterospecific pollen (Table SXX).

### 2019-03-05 paper/supp-info.Rmd
remove first two plots from the supplementary information

@@
 ```{r fig-deposition-gain-log-transformed-or-not, fig.height = 1.8, fig.cap = "Distribution of the stigmatic pollen density for one of the bootstrap replicates used in the model sets.
-When (A) using directly the gain in pollen density and (B) when pollen density is log transormed (for the relative amount of conspecific pollen, density was log-transformed prior to calculating the gain).", eval=T}
+When (A) using directly the gain in pollen density and (B) when pollen density is log transormed (for the relative amount of conspecific pollen, density was log-transformed prior to calculating the gain).", eval=F}
 drake::loadd(fig_pollen_density_diff)
@@
 
-```{r fig-abundance-logtransformed-or-not, fig.height = 1.65, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been log transformed and scaled to have a mean of zero and a standard deviation of one."}
+```{r fig-abundance-logtransformed-or-not, fig.height = 1.65, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been log transformed and scaled to have a mean of zero and a standard deviation of one.", eval = F}
 drake::loadd(fig_abundance)

### 2019-03-05 paper/supp-info.Rmd
Add results tables for facilitation models in the supp info

@@
   - \usepackage{booktabs}
+editor_options: 
+  chunk_output_type: console
 ---
@@
         xtable.size = 'small',
-        booktabs = TRUE)
+        booktabs = TRUE, 
+        knitr.kable.NA = "-")
 ```
@@
   rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
+```
+
+```{r table-facilitation-models-general, results='asis'}
+drake::loadd(facilitation_models)
+
+broom::tidy(facilitation_models, conf.int = F) %>%
+  dplyr::select(-p.value, -group) %>%
+  dplyr::mutate(term = dplyr::case_when(
+    term == "sd_(Intercept).plant_name:site_name" ~ "S.D. random intercept", 
+    term == "sd_heterospecific.plant_name:site_name" ~ "S.D. random slope", 
+    TRUE ~ term
+  )) %>%
+  dplyr::filter(term != "cor_(Intercept).heterospecific.plant_name:site_name") %>%
+  knitr::kable(caption = "Summary of the model of the relationship of heterospecific and conspecific pollen", 
+               digits = 3, 
+               booktabs = T) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::group_rows(index = c("fixed component" = 2, "random component (plant species:community)" = 2)) 
+```
+
+```{r table-facilitation-models-random, results='asis'}
+drake::loadd(facilitation_random_effects)
+drake::loadd(sites)
+
+tbl_frame <- facilitation_random_effects %>%
+ dplyr::inner_join(sites, by = "site_name") %>%
+  dplyr::mutate(site_name = paste(locality_name, 
+                                  land_use, 
+                                  fragment, 
+                                  sep = ' - ')) %>%
+  dplyr::select(plant_name, site_name, heterospecific, error)
+
+# linesep <- tbl_frame %>%
+#   dplyr::mutate(same_species = plant_name == dplyr::lead(plant_name), 
+#                 same_species = dplyr::if_else(is.na(same_species), TRUE, same_species),
+#                 separator = dplyr::if_else(same_species, "", "\\addlinespace")) %$%
+#   separator
+
+tbl_frame %>%
+  knitr::kable("latex", 
+               digits = 4, 
+               col.names = c("species name", "community", "slope", "S.E."), 
+               caption = "asd", 
+               booktabs = T, 
+               linesep = "") %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::column_spec(1, italic = T)
 ```

### 2019-03-05 paper/manuscript.Rmd
Add result tables of open/bagged models in supp info

@@
 * Using a similar approach to compare conspecific pollen deposited in open and bagged flowers (I used a series of Mann-Withney U tests before)
+* Added model results tables in the Supplementary Information
 
@@
 Specifically, we examined the slope of the relationship between the heterospecific and conspecific pollen deposited on stigmas of each species in a community.
-We found that overall neither facilitation nor competition dominates. 
-Indeed, we found that the proportion of species that experienced a significantly positive or neggative relationship between heterospecific and conspecific pollen than neggative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a).
+We found that overall neither facilitation nor competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
+Indeed, we found that the proportion of species that experienced a significantly positive or neggative relationship between heterospecific and conspecific pollen than neggative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)).
 Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
-For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that facilitation (positive relationships) predominated in some communities while competition (negative relationships) predominated in others.
+For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that, the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others.
 Interestingly, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

### 2019-03-05 paper/supp-info.Rmd
Add result tables of open/bagged models in supp info

@@
   dplyr::mutate(term = dplyr::case_when(
+    # term == "(Intercept)" ~ "Intercept",
     term == "sd_(Intercept).plant_name:site_name" ~ "S.D. random intercept", 
@@
   dplyr::filter(term != "cor_(Intercept).heterospecific.plant_name:site_name") %>%
-  knitr::kable(caption = "Summary of the model of the relationship of heterospecific and conspecific pollen", 
+  knitr::kable(caption = "Summary of the model used to analyse the relationship of heterospecific and conspecific pollen", 
                digits = 3,
-               booktabs = T) %>%
+               booktabs = T,
+               col.names = c("predictor", "estimate" ,"S.E.", "z-value")) %>%
   kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::group_rows(index = c("fixed component" = 2, "random component (plant species:community)" = 2)) 
+  kableExtra::group_rows(index = c("fixed component" = 2, 
+                                   "random component (species:community)" = 2)) 
 ```
@@
 
-# linesep <- tbl_frame %>%
-#   dplyr::mutate(same_species = plant_name == dplyr::lead(plant_name), 
-#                 same_species = dplyr::if_else(is.na(same_species), TRUE, same_species),
-#                 separator = dplyr::if_else(same_species, "", "\\addlinespace")) %$%
-#   separator
-
 tbl_frame %>%
@@
                col.names = c("species name", "community", "slope", "S.E."), 
-               caption = "asd", 
+               caption = "Slope of the relationship of heterospecific and conspecific pollen for each species in their community (fixed effect + conditional effect).
+Community names are constructed by location - agricultural/restored - fragment number.",
                booktabs = T, 
@@
   kableExtra::column_spec(1, italic = T)
+```
+
+```{r table-open-bagged-models-general, results = "asis"}
+drake::loadd(open_bagged_model)
+
+broom::tidy(open_bagged_model, conf.int = F) %>%
+  dplyr::select(-p.value, -group) %>%
+  dplyr::mutate(term = dplyr::case_when(
+    # term == "(Intercept)" ~ "Intercept (bagged flower)",
+    term == "treatmentopen" ~ "treatment (unbagged flower)",
+    term == "sd_(Intercept).plant_name:site_name" ~ "S.D. random intercept", 
+    term == "sd_treatmentopen.plant_name:site_name" ~ "S.D. random slope", 
+    TRUE ~ term
+  )) %>%
+  dplyr::filter(term != "cor_(Intercept).treatmentopen.plant_name:site_name") %>%
+  knitr::kable(caption = "Summary of the model used to analyse the relationship of heterospecific and conspecific pollen", 
+               digits = 3,
+               booktabs = T,
+               col.names = c("predictor", "estimate" ,"S.E.", "z-value")) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::group_rows(index = c("fixed component" = 2, 
+                                   "random component (species:community)" = 2)) 
+```
+
+```{r table-open-bagged-models-random, results='asis'}
+drake::loadd(con_con_plot_df)
+
+coef_open_bagged %>%
+ dplyr::inner_join(sites, by = "site_name") %>%
+  dplyr::mutate(site_name = paste(locality_name, 
+                                  land_use, 
+                                  fragment, 
+                                  sep = ' - ')) %>%
+  dplyr::mutate()
+  dplyr::select(plant_name, site_name, heterospecific, error)
 ```

### 2019-03-06 paper/manuscript.Rmd
Improve result tables of facilitation models and reference them from the paper

@@
 Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with that of those that were closed. 
-Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers. 
-Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had significantly more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open (the difference was non-signifcant for the remainding `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c).
+Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers (Table \@ref(S-tab:table-open-bagged-models-general)). 
+Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had significantly more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open (the difference was non-signifcant for the remainding `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
 Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both significantly positive and negative differences.

### 2019-03-06 paper/supp-info.Rmd
Improve result tables of facilitation models and reference them from the paper

@@
   dplyr::filter(term != "cor_(Intercept).heterospecific.plant_name:site_name") %>%
-  knitr::kable(caption = "Summary of the model used to analyse the relationship of heterospecific and conspecific pollen", 
+  knitr::kable(caption = "Summary of the model used to analyse the relationship between heterospecific and conspecific pollen", 
                digits = 3,
@@
                col.names = c("species name", "community", "slope", "S.E."), 
-               caption = "Slope of the relationship of heterospecific and conspecific pollen for each species in their community (fixed effect + conditional effect).
+               caption = "Slope of the relationship between heterospecific and conspecific pollen for each species in their community (fixed effect + conditional effect).
 Community names are constructed by location - agricultural/restored - fragment number.",
@@
   dplyr::filter(term != "cor_(Intercept).treatmentopen.plant_name:site_name") %>%
-  knitr::kable(caption = "Summary of the model used to analyse the relationship of heterospecific and conspecific pollen", 
+  knitr::kable(caption = "Summary of the model used to analyse the relationship between conspecific pollen deposited in bagged and unbagged flowers (open to animal pollination).", 
                digits = 3,
@@
 
-coef_open_bagged %>%
+con_con_plot_df %>%
  dplyr::inner_join(sites, by = "site_name") %>%
@@
                                   sep = ' - ')) %>%
-  dplyr::mutate()
-  dplyr::select(plant_name, site_name, heterospecific, error)
+  dplyr::mutate_if(is.numeric, round, digits = 0) %>%
+  dplyr::mutate(open_ci = paste0("[", open_lower, ", ", open_upper, "]"), 
+                closed_ci = paste0("[", closed_lower, ", ", closed_upper, "]")) %>%
+  dplyr::select(plant_name, site_name, closed_mid, closed_ci, open_mid, open_ci) %>%
+  knitr::kable("latex", 
+               col.names = c("species name", "community", "mean", "C.I.", "mean", "C.I."), 
+               caption = "Amount of conspecific pollen deposited  in bagged and unbagged flowers (open to animal pollination) for each species in their community.
+Community names are constructed by location - agricultural/restored - fragment number.",
+               booktabs = T, 
+               linesep = "", 
+               align = "llrlrl") %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::column_spec(1, italic = T) %>%
+  kableExtra::add_header_above(c(" " = 2, "bagged" = 2, "unbagged" = 2))
 ```

### 2019-03-06 paper/supp-info.Rmd
Format table of random effects AIC selection in supp info

@@
 
-```{r table-aic-random-models, results= 'asis', eval=T}
+```{r table-aic-random-models, results= 'asis'}
 drake::loadd(glanced_random, random_effects)
@@
   dplyr::mutate_if(is.numeric, round, digits = 1) %>% 
-  dplyr::mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "]"), 
-         delta_AIC = dplyr::if_else(grepl("NA", delta_AIC), "---", delta_AIC)) %>%
+  dplyr::mutate(delta_AIC = AIC_50, 
+                delta_AIC_CI = paste0("[", AIC_05, ", ", AIC_95, "]")) %>%
   dplyr::group_by() %>%
   humanize(random_effects = random_effects) %>%
-  dplyr::arrange(pollen_category, random_name, scale) %>%
+  dplyr::filter(pollen_category %in% c("conspecific (absolute)", "heterospecific")) %>%
+  dplyr::mutate(
+    pollen_category = dplyr::if_else(
+      pollen_category == "conspecific (absolute)", 
+      "conspecific pollen", "heterospecific pollen"), 
+    random_name = knitr:::escape_latex(random_name)) %>%
+  dplyr::arrange(pollen_category, delta_AIC) %>%
   dplyr::rename(`pollen type` = pollen_category,
@@
 summ %>%
-  dplyr::select(`pollen type`, `random structure`, delta_AIC) %>%
-  knitr::kable(caption = paste('Comparison of the different random structures we considered.
-The table shows median delta AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data.
+  dplyr::select(`random structure`, delta_AIC, delta_AIC_CI) %>%
+  kableExtra::kable("latex", 
+               caption = paste('Comparison of the two random structures we considered for the models of conspecific and heterospecific pollen deposition.
+The table shows median $\\Delta$AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data.
 The 5th and 95th percentile are shown inside square brackets.
 Communities are defined by individual fragments but ignore the hierarchical arrangement of sampling sites."),
-               booktabs = TRUE) %>%
+               col.names = c("random structure", "median", "C.I."),
+               booktabs = TRUE, 
+               escape = F) %>%
   kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::column_spec(column = 1, bold=T) %>%
-  kableExtra::collapse_rows(columns = 1, latex_hline = "major", valign = "middle")
+  kableExtra::group_rows(index = c("conspecific pollen" = 2, 
+                                   "heterospecific pollen" = 2)) %>%
+  kableExtra::add_header_above(c(" " = 1, "$\\\\Delta$AIC" = 2), escape = F)
 ```
 
-```{r table-species-gain-global, results = 'asis', eval=T}
+```{r table-species-gain-global, results = 'asis', eval=F}
 drake::loadd(significant_gain_global, significant_gain_site, sites)

### 2019-03-06 paper/supp-info.Rmd
Making explicit latex output in Supp Info tables

@@
 
+<!-- To add an S before each figure and table -->
 \renewcommand\thefigure{S\arabic{figure}}    
@@
   dplyr::filter(term != "cor_(Intercept).heterospecific.plant_name:site_name") %>%
-  knitr::kable(caption = "Summary of the model used to analyse the relationship between heterospecific and conspecific pollen", 
+  knitr::kable("latex", 
+               caption = "Summary of the model used to analyse the relationship between heterospecific and conspecific pollen", 
                digits = 3,
@@
   dplyr::filter(term != "cor_(Intercept).treatmentopen.plant_name:site_name") %>%
-  knitr::kable(caption = "Summary of the model used to analyse the relationship between conspecific pollen deposited in bagged and unbagged flowers (open to animal pollination).", 
+  knitr::kable("latex", 
+               caption = "Summary of the model used to analyse the relationship between conspecific pollen deposited in bagged and unbagged flowers (open to animal pollination).", 
                digits = 3,
@@
          `plant species` = recipient) %>%
-  knitr::kable(
+  knitr::kable("latex", 
     caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
@@
                 `fixed structure` = fixed_formula) %>%
-  knitr::kable(caption = paste('Comparison of the different fixed structures we considered.
+  knitr::kable("latex", 
+               caption = paste('Comparison of the different fixed structures we considered.
 The table shows median delta AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data.
@@
 table_frame %>%
-  knitr::kable(
+  knitr::kable("latex", 
     caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
@@
   anova(test = "Chisq")  %>%
-  knitr::kable(
+  knitr::kable("latex", 
     caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).

### 2019-03-06 paper/manuscript.Rmd
Format table of random effects AIC selection in supp info
Finish off text edits for second subsection of results

@@
 As determined by AICc, the random structure best supported by the data was the one that fit an intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community they belong to).
-This structure was best for both the models of conspecific and heterospecific pollen (Table SXX).
+This structure was best for both the models of conspecific and heterospecific pollen (Table \@ref(S-tab:table-aic-random-models)).
 
-Out of the four variables we explored, we found that the plants' mean visit effectiveness and its abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
-Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only included in models with relatively large AICc values.
-
-We found that the relationship between each of the strategies and pollen deposition was similar for both conspecific and heterospecific pollen. 
-This is, strategies that were associated with an increase (or a decrease) in conspecific pollen, were also associated with an increase (or a decrease) in heterospecific pollen deposition. 
-Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
-The positive association with conspecific pollen indicates a positive effect on the quantity of pollination. 
-However, the mean of the coefficients that relates visit effectiveness to heterospecific pollen deposition is slightly larger than that of conspecific pollen. 
-This suggest a negative, albeit marginal, relationship of visit effectiveness and our definition of the quality of the pollination service (Figure \@ref(fig:fig-average-qual-quant)c). 
-Contrastingly, the plants' relative abundance had a negative effect in pollen deposition (and consequently the quantity of pollination), but the difference between the coefficients in the models of conspecific and heterospecific pollen indicates a considerable positive impact on the quality of pollination.
-The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and quality of pollination. 
-Finally, the number of shared pollinators had a negative association with the quantity and quality of pollination, but these impacts were small when compared to the other variables. 
-Although relative abundance, the number of shared pollinators, and the visit effectiveness were positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
+Of the four variables we considered, we found that a plant's mean visit effectiveness and abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
+Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values.
 
@@
 ```
+
+We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
+That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
+Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
+However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
+This indicates that, although there is a positive association between visit effectiveness and the *absolute* amount of conspecific pollen, there is a negative relationship with the *relative* amount of conspecific relative to heterospecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
+In contrast, a plants' relative abundance had a negative effect on the absolute amount of conspecific pollen, but the mean difference between the coefficients in the models indicates a positive association with the relatvie amount of conspecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
+The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the absolute and relative amount of conspecific pollen deposited. 
+Finally, the number of shared pollinators had a negative association with both the absolute and relative amounts of conspecific pollen deposited, but these impacts were small when compared to the other variables.
+Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)), indicating that collinearity did not influence our findings qualitatively.
 

### 2019-03-07 paper/manuscript.Rmd
Finish table of AIC of fixed deposition models in supp info and reference it from the main text

@@
 Of the four variables we considered, we found that a plant's mean visit effectiveness and abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
-Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values.
+Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (\@ref(S-tab:table-aic-fixed-models)).
 

### 2019-03-07 paper/supp-info.Rmd
Finish table of AIC of fixed deposition models in supp info and reference it from the main text

@@
   - \usepackage{booktabs}
+  - \usepackage{longtable}
+  - \usepackage{array}
+  - \usepackage{multirow}
+  - \usepackage{wrapfig}
+  - \usepackage{float}
+  - \usepackage{colortbl}
+  - \usepackage{pdflscape}
+  - \usepackage{tabu}
+  - \usepackage{threeparttable}
+  - \usepackage{threeparttablex}
+  - \usepackage[normalem]{ulem}
+  - \usepackage{makecell}
+  - \usepackage{xcolor}
 editor_options: 
@@
                                   sep = ' - ')) %>%
+  dplyr::mutate_if(is.character, knitr:::escape_latex) %>%
+  dplyr::mutate(plant_name = paste0("\\textit{", plant_name, "}")) %>%
   dplyr::select(plant_name, site_name, heterospecific, error)
@@
                booktabs = T, 
-               linesep = "") %>%
-  kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::column_spec(1, italic = T)
+               linesep = "", 
+               escape = F) %>%
+  kableExtra::kable_styling(font_size = 8) 
 ```
@@
                 closed_ci = paste0("[", closed_lower, ", ", closed_upper, "]")) %>%
+  dplyr::mutate_if(is.character, knitr:::escape_latex) %>%
+  dplyr::mutate(plant_name = paste0("\\textit{", plant_name, "}")) %>%
   dplyr::select(plant_name, site_name, closed_mid, closed_ci, open_mid, open_ci) %>%
@@
 Community names are constructed by location - agricultural/restored - fragment number.",
-               booktabs = T, 
+               booktabs = TRUE, 
                linesep = "", 
-               align = "llrlrl") %>%
+               align = "llrlrl", 
+               escape = FALSE) %>%
   kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::column_spec(1, italic = T) %>%
   kableExtra::add_header_above(c(" " = 2, "bagged" = 2, "unbagged" = 2))
@@
   dplyr::filter(scale == "community") %>%
-  dplyr::mutate(delta_AIC = paste0(round(delta_AIC, 1), 
-                                  " [", 
-                                  round(delta_AIC_quantile_05, 1),
+  dplyr::mutate_if(is.numeric, round, digits = 1) %>%
+  dplyr::mutate(delta_AIC_CI = paste0(" [", delta_AIC_quantile_05,
                                       " ,", 
-                                  round(delta_AIC_quantile_95, 1),
+                                      delta_AIC_quantile_95,
                                       "]")) %>% 
@@
   humanize(formula_long = TRUE) %>%
+  dplyr::filter(pollen_category %in% c("conspecific (absolute)", "heterospecific")) %>%
+  dplyr::mutate(
+    pollen_category = dplyr::if_else(
+      pollen_category == "conspecific (absolute)", 
+      "conspecific pollen", "heterospecific pollen")) %>% 
   dplyr::mutate(fixed_formula = paste("~", fixed_formula)) %>%
   dplyr::arrange(pollen_category, delta_AIC_rank) %>%
-  dplyr::select(pollen_category, fixed_formula, delta_AIC) %>%
-  dplyr::rename(`pollen type` = pollen_category, 
-                `fixed structure` = fixed_formula) %>%
+  dplyr::select(fixed_formula, delta_AIC, delta_AIC_CI) %>%
+  dplyr::rename(`fixed structure` = fixed_formula) %>% 
   knitr::kable("latex", 
-               caption = paste('Comparison of the different fixed structures we considered.
-The table shows median delta AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data.
+               col.names = c("fixed structure", "median", "C.I."),
+               caption = paste('Comparison of the different fixed structures we consideredfor the models of conspecific and heterospecific pollen deposition.
+The table shows median $\\Delta$AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data.
 The 5th and 95th percentile are shown inside square brackets."),
@@
   kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::column_spec(column = 1, bold=T) %>%
-  kableExtra::collapse_rows(columns = 1, latex_hline = "major", valign = "middle")
+  kableExtra::group_rows(index = c("conspecific pollen" = 15, 
+                                   "heterospecific pollen" = 15)) %>%
+  # kableExtra::collapse_rows(columns = 1, latex_hline = "major", valign = "middle") %>%
+  kableExtra::add_header_above(c(" " = 1, "$\\\\Delta$AIC" = 2), escape = F)
 ```

### 2019-03-07 paper/supp-info.Rmd
Remove table of pollen gain using Mann-Withney test from the supp. info

@@
 
-```{r table-species-gain-global, results = 'asis', eval=F}
-drake::loadd(significant_gain_global, significant_gain_site, sites)
-
-glance_table(significant_gain_global) %>%
-  dplyr::select(recipient, estimate, statistic, p.value) %>%
-  dplyr::mutate(recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
-  dplyr::rename(`p value` = p.value,
-         `difference` = estimate,
-         `plant species` = recipient) %>%
-  knitr::kable("latex", 
-    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
-Tests were performed at the species level (across communities).",
-    escape = FALSE, 
-    booktabs = TRUE, 
-    linesep = c("")) %>%
-  kableExtra::kable_styling(font_size = 8)
-```
-
 ```{r table-aic-fixed-models, results= 'asis', eval=T}

### 2019-03-07 paper/supp-info.Rmd
Make fig. supp info. distribution of effects clearer and larger

@@
 
-```{r fig-model-results, fig.height = 7, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
-Only results for the models with the most parsimonous fixed effects.", eval=T}
+```{r fig-model-results, fig.height = 9, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
+Model formulas have been abbreviated: *a* for abundance, *k* for the number of shared polinators, *p* for the visit effectiveness, and *t* for trait originality.", eval=T}
 drake::readd(fig_all_model_results)

### 2019-03-07 code/fig_all_model_results.R

@@ -5,41 +5,55 @@ make_fig_all_model_results <- function(tidied_fixed, sites, model_formula_rankin
   # only keep models that make up to 95% of the evidence
   best_models <- model_formula_ranking$by_model_set %>%
     dplyr::group_by(scale, pollen_category) %>%
-    dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC), 
-                  weights = get_weights(likelyhood)) %>% 
-    dplyr::arrange(delta_AIC) %>% 
-    dplyr::mutate(cum_weight = cumsum(weights), 
-                  best_set = dplyr::lag(cum_weight) < 0.99, 
+    dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC),
+                  weights = get_weights(likelyhood)) %>%
+    dplyr::arrange(delta_AIC) %>%
+    dplyr::mutate(cum_weight = cumsum(weights),
+                  best_set = dplyr::lag(cum_weight) < 0.99,
                   best_set = dplyr::if_else(is.na(best_set), TRUE, best_set)) %>%
-    dplyr::filter(best_set) 
-  
+    dplyr::filter(best_set)
+
   best_model_formulas <- model_formula_ranking$by_model_set %$%
     fixed_formula %>%
     unique()
-  
+
+  col_pal <- cgm()$pal_el_green[c(13,7)]
+
   tidied_fixed %>%
-    dplyr::filter(term != "(Intercept)" , 
-                  var_trans == 'log', 
+    dplyr::filter(term != "(Intercept)" ,
+                  var_trans == 'log',
                   fixed_formula %in% best_model_formulas,
-                  scale == "community"
-    ) %>%
+                  scale == "community") %>%
     dplyr::group_by(pollen_category,scale, model, var_trans, term, fixed_formula) %>%
     dplyr::summarise(estimate = dplyr::first(estimate)) %>%
     dplyr::group_by() %>%
     humanize() %>%
-    ggplot(aes(x = estimate, 
-               colour = pollen_category, 
+    dplyr::filter(pollen_category %in% c("conspecific (absolute)",
+                                         "heterospecific")) %>%
+    dplyr::mutate(pollen_category =
+                    dplyr::if_else(pollen_category == "conspecific (absolute)",
+      "conspecific pollen", "heterospecific pollen")) %>%
+    ggplot(aes(x = estimate,
+               colour = pollen_category,
                fill = pollen_category)) +
[…]

### 2019-03-08 paper/manuscript.Rmd
Update comments for compiling facilitation figure quickly in manuscript

@@
 # fig_random_slopes <- plot_random_slopes(facilitation_plot_df)
-# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
 # fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
+# fig_con_con = plot_bagged_vs_open_conspecific(drake::readd(con_con_plot_df))
 # pdf(width = 6.5, height = 4)

### 2019-03-10 paper/manuscript.Rmd
Change order of colours in FIg 1 categories so its sequential

@@
 Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities.
-Significantly negative slopes (dark grey) indicate that plants experience competition for animal-mediated pollination, while significantly positive slopes (light grey) indicate that facilitation is the predominant outcome.
+Significantly negative slopes (darkest shade) indicate that plants experience competition for animal-mediated pollination, while significantly positive slopes (lightest shade) indicate that facilitation is the predominant outcome.
 The number of plants analysed for each species is shown within brackets next to the species name.

### 2019-03-10 code/facilitation.R

@@ -58,7 +58,7 @@ get_facilitation_plot_df <- function(dep_frame, facilitation_random_effects){
 
 # plot the slopes of the random effects models
 plot_random_slopes <- function(facilitation_plot_df){
-  pal <- common_graphic_metrics()$pal_el_green[c(8,1,5)]
+  pal <- common_graphic_metrics()$pal_el_green[c(8,5, 1)]
   shape_col <- common_graphic_metrics()$pal_el_green[9]
 
   require(ggplot2)
@@ -195,7 +195,7 @@ plot_bar_proportion <- function(x, pal){
              position = "fill") +
     geom_text(aes(label = label,
                   y = label_height,
-                  colour = label_col,
+                  colour = label,
                   size = label_col,
                   fontface = fontface),
               stat = "unique",
@@ -205,7 +205,7 @@ plot_bar_proportion <- function(x, pal){
                        expand = c(0,0),
                        labels = scales::percent) +
     scale_fill_manual(values = rev(pal)) +
-    scale_color_manual(values = c("black", "white")) +
+    scale_color_manual(values = c("black", "white", pal[1])) +
     scale_size_manual(values = c(2,2.5)) +
     labs(y = "% species") +
     pub_theme() +

### 2019-03-10 code/make_fig_con_hetero_gain.R

@@ -205,7 +205,7 @@ plot_bagged_vs_open_conspecific <- function(con_df){
   axis_breaks <-  cgm()$log1p_axis_breaks_10
   linesize <- common_graphic_metrics()$size_errorbars
   linecolor <- cgm()$color_errorbars_light
-  pal <-common_graphic_metrics()$pal_el_green[c(8,1,5)]
+  pal <-common_graphic_metrics()$pal_el_green[c(8,5,1)]
   shape_col <- common_graphic_metrics()$pal_el_green[9]
 
   scatter_plot <- con_df %>%

### 2019-03-10 code/coefficient_averages.R
Y labels of figure 2 are now always centered. Close #52

@@ -1,29 +1,29 @@
 get_coefficient_averages <- function(tidied_fixed, model_formula_ranking, N = 99){
   model_weights <- model_formula_ranking$by_model_set %>%
     dplyr::group_by(pollen_category, scale) %>%
-    dplyr::mutate(l = get_likelyhoods(delta_AIC_median), 
-                  w = get_weights(l)) %>% 
+    dplyr::mutate(l = get_likelyhoods(delta_AIC_median),
+                  w = get_weights(l)) %>%
     dplyr::select(pollen_category, scale, fixed_formula, w)
-    
+
   1:N %>%
     purrr::map_df(get_coeficient_estimate_sample, tidied_fixed, model_weights, N)
-  
+
 }
 
 get_coeficient_estimate_sample <- function(sample_n, tidied_fixed, model_weights, N){
   # consider cases with zero
-  
+
   tidied_fixed %>%
-    dplyr::filter(term != "(Intercept)") %>% 
+    dplyr::filter(term != "(Intercept)") %>%
     dplyr::group_by(model, pollen_category, scale, fixed_formula, term) %>%
-    dplyr::summarise(estimate = mean(estimate)) %>% 
-    dplyr::group_by() %>% 
+    dplyr::summarise(estimate = mean(estimate)) %>%
+    dplyr::group_by() %>%
     # complete cases. The estimate of the term for the models in which it wasn't present is zero
-    tidyr::complete(model, pollen_category, scale, fixed_formula, term, fill = list(estimate = 0)) %>% 
-    dplyr::inner_join(model_weights, 
-                      by = c("pollen_category", "scale", "fixed_formula")) %>% 
+    tidyr::complete(model, pollen_category, scale, fixed_formula, term, fill = list(estimate = 0)) %>%
+    dplyr::inner_join(model_weights,
+                      by = c("pollen_category", "scale", "fixed_formula")) %>%
     dplyr::group_by(pollen_category, scale, term) %>%
-    dplyr::sample_n(size = N, replace = T, weight = w) %>% 
+    dplyr::sample_n(size = N, replace = T, weight = w) %>%
     # dplyr::summarise(estimate = weighted.mean(estimate, w)) %>%
     dplyr::mutate(sample_n = sample_n)
 }
@@ -45,24 +45,24 @@ plot_coefficient_averages <- function(coefficient_averages, variable_importance)
       tidyr::gather("key", "value", `conspecific (absolute)`:heterospecific) %>%
[…]

### 2019-03-10 code/get_variable_importance.R

@@ -1,98 +1,112 @@
 get_variable_importance <- function(model_formula_ranking){
-  
+
   # get the terms in the models
   terms <- model_formula_ranking$aggregated$fixed_formula %>%
     stringr::str_remove("pollen_gain ~  ") %>%
     stringr::str_split(stringr::fixed(" + ")) %>%
     unlist() %>%
-    unique() 
+    unique()
   # remove the null model
   terms <- terms[terms != "1"]
-  
+
   model_weights <- model_formula_ranking$by_model_set %>%
     dplyr::filter(scale == "community") %>%
     dplyr::group_by(pollen_category) %>%
-    dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
+    dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median),
                   weight = get_weights(likelyhood))
-  
+
   crosses <- purrr::cross2(terms, unique(model_formula_ranking$by_model_set$pollen_category))
   crosses %>%
     purrr::map(~model_weights$weight[stringr::str_detect(model_weights$fixed_formula, .[[1]]) & model_weights$pollen_category == .[[2]]]) %>%
     purrr::map(sum) %>%
-    purrr::map2_df(crosses, 
+    purrr::map2_df(crosses,
                    ~ dplyr::data_frame(
                      var = .y[[1]],
-                     pollen_category = .y[[2]], 
+                     pollen_category = .y[[2]],
                      importance = .x)
     ) %>%
     dplyr::mutate(importance = round(importance, digits = 3)) %>%
     dplyr::rename(term = var) %>%
-    humanize() %>% 
+    humanize() %>%
     tidyr::spread(pollen_category, importance) %>%
     dplyr::arrange(dplyr::desc(heterospecific))
 }
 
 plot_variable_importance <- function(variable_importance) {
   require(ggplot2)
-  
+
   plot_importance <- function(x){
     middle_space <- -0.4  # for 1/3 is -0.525
     x %>% ggplot(aes(x = term, y = value)) +
       # geom_segment(aes(xend = term, yend = 0)) +
       # geom_point(shape = 21, fill = cgm()$pal_rb3[2], size = 6) +
-      
+
       geom_col(fill = "grey90") +
       # geom_hline(yintercept = 0, linetype = 2, size = 0.25, colour = "grey30") +
-      
-      geom_point(aes(x = 1, y = middle_space), alpha = 0) +
[…]

### 2019-03-10 paper/manuscript.Rmd
Make figure 2 a narrow 1 col figure

@@
 
-```{r fig-average-qual-quant, fig.height= 2.29*2, fig.width=6.5/3*2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
+```{r fig-average-qual-quant, fig.height= 2.29*2, fig.width=6.5/2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
 (a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
@@
 height2 <- 1.29
-# pdf(width = 3.25 * 2 / 3 * 2, height = sum(c(height1, height2))*2)
+# pdf(width = 3.25 , height = sum(c(height1, height2))*2)
 # fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
-width_imp <- 6.5/5*2
-mult <- 2.455 # for 2/3 is xx, for 3/5 is 2.355
-width_coef_1 <- (6.5 - width_imp) / (1 + mult)
-width_coef_2 <- 5.6 - width_imp - width_coef_1
+# width_imps <- 6.5/5*2
+# mult <- 2.455 # for 2/3 is xx, for 3/5 is 2.355
+# width_coef_1 <- (6.5 - width_imp) / (1 + mult)
+# width_coef_2 <- 5.6 - width_imp - width_coef_1
 # fig_var_importance <- plot_variable_importance(variable_importance)
@@
 
-left_top <- cowplot::plot_grid(
+var_impo <- cowplot::plot_grid(
   fig_var_importance[[1]],
+  fig_var_importance[[3]],
   fig_var_importance[[2]],
-  ncol = 2, 
+  ncol = 3,
+  rel_widths = c(1,0.75,1),
   align = "h"
@@
 
-left_bottom <- cowplot::plot_grid(
+bottom <- cowplot::plot_grid(
   fig_coef_avg[[1]],
+  fig_coef_avg[[3]],
   fig_coef_avg[[2]],
-  rel_widths = c(width_coef_1, width_coef_2), 
+  rel_widths = c(1,0.75,1), 
+  ncol = 3,
   align = "h"
@@
 cowplot::plot_grid(
-  left_top, 
+  var_impo, 
   fig_coefficient_averages,
-  left_bottom, 
+  bottom, 
   ncol = 1, 

### 2019-03-11 paper/manuscript.Rmd
Adjust height of mean effect figure (Fig 2c)

@@
 height1 <- 1
-height2 <- 1.29
+height2 <- 1.18
 # pdf(width = 3.25 , height = sum(c(height1, height2))*2)

### 2019-03-11 paper/manuscript.Rmd
Evaluate figure heights dynamically based on values on he code using eval.after

@@
                       warning = FALSE)
+knitr::opts_knit$set(eval.after = c("fig.height"))
 ```
@@
 
-```{r fig-average-qual-quant, fig.height= 2.29*2, fig.width=6.5/2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
+```{r fig-average-qual-quant, fig.height= height1+height2, fig.width=6.5/2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
 (a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
@@
 Visit effectiveness and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association.
-The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific (top panel) and heterospecific pollen (bottom panel).
+The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific and heterospecific pollen.
 Results are only shown for models that included explanatory variable.
-(c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and quality of pollination.
-The plot shows the model averaged mean effect ($\\pm$ SE) of the four analysed ecological variables in the quantity and quality of pollination."}
+(c) The end result of these associations is that only the plants' functional originality has a positive impact on both the absolute and relative amount of conspecific pollen deposition (relative to heterospecific pollen).
+The plot shows the model averaged mean effect ($\\pm$ SE)."}
 height1 <- 1
@@
 
-```{r strategy-fig-height}
-height0 <- 1.55
-height1 <- 2.7
-height2 <- 2.4
-strategy_fig_height <- sum(height0, height1, height2)
-```
-
 ```{r fig-pca, fig.width=3.25, fig.height=strategy_fig_height, fig.cap="**The flexibility of plant strategies**.
@@
 Only one of the examined species had strategies that were more tightly connected than what would be expected at random."}
+height0 <- 1.55
+height1 <- 2.7
+height2 <- 2.4
+strategy_fig_height <- sum(height0, height1, height2)
 # fig_pca <- plot_pca(pcas, chosen_threshold = 0)

### 2019-03-11 paper/manuscript.Rmd
Update changelog

@@
 * Using a similar approach to compare conspecific pollen deposited in open and bagged flowers (I used a series of Mann-Withney U tests before)
-* Added model results tables in the Supplementary Information
+* Added facilitation model results tables in the Supplementary Information
+* Made Figure 2 (model of enviornmental factors) one-column
+* Applied a green palette to all figures. Improves legibility when looking at it in a screen an performance when printed in greyscale is maintained
+* Show niche points for all species and not only those in two communities or more
 

### 2019-03-12 paper/manuscript.Rmd
Using dynamic height doesn't work. Back to manual height

@@
                       warning = FALSE)
-knitr::opts_knit$set(eval.after = c("fig.height"))
 ```
@@
 
-```{r fig-average-qual-quant, fig.height= height1+height2, fig.width=6.5/2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
+```{r fig-average-qual-quant, fig.height= 2.29*2, fig.width=6.5/2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
 (a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
@@
 The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable.
-(b) The association of ecological variables on heterospecific pollen tended to be aligned with its association on conspecific pollen.
+(b) The association between ecological variables and heterospecific pollen tended to align with their association with conspecific pollen.
 Visit effectiveness and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association.
 The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific and heterospecific pollen.
-Results are only shown for models that included explanatory variable.
 (c) The end result of these associations is that only the plants' functional originality has a positive impact on both the absolute and relative amount of conspecific pollen deposition (relative to heterospecific pollen).
@@
 
-```{r fig-pca, fig.width=3.25, fig.height=strategy_fig_height, fig.cap="**The flexibility of plant strategies**.
+```{r fig-pca, fig.width=3.25, fig.height=6.65, fig.cap="**The flexibility of plant strategies**.
 (a) The two first components explain a large proportion of the total variance.

### 2019-03-12 paper/manuscript.Rmd
Calculate number of species with significant niche differences dynamically

@@
 drake::loadd(pcas)
+drake::loadd(permanova_plant_distances)
 chosen_threshold <- 0
@@
     extract2(1)
+median_distances <- permanova_plant_distances %>% 
+  dplyr::filter(na_threshold == 0, metric == "median_dist", !is.na(value)) %$%
+  value
 ```
@@
 When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the strategies of a species do not seem to be close to each other.
-Indeed, when we measured the median distance between the plants coordinates, we found that it was significantly smaller than that of randomisations for only one of all analysed species (Figure \@ref(fig:fig-pca)c).
+Indeed, when we measured the median distance between the plants coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` analysed species (Figure \@ref(fig:fig-pca)c).
 

### 2019-03-12 paper/manuscript.Rmd
making Figure 2 bottom a bit taller to keep same line spacing

@@
 height1 <- 1
-height2 <- 1.18
+height2 <- 1.29
 # pdf(width = 3.25 , height = sum(c(height1, height2))*2)

### 2019-03-12 paper/manuscript.Rmd
Edits to third section of the results

@@
 Of the four variables we considered, we found that a plant's mean visit effectiveness and abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
-Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (\@ref(S-tab:table-aic-fixed-models)).
+Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
 
@@
 
-We used a PCA of the analysed species to investigate whether plants strategies are similar across communities or whether they are flexible, and therefore able to adapt to the community context. 
+We used a PCA of the analysed species to investigate whether plant's niche of competition for pollination are similar across communities or whether they are flexible, and therefore a reflection of the community context.
 The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
-The first component was dominated by changes in the visit effectiveness and the relative abundance, while the second component was dominated by the number of shared pollinators and the plant's functional originality.
-When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the strategies of a species do not seem to be close to each other.
+The first component was dominated by changes in visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality.
+When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
 Indeed, when we measured the median distance between the plants coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` analysed species (Figure \@ref(fig:fig-pca)c).

### 2019-03-12 paper/manuscript.Rmd
slightly smaller proportions Fig 2

@@
 
-```{r fig-average-qual-quant, fig.height= 2.29*2, fig.width=6.5/2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
+```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=6.5/2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
 (a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
@@
 height1 <- 1
-height2 <- 1.29
+height2 <- 1.28
 # pdf(width = 3.25 , height = sum(c(height1, height2))*2)

### 2019-03-13 code/pca.R
Change headings of PCA figure (3)

@@ -272,7 +272,7 @@ plot_permanova_dist <- function(permanova_plant_distances,
           axis.line.x = element_line(size = 0.25)) +
     labs(x = expression(italic(p) - plain("value")),
          title = "(c) flexibility of plant's strategies",
-         subtitle = "median distance between plant strategies vs. randomisations") +
+         subtitle = "median distance between plant niches vs. randomisations") +
     coord_cartesian(clip = "off") +
     scale_x_continuous(expand = c(0,0.1),
                        breaks = c(0.01, 0.05, 0.5, 0.99),
@@ -344,8 +344,8 @@ plot_pca <- function(pcas, chosen_threshold){
     # coord_equal() +
     labs(x = paste0("1st component (", round(variances_data$`percentage of variance`[1]), "%)"),
          y = paste0("1nd component (", round(variances_data$`percentage of variance`[2]), "%)"),
-         title = "(b) plant strategies in PCA space",
-         subtitle = "convex hulls of species in two communities or more")
+         title = "(b) plant realised niches in PCA space",
+         subtitle = "convex hulls of species niches across communities")
 
 }
 

### 2019-03-13 paper/manuscript.Rmd
Some edits to the discussion

@@
 
-Our results suggest that the community context plays a central role in determining competition for pollination. 
+All else being equal, our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
 First, we found that the costs of pollinator sharing are pervasive. 
-In particular, we found that a significant proportion of species undergoes overall neutral or competitive effects from animal-mediated pollination.
-Second, we found that plants are able to minimise the intensity of this competition using multiple strategies, however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these strategies are likely to involve a trade-off between the quantity and quality of pollination.
-Third, we found that these strategies are strongly shaped by the community context, this is, the same plant species can adopt dramatically different strategies depending on the community it belongs to.
+In particular, we found that a significant proportion of species experiences overall neutral or competitive effects from animal-mediated pollination. 
+Second, we found that multiple ecological factors can modulate the intensity of this competition; however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these factors are likely to involve a trade-off between the quantity and quality of pollination.
+Third, we found that the way these factors influence competition is strongly shaped by the community context, this is, if collectively these factors are used to define a niche of competition for pollination, the same plant species can occupy dramatically different niches depending on the community it belongs to.
 
-\R{disc-facil-comp}Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community.
-Although a recent study already suggested a wide range of outcomes in a multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood.
-Here we show that the prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.
+Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that net facilitation is only experienced by a fraction of species in a community. 
+A recent study also suggested a wide range of outcomes in a multi-species context [@tur_evaluating_2016]. 
+However, the factors explaining why some species experience more competition than others were not understood. 
+Here we show that the prevalence of neutral and competitive effects of animal-mediated pollination can be at least partially explained by the trade-offs that minimising competition can involve.  
+These trade-offs were most evident in precisely the factors that most strongly modulate pollen deposition. 
+Specifically, we found that the factors related to the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition.
+At the same time, receiving high visitation increases the absolute levels of conspecific pollen deposition but increasses heterospeicific deposition to a greater extent even when the visitors are likely carry a high proportion of conspecific pollen.
+Similarly, being abundant reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
+Multiple studies recognise the importance of visitation and abundance to competition for pollination, however, some suggest a positive effect on the pollination service while some others a negative one [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008].
+Our results corroborate the importance of these two factors, and show that the contrsating results obtained by earlier studies could be explained by the trade-offs involved.
 
-These trade-offs were most evident precisely in the strategies that most strongly modulate pollen deposition. 
-We found that the strategies that increased the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition. 
-Adopting a strategy of high visitation increases the rates of conspecific pollen deposition at the expense of a reduction in the quality of pollination even when the visitors carry a high proportion of conspecific pollen.
-Similarly, adopting a strategy of high abundance reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
-Our results corroborate the importance that previous studies have attributed to the role that visitation and abundance play at determining competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008].
-The fact that they also involve a trade-off between the quantity and quality of pollination might explain the often contrasting results that these studies, based on two or three species systems obtained.
-
-Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition.
-The relatively wide range of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
-While some plant species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
+Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition to minimise competition for pollination.
+The relatively broad distribution of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
+Indeed, some plant species experience a large reduction in seed set due to heterospecific pollen deposition, while others are relatively insensitive to heterospecific pollen but greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
 

### 2019-03-14 paper/supp-info.Rmd
Only show results for candidate formulas with a delta AICc < 4

--- 2019-03-07 paper/supp-info.Rmd
@@
 
-```{r fig-model-results, fig.height = 7, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
-Only results for the models with the most parsimonous fixed effects.", eval=T}
+```{r fig-model-results, fig.height = 5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
+Model formulas have been abbreviated: *a* for abundance, *k* for the number of shared polinators, *p* for the visit effectiveness, and *t* for trait originality.
+Only candidate formulas with a $\Delta AICc < 4$ for either conspecific or heterospecific pollen are shown.
+Models candidates are arranged in decreassing order of support.", eval=T}
 drake::readd(fig_all_model_results)

### 2019-03-14 code/fig_all_model_results.R

@@ -13,9 +13,21 @@ make_fig_all_model_results <- function(tidied_fixed, sites, model_formula_rankin
                   best_set = dplyr::if_else(is.na(best_set), TRUE, best_set)) %>%
     dplyr::filter(best_set)
 
-  best_model_formulas <- model_formula_ranking$by_model_set %$%
+  best_model_formulas <- model_formula_ranking$by_model_set %>%
+    dplyr::ungroup() %>%
+    dplyr::filter(pollen_category %in% c("conspecific_abs", "heterospecific_abs"),
+                  delta_AIC_median < 4) %>%
+    dplyr::mutate(fixed_formula = forcats::fct_reorder(fixed_formula,
+                                                       delta_AIC_median,
+                                                       .desc = T)) %>%
+    dplyr::arrange(dplyr::desc(fixed_formula)) %$%
     fixed_formula %>%
     unique()
+
+  best_model_formula_short <-
+    tibble::data_frame(fixed_formula = best_model_formulas) %>%
+    humanize() %$%
+    fixed_formula
 
   col_pal <- cgm()$pal_el_green[c(8,6)]
 
@@ -28,6 +40,8 @@ make_fig_all_model_results <- function(tidied_fixed, sites, model_formula_rankin
     dplyr::summarise(estimate = dplyr::first(estimate)) %>%
     dplyr::group_by() %>%
     humanize() %>%
+    dplyr::mutate(fixed_formula = forcats::fct_relevel(fixed_formula,
+                                                       best_model_formula_short)) %>%
     dplyr::filter(pollen_category %in% c("conspecific (absolute)",
                                          "heterospecific")) %>%
     dplyr::mutate(pollen_category =

### 2019-03-14 paper/manuscript.Rmd
Calculate R2 of models in the workflow

@@
 ```{r model-fit-statistics}
-drake::loadd(model_formula_ranking, glanced_fixed)
-
-r2_values <- model_formula_ranking$by_model_set %>%
-  dplyr::filter(grepl("abs", pollen_category)) %>% 
-  dplyr::group_by(pollen_category) %>%
-  dplyr::filter(delta_AIC_median == min(delta_AIC_median)) %>%
-  dplyr::select(fixed_formula, pollen_category, scale) %>%
-  dplyr::left_join(glanced_fixed) %>% 
-  dplyr::select(r2m, r2c) %>%
-  dplyr::summarise_all(dplyr::funs(min, median, mean, max)) %>%
-  dplyr::mutate_if(is.numeric, round, digits = 2)
+drake::loadd(r2_values)
 ```

### 2019-03-14 code/model_r2.R

@@ -1,0 +1,11 @@
+calc_model_r2_values <- function(model_formula_ranking, glanced_fixed){
+  model_formula_ranking$by_model_set %>%
+    dplyr::filter(grepl("abs", pollen_category)) %>%
+    dplyr::group_by(pollen_category) %>%
+    dplyr::filter(delta_AIC_median == min(delta_AIC_median)) %>%
+    dplyr::select(fixed_formula, pollen_category, scale) %>%
+    dplyr::left_join(glanced_fixed) %>%
+    dplyr::select(r2m, r2c) %>%
+    dplyr::summarise_all(dplyr::funs(min, median, mean, max)) %>%
+    dplyr::mutate_if(is.numeric, round, digits = 2)
+}

### 2019-03-14 main.R

@@ -126,7 +126,8 @@ fixed_summaries <- drake_plan(
   wilcox_glo_com = global_vs_community(glanced_fixed, model_formula = best_model_formula),
   summary_effects = get_summary_effects(tidied_fixed),
   coefficient_averages = get_coefficient_averages(tidied_fixed, model_formula_ranking, N = 99),
-  variable_importance = get_variable_importance(model_formula_ranking)
+  variable_importance = get_variable_importance(model_formula_ranking),
+  r2_values = calc_model_r2_values(model_formula_ranking, glanced_fixed)
 )
 
 predictions <- drake_plan(

### 2019-03-14 paper/manuscript.Rmd
Move R2 details to the supp info from the msc to save space

@@
 
-We then examined the potential roles played by four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality) play in pollen deposition and, by extension, in the quantity and quality of pollination.
-Together these variables can describe the niche that plants might occupy in the context of competition for pollination. 
-We found that our linear mixed models of pollen deposition had high explanatory power. 
-The conditional coefficient of determination R^2^~(c)~ of the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean of `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the bootstrap replicates of the conspecific pollen models and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen [@nakagawa_general_2013].
-A large portion of this explanatory power came from the random effects, particularly for models of conspecific pollen. 
-The marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained by just the fixed effects, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models.
-
-We tested two structures for the random effects. 
+We then examined the potential roles played by four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality) play in pollen deposition. 
+<!-- Together these variables can describe the niche that plants might occupy in the context of competition for pollination.  -->
+We found that our models of pollen deposition had high explanatory power (the coefficient of determination R^2^ ranged between `r min(r2_values$r2c_min)` and `r max(r2_values$r2c_max)`) although a large portion of the explanatory power came from the random effects (Table \@ref(S-tab:table-R2)).
 As determined by AICc, the random structure best supported by the data was the one that fit an intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community they belong to).

### 2019-03-14 paper/supp-info.Rmd
Move R2 details to the supp info from the msc to save space

@@
 
+```{r table-R2, results="asis"}
+drake::loadd(r2_values)
+
+r2_values %>%
+  dplyr::select(r2c_mean, r2c_min, r2c_max, r2m_mean, r2m_min, r2m_max) %>%
+  knitr::kable("latex", 
+               col.names = c(rep(c("mean", "min", "max"), times = 2)), 
+               caption = "Coefficient of determination $R^2$ of the most parsimonious pollen deposition models (those with the lowest AICc).
+The marginal coefficient of determination describes the proportion of variance explained by just the fixed effects.",
+               booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::add_header_above(c("conditional $R^2_{(c)}$" = 3,
+                                 "marginal $R^2_{(m)}$" = 3), 
+                               escape = FALSE) %>%
+  kableExtra::group_rows(index = c("conspecific pollen" = 1, 
+                                   "heterospecific pollen" = 1))
+```
+
 ```{r table-aic-random-models, results= 'asis'}

### 2019-03-14 paper/manuscript.Rmd
Move collinearity results to its own paragraph

@@
 
+We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
+That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
+Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
+However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
+This indicates that, although there is a positive association between visit effectiveness and the *absolute* amount of conspecific pollen, there is a negative relationship with the *relative* amount of conspecific relative to heterospecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
+In contrast, a plants' relative abundance had a negative effect on the absolute amount of conspecific pollen, but the mean difference between the coefficients in the models indicates a positive association with the relatvie amount of conspecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
+The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the absolute and relative amount of conspecific pollen deposited. 
+Finally, the number of shared pollinators had a negative and neutral association with conspecific and heterospecific pollen, but these impacts were small when compared to the other variables.
+
+Overall, collinearity did not influence our findings qualitatively.
+Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
+One exception was visit effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations (all with relatively low AICc support).
+
 ```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=6.5/2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
@@
 ```
-
-We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
-That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
-Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
-However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
-This indicates that, although there is a positive association between visit effectiveness and the *absolute* amount of conspecific pollen, there is a negative relationship with the *relative* amount of conspecific relative to heterospecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
-In contrast, a plants' relative abundance had a negative effect on the absolute amount of conspecific pollen, but the mean difference between the coefficients in the models indicates a positive association with the relatvie amount of conspecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
-The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the absolute and relative amount of conspecific pollen deposited. 
-Finally, the number of shared pollinators had a negative association with both the absolute and relative amounts of conspecific pollen deposited, but these impacts were small when compared to the other variables.
-Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)), indicating that collinearity did not influence our findings qualitatively.
 

### 2019-03-14 paper/supp-info.Rmd
Make correlation figure in supp info a bit taller

@@
 
-```{r fig-correlation, fig.height = 4.5, fig.cap = "Corelation between the explanatory variables included in the statistical models.", eval=T}
+```{r fig-correlation, fig.height = 5, fig.cap = "Corelation between the explanatory variables included in the statistical models.", eval=T}
 drake::readd(fig_correlation)

### 2019-03-14 main.R
Ignore some more lines when counting words in the manuscript

@@ -210,7 +210,7 @@ reporting_plan <- drake_plan(
   abstract = readLines(file_in("./paper/abstract.md")),
   acknowledgements = readLines(file_in("./paper/acknowledgements.md")),
   abs_wordcount = count_words(file_in("paper/abstract.md")),
-  msc_wordcount = count_words(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:89),
+  msc_wordcount = count_words(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:100),
   render_pdf(knitr_in('paper/supp-info.Rmd'), file_out('paper/supp-info.pdf'), clean_md = FALSE),
   render_pdf(knitr_in('paper/manuscript.Rmd'), file_out('paper/manuscript.pdf'), clean_md = FALSE)
   )

### 2019-03-14 paper/manuscript.Rmd
Some more extra edits to the discussion based on Jasons suggestions

@@
 
-We used a PCA of the analysed species to investigate whether plant's niche of competition for pollination are similar across communities or whether they are flexible, and therefore a reflection of the community context.
-The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
-The first component was dominated by changes in visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality.
-When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
-Indeed, when we measured the median distance between the plants coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` analysed species (Figure \@ref(fig:fig-pca)c).
-
 ```{r fig-pca, fig.width=3.25, fig.height=6.65, fig.cap="**The flexibility of plant strategies**.
@@
 
+We used a PCA of the analysed species to investigate whether plant's niche of competition for pollination are similar across communities or whether they are flexible, and therefore a reflection of the community context.
+The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
+The first component was dominated by changes in visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality.
+When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
+Indeed, when we measured the median distance between the plants coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` analysed species (Figure \@ref(fig:fig-pca)c).
+
 # Discussion
@@
 Here we show that the prevalence of neutral and competitive effects of animal-mediated pollination can be at least partially explained by the trade-offs that minimising competition can involve.
+
 These trade-offs were most evident in precisely the factors that most strongly modulate pollen deposition. 
 Specifically, we found that the factors related to the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition.
-At the same time, receiving high visitation increases the absolute levels of conspecific pollen deposition but increasses heterospeicific deposition to a greater extent even when the visitors are likely carry a high proportion of conspecific pollen.
+At the same time, receiving high visitation increases the absolute levels of conspecific pollen deposition but increasses heterospeicific deposition to a greater extent---even when the visitors are likely carry a high proportion of conspecific pollen.
 Similarly, being abundant reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
-Multiple studies recognise the importance of visitation and abundance to competition for pollination, however, some suggest a positive effect on the pollination service while some others a negative one [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008].
-Our results corroborate the importance of these two factors, and show that the contrsating results obtained by earlier studies could be explained by the trade-offs involved.
+Multiple studies recognise the importance of visitation and abundance to competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
+Our results strongly corroborate the importance of these two factors but also suggest that [because visitation, pollen production and abundance are correlated; @sargent_role_2006], plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition to minimise competition for pollination.
 
-Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition to minimise competition for pollination.
+Further evidence of the complexity involved in achieving a balance between costs and benefits can be found when we examine the other two factors analysed in our models. 
+For instance, the networks we studied represent only a snapshot of the community dynamics. 
+While we show that being a specialist and sharing no pollinators might be preferable in the short term, over long periods of time there could be a risk associated to a plant having no pollinators. 
+Hence, is likely that plants need to compensate this risk for the costs of sharing pollinators. 
+One possible evolutionary strategt is having original traits as it’s commonly thought that species that are further from others in trait space suffer reduced competition. 
+Yet, there are two possible caveats to this strategy that highlight the interrelatedness of the ecological factors. 
+First, in a mutualism context, it is also possible that this could come at the cost of being less ‘apparent’ to pollinators. 
+Second, the usuallly negative, relationship between trait originality and generalism has been shown to be dependent on abundance [@coux_linking_2016], with generalist being able to have original traits when they are abundant enough to proviude a valuable reward to make it worth to pollinators.
+Overall, competition for pollination niche a plant species occupies seems to be dictated by the trade-offs between
+
+The two other factors we analysed, did not exhibit a pollination trade-off: functional originallity was generally benefitial, while sharing pollinators was generally detrimental to pollen deposition.
+Somewhat surprisingly, these two factors had considerably lower explanatory power in the models of pollen deposition when compared to visits and abundance. 
+This does not necessarily imply that these variables are unimportant to competition for pollination. 
+Instead, it is possible that the processes that underlay these strategies might be more complex than what our study was able to capture.
+
+Yet again, the interelatedness of the ecological factors and the fine balance between conspecific and heterospecific pollen is highlighted as @coux_linking_2016 showed that plants can be generalists *and* have original traits only when they are abundant
+
+This apparency problem could be overcome if you’re abundant and provide a valuable enough reward to make it worth pollinators while to develop a search image for you.
+
 The relatively broad distribution of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
@@
 
-The two other strategies we analysed involved a smaller trade-off than the abundance or visit efficacy. 
-Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be beneficial to both the quantity and quality of pollination.
-Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
-This does not necessarily imply that these variables are unimportant to pollen deposition. 
-Instead, it is possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
+<!-- The two other factors we analysed, functional originality and the number of involved a smaller trade-off than the abundance or visit efficacy.  -->
+<!-- Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be beneficial to both the quantity and quality of pollination.
+-->
+<!-- Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition.  -->
+<!-- This does not necessarily imply that these variables are unimportant to pollen deposition.  -->
+<!-- Instead, it is possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture.  -->
 Particularly so for conspecific pollen deposition, which was harder to predict than heterospecific pollen. 

### 2019-03-17 paper/manuscript.Rmd
Add full initials to my name
Complete edits to discussion

--- 2019-03-14 paper/manuscript.Rmd
@@
 title: "The pollination trade-off"
-author: "Fernando Cagua^1^, Hugo J. Marrero^2^, Jason M. Tylianakis^1^, Daniel B. Stouffer^1^"
+author: "E. Fernando Cagua^1^, Hugo J. Marrero^2^, Jason M. Tylianakis^1^, Daniel B. Stouffer^1^"
 bibliography: phd-bibliography/pollen-competition.bib
@@
 Here we show that the prevalence of neutral and competitive effects of animal-mediated pollination can be at least partially explained by the trade-offs that minimising competition can involve.
+
 These trade-offs were most evident in precisely the factors that most strongly modulate pollen deposition. 
 Specifically, we found that the factors related to the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition.
-At the same time, receiving high visitation increases the absolute levels of conspecific pollen deposition but increasses heterospeicific deposition to a greater extent even when the visitors are likely carry a high proportion of conspecific pollen.
+At the same time, receiving high visitation increases the absolute levels of conspecific pollen deposition but increasses heterospeicific deposition to a greater extent---even when the visitors are likely carry a high proportion of conspecific pollen.
 Similarly, being abundant reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
-Multiple studies recognise the importance of visitation and abundance to competition for pollination, however, some suggest a positive effect on the pollination service while some others a negative one [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008].
-Our results corroborate the importance of these two factors, and show that the contrsating results obtained by earlier studies could be explained by the trade-offs involved.
+Multiple studies recognise the importance of visitation and abundance to competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
+Our results strongly corroborate the importance of these two factors but also suggest that [because visitation, pollen production and abundance are correlated; @sargent_role_2006], plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition to minimise competition for pollination.
 
-Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition to minimise competition for pollination.
-The relatively broad distribution of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
-Indeed, some plant species experience a large reduction in seed set due to heterospecific pollen deposition, while others are relatively insensitive to heterospecific pollen but greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
+Further evidence of the intricacies of balancing costs and benefits can be found when we examine the other two factors analysed in our models. 
+We show that being a specialist and sharing no pollinators might be preferable in the short term (as it is generally detrimental to pollen deposition). 
+However, over long periods of time there could be a risk associated to a specialist plant having no pollinators. 
+Hence, is likely that, to ensure long term survival, plants also need to balance this risk with the costs of sharing pollinators. 
+One possible solution is to share pollinators *and* have original traits---as we show that trait originallity is generally benefitial to pollen deposition and it’s commonly thought that species that are further from others in trait space suffer reduced competition.
+Yet again, there are two possible caveats to this strategy that highlight the interrelatedness of the ecological factors. 
+First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators. 
+Second, the usuallly negative, relationship between originality and generalism has been shown depend on the plants abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make it worth to pollinators.
 
-The two other strategies we analysed involved a smaller trade-off than the abundance or visit efficacy. 
-Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be beneficial to both the quantity and quality of pollination.
-Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
-This does not necessarily imply that these variables are unimportant to pollen deposition. 
-Instead, it is possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
-Particularly so for conspecific pollen deposition, which was harder to predict than heterospecific pollen. 
-For instance, having distinct traits, for example through phenology differentiation, might have a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities (ref).
-In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
-Alternatively, other factors that we were unable to measure, like pollinator behaviour and densities [@ye_competition_2014; @flanagan_effects_2011; @melissas_2019?] or the spatial context [@cariveau_spatially_2009], can also shape the way sharing pollinators affect the pollination service.
-
-\R{strategies}Regardless of the specific factors involved it is clear, however, that the community context has a very important effect on the way plant species respond to competition for pollination. 
-First, in the models of pollen deposition, the random structure that allowed plants of the same species to have different intercepts across communities was much better supported by the data than the structure that fixed the intercept for a plant species irrespective of the community.
-Second, in a large majority of cases, the strategies that a species uses across communities are not more similar to each other than what would be expected at random. 
-Lit? Context?
+How precisely plants balance the costs and benefits in the short and the long term likely depends on the species sensitivity to different risks but also, as we show here, on the community it belongs to.
+For instance, a plant species that experience a large reduction in seed set due to heterospecific pollen deposition might be better off by sharing few pollinators, while sharing pollinators makes more sense for those mainly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
+Nevertheless, the diversity of the facilitation/competition outcomes across communities we observed and the relevance of random effects in our models suggests that the community context has a very important effect on the way plant species respond to competition for pollination beyond species identity.
+Perhaps overgeneralising, some plant families (Asteraceae for example) are often generalists in their communities, others (Orchidaceae) are known to be more commonly specialised. 
+While it is possible, from an evolutionary perspective, that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history, we show that most plant species are still flexible enough to adopt markedly different niches in different communities.
+From a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
+Our results highlight the difficulties involved with predicting wether the introduced plant species will facilitate or compete with neighbours. 
+This is so because the outcome might depend not only on the particular niche each species occupies in a particular community, but also on other factors that we were unable to measure [e.g.
+pollinator behaviour and densities or spatial context; @ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009].
+However, our results also suggest that introduced species are more likely to be benefitial if they have differing traits to local plants. 
+<!-- cite melissa's paper if available before publication -->
 

### 2019-03-17 paper/draft-info.Rmd
Move draft info to its own file

--- 2019-03-14 paper/manuscript.Rmd
@@
 title: "The pollination trade-off"
-author: "Fernando Cagua^1^, Hugo J. Marrero^2^, Jason M. Tylianakis^1^, Daniel B. Stouffer^1^"
+subtitle: "Draft information"
+author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
 bibliography: phd-bibliography/pollen-competition.bib
@@
   - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
-  - \externaldocument[S-]{supp-info}
 ---
 
-\linenumbers
-\doublespacing
-
-^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand
-
-^2^ Centro de Recursos Naturales Renovables de las Zonas Semiáridas, CONICET, Camino de la Carrindanga Km. 7, 8000 Bahía Blanca, Argentina
-
-**Author for correspondence:** E.
-Fernando Cagua (efc29@uclive.ac.nz) - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
-                      warning = FALSE)
-```
-
-```{r draft-details}
-drake::loadd(msc_wordcount, abs_wordcount)
-```
-
-**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters, approx.
-`r format(round(msc_wordcount$n_words_stri/10)*10, big.mark = ",")` words (excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` min.
-reading time.
-
-**Abstract length:** `r abs_wordcount$n_words_stri` words.
-
-\clearpage
-
-# Draft Info
+\onehalfspacing
 
@@
 * Show niche points for all species and not only those in two communities or more
+* Added the following elements to the disussion: 
+    * That our networks are a snapshot
+    * How the degree-trait originality relationship can be shaped by abundance
+    * How strategy could be a result of a specie's historical communities
+    * How attracting pollinators using flowering plants might work
 
@@
 --- *DBS says is OK to leave it out*
-
-\clearpage
-
-# Abstract
-
-`r paste(drake::readd(abstract), collapse = "")`
-
-**Keywords:** X, Y, Z
-
-\clearpage
-
-# Introduction
-
-Animal pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011].
-<!-- FDO: Asked coauthors for a reference for the following statement but no-one provided. Therefore removing -->
-Alongside the direct mutualisms between plants and their pollinators, biodiversity can be supported as a result of inter-species "facilitation"—the positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008].
-This inter-species facilitation is able to promote species coexistence by offsetting the effects of direct resource competition [@stachowicz_mutualism_2001]. 
-Indeed, studies at the core of our current theoretical knowledge of mutualisms predict that the maximum number of coexisting species is achieved when the number of shared mutualistic partners is maximised in a community [@bastolla_architecture_2009].
-
-However, in natural communities, plants rarely share all available pollinators.
-One explanation is that plants are effectively competing for mutualistic partners because there is a *trade-off* between the benefits gained from maximising the number of mutualistic partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
-It has been clear for a long time [both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970] that when competition for pollination is strong enough, it can be detrimental to plants' fitness.
-In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000]. 
-It is less clear, however, how exactly ecological differentiation, in turn, affect the trade-off between facilitation and competition that is involved in the pollination service.
-
-There are two main mechanisms through which competition for pollinators can affect plant fertilization [@morales_interspecific_2008]. 
-The first is intraspecific pollen transfer. 
-This happens, for example, when plants with distinctively attractive flowers might reduce the number of visits---and hence the amount of *conspecific pollen* deposited by animals---to those less attractive neighbouring plants [@yang_pollinator_2011].
-The second is intraspecific pollen transfer and occurs when plants share pollination partners. 
-In that case, even receiving a visit might not necessarly translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or pollen from the focal plant might be lost to different species.
-Generally speaking, the higher the amount of conspecific pollen (both in absulute terms and relative to heterospecific pollen) the better the pollination service received by the focal plant.
-These two mechanisms of competition, by definition, occur at the community scale. 
-However, with few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the deposition of conspecific and heterospecific pollen---and its relationship to competition vs.
-facilitation in pollination systems---is based on studies of two plant species.
-
-At the community scale the factors that determine the patterns of conspecific and heterospecific pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
-For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016].
-This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly (TODO: ref needed).
-If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase in species with a large number of interaction partners [@gibson_can_2012].
-Alternatively, it might also be the case that density (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
-Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both visits and pollinator "real state".
-In this case, a potential reduction the absolute amount of conspecific pollen received could be compensated by an increase amount relative to heterospecific pollen. 
-Altogether, it is clear that some ecological factors can influence pollen deposition and that these factors, in the specific context of pollination, could be used to roughly define a species *realised niche* in their community.
-However, the intertwined nature of these factors makes it hard to determine wether they favour or hinder the pollination service at the community level. 
-Moreover, their relative importance has not yet been empirically evaluated in natural plant communities.
-
-Here, we investigate competition for pollination at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
-**First**, we estimate the extent to which the net outcome of plants sharing polinators is facilitation or competition. 
-If facilitation is the primary outcome, we could expect two tings. 
-On the one hand, we could expect an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the amount of heterospecific pollen [@tur_evaluating_2016]. 
-The higher the deposition of conspecific pollen relative to heterospecific, the larger the slope of that relationship.
-On the other, we could also expect a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than is deposited due to self-pollination. 
-**Second**, we investigate the relative contribution that four ecological factors have on the pollination service. 
-Sepecifically, we hypothesize that competition (measured as absolute and relative conspecific pollen deposition) should increase for plants that share many pollination partners.
-However, we also hypothesize that other factors like the plant's functional originality, its relative abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
-**Third**, we examine how community context influences the way plants use these factors to minimise competition. 
-Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict the competition for pollination niche to be influenced by the local context.
-If plant strategy is not flexible across communities (TODO: ref needed), we could expect niches to be more similar within species than across species in the study. 
-On the contrary, if a species' strategy is flexible, we should expect plants to be able to occupy different niches in each community such that competition could be minimised regardless of the context.
-
-# Methods
-
-We collected data from eleven co-flowering plant communities and their pollinators in three locations in the Argentinian Pampas. 
-These locations are distributed across a precipitation gradient with a humid temperate climate in the eastern Flooding Pampas and becoming drier as one moves inland and westward towards the Pampean Grasslands.
-This precipitation gradient generatesd a natural gradient of network architecture which allowed us to examine the generality of our findings. 
-In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where we were only able to sample one restored fragment due to the lack of available sites.
-
-## Competition vs. facilitation
-
-Our first objective was to identify whether the outcome of plants sharing polinators at the community level is facilitation or competition. 
-The first line of evidence can be found via the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
-This is because heterospecific pollen can be seen as an unavoidable cost that plants must pay for receiving conspecific pollen from shared pollinators. 
-A negative relationship (when shared pollinators increase heterospecific pollen loads and decrease conspecific loads) may indicate that competition for pollination is strong. 
-This negative relationship could arise, for example, when another, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; @lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
-In contrast, a positive relationship is what would be observed when facilitation is the dominant outcome. 
-For example, when the abundance of shared pollinators is positively influenced by floral resources, these positive effects ripple through the mutualistic network in a chain of positive feedback loops [@liao_presence_2011].
-
-The second line of evidence can be obtained by examining the difference between the amount of conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination. 
-Self-pollination can be favourable to plant reproduction when competition for pollination is strong because it provides insurance against poor pollination service [@kalisz_benefits_2003]. 
-If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented could be higher than when floral visits are allowed.
-In contrast, the opposite pattern may indicate that plants benefit from having pollen delivered directly to the stigma by animals. 
-We did not specifically test the effect of pollen viability or the extent to which self-pollen vs.
-pollen from a conspecific may differ in their value for fertilization which can be important factors (TODO: ref needed).
-However, it is reasonable to expect that the difference between outcross and self-pollen may be generally relevant and particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy) (TODO: ref needed).
-
-### Data collection
-
-In each of the studied communities, we quantified pollen deposition in a subset of plant species between December 2010 and February 2011. 
-This subset comprised between three and nine common insect-pollinated (entomophilous) plant species that were flowering during the sampling period (see Figure \@ref(fig:fig-trade-off-predictions)a). 
-We chose plant species such that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
-Briefly, in each of the selected plants, we removed all flowers leaving only buds that were expected to go into florescence on the next day. 
-Approximately a quarter of these buds were bagged to prevent animal pollination. 
-Two days after inflorescence, we counted the pollen grains in the remaining flowers' pistils, classified them between conspecific and heterospecific pollen, and calculated the number of pollen grains per stigma in each flower.
-More details about the study sites, data collection, and laboratory protocols can be found in @marrero_agricultural_2016.
-
-### Data analysis
-
-To evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution [@tur_evaluating_2016]. 
-In this model, the number conspecific pollen grains per stigma was the response variable and the number of heterospecific grains the predictor (the number of stigmas sampled from the flower was added as an offset term).
-The slope and intercept of this relationship were allowed to differ between plant species within each community, which were modelled as a random effect. 
-Models were fitted using the function `glmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]. 
-To compare the conspecific pollen deposited with and without animal-mediated pollination, we followed the same approach as above. 
-In this case, however, the predictor was the treatment (wether the flower was bagged or unbagged) instead of the number of heterospecific grains.
-
-## Ecological constraints the pollination service
-
-Our second objective was to investigate the relative contribution of different factors that describe the plant competition for pollination niche to the pollination service. 
-Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plants abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them (see *Data Analysis* section below for more details), and (*iv*) the plants functional originality (add ref).
-<!-- Here, we define visit effectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
--->
-
-### Data collection
-
-To obtain the number of shared pollinators for each species, we collected data to construct qualitative and quantitative pollination networks. 
-Qualitative networks were constructed based on two-hour observations of floral visits in each fragment. 
-Quantitative networks were constructed using two 50 m randomly located transects in each fragment. 
-We counted and collected all floral visitors found in a 2 m wide strip while walking at a pace of 10 m per minute [@marrero_effect_2014; @memmott_structure_1999]. 
-We visited the transects each month between November 2010 and March 2011. 
-To obtain plant abundance, we counted all units of floral attraction found during an independent sampling of the transects used to construct the quantitative visitation networks. 
-To estimate visit effectiveness we need to construct pollen transfer networks in addition to the visitation networks. 
-To construct the transfer networks, we examined the pollen loads present on the floral visitors collected [@marrero_exotic_2017]. 
-When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level when possible and to pollen complexes when it was not. 
-When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
-Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region.
-We used those traits because they were the only ones available... (TODO: Add a better justification for the traits used)
-More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014 and 2017).
-
-### Data analysis
-
-We investigated the impact of the ecological factors on pollination services.
-Generally speaking, the more conspecific pollen deposited in stigmas, both absolutely and relative to heterospecific pollen, the better the pollination service. 
-Specifically, we used two sets of linear mixed models (LMM) in which the response variables are the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination.
-In general, using LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) offered better fit than a GLMM with Poisson (or quasipoisson) error structure.
-Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].
-
-Because the amount of deposited pollen can vary widely across species, and potentially also across communities, we evaluated two possible structures for the random effects: one that includes a random intercept for plant species, and one that treats measures from species across different communities as independent.
-We selected the best random structure by comparing the median Akaike Information Criterion for small samples (AICc).
-
-As predictors in the models, we included the four ecological variables described above. 
-Specifically, we calculated the number of shared pollinators for each plant species by pooling data from the qualitative and quantitative pollination networks. 
-<!-- This variable is strongly correlated to the number of animal species a plant interacts with (the species degree).  -->
-To calculate the plants' relative abundance in their community, we simply aggregated floral counts for each species. 
-We then calculated the mean visit effectiveness. 
-We define the effectiveness of a visit by pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
-Because the number of shared pollinators, floral abundance, visitation, and pollen production roughly followed a power-law distribution, we log-transformed these three predictors before including them in the model.
-
-Finally, functional originality is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016].
-<!-- As phenology has been shown to be a key mechanism of niche differentiation among plants, we also  -->
-To include phenology we treated plant abundance in each of the survey months (November to March) as a "trait" in our analysis. 
-<!-- This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits.  -->
-Then we assigned the abundances a weight of 1/5 compared to other functional traits, this accounted for the non-independence of floral counts across months and effectively weights phenology equally to other traits.
-We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
-Finally, to facilitate comparison across the four continuous explanatory variables in our models, we rescaled them all to have a zero mean and unitary variance.
-
-To estimate the coefficients and to perform model selection and quantify the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with one hundred replicates.
-First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc (relative to the most likely model) for each bootstrap sample.
-As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our variables proportional to the likelihood of its candidate model.
-We "shrank" the estimated coefficient of potentially unimportant variables by setting their estimate to 0 when the variable was not included in the model. 
-Finally, we used these distributions of the model coefficients to estimate their mean impact on the pollination service (in terms of absoulte and relative conspecific pollen deposition). 
-Again, here we used bootstrap resampling to estimate the uncertainty around these means.
-
-## Flexibility of plant strategies
-
-Our last objective was to tease apart the plant strategies that might reduce competition and, importantly, how the community context influences these strategies. 
-If community context plays a relatively small role or the species strategy is inflexible we would expect plants of the same species to fill similar competition for pollination niches across different communities.
-Alternatively, if the community plays a large role and plants sttrategies are flexible, we should be able to observe differences in the niche a plant species occupies across communities. 
-First, we used a principal component analysis (PCA) of the four ecological variables. 
-We scaled variables across the whole study to ensure that the PCA space does not change acording to the species present in each community. 
-We define a species' niche in a community as its coordinates in PCA space. 
-For each species that was present in two or more communities, we then calculated (*i*) the median distance between the strategies that the species uses in different communities and (*ii*) the area of the convex hull defined by these points in the first two principal components (only for species present in three or more communities).
-We then compared the magnitude of these two metrics to those obtained with 99 Monte Carlo randomizations in which we replaced the strategy of the focal plant species by that of another randomly selected species in the dataset.
-
-# Results
-
-## Competition vs. facilitation
-
-```{r facilitation-random-model-stats, echo = F}
-drake::loadd(facilitation_plot_df)
-
-# count number of species with positive and negative slopes
-counts_facilitation_slope <- facilitation_plot_df %>%
-  dplyr::group_by(effect_category) %>%
-  dplyr::count() %>%
-  dplyr::group_by() %>%
-  dplyr::mutate(np = nn/sum(nn), 
-                np = round_preserve_sum(np, 2)*100)
-
-# species with both positive and negative relationships
-get_sp_with_both_pos_neg <- . %>%
-  dplyr::filter(effect_category != "neutral") %>%
-  dplyr::group_by(plant_name) %>%
-  dplyr::summarise(both = dplyr::n_distinct(effect_category) > 1) %>%
-  dplyr::filter(both)
-
-# Get list of species with both positive and negative slopes
-sp_both_pos_neg <- facilitation_plot_df %>%
-  get_sp_with_both_pos_neg() %>%
-  dplyr::mutate(plant_name = as.character(plant_name)) %>%
-  dplyr::arrange(plant_name) %>%
-  dplyr::mutate(plant_name = stringr::str_extract(plant_name,
-                                                  "[A-Z]\\w+\\s[a-z]\\w+"), 
-                plant_label = paste0("*", plant_name, "*")) 
-# Human readable list of species with both positive and negative slopes
-sp_both_pos_neg_names <- sp_both_pos_neg %$%
-  glue::collapse(plant_label, sep = ", ", last = ", and ")
-
-# equal number of negative and positive?
-equal_pos_neg <- counts_facilitation_slope$nn[1] == counts_facilitation_slope$nn[3]
-```
-
-We first examined the degree of facilitation/competition in natural communities.
-Specifically, we examined the slope of the relationship between the heterospecific and conspecific pollen deposited on stigmas of each species in a community.
-We found that overall neither facilitation nor competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
-Indeed, we found that the proportion of species that experienced a significantly positive or neggative relationship between heterospecific and conspecific pollen than neggative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)).
-Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
-For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that, the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others.
-Interestingly, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
-
-```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "**Competition vs.
-facilitation at the community level**.
-(a) Some species experience more competition for pollination than others.
-Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities.
-Significantly negative slopes (darkest shade) indicate that plants experience competition for animal-mediated pollination, while significantly positive slopes (lightest shade) indicate that facilitation is the predominant outcome.
-The number of plants analysed for each species is shown within brackets next to the species name.
-(b) Despite the variety of slopes, overall plants had more conspecific than heterospecific pollen deposited in their stigmas.
-(c) Generally, plants also had more pollen deposited in their stigmas when they were open to animal-mediated pollination than when they were closed.
-In all plots, error bars correspond to $\\pm$ the standard error (SE)."}
-# fig_random_slopes <- plot_random_slopes(facilitation_plot_df)
-# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
-# fig_con_con = plot_bagged_vs_open_conspecific(drake::readd(con_con_plot_df))
-# pdf(width = 6.5, height = 4)
-drake::loadd(fig_random_slopes)
-drake::loadd(fig_con_con)
-drake::loadd(fig_hetero_con)
-width_left <- 6.5*3/5
-bar_plot_width <- 0.325
-rw <- c(width_left - bar_plot_width,
-        bar_plot_width, 
-        6.5 - width_left - bar_plot_width,
-        bar_plot_width)
-left <- cowplot::plot_grid(
-  fig_hetero_con,
-  NULL,
-  fig_con_con[[1]],
-  fig_con_con[[2]],
-  ncol = 2, 
-  rel_widths = rw[c(3,4)], 
-  align = "h"
-)
-right <- cowplot::plot_grid(
-  fig_random_slopes[[1]],
-  fig_random_slopes[[2]], 
-  # ncol = 2, 
-  align = "h", 
-  rel_widths = rw[1:2]
-)
-cowplot::plot_grid(
-  right,
-  left,
-  ncol = 2,
-  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
-)
-# dev.off()
-```
-
-```{r facilitation-conspecific-stats}
-drake::loadd(con_con_plot_df)
-# overall counts of possitive/negative
-sp_con_con <- con_con_plot_df %>%
-  dplyr::group_by(effect_category) %>%
-  dplyr::count() %>%
-  dplyr::group_by() %>%
-  dplyr::mutate(np = n/sum(n), 
-                np = round_preserve_sum(np, 2)*100)
-# species with contrasting behaviours
-sp_con_both_pos_neg <- con_con_plot_df %>%
-  get_sp_with_both_pos_neg() %>%
-  dplyr::arrange(plant_name) %>%
-  dplyr::mutate(plant_label = dplyr::if_else(plant_name %in% sp_both_pos_neg$plant_name, shorten_sp_name(plant_name), plant_name),
-                plant_label = paste0("*", plant_label, "*"))
-```
-
-Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with that of those that were closed. 
-Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers (Table \@ref(S-tab:table-open-bagged-models-general)). 
-Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had significantly more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open (the difference was non-signifcant for the remainding `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
-Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both significantly positive and negative differences.
-
-## Ecological constraints in the pollination service
-
-```{r model-fit-statistics}
-drake::loadd(r2_values)
-```
-
-We then examined the potential roles played by four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality) play in pollen deposition. 
-<!-- Together these variables can describe the niche that plants might occupy in the context of competition for pollination.  -->
-We found that our models of pollen deposition had high explanatory power (the coefficient of determination R^2^ ranged between `r min(r2_values$r2c_min)` and `r max(r2_values$r2c_max)`) although a large portion of the explanatory power came from the random effects (Table \@ref(S-tab:table-R2)).
-As determined by AICc, the random structure best supported by the data was the one that fit an intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community they belong to).
-This structure was best for both the models of conspecific and heterospecific pollen (Table \@ref(S-tab:table-aic-random-models)).
-
-Of the four variables we considered, we found that a plant's mean visit effectiveness and abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
-Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
-
-We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
-That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
-Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
-However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
-This indicates that, although there is a positive association between visit effectiveness and the *absolute* amount of conspecific pollen, there is a negative relationship with the *relative* amount of conspecific relative to heterospecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
-In contrast, a plants' relative abundance had a negative effect on the absolute amount of conspecific pollen, but the mean difference between the coefficients in the models indicates a positive association with the relatvie amount of conspecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
-The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the absolute and relative amount of conspecific pollen deposited. 
-Finally, the number of shared pollinators had a negative and neutral association with conspecific and heterospecific pollen, but these impacts were small when compared to the other variables.
-
-Overall, collinearity did not influence our findings qualitatively.
-Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
-One exception was visit effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations (all with relatively low AICc support).
-
-```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=6.5/2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
-(a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
-Meanwhile, the number of shared pollinators was relatively unimportant.
-The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable.
-(b) The association between ecological variables and heterospecific pollen tended to align with their association with conspecific pollen.
-Visit effectiveness and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association.
-The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific and heterospecific pollen.
-(c) The end result of these associations is that only the plants' functional originality has a positive impact on both the absolute and relative amount of conspecific pollen deposition (relative to heterospecific pollen).
-The plot shows the model averaged mean effect ($\\pm$ SE)."}
-height1 <- 1
-height2 <- 1.28
-# pdf(width = 3.25 , height = sum(c(height1, height2))*2)
-# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
-# width_imps <- 6.5/5*2
-# mult <- 2.455 # for 2/3 is xx, for 3/5 is 2.355
-# width_coef_1 <- (6.5 - width_imp) / (1 + mult)
-# width_coef_2 <- 5.6 - width_imp - width_coef_1
-# fig_var_importance <- plot_variable_importance(variable_importance)
-drake::loadd(fig_var_importance)
-drake::loadd(fig_coef_avg)
-drake::loadd(fig_coefficient_averages)
-
-var_impo <- cowplot::plot_grid(
-  fig_var_importance[[1]],
-  fig_var_importance[[3]],
-  fig_var_importance[[2]],
-  ncol = 3,
-  rel_widths = c(1,0.75,1),
-  align = "h"
-)
-
-bottom <- cowplot::plot_grid(
-  fig_coef_avg[[1]],
-  fig_coef_avg[[3]],
-  fig_coef_avg[[2]],
-  rel_widths = c(1,0.75,1), 
-  ncol = 3,
-  align = "h"
-)
-
-cowplot::plot_grid(
-  var_impo, 
-  fig_coefficient_averages,
-  bottom, 
-  ncol = 1, 
-  rel_heights = c(height1, height1 + height2, height2)
-)
-
-# dev.off()
-```
-
-## Flexibility of plant strategies
-
-```{r pca-stats}
-drake::loadd(pcas)
-drake::loadd(permanova_plant_distances)
-chosen_threshold <- 0
-this_pca <- pcas %>%
-    purrr::keep(~ .$call$X$pca_type[1] == "across") %>%
-    purrr::keep(~ .$call$X$threshold[1] == chosen_threshold) %>%
-    extract2(1)
-median_distances <- permanova_plant_distances %>% 
-  dplyr::filter(na_threshold == 0, metric == "median_dist", !is.na(value)) %$%
-  value
-```
-
-We used a PCA of the analysed species to investigate whether plant's niche of competition for pollination are similar across communities or whether they are flexible, and therefore a reflection of the community context.
-The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
-The first component was dominated by changes in visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality.
-When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
-Indeed, when we measured the median distance between the plants coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` analysed species (Figure \@ref(fig:fig-pca)c).
-
-```{r fig-pca, fig.width=3.25, fig.height=6.65, fig.cap="**The flexibility of plant strategies**.
-(a) The two first components explain a large proportion of the total variance.
-(b) When plants that were sampled in more than one community are plotted with these two components, we observe that points, which represent the strategy (the particular combination of ecological variables) of a species in a community do not seem to be grouped by plant species.
-(c) This was confirmed using Monte Carlo randomizations of the median distance between strategies of a plant species.
-Only one of the examined species had strategies that were more tightly connected than what would be expected at random."}
-height0 <- 1.55
-height1 <- 2.7
-height2 <- 2.4
-strategy_fig_height <- sum(height0, height1, height2)
-# fig_pca <- plot_pca(pcas, chosen_threshold = 0)
-# fig_distances <- plot_permanova_dist(permanova_plant_distances, permanova_site_distances)
-# fig_pca_contrib <- plot_pca_variances_and_contributions(pcas, chosen_threshold = 0)
-# pdf(width = 3.25, height = strategy_fig_height)
-drake::loadd(fig_pca_contrib)
-drake::loadd(fig_pca)
-drake::loadd(fig_distances)
-cowplot::plot_grid(
-  fig_pca_contrib,
-  fig_pca,
-  fig_distances,
-  ncol = 1, 
-  rel_heights = c(height0, height1, height2), 
-  align = "v"
-)
-# dev.off()
-```
-
-# Discussion
-
-All else being equal, our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
-First, we found that the costs of pollinator sharing are pervasive. 
-In particular, we found that a significant proportion of species experiences overall neutral or competitive effects from animal-mediated pollination. 
-Second, we found that multiple ecological factors can modulate the intensity of this competition; however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these factors are likely to involve a trade-off between the quantity and quality of pollination.
-Third, we found that the way these factors influence competition is strongly shaped by the community context, this is, if collectively these factors are used to define a niche of competition for pollination, the same plant species can occupy dramatically different niches depending on the community it belongs to.
-
-Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that net facilitation is only experienced by a fraction of species in a community. 
-A recent study also suggested a wide range of outcomes in a multi-species context [@tur_evaluating_2016]. 
-However, the factors explaining why some species experience more competition than others were not understood. 
-Here we show that the prevalence of neutral and competitive effects of animal-mediated pollination can be at least partially explained by the trade-offs that minimising competition can involve.  
-These trade-offs were most evident in precisely the factors that most strongly modulate pollen deposition. 
-Specifically, we found that the factors related to the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition.
-At the same time, receiving high visitation increases the absolute levels of conspecific pollen deposition but increasses heterospeicific deposition to a greater extent even when the visitors are likely carry a high proportion of conspecific pollen.
-Similarly, being abundant reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
-Multiple studies recognise the importance of visitation and abundance to competition for pollination, however, some suggest a positive effect on the pollination service while some others a negative one [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008].
-Our results corroborate the importance of these two factors, and show that the contrsating results obtained by earlier studies could be explained by the trade-offs involved.
-
-Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition to minimise competition for pollination.
-The relatively broad distribution of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
-Indeed, some plant species experience a large reduction in seed set due to heterospecific pollen deposition, while others are relatively insensitive to heterospecific pollen but greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
-
-The two other strategies we analysed involved a smaller trade-off than the abundance or visit efficacy. 
-Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be beneficial to both the quantity and quality of pollination.
-Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
-This does not necessarily imply that these variables are unimportant to pollen deposition. 
-Instead, it is possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
-Particularly so for conspecific pollen deposition, which was harder to predict than heterospecific pollen. 
-For instance, having distinct traits, for example through phenology differentiation, might have a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities (ref).
-In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
-Alternatively, other factors that we were unable to measure, like pollinator behaviour and densities [@ye_competition_2014; @flanagan_effects_2011; @melissas_2019?] or the spatial context [@cariveau_spatially_2009], can also shape the way sharing pollinators affect the pollination service.
-
-\R{strategies}Regardless of the specific factors involved it is clear, however, that the community context has a very important effect on the way plant species respond to competition for pollination. 
-First, in the models of pollen deposition, the random structure that allowed plants of the same species to have different intercepts across communities was much better supported by the data than the structure that fixed the intercept for a plant species irrespective of the community.
-Second, in a large majority of cases, the strategies that a species uses across communities are not more similar to each other than what would be expected at random. 
-Lit? Context?
-
-## Conclusion
-
-Here we show that competition for pollination is pervasive in ecological communities and that its effect on plant species strongly influenced by the community context. 
-Our results suggest that at the community level, the strategies that plants adopt to minimise competition require reaching a fine balancing act between the quantity and quality of pollination. 
-In particular, strategies that promote dominance of the species in its community (in terms of abundance, visitation and participation in the pollen pool) had the largest impacts on pollen deposition but also the largest trade-offs between increasing deposition of conspecific pollen and reducing that of heterospecific pollen.
-Contrastingly, strategies that increase niche differentiation (functional originality and specialization) were positive to both the quantity and quality of pollination, but its effect was comparatively small compared to strategies of dominance.
-Remarkably, the particular strategy a plant uses is strongly shaped by its context and hence can be dramatically different in each of the communities it is part of. 
-[Wider application? Catchy closing line ideas?]
-
-# Acknowledgements
-
-`r paste(drake::readd(acknowledgements), collapse = "")`
-
-# References

### 2019-03-17 paper/manuscript.Rmd
Move draft info to its own file

@@
 **Abstract length:** `r abs_wordcount$n_words_stri` words.
-
-\clearpage
-
-# Draft Info
-
-## Changes
-
-* Now using `docker` to manage project dependencies. Image is now available on dockerhub efcaguab/pollen-competition.
-* Removing *quantity* and *quality* of pollination in favour of the plain metrics of *conspecific* and *heterospecific* pollen deposition. 
-* Rewording the plant strategies idea as it was confussing.
-Now the combination of ecological variables (number shared pol., abundance, visitation patterns, and traits) define a species *realised niche* (this was previoulsy called the plant strategy).
-Plants that can have very different realised niches across different communities have a *flexible strategy* (this was previously called strategy as well).
-* Manuscript formatted for submission to Ecology Letters.
-* Sticking to past tense throughout the methods.
-* GLMM to fit slope of heterospecific-conspecific pollen relationship tests all communities at once (it was a model per community).
-Response variable is the number of grains (it was number of grains per stigma) and the (log) number of stigmas in the flowers has been included as an offset term.
-* Using a similar approach to compare conspecific pollen deposited in open and bagged flowers (I used a series of Mann-Withney U tests before)
-* Added facilitation model results tables in the Supplementary Information
-* Made Figure 2 (model of enviornmental factors) one-column
-* Applied a green palette to all figures. Improves legibility when looking at it in a screen an performance when printed in greyscale is maintained
-* Show niche points for all species and not only those in two communities or more
-
-## Todo
-
-* Polish discussion, will appreciate input here. 
-* Polish supp. info.
-* Spell-check everything & check that reference list is correct.
-* I think its not supper clear in the manuscript what is meant by a plant strategy. Need to re-check in the next iteration.
-
-## Questions
-
-Feel free to come back here after you've read the manuscript. Thanks!
-
-* Minor point: DBS thinks that normally one would use the technical word and then put the definition in parenthesis.
-In a previous revision I got from JMT that it's better to lead with the concept and then add the jargon last.
-Examples: *"...due to a temporary separation in the maturation of sexes (dichogamy)"*, *"...common insect-pollinated (entomophilous) species"*.
-
-* Journal? --- *Hugo says PNAS, Proceedings B and Science. No answer from other coauthors*
-* I think the story is still a bit disperse.
-Will appreciate feedback on identifying the most important/exciting findings to tie the others around it.
-So far the central topic is scaling up of competition to the community level.
---- *No particular feedback received*
-* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}? --- *No particicular feedback received*
-* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private? --- *It is OK*
-* In Figure \@ref(fig:fig-trade-off-predictions)a, I determine if the slope is significantly positive or negative by checking whether the standard errors cross 0.
-Should it be 2 times SE?
-Should all other error bars in Figure \@ref(fig:fig-trade-off-predictions) be 2 times SE?
---- *No particular feedback received*
-* What do you think about the quantity/quality discourse now?
-I'm still unconvinced.
-Maybe I should just go for relationship conspecific/heterospecific instead of quality?
-That would mean that Figure \@ref(fig:fig-average-qual-quant)c would just need the right panel.
-Cause the left is just almost the same as Figure \@ref(fig:fig-average-qual-quant)b, except that it includes models in which the variable was not present and hence "shrinks" the model averaged estimate.
---- *Daniel advocates for getting rid of quantity/quality and go for conspecific/conspecific proportion*
-* Unsure of whether in Figure \@ref(fig:fig-pca)a, it would be better to display the contribution of each component to total variance instead of the cummulative contribution.
---- *Add info to left of the figure*
-* I'm not very happy with the way the third hypothesis is described in the intro (\lr{third-hypothesis}). I would appreciate ideas to rephrase it clearly
-* Does the paragraph in \lr{disc-facil-comp} needs more meat? Any suggestions?
-* My background in the topic is limited, would be grateful if you could point me out to key papers that could be used to put some context to the finding of the "flexibility" of plants strategies (paragraph in \lr{strategies}) --- *DBS argues that I say that strategies minimise competition but I never show that, only show that strategies change.
-Need to think about that*
-* Part of the discussion before revolved about the fact that degree is commonly used in theoretical models of mutualism to adjust the mutualistic benefit of generalist species.
-I've removed it because I think the discussion is already a bit long and didn't fit that nicely in the story.
-You think it should be included?
---- *DBS says is OK to leave it out*
 

### 2019-03-17 main.R

@@ -212,6 +212,7 @@ reporting_plan <- drake_plan(
   abs_wordcount = count_words(file_in("paper/abstract.md")),
   msc_wordcount = count_words(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:100),
   render_pdf(knitr_in('paper/supp-info.Rmd'), file_out('paper/supp-info.pdf'), clean_md = FALSE),
+  render_pdf(file_in('paper/draft-info.Rmd'), file_out('paper/draft-info.pdf'), clean_md = FALSE),
   render_pdf(knitr_in('paper/manuscript.Rmd'), file_out('paper/manuscript.pdf'), clean_md = FALSE)
   )
 

### 2019-03-17 paper/manuscript.Rmd
Finish off conclusion

@@
 
-## Conclusion
-
-Here we show that competition for pollination is pervasive in ecological communities and that its effect on plant species strongly influenced by the community context. 
-Our results suggest that at the community level, the strategies that plants adopt to minimise competition require reaching a fine balancing act between the quantity and quality of pollination. 
-In particular, strategies that promote dominance of the species in its community (in terms of abundance, visitation and participation in the pollen pool) had the largest impacts on pollen deposition but also the largest trade-offs between increasing deposition of conspecific pollen and reducing that of heterospecific pollen.
-Contrastingly, strategies that increase niche differentiation (functional originality and specialization) were positive to both the quantity and quality of pollination, but its effect was comparatively small compared to strategies of dominance.
-Remarkably, the particular strategy a plant uses is strongly shaped by its context and hence can be dramatically different in each of the communities it is part of. 
-[Wider application? Catchy closing line ideas?]
+Overall, our results suggest that pollination communities might not necessarily be the paradigmatic mutualistic communities we often believe. 
+Instead, we confirm that plant competition is pervasive in pollination communities and that potential strategies to minimise competition are likely involve strong trade-offs in the pollination service either in the short or the long term.
+As expected, not sharing pollinators and being functionally unique reduces competition for pollination by increassing conspecific pollen deposition (both in absolute numbers and relative to heterospecific pollen).
+However, this increasse is surprisingly small when compared to the effect of relative abundance and visitation. 
+Interestingly, these two factors also involve the largest trade-offs between increasing deposition of conspecific pollen and reducing that of heterospecific pollen. 
+Despite large intra-species differences among species our results provide solid evidence of the role that competition for pollination plays in natural communities. 
+Species coexistence is not solely determined by direct and indirect mutualistic relationships, but also strongly shaped by the multiple intewined ecological factors that shape competition for pollination at the community level.
+Achieving a better understanding how biodiversity is supported by pollination communities will require seeing them as both mutualistic and competitive comminities.
 

### 2019-03-17 paper/manuscript.Rmd
Basic spellcheck

@@
 It has been clear for a long time [both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970] that when competition for pollination is strong enough, it can be detrimental to plants' fitness.
-In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000]. 
+In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000]. 
 It is less clear, however, how exactly ecological differentiation, in turn, affect the trade-off between facilitation and competition that is involved in the pollination service.
@@
 The second is intraspecific pollen transfer and occurs when plants share pollination partners. 
-In that case, even receiving a visit might not necessarly translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or pollen from the focal plant might be lost to different species.
-Generally speaking, the higher the amount of conspecific pollen (both in absulute terms and relative to heterospecific pollen) the better the pollination service received by the focal plant.
+In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or pollen from the focal plant might be lost to different species.
+Generally speaking, the higher the amount of conspecific pollen (both in absolute terms and relative to heterospecific pollen) the better the pollination service received by the focal plant.
 These two mechanisms of competition, by definition, occur at the community scale. 
@@
 
-At the community scale the factors that determine the patterns of conspecific and heterospecific pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
+At the community scale, the factors that determine the patterns of conspecific and heterospecific pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
 For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016].
@@
 Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both visits and pollinator "real state".
-In this case, a potential reduction the absolute amount of conspecific pollen received could be compensated by an increase amount relative to heterospecific pollen. 
+In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount relative to heterospecific pollen. 
 Altogether, it is clear that some ecological factors can influence pollen deposition and that these factors, in the specific context of pollination, could be used to roughly define a species *realised niche* in their community.
-However, the intertwined nature of these factors makes it hard to determine wether they favour or hinder the pollination service at the community level. 
+However, the intertwined nature of these factors makes it hard to determine whether they favour or hinder the pollination service at the community level. 
 Moreover, their relative importance has not yet been empirically evaluated in natural plant communities.
@@
 Here, we investigate competition for pollination at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
-**First**, we estimate the extent to which the net outcome of plants sharing polinators is facilitation or competition. 
-If facilitation is the primary outcome, we could expect two tings. 
+**First**, we estimate the extent to which the net outcome of plants sharing pollinators is facilitation or competition. 
+If facilitation is the primary outcome, we could expect two things. 
 On the one hand, we could expect an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the amount of heterospecific pollen [@tur_evaluating_2016]. 
@@
 **Second**, we investigate the relative contribution that four ecological factors have on the pollination service. 
-Sepecifically, we hypothesize that competition (measured as absolute and relative conspecific pollen deposition) should increase for plants that share many pollination partners.
+Specifically, we hypothesize that competition (measured as absolute and relative conspecific pollen deposition) should increase for plants that share many pollination partners.
 However, we also hypothesize that other factors like the plant's functional originality, its relative abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
@@
 These locations are distributed across a precipitation gradient with a humid temperate climate in the eastern Flooding Pampas and becoming drier as one moves inland and westward towards the Pampean Grasslands.
-This precipitation gradient generatesd a natural gradient of network architecture which allowed us to examine the generality of our findings. 
+This precipitation gradient generated a natural gradient of network architecture which allowed us to examine the generality of our findings. 
 In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where we were only able to sample one restored fragment due to the lack of available sites.
@@
 
-Our first objective was to identify whether the outcome of plants sharing polinators at the community level is facilitation or competition. 
+Our first objective was to identify whether the outcome of plants sharing pollinators at the community level is facilitation or competition. 
 The first line of evidence can be found via the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
@@
 To compare the conspecific pollen deposited with and without animal-mediated pollination, we followed the same approach as above. 
-In this case, however, the predictor was the treatment (wether the flower was bagged or unbagged) instead of the number of heterospecific grains.
+In this case, however, the predictor was the treatment (whether the flower was bagged or unbagged) instead of the number of heterospecific grains.
 
@@
 Specifically, we used two sets of linear mixed models (LMM) in which the response variables are the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination.
-In general, using LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) offered better fit than a GLMM with Poisson (or quasipoisson) error structure.
+In general, using LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) offered a better fit than a GLMM with Poisson (or quasipoisson) error structure.
 Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].
@@
 We "shrank" the estimated coefficient of potentially unimportant variables by setting their estimate to 0 when the variable was not included in the model. 
-Finally, we used these distributions of the model coefficients to estimate their mean impact on the pollination service (in terms of absoulte and relative conspecific pollen deposition). 
+Finally, we used these distributions of the model coefficients to estimate their mean impact on the pollination service (in terms of absolute and relative conspecific pollen deposition). 
 Again, here we used bootstrap resampling to estimate the uncertainty around these means.
@@
 If community context plays a relatively small role or the species strategy is inflexible we would expect plants of the same species to fill similar competition for pollination niches across different communities.
-Alternatively, if the community plays a large role and plants sttrategies are flexible, we should be able to observe differences in the niche a plant species occupies across communities. 
+Alternatively, if the community plays a large role and plants strategies are flexible, we should be able to observe differences in the niche a plant species occupies across communities. 
 First, we used a principal component analysis (PCA) of the four ecological variables. 
-We scaled variables across the whole study to ensure that the PCA space does not change acording to the species present in each community. 
+We scaled variables across the whole study to ensure that the PCA space does not change according to the species present in each community. 
 We define a species' niche in a community as its coordinates in PCA space. 
@@
 Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
-For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that, the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others.
+For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others.
 Interestingly, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
@@
 
-Of the four variables we considered, we found that a plant's mean visit effectiveness and abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
+Of the four variables, we considered, we found that a plant's mean visit effectiveness and abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
 Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
@@
 This indicates that, although there is a positive association between visit effectiveness and the *absolute* amount of conspecific pollen, there is a negative relationship with the *relative* amount of conspecific relative to heterospecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
-In contrast, a plants' relative abundance had a negative effect on the absolute amount of conspecific pollen, but the mean difference between the coefficients in the models indicates a positive association with the relatvie amount of conspecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
+In contrast, a plants' relative abundance had a negative effect on the absolute amount of conspecific pollen, but the mean difference between the coefficients in the models indicates a positive association with the relative amount of conspecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
 The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the absolute and relative amount of conspecific pollen deposited. 
@@
 Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
-One exception was visit effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations (all with relatively low AICc support).
+One exception was visit-effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations (all with relatively low AICc support).
 
@@
 
-We used a PCA of the analysed species to investigate whether plant's niche of competition for pollination are similar across communities or whether they are flexible, and therefore a reflection of the community context.
+We used a PCA of the analysed species to investigate whether plants' niche of competition for pollination is similar across communities or whether they are flexible, and therefore a reflection of the community context.
 The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
@@
 Specifically, we found that the factors related to the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition.
-At the same time, receiving high visitation increases the absolute levels of conspecific pollen deposition but increasses heterospeicific deposition to a greater extent---even when the visitors are likely carry a high proportion of conspecific pollen.
+At the same time, receiving high visitation increases the absolute levels of conspecific pollen deposition but increases heterospecific deposition to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen.
 Similarly, being abundant reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
@@
 We show that being a specialist and sharing no pollinators might be preferable in the short term (as it is generally detrimental to pollen deposition). 
-However, over long periods of time there could be a risk associated to a specialist plant having no pollinators. 
-Hence, is likely that, to ensure long term survival, plants also need to balance this risk with the costs of sharing pollinators. 
-One possible solution is to share pollinators *and* have original traits---as we show that trait originallity is generally benefitial to pollen deposition and it’s commonly thought that species that are further from others in trait space suffer reduced competition.
+However, over long periods of time, there could be a risk associated with a specialist plant having no pollinators. 
+Hence, is likely that to ensure long term survival, plants also need to balance this risk with the costs of sharing pollinators. 
+One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it’s commonly thought that species that are further from others in trait space suffer reduced competition.
 Yet again, there are two possible caveats to this strategy that highlight the interrelatedness of the ecological factors. 
 First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators. 
-Second, the usuallly negative, relationship between originality and generalism has been shown depend on the plants abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make it worth to pollinators.
+Second, the usually negative, relationship between originality and generalism has been shown depend on the plant's abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make it worth to pollinators.
 
@@
 From a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
-Our results highlight the difficulties involved with predicting wether the introduced plant species will facilitate or compete with neighbours. 
-This is so because the outcome might depend not only on the particular niche each species occupies in a particular community, but also on other factors that we were unable to measure [e.g.
+Our results highlight the difficulties involved in predicting whether the introduced plant species will facilitate or compete with neighbours. 
+This is so because the outcome might depend not only on the particular niche each species occupies in a particular community but also on other factors that we were unable to measure [e.g.
 pollinator behaviour and densities or spatial context; @ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009].
-However, our results also suggest that introduced species are more likely to be benefitial if they have differing traits to local plants. 
+However, our results also suggest that introduced species are more likely to be beneficial if they have different traits to local plants. 
 <!-- cite melissa's paper if available before publication -->
@@
 Overall, our results suggest that pollination communities might not necessarily be the paradigmatic mutualistic communities we often believe. 
-Instead, we confirm that plant competition is pervasive in pollination communities and that potential strategies to minimise competition are likely involve strong trade-offs in the pollination service either in the short or the long term.
-As expected, not sharing pollinators and being functionally unique reduces competition for pollination by increassing conspecific pollen deposition (both in absolute numbers and relative to heterospecific pollen).
-However, this increasse is surprisingly small when compared to the effect of relative abundance and visitation. 
+Instead, we confirm that plant competition is pervasive in pollination communities and that potential strategies to minimise competition are likely to involve strong trade-offs in the pollination service either in the short or the long term.
+As expected, not sharing pollinators and being functionally unique reduces competition for pollination by increasing conspecific pollen deposition (both in absolute numbers and relative to heterospecific pollen).
+However, this increase is surprisingly small when compared to the effect of relative abundance and visitation. 
 Interestingly, these two factors also involve the largest trade-offs between increasing deposition of conspecific pollen and reducing that of heterospecific pollen. 
 Despite large intra-species differences among species our results provide solid evidence of the role that competition for pollination plays in natural communities. 
-Species coexistence is not solely determined by direct and indirect mutualistic relationships, but also strongly shaped by the multiple intewined ecological factors that shape competition for pollination at the community level.
-Achieving a better understanding how biodiversity is supported by pollination communities will require seeing them as both mutualistic and competitive comminities.
+Species coexistence is not solely determined by direct and indirect mutualistic relationships, but also strongly shaped by the multiple intertwined ecological factors that shape competition for pollination at the community level.
+Achieving a better understanding of how biodiversity is supported by pollination communities will require seeing them as both mutualistic and competitive communities.
 

### 2019-03-17 paper/supp-info.Rmd
Double escape math symbols in figure captions. Otherwise drake has trouble analysing dependencies
Remove unevaluated chunks from supp. info

@@
         knitr.kable.NA = "-")
-```
-
-```{r fig-deposition-log-transformed-or-not, fig.height = 2, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown).", eval=F}
-drake::loadd(fig_pollen_density)
-
-leg <- cowplot::get_legend(fig_pollen_density[[1]])
-cowplot::plot_grid(
-  remove_legend(fig_pollen_density[[1]]),
-  remove_legend(fig_pollen_density[[2]]), 
-  labels = LETTERS[1:2], 
-  label_size = 8) %>%
-  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
-```
-
-```{r fig-deposition-gain-log-transformed-or-not, fig.height = 1.8, fig.cap = "Distribution of the stigmatic pollen density for one of the bootstrap replicates used in the model sets.
-When (A) using directly the gain in pollen density and (B) when pollen density is log transormed (for the relative amount of conspecific pollen, density was log-transformed prior to calculating the gain).", eval=F}
-drake::loadd(fig_pollen_density_diff)
-
-leg <- cowplot::get_legend(fig_pollen_density_diff[[1]])
-cowplot::plot_grid(
-  remove_legend(fig_pollen_density_diff[[1]]), 
-  remove_legend(fig_pollen_density_diff[[2]]), 
-  labels = LETTERS[1:2], 
-  label_size = 8,
-  ncol = 2) %>%
-  cowplot::plot_grid(leg, ., rel_heights = c(0.1, 0.9), ncol = 1)
-```
-
-```{r fig-abundance-logtransformed-or-not, fig.height = 1.65, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been log transformed and scaled to have a mean of zero and a standard deviation of one.", eval = F}
-drake::loadd(fig_abundance)
-
-cowplot::plot_grid(
-  fig_abundance[[2]], 
-  fig_abundance[[1]],
-  rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
 ```
@@
 Model formulas have been abbreviated: *a* for abundance, *k* for the number of shared polinators, *p* for the visit effectiveness, and *t* for trait originality.
-Only candidate formulas with a $\Delta AICc < 4$ for either conspecific or heterospecific pollen are shown.
+Only candidate formulas with a $\\Delta AICc < 4$ for either conspecific or heterospecific pollen are shown.
 Models candidates are arranged in decreassing order of support.", eval=T}
 drake::readd(fig_all_model_results)
-```
-
-```{r table-species-gain-site, results = 'asis', eval=F}
-drake::loadd(significant_gain_global, significant_gain_site, sites)
-table_frame <- glance_table(significant_gain_site) %>%
- dplyr::inner_join(sites, by = "site_name") %>%
-  dplyr::group_by(recipient) %>%
-  dplyr::mutate(n_sites = dplyr::n_distinct(site_name)) %>%
-  dplyr::filter(n_sites > 1) %>%
-  dplyr::group_by() %>%
-  dplyr::mutate(site_name = paste(locality_name, land_use, fragment, sep = ' - '),
-         recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
-  dplyr::select(recipient, site_name, estimate, statistic, p.value) %>%
-  dplyr::rename(`p value` = p.value,
-         `difference` = estimate,
-         `plant species` = recipient, 
-         `community` = site_name)
-
-seps <-dplyr::if_else(table_frame$`plant species` == 
-  dplyr::lag(table_frame$`plant species`), "", "\\addlinespace") %>%
-  na.omit()
-
-table_frame %>%
-  knitr::kable("latex", 
-    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers.
-Tests were performed at the community level.
-Only species present in more than one community are shown.",
-    escape = FALSE, 
-    booktabs = TRUE, 
-    linesep = seps, 
-    digits = 3) %>%
-  kableExtra::kable_styling(font_size = 8)
-```
-
-```{r table-variation-across-sites, eval=FALSE, results='asis', eval=F}
-drake::loadd(consp_self)
-consp_self %>%
-  anova(test = "Chisq")  %>%
-  knitr::kable("latex", 
-    caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).
-Density were modelled using a quasipoisson distribution.
-The model suggests that self-pollination rates are species dependent but not across.',
-    booktabs = TRUE) %>%
-  kableExtra::kable_styling(font_size = 8)
 ```
@@
 ```
-
-```{r fig_effect_quant_qual, fig.height=3.5, fig.cap="asd", eval=F}
-drake::loadd(fig_effect_quant_qual)
-
-cowplot::plot_grid(
- fig_effect_quant_qual[[1]], 
- fig_effect_quant_qual[[2]],
-  labels = LETTERS[1:2], 
-  label_size = 8, ncol = 2)
-```

### 2019-03-17 paper/supp-info.Rmd
Spell check supp. info captions

@@
                col.names = c("species name", "community", "slope", "S.E."), 
-               caption = "Slope of the relationship between heterospecific and conspecific pollen for each species in their community (fixed effect + conditional effect).
+               caption = "The slope of the relationship between heterospecific and conspecific pollen for each species in their community (fixed effect + conditional effect).
 Community names are constructed by location - agricultural/restored - fragment number.",
@@
                col.names = c(rep(c("mean", "min", "max"), times = 2)), 
-               caption = "Coefficient of determination $R^2$ of the most parsimonious pollen deposition models (those with the lowest AICc).
+               caption = "The coefficient of determination $R^2$ of the most parsimonious pollen deposition models (those with the lowest AICc).
 The marginal coefficient of determination describes the proportion of variance explained by just the fixed effects.",
@@
                caption = paste('Comparison of the two random structures we considered for the models of conspecific and heterospecific pollen deposition.
-The table shows median $\\Delta$AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data.
+The table shows median $\\Delta$AIC values of', dplyr::n_distinct(glanced_random$model), "bootstrap resamples of the data.
 The 5th and 95th percentile are shown inside square brackets.
@@
                col.names = c("fixed structure", "median", "C.I."),
-               caption = paste('Comparison of the different fixed structures we consideredfor the models of conspecific and heterospecific pollen deposition.
-The table shows median $\\Delta$AIC values of', dplyr::n_distinct(glanced_random$model), "bootsrap resamples of the data.
+               caption = paste('Comparison of the different fixed structures we considered for the models of conspecific and heterospecific pollen deposition.
+The table shows median $\\Delta$AIC values of', dplyr::n_distinct(glanced_random$model), "bootstrap resamples of the data.
 The 5th and 95th percentile are shown inside square brackets."),
@@
 
-```{r fig-correlation, fig.height = 5, fig.cap = "Corelation between the explanatory variables included in the statistical models.", eval=T}
+```{r fig-correlation, fig.height = 5, fig.cap = "Correlation between the explanatory variables included in the statistical models.", eval=T}
 drake::readd(fig_correlation)
@@
 ```{r fig-model-results, fig.height = 5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
-Model formulas have been abbreviated: *a* for abundance, *k* for the number of shared polinators, *p* for the visit effectiveness, and *t* for trait originality.
+Model formulas have been abbreviated: *a* for abundance, *k* for the number of shared pollinators, *p* for the visit effectiveness, and *t* for trait originality.
 Only candidate formulas with a $\\Delta AICc < 4$ for either conspecific or heterospecific pollen are shown.
-Models candidates are arranged in decreassing order of support.", eval=T}
+Models candidates are arranged in decreasing order of support.", eval=T}
 drake::readd(fig_all_model_results)
@@
 
-```{r fig-global-community-correlations, fig.height = 2, fig.cap = "Relationship between the model's independent variables calculated at the community level and at the study-wide level.", eval=F}
+```{r fig-global-community-correlations, fig.height = 2, fig.cap = "The relationship between the model's independent variables calculated at the community level and at the study-wide level.", eval=F}
 drake::readd(fig_community_global_scatter)

### 2019-03-17 paper/draft-info.Rmd
Remove old questions

@@
 
-* Polish discussion, will appreciate input here. 
+* Polish discussion, will appreciate input here. Hugo, feel free to make edits to the text. Large and small. will really appreciate specific input here. 
 * Polish supp. info.
 * Spell-check everything & check that reference list is correct.
-* I think its not supper clear in the manuscript what is meant by a plant strategy. Need to re-check in the next iteration.
 
@@
 Feel free to come back here after you've read the manuscript. Thanks!
-
-* Minor point: DBS thinks that normally one would use the technical word and then put the definition in parenthesis.
-In a previous revision I got from JMT that it's better to lead with the concept and then add the jargon last.
-Examples: *"...due to a temporary separation in the maturation of sexes (dichogamy)"*, *"...common insect-pollinated (entomophilous) species"*.
-
-* Journal? --- *Hugo says PNAS, Proceedings B and Science. No answer from other coauthors*
-* I think the story is still a bit disperse.
-Will appreciate feedback on identifying the most important/exciting findings to tie the others around it.
-So far the central topic is scaling up of competition to the community level.
---- *No particular feedback received*
-* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}? --- *No particicular feedback received*
-* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private? --- *It is OK*
-* In Figure \@ref(fig:fig-trade-off-predictions)a, I determine if the slope is significantly positive or negative by checking whether the standard errors cross 0.
-Should it be 2 times SE?
-Should all other error bars in Figure \@ref(fig:fig-trade-off-predictions) be 2 times SE?
---- *No particular feedback received*
-* What do you think about the quantity/quality discourse now?
-I'm still unconvinced.
-Maybe I should just go for relationship conspecific/heterospecific instead of quality?
-That would mean that Figure \@ref(fig:fig-average-qual-quant)c would just need the right panel.
-Cause the left is just almost the same as Figure \@ref(fig:fig-average-qual-quant)b, except that it includes models in which the variable was not present and hence "shrinks" the model averaged estimate.
---- *Daniel advocates for getting rid of quantity/quality and go for conspecific/conspecific proportion*
-* Unsure of whether in Figure \@ref(fig:fig-pca)a, it would be better to display the contribution of each component to total variance instead of the cummulative contribution.
---- *Add info to left of the figure*
-* I'm not very happy with the way the third hypothesis is described in the intro (\lr{third-hypothesis}). I would appreciate ideas to rephrase it clearly
-* Does the paragraph in \lr{disc-facil-comp} needs more meat? Any suggestions?
-* My background in the topic is limited, would be grateful if you could point me out to key papers that could be used to put some context to the finding of the "flexibility" of plants strategies (paragraph in \lr{strategies}) --- *DBS argues that I say that strategies minimise competition but I never show that, only show that strategies change.
-Need to think about that*
-* Part of the discussion before revolved about the fact that degree is commonly used in theoretical models of mutualism to adjust the mutualistic benefit of generalist species.
-I've removed it because I think the discussion is already a bit long and didn't fit that nicely in the story.
-You think it should be included?
---- *DBS says is OK to leave it out*

### 2019-03-17 paper/manuscript.Rmd
Add stuff so its easy to produce word on demand

@@
 csl: ecology-letters.csl
-output:
+output: #word_document
   bookdown::pdf_document2:
@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
-                      warning = FALSE)
+                      warning = FALSE, dpi = 300)
+# library(magrittr)
+# library(foreach)
+# library(drake)
+# # load functions
+# f <- lapply(list.files("../code", full.names = T), source)
 ```

### 2019-04-08 paper/draft-info.Rmd
Fix figure sizes to match ecology letters format

@@
 * Show niche points for all species and not only those in two communities or more
+* Figures edited to match one and two column sizes at Ecology Letters
 * Added the following elements to the disussion: 

### 2019-04-08 paper/manuscript.Rmd
Fix figure sizes to match ecology letters format

@@
   - \externaldocument[S-]{supp-info}
+  - \usepackage[export]{adjustbox}
 ---
@@
 
-```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "**Competition vs.
-facilitation at the community level**.
+```{r fig-trade-off-predictions, fig.height= 4, out.height="4in", fig.width = 7.49, out.width="7.49in", out.extra="center", fig.cap = "Competition vs.
+facilitation at the community level.
 (a) Some species experience more competition for pollination than others.
 Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities.
-Significantly negative slopes (darkest shade) indicate that plants experience competition for animal-mediated pollination, while significantly positive slopes (lightest shade) indicate that facilitation is the predominant outcome.
+Statistically significant negative slopes (darkest shade) indicate that plants experience competition for animal-mediated pollination, while significantly positive slopes (lightest shade) indicate that facilitation is the predominant outcome.
 The number of plants analysed for each species is shown within brackets next to the species name.
@@
 width_left <- 6.5*3/5
-bar_plot_width <- 0.325
+bar_plot_width <- 0.29
 rw <- c(width_left - bar_plot_width,
@@
 
-```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=6.5/2, fig.cap="**Effect of strategies to minimise competition in the pollination service**.
+```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=width('single'), out.height="4.56in", out.width="3.57in", out.extra="center", fig.cap="Effect of strategies to minimise competition in the pollination service.
 (a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
@@
 
-```{r fig-pca, fig.width=3.25, fig.height=6.65, fig.cap="**The flexibility of plant strategies**.
+```{r fig-pca, fig.width=3.57, fig.height=6.65, out.width="3.57in", out.height="6.65in",  out.extra="center", fig.cap="**The flexibility of plant strategies**.
 (a) The two first components explain a large proportion of the total variance.

### 2019-04-08 code/plotting_and_formatting.R

@@ -20,6 +20,20 @@ pub_theme <- function(){
           plot.background = element_blank())
 }
 
+width <- function(type, unit=NULL){
+  # Ecology letters has a paper width of 200 mm
+  widths <- dplyr::case_when(
+    type == "single" ~ 3.57,
+    TRUE ~ 7.49
+  )
+  if(is.null(unit)) return(widths)
+  else if (unit=="in") {
+    widths %>%
+      as.character() %>%
+      paste0("in")
+  }
+}
+
 remove_legend <- function(x){
   require(ggplot2)
   x + theme(legend.position = 'none')

### 2019-04-08 paper/manuscript.Rmd
Improve manuscript readability - more margin, larger font

@@
 toc: false
+fontsize: 11pt
+classoption: a4paper
+geometry: 
+  - textwidth=33em
+  - textheight=48\baselineskip
 header-includes:

### 2019-04-08 paper/manuscript.Rmd
Replace instances when "significant" is used to mean considerable
Prevent confusion with statistical significancy

@@
 We found that overall neither facilitation nor competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
-Indeed, we found that the proportion of species that experienced a significantly positive or neggative relationship between heterospecific and conspecific pollen than neggative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)).
+Indeed, we found that the proportion of species that experienced a statistically significant positive or neggative relationship between heterospecific and conspecific pollen than neggative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)).
 Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
@@
 Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers (Table \@ref(S-tab:table-open-bagged-models-general)). 
-Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had significantly more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open (the difference was non-signifcant for the remainding `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
-Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both significantly positive and negative differences.
+Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had less pollen when open (the difference was statistically non-signifcant for the remainding `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
+Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both positive and negative differences.
 
@@
 
-Overall, collinearity did not influence our findings qualitatively.
+Overall, collinearity did not affect our findings qualitatively.
 Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
@@
 First, we found that the costs of pollinator sharing are pervasive. 
-In particular, we found that a significant proportion of species experiences overall neutral or competitive effects from animal-mediated pollination. 
+In particular, we found that a considerable proportion of species experiences overall neutral or competitive effects from animal-mediated pollination. 
 Second, we found that multiple ecological factors can modulate the intensity of this competition; however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these factors are likely to involve a trade-off between the quantity and quality of pollination.

### 2019-04-08 paper/manuscript.Rmd
Add colleagues feedback to introduction

@@
 <!-- FDO: Asked coauthors for a reference for the following statement but no-one provided. Therefore removing -->
-Alongside the direct mutualisms between plants and their pollinators, biodiversity can be supported as a result of inter-species "facilitation"—the positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008].
+Alongside the direct mutualisms between plants and their pollinators, biodiversity can be supported as a result of the inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008].
 This inter-species facilitation is able to promote species coexistence by offsetting the effects of direct resource competition [@stachowicz_mutualism_2001]. 
@@
 However, in natural communities, plants rarely share all available pollinators.
-One explanation is that plants are effectively competing for mutualistic partners because there is a *trade-off* between the benefits gained from maximising the number of mutualistic partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
-It has been clear for a long time [both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970] that when competition for pollination is strong enough, it can be detrimental to plants' fitness.
+One explanation is that plants are effectively competing for mutualistic partners because there is a *trade-off* between the benefits gained from maximising the number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
+It has been clear for a long time that when competition for pollination is strong enough, these costs can make it detrimental to plants' fitness [shown both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970].
 In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000]. 
@@
 The first is intraspecific pollen transfer. 
-This happens, for example, when plants with distinctively attractive flowers might reduce the number of visits---and hence the amount of *conspecific pollen* deposited by animals---to those less attractive neighbouring plants [@yang_pollinator_2011].
+This happens, for example, when plants with distinctively attractive flowers might reduce the number of visits to those less attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
 The second is intraspecific pollen transfer and occurs when plants share pollination partners. 
-In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or pollen from the focal plant might be lost to different species.
+In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
 Generally speaking, the higher the amount of conspecific pollen (both in absolute terms and relative to heterospecific pollen) the better the pollination service received by the focal plant.
@@
 However, with few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the deposition of conspecific and heterospecific pollen---and its relationship to competition vs.
-facilitation in pollination systems---is based on studies of two plant species.
+facilitation in pollination systems---is based on studies with two plant species.
 
@@
 For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016].
-This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly (TODO: ref needed).
-If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase in species with a large number of interaction partners [@gibson_can_2012].
+This evidence is aligned with the notion that a species which interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly (TODO: ref needed).
+If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012].
 Alternatively, it might also be the case that density (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
-Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both visits and pollinator "real state".
-In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount relative to heterospecific pollen. 
+Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators.
+In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount of conspecific pollen relative to heterospecific pollen. 
 Altogether, it is clear that some ecological factors can influence pollen deposition and that these factors, in the specific context of pollination, could be used to roughly define a species *realised niche* in their community.
@@
 Here, we investigate competition for pollination at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
-**First**, we estimate the extent to which the net outcome of plants sharing pollinators is facilitation or competition. 
+First, we estimate the extent to which the net outcome of plants sharing pollinators is facilitation or competition. 
 If facilitation is the primary outcome, we could expect two things. 
@@
 The higher the deposition of conspecific pollen relative to heterospecific, the larger the slope of that relationship.
-On the other, we could also expect a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than is deposited due to self-pollination. 
-**Second**, we investigate the relative contribution that four ecological factors have on the pollination service. 
+On the other, we could also expect a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination. 
+Second, we investigate the relative contribution that four ecological factors have on the pollination service. 
 Specifically, we hypothesize that competition (measured as absolute and relative conspecific pollen deposition) should increase for plants that share many pollination partners.
 However, we also hypothesize that other factors like the plant's functional originality, its relative abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
-**Third**, we examine how community context influences the way plants use these factors to minimise competition. 
+Third, we examine how much does the community context influences the way plants use these factors to minimise competition. 
 Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict the competition for pollination niche to be influenced by the local context.

### 2019-04-09 code/count_words.R
Add automatic counter of references (due to Ecology Letters requirement)

@@ -44,3 +44,29 @@ prep_text <- function(text) {
       return(text)
     }
 }
+
+
+get_citations <- function(filename, lines_to_ignore = NULL, refs_to_exclude = NULL, refs_to_include = NULL){
+  text_lines <- readLines(filename)
+  if (!is.null(lines_to_ignore)) {
+    text_lines <- text_lines[-lines_to_ignore]
+  }
+
+  citations <- text_lines %>%
+    stringr::str_extract("@\\w+") %>%
+    na.omit()
+
+  if (!is.null(refs_to_exclude)) {
+    citations <- citations[!citations %in% refs_to_exclude]
+  }
+  if(!is.null(refs_to_include)) {
+    citations <- union(citations, refs_to_include)
+  }
+
+  citations
+}
+
+count_references <- function(filename, ...){
+  citations <- get_citations(filename, ...)
+  dplyr::n_distinct(citations)
+}

### 2019-04-09 main.R

@@ -211,6 +211,7 @@ reporting_plan <- drake_plan(
   acknowledgements = readLines(file_in("./paper/acknowledgements.md")),
   abs_wordcount = count_words(file_in("paper/abstract.md")),
   msc_wordcount = count_words(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:56),
+  n_references = count_references(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:59, refs_to_exclude = "@ref"),
   render_pdf(knitr_in('paper/supp-info.Rmd'), file_out('paper/supp-info.pdf'), clean_md = FALSE),
   render_pdf(file_in('paper/draft-info.Rmd'), file_out('paper/draft-info.pdf'), clean_md = FALSE),
   render_pdf(knitr_in('paper/manuscript.Rmd'), file_out('paper/manuscript.pdf'), clean_md = FALSE)

### 2019-04-09 code/count_words.R
Add automatic counter of displays

@@ -10,7 +10,7 @@ count_words <- function(filename = "", lines_to_ignore = NULL, remove_md_heading
       text_lines <- text_lines[-heading_lines]
     }
   }
-  text_to_count <- paste(text_lines, 
+  text_to_count <- paste(text_lines,
                          collapse = " ")
   get_text_stats(text_to_count)
 }
@@ -22,7 +22,7 @@ get_text_stats <- function(text){
   n_words_stri <- unname(stringi::stri_stats_latex(text)[4])
   wpm <- 200
   reading_time_stri <- ceiling(n_words_stri/wpm)
-  return(list(n_char_tot_stri = n_char_tot, n_words_stri = n_words_stri, 
+  return(list(n_char_tot_stri = n_char_tot, n_words_stri = n_words_stri,
               reading_time_stri = reading_time_stri))
 }
 
@@ -69,4 +69,16 @@ get_citations <- function(filename, lines_to_ignore = NULL, refs_to_exclude = NU
 count_references <- function(filename, ...){
   citations <- get_citations(filename, ...)
   dplyr::n_distinct(citations)
+}
+
+count_displays <- function(filename, lines_to_ignore = NULL){
+  text_lines <- readLines(filename)
+  if (!is.null(lines_to_ignore)) {
+    text_lines <- text_lines[-lines_to_ignore]
+  }
+
+  c(figures = "fig", tables = "tab", text_boxes = "box") %>%
+    purrr::map(~paste0("```\\{.+", ., "-.+\\}")) %>%
+    purrr::map(~stringr::str_detect(text_lines, pattern = .)) %>%
+    purrr::map(sum)
 }

### 2019-04-09 main.R

@@ -212,6 +212,7 @@ reporting_plan <- drake_plan(
   abs_wordcount = count_words(file_in("paper/abstract.md")),
   msc_wordcount = count_words(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:56),
   n_references = count_references(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:59, refs_to_exclude = "@ref"),
+  n_displays = count_displays(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:56),
   render_pdf(knitr_in('paper/supp-info.Rmd'), file_out('paper/supp-info.pdf'), clean_md = FALSE),
   render_pdf(file_in('paper/draft-info.Rmd'), file_out('paper/draft-info.pdf'), clean_md = FALSE),
   render_pdf(knitr_in('paper/manuscript.Rmd'), file_out('paper/manuscript.pdf'), clean_md = FALSE)

### 2019-04-09 paper/manuscript.Rmd
Add automatic counter of references (due to Ecology Letters requirement)
Add automatic counter of displays
Add running title

@@
 
-**Author for correspondence:** E.
-Fernando Cagua (efc29@uclive.ac.nz) - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
+**Running title:** The pollination trade off
+
+**Number of displays:** `r readd(n_displays)$figures` figures; `r readd(n_displays)$tables` tables; `r readd(n_displays)$text_boxes` text boxes.
+
+**Number of references:** `r readd(n_references)`
 

### 2019-04-09 paper/manuscript.Rmd
Add data acesibility and author contribution statement

@@
 **Number of references:** `r readd(n_references)`
+
+**Data acessibility:** Data supporting the results will be accesible in an appropiate data repository after publication. The data DOI will be included here.
+
+**Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.
 

### 2019-04-09 paper/manuscript.Rmd
Number of words in main text and abstract together in same line

@@
 
+**Number of words:** `r readd(abs_wordcount)$n_words_stri` in the abstract; `r format(round(readd(msc_wordcount)$n_words_stri/10)*10, big.mark = ",")` in the main text.
+
 **Number of displays:** `r readd(n_displays)$figures` figures; `r readd(n_displays)$tables` tables; `r readd(n_displays)$text_boxes` text boxes.
@@
 ```
-
-```{r draft-details}
-drake::loadd(msc_wordcount, abs_wordcount)
 ```
-
-**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters, approx.
-`r format(round(msc_wordcount$n_words_stri/10)*10, big.mark = ",")` words (excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` min.
-reading time.
-
-**Abstract length:** `r abs_wordcount$n_words_stri` words.
 

### 2019-04-09 paper/manuscript.Rmd
Move keywords to title page
Other edits to title page re. author information

@@
 
+**Keywords:** X,Y,Z
+
+**Type of article:** Letter
+
 **Number of words:** `r readd(abs_wordcount)$n_words_stri` in the abstract; `r format(round(readd(msc_wordcount)$n_words_stri/10)*10, big.mark = ",")` in the main text.
@@
 **Number of references:** `r readd(n_references)`
+
+**Author for correspondence:** E. Fernando Cagua (efc29@uclive.ac.nz) - +64 20 4026 8153
+
+**Authors' email addresses:** Hugo J. Marrrero (hugomarrero@gmail.com); Jason M. Tylianakis (jason.tylianakis@canterbury.ac.nz); Daniel B. Stouffer (daniel.stouffer@canterbury.ac.nz)
 
@@
                       warning = FALSE, dpi = 300)
-# library(magrittr)
-# library(foreach)
-# library(drake)
-# # load functions
-# f <- lapply(list.files("../code", full.names = T), source)
-```
 ```
@@
 `r paste(drake::readd(abstract), collapse = "")`
-
-**Keywords:** X, Y, Z
 

### 2019-04-09 paper/manuscript.Rmd
Cosmetic changes to title page

@@
 title: "The pollination trade-off"
-author: "E. Fernando Cagua^1^, Hugo J. Marrero^2^, Jason M. Tylianakis^1^, Daniel B. Stouffer^1^"
+author: 
+  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
+  - "Hugo J. Marrero^2^ ([hugomarrero@gmail.com](hugomarrero@gmail.com))"
+  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
+  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
 bibliography: phd-bibliography/pollen-competition.bib
@@
 
+<!-- ^a^ [efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz); ^b^ [hugomarrero@gmail.com](hugomarrero@gmail.com); ^c^ [jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz); ^d^ [daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz) -->
+
 **Running title:** The pollination trade off
 
-**Keywords:** X,Y,Z
+**Keywords:** X,Y,Z (up to 10)
 
@@
 
-**Author for correspondence:** E. Fernando Cagua (efc29@uclive.ac.nz) - +64 20 4026 8153
-
-**Authors' email addresses:** Hugo J. Marrrero (hugomarrero@gmail.com); Jason M. Tylianakis (jason.tylianakis@canterbury.ac.nz); Daniel B. Stouffer (daniel.stouffer@canterbury.ac.nz)
+**Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153)
 

### 2019-04-09 paper/manuscript.Rmd
Load msc data in its own chunk so that the drake dependences are correctly calculated

@@
 
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
+                      warning = FALSE, dpi = 300)
+
+loadd(abs_cordcount, msc_wordcount, n_displays, n_references)
+```
+
 ^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand
@@
 
-**Keywords:** X,Y,Z (up to 10)
+**Keywords:** X,Y,Z (up to 10).
 
-**Type of article:** Letter
+**Type of article:** Letter.
 
-**Number of words:** `r readd(abs_wordcount)$n_words_stri` in the abstract; `r format(round(readd(msc_wordcount)$n_words_stri/10)*10, big.mark = ",")` in the main text.
+**Number of words:** `r abs_wordcount$n_words_stri` in the abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in the main text.
 
-**Number of displays:** `r readd(n_displays)$figures` figures; `r readd(n_displays)$tables` tables; `r readd(n_displays)$text_boxes` text boxes.
+**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.
 
-**Number of references:** `r readd(n_references)`
+**Number of references:** `r n_references`
 
-**Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153)
+**Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153).
 
@@
 **Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
-                      warning = FALSE, dpi = 300)
-```
 

### 2019-04-09 paper/manuscript.Rmd
Move some justification on facilitation/competition from methods to discussion

@@
 A negative relationship (when shared pollinators increase heterospecific pollen loads and decrease conspecific loads) may indicate that competition for pollination is strong. 
-This negative relationship could arise, for example, when another, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; @lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
 In contrast, a positive relationship is what would be observed when facilitation is the dominant outcome.
-For example, when the abundance of shared pollinators is positively influenced by floral resources, these positive effects ripple through the mutualistic network in a chain of positive feedback loops [@liao_presence_2011].
 
@@
 In contrast, the opposite pattern may indicate that plants benefit from having pollen delivered directly to the stigma by animals.
-We did not specifically test the effect of pollen viability or the extent to which self-pollen vs.
-pollen from a conspecific may differ in their value for fertilization which can be important factors (TODO: ref needed).
-However, it is reasonable to expect that the difference between outcross and self-pollen may be generally relevant and particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy) (TODO: ref needed).
 
@@
 Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that net facilitation is only experienced by a fraction of species in a community. 
-A recent study also suggested a wide range of outcomes in a multi-species context [@tur_evaluating_2016]. 
+Instead, we observed a negative relationships between conspecific and heterospecific in a considerable proportion of the analysed species. 
+This relationship could arise, for example, when another, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; @lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma phisically interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
+Similarly, not all species had more pollen deposited when open to animal pollination compared to when they were closed. 
+Although it can be important, we were unable to test the effect of pollen viability or the extent to which self- vs. outcross-pollen may differ in their value for fertilization (TODO: ref needed). 
+However, it is reasonable to expect that the difference between these two may be generally relevant. 
+Particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy) (TODO: ref needed).
+These findings agree with a recent study showing a wide range of outcomes in a multi-species context [@tur_evaluating_2016]. 
 However, the factors explaining why some species experience more competition than others were not understood. 

### 2019-04-09 paper/manuscript.Rmd
Some edits to methods

@@
 We collected data from eleven co-flowering plant communities and their pollinators in three locations in the Argentinian Pampas. 
-These locations are distributed across a precipitation gradient with a humid temperate climate in the eastern Flooding Pampas and becoming drier as one moves inland and westward towards the Pampean Grasslands.
+These locations are distributed across a precipitation gradient with a humid temperate climate of the eastern Flooding Pampas becoming drier as one moves inland and westward towards the Pampean Grasslands.
 This precipitation gradient generated a natural gradient of network architecture which allowed us to examine the generality of our findings. 
@@
 Our first objective was to identify whether the outcome of plants sharing pollinators at the community level is facilitation or competition. 
-The first line of evidence can be found via the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
+We use two complementary lines of evidence.  
+The first line can be found via the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
 This is because heterospecific pollen can be seen as an unavoidable cost that plants must pay for receiving conspecific pollen from shared pollinators. 
@@
 Self-pollination can be favourable to plant reproduction when competition for pollination is strong because it provides insurance against poor pollination service [@kalisz_benefits_2003]. 
-If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented could be higher than when floral visits are allowed.
+If competition <!-- for pollination-->is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented should be higher than when animal pollination is allowed.
 In contrast, the opposite pattern may indicate that plants benefit from having pollen delivered directly to the stigma by animals.
@@
 We chose plant species such that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
-Briefly, in each of the selected plants, we removed all flowers leaving only buds that were expected to go into florescence on the next day. 
+In each of the selected plants, we removed all flowers leaving only buds that were expected to go into florescence on the next day. 
 Approximately a quarter of these buds were bagged to prevent animal pollination. 
-Two days after inflorescence, we counted the pollen grains in the remaining flowers' pistils, classified them between conspecific and heterospecific pollen, and calculated the number of pollen grains per stigma in each flower.
-More details about the study sites, data collection, and laboratory protocols can be found in @marrero_agricultural_2016.
+Two days after inflorescence, we collected all remaining flowers' and counted the pollen grains in their pistils. 
+We then classified them between conspecific and heterospecific pollen, and calculated the number of pollen grains per stigma in each flower. 
+More details can be found in @marrero_agricultural_2016.
 
@@
 Models were fitted using the function `glmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]. 
+A positive slope for a plant-community combination might indicate facilitation while a negative slope might indicate competition.
+
 To compare the conspecific pollen deposited with and without animal-mediated pollination, we followed the same approach as above. 
@@
 
-Our second objective was to investigate the relative contribution of different factors that describe the plant competition for pollination niche to the pollination service. 
-Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plants abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them (see *Data Analysis* section below for more details), and (*iv*) the plants functional originality (add ref).
+Our second objective was to investigate the relative contribution of different factors---that describe the plant competition for pollination niche---to the pollination service. 
+Generally speaking, in the context of competition for pollination we expect that a factor that increasse on the amount of conspecific pollen deposited in stigmas (both in absolute terms and relative to heterospecific pollen) also has a positive effect on the pollination service.
+Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plants abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them, and (*iv*) the plants functional originality [@laliberte_distance-based_2010].
+See *Data Analysis* section below for more details on these four variables. 
 <!-- Here, we define visit effectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
@@
 Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region.
-We used those traits because they were the only ones available... (TODO: Add a better justification for the traits used)
-More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014 and 2017).
+We used those traits because they were the only ones available. <!--.. (TODO: Add a better justification for the traits used)-->
+More details can be found in Marrero *et al.* (2014 and 2017).
 
@@
 
-We investigated the impact of the ecological factors on pollination services.
-Generally speaking, the more conspecific pollen deposited in stigmas, both absolutely and relative to heterospecific pollen, the better the pollination service. 
-Specifically, we used two sets of linear mixed models (LMM) in which the response variables are the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination.
-In general, using LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) offered a better fit than a GLMM with Poisson (or quasipoisson) error structure.
+To investigate the impact of ecological factors on pollination service we used two sets of linear mixed models (LMM) with boothstrap resampling.
+The response variables for these model sets were the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination. 
+We used LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) because these models offered a better fit than a GLMM with Poisson (or quasipoisson) error structure.
 Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].
@@
 <!-- As phenology has been shown to be a key mechanism of niche differentiation among plants, we also  -->
-To include phenology we treated plant abundance in each of the survey months (November to March) as a "trait" in our analysis. 
+To include phenology, we treated plant abundance in each of the survey months (November to March) as a "trait" in our analysis. 
 <!-- This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits.  -->
-Then we assigned the abundances a weight of 1/5 compared to other functional traits, this accounted for the non-independence of floral counts across months and effectively weights phenology equally to other traits.
+To account for the non-independence of floral counts and weight all traits equally, we assigned the abundances a weight of 1/5 compared to other functional traits. 
 We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
@@
 As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our variables proportional to the likelihood of its candidate model.
-We "shrank" the estimated coefficient of potentially unimportant variables by setting their estimate to 0 when the variable was not included in the model. 
+<!-- We "shrank" the estimated coefficient of potentially unimportant variables by setting their estimate to 0 when the variable was not included in the model.  -->
 Finally, we used these distributions of the model coefficients to estimate their mean impact on the pollination service (in terms of absolute and relative conspecific pollen deposition). 
-Again, here we used bootstrap resampling to estimate the uncertainty around these means.
+<!-- Again, here we used bootstrap resampling to estimate the uncertainty around these means.  -->
 
@@
 (c) The end result of these associations is that only the plants' functional originality has a positive impact on both the absolute and relative amount of conspecific pollen deposition (relative to heterospecific pollen).
-The plot shows the model averaged mean effect ($\\pm$ SE)."}
+The plot shows the model averaged mean effect ($\\pm$ SE of 99 bootstrap replicates)."}
 height1 <- 1

### 2019-04-09 paper/cover-letter.tex
Add draft cover letter

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[a4paper, 10pt]{letter}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua,\\
    University of Canterbury, \\
    Private Bag 4800, Christchurch 8041, \\
    New Zealand.
}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Tim Coulson,\\
    Editor-in-chief,\\
    Ecology Letters
}
% Opening statement
\opening{Dear Kathleen,}
% Letter body
I am aware that you are pretty miffed at me for being the cause of the demise of your bookstore. You have to believe in me, that was not my intention at all.
I hope we can talk about this over coffee. How about we meet this Friday evening at the corner cafe? Let me know.
% Closing statement
\closing{Yours truly,}
\end{letter}
\end{document}
%-----------------------------------------------------------------------------%

### 2019-04-10 paper/draft-info.Rmd
Update changelog

--- 2019-03-17 paper/draft-info.Rmd
@@
 * Applied a green palette to all figures. Improves legibility when looking at it in a screen an performance when printed in greyscale is maintained
+* Moved some of the justification on the criteria used to identify facilitation/competition to the discussion.
 * Show niche points for all species and not only those in two communities or more
+* Figures edited to match one and two column sizes at Ecology Letters. Implemented all format requirements for EL.
 * Added the following elements to the disussion: 
@@
 
-## Questions
+## Specific requests
+
+* Help suggesting a justification for the traits used. 
+* Help identifying sections to trim to achieve the word limit.
 

### 2019-04-10 paper/cover-letter.Rnw
Use Rnw for the cover letter so that title can be changed dynamically

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[a4paper, 11pt]{letter}
\usepackage{hyperref}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    University of Canterbury, \\
    New Zealand
}
\date{April 15, 2019}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Prof. Tim Coulson,\\
    Editor-in-chief,\\
    Ecology Letters
}
% Opening statement
\opening{Dear Professor Coulson,}
% Letter body

<<my-label, eval=TRUE, echo=FALSE>>=
drake::loadd(msc_title)
@

We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Ecology Letters}.

The covering letter to the Editorial Office should succinctly describe why the enclosed work is novel, exciting and of general interest in ecology.

Additionally, the covering letter should include a clear statement of exactly how the present manuscript is outstandingly novel relative to recent work by the author or coauthors cited in the present submission.

At the time of submission, PDFs of any recent manuscripts or book chapters by the author or coauthors and cited in the present submission must be uploaded as supporting files. This includes all cited manuscripts by the author or coauthors published this year, last year, in press or submitted. These files are made accessible to referees with the understanding that "in press" and "submitted" manuscripts represent privileged communications which may not be cited or used in any way other than for reference while reviewing the current manuscript. If there is a particular reason why a file should not be made available to reviewers, please point this out and provide an explanation in the cover letter.

This manuscript has not been published, is not under consideration for publication elsewhere.
Thank you for your consideration.

% Closing statement
\closing{Regards,}
\end{letter}
\end{document}
%-----------------------------------------------------------------------------%

### 2019-04-10 code/count_words.R

@@ -89,3 +89,8 @@ get_line_number <- function(filename, string){
   stringr::str_detect(text_lines, "# Introduction") %>%
     which()
 }
+
+# get the title of a document from its yaml header
+get_yaml_title <- function(filename){
+  rmarkdown::yaml_front_matter(filename)$title
+}

### 2019-04-10 main.R

@@ -214,9 +214,11 @@ reporting_plan <- drake_plan(
   msc_wordcount = count_words(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:intro_line_number),
   n_references = count_references(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:intro_line_number, refs_to_exclude = "@ref"),
   n_displays = count_displays(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:intro_line_number),
+  msc_title = get_yaml_title(file_in('paper/manuscript.Rmd')),
   render_pdf(knitr_in('paper/supp-info.Rmd'), file_out('paper/supp-info.pdf'), clean_md = FALSE),
   render_pdf(file_in('paper/draft-info.Rmd'), file_out('paper/draft-info.pdf'), clean_md = FALSE),
-  render_pdf(knitr_in('paper/manuscript.Rmd'), file_out('paper/manuscript.pdf'), clean_md = FALSE)
+  render_pdf(knitr_in('paper/manuscript.Rmd'), file_out('paper/manuscript.pdf'), clean_md = FALSE),
+  knitr::knit2pdf(knitr_in("paper/cover-letter.Rnw"), output = file_out("paper/cover-letter.tex"))
   )
 
 paper_plan <- rbind(

### 2019-04-12 code/pca.R
Fix PCA figure y axis label

@@ -343,7 +343,7 @@ plot_pca <- function(pcas, chosen_threshold){
     theme(legend.position = "none") +
     # coord_equal() +
     labs(x = paste0("1st component (", round(variances_data$`percentage of variance`[1]), "%)"),
-         y = paste0("1nd component (", round(variances_data$`percentage of variance`[2]), "%)"),
+         y = paste0("2nd component (", round(variances_data$`percentage of variance`[2]), "%)"),
          title = "(b) plant realised niches in PCA space",
          subtitle = "convex hulls of species niches across communities")
 

### 2019-04-12 paper/cover-letter.Rnw
Add hugo's papers to Cover Letter

@@
 \usepackage{hyperref}
+\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
+\addbibresource{phd-bibliography/pollen-competition.bib}
 % Name of sender
@@
     Prof. Tim Coulson,\\
-    Editor-in-chief,\\
+    Editorial Office,\\
     Ecology Letters
@@
 
+In this manuscript we show that
+
 The covering letter to the Editorial Office should succinctly describe why the enclosed work is novel, exciting and of general interest in ecology.
@@
 
-At the time of submission, PDFs of any recent manuscripts or book chapters by the author or coauthors and cited in the present submission must be uploaded as supporting files.
-This includes all cited manuscripts by the author or coauthors published this year, last year, in press or submitted.
-These files are made accessible to referees with the understanding that "in press" and "submitted" manuscripts represent privileged communications which may not be cited or used in any way other than for reference while reviewing the current manuscript.
-If there is a particular reason why a file should not be made available to reviewers, please point this out and provide an explanation in the cover letter.
+Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors, however the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.
 
-This manuscript has not been published, is not under consideration for publication elsewhere.
 Thank you for your consideration.

### 2019-04-12 paper/manuscript.Rmd
Minor changes to the discussion

@@
 
-loadd(abs_cordcount, msc_wordcount, n_displays, n_references)
+loadd(abs_wordcount, msc_wordcount, n_displays, n_references)
 ```
@@
 <!-- This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits.  -->
-To account for the non-independence of floral counts and weight all traits equally, we assigned the abundances a weight of 1/5 compared to other functional traits. 
+To account for the non-independence of floral counts and weight all traits equally, we assigned the abundances a weight of 1/5 (one for each month) compared to other functional traits. 
 We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
@@
 We found that overall neither facilitation nor competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
-Indeed, we found that the proportion of species that experienced a statistically significant positive or neggative relationship between heterospecific and conspecific pollen than neggative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)).
+Indeed, we found that the proportion of species that experienced a statistically significant positive or negative relationship between heterospecific and conspecific pollen than negative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)).
 Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
@@
 
-We then examined the potential roles played by four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality) play in pollen deposition. 
+We then examined the potential roles played by four ecological variables (number of shared pollinators, plant abundance, mean visit effectiveness, and functional originality) play in pollen deposition.
 <!-- Together these variables can describe the niche that plants might occupy in the context of competition for pollination.  -->
@@
 Hence, is likely that to ensure long term survival, plants also need to balance this risk with the costs of sharing pollinators. 
-One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it’s commonly thought that species that are further from others in trait space suffer reduced competition.
+One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it’s commonly thought that species that are further from others in trait space benefit from reduced competition.
 Yet again, there are two possible caveats to this strategy that highlight the interrelatedness of the ecological factors. 
@@
 For instance, a plant species that experience a large reduction in seed set due to heterospecific pollen deposition might be better off by sharing few pollinators, while sharing pollinators makes more sense for those mainly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
-Nevertheless, the diversity of the facilitation/competition outcomes across communities we observed and the relevance of random effects in our models suggests that the community context has a very important effect on the way plant species respond to competition for pollination beyond species identity.
-Perhaps overgeneralising, some plant families (Asteraceae for example) are often generalists in their communities, others (Orchidaceae) are known to be more commonly specialised. 
+Nevertheless, the observed diversity of the facilitation/competition outcomes across communities and the relevance of random effects in our models suggests that the community context has a very important effect on the way plant species respond to competition for pollination beyond species identity.
+Although there are exceptions, some plant families (Asteraceae for example) are often generalists in their communities while others (Orchidaceae) are known to be more commonly specialised. 
 While it is possible, from an evolutionary perspective, that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history, we show that most plant species are still flexible enough to adopt markedly different niches in different communities.
@@
 Species coexistence is not solely determined by direct and indirect mutualistic relationships, but also strongly shaped by the multiple intertwined ecological factors that shape competition for pollination at the community level.
-Achieving a better understanding of how biodiversity is supported by pollination communities will require seeing them as both mutualistic and competitive communities.
+Achieving a better understanding of how plant biodiversity is supported by pollination communities will require seeing them as both mutualistic and competitive communities.
 

### 2019-04-15 paper/cover-letter.Rnw
Ignore tex file of cover letter

@@
 
-Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors, however the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.
+Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors.
+However the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.
 

### 2019-04-15 paper/manuscript.Rmd
Add tentative title
Add some of Hugo's feedback to discussion

@@
 ---
-title: "The pollination trade-off"
+title: "Community context determines competition/facilitation trade-offs in pollination systems"
 author: 
@@
 
-All else being equal, our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
+Our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
 First, we found that the costs of pollinator sharing are pervasive. 
@@
 
-Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that net facilitation is only experienced by a fraction of species in a community. 
-Instead, we observed a negative relationships between conspecific and heterospecific in a considerable proportion of the analysed species. 
-This relationship could arise, for example, when another, more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; @lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma phisically interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
-Similarly, not all species had more pollen deposited when open to animal pollination compared to when they were closed. 
-Although it can be important, we were unable to test the effect of pollen viability or the extent to which self- vs. outcross-pollen may differ in their value for fertilization (TODO: ref needed). 
-However, it is reasonable to expect that the difference between these two may be generally relevant. 
-Particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy) (TODO: ref needed).
-These findings agree with a recent study showing a wide range of outcomes in a multi-species context [@tur_evaluating_2016]. 
-However, the factors explaining why some species experience more competition than others were not understood. 
-Here we show that the prevalence of neutral and competitive effects of animal-mediated pollination can be at least partially explained by the trade-offs that minimising competition can involve.
+Both of the criteria we used to identify the effect of animal-mediated pollination suggested the same outcome: that neither facilitation or competition are dominant in pollination communities.
+A previous study showed that in diverse pollination communities, sharing pollinators does not necessarily translate to net competition [@tur_evaluating_2016]. 
+The overall extent of facilitation/competition of pollination communities can depend on factors like the adversity of the environment [@tur_evaluating_2016; @callaway_positive_2002] or how disturbances affect pollinator populations [@stavert_exotic_2017]
+However, why some species experience more competition than others was not understood. 
+Here we show that the coexistence of facilitative and competitive effects of animal-mediated pollination can be at least partially explained by the trade-offs plants have to undergo when maximising the deposition of conspecific pollen and simultaneously minimising that of heterospecific pollen both in the short and the long term.
 
-These trade-offs were most evident in precisely the factors that most strongly modulate pollen deposition. 
-Specifically, we found that the factors related to the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition.
-At the same time, receiving high visitation increases the absolute levels of conspecific pollen deposition but increases heterospecific deposition to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen.
-Similarly, being abundant reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
-Multiple studies recognise the importance of visitation and abundance to competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
-Our results strongly corroborate the importance of these two factors but also suggest that [because visitation, pollen production and abundance are correlated; @sargent_role_2006], plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition to minimise competition for pollination.
-
-Further evidence of the intricacies of balancing costs and benefits can be found when we examine the other two factors analysed in our models. 
-We show that being a specialist and sharing no pollinators might be preferable in the short term (as it is generally detrimental to pollen deposition). 
+In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, as we show that sharing pollinators reduces conspecific pollen deposition both in absoluate terms and relative to heterospecific pollen.
 However, over long periods of time, there could be a risk associated with a specialist plant having no pollinators. 
@@
 One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it’s commonly thought that species that are further from others in trait space benefit from reduced competition.
-Yet again, there are two possible caveats to this strategy that highlight the interrelatedness of the ecological factors. 
+Yet, there are two possible caveats to this strategy that highlight the interrelatedness of the ecological factors. 
 First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators. 
@@
 
+Visit effectiveness (high pollen and visits) and abundance, which were the most important predictors of pollen deposition, involved an even more explicit trade-off between conspecific and heterospecific pollen.
+On the one hand, receiving high visitation increases the absolute levels of conspecific pollen deposition but increases heterospecific deposition to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen.
+On the other, being abundant reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
+Our results corroborate the importance that two-species studies have ascribed to visitation and abundance [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
+But importantly, they also suggest that [because visitation, pollen production and abundance are usually correlated; @sargent_role_2006] balancing the pros and cons of sharing pollinators at the community level is not trivial and might even be partially responsible for the diversity of plant-pollinator communities [@benadi_frequency_2018].
+
 How precisely plants balance the costs and benefits in the short and the long term likely depends on the species sensitivity to different risks but also, as we show here, on the community it belongs to.
+<!-- The mechanisms through which sharing pollinators may induce net competition are relatively well understood.  -->
+<!-- It can occurr for example, when a more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; @lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma phisically interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
+-->
+<!-- Similarly, not all species had more pollen deposited when open to animal pollination compared to when they were closed.  -->
+<!-- Although it can be important, we were unable to test the effect of pollen viability or the extent to which self- vs.
+outcross-pollen may differ in their value for fertilization (TODO: ref needed).
+-->
+<!-- However, it is reasonable to expect that the difference between these two may be generally relevant.  -->
+<!-- Particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy) (TODO: ref needed).
+-->
 For instance, a plant species that experience a large reduction in seed set due to heterospecific pollen deposition might be better off by sharing few pollinators, while sharing pollinators makes more sense for those mainly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
@@
 
+Extra potential refs:
+https://besjournals.onlinelibrary.wiley.com/doi/pdf/10.1111/1365-2745.12256
+https://academic.oup.com/aob/article/118/2/249/1741474
+https://www.jstor.org/stable/3547899?seq=1#metadata_info_tab_contents
+https://onlinelibrary.wiley.com/doi/full/10.1111/ele.12342
+
 # Acknowledgements

### 2019-04-18 paper/manuscript.Rmd
Couple more edits to discussion

@@
 
-How precisely plants balance the costs and benefits in the short and the long term likely depends on the species sensitivity to different risks but also, as we show here, on the community it belongs to.
+The strong contribution of the random effects in our models suggest that the effects of pollen deposition can vary greatly among species. 
+For instance, for some plant species even low amounts of heterospecific pollen deposition can have a large impact on fitness while other species might be instead limited by the amount of conspecific pollen deposited by animal pollination [@campbell_mechanism_1985; @arceo-gomez_interactive_2019].
+Similarly, plant species can also differ on the extent to which self- vs. outcross-pollen differ in their value for fertilization. 
+For species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy), even 
+Wether some patterns indicate facilitation or competition might
+
+Beyond species identity, however we show that the way plants balance the costs and benefits of sharing pollinators, beyond species identity, is strongly determined by the community it belongs to.
+
+Different species balance the costs and benefits differently as the effects of conspecific and 
+Here we also show that  
+Na
 <!-- The mechanisms through which sharing pollinators may induce net competition are relatively well understood.  -->
@@
 -->
-For instance, a plant species that experience a large reduction in seed set due to heterospecific pollen deposition might be better off by sharing few pollinators, while sharing pollinators makes more sense for those mainly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
 Nevertheless, the observed diversity of the facilitation/competition outcomes across communities and the relevance of random effects in our models suggests that the community context has a very important effect on the way plant species respond to competition for pollination beyond species identity.

### 2019-04-23 paper/manuscript.Rmd
Finish discussion story

--- 2019-04-15 paper/manuscript.Rmd
@@
 Our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
-First, we found that the costs of pollinator sharing are pervasive. 
-In particular, we found that a considerable proportion of species experiences overall neutral or competitive effects from animal-mediated pollination. 
-Second, we found that multiple ecological factors can modulate the intensity of this competition; however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these factors are likely to involve a trade-off between the quantity and quality of pollination.
+First, we found that pollinatior sharing can lead to both overall facilitative and competitive effects to plant species in a community. 
+Second, we found that multiple ecological factors can modulate the intensity of competition; however, conspecific and heterospecific pollen deposition are tightly coupled and therefore there is a clear trade-off between the quantity and purity of pollination [@thomson_effects_2019].
 Third, we found that the way these factors influence competition is strongly shaped by the community context, this is, if collectively these factors are used to define a niche of competition for pollination, the same plant species can occupy dramatically different niches depending on the community it belongs to.
@@
 
-In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, as we show that sharing pollinators reduces conspecific pollen deposition both in absoluate terms and relative to heterospecific pollen.
+In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, as we show that sharing pollinators reduces both the quantity and purity of the conspecific pollen deposited.
 However, over long periods of time, there could be a risk associated with a specialist plant having no pollinators. 
@@
 Yet, there are two possible caveats to this strategy that highlight the interrelatedness of the ecological factors. 
-First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators. 
-Second, the usually negative, relationship between originality and generalism has been shown depend on the plant's abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make it worth to pollinators.
-
-Visit effectiveness (high pollen and visits) and abundance, which were the most important predictors of pollen deposition, involved an even more explicit trade-off between conspecific and heterospecific pollen.
-On the one hand, receiving high visitation increases the absolute levels of conspecific pollen deposition but increases heterospecific deposition to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen.
-On the other, being abundant reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
+First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators [@reverte_pollinators_2016]. 
+Second, the negative, relationship between originality and generalism  [@carvalheiro_potential_2014] has been shown depend on the plant's abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make it worth to pollinators.
+Visit effectiveness (high pollen and visits) and abundance, which were the most important predictors of pollen deposition, involved an even more explicit trade-off between gaining  conspecific pollen and avoiding heterospecific pollen.
+On the one hand, receiving high visitation increases conspecific pollen deposition but increases heterospecific pollen to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen [@fang_paradoxical_2016].
+On the other, being abundant reduces the amount of heterospecific pollen deposited but this comes at the expense of a noticeable reduction in the amount of conspecific pollen. 
 Our results corroborate the importance that two-species studies have ascribed to visitation and abundance [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
@@
 
-How precisely plants balance the costs and benefits in the short and the long term likely depends on the species sensitivity to different risks but also, as we show here, on the community it belongs to.
-<!-- The mechanisms through which sharing pollinators may induce net competition are relatively well understood.  -->
-<!-- It can occurr for example, when a more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; @lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma phisically interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].
+We observed, as expected, that the effects of pollen deposition can vary widely among species. 
+For instance, while the fitness of some plant species can be hurt even by low amounts of heterospecific pollen, for others species, fitness can instead be limited by the amount of conspecific pollen [@campbell_mechanism_1985; @arceo-gomez_interactive_2019].
+Alternatively, plant species can also differ substantially on the extent to which self- vs. outcross-pollen differ in their value for fertilization. 
+The difference can be particularly relevant for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy).
+
+Importantly, here we show that the balances between cost and benefits are determined not only by species identity but also on the community plants belong to. 
+Specifically, most plant species appear to be flexible enough to adopt markedly different niches in different communities. 
+Although there are many exceptions, some plant families (Asteraceae for example) are often generalists in their communities while others (Orchidaceae) are known to be more commonly specialised [@johnson_generalization_2000].
+From an evolutionary perspective, our results suggest that that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history.
+Furthermore, from a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
+On the one hand, our results suggest that introduced plants that increasse the relative originality of natives (e.g. through distinct phenology) might have positive effects [@gibson_can_2012]. 
+On the other, because different niches can lead to different outcomes across communities, our results also highlight the difficulties involved in predicting whether the introduced plant species will facilitate or compete with neighbours [@bartomeus_contrasting_2008].
+Other factors that we were unable to measure (e.g.
+pollinator behaviour and densities or the spatial context) have also be shown to play a role in the outcome of animal-mediated pollination [@ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009; @thomson_effects_2019].
+Nevertheless our results indicate that the strategies plant might use to minimise competition for pollination must be relative to other species in the community, rather than an absolute property of the species.
+
+Overall, pollination communities might not necessarily be the paradigmatic mutualistic communities we often believe. 
+Instead, we confirm that plant competition is pervasive in pollination communities. 
+The potential strategies to minimise competition are likely to involve strong trade-offs in the pollination service both in the short and long-term. 
+<!-- Specifically, although not sharing pollinators and being functionally unique reduces competition for pollination by increasing the quantity and purity of conspecific pollen deposition.  --> 
+<!-- Remarkably, this increase is surprisingly small when compared to the effect of relative abundance and visitation.  -->
+<!-- Interestingly, these two factors also involve the largest trade-offs between increasing deposition of conspecific pollen and reducing that of heterospecific pollen.  -->
+Most remarkably, despite large differences on the quantity and purity of conspecific pollen deposition among species, our results provide solid evidence that competition for pollination is inherently a community process and the same species can occupy different niches in different communities.
+<!-- Overall, species coexistence is not solely determined by direct and indirect mutualistic relationships, but also strongly shaped by the multiple intertwined ecological factors that shape competition for pollination at the community level.
 -->
-<!-- Similarly, not all species had more pollen deposited when open to animal pollination compared to when they were closed.  -->
-<!-- Although it can be important, we were unable to test the effect of pollen viability or the extent to which self- vs.
-outcross-pollen may differ in their value for fertilization (TODO: ref needed).
--->
-<!-- However, it is reasonable to expect that the difference between these two may be generally relevant.  -->
-<!-- Particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy) (TODO: ref needed).
--->
-For instance, a plant species that experience a large reduction in seed set due to heterospecific pollen deposition might be better off by sharing few pollinators, while sharing pollinators makes more sense for those mainly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
-Nevertheless, the observed diversity of the facilitation/competition outcomes across communities and the relevance of random effects in our models suggests that the community context has a very important effect on the way plant species respond to competition for pollination beyond species identity.
-Although there are exceptions, some plant families (Asteraceae for example) are often generalists in their communities while others (Orchidaceae) are known to be more commonly specialised. 
-While it is possible, from an evolutionary perspective, that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history, we show that most plant species are still flexible enough to adopt markedly different niches in different communities.
-From a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
-Our results highlight the difficulties involved in predicting whether the introduced plant species will facilitate or compete with neighbours. 
-This is so because the outcome might depend not only on the particular niche each species occupies in a particular community but also on other factors that we were unable to measure [e.g.
-pollinator behaviour and densities or spatial context; @ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009].
-However, our results also suggest that introduced species are more likely to be beneficial if they have different traits to local plants. 
-<!-- cite melissa's paper if available before publication -->
-
-Overall, our results suggest that pollination communities might not necessarily be the paradigmatic mutualistic communities we often believe. 
-Instead, we confirm that plant competition is pervasive in pollination communities and that potential strategies to minimise competition are likely to involve strong trade-offs in the pollination service either in the short or the long term.
-As expected, not sharing pollinators and being functionally unique reduces competition for pollination by increasing conspecific pollen deposition (both in absolute numbers and relative to heterospecific pollen).
-However, this increase is surprisingly small when compared to the effect of relative abundance and visitation. 
-Interestingly, these two factors also involve the largest trade-offs between increasing deposition of conspecific pollen and reducing that of heterospecific pollen. 
-Despite large intra-species differences among species our results provide solid evidence of the role that competition for pollination plays in natural communities. 
-Species coexistence is not solely determined by direct and indirect mutualistic relationships, but also strongly shaped by the multiple intertwined ecological factors that shape competition for pollination at the community level.
-Achieving a better understanding of how plant biodiversity is supported by pollination communities will require seeing them as both mutualistic and competitive communities.
-
-Extra potential refs:
-https://besjournals.onlinelibrary.wiley.com/doi/pdf/10.1111/1365-2745.12256
-https://academic.oup.com/aob/article/118/2/249/1741474
-https://www.jstor.org/stable/3547899?seq=1#metadata_info_tab_contents
-https://onlinelibrary.wiley.com/doi/full/10.1111/ele.12342
+Many of the widely used theoretical models of plant-pollinator communities do not account for the negative effects of sharing pollinators [but see @rohr_structural_2014 and similars]. 
+However, achieving a better understanding of species coexistence and how plant biodiversity is supported by pollination communities will require seeing them as both mutualistic and competitive communities [@johnson_coexistence_2019].
 

### 2019-04-23 paper/manuscript.Rmd
Some extra refs

@@
 This evidence is aligned with the notion that a species which interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly (TODO: ref needed).
-If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012].
+If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012; @carvalheiro_potential_2014].
 Alternatively, it might also be the case that density (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 

### 2019-04-23 paper/manuscript.Rmd
Remove trait justification sentence

@@
 fontsize: 11pt
-classoption: a4paper
+# classoption: a4paper
 geometry: 
@@
 Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region.
-We used those traits because they were the only ones available. <!--.. (TODO: Add a better justification for the traits used)-->
+<!-- We used those traits because they were the only ones available. <!--.. (TODO: Add a better justification for the traits used)--> -->
 More details can be found in Marrero *et al.* (2014 and 2017).

### 2019-04-23 paper/manuscript.Rmd
Spell checking

@@
 
-**Running title:** The pollination trade off
+**Running title:** The pollination trade-off
 
@@
 
-**Data acessibility:** Data supporting the results will be accesible in an appropiate data repository after publication. The data DOI will be included here.
+**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. The data DOI will be included here.
 
@@
 Our second objective was to investigate the relative contribution of different factors---that describe the plant competition for pollination niche---to the pollination service. 
-Generally speaking, in the context of competition for pollination we expect that a factor that increasse on the amount of conspecific pollen deposited in stigmas (both in absolute terms and relative to heterospecific pollen) also has a positive effect on the pollination service.
+Generally speaking, in the context of competition for pollination, we expect that a factor that increases the amount of conspecific pollen deposited in stigmas (both in absolute terms and relative to heterospecific pollen) also has a positive effect on the pollination service.
 Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plants abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them, and (*iv*) the plants functional originality [@laliberte_distance-based_2010].
@@
 
-To investigate the impact of ecological factors on pollination service we used two sets of linear mixed models (LMM) with boothstrap resampling.
+To investigate the impact of ecological factors on pollination service we used two sets of linear mixed models (LMM) with bootstrap resampling.
 The response variables for these model sets were the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination. 
@@
 
-Because the amount of deposited pollen can vary widely across species, and potentially also across communities, we evaluated two possible structures for the random effects: one that includes a random intercept for plant species, and one that treats measures from species across different communities as independent.
+Because the amount of deposited pollen can vary widely across species, and potentially also across communities, we evaluated two possible structures for the random effects: one that includes a random intercept for plant species, and one that treats measures from species across different communities independently.
 We selected the best random structure by comparing the median Akaike Information Criterion for small samples (AICc).
@@
 Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers (Table \@ref(S-tab:table-open-bagged-models-general)). 
-Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had less pollen when open (the difference was statistically non-signifcant for the remainding `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
+Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had less pollen when open (the difference was statistically non-significant for the remaining `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
 Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both positive and negative differences.
@@
 Our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
-First, we found that pollinatior sharing can lead to both overall facilitative and competitive effects to plant species in a community. 
+First, we found that pollinator sharing can lead to both overall facilitative and competitive effects to plant species in a community. 
 Second, we found that multiple ecological factors can modulate the intensity of competition; however, conspecific and heterospecific pollen deposition are tightly coupled and therefore there is a clear trade-off between the quantity and purity of pollination [@thomson_effects_2019].
@@
 
-Both of the criteria we used to identify the effect of animal-mediated pollination suggested the same outcome: that neither facilitation or competition are dominant in pollination communities.
+Both of the criteria we used to identify the effect of animal-mediated pollination suggested the same outcome: that neither facilitation nor competition are dominant in pollination communities.
 A previous study showed that in diverse pollination communities, sharing pollinators does not necessarily translate to net competition [@tur_evaluating_2016]. 
@@
 Furthermore, from a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
-On the one hand, our results suggest that introduced plants that increasse the relative originality of natives (e.g. through distinct phenology) might have positive effects [@gibson_can_2012]. 
+On the one hand, our results suggest that introduced plants that increase the relative originality of natives (e.g. through distinct phenology) might have positive effects [@gibson_can_2012]. 
 On the other, because different niches can lead to different outcomes across communities, our results also highlight the difficulties involved in predicting whether the introduced plant species will facilitate or compete with neighbours [@bartomeus_contrasting_2008].
 Other factors that we were unable to measure (e.g.
-pollinator behaviour and densities or the spatial context) have also be shown to play a role in the outcome of animal-mediated pollination [@ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009; @thomson_effects_2019].
-Nevertheless our results indicate that the strategies plant might use to minimise competition for pollination must be relative to other species in the community, rather than an absolute property of the species.
+pollinator behaviour and densities or the spatial context) have also been shown to play a role in the outcome of animal-mediated pollination [@ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009; @thomson_effects_2019].
+Nevertheless, our results indicate that the strategies plant might use to minimise competition for pollination must be relative to other species in the community, rather than an absolute property of the species.
 
@@
 -->
-Many of the widely used theoretical models of plant-pollinator communities do not account for the negative effects of sharing pollinators [but see @rohr_structural_2014 and similars]. 
+Many of the widely used theoretical models of plant-pollinator communities do not account for the negative effects of sharing pollinators [but see @rohr_structural_2014 and similar]. 
 However, achieving a better understanding of species coexistence and how plant biodiversity is supported by pollination communities will require seeing them as both mutualistic and competitive communities [@johnson_coexistence_2019].

### 2019-04-24 paper/manuscript.Rmd
Change subheadings
Use pollination quantity and purity throughout

@@
 For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016].
-This evidence is aligned with the notion that a species which interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly (TODO: ref needed).
+This evidence is aligned with the notion that a species which interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly\R{ref-interaction-strength}.
 If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012; @carvalheiro_potential_2014].
@@
 Second, we investigate the relative contribution that four ecological factors have on the pollination service. 
-Specifically, we hypothesize that competition (measured as absolute and relative conspecific pollen deposition) should increase for plants that share many pollination partners.
+Specifically, we hypothesize that competition, measured as the quantity of conspecific pollen deposition and its purity (relative to heterospecific pollen), should increase for plants that share many pollination partners.
 However, we also hypothesize that other factors like the plant's functional originality, its relative abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
-Third, we examine how much does the community context influences the way plants use these factors to minimise competition. 
+Third and finally, we examine how much does the community context influences the way plants use these factors to minimise competition. 
 Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict the competition for pollination niche to be influenced by the local context.
-If plant strategy is not flexible across communities (TODO: ref needed), we could expect niches to be more similar within species than across species in the study. 
+If plant strategy is not flexible across communities\R{ref-plant-flexibility}, we could expect niches to be more similar within species than across species in the study. 
 On the contrary, if a species' strategy is flexible, we should expect plants to be able to occupy different niches in each community such that competition could be minimised regardless of the context.
@@
 Approximately a quarter of these buds were bagged to prevent animal pollination. 
-Two days after inflorescence, we collected all remaining flowers' and counted the pollen grains in their pistils. 
-We then classified them between conspecific and heterospecific pollen, and calculated the number of pollen grains per stigma in each flower. 
+Two days after inflorescence, we collected all remaining flowers' and counted the number of conspecific and heterospecific pollen grains in their pistils. 
 More details can be found in @marrero_agricultural_2016.
@@
 To evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution [@tur_evaluating_2016]. 
-In this model, the number conspecific pollen grains per stigma was the response variable and the number of heterospecific grains the predictor (the number of stigmas sampled from the flower was added as an offset term).
+In this model, the number of conspecific pollen grains per flower was the response variable and the number of heterospecific grains the predictor (the number of stigmas sampled was added as an offset term).
 The slope and intercept of this relationship were allowed to differ between plant species within each community, which were modelled as a random effect. 
 Models were fitted using the function `glmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]. 
-A positive slope for a plant-community combination might indicate facilitation while a negative slope might indicate competition.
+A positive slope for a plant-community combination might indicate facilitation while a negative slope might indicate competition [@tur_evaluating_2016].
 
@@
 
-## Ecological constraints the pollination service
+## Factors affecting quantity and purity of pollination service
 
 Our second objective was to investigate the relative contribution of different factors---that describe the plant competition for pollination niche---to the pollination service. 
-Generally speaking, in the context of competition for pollination, we expect that a factor that increases the amount of conspecific pollen deposited in stigmas (both in absolute terms and relative to heterospecific pollen) also has a positive effect on the pollination service.
+Generally speaking, in the context of competition for pollination, we expect that a factor that increases the amount of conspecific pollen deposited in stigmas, both in quantity and purity relative to heterospecific pollen, also has a positive effect on the pollination service.
 Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plants abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them, and (*iv*) the plants functional originality [@laliberte_distance-based_2010].
@@
 To estimate visit effectiveness we need to construct pollen transfer networks in addition to the visitation networks. 
-To construct the transfer networks, we examined the pollen loads present on the floral visitors collected [@marrero_exotic_2017]. 
+To do this, we examined the pollen loads present on the floral visitors collected [@marrero_exotic_2017]. 
 When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level when possible and to pollen complexes when it was not. 
 When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
-Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region.
-<!-- We used those traits because they were the only ones available. <!--.. (TODO: Add a better justification for the traits used)--> -->
+Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region\R{justification-traits}.
+<!-- We used those traits because they were the only ones available. <!--.. (TODO: Add a better justification for the traits used)--> 
 More details can be found in Marrero *et al.* (2014 and 2017).
@@
 
-To estimate the coefficients and to perform model selection and quantify the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with one hundred replicates.
+To estimate the coefficients, perform model selection, and quantify the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with one hundred replicates. 
 First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc (relative to the most likely model) for each bootstrap sample.
@@
 <!-- We "shrank" the estimated coefficient of potentially unimportant variables by setting their estimate to 0 when the variable was not included in the model.  -->
-Finally, we used these distributions of the model coefficients to estimate their mean impact on the pollination service (in terms of absolute and relative conspecific pollen deposition). 
+Finally, we used these distributions of the model coefficients to estimate their mean impact on the pollination service (in terms of quantity and purity of conspecific pollen deposition). 
 <!-- Again, here we used bootstrap resampling to estimate the uncertainty around these means.  -->
@@
 If community context plays a relatively small role or the species strategy is inflexible we would expect plants of the same species to fill similar competition for pollination niches across different communities.
-Alternatively, if the community plays a large role and plants strategies are flexible, we should be able to observe differences in the niche a plant species occupies across communities. 
+Alternatively, if the community plays a large role and plants strategies are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
 First, we used a principal component analysis (PCA) of the four ecological variables. 
@@
 
-## Ecological constraints in the pollination service
+## Factors affecting quantity and purity of pollination service
 
@@
 However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
-This indicates that, although there is a positive association between visit effectiveness and the *absolute* amount of conspecific pollen, there is a negative relationship with the *relative* amount of conspecific relative to heterospecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
-In contrast, a plants' relative abundance had a negative effect on the absolute amount of conspecific pollen, but the mean difference between the coefficients in the models indicates a positive association with the relative amount of conspecific pollen (Figure \@ref(fig:fig-average-qual-quant)c).
-The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the absolute and relative amount of conspecific pollen deposited. 
+This indicates that, although there is a positive association between visit effectiveness and the quantity pollen deposition, there is a negative relationship with its purity (Figure \@ref(fig:fig-average-qual-quant)c).
+In contrast, a plants' relative abundance had a negative effect on the pollen deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with the the purity (Figure \@ref(fig:fig-average-qual-quant)c).
+The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and purity. 
 Finally, the number of shared pollinators had a negative and neutral association with conspecific and heterospecific pollen, but these impacts were small when compared to the other variables.
@@
 Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
-One exception was visit-effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations (all with relatively low AICc support).
+One exception was visit-effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations. 
+Nevertheless, these differences were observed only in model specifications with relatively low AICc support.
 
@@
 
-We used a PCA of the analysed species to investigate whether plants' niche of competition for pollination is similar across communities or whether they are flexible, and therefore a reflection of the community context.
+We used a PCA of the analysed species to investigate whether plants' realised niche of competition for pollination is similar across communities or whether they are flexible, and therefore a reflection of the community context.
 The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 

### 2019-04-24 paper/draft-info.Rmd
Move up co-author requests to the top and add line numbers

@@
   - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
+  - \externaldocument[M-]{manuscript}
+
 ---
@@
 
+## Specific requests to coauthors
+
+* Suggest a justification for the traits used if needed (see \lr{M-justification-traits}). 
+* Identify sections/sentences to trim to achieve the word limit.
+* Suggest a reference for sentence in \lr{M-ref-interaction-strength} if needed.
+* Suggest a reference for sentence in \lr{M-ref-plant-flexibility} if needed. 
+* Suggest alternative, more-appropiate, sub-headings if needed.
+
 ## Changes
@@
 * Now using `docker` to manage project dependencies. Image is now available on dockerhub efcaguab/pollen-competition.
-* Removing *quantity* and *quality* of pollination in favour of the plain metrics of *conspecific* and *heterospecific* pollen deposition. 
+* Removing *quantity* and *quality* of pollination in favour of *quantity* and *purity* or plain metrics of *conspecific* and *heterospecific* pollen deposition. 
 * Rewording the plant strategies idea as it was confussing.
@@
 
-* Polish discussion, will appreciate input here. Hugo, feel free to make edits to the text. Large and small. will really appreciate specific input here. 
-* Polish supp. info.
 * Spell-check everything & check that reference list is correct.
 
-## Specific requests
-
-* Help suggesting a justification for the traits used. 
-* Help identifying sections to trim to achieve the word limit.
-
 Feel free to come back here after you've read the manuscript. Thanks!

### 2019-04-24 paper/manuscript.Rmd
Typo

@@
 This indicates that, although there is a positive association between visit effectiveness and the quantity pollen deposition, there is a negative relationship with its purity (Figure \@ref(fig:fig-average-qual-quant)c).
-In contrast, a plants' relative abundance had a negative effect on the pollen deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with the the purity (Figure \@ref(fig:fig-average-qual-quant)c).
+In contrast, a plants' relative abundance had a negative effect on the pollen deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with the purity (Figure \@ref(fig:fig-average-qual-quant)c).
 The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and purity. 

### 2019-04-24 paper/manuscript.Rmd
Update Fig 1 legend to make it clearer

@@
 facilitation at the community level.
-(a) Some species experience more competition for pollination than others.
+(a) According to the first criterion we used, some species experience more competition for pollination than others.
 Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities.
@@
 (b) Despite the variety of slopes, overall plants had more conspecific than heterospecific pollen deposited in their stigmas.
-(c) Generally, plants also had more pollen deposited in their stigmas when they were open to animal-mediated pollination than when they were closed.
+(c) The second criterion we used to distinguish between facilitation and competition shows similar patterns as the first one.
+Here we compare the amount of conspecific pollen deposited in plants' stigmas when they were open to animal-mediated pollination and when they were closed.
+Statistically significant negative differences (darkest shade) indicates competition while positive differences (lightest shade) indicates facilitation.
 In all plots, error bars correspond to $\\pm$ the standard error (SE)."}

### 2019-04-24 paper/manuscript.Rmd
Update Fig 2 and its legend to use quantity and purity

@@
 The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific and heterospecific pollen.
-(c) The end result of these associations is that only the plants' functional originality has a positive impact on both the absolute and relative amount of conspecific pollen deposition (relative to heterospecific pollen).
+(c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and purity of conspecific pollen deposition (relative to heterospecific pollen).
 The plot shows the model averaged mean effect ($\\pm$ SE of 99 bootstrap replicates)."}

### 2019-04-24 code/coefficient_averages.R

@@ -143,7 +143,7 @@ plot_coefficient_averages <- function(coefficient_averages, variable_importance)
 
     plots <- purrr::map(c("quantity", "quality"),
                         ~ plot_metric_qual_quan(qua_qua_data, .)) %>%
-      purrr::map2(c("absolute deposition\n(conspecific)", "relative deposition\n(consp. / heterosp.)"),
+      purrr::map2(c("quantity\n(conspecific)", "purity\n(consp. / heterosp.)"),
                   function(x,y) {x + labs(subtitle = y)})
 
     plots[[1]] <- plots[[1]] +

### 2019-04-24 paper/manuscript.Rmd
Update fig widths for draft PDF figures

@@
 # fig_con_con = plot_bagged_vs_open_conspecific(drake::readd(con_con_plot_df))
-# pdf(width = 6.5, height = 4)
+# pdf(width = 7.49, height = 4)
 drake::loadd(fig_random_slopes)
@@
 height2 <- 1.28
-# pdf(width = 3.25 , height = sum(c(height1, height2))*2)
+# pdf(width = 3.57 , height = sum(c(height1, height2))*2)
 # fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
@@
 # fig_pca_contrib <- plot_pca_variances_and_contributions(pcas, chosen_threshold = 0)
-# pdf(width = 3.25, height = strategy_fig_height)
+# pdf(width = 3.57, height = strategy_fig_height)
 drake::loadd(fig_pca_contrib)

### 2019-04-24 paper/manuscript.Rmd
Typo

@@
 
-To estimate the coefficients, perform model selection, and quantify the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with one hundred replicates. 
+To estimate the coefficients, perform model selection, and quantify the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with 99 replicates. 
 First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc (relative to the most likely model) for each bootstrap sample.

### 2019-04-26 paper/manuscript.Rmd
Remove bold figure title from Fig 3

@@
 
-```{r fig-pca, fig.width=3.57, fig.height=6.65, out.width="3.57in", out.height="6.65in",  out.extra="center", fig.cap="**The flexibility of plant strategies**.
+```{r fig-pca, fig.width=3.57, fig.height=6.65, out.width="3.57in", out.height="6.65in",  out.extra="center", fig.cap="The flexibility of plant strategies.
 (a) The two first components explain a large proportion of the total variance.

### 2019-04-26 paper/draft-info.Rmd
Update draft changes

@@
 * Suggest alternative, more-appropiate, sub-headings if needed. 
+* Check statement in \lr{M-theoretical-models}
 
@@
 * Added facilitation model results tables in the Supplementary Information
+* Applied a green palette to all figures. Improves legibility when looking at it in a screen an performance when printed in greyscale is maintained
+* Updated the headings in Figure 1 to make it clearer that we're looking at two distinct criteria
 * Made Figure 2 (model of enviornmental factors) one-column
-* Applied a green palette to all figures. Improves legibility when looking at it in a screen an performance when printed in greyscale is maintained
+* Labelled some of the polygons in Fig 3c to make it easier to understand
 * Moved some of the justification on the criteria used to identify facilitation/competition to the discussion.
@@
     * How attracting pollinators using flowering plants might work
-
-## Todo
-
-* Spell-check everything & check that reference list is correct.
-
-Feel free to come back here after you've read the manuscript. Thanks!
+* Reorganised the topics in the discussion

### 2019-04-26 paper/manuscript.Rmd
Add ref to theoretical models

@@
 
-**Number of words:** `r abs_wordcount$n_words_stri` in the abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in the main text.
+**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.
 
@@
 -->
-Many of the widely used theoretical models of plant-pollinator communities do not account for the negative effects of sharing pollinators [but see @rohr_structural_2014 and similar]. 
+Many of the widely used theoretical models of plant-pollinator communities do not account for the negative effects of sharing pollinators [but see @rohr_structural_2014 and similar]\R{theoretical-models}.
 However, achieving a better understanding of species coexistence and how plant biodiversity is supported by pollination communities will require seeing them as both mutualistic and competitive communities [@johnson_coexistence_2019].

### 2019-04-26 paper/draft-info.Rmd
Typos draft info

@@
 * Removing *quantity* and *quality* of pollination in favour of *quantity* and *purity* or plain metrics of *conspecific* and *heterospecific* pollen deposition. 
-* Rewording the plant strategies idea as it was confussing.
-Now the combination of ecological variables (number shared pol., abundance, visitation patterns, and traits) define a species *realised niche* (this was previoulsy called the plant strategy).
+* Rewording the plant strategies idea as it was confusing.
+Now the combination of ecological variables (number shared pol., abundance, visitation patterns, and traits) define a species *realised niche* (this was previously called the plant strategy).
 Plants that can have very different realised niches across different communities have a *flexible strategy* (this was previously called strategy as well).
@@
 * Sticking to past tense throughout the methods.
-* GLMM to fit slope of heterospecific-conspecific pollen relationship tests all communities at once (it was a model per community).
-Response variable is the number of grains (it was number of grains per stigma) and the (log) number of stigmas in the flowers has been included as an offset term.
+* GLMM to fit the slope of heterospecific-conspecific pollen relationship tests all communities at once (it was a model per community).
+The response variable is the number of grains (it was the number of grains per stigma) and the (log) number of stigmas in the flowers has been included as an offset term.
 * Using a similar approach to compare conspecific pollen deposited in open and bagged flowers (I used a series of Mann-Withney U tests before)
 * Added facilitation model results tables in the Supplementary Information
-* Applied a green palette to all figures. Improves legibility when looking at it in a screen an performance when printed in greyscale is maintained
+* Applied a green palette to all figures. Improves legibility when looking at it in a screen and the performance when printed in greyscale is maintained
 * Updated the headings in Figure 1 to make it clearer that we're looking at two distinct criteria
-* Made Figure 2 (model of enviornmental factors) one-column
+* Made Figure 2 (model of environmental factors) one-column
 * Labelled some of the polygons in Fig 3c to make it easier to understand
@@
 * Figures edited to match one and two column sizes at Ecology Letters. Implemented all format requirements for EL.
-* Added the following elements to the disussion: 
+* Added the following elements to the discussion: 
     * That our networks are a snapshot
-    * How the degree-trait originality relationship can be shaped by abundance
-    * How strategy could be a result of a specie's historical communities
+    * How the degree-trait originality relationship can be shaped by the abundance
+    * How strategy could be a result of a species historical communities
     * How attracting pollinators using flowering plants might work

### 2019-04-26 paper/draft-info.Rmd
Make draft info two-column

@@
 toc: false
+classoption: twocolumn
 header-includes:

### 2019-04-26 paper/manuscript.Rmd
Correct even more references...

@@
 <!-- FDO: Asked coauthors for a reference for the following statement but no-one provided. Therefore removing -->
-Alongside the direct mutualisms between plants and their pollinators, biodiversity can be supported as a result of the inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008].
+Alongside the direct mutualisms between plants and their pollinators, biodiversity can be supported as a result of the inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008; @liao_presence_2011].
 This inter-species facilitation is able to promote species coexistence by offsetting the effects of direct resource competition [@stachowicz_mutualism_2001]. 

### 2019-04-26 paper/manuscript.Rmd
Updated lopezaraiza citation key

@@
 These two mechanisms of competition, by definition, occur at the community scale. 
-However, with few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the deposition of conspecific and heterospecific pollen---and its relationship to competition vs.
+However, with few exceptions [@rathcke_interactions_1988; @lopezaraiza-mikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the deposition of conspecific and heterospecific pollen---and its relationship to competition vs.
 facilitation in pollination systems---is based on studies with two plant species.

### 2019-04-26 paper/cover-letter.Rnw
Finish cover letter

@@
 \addbibresource{phd-bibliography/pollen-competition.bib}
+\usepackage{geometry}
+\geometry{textwidth=43em, textheight=52\baselineskip}
 % Name of sender
@@
 
-In this manuscript we show that
+In this manuscript, we show that the realised competition for pollination niche (which can also be viewed as a plant species strategy to minimise competition for pollination) is strongly determined by the community it belongs to.
+Furthermore, we show that in pollination there is no free lunch and plants need to balance multiple trade-offs when minimising competition for pollination.
+On the one hand, factors that increase the quantity of pollen deposited by animals may also decrease its purity (and vice-versa).
+On the other, factors that increase both the quantity and purity do so only mildly and potentially only in the short-term.
 
-The covering letter to the Editorial Office should succinctly describe why the enclosed work is novel, exciting and of general interest in ecology.
+Very few studies have previously investigated how competition for pollination affects the pollination service at the community level using \emph{empirical data}.
+We do so and go one step beyond by collecting not only pollen-deposition data but also plant abundance, visitation, pollen transfer, phenology and traits.
+This allowed us to investigate the relationship between pollination service and multiple ecological factors, and for the first time, quantify the competition for pollination realised niche of plant populations.
 
-Additionally, the covering letter should include a clear statement of exactly how the present manuscript is outstandingly novel relative to recent work by the author or coauthors cited in the present submission.
+Most studies of pollination communities focus on the mutualistic aspects of plant-pollination communities.
+Ours provides evidence that animal-mediated pollination is actually a fluid dance between competition and pollination, and as such call for a shift in the way we think about pollination in community ecology.
 
 Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors.
-However the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.
+However, the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.
 

### 2019-04-26 paper/draft-info.Rmd
Format draft info

--- 2019-04-26 paper/draft-info.Rmd
@@
 ---
-title: "The pollination trade-off"
-subtitle: "Draft information"
-author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
+title: "Draft information"
+subtitle: "version: draft-4.0"
+date: "2019-04-26"
+# author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
 bibliography: phd-bibliography/pollen-competition.bib
@@
 toc: false
+geometry: 
+  - textwidth=33em
+  - textheight=48\baselineskip
+# classoption: twocolumn
 header-includes:
@@
 
-## Specific requests to coauthors
+## Requests to coauthors
 
@@
 
-## Changes
+## Changes since last draft
 

### 2019-04-26 paper/draft-info.Rmd
Add keywords

@@
 * Figures edited to match one and two column sizes at Ecology Letters. Implemented all format requirements for EL.
-* Added the following elements to the discussion: 
+* Rewrote the discussion and added the following elements: 
     * That our networks are a snapshot
@@
     * How attracting pollinators using flowering plants might work
-* Reorganised the topics in the discussion
+* Wrote abstract & keyworkds
+* Wrote cover letter

### 2019-04-26 paper/manuscript.Rmd
Add keywords
Remove ref to supp info figure that has been removed too

@@
 
-**Keywords:** X,Y,Z (up to 10).
+**Keywords:** Competition, facilitation, interspecific pollen transfer, conspecific, pollen deposition, multi-species, plant-pollinator interaction, pollination trade-off, pollination costs, networks (up to 10).
 
@@
 The response variables for these model sets were the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination. 
-We used LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) because these models offered a better fit than a GLMM with Poisson (or quasipoisson) error structure.
+We used LMMs in which pollen loads were log-transformed because these models offered a better fit than a GLMM with Poisson (or quasipoisson) error structure. 
 Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].

### 2019-04-28 paper/manuscript.Rmd
dbs edits and comments prior to the fire alarm

@@
 
-Animal pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011].
+Animal pollination plays a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
 <!-- FDO: Asked coauthors for a reference for the following statement but no-one provided. Therefore removing -->
-Alongside the direct mutualisms between plants and their pollinators, biodiversity can be supported as a result of the inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008; @liao_presence_2011].
+Alongside the direct benefits of mutualisms between plants and their pollinators, biodiversity can be supported as a result of the inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008; @liao_presence_2011].
 This inter-species facilitation is able to promote species coexistence by offsetting the effects of direct resource competition [@stachowicz_mutualism_2001]. 
@@
 One explanation is that plants are effectively competing for mutualistic partners because there is a *trade-off* between the benefits gained from maximising the number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
-It has been clear for a long time that when competition for pollination is strong enough, these costs can make it detrimental to plants' fitness [shown both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970].
+It has been clear for a long time that when competition for pollination is strong enough, these costs can make pollination detrimental to plants' fitness [shown both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970].
 In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000]. 
-It is less clear, however, how exactly ecological differentiation, in turn, affect the trade-off between facilitation and competition that is involved in the pollination service.
+However, it is less clear how exactly ecological differentiation, in turn, affects the trade-off between facilitation and competition that is involved in the pollination service.
+<!-- DBS; The end of the sentence above is confusing. Is it because what you mean by "the pollination service" hasn't been made explicit yet? -->
 
 There are two main mechanisms through which competition for pollinators can affect plant fertilization [@morales_interspecific_2008]. 
-The first is intraspecific pollen transfer. 
-This happens, for example, when plants with distinctively attractive flowers might reduce the number of visits to those less attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
-The second is intraspecific pollen transfer and occurs when plants share pollination partners. 
+The first is by changes in intraspecific pollen transfer.
+<!-- DBS: The above should be interspecific, no? -->
+This happens, for example, when plants with more attractive flowers might reduce the number of visits to those less of attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
+The second is via intraspecific pollen transfer and occurs when plants share pollination partners. 
 In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
-Generally speaking, the higher the amount of conspecific pollen (both in absolute terms and relative to heterospecific pollen) the better the pollination service received by the focal plant.
-These two mechanisms of competition, by definition, occur at the community scale. 
+Generally speaking, the higher the amount of conspecific pollen (both in absolute terms and relative to heterospecific pollen), the better the pollination service received by the focal plant.
+By definition, these two mechanisms of competition occur at the community scale. 
 However, with few exceptions [@rathcke_interactions_1988; @lopezaraiza-mikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the deposition of conspecific and heterospecific pollen---and its relationship to competition vs.
-facilitation in pollination systems---is based on studies with two plant species.
+facilitation in pollination communities---is based on studies with two plant species.
 
 At the community scale, the factors that determine the patterns of conspecific and heterospecific pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
+<!-- DBS: Fer, I absolutely love this sentence. -->
 For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016].
-This evidence is aligned with the notion that a species which interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly\R{ref-interaction-strength}.
+This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly\R{ref-interaction-strength}.
+<!-- DBS: Doesn't Bascompte et al 2006 Science show this? Or maybe Thébault and Fontaine 2008 Oikos? -->
 If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012; @carvalheiro_potential_2014].
-Alternatively, it might also be the case that density (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
+Alternatively, it might also be the case that abundance (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
 Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators.
 In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount of conspecific pollen relative to heterospecific pollen.
+<!-- DBS: I feel like the paragraph starts to lose the plot in the bit that follows. Where did realised niche come from and why invoke it? -->
 Altogether, it is clear that some ecological factors can influence pollen deposition and that these factors, in the specific context of pollination, could be used to roughly define a species *realised niche* in their community.
@@
 On the one hand, we could expect an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the amount of heterospecific pollen [@tur_evaluating_2016]. 
-The higher the deposition of conspecific pollen relative to heterospecific, the larger the slope of that relationship.
-On the other, we could also expect a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination. 
-Second, we investigate the relative contribution that four ecological factors have on the pollination service. 
-Specifically, we hypothesize that competition, measured as the quantity of conspecific pollen deposition and its purity (relative to heterospecific pollen), should increase for plants that share many pollination partners.
+The higher the deposition of conspecific pollen relative to heterospecific, the larger the slope of this relationship.
+On the other hand, we could expect a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination. 
+Second, we investigate the relative contribution that four ecological factors have to the pollination service. 
+Specifically, we hypothesize that competition, measured as the quantity of conspecific pollen deposition and its purity (amount relative to heterospecific pollen), should increase for plants that share many pollination partners.
+<!-- DBS: Should we interchange amount and quantity so loosely like in the start of the sentence above?
+Also, it seems weird to call quantity of conspecific pollen a proxy for competition since it should be the inverse...
+-->
 However, we also hypothesize that other factors like the plant's functional originality, its relative abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
-Third and finally, we examine how much does the community context influences the way plants use these factors to minimise competition. 
+Third and finally, we examine how much the community context influences the way plants exploit these factors to minimise competition. 
 Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict the competition for pollination niche to be influenced by the local context.
-If plant strategy is not flexible across communities\R{ref-plant-flexibility}, we could expect niches to be more similar within species than across species in the study. 
-On the contrary, if a species' strategy is flexible, we should expect plants to be able to occupy different niches in each community such that competition could be minimised regardless of the context.
+<!-- DBS: I find the phrase "competition for pollination niche" to be very clunky. Can we do better? -->
+If plant strategy is not flexible across the communities in our study\R{ref-plant-flexibility}, we could expect niches to be more similar within species than across species. 
+On the contrary, if a species' strategy is flexible, we should expect plants to be able to occupy different niches in each community such that competition could ultimately be minimised regardless of the context.
+<!-- DBS: Why do we always say could and not would? -->
 
@@
 We collected data from eleven co-flowering plant communities and their pollinators in three locations in the Argentinian Pampas. 
-These locations are distributed across a precipitation gradient with a humid temperate climate of the eastern Flooding Pampas becoming drier as one moves inland and westward towards the Pampean Grasslands.
+These locations are distributed across a precipitation gradient with the humid temperate climate of the eastern Flooding Pampas becoming drier as one moves inland and westward towards the Pampean Grasslands.
 This precipitation gradient generated a natural gradient of network architecture which allowed us to examine the generality of our findings.
+<!-- DBS: "Natural gradient" of network architecture seems purposefully vague. -->
 In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where we were only able to sample one restored fragment due to the lack of available sites.
@@
 
-Our first objective was to identify whether the outcome of plants sharing pollinators at the community level is facilitation or competition. 
+Our first objective was to identify whether the net outcome of plants sharing pollinators at the community level is facilitation or competition. 
 We use two complementary lines of evidence.  
-The first line can be found via the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
+The first can be found via the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
 This is because heterospecific pollen can be seen as an unavoidable cost that plants must pay for receiving conspecific pollen from shared pollinators. 
@@
 Approximately a quarter of these buds were bagged to prevent animal pollination. 
-Two days after inflorescence, we collected all remaining flowers' and counted the number of conspecific and heterospecific pollen grains in their pistils. 
+Two days after inflorescence, we collected all remaining flowers and counted the number of conspecific and heterospecific pollen grains in their pistils. 
 More details can be found in @marrero_agricultural_2016.
@@
 To evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution [@tur_evaluating_2016]. 
-In this model, the number of conspecific pollen grains per flower was the response variable and the number of heterospecific grains the predictor (the number of stigmas sampled was added as an offset term).
+In this model, the number of conspecific pollen grains per flower was the response variable and the number of heterospecific grains the predictor variable (the number of stigmas sampled was added as an offset term).
+<!-- DBS: I have a technical question about this offset. Is it the raw count or the log of said count? -->
 The slope and intercept of this relationship were allowed to differ between plant species within each community, which were modelled as a random effect. 
+<!-- DBS: This is slightly ambiguous. Are communities or species the random effect? -->
 Models were fitted using the function `glmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]. 
 A positive slope for a plant-community combination might indicate facilitation while a negative slope might indicate competition [@tur_evaluating_2016]. 
+<!-- DBS: Everywhere else, we use definitive language about this interpretation. Here we temper it with 'might'. Why? -->
 
 To compare the conspecific pollen deposited with and without animal-mediated pollination, we followed the same approach as above. 
-In this case, however, the predictor was the treatment (whether the flower was bagged or unbagged) instead of the number of heterospecific grains.
+In this case, however, the predictor variable was the treatment (whether the flower was bagged or unbagged) instead of the number of heterospecific grains.
 
@@
 
-Our second objective was to investigate the relative contribution of different factors---that describe the plant competition for pollination niche---to the pollination service. 
-Generally speaking, in the context of competition for pollination, we expect that a factor that increases the amount of conspecific pollen deposited in stigmas, both in quantity and purity relative to heterospecific pollen, also has a positive effect on the pollination service.
-Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plants abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them, and (*iv*) the plants functional originality [@laliberte_distance-based_2010].
+Our second objective was to investigate the relative contribution of different factors---that describe the plants' competition for pollination niches---to the pollination service. 
+Generally speaking,
+<!-- in the context of competition for pollination, -->
+we expect that any factor that increases the amount of conspecific pollen deposited in stigmas, both in quantity and purity relative to heterospecific pollen, also has a positive effect on the pollination service.
+<!-- DBS: There is no use to calling it something succinct like purity if we always have to say "purity relative to heterospecific pollen"...  -->
+Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines
+the share of pollen that a plant species is able to place on each of their floral visitors
+<!-- DBS: The line above is very confusing and took me about five reads before I understood what you wanted to say. We need to revise it. -->
+and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010]. 
 See *Data Analysis* section below for more details on these four variables. 
@@
 We visited the transects each month between November 2010 and March 2011. 
-To obtain plant abundance, we counted all units of floral attraction found during an independent sampling of the transects used to construct the quantitative visitation networks. 
-To estimate visit effectiveness we need to construct pollen transfer networks in addition to the visitation networks. 
+To obtain plant abundance, we counted all units of floral attraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
+To estimate visit effectiveness, we need to construct pollen transfer networks in addition to the visitation networks. 
 To do this, we examined the pollen loads present on the floral visitors collected [@marrero_exotic_2017]. 
 When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level when possible and to pollen complexes when it was not. 
-When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
+When the pollen count was above 2,000 grains, we classified approximately 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
 Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region\R{justification-traits}.
 <!-- We used those traits because they were the only ones available. <!--.. (TODO: Add a better justification for the traits used)--> 
+<!-- DBS: I bet we can get away with submitting without justifying the traits. -->
 More details can be found in Marrero *et al.* (2014 and 2017).
@@
 
-To investigate the impact of ecological factors on pollination service we used two sets of linear mixed models (LMM) with bootstrap resampling.
+To investigate the impact of ecological factors on pollination service, we used two sets of linear mixed models (LMM) with bootstrap resampling.
 The response variables for these model sets were the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination. 
-We used LMMs in which pollen loads were log-transformed because these models offered a better fit than a GLMM with Poisson (or quasipoisson) error structure. 
+We used LMMs in which pollen loads were log-transformed because these models offered a better fit than equivalent GLMMs with Poisson (or quasi-Poisson) error structure. 
 Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].

### 2019-04-28 paper/manuscript.Rmd
dbs edits to the remainder of the main text

@@
 
-As predictors in the models, we included the four ecological variables described above. 
+As fixed predictors in the models, we included the four ecological variables described above. 
 Specifically, we calculated the number of shared pollinators for each plant species by pooling data from the qualitative and quantitative pollination networks. 
 <!-- This variable is strongly correlated to the number of animal species a plant interacts with (the species degree).  -->
-To calculate the plants' relative abundance in their community, we simply aggregated floral counts for each species. 
-We then calculated the mean visit effectiveness. 
-We define the effectiveness of a visit by pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
+To calculate the plants' relative abundance in their community, we aggregated floral counts for each species. 
+We then calculated the mean visit effectiveness of pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\], where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
 Because the number of shared pollinators, floral abundance, visitation, and pollen production roughly followed a power-law distribution, we log-transformed these three predictors before including them in the model.
+<!-- DBS: Log transforming power-law distributed variables doesn't give them a natural scale (which is the overarching point of transforming variables) since they're scale free by definition... -->
 
@@
 <!-- As phenology has been shown to be a key mechanism of niche differentiation among plants, we also  -->
-To include phenology, we treated plant abundance in each of the survey months (November to March) as a "trait" in our analysis. 
+To include phenological variation, we treated plant abundance in each of the survey months (November to March) as a "trait" in our analysis. 
 <!-- This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits.  -->
@@
 Finally, to facilitate comparison across the four continuous explanatory variables in our models, we rescaled them all to have a zero mean and unitary variance.
+<!-- DBS: I'm lost. Why did we scale and then rescale? This doesn't seem to make any sense. -->
 
@@
 <!-- Again, here we used bootstrap resampling to estimate the uncertainty around these means.  -->
+<!-- DBS: This is a great example where we use 'purity' on its own. -->
 
@@
 Our last objective was to tease apart the plant strategies that might reduce competition and, importantly, how the community context influences these strategies.
-If community context plays a relatively small role or the species strategy is inflexible we would expect plants of the same species to fill similar competition for pollination niches across different communities.
-Alternatively, if the community plays a large role and plants strategies are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
-First, we used a principal component analysis (PCA) of the four ecological variables. 
+<!-- DBS: Thinking out loud here, but are the strategies for reducing competition or for increasing facilitation/mutualism?  -->
+If community context plays a relatively small role or the species strategy is inflexible, we would expect plants of the same species to fill similar competition for pollination niches across different communities.
+Alternatively, if the community plays a large role and/or plants strategies are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
+To test this, we first used a principal component analysis (PCA) of the four ecological variables. 
 We scaled variables across the whole study to ensure that the PCA space does not change according to the species present in each community. 
@@
 We first examined the degree of facilitation/competition in natural communities.
-Specifically, we examined the slope of the relationship between the heterospecific and conspecific pollen deposited on stigmas of each species in a community.
-We found that overall neither facilitation nor competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
-Indeed, we found that the proportion of species that experienced a statistically significant positive or negative relationship between heterospecific and conspecific pollen than negative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)).
+Specifically, we examined the slope of the relationship between the quantities of heterospecific and conspecific pollen deposited on stigmas of each species in a community.
+Overall, we found that neither net facilitation nor net competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
+Indeed, we found that the proportions of species that experienced a statistically significant positive or negative relationship between heterospecific and conspecific pollen were very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)).
+<!-- DBS: Fer, please check my edit above to make sure it's correct. -->
 Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
 For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others.
-Interestingly, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
+Interestingly, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
 
@@
 
-Of the four variables, we considered, we found that a plant's mean visit effectiveness and abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
+Of the four variables we considered, we found that a plant's mean visit effectiveness and realtive abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
 Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
+<!-- DBS: Two-sentence paragraphs are universally frowned upon. -->
 
@@
 The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and purity. 
-Finally, the number of shared pollinators had a negative and neutral association with conspecific and heterospecific pollen, but these impacts were small when compared to the other variables.
+Finally, the number of shared pollinators had negative and neutral associations with conspecific and heterospecific pollen, respectively, but these impacts were small when compared to the other variables.
 
-Overall, collinearity did not affect our findings qualitatively.
+Overall, collinearity between predictors did not qualitatively affect our findings.
 Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
@@
 Nevertheless, these differences were observed only in model specifications with relatively low AICc support.
+<!-- DBS: I think we can cut this. It's low hanging fruit for a reviewer to ask, we know the answer is unimportant, and hence can save some space by cutting it (for now). -->
 
@@
 
-We used a PCA of the analysed species to investigate whether plants' realised niche of competition for pollination is similar across communities or whether they are flexible, and therefore a reflection of the community context.
+We used a PCA of the analysed species to investigate whether plants' realised niches of competition for pollination is similar across communities or whether they are flexible and therefore a reflection of the community context.
 The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
 The first component was dominated by changes in visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality.
+<!-- DBS: Why "changes" in visit effectiveness? -->
 When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
-Indeed, when we measured the median distance between the plants coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` analysed species (Figure \@ref(fig:fig-pca)c).
+Indeed, when we measured the median distance between the plants coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` species analysed (Figure \@ref(fig:fig-pca)c).
+<!-- DBS: Are we consistent with UK vs US spellings? Does Ecology Letters prefer UK spelling? -->
 
@@
 Our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
-First, we found that pollinator sharing can lead to both overall facilitative and competitive effects to plant species in a community. 
-Second, we found that multiple ecological factors can modulate the intensity of competition; however, conspecific and heterospecific pollen deposition are tightly coupled and therefore there is a clear trade-off between the quantity and purity of pollination [@thomson_effects_2019].
-Third, we found that the way these factors influence competition is strongly shaped by the community context, this is, if collectively these factors are used to define a niche of competition for pollination, the same plant species can occupy dramatically different niches depending on the community it belongs to.
+<!-- DBS: In the intro, it's about net outcome. Here, it's about net cost or benefit. Which is it? -->
+First, we found that pollinator sharing can lead to both net facilitative and net competitive effects to plant species in a community. 
+Second, we found that multiple ecological factors can modulate the intensity of competition; however, conspecific and heterospecific pollen deposition are tightly coupled and this creates a clear trade-off between the quantity and purity of pollination [@thomson_effects_2019].
+Third, we found that the way these factors influence competition is strongly shaped by the community context.
+That is, if these factors collectively define a species' niche of competition for pollination,
+<!-- DBS: Yet another way to phrase this concept... -->
+the same plant species can occupy dramatically different niches depending on the community to which it belongs.
 
 Both of the criteria we used to identify the effect of animal-mediated pollination suggested the same outcome: that neither facilitation nor competition are dominant in pollination communities.
-A previous study showed that in diverse pollination communities, sharing pollinators does not necessarily translate to net competition [@tur_evaluating_2016]. 
+A previous study showed that, in diverse pollination communities, sharing pollinators does not necessarily translate to net competition [@tur_evaluating_2016]. 
 The overall extent of facilitation/competition of pollination communities can depend on factors like the adversity of the environment [@tur_evaluating_2016; @callaway_positive_2002] or how disturbances affect pollinator populations [@stavert_exotic_2017]
 However, why some species experience more competition than others was not understood. 
-Here we show that the coexistence of facilitative and competitive effects of animal-mediated pollination can be at least partially explained by the trade-offs plants have to undergo when maximising the deposition of conspecific pollen and simultaneously minimising that of heterospecific pollen both in the short and the long term.
+Here we show that the coexistence of facilitative and competitive effects of animal-mediated pollination can be at least partially explained by the trade-offs plants have to face when simultaneously maximising the deposition of conspecific pollen and minimising that of heterospecific pollen in both the short and the long term.
 
@@
 However, over long periods of time, there could be a risk associated with a specialist plant having no pollinators. 
-Hence, is likely that to ensure long term survival, plants also need to balance this risk with the costs of sharing pollinators. 
+To ensure long-term survival, it is thus likely that plants also need to balance this risk with the costs of sharing pollinators. 
 One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it’s commonly thought that species that are further from others in trait space benefit from reduced competition.
@@
 First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators [@reverte_pollinators_2016]. 
-Second, the negative, relationship between originality and generalism  [@carvalheiro_potential_2014] has been shown depend on the plant's abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make it worth to pollinators.
-Visit effectiveness (high pollen and visits) and abundance, which were the most important predictors of pollen deposition, involved an even more explicit trade-off between gaining conspecific pollen and avoiding heterospecific pollen.
-On the one hand, receiving high visitation increases conspecific pollen deposition but increases heterospecific pollen to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen [@fang_paradoxical_2016].
-On the other, being abundant reduces the amount of heterospecific pollen deposited but this comes at the expense of a noticeable reduction in the amount of conspecific pollen. 
-Our results corroborate the importance that two-species studies have ascribed to visitation and abundance [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
-But importantly, they also suggest that [because visitation, pollen production and abundance are usually correlated; @sargent_role_2006] balancing the pros and cons of sharing pollinators at the community level is not trivial and might even be partially responsible for the diversity of plant-pollinator communities [@benadi_frequency_2018].
+Second, the negative relationship between originality and generalism  [@carvalheiro_potential_2014] also depends on plant abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make visiting worthwhile to pollinators.
+
+Visit effectiveness (high pollen and visits) and abundance, which were the most important predictors of pollen deposition here, introduced an even more explicit trade-off between gaining conspecific pollen and avoiding heterospecific pollen.
+On the one hand, receiving high visitation increases conspecific pollen deposition but increases heterospecific pollen deposition to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen [@fang_paradoxical_2016].
+On the other hand, being abundant reduces the amount of heterospecific pollen deposited but this comes at the expense of a noticeable reduction in the amount of conspecific pollen. 
+Our results corroborate the importance that two-species studies have ascribed to visitation and abundance [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008], 
+but they also suggest that [because visitation, pollen production and abundance are usually correlated; @sargent_role_2006] balancing the pros and cons of sharing pollinators at the community level is not trivial and might even be partially responsible for the diversity of plant-pollinator communities [@benadi_frequency_2018].
 
@@
 
-Importantly, here we show that the balances between cost and benefits are determined not only by species identity but also on the community plants belong to. 
+Importantly, we show here that the balances between costs and benefits are determined not only by species identity but also on the community plants belong to. 
 Specifically, most plant species appear to be flexible enough to adopt markedly different niches in different communities. 
 Although there are many exceptions, some plant families (Asteraceae for example) are often generalists in their communities while others (Orchidaceae) are known to be more commonly specialised [@johnson_generalization_2000].
+<!-- DBS: I'd cut the sentence above. -->
 From an evolutionary perspective, our results suggest that that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history.
 Furthermore, from a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
+<!-- DBS: Below, we do the 'on the one hand', 'on the other (hand)' dance for the third or fourth time. We should change some of them to spice things up. -->
 On the one hand, our results suggest that introduced plants that increase the relative originality of natives (e.g. through distinct phenology) might have positive effects [@gibson_can_2012]. 
@@
 pollinator behaviour and densities or the spatial context) have also been shown to play a role in the outcome of animal-mediated pollination [@ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009; @thomson_effects_2019].
-Nevertheless, our results indicate that the strategies plant might use to minimise competition for pollination must be relative to other species in the community, rather than an absolute property of the species.
+Nevertheless, our results indicate that the strategies plant might use to successfully minimise competition for pollination must be determined relative to other species in the community, rather than an absolute property of the species itself.
 
@@
 
+<!-- DBS: If we're really looking for a paragraph to cut, we can cut this last one in its entirety. -->
+
 # Acknowledgements

### 2019-04-29 paper/manuscript.Rmd
edine
small tweak to caption 2
small tweaks to caption 3; I'm still not entirely convinced by the long-winded explanation of (b)

@@
 (a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
-Meanwhile, the number of shared pollinators was relatively unimportant.
+Meanwhile, the number of shared pollinators was generally less important.
 The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable.
@@
 (a) The two first components explain a large proportion of the total variance.
-(b) When plants that were sampled in more than one community are plotted with these two components, we observe that points, which represent the strategy (the particular combination of ecological variables) of a species in a community do not seem to be grouped by plant species.
+(b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points—which represent the strategy (the particular combination of ecological variables) of that species in its community—do not seem to be grouped by plant species.
 (c) This was confirmed using Monte Carlo randomizations of the median distance between strategies of a plant species.
-Only one of the examined species had strategies that were more tightly connected than what would be expected at random."}
+Only one of the examined species had strategies that were closer together than would be expected at random."}
 height0 <- 1.55
@@
 
+<!-- ESC: hi fernando. i'm edine. i'm here with my papa. have a nice day!!!!!! -->
+
 # Acknowledgements

### 2019-04-29 paper/cover-letter.Rnw
Some dbs edits to the cover letter, comments left behind, and a few fill in the blanks too for good measure

--- 2019-04-15 paper/cover-letter.Rnw
@@
 {
-    Prof. Tim Coulson,\\
+    Prof.\ Tim Coulson,\\
     Editorial Office,\\
@@
 
-In this manuscript we show that
+In this manuscript, we show that the realised competition for pollination niche (which can also be viewed as a plant species strategy to minimise competition for pollination) is strongly determined by the community it belongs to.
+% DBS: The sentence above just reaffirms my belief that "competition for pollination niche" is NOT the wording we want to use.
+Furthermore, we show that even in pollination there is no such thing as a free lunch, and plants need to balance multiple trade-offs when minimising competition for pollination.
+On the one hand, factors that increase the quantity of pollen deposited by animals may also decrease its purity (and vice-versa).
+On the other, factors that increase both the quantity and purity do so only mildly and potentially only in the short-term.
+% DBS: one hand and the other, again...
+% DBS: The use of short-term here is very ambiguous.
 
-The covering letter to the Editorial Office should succinctly describe why the enclosed work is novel, exciting and of general interest in ecology.
+Very few studies have previously investigated how competition for pollination affects the pollination service using empirical data \emph{at the community level}.
+When they have, XXX and YYY.
+Here, we take this approach a critical step beyond by not only collecting pollen-deposition data but also visitation, pollen transfer, and plant abundance, phenology and traits.
+These extra pieces of information allowed us to interrogate the relationship between pollination service and multiple ecological factors, and, for the first time, quantify the competition for pollination realised niche of plant populations.
+% DBS: And again, it just can't roll off anyone's tongue.
 
-Additionally, the covering letter should include a clear statement of exactly how the present manuscript is outstandingly novel relative to recent work by the author or coauthors cited in the present submission.
+Within the literature, studies of pollination almost always focus on the inherently mutualistic aspects of plant-pollinator communities. In contrast,
+ours provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
+This calls for a critical shift in the way we think about pollination in community ecology, as well as XXX.
 
 Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors.
-However the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.
+However, the enclosed work represents a novel contribution for all involved, and no related work published, in press, or submitted during this or last year has been cited.
 

### 2019-05-02 paper/manuscript.Rmd

@@
 facilitation at the community level.
-(a) According to the first criterion we used, some species experience more competition for pollination than others.
-Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities.
-Statistically significant negative slopes (darkest shade) indicate that plants experience competition for animal-mediated pollination, while significantly positive slopes (lightest shade) indicate that facilitation is the predominant outcome.
+(a) Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in each of their communities.
+Statistically significant negative slopes (darkest shade) indicate that plants experience net competition for animal-mediated pollination, while significantly positive slopes (lightest shade) indicate that net facilitation is the predominant outcome.
 The number of plants analysed for each species is shown within brackets next to the species name.
-(b) Despite the variety of slopes, overall plants had more conspecific than heterospecific pollen deposited in their stigmas.
-(c) The second criterion we used to distinguish between facilitation and competition shows similar patterns as the first one.
-Here we compare the amount of conspecific pollen deposited in plants' stigmas when they were open to animal-mediated pollination and when they were closed.
+(b) Despite the variation in these slopes, plants overall had more conspecific than heterospecific pollen deposited in their stigmas.
+(c) We plot the amount of conspecific pollen deposited in plants' stigmas when they were open to animal-mediated pollination and the same when they were closed.
 Statistically significant negative differences (darkest shade) indicates competition while positive differences (lightest shade) indicates facilitation.
-In all plots, error bars correspond to $\\pm$ the standard error (SE)."}
+In all panels, error bars correspond to $\\pm$ the standard error (SE)."}
 # fig_random_slopes <- plot_random_slopes(facilitation_plot_df)

### 2019-05-02 paper/supp-info.Rmd

@@
 title: "The pollination trade-off"
+# DBS: The title above needs editing to match the final version in the paper
 subtitle: "Supplementary information"
-author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
+author: "E. Fernando Cagua, Hugo J. Marrero, Jason M. Tylianakis, Daniel B. Stouffer"
 # bibliography: references.bib
@@
   dplyr::mutate(delta_AIC_CI = paste0(" [", delta_AIC_quantile_05,
-                                      " ,", 
+                                      ", ", 
                                       delta_AIC_quantile_95,

### 2019-05-03 paper/manuscript.Rmd
Some changes to intro

@@
 Animal pollination plays a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
-<!-- FDO: Asked coauthors for a reference for the following statement but no-one provided. Therefore removing -->
-Alongside the direct benefits of mutualisms between plants and their pollinators, biodiversity can be supported as a result of the inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008; @liao_presence_2011].
+Alongside the direct benefits of mutualisms between plants and their pollinators, biodiversity can be supported as a result of inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008; @liao_presence_2011].
 This inter-species facilitation is able to promote species coexistence by offsetting the effects of direct resource competition [@stachowicz_mutualism_2001]. 
@@
 In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000]. 
-However, it is less clear how exactly ecological differentiation, in turn, affects the trade-off between facilitation and competition that is involved in the pollination service.
-<!-- DBS; The end of the sentence above is confusing. Is it because what you mean by "the pollination service" hasn't been made explicit yet? -->
+However, it is less clear how exactly this ecological differentiation may, in turn, favour (or hinder) the pollination service.
 
 There are two main mechanisms through which competition for pollinators can affect plant fertilization [@morales_interspecific_2008]. 
-The first is by changes in intraspecific pollen transfer.
-<!-- DBS: The above should be interspecific, no? -->
+The first is by changes in interspecific pollen transfer.
 This happens, for example, when plants with more attractive flowers might reduce the number of visits to those less of attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
@@
 In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
-Generally speaking, the higher the amount of conspecific pollen (both in absolute terms and relative to heterospecific pollen), the better the pollination service received by the focal plant.
+Generally speaking, provided pollen is viable and compatible [@ramsey_pollen_2000; @de_jong_plant_1992; @dafni_pollen_2000], the higher the amount of conspecific pollen (both in absolute terms and relative to heterospecific pollen), the better the pollination service received by the focal plant.
 By definition, these two mechanisms of competition occur at the community scale. 
-However, with few exceptions [@rathcke_interactions_1988; @lopezaraiza-mikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the deposition of conspecific and heterospecific pollen---and its relationship to competition vs.
-facilitation in pollination communities---is based on studies with two plant species.
+However, with few exceptions [@tur_evaluating_2016; @aizen_reproductive_2010], most of what we know about the relationship between pollen deposition and competition vs.
+facilitation in pollination communities is based on studies with two plant species.
 
 At the community scale, the factors that determine the patterns of conspecific and heterospecific pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
-<!-- DBS: Fer, I absolutely love this sentence. -->
 For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016].
-This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly\R{ref-interaction-strength}.
-<!-- DBS: Doesn't Bascompte et al 2006 Science show this? Or maybe Thébault and Fontaine 2008 Oikos? -->
+This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly [@thebault_does_2008; @bascompte_asymmetric_2006; @vazquez_species_2007].
 If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012; @carvalheiro_potential_2014].
 Alternatively, it might also be the case that abundance (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
-Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators.
+Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987; @feldman_when_2004] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators.
 In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount of conspecific pollen relative to heterospecific pollen.
-<!-- DBS: I feel like the paragraph starts to lose the plot in the bit that follows. Where did realised niche come from and why invoke it? -->
-Altogether, it is clear that some ecological factors can influence pollen deposition and that these factors, in the specific context of pollination, could be used to roughly define a species *realised niche* in their community.
-However, the intertwined nature of these factors makes it hard to determine whether they favour or hinder the pollination service at the community level. 
+Altogether, it is clear that some ecological factors can influence pollen deposition. 
+However, the intertwined nature of these factors makes it hard to determine exactly how they can minimise competition, or equivalently maximise facilitation, at the community level. 
 Moreover, their relative importance has not yet been empirically evaluated in natural plant communities.
@@
 The higher the deposition of conspecific pollen relative to heterospecific, the larger the slope of this relationship.
-On the other hand, we could expect a larger amount of conspecific pollen deposited in stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination. 
+On the other hand, we could expect a larger amount of conspecific pollen deposited on stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination. 
 Second, we investigate the relative contribution that four ecological factors have to the pollination service. 

### 2019-05-03 paper/draft-info.Rmd

--- 2019-04-26 paper/draft-info.Rmd
@@
 
-* Now using `docker` to manage project dependencies. Image is now available on dockerhub efcaguab/pollen-competition.
-* Removing *quantity* and *quality* of pollination in favour of *quantity* and *purity* or plain metrics of *conspecific* and *heterospecific* pollen deposition. 
-* Rewording the plant strategies idea as it was confusing.
-Now the combination of ecological variables (number shared pol., abundance, visitation patterns, and traits) define a species *realised niche* (this was previously called the plant strategy).
-Plants that can have very different realised niches across different communities have a *flexible strategy* (this was previously called strategy as well).
-* Manuscript formatted for submission to Ecology Letters.
-* Sticking to past tense throughout the methods.
-* GLMM to fit the slope of heterospecific-conspecific pollen relationship tests all communities at once (it was a model per community).
-The response variable is the number of grains (it was the number of grains per stigma) and the (log) number of stigmas in the flowers has been included as an offset term.
-* Using a similar approach to compare conspecific pollen deposited in open and bagged flowers (I used a series of Mann-Withney U tests before)
-* Added facilitation model results tables in the Supplementary Information
-* Applied a green palette to all figures. Improves legibility when looking at it in a screen and the performance when printed in greyscale is maintained
-* Updated the headings in Figure 1 to make it clearer that we're looking at two distinct criteria
-* Made Figure 2 (model of environmental factors) one-column
-* Labelled some of the polygons in Fig 3c to make it easier to understand
-* Moved some of the justification on the criteria used to identify facilitation/competition to the discussion.
-* Show niche points for all species and not only those in two communities or more
-* Figures edited to match one and two column sizes at Ecology Letters. Implemented all format requirements for EL.
-* Added the following elements to the discussion: 
-    * That our networks are a snapshot
-    * How the degree-trait originality relationship can be shaped by the abundance
-    * How strategy could be a result of a species historical communities
-    * How attracting pollinators using flowering plants might work
-* Reorganised the topics in the discussion
+* Added .git and .drake to .dockerignore to speed up build

### 2019-05-03 paper/manuscript.Rmd
Add Daniel, Jamie, and Jason's edits to Introduction

@@
 Alternatively, it might also be the case that abundance (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
-Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987; @feldman_when_2004] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators.
+Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987; @feldman_when_2004] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators<!-- cite Savert et al.
+2019 here once it has a doi-->.
 In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount of conspecific pollen relative to heterospecific pollen.
@@
 On the other hand, we could expect a larger amount of conspecific pollen deposited on stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination. 
-Second, we investigate the relative contribution that four ecological factors have to the pollination service. 
-Specifically, we hypothesize that competition, measured as the quantity of conspecific pollen deposition and its purity (amount relative to heterospecific pollen), should increase for plants that share many pollination partners.
-<!-- DBS: Should we interchange amount and quantity so loosely like in the start of the sentence above?
-Also, it seems weird to call quantity of conspecific pollen a proxy for competition since it should be the inverse...
--->
+Second, we investigate the relative contribution that four ecological factors have on the pollination service. 
+Specifically, we hypothesize that cospecific pollen deposition (both its quantity and its purity relative to heterospecific pollen) should decreasse for plants that share many pollination partners
 However, we also hypothesize that other factors like the plant's functional originality, its relative abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
-Third and finally, we examine how much the community context influences the way plants exploit these factors to minimise competition. 
-Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict the competition for pollination niche to be influenced by the local context.
-<!-- DBS: I find the phrase "competition for pollination niche" to be very clunky. Can we do better? -->
+Third and finally, we examine how much the community context influences the way plants exploit these factors to minimise competition/maximise facilitation. 
+We use these four ecological factors as a proxy of the realised pollination niche of a plant species in their comunity.
+Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict the pollination niche to be influenced by the local context.
 If plant strategy is not flexible across the communities in our study\R{ref-plant-flexibility}, we could expect niches to be more similar within species than across species. 
-On the contrary, if a species' strategy is flexible, we should expect plants to be able to occupy different niches in each community such that competition could ultimately be minimised regardless of the context.
-<!-- DBS: Why do we always say could and not would? -->
+On the contrary, if a species' strategy is flexible, we should expect plants to be able to occupy different niches in each community such that intraspecific competition could ultimately be minimised regardless of the context.
 

### 2019-05-05 paper/manuscript.Rmd
Change title?

@@
 ---
-title: "Community context determines competition/facilitation trade-offs in pollination systems"
+title: "Community context determines competition vs. facilitation trade-offs in pollination systems"
 author: 
@@
 
-Our second objective was to investigate the relative contribution of different factors---that describe the plants' competition for pollination niches---to the pollination service. 
+Our second objective was to investigate the relative contribution of different mechanisms of pollinator mediated competition. 
 Generally speaking,

### 2019-05-06 paper/manuscript.Rmd
Edits to the Methods

--- 2019-05-03 paper/manuscript.Rmd
@@
 We collected data from eleven co-flowering plant communities and their pollinators in three locations in the Argentinian Pampas. 
-These locations are distributed across a precipitation gradient with the humid temperate climate of the eastern Flooding Pampas becoming drier as one moves inland and westward towards the Pampean Grasslands.
-This precipitation gradient generated a natural gradient of network architecture which allowed us to examine the generality of our findings.
+<!-- These locations are distributed across a precipitation gradient with the humid temperate climate of the eastern Flooding Pampas becoming drier as one moves inland and westward towards the Pampean Grasslands.
+-->
+<!-- This precipitation gradient generated a natural gradient of network architecture which allowed us to examine the generality of our findings. -->
 <!-- DBS: "Natural gradient" of network architecture seems purposefully vague. -->
-In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where we were only able to sample one restored fragment due to the lack of available sites.
+In each location, we sampled two restored and two agricultural fragments, except in one located in the Flooding Pampas, where we were only able to sample one restored fragment due to the lack of available sites.
 
@@
 This subset comprised between three and nine common insect-pollinated (entomophilous) plant species that were flowering during the sampling period (see Figure \@ref(fig:fig-trade-off-predictions)a). 
-We chose plant species such that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
+Based on data from previous years [@marrero_effect_2014], we chose plant species such that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
 In each of the selected plants, we removed all flowers leaving only buds that were expected to go into florescence on the next day. 
@@
 
-To evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution [@tur_evaluating_2016]. 
-In this model, the number of conspecific pollen grains per flower was the response variable and the number of heterospecific grains the predictor variable (the number of stigmas sampled was added as an offset term).
-<!-- DBS: I have a technical question about this offset. Is it the raw count or the log of said count? -->
-The slope and intercept of this relationship were allowed to differ between plant species within each community, which were modelled as a random effect. 
-<!-- DBS: This is slightly ambiguous. Are communities or species the random effect? -->
+To evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution [following @tur_evaluating_2016]. 
+In this model, the number of conspecific pollen grains per flower was the response variable and the number of heterospecific grains the predictor variable (the log number of stigmas sampled was added as an offset term).
+The slope and intercept of this relationship were allowed to differ between populations (plant species \(\times\) community), which were modelled as a random effect. 
 Models were fitted using the function `glmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]. 
-A positive slope for a plant-community combination might indicate facilitation while a negative slope might indicate competition [@tur_evaluating_2016]. 
-<!-- DBS: Everywhere else, we use definitive language about this interpretation. Here we temper it with 'might'. Why? -->
+A positive slope for a plant population indicates facilitation while a negative slope competition [@tur_evaluating_2016].
 
@@
 
-Our second objective was to investigate the relative contribution of different factors---that describe the plants' competition for pollination niches---to the pollination service. 
+Our second objective was to investigate the relative contribution of different mechanisms of pollinator-mediated competition to the pollination service. 
 Generally speaking,
-<!-- in the context of competition for pollination, -->
 we expect that any factor that increases the amount of conspecific pollen deposited in stigmas, both in quantity and purity relative to heterospecific pollen, also has a positive effect on the pollination service.
 <!-- DBS: There is no use to calling it something succinct like purity if we always have to say "purity relative to heterospecific pollen"...  -->
+<!-- FDO: Only mention purity relative to heterospecific pollen cause it's first time it gets mentioned in the methodsa  -->
 Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines
@@
 We visited the transects each month between November 2010 and March 2011. 
-To obtain plant abundance, we counted all units of floral attraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
+To obtain floral abundance, we counted all units of floral attraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
 To estimate visit effectiveness, we need to construct pollen transfer networks in addition to the visitation networks. 
@@
 <!-- This variable is strongly correlated to the number of animal species a plant interacts with (the species degree).  -->
-To calculate the plants' relative abundance in their community, we aggregated floral counts for each species. 
+To calculate the plants' relative floral abundance in their community, we aggregated floral counts for each species. 
 We then calculated the mean visit effectiveness of pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\], where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
-Because the number of shared pollinators, floral abundance, visitation, and pollen production roughly followed a power-law distribution, we log-transformed these three predictors before including them in the model.
-<!-- DBS: Log transforming power-law distributed variables doesn't give them a natural scale (which is the overarching point of transforming variables) since they're scale free by definition... -->
+We log-transformed the number of shared pollinators, floral abundance, and visit effecvtiveness before including them in the model.
 
@@
 <!-- As phenology has been shown to be a key mechanism of niche differentiation among plants, we also  -->
-To include phenological variation, we treated plant abundance in each of the survey months (November to March) as a "trait" in our analysis. 
+To include phenological variation, we treated floral abundance in each of the survey months (November to March) as a "trait" in our analysis. 
 <!-- This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits.  -->
-To account for the non-independence of floral counts and weight all traits equally, we assigned the abundances a weight of 1/5 (one for each month) compared to other functional traits. 
-We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
-Finally, to facilitate comparison across the four continuous explanatory variables in our models, we rescaled them all to have a zero mean and unitary variance.
-<!-- DBS: I'm lost. Why did we scale and then rescale? This doesn't seem to make any sense. -->
+To account for the non-independence of floral counts and weight all traits equally, we gave a weight of 1/5 to the abundances (one for each month). 
+Finally, we scaled all variables to have a zero mean and unitary variance and calculated the centroid of the functional space and the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014].
 
@@
 First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc (relative to the most likely model) for each bootstrap sample.
-As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our variables proportional to the likelihood of its candidate model.
+As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our variables proportionally to the likelihood of their candidate model.
 <!-- We "shrank" the estimated coefficient of potentially unimportant variables by setting their estimate to 0 when the variable was not included in the model.  -->
@@
 <!-- DBS: Thinking out loud here, but are the strategies for reducing competition or for increasing facilitation/mutualism?  -->
-If community context plays a relatively small role or the species strategy is inflexible, we would expect plants of the same species to fill similar competition for pollination niches across different communities.
-Alternatively, if the community plays a large role and/or plants strategies are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
-To test this, we first used a principal component analysis (PCA) of the four ecological variables. 
+If community context plays a relatively small role or the species strategy is inflexible, we would expect plants of the same species to fill similar pollination niches across different communities. 
+Alternatively, if the community plays a large role and/or plant strategies are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
+To test this, we first used a principal component analysis (PCA) of the four ecological variables (number of shared pollinators, floral abundance, visit effectiveness, and trait originality). 
 We scaled variables across the whole study to ensure that the PCA space does not change according to the species present in each community. 

### 2019-05-06 paper/manuscript.Rmd
Floral abundances in intro

@@
 Specifically, we hypothesize that cospecific pollen deposition (both its quantity and its purity relative to heterospecific pollen) should decreasse for plants that share many pollination partners
-However, we also hypothesize that other factors like the plant's functional originality, its relative abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
+However, we also hypothesize that other factors like the plant's functional originality, its relative floral abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
 Third and finally, we examine how much the community context influences the way plants exploit these factors to minimise competition/maximise facilitation. 

### 2019-05-06 paper/manuscript.Rmd
Edits to the results

@@
 Indeed, we found that the proportions of species that experienced a statistically significant positive or negative relationship between heterospecific and conspecific pollen were very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)).
-<!-- DBS: Fer, please check my edit above to make sure it's correct. -->
 Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
@@
 
-We then examined the potential roles played by four ecological variables (number of shared pollinators, plant abundance, mean visit effectiveness, and functional originality) play in pollen deposition.
+We then examined the potential roles played by four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality). 
 <!-- Together these variables can describe the niche that plants might occupy in the context of competition for pollination.  -->
 We found that our models of pollen deposition had high explanatory power (the coefficient of determination R^2^ ranged between `r min(r2_values$r2c_min)` and `r max(r2_values$r2c_max)`) although a large portion of the explanatory power came from the random effects (Table \@ref(S-tab:table-R2)).
-As determined by AICc, the random structure best supported by the data was the one that fit an intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community they belong to).
+As determined by AICc, the random structure best supported by the data was the one that fit an intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community to which they belong).
 This structure was best for both the models of conspecific and heterospecific pollen (Table \@ref(S-tab:table-aic-random-models)).
 
-Of the four variables we considered, we found that a plant's mean visit effectiveness and realtive abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
+Of the four variables we considered, we found that a plant's mean visit effectiveness and realtive floral abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
 Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
@@
 However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
-This indicates that, although there is a positive association between visit effectiveness and the quantity pollen deposition, there is a negative relationship with its purity (Figure \@ref(fig:fig-average-qual-quant)c).
-In contrast, a plants' relative abundance had a negative effect on the pollen deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with the purity (Figure \@ref(fig:fig-average-qual-quant)c).
+This indicates that, although there is a positive association between visit effectiveness and the quantity of pollen deposition, there is a negative relationship with its purity (Figure \@ref(fig:fig-average-qual-quant)c).
+In contrast, a plants' relative floral abundance negatively affect deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with purity (Figure \@ref(fig:fig-average-qual-quant)c).
 The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and purity. 
@@
 ```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=width('single'), out.height="4.56in", out.width="3.57in", out.extra="center", fig.cap="Effect of strategies to minimise competition in the pollination service.
-(a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
+(a) The plant's visit effectiveness and relative floral abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
 Meanwhile, the number of shared pollinators was generally less important.
@@
 (b) The association between ecological variables and heterospecific pollen tended to align with their association with conspecific pollen.
-Visit effectiveness and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association.
+Visit effectiveness and functional originality had a positive association with pollen deposition, while floral abundance and the number of shared pollinators had a negative association.
 The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific and heterospecific pollen.
@@
 (c) This was confirmed using Monte Carlo randomizations of the median distance between strategies of a plant species.
-Only one of the examined species had strategies that were closer together than would be expected at random."}
+Only two of the examined species had strategies that were less flexible than would be expected at random."}
 height0 <- 1.55
@@
 
-We used a PCA of the analysed species to investigate whether plants' realised niches of competition for pollination is similar across communities or whether they are flexible and therefore a reflection of the community context.
+We used a PCA of the analysed species to investigate whether plants' realised pollination niche is similar across communities or whether they are flexible and therefore a reflection of the community context.
 The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
@@
 When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
-Indeed, when we measured the median distance between the plants coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` species analysed (Figure \@ref(fig:fig-pca)c).
+Indeed, when we measured the median distance between the plants' coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` species analysed (Figure \@ref(fig:fig-pca)c).
 <!-- DBS: Are we consistent with UK vs US spellings? Does Ecology Letters prefer UK spelling? -->

### 2019-05-06 paper/manuscript.Rmd
Remove bars from figure 1

@@
   fig_hetero_con,
-  NULL,
   fig_con_con[[1]],
-  fig_con_con[[2]],
-  ncol = 2, 
+  # fig_con_con[[2]],
+  ncol = 1, 
   rel_widths = rw[c(3,4)], 
-  align = "h"
+  align = "hv"
 )
@@
   fig_random_slopes[[1]],
-  fig_random_slopes[[2]], 
+  # fig_random_slopes[[2]],
   # ncol = 2, 

### 2019-05-06 code/facilitation.R
Looks ugly but add facilitation competition annotations from Fig 1 in both sides

@@ -146,14 +146,14 @@ plot_random_slopes <- function(facilitation_plot_df){
               fontface = "italic",
               hjust = "inward") +
     geom_point(aes(y = 0, x = -0.5), alpha = 0) +
-    annotate(geom = "text", x = n_plants + 1, y = 0,
+    annotate(geom = "text", x = c(n_plants + 1, 0), y = 0,
              label = expression(" " %->% plain("facilitation predominates") %->% ""),
              hjust = "left",
              vjust = 0.5,
              size = 2.25,
              colour = "grey20") +
     geom_point(aes(y = 0, x = n_plants + 1.5), alpha = 0) +
-    annotate(geom = "text", x = 0, y = 0,
+    annotate(geom = "text", x = c(n_plants + 1, 0), y = 0,
              label = expression(" " %<-% plain("competition predominates") %<-% ""),
              hjust = "right",
              vjust = 0.5,

### 2019-05-06 paper/draft-info.Rmd
Updated draft changes

@@
 * Added .git and .drake to .dockerignore to speed up build
+* As suggested by Jason I refer to the factors on the main models as mechanisms of pollinator mediated competition. 
+* Many minor changes to the text
+* Replaced instances of "plant abundance" to the more specific term "floral abundance" (Jamie suggested some people working in the field might be finicky with terminology).

### 2019-05-06 paper/manuscript.Rmd
Some changes to the discussion

@@
 
-Our results suggest that community context plays a central role in determining net cost or benefit of sharing pollinators.
+Our results suggest that community context plays a central role in determining the net cost or benefit of sharing pollinators.
 <!-- DBS: In the intro, it's about net outcome. Here, it's about net cost or benefit. Which is it? -->
@@
 A previous study showed that, in diverse pollination communities, sharing pollinators does not necessarily translate to net competition [@tur_evaluating_2016]. 
-The overall extent of facilitation/competition of pollination communities can depend on factors like the adversity of the environment [@tur_evaluating_2016; @callaway_positive_2002] or how disturbances affect pollinator populations [@stavert_exotic_2017]
+The overall extent of facilitation/competition of pollination communities can depend on factors like the adversity of the environment [@tur_evaluating_2016; @callaway_positive_2002] or how disturbances affect pollinator populations [@stavert_exotic_2017].
 However, why some species experience more competition than others was not understood. 
@@
 In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, as we show that sharing pollinators reduces both the quantity and purity of the conspecific pollen deposited.
-However, over long periods of time, there could be a risk associated with a specialist plant having no pollinators. 
+However, over long periods of time, there could be a risk associated with a specialist plant not having pollinators [@ricketts_tropical_2004]. 
 To ensure long-term survival, it is thus likely that plants also need to balance this risk with the costs of sharing pollinators. 
-One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it’s commonly thought that species that are further from others in trait space benefit from reduced competition.
+One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it is commonly thought that species that are further from others in trait space benefit from reduced competition.
 Yet, there are two possible caveats to this strategy that highlight the interrelatedness of the ecological factors. 
@@
 
-Visit effectiveness (high pollen and visits) and abundance, which were the most important predictors of pollen deposition here, introduced an even more explicit trade-off between gaining conspecific pollen and avoiding heterospecific pollen.
+Visit effectiveness (high pollen and visits) and floral abundance, which were the most important predictors of pollen deposition here, introduced an even more explicit trade-off between gaining conspecific pollen and avoiding heterospecific pollen.
 On the one hand, receiving high visitation increases conspecific pollen deposition but increases heterospecific pollen deposition to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen [@fang_paradoxical_2016].

### 2019-05-06 paper/manuscript.Rmd
Further edits to discussion

@@
 Third, we found that the way these factors influence competition is strongly shaped by the community context. 
-That is, if these factors collectively define a species' niche of competition for pollination,
+That is, if these factors collectively define a species' pollination niche,
 <!-- DBS: Yet another way to phrase this concept... -->
@@
 However, why some species experience more competition than others was not understood. 
-Here we show that the coexistence of facilitative and competitive effects of animal-mediated pollination can be at least partially explained by the trade-offs plants have to face when simultaneously maximising the deposition of conspecific pollen and minimising that of heterospecific pollen in both the short and the long term.
+Although we were unable to measure the fitness outcomes, here we show that the coexistence of facilitative and competitive effects of animal-mediated pollination can be at least partially explained by trade-offs in the pollination sercice--both the short and the long term.
+These trade-offs arise when plants simultaneously maximise the deposition of conspecific pollen and minimise that of heterospecific pollen.
 
-In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, as we show that sharing pollinators reduces both the quantity and purity of the conspecific pollen deposited.
+In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, not only due to costs to male fitness [@muchhala_interspecific_2012; @morales_interspecific_2008], but also because, as we show here, sharing pollinators reduces both the quantity and purity of the conspecific pollen deposited.
 However, over long periods of time, there could be a risk associated with a specialist plant not having pollinators [@ricketts_tropical_2004]. 
-To ensure long-term survival, it is thus likely that plants also need to balance this risk with the costs of sharing pollinators. 
+To ensure long-term survival, it is thus likely that plants also need to balance this risk with the costs of sharing pollinators [@aizen_specialization_2012]. 
 One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it is commonly thought that species that are further from others in trait space benefit from reduced competition.
@@
 Visit effectiveness (high pollen and visits) and floral abundance, which were the most important predictors of pollen deposition here, introduced an even more explicit trade-off between gaining conspecific pollen and avoiding heterospecific pollen.
-On the one hand, receiving high visitation increases conspecific pollen deposition but increases heterospecific pollen deposition to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen [@fang_paradoxical_2016].
-On the other hand, being abundant reduces the amount of heterospecific pollen deposited but this comes at the expense of a noticeable reduction in the amount of conspecific pollen. 
+Receiving high visitation increases conspecific pollen deposition but increases heterospecific pollen deposition to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen [@fang_paradoxical_2016].
+Contrastingly, being abundant reduces the amount of conspecific pollen deposited and simultaneously reduces heterospecific pollen at a faster rate. 
 Our results corroborate the importance that two-species studies have ascribed to visitation and abundance [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008], 
@@
 We observed, as expected, that the effects of pollen deposition can vary widely among species. 
-For instance, while the fitness of some plant species can be hurt even by low amounts of heterospecific pollen, for others species, fitness can instead be limited by the amount of conspecific pollen [@campbell_mechanism_1985; @arceo-gomez_interactive_2019].
-Alternatively, plant species can also differ substantially on the extent to which self- vs. outcross-pollen differ in their value for fertilization. 
+For instance, while the fitness of some plant species can be hurt even by low amounts of heterospecific pollen, for others, fitness can instead be limited by the amount of conspecific pollen [@campbell_mechanism_1985; @arceo-gomez_interactive_2019].
+Alternatively, plant species can also differ substantially in the extent to which self- vs. outcross-pollen differ in their value for fertilization. 
 The difference can be particularly relevant for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy).
 
-Importantly, we show here that the balances between costs and benefits are determined not only by species identity but also on the community plants belong to. 
+Importantly, we show here that the balances between costs and benefits are determined not only by species identity but also by the community to which plants belong. 
 Specifically, most plant species appear to be flexible enough to adopt markedly different niches in different communities. 
-Although there are many exceptions, some plant families (Asteraceae for example) are often generalists in their communities while others (Orchidaceae) are known to be more commonly specialised [@johnson_generalization_2000].
+<!-- Although there are many exceptions, some plant families (Asteraceae for example) are often generalists in their communities while others (Orchidaceae) are known to be more commonly specialised [@johnson_generalization_2000].
+-->
 <!-- DBS: I'd cut the sentence above. -->
@@
 pollinator behaviour and densities or the spatial context) have also been shown to play a role in the outcome of animal-mediated pollination [@ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009; @thomson_effects_2019].
-Nevertheless, our results indicate that the strategies plant might use to successfully minimise competition for pollination must be determined relative to other species in the community, rather than an absolute property of the species itself.
+Nevertheless, our results indicate that the strategies that plant might use to successfully minimise competition for pollination must be determined relative to other species in the community, rather than an absolute property of the species itself.
 

### 2019-05-06 paper/manuscript.Rmd
On the one hand its a nice idiom, on the other there were too many

@@
 The higher the deposition of conspecific pollen relative to heterospecific, the larger the slope of this relationship.
-On the other hand, we could expect a larger amount of conspecific pollen deposited on stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination. 
+On the other, we could expect a larger amount of conspecific pollen deposited on stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination. 
 Second, we investigate the relative contribution that four ecological factors have on the pollination service. 

### 2019-05-06 paper/manuscript.Rmd
Move coolinearlity to supp info.

@@
 Finally, the number of shared pollinators had negative and neutral associations with conspecific and heterospecific pollen, respectively, but these impacts were small when compared to the other variables.
-
-Overall, collinearity between predictors did not qualitatively affect our findings.
-Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).
-One exception was visit-effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations. 
-Nevertheless, these differences were observed only in model specifications with relatively low AICc support.
-<!-- DBS: I think we can cut this. It's low hanging fruit for a reviewer to ask, we know the answer is unimportant, and hence can save some space by cutting it (for now). -->
+Athough the explanatory variables were positively correlated (Figure \@ref(S-fig:fig-correlation)), the collinearity between predictors did not qualitatively affect our findings (Figure \@ref(S-fig:fig-model-results)).
 

### 2019-05-06 paper/supp-info.Rmd
Move coolinearlity to supp info.

@@
 Only candidate formulas with a $\\Delta AICc < 4$ for either conspecific or heterospecific pollen are shown.
-Models candidates are arranged in decreasing order of support.", eval=T}
+Models candidates are arranged in decreasing order of support.
+Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated, the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables.
+One exception was visit-effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations.
+Nevertheless, these differences were observed only in model specifications with relatively low AICc support.", eval=T}
 drake::readd(fig_all_model_results)

### 2019-05-06 paper/manuscript.Rmd
Couple more edits for clarity

@@
 <!-- FDO: Only mention purity relative to heterospecific pollen cause it's first time it gets mentioned in the methodsa  -->
-Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines
-the share of pollen that a plant species is able to place on each of their floral visitors
-<!-- DBS: The line above is very confusing and took me about five reads before I understood what you wanted to say. We need to revise it. -->
-and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010]. 
+Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the amount and type of pollen carried by floral visitors and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010].
 See *Data Analysis* section below for more details on these four variables. 
@@
 The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
-The first component was dominated by changes in visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality.
-<!-- DBS: Why "changes" in visit effectiveness? -->
+The first component was dominated by visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality. 
 When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.

### 2019-05-06 paper/draft-info.Rmd
Update draft info

@@
 
-* Suggest a justification for the traits used if needed (see \lr{M-justification-traits}).
-* Identify sections/sentences to trim to achieve the word limit.
-* Suggest a reference for sentence in \lr{M-ref-interaction-strength} if needed.
-* Suggest a reference for sentence in \lr{M-ref-plant-flexibility} if needed. 
-* Suggest alternative, more-appropiate, sub-headings if needed. 
-* Check statement in \lr{M-theoretical-models}
+* Specify grant numbers in the Awknoledgements and make sure the ones stated there now are correct. 
+* Aprove (or not for submission)
 
@@
 * Replaced instances of "plant abundance" to the more specific term "floral abundance" (Jamie suggested some people working in the field might be finicky with terminology). 
+* Some extra refs added
+* Moved the sentences about variable collinearity to the supp. info. to save a bit of space in the main text
+* Removed criteria #2...

### 2019-05-07 paper/manuscript.Rmd
Update keywords

@@
 
-loadd(abs_wordcount, msc_wordcount, n_displays, n_references)
+loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords)
 ```
@@
 
-**Running title:** The pollination trade-off
-
-**Keywords:** Competition, facilitation, interspecific pollen transfer, conspecific, pollen deposition, multi-species, plant-pollinator interaction, pollination trade-off, pollination costs, networks (up to 10).
+**Keywords:** `r keywords`
 

### 2019-05-07 code/keywords.R

@@ -1,0 +1,8 @@
+# read keywords and order them alphabetically
+process_keywords <- function(filename){
+  readLines(filename) %>%
+    purrr::discard(~ . == "") %>%
+    purrr::map_chr(stringr::str_trim) %>%
+    sort() %>%
+    glue::collapse(sep = ", ", last = ", and ")
+}

### 2019-05-07 main.R

@@ -208,6 +208,7 @@ figure_plan <- drake_plan(
 
 reporting_plan <- drake_plan(
   abstract = readLines(file_in("./paper/abstract.md")),
+  keywords = process_keywords(file_in("./paper/keywords.md")),
   acknowledgements = readLines(file_in("./paper/acknowledgements.md")),
   intro_line_number = get_line_number(file_in("paper/manuscript.Rmd"), "# Introduction"),
   abs_wordcount = count_words(file_in("paper/abstract.md")),

### 2019-05-07 paper/manuscript.Rmd
Improvements to introduction

@@
 However, in natural communities, plants rarely share all available pollinators. 
-One explanation is that plants are effectively competing for mutualistic partners because there is a *trade-off* between the benefits gained from maximising the number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
+One explanation is that plants are effectively competing for mutualistic partners because there is a trade-off between the benefits gained from maximising the number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
 It has been clear for a long time that when competition for pollination is strong enough, these costs can make pollination detrimental to plants' fitness [shown both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970].
@@
 There are two main mechanisms through which competition for pollinators can affect plant fertilization [@morales_interspecific_2008]. 
-The first is by changes in interspecific pollen transfer.
+The first is by changes in intraspecific pollen transfer.
 This happens, for example, when plants with more attractive flowers might reduce the number of visits to those less of attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
-The second is via intraspecific pollen transfer and occurs when plants share pollination partners. 
+The second is via intrerspecific pollen transfer and occurs when plants share pollination partners. 
 In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
-Generally speaking, provided pollen is viable and compatible [@ramsey_pollen_2000; @de_jong_plant_1992; @dafni_pollen_2000], the higher the amount of conspecific pollen (both in absolute terms and relative to heterospecific pollen), the better the pollination service received by the focal plant.
+Generally speaking, provided pollen is viable and compatible [@ramsey_pollen_2000; @de_jong_plant_1992; @dafni_pollen_2000], the higher the quantity of conspecific pollen and its purity (relative to heterospecific pollen), the better the pollination service received by the focal plant.
 By definition, these two mechanisms of competition occur at the community scale. 
-However, with few exceptions [@tur_evaluating_2016; @aizen_reproductive_2010], most of what we know about the relationship between pollen deposition and competition vs.
-facilitation in pollination communities is based on studies with two plant species.
+However, with few exceptions [@tur_evaluating_2016; @aizen_reproductive_2010], most of what we know about them and their relationship with key ecological factors is based on studies with two plant species.
 
-At the community scale, the factors that determine the patterns of conspecific and heterospecific pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
+That is partly so because, at the community scale, the factors that determine the patterns of pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
 For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016].
@@
 In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount of conspecific pollen relative to heterospecific pollen.
-Altogether, it is clear that some ecological factors can influence pollen deposition. 
-However, the intertwined nature of these factors makes it hard to determine exactly how they can minimise competition, or equivalently maximise facilitation, at the community level. 
-Moreover, their relative importance has not yet been empirically evaluated in natural plant communities.
+Altogether, it is clear that these ecological factors can indeed shape pollen deposition at the community level. 
+However, their relative importance and how exactly they can minimise competition for pollination—or equivalently, maximise facilitation—in plant populations (acrosss species and communities) has not been determined.
 
-Here, we investigate competition for pollination at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
+Here, we investigate the balance between competition for pollination abd facilitation at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
 First, we estimate the extent to which the net outcome of plants sharing pollinators is facilitation or competition. 

### 2019-05-07 paper/manuscript.Rmd
Update title and running title

@@
 
-<!-- ^a^ [efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz); ^b^ [hugomarrero@gmail.com](hugomarrero@gmail.com); ^c^ [jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz); ^d^ [daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz) -->
+**Running title:** 
+Competition for pollination vs. facilitation
 
@@
 
-**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. The data DOI will be included here.
+**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. The DOI will be included here.
 

### 2019-05-07 paper/manuscript.Rmd
Remove second criterion to determine facilitation/competition
Adds very little to the story and can be easily attacked

@@
 First, we estimate the extent to which the net outcome of plants sharing pollinators is facilitation or competition. 
-If facilitation is the primary outcome, we could expect two things. 
-On the one hand, we could expect an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the amount of heterospecific pollen [@tur_evaluating_2016]. 
+If facilitation is the primary outcome, we could expect an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the amount of heterospecific pollen [@tur_evaluating_2016].
 The higher the deposition of conspecific pollen relative to heterospecific, the larger the slope of this relationship.
-On the other, we could expect a larger amount of conspecific pollen deposited on stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination. 
+<!-- On the other, we could expect a larger amount of conspecific pollen deposited on stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination.  -->
 Second, we investigate the relative contribution that four ecological factors have on the pollination service. 
@@
 Our first objective was to identify whether the net outcome of plants sharing pollinators at the community level is facilitation or competition. 
-We use two complementary lines of evidence.  
-The first can be found via the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
+<!-- We use two complementary lines of evidence.   -->
+To do that  we examine <!-- first can be found via --> the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
 This is because heterospecific pollen can be seen as an unavoidable cost that plants must pay for receiving conspecific pollen from shared pollinators. 
@@
 
-The second line of evidence can be obtained by examining the difference between the amount of conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination. 
-Self-pollination can be favourable to plant reproduction when competition for pollination is strong because it provides insurance against poor pollination service [@kalisz_benefits_2003]. 
-If competition <!-- for pollination-->is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented should be higher than when animal pollination is allowed.
-In contrast, the opposite pattern may indicate that plants benefit from having pollen delivered directly to the stigma by animals.
+<!-- The second line of evidence can be obtained by examining the difference between the amount of conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination.  -->
+<!-- Self-pollination can be favourable to plant reproduction when competition for pollination is strong because it provides insurance against poor pollination service [@kalisz_benefits_2003].  -->
+<!-- If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented should be higher than when animal pollination is allowed.
+-->
+<!-- In contrast, the opposite pattern may indicate that plants benefit from having pollen delivered directly to the stigma by animals.  -->
 
@@
 In each of the selected plants, we removed all flowers leaving only buds that were expected to go into florescence on the next day. 
-Approximately a quarter of these buds were bagged to prevent animal pollination. 
+<!-- Approximately a quarter of these buds were bagged to prevent animal pollination.  -->
 Two days after inflorescence, we collected all remaining flowers and counted the number of conspecific and heterospecific pollen grains in their pistils. 
@@
 
-To compare the conspecific pollen deposited with and without animal-mediated pollination, we followed the same approach as above. 
-In this case, however, the predictor variable was the treatment (whether the flower was bagged or unbagged) instead of the number of heterospecific grains.
+<!-- To compare the conspecific pollen deposited with and without animal-mediated pollination, we followed the same approach as above.  -->
+<!-- In this case, however, the predictor variable was the treatment (whether the flower was bagged or unbagged) instead of the number of heterospecific grains.  -->
 
@@
 For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others.
-Interestingly, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).
+Interestingly, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(S-fig:fig-conspecififc-heterospecific)).
 
-```{r fig-trade-off-predictions, fig.height= 4, out.height="4in", fig.width = 7.49, out.width="7.49in", out.extra="center", fig.cap = "Competition vs.
+```{r fig-trade-off-predictions, fig.height= 4, out.height="4in", fig.width = 3.57, out.width="3.57in", out.extra="center", fig.cap = "Competition vs.
 facilitation at the community level.
-(a) Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in each of their communities.
+Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in each of their communities.
 Statistically significant negative slopes (darkest shade) indicate that plants experience net competition for animal-mediated pollination, while significantly positive slopes (lightest shade) indicate that net facilitation is the predominant outcome.
 The number of plants analysed for each species is shown within brackets next to the species name.
-(b) Despite the variation in these slopes, plants overall had more conspecific than heterospecific pollen deposited in their stigmas.
-(c) We plot the amount of conspecific pollen deposited in plants' stigmas when they were open to animal-mediated pollination and the same when they were closed.
-Statistically significant negative differences (darkest shade) indicates competition while positive differences (lightest shade) indicates facilitation.
-In all panels, error bars correspond to $\\pm$ the standard error (SE)."}
+Error bars correspond to $\\pm$ the standard error (SE)."}
 # fig_random_slopes <- plot_random_slopes(facilitation_plot_df)
-# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
-# fig_con_con = plot_bagged_vs_open_conspecific(drake::readd(con_con_plot_df))
-# pdf(width = 7.49, height = 4)
+# pdf(width = 3.57, height = 4)
 drake::loadd(fig_random_slopes)
-drake::loadd(fig_con_con)
-drake::loadd(fig_hetero_con)
-width_left <- 6.5*3/5
-bar_plot_width <- 0.29
-rw <- c(width_left - bar_plot_width,
-        bar_plot_width, 
-        6.5 - width_left - bar_plot_width,
-        bar_plot_width)
-left <- cowplot::plot_grid(
-  fig_hetero_con,
-  fig_con_con[[1]],
-  # fig_con_con[[2]],
-  ncol = 1, 
-  rel_widths = rw[c(3,4)], 
-  align = "hv"
-)
-right <- cowplot::plot_grid(
-  fig_random_slopes[[1]],
-  # fig_random_slopes[[2]],
-  # ncol = 2, 
-  align = "h", 
-  rel_widths = rw[1:2]
-)
-cowplot::plot_grid(
-  right,
-  left,
-  ncol = 2,
-  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
-)
+  fig_random_slopes[[1]]
 # dev.off()
@@
 
-Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with that of those that were closed. 
-Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers (Table \@ref(S-tab:table-open-bagged-models-general)). 
-Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had less pollen when open (the difference was statistically non-significant for the remaining `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
-Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both positive and negative differences.
+<!-- Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with that of those that were closed.  -->
+<!-- Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers (Table \@ref(S-tab:table-open-bagged-models-general)).  -->
+<!-- Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had less pollen when open (the difference was statistically non-significant for the remaining `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
+-->
+<!-- Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both positive and negative differences.
+-->
 
@@
 
-Both of the criteria we used to identify the effect of animal-mediated pollination suggested the same outcome: that neither facilitation nor competition are dominant in pollination communities.
+The criterion we used to identify the effect of animal-mediated pollination suggested that neither facilitation nor competition are dominant in pollination communities.
 A previous study showed that, in diverse pollination communities, sharing pollinators does not necessarily translate to net competition [@tur_evaluating_2016]. 

### 2019-05-07 code/facilitation.R

@@ -166,7 +166,7 @@ plot_random_slopes <- function(facilitation_plot_df){
     scale_x_discrete(expand = c(0,0)) +
     scale_alpha_manual(values = c(0,1)) +
     labs(y = bquote("slope of species-community random effects" ~ beta[i]),
-         title = "(a) competition vs. facilitation - criterion #1",
+         title = "competition vs. facilitation",
          subtitle = "relationship hetero-conspecific pollen") +
     coord_flip() +
     pub_theme() +

### 2019-05-07 paper/supp-info.Rmd
Move plot conspecific vs heterospecific pollen to the supplementary

@@
 
-```{r table-open-bagged-models-general, results = "asis"}
+```{r fig-conspecififc-heterospecific, fig.height=2, fig.width = 3.57, fig.cap="Despite the variation in these slopes, plants overall had more conspecific than heterospecific pollen deposited in their stigmas."}
+# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
+drake::loadd(fig_hetero_con)
+fig_hetero_con
+```
+
+```{r table-open-bagged-models-general, results = "asis", eval = FALSE}
 drake::loadd(open_bagged_model)
@@
 
-```{r table-open-bagged-models-random, results='asis'}
+```{r table-open-bagged-models-random, results='asis', eval = FALSE}
 drake::loadd(con_con_plot_df)

### 2019-05-07 code/make_fig_con_hetero_gain.R

@@ -400,7 +400,7 @@ make_fig_con_hetero_empirical <- function(dep_frame){
     scale_y_continuous(trans = "log1p", breaks = axis_breaks, labels = function(x) paste0(" ", x)) +
     labs(x = "heterospecific",
          y = "conspecific",
-         title = "(b) hetero- vs. conspecific pollen",
+         title = "hetero- vs. conspecific pollen",
          subtitle = "mean pollen grains per stigma") +
     pub_theme()
 }

### 2019-05-07 paper/supp-info.Rmd
Change aspect ratio of heterospecific vs conspecific pollen figure

@@
 
-```{r fig-conspecififc-heterospecific, fig.height=2, fig.width = 3.57, fig.cap="Despite the variation in these slopes, plants overall had more conspecific than heterospecific pollen deposited in their stigmas."}
+```{r fig-conspecififc-heterospecific, fig.height=4, fig.cap="Despite the variation in these slopes, plants overall had more conspecific than heterospecific pollen deposited in their stigmas."}
 # fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)

### 2019-05-07 code/make_fig_con_hetero_gain.R

@@ -402,7 +402,8 @@ make_fig_con_hetero_empirical <- function(dep_frame){
          y = "conspecific",
          title = "hetero- vs. conspecific pollen",
          subtitle = "mean pollen grains per stigma") +
-    pub_theme()
+    pub_theme() +
+    coord_fixed()
 }
 
 mid <- function(x){

### 2019-05-07 paper/manuscript.Rmd
Replace variables and mechanisms to "factors"

@@
 Second, we investigate the relative contribution that four ecological factors have on the pollination service. 
-Specifically, we hypothesize that cospecific pollen deposition (both its quantity and its purity relative to heterospecific pollen) should decreasse for plants that share many pollination partners
+Specifically, we hypothesize that the quantity and purity of cospecific pollen deposition should decreasse for plants that share many pollination partners
 However, we also hypothesize that other factors like the plant's functional originality, its relative floral abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
@@
 
-Our second objective was to investigate the relative contribution of different mechanisms of pollinator-mediated competition to the pollination service. 
+Our second objective was to investigate the relative contribution that different eological factors have on the mechanisms of pollinator-mediated competition. 
 Generally speaking,
@@
 Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the amount and type of pollen carried by floral visitors and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010].
-See *Data Analysis* section below for more details on these four variables. 
+See *Data Analysis* section below for more details on these four factors. 
 <!-- Here, we define visit effectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
@@
 
-As fixed predictors in the models, we included the four ecological variables described above. 
+As fixed predictors in the models, we included the four ecological factors described above. 
 Specifically, we calculated the number of shared pollinators for each plant species by pooling data from the qualitative and quantitative pollination networks. 
@@
 To account for the non-independence of floral counts and weight all traits equally, we gave a weight of 1/5 to the abundances (one for each month). 
-Finally, we scaled all variables to have a zero mean and unitary variance and calculated the centroid of the functional space and the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014].
+We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
+Finally, we scaled all foyr factors to have a zero mean and unitary variance.
 
 To estimate the coefficients, perform model selection, and quantify the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with 99 replicates. 
-First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predicting variables) by calculating the median \(\Delta\)AICc (relative to the most likely model) for each bootstrap sample.
-As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our variables proportionally to the likelihood of their candidate model.
+First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predictors) by calculating the median \(\Delta\)AICc (relative to the most likely model) for each bootstrap sample.
+As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our factors proportionally to the likelihood of their candidate model.
 <!-- We "shrank" the estimated coefficient of potentially unimportant variables by setting their estimate to 0 when the variable was not included in the model.  -->
@@
 Alternatively, if the community plays a large role and/or plant strategies are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
-To test this, we first used a principal component analysis (PCA) of the four ecological variables (number of shared pollinators, floral abundance, visit effectiveness, and trait originality). 
-We scaled variables across the whole study to ensure that the PCA space does not change according to the species present in each community. 
+To test this, we first used a principal component analysis (PCA) of the four ecological factors (number of shared pollinators, floral abundance, visit effectiveness, and trait originality). 
+We scaled factors across the whole study to ensure that the PCA space does not change according to the species present in each community. 
 We define a species' niche in a community as its coordinates in PCA space. 
@@
 
-We then examined the potential roles played by four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality). 
+We then examined the potential roles played by four ecological factors (number of shared pollinators, abundance, mean visit effectiveness, and functional originality). 
 <!-- Together these variables can describe the niche that plants might occupy in the context of competition for pollination.  -->
@@
 
-Of the four variables we considered, we found that a plant's mean visit effectiveness and realtive floral abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
+Of the four factors we considered, we found that a plant's mean visit effectiveness and realtive floral abundance were the most important at predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
 Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
@@
 In contrast, a plants' relative floral abundance negatively affect deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with purity (Figure \@ref(fig:fig-average-qual-quant)c).
-The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and purity. 
-Finally, the number of shared pollinators had negative and neutral associations with conspecific and heterospecific pollen, respectively, but these impacts were small when compared to the other variables.
-Athough the explanatory variables were positively correlated (Figure \@ref(S-fig:fig-correlation)), the collinearity between predictors did not qualitatively affect our findings (Figure \@ref(S-fig:fig-model-results)).
+The third most important factor, functional originality, had a positive, although comparatively smaller, association with both the quantity and purity. 
+Finally, the number of shared pollinators had negative and neutral associations with conspecific and heterospecific pollen, respectively, but these impacts were small when compared to the other factors.
+Athough the ecological factors were positively correlated (Figure \@ref(S-fig:fig-correlation)), the collinearity between predictors did not qualitatively affect our findings (Figure \@ref(S-fig:fig-model-results)).
 
 ```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=width('single'), out.height="4.56in", out.width="3.57in", out.extra="center", fig.cap="Effect of strategies to minimise competition in the pollination service.
-(a) The plant's visit effectiveness and relative floral abundance are the most important variables determining the deposition of conspecific and heterospecific pollen.
+(a) The plant's visit effectiveness and relative floral abundance are the most important factors determining the deposition of conspecific and heterospecific pollen.
 Meanwhile, the number of shared pollinators was generally less important.
-The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable.
-(b) The association between ecological variables and heterospecific pollen tended to align with their association with conspecific pollen.
+The graph shows the relative importance calculated as the sum of the Akaike weights of the candidate models that included the selected factor.
+(b) The association between ecological factors and heterospecific pollen tended to align with their association with conspecific pollen.
 Visit effectiveness and functional originality had a positive association with pollen deposition, while floral abundance and the number of shared pollinators had a negative association.
-The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific and heterospecific pollen.
+The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological factors for conspecific and heterospecific pollen.
 (c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and purity of conspecific pollen deposition (relative to heterospecific pollen).
@@
 (a) The two first components explain a large proportion of the total variance.
-(b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points—which represent the strategy (the particular combination of ecological variables) of that species in its community—do not seem to be grouped by plant species.
+(b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points—which represent the strategy (the particular combination of ecological factors) of that species in its community—do not seem to be grouped by plant species.
 (c) This was confirmed using Monte Carlo randomizations of the median distance between strategies of a plant species.
@@
 pollinator behaviour and densities or the spatial context) have also been shown to play a role in the outcome of animal-mediated pollination [@ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009; @thomson_effects_2019].
-Nevertheless, our results indicate that the strategies that plant might use to successfully minimise competition for pollination must be determined relative to other species in the community, rather than an absolute property of the species itself.
+Nevertheless, our results indicate that the strategies that plant might use to successfully minimise competition for pollination (or maximise facilitation) must be determined relative to other species in the community, rather than an absolute property of the species itself.
 

### 2019-05-07 paper/draft-info.Rmd
Update draft info

@@
 
+* Removed the criterion to distinguish between competition and facilitation that was based on the difference between conspecific pollen in open and bagged flowers as it didn't add much to the story (said the same as the previously published criteron based on
+the relationship between conspecific and heterospecific pollen) and was based on some assumptions that are easy to question.
 * Added .git and .drake to .dockerignore to speed up build
-* As suggested by Jason I refer to the factors on the main models as mechanisms of pollinator mediated competition. 
+* I refer to the variables on the main models factors and use that term consistently throughout the paper. Previously I was using factor, variable, and sometimes mechanism interchangeably
 * Many minor changes to the text
@@
 * Moved the sentences about variable collinearity to the supp. info. to save a bit of space in the main text
-* Removed criteria #2...

### 2019-05-07 paper/manuscript.Rmd
Some more suggestions by Jason

@@
 <!-- On the other, we could expect a larger amount of conspecific pollen deposited on stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination.  -->
-Second, we investigate the relative contribution that four ecological factors have on the pollination service. 
+Second, we investigate the relative contribution that four ecological factors have to the pollination service. 
 Specifically, we hypothesize that the quantity and purity of cospecific pollen deposition should decreasse for plants that share many pollination partners
@@
 We use these four ecological factors as a proxy of the realised pollination niche of a plant species in their comunity.
-Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict the pollination niche to be influenced by the local context.
+Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict that pollination niche will be influenced by the local context.
 If plant strategy is not flexible across the communities in our study\R{ref-plant-flexibility}, we could expect niches to be more similar within species than across species. 
@@
 
-To investigate the impact of ecological factors on pollination service, we used two sets of linear mixed models (LMM) with bootstrap resampling.
+To investigate the impact of ecological factors on pollination services, we used two sets of linear mixed models (LMM) with bootstrap resampling.
 The response variables for these model sets were the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination. 
@@
 <!-- This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits.  -->
-To account for the non-independence of floral counts and weight all traits equally, we gave a weight of 1/5 to the abundances (one for each month). 
+To account for the non-independence of floral counts and weight all traits equally, we assigned a weight of 1/5 to these abundances (one for each month). 
 We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
@@
 
-We then examined the potential roles played by four ecological factors (number of shared pollinators, abundance, mean visit effectiveness, and functional originality). 
+We then examined the potential roles played in pollen deposition by four ecological factors (number of shared pollinators, abundance, mean visit effectiveness, and functional originality). 
 <!-- Together these variables can describe the niche that plants might occupy in the context of competition for pollination.  -->
@@
 This indicates that, although there is a positive association between visit effectiveness and the quantity of pollen deposition, there is a negative relationship with its purity (Figure \@ref(fig:fig-average-qual-quant)c).
-In contrast, a plants' relative floral abundance negatively affect deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with purity (Figure \@ref(fig:fig-average-qual-quant)c).
+In contrast, a plants' relative floral abundance negatively affected its deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with purity (Figure \@ref(fig:fig-average-qual-quant)c).
 The third most important factor, functional originality, had a positive, although comparatively smaller, association with both the quantity and purity. 
@@
 In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, not only due to costs to male fitness [@muchhala_interspecific_2012; @morales_interspecific_2008], but also because, as we show here, sharing pollinators reduces both the quantity and purity of the conspecific pollen deposited.
-However, over long periods of time, there could be a risk associated with a specialist plant not having pollinators [@ricketts_tropical_2004]. 
+However, over long periods of time, there could be a risk associated with a specialist plant having few pollinators [@ricketts_tropical_2004]. 
 To ensure long-term survival, it is thus likely that plants also need to balance this risk with the costs of sharing pollinators [@aizen_specialization_2012]. 
@@
 First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators [@reverte_pollinators_2016]. 
-Second, the negative relationship between originality and generalism  [@carvalheiro_potential_2014] also depends on plant abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make visiting worthwhile to pollinators.
+Second, the negative relationship between originality and generalism  [@carvalheiro_potential_2014] has been shown to depend on plant abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make visiting worthwhile to pollinators.
 
@@
 pollinator behaviour and densities or the spatial context) have also been shown to play a role in the outcome of animal-mediated pollination [@ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009; @thomson_effects_2019].
-Nevertheless, our results indicate that the strategies that plant might use to successfully minimise competition for pollination (or maximise facilitation) must be determined relative to other species in the community, rather than an absolute property of the species itself.
+Nevertheless, our results indicate that the strategies a plant might use to successfully minimise competition for pollination (or maximise facilitation) must be determined relative to other species in the community, rather than an absolute property of the species itself.
 
@@
 <!-- Interestingly, these two factors also involve the largest trade-offs between increasing deposition of conspecific pollen and reducing that of heterospecific pollen.  -->
-Most remarkably, despite large differences on the quantity and purity of conspecific pollen deposition among species, our results provide solid evidence that competition for pollination is inherently a community process and the same species can occupy different niches in different communities.
+Most remarkably, despite large differences in the quantity and purity of conspecific pollen deposition among species, our results provide solid evidence that competition for pollination is inherently a community process and the same species can occupy different niches in different communities.
 <!-- Overall, species coexistence is not solely determined by direct and indirect mutualistic relationships, but also strongly shaped by the multiple intertwined ecological factors that shape competition for pollination at the community level.

### 2019-05-07 paper/draft-info.Rmd
Spellchecking

@@
 
-* Specify grant numbers in the Awknoledgements and make sure the ones stated there now are correct. 
-* Aprove (or not for submission)
+* Specify grant numbers in the Acknowledgements and make sure the ones stated there now are correct. 
+* Approve (or not) for submission
 
-## Changes since last draft
+## Changes since the last draft
 
-* Removed the criterion to distinguish between competition and facilitation that was based on the difference between conspecific pollen in open and bagged flowers as it didn't add much to the story (said the same as the previously published criteron based on
-the relationship between conspecific and heterospecific pollen) and was based on some assumptions that are easy to question.
+* Removed the criterion to distinguish between competition and facilitation that was based on the difference between conspecific pollen in open and bagged flowers as it didn't add much to the story (said the same as the previously published criterion based on the relationship between conspecific and heterospecific pollen) and was based on some assumptions that are easy to question.
+* This simplified Figure 1
 * Added .git and .drake to .dockerignore to speed up build
-* I refer to the variables on the main models factors and use that term consistently throughout the paper. Previously I was using factor, variable, and sometimes mechanism interchangeably
+* I refer to the variables on the main model's factors and use that term consistently throughout the paper. Previously I was using factor, variable, and sometimes mechanism interchangeably
 * Many minor changes to the text

### 2019-05-07 paper/manuscript.Rmd
Spellchecking

@@
 This happens, for example, when plants with more attractive flowers might reduce the number of visits to those less of attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
-The second is via intrerspecific pollen transfer and occurs when plants share pollination partners. 
+The second is via interspecific pollen transfer and occurs when plants share pollination partners. 
 In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
@@
 Altogether, it is clear that these ecological factors can indeed shape pollen deposition at the community level. 
-However, their relative importance and how exactly they can minimise competition for pollination—or equivalently, maximise facilitation—in plant populations (acrosss species and communities) has not been determined.
+However, their relative importance and how exactly they can minimise competition for pollination—or equivalently, maximise facilitation—in plant populations (across species and communities) has not been determined.
 
-Here, we investigate the balance between competition for pollination abd facilitation at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
+Here, we investigate the balance between competition for pollination and facilitation at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
 First, we estimate the extent to which the net outcome of plants sharing pollinators is facilitation or competition. 
@@
 Second, we investigate the relative contribution that four ecological factors have to the pollination service. 
-Specifically, we hypothesize that the quantity and purity of cospecific pollen deposition should decreasse for plants that share many pollination partners
+Specifically, we hypothesize that the quantity and purity of conspecific pollen deposition should decrease for plants that share many pollination partners
 However, we also hypothesize that other factors like the plant's functional originality, its relative floral abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
-Third and finally, we examine how much the community context influences the way plants exploit these factors to minimise competition/maximise facilitation. 
-We use these four ecological factors as a proxy of the realised pollination niche of a plant species in their comunity.
+Third and finally, we examine how much the community context influences the way plants use these factors to minimise competition/maximise facilitation. 
+We use these four ecological factors as a proxy of the realised pollination niche of a plant species in their community.
 Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict that pollination niche will be influenced by the local context.
@@
 
-Our second objective was to investigate the relative contribution that different eological factors have on the mechanisms of pollinator-mediated competition. 
+Our second objective was to investigate the relative contribution that different ecological factors have on the mechanisms of pollinator-mediated competition. 
 Generally speaking,
@@
 <!-- DBS: There is no use to calling it something succinct like purity if we always have to say "purity relative to heterospecific pollen"...  -->
-<!-- FDO: Only mention purity relative to heterospecific pollen cause it's first time it gets mentioned in the methodsa  -->
+<!-- FDO: Only mention purity relative to heterospecific pollen cause it's first time it gets mentioned in the methods  -->
 Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the amount and type of pollen carried by floral visitors and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010].
@@
 We then calculated the mean visit effectiveness of pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\], where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
-We log-transformed the number of shared pollinators, floral abundance, and visit effecvtiveness before including them in the model.
+We log-transformed the number of shared pollinators, floral abundance, and visit effectiveness before including them in the model.
 
@@
 We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
-Finally, we scaled all foyr factors to have a zero mean and unitary variance.
+Finally, we scaled all four factors to have a zero mean and unitary variance.
 
@@
 For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others.
-Interestingly, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(S-fig:fig-conspecififc-heterospecific)).
+Interestingly, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(S-fig:fig-conspecific-heterospecific)).
 
@@
 
-Of the four factors we considered, we found that a plant's mean visit effectiveness and realtive floral abundance were the most important at predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
+Of the four factors we considered, we found that a plant's mean visit effectiveness and relative floral abundance were the most important at predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
 Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
@@
 Finally, the number of shared pollinators had negative and neutral associations with conspecific and heterospecific pollen, respectively, but these impacts were small when compared to the other factors.
-Athough the ecological factors were positively correlated (Figure \@ref(S-fig:fig-correlation)), the collinearity between predictors did not qualitatively affect our findings (Figure \@ref(S-fig:fig-model-results)).
+Although the ecological factors were positively correlated (Figure \@ref(S-fig:fig-correlation)), the collinearity between predictors did not qualitatively affect our findings (Figure \@ref(S-fig:fig-model-results)).
 
@@
 However, why some species experience more competition than others was not understood. 
-Although we were unable to measure the fitness outcomes, here we show that the coexistence of facilitative and competitive effects of animal-mediated pollination can be at least partially explained by trade-offs in the pollination sercice--both the short and the long term.
+Although we were unable to measure the fitness outcomes, here we show that the coexistence of facilitative and competitive effects of animal-mediated pollination can be at least partially explained by trade-offs in the pollination service--both the short and the long term.
 These trade-offs arise when plants simultaneously maximise the deposition of conspecific pollen and minimise that of heterospecific pollen.

### 2019-05-07 paper/supp-info.Rmd
Spellchecking

@@
 
-```{r fig-conspecififc-heterospecific, fig.height=4, fig.cap="Despite the variation in these slopes, plants overall had more conspecific than heterospecific pollen deposited in their stigmas."}
+```{r fig-conspecific-heterospecific, fig.height=4, fig.cap="Despite the variation in these slopes, plants overall had more conspecific than heterospecific pollen deposited in their stigmas."}
 # fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)

### 2019-05-07 paper/cover-letter.Rnw
Update cover letter

@@
 }
-\date{April 15, 2019}
+\date{May 7, 2019}
 %-----------------------------------------------------------------------------%
@@
 
-In this manuscript, we show that the realised competition for pollination niche (which can also be viewed as a plant species strategy to minimise competition for pollination) is strongly determined by the community it belongs to.
-% DBS: The sentence above just reaffirms my belief that "competition for pollination niche" is NOT the wording we want to use.
+In this manuscript, we show that the realised pollination niche (which can also be viewed as a plant species' strategy to minimise competition for pollination) is strongly determined by the community to which it belongs.
 Furthermore, we show that even in pollination there is no such thing as a free lunch, and plants need to balance multiple trade-offs when minimising competition for pollination.
@@
 
-Very few studies have previously investigated how competition for pollination affects the pollination service using empirical data \emph{at the community level}.
-When they have, XXX and YYY.
-Here, we take this approach a critical step beyond by not only collecting pollen-deposition data but also visitation, pollen transfer, and plant abundance, phenology and traits.
-These extra pieces of information allowed us to interrogate the relationship between pollination service and multiple ecological factors, and, for the first time, quantify the competition for pollination realised niche of plant populations.
-% DBS: And again, it just can't roll off anyone's tongue.
+Very few studies have previously investigated how competition for pollination affects the pollination service using \emph{empirical data at the community level}.
+When they have they have focused on pollen deposition alone and failed to incorporate other metrics that might influence the pollination service in natural communities.
+Here, we take a step beyond by not only collecting pollen-deposition data but also visitation, pollen transfer, plant abundance, phenology, and traits.
+These extra pieces of information allowed us to investigate the relationship between pollination service and multiple ecological factors, and, for the first time, quantify the pollination niche of plant populations.
 
-Within the literature, studies of pollination almost always focus on the inherently mutualistic aspects of plant-pollinator communities. In contrast,
-ours provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
-This calls for a critical shift in the way we think about pollination in community ecology, as well as XXX.
+Within the literature, studies of pollination almost always focus on the inherently mutualistic aspects of plant-pollinator communities.
+In contrast, ours provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
+This calls for a shift in the way we think about pollination in community ecology, especially from a theoretical perspective.
 
-Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors.
+Lastly, please note that the data used in this manuscript have been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors.
 However, the enclosed work represents a novel contribution for all involved, and no related work published, in press, or submitted during this or last year has been cited.
@@
 Thank you for your consideration.
+\vfill
 
+\hfill
+Fernando Cagua
+
+\medskip
 % Closing statement
-\closing{Regards,}
+% \closing{ }
 \end{letter}

### 2019-05-13 paper/cover-letter.Rnw
Use US Letter paper for the cover letter
Typos and fixes discovered by Hugo

@@
 % Letter class
-\documentclass[a4paper, 11pt]{letter}
+\documentclass[11pt]{letter}
 \usepackage{hyperref}
@@
 Very few studies have previously investigated how competition for pollination affects the pollination service using \emph{empirical data at the community level}.
-When they have they have focused on pollen deposition alone and failed to incorporate other metrics that might influence the pollination service in natural communities.
+When they have, they have focused on pollen deposition alone and failed to incorporate other metrics that might influence the pollination service in natural communities.
 Here, we take a step beyond by not only collecting pollen-deposition data but also visitation, pollen transfer, plant abundance, phenology, and traits.
@@
 
-Within the literature, studies of pollination almost always focus on the inherently mutualistic aspects of plant-pollinator communities.
+Within the literature, studies of pollination communities almost always focus on the inherently mutualistic aspects of plant-pollinator interactions.
 In contrast, ours provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.

### 2019-05-13 paper/manuscript.Rmd
Typos and fixes discovered by Hugo

@@
 Second, we investigate the relative contribution that four ecological factors have to the pollination service. 
-Specifically, we hypothesize that the quantity and purity of conspecific pollen deposition should decrease for plants that share many pollination partners
+Specifically, we hypothesize that the quantity and purity of conspecific pollen deposition should decrease for plants that share many pollination partners. 
 However, we also hypothesize that other factors like the plant's functional originality, its relative floral abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
@@
 <!-- Approximately a quarter of these buds were bagged to prevent animal pollination.  -->
-Two days after inflorescence, we collected all remaining flowers and counted the number of conspecific and heterospecific pollen grains in their pistils. 
+Two days after flowering, we collected all remaining flowers and counted the number of conspecific and heterospecific pollen grains in their pistils. 
 More details can be found in @marrero_agricultural_2016.
@@
 To obtain the number of shared pollinators for each species, we collected data to construct qualitative and quantitative pollination networks. 
-Qualitative networks were constructed based on two-hour observations of floral visits in each fragment. 
+Qualitative networks were constructed based on ten-hour observations of floral visits in each fragment. 
 Quantitative networks were constructed using two 50 m randomly located transects in each fragment. 
@@
 Overall, we found that neither net facilitation nor net competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
-Indeed, we found that the proportions of species that experienced a statistically significant positive or negative relationship between heterospecific and conspecific pollen were very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a; Table \@ref(S-tab:table-facilitation-models-random)).
+Indeed, we found that the proportions of species that experienced a statistically significant positive or negative relationship between heterospecific and conspecific pollen were very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions); Table \@ref(S-tab:table-facilitation-models-random)).
 Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
@@
 <!-- DBS: I'd cut the sentence above. -->
-From an evolutionary perspective, our results suggest that that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history.
+From an evolutionary perspective, our results suggest that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history.
 Furthermore, from a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 

### 2019-05-13 paper/draft-info.Rmd
Update draft info

--- 2019-05-06 paper/draft-info.Rmd
@@
 title: "Draft information"
-subtitle: "version: draft-4.0"
-date: "2019-04-26"
+subtitle: "version: draft-6.0"
+date: "2019-05-XX"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
@@
 
-* Specify grant numbers in the Awknoledgements and make sure the ones stated there now are correct. 
-* Aprove (or not for submission)
+* Specify grant numbers in the Acknowledgements and make sure the ones stated there now are correct. 
+* Suggestions to bring the abstract down to 150 words.
+* Approve (or not) for submission.
 
-## Changes since last draft
+## Changes since the last draft
 
-* Added .git and .drake to .dockerignore to speed up build
-* As suggested by Jason I refer to the factors on the main models as mechanisms of pollinator mediated competition. 
-* Many minor changes to the text
-* Replaced instances of "plant abundance" to the more specific term "floral abundance" (Jamie suggested some people working in the field might be finicky with terminology). 
-* Some extra refs added
-* Moved the sentences about variable collinearity to the supp. info. to save a bit of space in the main text
-* Removed criteria #2...
+* Fixed typos and minor wording mistakes

### 2019-05-15 paper/manuscript.Rmd
Pull bibliography from remote instead of submodule

@@
   - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
-bibliography: phd-bibliography/pollen-competition.bib
+bibliography: bibliography.bib
 csl: ecology-letters.csl

### 2019-05-15 paper/draft-info.Rmd
Update manuscript date

@@
 subtitle: "version: draft-6.0"
-date: "2019-05-XX"
+date: "2019-05-15"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"

### 2019-05-15 paper/draft-info.Rmd
Update manuscript changes

@@
 
-## Requests to coauthors
-
-* Specify grant numbers in the Acknowledgements and make sure the ones stated there now are correct. 
-* Suggestions to bring the abstract down to 150 words.
-* Approve (or not) for submission.
-
 ## Changes since the last draft
 
-* Fixed typos and minor wording mistakes
+* Shortened abstract to required length
+* Updated grant numbers in acknowledgements 
+* References are stored in its own repository (efcaguab/phd-references).
+Previously, references were accessed by pulling them as a submodule.
+This created problems when working from different computres.
+References are now just downloaded from the remote file in the github.

### 2019-05-22 paper/draft-info.Rmd

@@
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
-bibliography: phd-bibliography/pollen-competition.bib
+bibliography: bibliography.bib
 csl: ecology-letters.csl

### 2019-05-22 paper/supp-info.Rmd

@@
 ---
-title: "The pollination trade-off"
-# DBS: The title above needs editing to match the final version in the paper
+title: "Community context determines competition vs. facilitation trade-offs in pollination systems"
 subtitle: "Supplementary information"

### 2019-05-22 paper/manuscript.Rmd
Minor edit to title page
Move figures to the end using end-float package

@@
   - \usepackage[export]{adjustbox}
+  - \usepackage[nomarkers]{endfloat}
 ---
@@
 
-**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. The DOI will be included here.
+**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication.
 

### 2019-05-22 paper/manuscript.Rmd
End float package is not compatible with em-dashes in the captions.

@@
 (a) The two first components explain a large proportion of the total variance.
-(b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points—which represent the strategy (the particular combination of ecological factors) of that species in its community—do not seem to be grouped by plant species.
+(b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points, which represent the strategy (the particular combination of ecological factors) of that species in its community, do not seem to be grouped by plant species.
 (c) This was confirmed using Monte Carlo randomizations of the median distance between strategies of a plant species.

### 2019-05-22 paper/manuscript.Rmd
Double spacing of legends at the end of paper
Remove comment, was showing up in the manuscript
Fix legend of fig. 2 to use ecological factors instead of strategies

@@
 \doublespacing
+\AtBeginDelayedFloats{%
+      \renewcommand{\baselinestretch}{2}}
 
@@
 
-```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=width('single'), out.height="4.56in", out.width="3.57in", out.extra="center", fig.cap="Effect of strategies to minimise competition in the pollination service.
+```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=width('single'), out.height="4.56in", out.width="3.57in", out.extra="center", fig.cap="Effect of ecological factors on the pollination service.
 (a) The plant's visit effectiveness and relative floral abundance are the most important factors determining the deposition of conspecific and heterospecific pollen.

### 2019-05-26 paper/draft-info.Rmd

--- 2019-05-15 paper/draft-info.Rmd
@@
 title: "Draft information"
-subtitle: "version: draft-6.0"
-date: "2019-05-15"
+subtitle: "version: draft-6.1"
+date: "2019-05-23"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
-bibliography: phd-bibliography/pollen-competition.bib
+bibliography: bibliography.bib
 csl: ecology-letters.csl
@@
 
-## Requests to coauthors
-
-* Specify grant numbers in the Acknowledgements and make sure the ones stated there now are correct. 
-* Suggestions to bring the abstract down to 150 words.
-* Approve (or not) for submission.
-
 ## Changes since the last draft
 
-* Fixed typos and minor wording mistakes
+* Moved figures at the end of the manuscript
+* Refer to Figures as "Fig." in the main text
+* Minor correction to Figure 2 caption

### 2019-05-26 paper/manuscript.Rmd

@@
 In each of the studied communities, we quantified pollen deposition in a subset of plant species between December 2010 and February 2011. 
-This subset comprised between three and nine common insect-pollinated (entomophilous) plant species that were flowering during the sampling period (see Figure \@ref(fig:fig-trade-off-predictions)a). 
+This subset comprised between three and nine common insect-pollinated (entomophilous) plant species that were flowering during the sampling period (see Fig. \@ref(fig:fig-trade-off-predictions)a). 
 Based on data from previous years [@marrero_effect_2014], we chose plant species such that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 
@@
 Overall, we found that neither net facilitation nor net competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
-Indeed, we found that the proportions of species that experienced a statistically significant positive or negative relationship between heterospecific and conspecific pollen were very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions); Table \@ref(S-tab:table-facilitation-models-random)).
+Indeed, we found that the proportions of species that experienced a statistically significant positive or negative relationship between heterospecific and conspecific pollen were very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Fig.
+\@ref(fig:fig-trade-off-predictions); Table \@ref(S-tab:table-facilitation-models-random)).
 Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
 For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others.
-Interestingly, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(S-fig:fig-conspecific-heterospecific)).
+Interestingly, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Fig.
+\@ref(S-fig:fig-conspecific-heterospecific)).
 
@@
 <!-- Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers (Table \@ref(S-tab:table-open-bagged-models-general)).  -->
-<!-- Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had less pollen when open (the difference was statistically non-significant for the remaining `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
+<!-- Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had less pollen when open (the difference was statistically non-significant for the remaining `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Fig.
+\@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
 -->
@@
 
-Of the four factors we considered, we found that a plant's mean visit effectiveness and relative floral abundance were the most important at predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a).
+Of the four factors we considered, we found that a plant's mean visit effectiveness and relative floral abundance were the most important at predicting pollen deposition in plant stigmas (Fig.
+\@ref(fig:fig-average-qual-quant)a).
 Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
@@
 That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
-Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
+Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Fig. \@ref(fig:fig-average-qual-quant)b). 
 However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
-This indicates that, although there is a positive association between visit effectiveness and the quantity of pollen deposition, there is a negative relationship with its purity (Figure \@ref(fig:fig-average-qual-quant)c).
-In contrast, a plants' relative floral abundance negatively affected its deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with purity (Figure \@ref(fig:fig-average-qual-quant)c).
+This indicates that, although there is a positive association between visit effectiveness and the quantity of pollen deposition, there is a negative relationship with its purity (Fig.
+\@ref(fig:fig-average-qual-quant)c).
+In contrast, a plants' relative floral abundance negatively affected its deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with purity (Fig.
+\@ref(fig:fig-average-qual-quant)c).
 The third most important factor, functional originality, had a positive, although comparatively smaller, association with both the quantity and purity. 
 Finally, the number of shared pollinators had negative and neutral associations with conspecific and heterospecific pollen, respectively, but these impacts were small when compared to the other factors.
-Although the ecological factors were positively correlated (Figure \@ref(S-fig:fig-correlation)), the collinearity between predictors did not qualitatively affect our findings (Figure \@ref(S-fig:fig-model-results)).
+Although the ecological factors were positively correlated (Fig.
+\@ref(S-fig:fig-correlation)), the collinearity between predictors did not qualitatively affect our findings (Fig.
+\@ref(S-fig:fig-model-results)).
 
@@
 We used a PCA of the analysed species to investigate whether plants' realised pollination niche is similar across communities or whether they are flexible and therefore a reflection of the community context.
-The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
+The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Fig. \@ref(fig:fig-pca)a). 
 The first component was dominated by visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality. 
-When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
-Indeed, when we measured the median distance between the plants' coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` species analysed (Figure \@ref(fig:fig-pca)c).
+When we locate the species that were sampled in more than one community in the first two PCA components (Fig.
+\@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
+Indeed, when we measured the median distance between the plants' coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` species analysed (Fig.
+\@ref(fig:fig-pca)c).
 <!-- DBS: Are we consistent with UK vs US spellings? Does Ecology Letters prefer UK spelling? -->

### 2019-06-06 paper/draft-info.Rmd
Use plos Biology citation format

@@
 bibliography: bibliography.bib
-csl: ecology-letters.csl
+csl: plos-biology.csl
 output:

### 2019-06-06 paper/manuscript.Rmd
Use plos Biology citation format

@@
 bibliography: bibliography.bib
-csl: ecology-letters.csl
+csl: plos-biology.csl
 output: #word_document

### 2019-06-06 paper/supp-info.Rmd
Use plos Biology citation format

@@
 # bibliography: references.bib
-csl: ecology-letters.csl
+csl: plos-biology.csl
 documentclass: book

### 2019-06-06 code/count_words.R
Remove comments when counting references

@@ -52,6 +52,12 @@ get_citations <- function(filename, lines_to_ignore = NULL, refs_to_exclude = NU
     text_lines <- text_lines[-lines_to_ignore]
   }
 
+  # remove comments
+  if(ignore_md_comments){
+    text_lines %<>%
+      stringr::str_replace("<!--.+-->", "")
+  }
+
   citations <- text_lines %>%
     stringr::str_extract("@\\w+") %>%
     na.omit()

### 2019-06-06 paper/manuscript.Rmd
Figures back to the middle of the text

@@
   - \usepackage[export]{adjustbox}
-  - \usepackage[nomarkers]{endfloat}
+  # - \usepackage[nomarkers]{endfloat}
 ---
@@
 \doublespacing
-\AtBeginDelayedFloats{%
-      \renewcommand{\baselinestretch}{2}}
 

### 2019-06-06 paper/manuscript.Rmd
Remove ref to Fig 1 from Methods

@@
 In each of the studied communities, we quantified pollen deposition in a subset of plant species between December 2010 and February 2011. 
-This subset comprised between three and nine common insect-pollinated (entomophilous) plant species that were flowering during the sampling period (see Fig. \@ref(fig:fig-trade-off-predictions)a). 
+This subset comprised between three and nine common insect-pollinated (entomophilous) plant species that were flowering during the sampling period. 
 Based on data from previous years [@marrero_effect_2014], we chose plant species such that they cover a wide range on a specialization-generalization gradient as well as a wide range of abundances. 

### 2019-06-06 paper/manuscript.Rmd
Move figures after paragraph from which they are first referenced

@@
 
-We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
-That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
-Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Fig. \@ref(fig:fig-average-qual-quant)b). 
-However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
-This indicates that, although there is a positive association between visit effectiveness and the quantity of pollen deposition, there is a negative relationship with its purity (Fig.
-\@ref(fig:fig-average-qual-quant)c).
-In contrast, a plants' relative floral abundance negatively affected its deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with purity (Fig.
-\@ref(fig:fig-average-qual-quant)c).
-The third most important factor, functional originality, had a positive, although comparatively smaller, association with both the quantity and purity. 
-Finally, the number of shared pollinators had negative and neutral associations with conspecific and heterospecific pollen, respectively, but these impacts were small when compared to the other factors.
-Although the ecological factors were positively correlated (Fig.
-\@ref(S-fig:fig-correlation)), the collinearity between predictors did not qualitatively affect our findings (Fig.
-\@ref(S-fig:fig-model-results)).
-
 ```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=width('single'), out.height="4.56in", out.width="3.57in", out.extra="center", fig.cap="Effect of ecological factors on the pollination service.
@@
 
+We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
+That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
+Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Fig. \@ref(fig:fig-average-qual-quant)b). 
+However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
+This indicates that, although there is a positive association between visit effectiveness and the quantity of pollen deposition, there is a negative relationship with its purity (Fig.
+\@ref(fig:fig-average-qual-quant)c).
+In contrast, a plants' relative floral abundance negatively affected its deposition quantity, but the mean difference between the coefficients in the models indicates a positive association with purity (Fig.
+\@ref(fig:fig-average-qual-quant)c).
+The third most important factor, functional originality, had a positive, although comparatively smaller, association with both the quantity and purity. 
+Finally, the number of shared pollinators had negative and neutral associations with conspecific and heterospecific pollen, respectively, but these impacts were small when compared to the other factors.
+Although the ecological factors were positively correlated (Fig.
+\@ref(S-fig:fig-correlation)), the collinearity between predictors did not qualitatively affect our findings (Fig.
+\@ref(S-fig:fig-model-results)).
+
 ## Flexibility of plant strategies
@@
 ```
+We used a PCA of the analysed species to investigate whether plants' realised pollination niche is similar across communities or whether they are flexible and therefore a reflection of the community context.
+The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Fig. \@ref(fig:fig-pca)a). 
+The first component was dominated by visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality. 
+When we locate the species that were sampled in more than one community in the first two PCA components (Fig.
+\@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
+Indeed, when we measured the median distance between the plants' coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` species analysed (Fig.
+\@ref(fig:fig-pca)c).
+<!-- DBS: Are we consistent with UK vs US spellings? Does Ecology Letters prefer UK spelling? -->
 
@@
 ```
-
-We used a PCA of the analysed species to investigate whether plants' realised pollination niche is similar across communities or whether they are flexible and therefore a reflection of the community context.
-The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Fig. \@ref(fig:fig-pca)a). 
-The first component was dominated by visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality. 
-When we locate the species that were sampled in more than one community in the first two PCA components (Fig.
-\@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
-Indeed, when we measured the median distance between the plants' coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` species analysed (Fig.
-\@ref(fig:fig-pca)c).
-<!-- DBS: Are we consistent with UK vs US spellings? Does Ecology Letters prefer UK spelling? -->
 

### 2019-06-06 paper/manuscript.Rmd
Visit effectiveness is now renamed as visit potential

@@
 Specifically, we hypothesize that the quantity and purity of conspecific pollen deposition should decrease for plants that share many pollination partners. 
-However, we also hypothesize that other factors like the plant's functional originality, its relative floral abundance, and the visit effectiveness should have the potential to compensate for this increase in competition.
+However, we also hypothesize that other factors like the plant's functional originality, its relative floral abundance, and the visit potential should have the potential to compensate for this increase in competition.
 Third and finally, we examine how much the community context influences the way plants use these factors to minimise competition/maximise facilitation. 
@@
 <!-- FDO: Only mention purity relative to heterospecific pollen cause it's first time it gets mentioned in the methods  -->
-Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines the amount and type of pollen carried by floral visitors and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010].
+Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit potential---a metric that combines the amount and type of pollen carried by floral visitors and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010].
 See *Data Analysis* section below for more details on these four factors. 
@@
 To obtain floral abundance, we counted all units of floral attraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
-To estimate visit effectiveness, we need to construct pollen transfer networks in addition to the visitation networks. 
+To estimate visit potential, we need to construct pollen transfer networks in addition to the visitation networks. 
 To do this, we examined the pollen loads present on the floral visitors collected [@marrero_exotic_2017]. 
@@
 To calculate the plants' relative floral abundance in their community, we aggregated floral counts for each species. 
-We then calculated the mean visit effectiveness of pollinator species *i* to plant species *j* as \[e_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\], where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
-We log-transformed the number of shared pollinators, floral abundance, and visit effectiveness before including them in the model.
+We then calculated the mean visit potential of pollinator species *i* to plant species *j* as \[o_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\], where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
+We log-transformed the number of shared pollinators, floral abundance, and visit potential before including them in the model.
 
@@
 Alternatively, if the community plays a large role and/or plant strategies are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
-To test this, we first used a principal component analysis (PCA) of the four ecological factors (number of shared pollinators, floral abundance, visit effectiveness, and trait originality). 
+To test this, we first used a principal component analysis (PCA) of the four ecological factors (number of shared pollinators, floral abundance, visit potential, and trait originality). 
 We scaled factors across the whole study to ensure that the PCA space does not change according to the species present in each community. 
@@
 
-We then examined the potential roles played in pollen deposition by four ecological factors (number of shared pollinators, abundance, mean visit effectiveness, and functional originality). 
+We then examined the potential roles played in pollen deposition by four ecological factors (number of shared pollinators, abundance, mean visit potential, and functional originality). 
 <!-- Together these variables can describe the niche that plants might occupy in the context of competition for pollination.  -->
@@
 
-Of the four factors we considered, we found that a plant's mean visit effectiveness and relative floral abundance were the most important at predicting pollen deposition in plant stigmas (Fig.
+Of the four factors we considered, we found that a plant's mean visit potential and relative floral abundance were the most important at predicting pollen deposition in plant stigmas (Fig.
 \@ref(fig:fig-average-qual-quant)a).
@@
 ```{r fig-average-qual-quant, fig.height= 2.28*2, fig.width=width('single'), out.height="4.56in", out.width="3.57in", out.extra="center", fig.cap="Effect of ecological factors on the pollination service.
-(a) The plant's visit effectiveness and relative floral abundance are the most important factors determining the deposition of conspecific and heterospecific pollen.
+(a) The plant's visit potential and relative floral abundance are the most important factors determining the deposition of conspecific and heterospecific pollen.
 Meanwhile, the number of shared pollinators was generally less important.
@@
 (b) The association between ecological factors and heterospecific pollen tended to align with their association with conspecific pollen.
-Visit effectiveness and functional originality had a positive association with pollen deposition, while floral abundance and the number of shared pollinators had a negative association.
+Visit potential and functional originality had a positive association with pollen deposition, while floral abundance and the number of shared pollinators had a negative association.
 The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological factors for conspecific and heterospecific pollen.
@@
 That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
-Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Fig. \@ref(fig:fig-average-qual-quant)b). 
+Specifically, the plants' mean visit potential had a positive effect on pollen deposition (Fig. \@ref(fig:fig-average-qual-quant)b). 
 However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
-This indicates that, although there is a positive association between visit effectiveness and the quantity of pollen deposition, there is a negative relationship with its purity (Fig.
+This indicates that, although there is a positive association between visit potential and the quantity of pollen deposition, there is a negative relationship with its purity (Fig.
 \@ref(fig:fig-average-qual-quant)c).
@@
 The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Fig. \@ref(fig:fig-pca)a). 
-The first component was dominated by visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality. 
+The first component was dominated by visit potential and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality. 
 When we locate the species that were sampled in more than one community in the first two PCA components (Fig.
@@
 
-Visit effectiveness (high pollen and visits) and floral abundance, which were the most important predictors of pollen deposition here, introduced an even more explicit trade-off between gaining conspecific pollen and avoiding heterospecific pollen.
+Visit potential (high pollen and visits) and floral abundance, which were the most important predictors of pollen deposition here, introduced an even more explicit trade-off between gaining conspecific pollen and avoiding heterospecific pollen.
 Receiving high visitation increases conspecific pollen deposition but increases heterospecific pollen deposition to a greater extent---even when the visitors are likely to carry a high proportion of conspecific pollen [@fang_paradoxical_2016].

### 2019-06-06 paper/supp-info.Rmd
Visit effectiveness is now renamed as visit potential

@@
 ```{r fig-model-results, fig.height = 5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain.
-Model formulas have been abbreviated: *a* for abundance, *k* for the number of shared pollinators, *p* for the visit effectiveness, and *t* for trait originality.
+Model formulas have been abbreviated: *a* for abundance, *k* for the number of shared pollinators, *o* for the visit potential, and *t* for functional originality.
 Only candidate formulas with a $\\Delta AICc < 4$ for either conspecific or heterospecific pollen are shown.
 Models candidates are arranged in decreasing order of support.
-Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated, the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables.
-One exception was visit-effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations.
+Although relative abundance, the number of shared pollinators, and the visit potential were all positively correlated, the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables.
+One exception was visit potential, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations.
 Nevertheless, these differences were observed only in model specifications with relatively low AICc support.", eval=T}

### 2019-06-06 code/pca.R

@@ -402,7 +402,7 @@ plot_pca_variances_and_contributions <- function(pcas, chosen_threshold){
 
   contributions_data %>%
     humanize(term_long = F) %>%
-    dplyr::mutate(term = forcats::fct_relevel(term, "visit effectiv.", "abundance", "func. originality")) %>%
+    dplyr::mutate(term = forcats::fct_relevel(term, "visit potential", "abundance", "func. originality")) %>%
     ggplot(aes(x = as.numeric(dim), y = contribution)) +
     geom_col(aes(fill = term), alpha = 0.75,
              position = position_stack(reverse = TRUE)) +

### 2019-06-06 code/plotting_and_formatting.R

@@ -82,8 +82,8 @@ humanize <- function(x, sites = NA, random_effects = NA, formula_long = FALSE, t
           grepl('rab', term) ~ 'abundance',
           grepl('deg', term) ~ '# shared pol.',
           grepl('k', term) ~ '# shared pol.',
-          grepl('poc', term) ~ 'visit effectiveness',
-          grepl('pollen_cont', term) ~ 'visit effectiveness',
+          grepl('poc', term) ~ 'visit potential',
+          grepl('pollen_cont', term) ~ 'visit potential',
           TRUE ~ term
         ))
     } else {
@@ -96,8 +96,8 @@ humanize <- function(x, sites = NA, random_effects = NA, formula_long = FALSE, t
           grepl('rab', term) ~ 'abundance',
           grepl('deg', term) ~ '# shared pol.',
           grepl('k', term) ~ '# shared pol.',
-          grepl('poc', term) ~ 'visit effectiv.',
-          grepl('pollen_cont', term) ~ 'visit effectiv.',
+          grepl('poc', term) ~ 'visit potential',
+          grepl('pollen_cont', term) ~ 'visit potential',
           TRUE ~ term
         ))
     }
@@ -109,15 +109,15 @@ humanize <- function(x, sites = NA, random_effects = NA, formula_long = FALSE, t
         dplyr::mutate(
           fixed_formula = stringr::str_replace(fixed_formula, "pollen_gain ~", ""),
           fixed_formula = stringr::str_replace(fixed_formula, "abn", "abundance"),
-          fixed_formula = stringr::str_replace(fixed_formula, "poc", "share pollen"),
+          fixed_formula = stringr::str_replace(fixed_formula, "poc", "visit potential"),
           fixed_formula = stringr::str_replace(fixed_formula, "org", "func. originality"),
-          fixed_formula = stringr::str_replace(fixed_formula, "deg", "degree"))
+          fixed_formula = stringr::str_replace(fixed_formula, "deg", "# shared pol."))
     } else {
       x <- x %>%
         dplyr::mutate(
           fixed_formula = stringr::str_replace(fixed_formula, "pollen_gain ~", ""),
           fixed_formula = stringr::str_replace(fixed_formula, "abn", "a"),
-          fixed_formula = stringr::str_replace(fixed_formula, "poc", "p"),
+          fixed_formula = stringr::str_replace(fixed_formula, "poc", "o"),
[…]

### 2019-06-07 paper/manuscript.Rmd
Add stuff in intro to support link between pollen deposition and fitness

@@
 In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
-Generally speaking, provided pollen is viable and compatible [@ramsey_pollen_2000; @de_jong_plant_1992; @dafni_pollen_2000], the higher the quantity of conspecific pollen and its purity (relative to heterospecific pollen), the better the pollination service received by the focal plant.
-By definition, these two mechanisms of competition occur at the community scale. 
-However, with few exceptions [@tur_evaluating_2016; @aizen_reproductive_2010], most of what we know about them and their relationship with key ecological factors is based on studies with two plant species.
+\R{start-deposition-facil-competition}Naturally, the precise effects on plant fitness of conspecific and heterospecific pollen deposition depend on the species involved (and are unknown for many plant species).
+However, there is substantial evidence supporting the link between pollen deposition and seed production; in particular for the detrimental effect of heterospecific pollen deposition on plant fitness [@ashman_toward_2013; @arceo-gomez_invasion_2016].
+All together, provided pollen is viable and compatible [@ramsey_pollen_2000; @de_jong_plant_1992; @dafni_pollen_2000], the higher the quantity of conspecific pollen and its purity (relative to heterospecific pollen), the better the pollination service received by the focal plant.
+As such, measuring conspecific and heterospecific pollen deposition provides a good indication of the potential levels of facilitation and competition a plant population might experience.
 
+By definition, these two mechanisms of competition, intra and interspecific pollen transfer, occur at the community scale.
+However, with few exceptions [@tur_evaluating_2016; @aizen_reproductive_2010], most of what we know about them and their relationship with key ecological factors is based on studies with two plant species\R{end-deposition-facil-competition}.
 That is partly so because, at the community scale, the factors that determine the patterns of pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].

### 2019-06-07 paper/draft-info.Rmd
Using A4 paper everywhere

@@
 toc: false
+classoption: a4paper
 geometry: 

### 2019-06-07 paper/manuscript.Rmd
Using A4 paper everywhere

@@
 fontsize: 11pt
-# classoption: a4paper
+classoption: a4paper
 geometry: 

### 2019-06-07 paper/supp-info.Rmd
Using A4 paper everywhere

@@
 documentclass: book
+classoption: a4paper
 nocite: | 

### 2019-06-07 paper/cover-letter.Rnw
Update manuscript date
Using A4 paper everywhere
Edits to the cover letter

@@
 % Letter class
-\documentclass[11pt]{letter}
+\documentclass[11pt, a4paper]{letter}
 \usepackage{hyperref}
 \usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
-\addbibresource{phd-bibliography/pollen-competition.bib}
+\addbibresource{bibliography.bib}
 \usepackage{geometry}
-\geometry{textwidth=43em, textheight=52\baselineskip}
+\geometry{textwidth=43em, textheight=55\baselineskip}
 % Name of sender
@@
 }
-\date{May 7, 2019}
+\date{May 15, 2019}
 %-----------------------------------------------------------------------------%
@@
 
-We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Ecology Letters}.
+We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Plos Biology}.
+The main goal of this study, to explore the balance between competition and facilitation in plants belonging to the same community.
+
+Although the idea that plants can compete for pollinators or facilitate each other has been on the table for a long time, a definitive answer has not been reached yet.
+Very few studies have previously investigated how competition for pollination affects the pollination service using \emph{empirical data at the community level}.
+When they have, they have focused on pollen deposition alone and failed to incorporate other metrics that might influence the pollination service in natural communities.
+Here, we take a step beyond by not only collecting pollen-deposition data but also visitation, pollen transfer, plant abundance, phenology, and traits.
+These extra pieces of information allowed us to investigate the relationship between pollination service and multiple ecological factors, and, for the first time, quantify the pollination niche of plant populations.
 
@@
 % DBS: The use of short-term here is very ambiguous.
-
-Very few studies have previously investigated how competition for pollination affects the pollination service using \emph{empirical data at the community level}.
-When they have, they have focused on pollen deposition alone and failed to incorporate other metrics that might influence the pollination service in natural communities.
-Here, we take a step beyond by not only collecting pollen-deposition data but also visitation, pollen transfer, plant abundance, phenology, and traits.
-These extra pieces of information allowed us to investigate the relationship between pollination service and multiple ecological factors, and, for the first time, quantify the pollination niche of plant populations.
 

### 2019-06-07 paper/draft-info.Rmd
Updates to draft info

--- 2019-06-06 paper/draft-info.Rmd
@@
 title: "Draft information"
-subtitle: "version: draft-6.1"
-date: "2019-05-23"
+subtitle: "version: draft-7.0"
+date: "2019-06-07"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
-bibliography: bibliography.bib
-csl: plos-biology.csl
+# bibliography: bibliography.bib
+# csl: plos-biology.csl
 output:
@@
   - \externaldocument[M-]{manuscript}
-
 ---
@@
 
+## Requests to coauthors
+
+* Check text between \lr{M-start-deposition-facil-competition} and \lr{M-end-deposition-facil-competition} where there were changes.
+* Check the cover letter. I made small changes based on assessment from EL editor and swapped the order of a couple paragraphs. 
+* __Jason__: Could you please double check your grant numbers? They look different to Daniel's.
+
 ## Changes since the last draft
 
-* Moved figures at the end of the manuscript
-* Refer to Figures as "Fig." in the main text
-* Minor correction to Figure 2 caption
+* Renamed visit effectiveness as visit potential throughout to reduce confusion with previous uses of the term.
+* Corrected a mistake on the names used for the model terms in Table S5. It used to say "degree" where it should have been "# shared pollinators".
+* Corrected caption of Fig S3 which used "trait originality" instead of "functional originality" which is the term we use in the paper
+* Paper has been formatted with minimum requirements for initial submission at Plos Biology.
+* Added some sentences in the intro to strengthten the link between competition/facilitation and conspecific/heterospecific pollen.

### 2019-06-07 paper/manuscript.Rmd
Minimal formatting for PLOS initial submission

@@
 
-**Running title:** 
-Competition for pollination vs. facilitation
+**Short title:** Competition for pollination vs. facilitation
 
-**Keywords:** `r keywords`
+<!-- **Keywords:** `r keywords` -->
 
-**Type of article:** Letter.
+**Type of article:** Primary research article
 
@@
 
-**Number of references:** `r n_references`
+<!-- **Number of references:** `r n_references` -->
 
@@
 
-**Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.
+<!-- **Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.  -->
+
+**Competing interests:** The authors have declared that no competing interests exist.
 

### 2019-06-11 paper/cover-letter.Rnw
Update cover letter

@@
 \usepackage{geometry}
-\geometry{textwidth=43em, textheight=55\baselineskip}
+\geometry{textwidth=33em, textheight=45\baselineskip}
 % Name of sender
@@
 }
-\date{May 15, 2019}
+\date{June 11, 2019}
 %-----------------------------------------------------------------------------%
@@
 {
-    Prof.\ Tim Coulson,\\
+    Dr. Emma Ganley, \\
     Editorial Office,\\
-    Ecology Letters
+    Plos Biology
 }
 % Opening statement
-\opening{Dear Professor Coulson,}
+\opening{Dear Doctor Ganley,}
 % Letter body
@@
 Although the idea that plants can compete for pollinators or facilitate each other has been on the table for a long time, a definitive answer has not been reached yet.
-Very few studies have previously investigated how competition for pollination affects the pollination service using \emph{empirical data at the community level}.
-When they have, they have focused on pollen deposition alone and failed to incorporate other metrics that might influence the pollination service in natural communities.
-Here, we take a step beyond by not only collecting pollen-deposition data but also visitation, pollen transfer, plant abundance, phenology, and traits.
-These extra pieces of information allowed us to investigate the relationship between pollination service and multiple ecological factors, and, for the first time, quantify the pollination niche of plant populations.
+Many of the key theoretical papers on mutualistic communities\autocite{bascompte_asymmetric_2006, bastolla_architecture_2009, rohr_structural_2014} almost always focus on the inherently beneficial aspects of plant-pollinator interactions.
+Empirical work has often mirrored this focus, though a few community-level studies have explored the extent to which plants who share pollinators compete vs.
+facilitate each other\autocite{tur_evaluating_2016, aizen_reproductive_2010}.
+Importantly, these studies only measured the deposition of pollen, whereas plants can modulate competition by partitioning their pollination niche in many ways, such as through flowering time, attractiveness, or how they attach pollen to pollinators.
+We, therefore, quantified, for the first time, the true pollination niche of plants, by incorporating measures of visitation, pollen transfer, floral abundance, phenology, and traits.
 
@@
 On the other, factors that increase both the quantity and purity do so only mildly and potentially only in the short-term.
-% DBS: one hand and the other, again...
-% DBS: The use of short-term here is very ambiguous.
 
-Within the literature, studies of pollination communities almost always focus on the inherently mutualistic aspects of plant-pollinator interactions.
-In contrast, ours provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
-This calls for a shift in the way we think about pollination in community ecology, especially from a theoretical perspective.
+This work provides fundamental understanding of plant reproductive biology, while also calling for a shift in the way we think about pollination in community ecology, especially from a theoretical perspective.
+In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
+Thus, we believe that this manuscript will be interesting to the broad readership of PLoS Biology.
 
 Lastly, please note that the data used in this manuscript have been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors.
-However, the enclosed work represents a novel contribution for all involved, and no related work published, in press, or submitted during this or last year has been cited.
+However, the enclosed work represents a novel contribution from all involved.
 
 Thank you for your consideration.
-\vfill
+\bigskip
 
 \hfill
-Fernando Cagua
+Fernando Cagua,
+Hugo Marrero,
+Jason Tylianakis \&
+Daniel Stouffer
 
-\medskip
+\vfill
 % Closing statement

### 2019-06-11 paper/cover-letter.Rnw
Final touches to cover letter

@@
 \usepackage{geometry}
-\geometry{textwidth=33em, textheight=45\baselineskip}
+\usepackage{setspace}
+\geometry{textwidth=30em, textheight=45\baselineskip}
 % Name of sender
@@
 % Letter body
-
+\onehalfspacing
 <<my-label, eval=TRUE, echo=FALSE>>=
@@
 Many of the key theoretical papers on mutualistic communities\autocite{bascompte_asymmetric_2006, bastolla_architecture_2009, rohr_structural_2014} almost always focus on the inherently beneficial aspects of plant-pollinator interactions.
-Empirical work has often mirrored this focus, though a few community-level studies have explored the extent to which plants who share pollinators compete vs.
-facilitate each other\autocite{tur_evaluating_2016, aizen_reproductive_2010}.
+Empirical work has often mirrored this focus, though a few community-level studies\autocite{tur_evaluating_2016, aizen_reproductive_2010} have explored the extent to which plants who share pollinators compete or facilitate each other.
 Importantly, these studies only measured the deposition of pollen, whereas plants can modulate competition by partitioning their pollination niche in many ways, such as through flowering time, attractiveness, or how they attach pollen to pollinators.
@@
 
-This work provides fundamental understanding of plant reproductive biology, while also calling for a shift in the way we think about pollination in community ecology, especially from a theoretical perspective.
+This work provides fundamental understanding of plant reproductive biology, while also \emph{calling for a shift in the way we think about pollination in community ecology}, especially from a theoretical perspective.
 In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.

### 2019-06-11 paper/draft-info.Rmd
Update draft information

--- 2019-06-06 paper/draft-info.Rmd
@@
 title: "Draft information"
-subtitle: "version: draft-6.1"
-date: "2019-05-23"
+subtitle: "version: draft-7.1"
+date: "2019-06-11"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
-bibliography: bibliography.bib
-csl: plos-biology.csl
+# bibliography: bibliography.bib
+# csl: plos-biology.csl
 output:
@@
 
-* Moved figures at the end of the manuscript
-* Refer to Figures as "Fig." in the main text
-* Minor correction to Figure 2 caption
+* Changed cover letter. Now the significance of results is clearer and the non-incremental aspects of the study are emphasized. Checked that it conforms to the journal guidelines. 
+* Adjusted one of Jason's grant numbers.

### 2019-06-12 paper/cover-letter.Rnw
Some format changes to enable initial submission in Nat Eco Evo

@@
 }
-\date{June 11, 2019}
+\date{June 13, 2019}
 %-----------------------------------------------------------------------------%
@@
 {
-    Dr. Emma Ganley, \\
     Editorial Office,\\
-    Plos Biology
+    Nature Ecology and Evolution
 }
 % Opening statement
-\opening{Dear Doctor Ganley,}
+\opening{Dear Editorial Team,}
 % Letter body
@@
 
-We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Plos Biology}.
+We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Nature Ecology and Evolution}.
 The main goal of this study, to explore the balance between competition and facilitation in plants belonging to the same community.

### 2019-06-12 paper/draft-info.Rmd
Some format changes to enable initial submission in Nat Eco Evo

--- 2019-06-07 paper/draft-info.Rmd
@@
 title: "Draft information"
-subtitle: "version: draft-6.1"
-date: "2019-05-23"
+subtitle: "version: draft-7.2"
+date: "2019-06-13"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
-bibliography: bibliography.bib
-csl: plos-biology.csl
+# bibliography: bibliography.bib
+# csl: plos-biology.csl
 output:
@@
 
-* Moved figures at the end of the manuscript
-* Refer to Figures as "Fig." in the main text
-* Minor correction to Figure 2 caption
+* Adjusted cover letter to submit to Nature Ecology and Evolution

### 2019-06-12 paper/manuscript.Rmd
Biorxiv declaration
Some format changes to enable initial submission in Nat Eco Evo

@@
 bibliography: bibliography.bib
-csl: plos-biology.csl
+csl: nature.csl
 output: #word_document
@@
 **Competing interests:** The authors have declared that no competing interests exist.
+
+<!-- The authors do not wish to opt-in to post the submission as a preprint on bioRxiv -->
 

### 2019-06-12 paper/supp-info.Rmd
Some format changes to enable initial submission in Nat Eco Evo

--- 2019-06-06 paper/supp-info.Rmd
@@
 # bibliography: references.bib
-csl: plos-biology.csl
+csl: nature.csl
 documentclass: book
+classoption: a4paper
 nocite: | 

### 2019-06-13 paper/cover-letter.Rnw
Fix reference to PLOS in cover letter
Update date

@@
 }
-\date{June 13, 2019}
+\date{June 14, 2019}
 %-----------------------------------------------------------------------------%
@@
     Editorial Office,\\
-    Nature Ecology and Evolution
+    Nature Ecology \& Evolution
 }
@@
 In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
-Thus, we believe that this manuscript will be interesting to the broad readership of PLoS Biology.
+Thus, we believe that this manuscript will be interesting to the broad readership of Nature Ecology \& Evolution.
 

### 2019-06-13 paper/draft-info.Rmd
Update date

@@
 subtitle: "version: draft-7.2"
-date: "2019-06-13"
+date: "2019-06-14"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
 # bibliography: bibliography.bib
-# csl: plos-biology.csl
+# csl: nature.csl
 output:

### 2019-06-17 paper/manuscript.Rmd
Use journal abbreviations in references
Explain that word count includes methods section

@@
 
-loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords)
+loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords, references)
 ```
@@
 
-**Type of article:** Primary research article
+<!-- **Type of article:** Primary research article -->
 
-**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.
+**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text (including Methods section).
 

### 2019-06-17 paper/cover-letter.Rnw
Add phone number in Cover Letter
NEE Requires full contact information in the cover letter
Add info about format of initial submition
Explaining that we're happy to change it in future drafts

@@
 \usepackage{setspace}
-\geometry{textwidth=30em, textheight=45\baselineskip}
+\geometry{textwidth=31em, textheight=46\baselineskip}
 % Name of sender
@@
     \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
+    +64 20 402 68153 \\
     University of Canterbury, \\
@@
 
-We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Nature Ecology and Evolution}.
-The main goal of this study, to explore the balance between competition and facilitation in plants belonging to the same community.
+We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Nature Ecology \& Evolution}.
+The main goal of this study is to explore the balance between competition and facilitation in plants belonging to the same community.
+The manuscript text is currently organised in the IMRaD structure, but, for future versions, we are more than happy to reformat it and adjust its length to comply with the journal requirements.
 

### 2019-06-23 paper/cover-letter.Rnw
Edit draft info and cover letter for submission to Nature Communications

@@
 }
-\date{June 14, 2019}
+\date{June 23, 2019}
 %-----------------------------------------------------------------------------%
@@
     Editorial Office,\\
-    Nature Ecology \& Evolution
+    Nature Communications
 }
@@
 
-We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Nature Ecology \& Evolution}.
+We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Nature Communications}.
+We previously submitted this manuscript to Nature Ecology \& Evolution and Dr Abel Barral suggested Nature Communications as a more appropriate venue for the publication of our results.
 The main goal of this study is to explore the balance between competition and facilitation in plants belonging to the same community.
@@
 In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
-Thus, we believe that this manuscript will be interesting to the broad readership of Nature Ecology \& Evolution.
+Some lessons might also be applicable to other complex systems where facilitation and competition might be at odds and global socio-economic networks of countries and companies.
+Thus, we believe that this manuscript will be interesting to the broad readership of Nature Communications.
 

### 2019-06-23 paper/draft-info.Rmd
Edit draft info and cover letter for submission to Nature Communications

@@
 title: "Draft information"
-subtitle: "version: draft-7.2"
-date: "2019-06-14"
+subtitle: "version: draft-7.3"
+date: "2019-06-23"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
@@
 
-* Adjusted cover letter to submit to Nature Ecology and Evolution
+* Adjusted cover letter to submit to Nature Communications

### 2019-07-04 paper/manuscript.Rmd
Specify NEE content type
Minimum proceedings B format structure

@@
 
-**Short title:** Competition for pollination vs. facilitation
+<!-- **Short title:** Competition for pollination vs. facilitation -->
 
-<!-- **Keywords:** `r keywords` -->
-
-<!-- **Type of article:** Primary research article -->
+**Content type:** Research article.
 
@@
 
-**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.
+<!-- **Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes. -->
 
@@
 
-**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication.
+<!-- **Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. -->
 
@@
 
-**Competing interests:** The authors have declared that no competing interests exist.
+<!-- **Competing interests:** The authors have declared that no competing interests exist. -->
 
@@
 `r paste(drake::readd(abstract), collapse = "")`
+
+**Keywords:** `r keywords`
 
@@
 
+# Funding
+
 # References

### 2019-07-04 paper/manuscript.Rmd
Split funding from awknoledgements

@@
 
+Fieldwork was supported by grants PICT 08–12504 and 0851. 
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship and a New Zealand International Doctoral Research Scholarship administered by New Zealand Education. 
+DBS and JMT acknowledge the support of Rutherford Discovery Fellowships (RDF-13-UOC-003 and RDF-UOC-1002) and the Marsden Fund Council (UOC-1705), administered by the Royal Society of New Zealand Te Apārangi.
+
 # References

### 2019-07-04 paper/cover-letter.Rnw
Reformat cover letter to fit in two pages
Update Cover Letter for Proceedings B

--- 2019-06-17 paper/cover-letter.Rnw
@@
 \usepackage{setspace}
-\geometry{textwidth=31em, textheight=46\baselineskip}
+\geometry{textwidth=32em, textheight=47\baselineskip}
 % Name of sender
@@
 }
-\date{June 14, 2019}
+\date{July 5, 2019}
 %-----------------------------------------------------------------------------%
@@
     Editorial Office,\\
-    Nature Ecology \& Evolution
+    Proceedings of the Royal Society B
 }
@@
 
-We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Nature Ecology \& Evolution}.
+We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Proceedings B}.
 The main goal of this study is to explore the balance between competition and facilitation in plants belonging to the same community.
-The manuscript text is currently organised in the IMRaD structure, but, for future versions, we are more than happy to reformat it and adjust its length to comply with the journal requirements.
 
@@
 In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
-Thus, we believe that this manuscript will be interesting to the broad readership of Nature Ecology \& Evolution.
+Some lessons might also be applicable to other biological complex systems where facilitation and competition might be at odds like plant-frugivore and plant-fungus interactions.
+Thus, we believe that this manuscript will be interesting to the broad readership of Proceedings B.
 

### 2019-07-04 paper/draft-info.Rmd
Update draft info

@@
 title: "Draft information"
-subtitle: "version: draft-7.3"
-date: "2019-06-23"
+subtitle: "version: draft-7.4"
+date: "2019-07-05"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
@@
 
-* Adjusted cover letter to submit to Nature Communications
+* Adjusted cover letter and minimum format requirements to submit to Proceedings B

### 2019-07-04 paper/manuscript.Rmd
Remove old unnecessary comments

@@
 Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region\R{justification-traits}.
-<!-- We used those traits because they were the only ones available. <!--.. (TODO: Add a better justification for the traits used)--> 
-<!-- DBS: I bet we can get away with submitting without justifying the traits. -->
 More details can be found in Marrero *et al.* (2014 and 2017).

### 2019-07-04 main.R

@@ -65,9 +65,6 @@ imputation_plan <- drake_plan(
 
 # Basic analyses ----------------------------------------------------------
 
-# TODO: Check that the missing plants with deposition are fine
-# TODO: Impute the community values with a fit from the global values?
-
 basic_analyses_plan <- drake_plan(
   consp_self = model_conspecific_self(dep_frame),
   significant_gain_global = mann_withney_part_df(

### 2019-07-05 paper/manuscript.Rmd
Updating citation style

@@
 bibliography: bibliography.bib
-csl: nature.csl
+csl: proceedings-of-the-royal-society-b.csl
 output: #word_document

### 2019-07-05 paper/manuscript.Rmd
Short title even shorter
Updated data accesibility

@@
 
-<!-- **Short title:** Competition for pollination vs. facilitation -->
+<!-- **Short title:** Competition/facilitation in pollination -->
 
@@
 
-<!-- **Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. -->
+<!-- **Data accessibility:** All data and code necessary to reproduce the results has been included in the Electronic Supplementary Materials and will be publicly available in appropriate databases upon acceptance..
+-->
 

### 2019-08-16 paper/drafts-and-revisions/2019-07-05/review-response-notes.md
Some notes on how to address the reviews

# Review response notes

Each section represents a major issue that needs to be addressed in the manuscript

## Heterospecific-conspecific slope and competition/facilitation

The fact that a negative slope might indicate competition and a posititve slope between conspecific and heterospecific pollen indicate facilitation is probably the most contentious point of both reviews and the editor. 
Comments indicate issues related to the assumptions, methods, and conclusions. 
The reference to Tur et al. 2016, where this method was proposed was not enough to counter the reviewer's concerns.

**Way forward:** Given the amount and range of the critisism and that there is not many ways to address it, I think the best approach is to remove this section altogether. It might require a change on the paper focus from less competition/facilitation to a more pollen loads at the community level paper.

## Pollen deposition and Male-female fitness

The main critisism is that heterospecific pollen loads in the stigmas may not be detrimental to female fitness in some species. For the male fitness, pollen found in a species might not indicate losses to male fitness of another species. 
This is all true, but we can argue that heterospecific pollen deposition and conspecific pollen loss is neutral at best. 
Might not be bad for some species but doesn't help reproduction in any way.

**Way forward:** Emphasise non-positive effects. Removing first hypothesis from the paper might help here as well. Discuss that weakness of sharing pollinator effect might be due to this.

## Self pollen loads

Associate editor mentions that self-pollen might be as detrimental as heterospecific pollen and there is no way to distinguish self-pollen from other conspecific pollen.

**Way forward:** Put self-pollination back into the modelling framework

## Confounding 'evolutionary specialization' and 'functional originality'

Not sure what is meant by the reviewer here. Other than functional originality is dependent on the community while evolutionary specialization is intrinsic. Problem is lines 81-84.

**Way forward:** Unsure. Reduce the emphasis on community or remove from intro.

## Chosen traits

Reviewer states that traits should be properly justified. Specifically commented that life-history traits are not relevant in the context of pollination as that are subject to a different set of selective pressures.

**Way forward:** Remove traits or use phylogeny instead. Phylogeny might not solve the main issue though as it encompasses an even broader set of selective pressures.

## Niche flexibility test

Reviewer states that this hypothesis is best tested

## Study sites

## Species description

## Model specification

## Discussion claims

### 2019-08-16 paper/drafts-and-revisions/2019-07-05/review-response-notes.md
Add extra items to response notes

@@
 
-Each section represents a major issue that needs to be addressed in the manuscript
+Each section represents a significant issue that we need to address in the manuscript.
 
@@
 
-The fact that a negative slope might indicate competition and a posititve slope between conspecific and heterospecific pollen indicate facilitation is probably the most contentious point of both reviews and the editor.
+The fact that a negative slope might indicate competition and a positive slope between conspecific and heterospecific pollen indicate facilitation is probably the most contentious point of both reviews and the editor.
 Comments indicate issues related to the assumptions, methods, and conclusions. 
-The reference to Tur et al. 2016, where this method was proposed was not enough to counter the reviewer's concerns.
+The reference to Tur et al. 2016, where this method was first proposed was not enough to counter the reviewer's concerns.
 
-**Way forward:** Given the amount and range of the critisism and that there is not many ways to address it, I think the best approach is to remove this section altogether.
-It might require a change on the paper focus from less competition/facilitation to a more pollen loads at the community level paper.
+**Way forward:** Given the amount and range of the criticism and that there are not many ways to address it, I think the best approach is to remove this section altogether.
+It might require a change on the paper focus from less competition/facilitation to more pollen loads at the community level paper.
 
@@
 
-The main critisism is that heterospecific pollen loads in the stigmas may not be detrimental to female fitness in some species.
+The main criticism is that heterospecific pollen loads in the stigmas may not be detrimental to female fitness in some species.
 For the male fitness, pollen found in a species might not indicate losses to male fitness of another species.
-This is all true, but we can argue that heterospecific pollen deposition and conspecific pollen loss is neutral at best. 
+These observations are all true, but we can argue that heterospecific pollen deposition and conspecific pollen loss is neutral at best. 
 Might not be bad for some species but doesn't help reproduction in any way.
 
-**Way forward:** Emphasise non-positive effects. Removing first hypothesis from the paper might help here as well. Discuss that weakness of sharing pollinator effect might be due to this.
+**Way forward:** Emphasise non-positive effects. Removing the first hypothesis from the paper might help here as well. Discuss that weakness of sharing pollinator effect might be due to this.
 
@@
 
-Associate editor mentions that self-pollen might be as detrimental as heterospecific pollen and there is no way to distinguish self-pollen from other conspecific pollen.
+The associate editor mentions that self-pollen might be as detrimental as heterospecific pollen and there is no way to distinguish self-pollen from other conspecific pollen.
 
@@
 
-**Way forward:** Unsure. Reduce the emphasis on community or remove from intro.
+**Way forward:** Unsure. Reduce the emphasis on community or remove from the intro.
 
@@
 
-Reviewer states that traits should be properly justified.
+The reviewer states that traits should be adequately justified.
 Specifically commented that life-history traits are not relevant in the context of pollination as that are subject to a different set of selective pressures.
 
-**Way forward:** Remove traits or use phylogeny instead. Phylogeny might not solve the main issue though as it encompasses an even broader set of selective pressures.
+**Way forward:** Remove traits or use phylogeny instead. Phylogeny might not solve the main issue though, as it encompasses an even broader set of selective pressures.
 
@@
 
-Reviewer states that this hypothesis is best tested
+The reviewer states that we can test this hypothesis better by comparing variation within communities vs.
+across communities.
+That comment is weird cause our variables are established at the community level and hence there is no within community variability in our dataset.
+
+**Way forward:** Cannot think of anything to do here, except try to explain the methods better?
 
@@
 
+The reviewer asks for more info about study sites. He remarks on why we didn't take into account the difference between agricultural and restored sites.
+
+**Way forward:** Include more info about the whole methods, even though it is published. Perhaps we should put this in the supporting info so that the paper doesn't get too long?
+
 ## Species description
+
+The reviewer asks for more information about the study plans, abundances, etc.
 
@@
 
+The reviewer suggests modelling ratio conspecific and heterospecific directly. Not sure about this, though.
+
+**Way forward:** This seemed to be a minor complain though. Might get away with the same model? Another possibility is to use a single model for the whole thing
+
 ## Discussion claims
+
+The reviewer suggests many of claims in the discussion are unsubstantiated.
+
+**Way forward:** Just more nuance in the discussion. I think the reviewer had a pretty negative approach by then and was being a bit nitpicky.

### 2019-08-16 paper/drafts-and-revisions/2019-07-05/review-response-notes.md
Add way forward for other minor stuff

@@
 
+**Way forward:** Just add that info in the supporting information
+
 ## Model specification
@@
 
-**Way forward:** Just more nuance in the discussion. I think the reviewer had a pretty negative approach by then and was being a bit nitpicky.
+**Way forward:** Just more nuance in the discussion and be more explicit about study limitations.
+I think the reviewer had a pretty negative mindset towards the paper by then and was being a bit nitpicky.
+
+## Other issues
+
+We can address most other issues can be easily addressed with some wording changes to improve clarity.

### 2019-11-22 paper/manuscript.Rmd
First paragraph intro

@@
 Animal pollination plays a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
+At a pairwise level, pollination is underpinned by a delicate balance between the mutualistic relationship between plants and pollinators. 
+At a community level, sometimes involving hundreds of species, both plant and pollinator species are connected in a myriad of indirect connections when pollination partners are shared. 
+These indirect connections can dramatically alter the quality of the pollination service that plants receive because they determine how conspecific and heterospecific pollen is transferend across the community.
+However, due to the large number of factors that operate at the community level, we do not understand how sharing pollinators affects the pollination service beyond systems with more than a handful of species.
+Here we investigate how pollinator sharing affects pollen transfer *in natural communities* and how it compares to other factors known to play a role in community dynamics like abundance, traits, and visitation patterns.
+
 Alongside the direct benefits of mutualisms between plants and their pollinators, biodiversity can be supported as a result of inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008; @liao_presence_2011].

### 2019-11-22 paper/manuscript.Rmd
Second paragraph intro

@@
 
+There are two main mechanisms through which sharing pollinators can affect plant fertilization [@morales_interspecific_2008]. 
+The first is by changes in intraspecific pollen transfer.
+This happens, for example, when plants with more attractive flowers might reduce the number of visits to those less of attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
+The second is via interspecific pollen transfer. 
+In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
+Naturally, the precise effects on female or male plant fitness of conspecific and heterospecific pollen deposition depend on the species involved (and are unknown for many plant species). 
+However, even for species well adapted to pollinator sharing, receiving foreign pollen on stigmas or loosing pollen to foreign stigmas, is neutral at best. 
+Indeed, there is substantial evidence supporting the idea that heterospecific pollen deposition can be detrimental to seed production and plant fitness [@ashman_toward_2013; @arceo-gomez_invasion_2016].
+
 Alongside the direct benefits of mutualisms between plants and their pollinators, biodiversity can be supported as a result of inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008; @liao_presence_2011].
@@
 
-There are two main mechanisms through which competition for pollinators can affect plant fertilization [@morales_interspecific_2008]. 
-The first is by changes in intraspecific pollen transfer.
-This happens, for example, when plants with more attractive flowers might reduce the number of visits to those less of attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
-The second is via interspecific pollen transfer and occurs when plants share pollination partners. 
-In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
-\R{start-deposition-facil-competition}Naturally, the precise effects on plant fitness of conspecific and heterospecific pollen deposition depend on the species involved (and are unknown for many plant species).
-However, there is substantial evidence supporting the link between pollen deposition and seed production; in particular for the detrimental effect of heterospecific pollen deposition on plant fitness [@ashman_toward_2013; @arceo-gomez_invasion_2016].
 All together, provided pollen is viable and compatible [@ramsey_pollen_2000; @de_jong_plant_1992; @dafni_pollen_2000], the higher the quantity of conspecific pollen and its purity (relative to heterospecific pollen), the better the pollination service received by the focal plant.

### 2019-11-22 paper/manuscript.Rmd
All paragraphs of introduction

@@
 
-Alongside the direct benefits of mutualisms between plants and their pollinators, biodiversity can be supported as a result of inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008; @liao_presence_2011].
-This inter-species facilitation is able to promote species coexistence by offsetting the effects of direct resource competition [@stachowicz_mutualism_2001]. 
-Indeed, studies at the core of our current theoretical knowledge of mutualisms predict that the maximum number of coexisting species is achieved when the number of shared mutualistic partners is maximised in a community [@bastolla_architecture_2009].
-
-However, in natural communities, plants rarely share all available pollinators. 
-One explanation is that plants are effectively competing for mutualistic partners because there is a trade-off between the benefits gained from maximising the number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
-It has been clear for a long time that when competition for pollination is strong enough, these costs can make pollination detrimental to plants' fitness [shown both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970].
-In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000]. 
-However, it is less clear how exactly this ecological differentiation may, in turn, favour (or hinder) the pollination service.
-
 All together, provided pollen is viable and compatible [@ramsey_pollen_2000; @de_jong_plant_1992; @dafni_pollen_2000], the higher the quantity of conspecific pollen and its purity (relative to heterospecific pollen), the better the pollination service received by the focal plant.
@@
 
-By definition, these two mechanisms of competition, intra and interspecific pollen transfer, occur at the community scale.
-However, with few exceptions [@tur_evaluating_2016; @aizen_reproductive_2010], most of what we know about them and their relationship with key ecological factors is based on studies with two plant species\R{end-deposition-facil-competition}.
+By definition, intra and interspecific pollen transfer, occur at the community scale.
+However, with few exceptions [@tur_evaluating_2016; @aizen_reproductive_2010], most of what we know about them and their relationship with key ecological factors is based on studies with two plant species.
 That is partly so because, at the community scale, the factors that determine the patterns of pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
 For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016].
+
 This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly [@thebault_does_2008; @bascompte_asymmetric_2006; @vazquez_species_2007].
@@
 Alternatively, it might also be the case that abundance (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
-Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987; @feldman_when_2004] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators<!-- cite Savert et al.
-2019 here once it has a doi-->.
+Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987; @feldman_when_2004] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators [@stavert_plant_2019].
 In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount of conspecific pollen relative to heterospecific pollen.
 Altogether, it is clear that these ecological factors can indeed shape pollen deposition at the community level. 
-However, their relative importance and how exactly they can minimise competition for pollination—or equivalently, maximise facilitation—in plant populations (across species and communities) has not been determined.
+However, their relative importance and **the trade-offs** that exist between them has not been determined.
 
-Here, we investigate the balance between competition for pollination and facilitation at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
-First, we estimate the extent to which the net outcome of plants sharing pollinators is facilitation or competition. 
-If facilitation is the primary outcome, we could expect an overall positive relationship between the amount of conspecific pollen deposited in stigmas and the amount of heterospecific pollen [@tur_evaluating_2016].
-The higher the deposition of conspecific pollen relative to heterospecific, the larger the slope of this relationship.
-<!-- On the other, we could expect a larger amount of conspecific pollen deposited on stigmas when flowers are open to animal pollinators than what is deposited due to self-pollination.  -->
-Second, we investigate the relative contribution that four ecological factors have to the pollination service. 
-Specifically, we hypothesize that the quantity and purity of conspecific pollen deposition should decrease for plants that share many pollination partners. 
-However, we also hypothesize that other factors like the plant's functional originality, its relative floral abundance, and the visit potential should have the potential to compensate for this increase in competition.
-Third and finally, we examine how much the community context influences the way plants use these factors to minimise competition/maximise facilitation. 
-We use these four ecological factors as a proxy of the realised pollination niche of a plant species in their community.
-Although some plant species might be widespread across multiple locations, competition for pollinators occurs at the community level and hence we predict that pollination niche will be influenced by the local context.
-If plant strategy is not flexible across the communities in our study\R{ref-plant-flexibility}, we could expect niches to be more similar within species than across species. 
-On the contrary, if a species' strategy is flexible, we should expect plants to be able to occupy different niches in each community such that intraspecific competition could ultimately be minimised regardless of the context.
+Here, we investigate pollen transfer dynamics at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
+First, we investigate the relative contribution that four ecological factors have to the pollination service. 
+Specifically, we hypothesize that there are trade offs on how these factors affect quantity and purity of conspecific pollen deposition. 
+While quantity and putity should decrease for plants that share many pollination partners, other factors like the plant's functional originality, its relative floral abundance, and its visitation patterns should have the potential to compensate for this decreasse
+Second, once we understand how these factors operate across species, we examine wether species show similar patterns in these four factors across the different communities where they are present. 
+Because these factors may affect the pollination service in contrasting ways, and a species role is relative to other species in the community, we predict that species present in multiple communities should be flexible enough to compete for pollinators under different community contexts.
+
+<!-- Alongside the direct benefits of mutualisms between plants and their pollinators, biodiversity can be supported as a result of inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008; @liao_presence_2011].
+-->
+<!-- This inter-species facilitation is able to promote species coexistence by offsetting the effects of direct resource competition [@stachowicz_mutualism_2001].  -->
+<!-- Indeed, studies at the core of our current theoretical knowledge of mutualisms predict that the maximum number of coexisting species is achieved when the number of shared mutualistic partners is maximised in a community [@bastolla_architecture_2009].
+-->
+
+<!-- However, in natural communities, plants rarely share all available pollinators.  -->
+<!-- One explanation is that plants are effectively competing for mutualistic partners because there is a trade-off between the benefits gained from maximising the number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
+-->
+<!-- It has been clear for a long time that when competition for pollination is strong enough, these costs can make pollination detrimental to plants' fitness [shown both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970].
+-->
+<!-- In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000].
+-->
+<!-- However, it is less clear how exactly this ecological differentiation may, in turn, favour (or hinder) the pollination service. -->
 

### 2019-11-22 paper/manuscript.Rmd
Improve spelling of introduction

@@
 Animal pollination plays a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
-At a pairwise level, pollination is underpinned by a delicate balance between the mutualistic relationship between plants and pollinators. 
+At a pairwise level, the mutually beneficial relationship between plants and pollinators underpins pollination. 
 At a community level, sometimes involving hundreds of species, both plant and pollinator species are connected in a myriad of indirect connections when pollination partners are shared. 
-These indirect connections can dramatically alter the quality of the pollination service that plants receive because they determine how conspecific and heterospecific pollen is transferend across the community.
-However, due to the large number of factors that operate at the community level, we do not understand how sharing pollinators affects the pollination service beyond systems with more than a handful of species.
+These indirect connections can dramatically alter the quality of the pollination service that plants receive because they determine how conspecific and heterospecific pollen is transferred across the community.
+However, due to the large number of factors that operate at the community level, we do not understand how sharing pollinators affect the pollination service beyond systems with more than a handful of species.
 Here we investigate how pollinator sharing affects pollen transfer *in natural communities* and how it compares to other factors known to play a role in community dynamics like abundance, traits, and visitation patterns.
 
-There are two main mechanisms through which sharing pollinators can affect plant fertilization [@morales_interspecific_2008]. 
+There are two main mechanisms through which sharing pollinators can affect plant fertilisation [@morales_interspecific_2008]. 
 The first is by changes in intraspecific pollen transfer.
-This happens, for example, when plants with more attractive flowers might reduce the number of visits to those less of attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
+Interspecific pollen transfer happens, for example, when plants with more attractive flowers might reduce the number of visits to those less of attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
 The second is via interspecific pollen transfer. 
-In that case, even receiving a visit might not necessarily translate into fertilization [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
+In that case, even receiving a visit might not necessarily translate into fertilisation [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
 Naturally, the precise effects on female or male plant fitness of conspecific and heterospecific pollen deposition depend on the species involved (and are unknown for many plant species). 
-However, even for species well adapted to pollinator sharing, receiving foreign pollen on stigmas or loosing pollen to foreign stigmas, is neutral at best. 
+However, even for species well adapted to pollinator sharing, receiving foreign pollen on stigmas or losing pollen to foreign stigmas, is neutral at best. 
 Indeed, there is substantial evidence supporting the idea that heterospecific pollen deposition can be detrimental to seed production and plant fitness [@ashman_toward_2013; @arceo-gomez_invasion_2016].
@@
 
-By definition, intra and interspecific pollen transfer, occur at the community scale.
-However, with few exceptions [@tur_evaluating_2016; @aizen_reproductive_2010], most of what we know about them and their relationship with key ecological factors is based on studies with two plant species.
+By definition, intra- and interspecific pollen transfer, occur at the community scale.
+However, with few exceptions [@tur_evaluating_2016; @aizen_reproductive_2010], most of what we know about pollen transfer and its relationship with key ecological factors are based on studies with two plant species.
 That is partly so because, at the community scale, the factors that determine the patterns of pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
@@
 
-This evidence is aligned with the notion that a species that interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly [@thebault_does_2008; @bascompte_asymmetric_2006; @vazquez_species_2007].
+This evidence aligns with the notion that a species that interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly [@thebault_does_2008; @bascompte_asymmetric_2006; @vazquez_species_2007].
 If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012; @carvalheiro_potential_2014].
-Alternatively, it might also be the case that abundance (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
+Alternatively, it might also be the case that abundance (for example, in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
 Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987; @feldman_when_2004] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators [@stavert_plant_2019].
@@
 Altogether, it is clear that these ecological factors can indeed shape pollen deposition at the community level. 
-However, their relative importance and **the trade-offs** that exist between them has not been determined.
+However, we still do not understand their relative importance and **the trade-offs** that might exist between them.
 
@@
 First, we investigate the relative contribution that four ecological factors have to the pollination service. 
-Specifically, we hypothesize that there are trade offs on how these factors affect quantity and purity of conspecific pollen deposition. 
-While quantity and putity should decrease for plants that share many pollination partners, other factors like the plant's functional originality, its relative floral abundance, and its visitation patterns should have the potential to compensate for this decreasse
-Second, once we understand how these factors operate across species, we examine wether species show similar patterns in these four factors across the different communities where they are present. 
+Specifically, we hypothesise that there are trade-offs on how these factors affect the quantity and purity of conspecific pollen deposition. 
+While quantity and purity should decrease for plants that share many pollination partners, other factors like the plant's functional originality, its relative floral abundance, and its visitation patterns should have the potential to compensate for this decrease
+Second, once we understand how these factors operate across species, we examine whether species show similar patterns in these four factors across the different communities where they are present. 
 Because these factors may affect the pollination service in contrasting ways, and a species role is relative to other species in the community, we predict that species present in multiple communities should be flexible enough to compete for pollinators under different community contexts.

### 2019-11-23 paper/manuscript.Rmd
Remove competition/facilitation from the methods

@@
 We collected data from eleven co-flowering plant communities and their pollinators in three locations in the Argentinian Pampas. 
-<!-- These locations are distributed across a precipitation gradient with the humid temperate climate of the eastern Flooding Pampas becoming drier as one moves inland and westward towards the Pampean Grasslands.
--->
-<!-- This precipitation gradient generated a natural gradient of network architecture which allowed us to examine the generality of our findings. -->
-<!-- DBS: "Natural gradient" of network architecture seems purposefully vague. -->
 In each location, we sampled two restored and two agricultural fragments, except in one located in the Flooding Pampas, where we were only able to sample one restored fragment due to the lack of available sites.
 
-## Competition vs. facilitation
+## Factors affecting quantity and purity of pollination service
 
-Our first objective was to identify whether the net outcome of plants sharing pollinators at the community level is facilitation or competition. 
-<!-- We use two complementary lines of evidence.   -->
-To do that  we examine <!-- first can be found via --> the relationship between heterospecific and conspecific pollen deposited in plant stigmas [@tur_evaluating_2016]. 
-This is because heterospecific pollen can be seen as an unavoidable cost that plants must pay for receiving conspecific pollen from shared pollinators. 
-A negative relationship (when shared pollinators increase heterospecific pollen loads and decrease conspecific loads) may indicate that competition for pollination is strong.
-In contrast, a positive relationship is what would be observed when facilitation is the dominant outcome.
-
-<!-- The second line of evidence can be obtained by examining the difference between the amount of conspecific pollen deposited in flower stigmas *with* and *without* animal-mediated pollination.  -->
-<!-- Self-pollination can be favourable to plant reproduction when competition for pollination is strong because it provides insurance against poor pollination service [@kalisz_benefits_2003].  -->
-<!-- If competition for pollination is sufficiently strong, then the amount of conspecific pollen deposited in flower stigmas when animal pollination is prevented should be higher than when animal pollination is allowed.
--->
-<!-- In contrast, the opposite pattern may indicate that plants benefit from having pollen delivered directly to the stigma by animals.  -->
+Our first objective was to investigate the relative contribution that different ecological factors have on pollen transfer. 
+Generally speaking, we expect that any factor that increases the amount of conspecific pollen deposited in stigmas, both in quantity and purity relative to heterospecific pollen, also has a positive effect on the pollination service.
+Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit potential---a metric that combines the amount and type of pollen carried by floral visitors and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010].
+See *Data Analysis* section below for more details on these four factors.
 
@@
 In each of the selected plants, we removed all flowers leaving only buds that were expected to go into florescence on the next day. 
-<!-- Approximately a quarter of these buds were bagged to prevent animal pollination.  -->
 Two days after flowering, we collected all remaining flowers and counted the number of conspecific and heterospecific pollen grains in their pistils. 
 More details can be found in @marrero_agricultural_2016.
-
-### Data analysis
-
-To evaluate the relationship between heterospecific and conspecific pollen, we used a generalised linear mixed model (GLMM) with a Poisson error distribution [following @tur_evaluating_2016]. 
-In this model, the number of conspecific pollen grains per flower was the response variable and the number of heterospecific grains the predictor variable (the log number of stigmas sampled was added as an offset term).
-The slope and intercept of this relationship were allowed to differ between populations (plant species \(\times\) community), which were modelled as a random effect. 
-Models were fitted using the function `glmer` from the R package `lme4 1.1-19` [@bates_fitting_2015]. 
-A positive slope for a plant population indicates facilitation while a negative slope competition [@tur_evaluating_2016].
-
-<!-- To compare the conspecific pollen deposited with and without animal-mediated pollination, we followed the same approach as above.  -->
-<!-- In this case, however, the predictor variable was the treatment (whether the flower was bagged or unbagged) instead of the number of heterospecific grains.  -->
-
-## Factors affecting quantity and purity of pollination service
-
-Our second objective was to investigate the relative contribution that different ecological factors have on the mechanisms of pollinator-mediated competition. 
-Generally speaking,
-we expect that any factor that increases the amount of conspecific pollen deposited in stigmas, both in quantity and purity relative to heterospecific pollen, also has a positive effect on the pollination service.
-<!-- DBS: There is no use to calling it something succinct like purity if we always have to say "purity relative to heterospecific pollen"...  -->
-<!-- FDO: Only mention purity relative to heterospecific pollen cause it's first time it gets mentioned in the methods  -->
-Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit potential---a metric that combines the amount and type of pollen carried by floral visitors and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010].
-See *Data Analysis* section below for more details on these four factors. 
-<!-- Here, we define visit effectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
--->
-
-### Data collection
 
@@
 Specifically, we calculated the number of shared pollinators for each plant species by pooling data from the qualitative and quantitative pollination networks. 
-<!-- This variable is strongly correlated to the number of animal species a plant interacts with (the species degree).  -->
 To calculate the plants' relative floral abundance in their community, we aggregated floral counts for each species. 
@@
 Finally, functional originality is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016].
-<!-- As phenology has been shown to be a key mechanism of niche differentiation among plants, we also  -->
 To include phenological variation, we treated floral abundance in each of the survey months (November to March) as a "trait" in our analysis. 
-<!-- This approach allowed us to integrate the originality in phenological niche alongside the originality on other functional traits.  -->
 To account for the non-independence of floral counts and weight all traits equally, we assigned a weight of 1/5 to these abundances (one for each month). 
@@
 As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our factors proportionally to the likelihood of their candidate model.
-<!-- We "shrank" the estimated coefficient of potentially unimportant variables by setting their estimate to 0 when the variable was not included in the model.  -->
 Finally, we used these distributions of the model coefficients to estimate their mean impact on the pollination service (in terms of quantity and purity of conspecific pollen deposition).
-<!-- Again, here we used bootstrap resampling to estimate the uncertainty around these means.  -->
-<!-- DBS: This is a great example where we use 'purity' on its own. -->
 
@@
 
-Our last objective was to tease apart the plant strategies that might reduce competition and, importantly, how the community context influences these strategies.
-<!-- DBS: Thinking out loud here, but are the strategies for reducing competition or for increasing facilitation/mutualism?  -->
+Our second objective was to tease apart the plant strategies that might reduce competition and, importantly, how the community context influences these strategies.
 If community context plays a relatively small role or the species strategy is inflexible, we would expect plants of the same species to fill similar pollination niches across different communities. 

### 2019-11-23 paper/manuscript.Rmd
Add smth about the trade-offs in the first paragraph of the intro

@@
 At a community level, sometimes involving hundreds of species, both plant and pollinator species are connected in a myriad of indirect connections when pollination partners are shared. 
-These indirect connections can dramatically alter the quality of the pollination service that plants receive because they determine how conspecific and heterospecific pollen is transferred across the community.
+These indirect connections can dramatically alter the quality of the pollination service that plants receive because they determine how conspecific and heterospecific pollen is transferred across the community [@morales_interspecific_2008].
+Generally speaking, there is a trade-off between the benefits gained from maximising the number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
 However, due to the large number of factors that operate at the community level, we do not understand how sharing pollinators affect the pollination service beyond systems with more than a handful of species.

### 2019-11-23 paper/manuscript.Rmd
Remove uncessesary comments

@@
 Because these factors may affect the pollination service in contrasting ways, and a species role is relative to other species in the community, we predict that species present in multiple communities should be flexible enough to compete for pollinators under different community contexts.
-
-<!-- Alongside the direct benefits of mutualisms between plants and their pollinators, biodiversity can be supported as a result of inter-species "facilitation"—the indirect positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008; @liao_presence_2011].
--->
-<!-- This inter-species facilitation is able to promote species coexistence by offsetting the effects of direct resource competition [@stachowicz_mutualism_2001].  -->
-<!-- Indeed, studies at the core of our current theoretical knowledge of mutualisms predict that the maximum number of coexisting species is achieved when the number of shared mutualistic partners is maximised in a community [@bastolla_architecture_2009].
--->
-
-<!-- However, in natural communities, plants rarely share all available pollinators.  -->
-<!-- One explanation is that plants are effectively competing for mutualistic partners because there is a trade-off between the benefits gained from maximising the number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
--->
-<!-- It has been clear for a long time that when competition for pollination is strong enough, these costs can make pollination detrimental to plants' fitness [shown both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970].
--->
-<!-- In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000].
--->
-<!-- However, it is less clear how exactly this ecological differentiation may, in turn, favour (or hinder) the pollination service. -->
 

### 2019-11-23 paper/manuscript.Rmd
Improve spiel in methods to avoid referring to competition/.facilitation

@@
 
-Here, we investigate pollen transfer dynamics at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
+Here, we investigate pollen deposition dynamics at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
 First, we investigate the relative contribution that four ecological factors have to the pollination service. 
@@
 While quantity and purity should decrease for plants that share many pollination partners, other factors like the plant's functional originality, its relative floral abundance, and its visitation patterns should have the potential to compensate for this decrease
-Second, once we understand how these factors operate across species, we examine whether species show similar patterns in these four factors across the different communities where they are present. 
+Second, we examine how these four factors that might affect pollen deposition can change across communities where species are present. 
 Because these factors may affect the pollination service in contrasting ways, and a species role is relative to other species in the community, we predict that species present in multiple communities should be flexible enough to compete for pollinators under different community contexts.
@@
 
-Our first objective was to investigate the relative contribution that different ecological factors have on pollen transfer. 
+Our first objective was to investigate the relative contribution that different ecological factors have on pollen deposition. 
 Generally speaking, we expect that any factor that increases the amount of conspecific pollen deposited in stigmas, both in quantity and purity relative to heterospecific pollen, also has a positive effect on the pollination service.
@@
 When the pollen count was above 2,000 grains, we classified approximately 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
-Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region\R{justification-traits}.
+Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region.
 More details can be found in Marrero *et al.* (2014 and 2017).
@@
 
-Our second objective was to tease apart the plant strategies that might reduce competition and, importantly, how the community context influences these strategies.
-If community context plays a relatively small role or the species strategy is inflexible, we would expect plants of the same species to fill similar pollination niches across different communities. 
-Alternatively, if the community plays a large role and/or plant strategies are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
+Our second objective was to tease apart whether and how these factors that might affect pollen deposition might change across communities species are present.
+If community context plays a relatively small role, or alternatively, species are inflexible in regards of these factors, we would expect plants of the same species to fill similar pollination niches across different communities.
+Alternatively, if the community plays a large role and plant species are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
 To test this, we first used a principal component analysis (PCA) of the four ecological factors (number of shared pollinators, floral abundance, visit potential, and trait originality). 

### 2019-11-23 paper/manuscript.Rmd
Remove competition section from the results :( It was a nice graph...

@@
 # Results
-
-## Competition vs. facilitation
-
-```{r facilitation-random-model-stats, echo = F}
-drake::loadd(facilitation_plot_df)
-
-# count number of species with positive and negative slopes
-counts_facilitation_slope <- facilitation_plot_df %>%
-  dplyr::group_by(effect_category) %>%
-  dplyr::count() %>%
-  dplyr::group_by() %>%
-  dplyr::mutate(np = nn/sum(nn), 
-                np = round_preserve_sum(np, 2)*100)
-
-# species with both positive and negative relationships
-get_sp_with_both_pos_neg <- . %>%
-  dplyr::filter(effect_category != "neutral") %>%
-  dplyr::group_by(plant_name) %>%
-  dplyr::summarise(both = dplyr::n_distinct(effect_category) > 1) %>%
-  dplyr::filter(both)
-
-# Get list of species with both positive and negative slopes
-sp_both_pos_neg <- facilitation_plot_df %>%
-  get_sp_with_both_pos_neg() %>%
-  dplyr::mutate(plant_name = as.character(plant_name)) %>%
-  dplyr::arrange(plant_name) %>%
-  dplyr::mutate(plant_name = stringr::str_extract(plant_name,
-                                                  "[A-Z]\\w+\\s[a-z]\\w+"), 
-                plant_label = paste0("*", plant_name, "*")) 
-# Human readable list of species with both positive and negative slopes
-sp_both_pos_neg_names <- sp_both_pos_neg %$%
-  glue::collapse(plant_label, sep = ", ", last = ", and ")
-
-# equal number of negative and positive?
-equal_pos_neg <- counts_facilitation_slope$nn[1] == counts_facilitation_slope$nn[3]
-```
-
-We first examined the degree of facilitation/competition in natural communities. 
-Specifically, we examined the slope of the relationship between the quantities of heterospecific and conspecific pollen deposited on stigmas of each species in a community. 
-Overall, we found that neither net facilitation nor net competition dominates (Table \@ref(S-tab:table-facilitation-models-general)). 
-Indeed, we found that the proportions of species that experienced a statistically significant positive or negative relationship between heterospecific and conspecific pollen were very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Fig.
-\@ref(fig:fig-trade-off-predictions); Table \@ref(S-tab:table-facilitation-models-random)).
-Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
-For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that the same species, can experience facilitation (positive relationships) in some communities and competition (negative relationships) in others.
-Interestingly, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Fig.
-\@ref(S-fig:fig-conspecific-heterospecific)).
-
-```{r fig-trade-off-predictions, fig.height= 4, out.height="4in", fig.width = 3.57, out.width="3.57in", out.extra="center", fig.cap = "Competition vs.
-facilitation at the community level.
-Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in each of their communities.
-Statistically significant negative slopes (darkest shade) indicate that plants experience net competition for animal-mediated pollination, while significantly positive slopes (lightest shade) indicate that net facilitation is the predominant outcome.
-The number of plants analysed for each species is shown within brackets next to the species name.
-Error bars correspond to $\\pm$ the standard error (SE)."}
-# fig_random_slopes <- plot_random_slopes(facilitation_plot_df)
-# pdf(width = 3.57, height = 4)
-drake::loadd(fig_random_slopes)
-  fig_random_slopes[[1]]
-# dev.off()
-```
-
-```{r facilitation-conspecific-stats}
-drake::loadd(con_con_plot_df)
-# overall counts of possitive/negative
-sp_con_con <- con_con_plot_df %>%
-  dplyr::group_by(effect_category) %>%
-  dplyr::count() %>%
-  dplyr::group_by() %>%
-  dplyr::mutate(np = n/sum(n), 
-                np = round_preserve_sum(np, 2)*100)
-# species with contrasting behaviours
-sp_con_both_pos_neg <- con_con_plot_df %>%
-  get_sp_with_both_pos_neg() %>%
-  dplyr::arrange(plant_name) %>%
-  dplyr::mutate(plant_label = dplyr::if_else(plant_name %in% sp_both_pos_neg$plant_name, shorten_sp_name(plant_name), plant_name),
-                plant_label = paste0("*", plant_label, "*"))
-```
-
-<!-- Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with that of those that were closed.  -->
-<!-- Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers (Table \@ref(S-tab:table-open-bagged-models-general)).  -->
-<!-- Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had less pollen when open (the difference was statistically non-significant for the remaining `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Fig.
-\@ref(fig:fig-trade-off-predictions)c; Table \@ref(S-tab:table-open-bagged-models-random)).
--->
-<!-- Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both positive and negative differences.
--->
 

### 2019-11-23 paper/manuscript.Rmd
Remove competition/niche lingo from results

@@
 We then examined the potential roles played in pollen deposition by four ecological factors (number of shared pollinators, abundance, mean visit potential, and functional originality). 
-<!-- Together these variables can describe the niche that plants might occupy in the context of competition for pollination.  -->
 We found that our models of pollen deposition had high explanatory power (the coefficient of determination R^2^ ranged between `r min(r2_values$r2c_min)` and `r max(r2_values$r2c_max)`) although a large portion of the explanatory power came from the random effects (Table \@ref(S-tab:table-R2)).
@@
 Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).
-<!-- DBS: Two-sentence paragraphs are universally frowned upon. -->
 
@@
 ```
-We used a PCA of the analysed species to investigate whether plants' realised pollination niche is similar across communities or whether they are flexible and therefore a reflection of the community context.
+
+We used a PCA of the ecological factors--species matrix to investigate whether plants' "strategy" towards pollen deposition is similar across communities or whether they are flexible and therefore a reflection of the community context.
 The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Fig. \@ref(fig:fig-pca)a). 
@@
 \@ref(fig:fig-pca)c).
-<!-- DBS: Are we consistent with UK vs US spellings? Does Ecology Letters prefer UK spelling? -->
-
 ```{r fig-pca, fig.width=3.57, fig.height=6.65, out.width="3.57in", out.height="6.65in",  out.extra="center", fig.cap="The flexibility of plant strategies.

### 2019-11-24 paper/manuscript.Rmd
Improve front page

@@
 
-**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text (including Methods section).
+**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.
 
-<!-- **Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes. -->
+**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.
 
-<!-- **Number of references:** `r n_references` -->
+**Number of references:** `r n_references`
 
@@
 
-<!-- **Data accessibility:** All data and code necessary to reproduce the results has been included in the Electronic Supplementary Materials and will be publicly available in appropriate databases upon acceptance..
--->
+**Data accessibility:** All data and code necessary to reproduce the results has been included in the Electronic Supplementary Materials and will be publicly available in appropriate databases upon acceptance.
 
-<!-- **Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.  -->
+**Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.
 
-<!-- **Competing interests:** The authors have declared that no competing interests exist. -->
+**Competing interests:** The authors have declared that no competing interests exist.
 

### 2019-11-24 paper/manuscript.Rmd
Redo first paragraph discussiojn

@@
 
-Our results suggest that community context plays a central role in determining the net cost or benefit of sharing pollinators.
-<!-- DBS: In the intro, it's about net outcome. Here, it's about net cost or benefit. Which is it? -->
-First, we found that pollinator sharing can lead to both net facilitative and net competitive effects to plant species in a community. 
-Second, we found that multiple ecological factors can modulate the intensity of competition; however, conspecific and heterospecific pollen deposition are tightly coupled and this creates a clear trade-off between the quantity and purity of pollination [@thomson_effects_2019].
-Third, we found that the way these factors influence competition is strongly shaped by the community context. 
-That is, if these factors collectively define a species' pollination niche,
-<!-- DBS: Yet another way to phrase this concept... -->
-the same plant species can occupy dramatically different niches depending on the community to which it belongs.
+Our results suggest that community context plays a central role in determining the pollen deposition dynamics and ultimately the net cost or benefit of sharing pollinators.
+First, we found that multiple ecological factors can modulate the quality of the pollination service; however, conspecific and heterospecific pollen deposition are tightly coupled and this creates a clear trade-off between the quantity and purity of pollination [@thomson_effects_2019].
+Second, we found that the way these factors shape pollen deposition for a species could be dramatically different across communities. 
+For instance, while in a particular community a plant species could show high levels of pollinator sharing and relatively low trait differentiation, the same species in another community can have relatively high trait differentiation and low levels of pollinator sharing.
+Our findings highlight that trade-offs can at least partially explain the coexistence of facilitative and competitive effects of animal-mediated pollination in the pollination service--both the short and the long term.
 
-The criterion we used to identify the effect of animal-mediated pollination suggested that neither facilitation nor competition are dominant in pollination communities.
-A previous study showed that, in diverse pollination communities, sharing pollinators does not necessarily translate to net competition [@tur_evaluating_2016]. 
-The overall extent of facilitation/competition of pollination communities can depend on factors like the adversity of the environment [@tur_evaluating_2016; @callaway_positive_2002] or how disturbances affect pollinator populations [@stavert_exotic_2017].
-However, why some species experience more competition than others was not understood. 
-Although we were unable to measure the fitness outcomes, here we show that the coexistence of facilitative and competitive effects of animal-mediated pollination can be at least partially explained by trade-offs in the pollination service--both the short and the long term.
-These trade-offs arise when plants simultaneously maximise the deposition of conspecific pollen and minimise that of heterospecific pollen.
-
+The trade-offs involved in attaining high-quality pollination service (and more broadly between facilitation and competition) are likely to arise when plants simultaneously maximise the deposition of conspecific pollen and minimise that of heterospecific pollen.
 In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, not only due to costs to male fitness [@muchhala_interspecific_2012; @morales_interspecific_2008], but also because, as we show here, sharing pollinators reduces both the quantity and purity of the conspecific pollen deposited.
@@
 First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators [@reverte_pollinators_2016]. 
-Second, the negative relationship between originality and generalism  [@carvalheiro_potential_2014] has been shown to depend on plant abundance [@coux_linking_2016], with generalist species being able to also have original traits only when they are abundant enough to provide a valuable reward to make visiting worthwhile to pollinators.
+Second, the negative relationship between originality and generalism  [@carvalheiro_potential_2014] has been shown to depend on plant abundance [@coux_linking_2016], with generalist species being able also to have original traits only when they are abundant enough to provide a valuable reward to make visiting worthwhile to pollinators.
 

### 2019-11-24 paper/manuscript.Rmd
Minor changes discussion

@@
 Our second objective was to tease apart whether and how these factors that might affect pollen deposition might change across communities species are present.
-If community context plays a relatively small role, or alternatively, species are inflexible in regards of these factors, we would expect plants of the same species to fill similar pollination niches across different communities.
-Alternatively, if the community plays a large role and plant species are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
+If community context plays a relatively small role, or species are inflexible in regards to these factors, we would expect plants of the same species to fill similar pollination niches across different communities.
+Alternatively, if the community plays a significant role and plant species are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
 To test this, we first used a principal component analysis (PCA) of the four ecological factors (number of shared pollinators, floral abundance, visit potential, and trait originality). 
@@
 However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
-This indicates that, although there is a positive association between visit potential and the quantity of pollen deposition, there is a negative relationship with its purity (Fig.
+This larger effect indicates that, although there is a positive association between visit potential and the quantity of pollen deposition, there is a negative relationship with its purity (Fig.
 \@ref(fig:fig-average-qual-quant)c).
@@
 Specifically, most plant species appear to be flexible enough to adopt markedly different niches in different communities. 
-<!-- Although there are many exceptions, some plant families (Asteraceae for example) are often generalists in their communities while others (Orchidaceae) are known to be more commonly specialised [@johnson_generalization_2000].
--->
-<!-- DBS: I'd cut the sentence above. -->
 From an evolutionary perspective, our results suggest that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history.
 Furthermore, from a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
-<!-- DBS: Below, we do the 'on the one hand', 'on the other (hand)' dance for the third or fourth time. We should change some of them to spice things up. -->
 On the one hand, our results suggest that introduced plants that increase the relative originality of natives (e.g. through distinct phenology) might have positive effects [@gibson_can_2012]. 

### 2019-11-24 paper/manuscript.Rmd
Rewrite conclusion paragraph

@@
 
-Overall, pollination communities might not necessarily be the paradigmatic mutualistic communities we often believe. 
-Instead, we confirm that plant competition is pervasive in pollination communities. 
-The potential strategies to minimise competition are likely to involve strong trade-offs in the pollination service both in the short and long-term. 
+Overall, using empirical data on pollen deposition, we show that at the community level sharing pollinators has a smaller effect on pollen deposition than what we expected based on experimental studies with a handful species.
+Other factors that underpin community dynamics (abundance, traits, visitation) also influence patterns of pollination quantity and purity. 
+The interrelatedness of these factors and the flexibility of species to position themselves within these factors means that their contributions to the quality of the pollination service should not and cannot be understood in isolation.
+All factors we analysed involve substantial trade-offs in pollen deposition in the short and likely also in the longer term. 
+These trade-offs emphasise the competitive nature of pollination. 
+However, many of the widely used theoretical models of plant-pollinator communities do not account for the adverse effects of sharing pollinators [but see @rohr_structural_2014 and similar]. 
+We propose that achieving a better understanding of species coexistence and how pollination support plant biodiversity will require seeing them as both mutualistic and competitive communities [@johnson_coexistence_2019].
+
+<!-- theprotagonist pollen deposition is  widely held that competition for pollination is pervasive in pollination communities.  -->
+<!-- The potential strategies to minimise competition are likely to involve strong trade-offs in the pollination service both in the short and long-term.  -->
 <!-- Specifically, although not sharing pollinators and being functionally unique reduces competition for pollination by increasing the quantity and purity of conspecific pollen deposition.  --> 
@@
 <!-- Interestingly, these two factors also involve the largest trade-offs between increasing deposition of conspecific pollen and reducing that of heterospecific pollen.  -->
-Most remarkably, despite large differences in the quantity and purity of conspecific pollen deposition among species, our results provide solid evidence that competition for pollination is inherently a community process and the same species can occupy different niches in different communities.
+<!-- Most remarkably, despite large differences in the quantity and purity of conspecific pollen deposition among species, our results provide solid evidence that competition for pollination is inherently a community process and the same species can occupy different niches in different communities.
+-->
 <!-- Overall, species coexistence is not solely determined by direct and indirect mutualistic relationships, but also strongly shaped by the multiple intertwined ecological factors that shape competition for pollination at the community level.
 -->
-Many of the widely used theoretical models of plant-pollinator communities do not account for the negative effects of sharing pollinators [but see @rohr_structural_2014 and similar]\R{theoretical-models}.
-However, achieving a better understanding of species coexistence and how plant biodiversity is supported by pollination communities will require seeing them as both mutualistic and competitive communities [@johnson_coexistence_2019].
-
-<!-- DBS: If we're really looking for a paragraph to cut, we can cut this last one in its entirety. -->
-
-<!-- ESC: hi fernando. i'm edine. i'm here with my papa. have a nice day!!!!!! -->
 

### 2019-11-24 paper/manuscript.Rmd
Join funding with awknowledgements

@@
 
-# Funding
-
-Fieldwork was supported by grants PICT 08–12504 and 0851. 
-EFC acknowledges the support from the University of Canterbury Doctoral Scholarship and a New Zealand International Doctoral Research Scholarship administered by New Zealand Education. 
-DBS and JMT acknowledge the support of Rutherford Discovery Fellowships (RDF-13-UOC-003 and RDF-UOC-1002) and the Marsden Fund Council (UOC-1705), administered by the Royal Society of New Zealand Te Apārangi.
-
 # References

### 2019-11-24 paper/manuscript.Rmd
Minor wording changes

@@
 To account for the non-independence of floral counts and weight all traits equally, we assigned a weight of 1/5 to these abundances (one for each month). 
-We scaled all traits prior to calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
+We scaled all traits before calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
 Finally, we scaled all four factors to have a zero mean and unitary variance.

### 2019-11-24 paper/manuscript.Rmd
Minor changes to front matter

@@
 
-**Content type:** Research article.
+<!-- **Content type:** Research article. -->
 
@@
 
-**Data accessibility:** All data and code necessary to reproduce the results has been included in the Electronic Supplementary Materials and will be publicly available in appropriate databases upon acceptance.
+<!-- **Data accessibility:** All data and code necessary to reproduce the results has been included in the Electronic Supplementary Materials and will be publicly available in appropriate databases upon acceptance.
+-->
 
@@
 Animal pollination plays a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
-At a pairwise level, the mutually beneficial relationship between plants and pollinators underpins pollination. 
+At a pairwise level, the mutually beneficial relationship between plants and pollinators underpins the pollination service. 
 At a community level, sometimes involving hundreds of species, both plant and pollinator species are connected in a myriad of indirect connections when pollination partners are shared. 

### 2019-11-24 paper/draft-info.Rmd
Update draft info to include readme upgrade
Update draft info

--- 2019-06-23 paper/draft-info.Rmd
@@
 title: "Draft information"
-subtitle: "version: draft-7.3"
-date: "2019-06-23"
+subtitle: "version: draft-8.0"
+date: "2019-11-24"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
@@
 
+## Requests to co-authors
+
+* Title suggestions/feedback?
+* Feedback primarly on abstract, introduction and discussion prior to submission.
+
 ## Changes since the last draft
 
-* Adjusted cover letter to submit to Nature Communications
+* Adjusted langage away from competition for pollination towards pollination service and pollen deposition across the paper.
+* Removed the section where we calculated competition/facilitation in ecological communities
+* Other minor adjustments to address comments by reviews received when submitted to Proceedings B
+* Rewrote abstract
+* Updated title

### 2019-11-24 paper/cover-letter.Rnw
Just add word pollination to first sentence cover letter
Reduce margin coverletter
Formatting for Ecology

@@
 \usepackage{setspace}
-\geometry{textwidth=32em, textheight=47\baselineskip}
+\geometry{textwidth=30em, textheight=47\baselineskip}
 % Name of sender
@@
     Editorial Office,\\
-    Proceedings of the Royal Society B
+    Ecology
 }
@@
 
-We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Proceedings B}.
-The main goal of this study is to explore the balance between competition and facilitation in plants belonging to the same community.
+We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Ecology}.
+The main goal of this study is to explore the balance between competition and facilitation in plants belonging to the same pollination community.
 

### 2019-11-24 paper/manuscript.Rmd
Update title
Formatting for Ecology

--- 2019-11-24 paper/manuscript.Rmd
@@
 ---
-title: "Community context determines competition vs. facilitation trade-offs in pollination systems"
+title: "The trade-offs of pollinator sharing: pollination service is determined by the community context"
 author: 
@@
 bibliography: bibliography.bib
-csl: proceedings-of-the-royal-society-b.csl
+csl: ecology.csl
 output: #word_document
@@
 toc: false
-fontsize: 11pt
-classoption: a4paper
-geometry: 
-  - textwidth=33em
-  - textheight=48\baselineskip
+fontsize: 12pt
+# classoption: a4paper
+# geometry: 
+  # - textwidth=33em
+  # - textheight=48\baselineskip
 header-includes:
@@
   - \usepackage[export]{adjustbox}
-  # - \usepackage[nomarkers]{endfloat}
+  - \usepackage{endfloat}
 ---

### 2019-11-24 paper/supp-info.Rmd
Formatting for Ecology

--- 2019-06-06 paper/supp-info.Rmd
@@
 # bibliography: references.bib
-csl: plos-biology.csl
+csl: nature.csl
 documentclass: book
+# classoption: a4paper
 nocite: | 

### 2019-11-28 paper/manuscript.Rmd
Update title
Minor edits to the introduction

@@
 ---
-title: "The trade-offs of pollinator sharing: pollination service is determined by the community context"
+title: "The trade-offs of sharing pollinators: pollination service is determined by the community context"
 author: 
@@
 These indirect connections can dramatically alter the quality of the pollination service that plants receive because they determine how conspecific and heterospecific pollen is transferred across the community [@morales_interspecific_2008].
-Generally speaking, there is a trade-off between the benefits gained from maximising the number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
-However, due to the large number of factors that operate at the community level, we do not understand how sharing pollinators affect the pollination service beyond systems with more than a handful of species.
+Generally speaking, there is a trade-off between the benefits gained from a species maximising its number of partners and the costs of sharing them with other plant species [@waser_interspecific_1978].
+However, due to the large number of factors that operate at the community level, we generally do not know how sharing pollinators affects the pollination service beyond systems with more than a handful of species.
 Here we investigate how pollinator sharing affects pollen transfer *in natural communities* and how it compares to other factors known to play a role in community dynamics like abundance, traits, and visitation patterns.
@@
 The first is by changes in intraspecific pollen transfer.
-Interspecific pollen transfer happens, for example, when plants with more attractive flowers might reduce the number of visits to those less of attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
+Changes in intraspecific pollen transfer happen, for example, when plants with more attractive flowers might reduce the number of visits to those less attractive neighbouring plants, and hence reduce the amount of *conspecific pollen* deposited by animals [@yang_pollinator_2011].
 The second is via interspecific pollen transfer. 
 In that case, even receiving a visit might not necessarily translate into fertilisation [@campbell_mechanism_1985] because a focal plant might receive *heterospecific pollen* or because pollen from the focal plant might be lost to different species.
-Naturally, the precise effects on female or male plant fitness of conspecific and heterospecific pollen deposition depend on the species involved (and are unknown for many plant species). 
-However, even for species well adapted to pollinator sharing, receiving foreign pollen on stigmas or losing pollen to foreign stigmas, is neutral at best. 
+Naturally, the precise effects on female or male plant fitness of conspecific and heterospecific pollen deposition depend on the species involved [@arceo-gomez_invasion_2016] and are unknown for many plant species.
+
+Even for species well adapted to pollinator sharing, receiving foreign pollen on stigmas or losing pollen to foreign stigmas is neutral (at best). 
 Indeed, there is substantial evidence supporting the idea that heterospecific pollen deposition can be detrimental to seed production and plant fitness [@ashman_toward_2013; @arceo-gomez_invasion_2016].
-
-All together, provided pollen is viable and compatible [@ramsey_pollen_2000; @de_jong_plant_1992; @dafni_pollen_2000], the higher the quantity of conspecific pollen and its purity (relative to heterospecific pollen), the better the pollination service received by the focal plant.
+All else being equal, provided pollen is viable and compatible [@ramsey_pollen_2000; @de_jong_plant_1992; @dafni_pollen_2000], the higher the quantity of conspecific pollen and its purity (relative to heterospecific pollen), the better the pollination service received by the focal plant.
 As such, measuring conspecific and heterospecific pollen deposition provides a good indication of the potential levels of facilitation and competition a plant population might experience.
 
-By definition, intra- and interspecific pollen transfer, occur at the community scale.
+By definition, intra- and interspecific pollen transfer occur at the community scale.
 However, with few exceptions [@tur_evaluating_2016; @aizen_reproductive_2010], most of what we know about pollen transfer and its relationship with key ecological factors are based on studies with two plant species.
-That is partly so because, at the community scale, the factors that determine the patterns of pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
+That is partly so because the factors that determine the patterns of pollen deposition at the community scale are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011].
 For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016].
@@
 Altogether, it is clear that these ecological factors can indeed shape pollen deposition at the community level. 
-However, we still do not understand their relative importance and **the trade-offs** that might exist between them.
+However, we still do not understand their relative importance and *the trade-offs* that might exist between them.
 
-Here, we investigate pollen deposition dynamics at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
-First, we investigate the relative contribution that four ecological factors have to the pollination service. 
+Here, we investigate pollen-deposition dynamics at the community scale using empirical data from eleven plant-pollinator communities in the Argentinian Pampas. 
+First, we investigate the relative contribution that four ecological factors make to the pollination service. 
 Specifically, we hypothesise that there are trade-offs on how these factors affect the quantity and purity of conspecific pollen deposition. 

### 2019-11-28 paper/manuscript.Rmd
Edits to the methods

@@
 As fixed predictors in the models, we included the four ecological factors described above. 
-Specifically, we calculated the number of shared pollinators for each plant species by pooling data from the qualitative and quantitative pollination networks. 
+Specifically, we calculated the number of shared pollinator species for each plant species by pooling data from the qualitative and quantitative pollination networks. 
 To calculate the plants' relative floral abundance in their community, we aggregated floral counts for each species. 
-We then calculated the mean visit potential of pollinator species *i* to plant species *j* as \[o_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j}\], where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
+We then calculated the mean visit potential of pollinator species *i* to plant species *j* as \[o_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j},\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
 We log-transformed the number of shared pollinators, floral abundance, and visit potential before including them in the model.
@@
 Finally, functional originality is defined as the distance of a species from the community trait average--the centroid of functional space of the community [@laliberte_distance-based_2010; @coux_linking_2016].
-To include phenological variation, we treated floral abundance in each of the survey months (November to March) as a "trait" in our analysis. 
+To include phenological variation, we treated floral abundance in each of the survey months (November to March) as a "trait" in this analysis. 
 To account for the non-independence of floral counts and weight all traits equally, we assigned a weight of 1/5 to these abundances (one for each month). 
 We scaled all traits before calculating the centroid of the functional space and calculated the species-specific functional coordinates using the R package `FD 1.0-12` [@laliberte_fd_2014]. 
-Finally, we scaled all four factors to have a zero mean and unitary variance.
+Finally, we scaled all four factors to have a zero mean and unit variance.
 
 To estimate the coefficients, perform model selection, and quantify the associated uncertainty, we used a combination of multi-model inference and bootstrap resampling with 99 replicates. 
-First, we performed model selection using the AICc and determined the likelihood of each candidate model (a particular combination of predictors) by calculating the median \(\Delta\)AICc (relative to the most likely model) for each bootstrap sample.
+Using bootstrap replicates allow us to better understand the uncertainties associated with our estimations. 
+First, we performed model selection using AICc and determined the likelihood of each candidate model (a particular combination of predictors) by calculating the median \(\Delta\)AICc (relative to the most likely model) for each bootstrap sample.
 As we wanted model coefficients from more likely candidate models to carry more weight in our results, we sampled the coefficients for our factors proportionally to the likelihood of their candidate model.
@@
 Our second objective was to tease apart whether and how these factors that might affect pollen deposition might change across communities species are present.
-If community context plays a relatively small role, or species are inflexible in regards to these factors, we would expect plants of the same species to fill similar pollination niches across different communities.
-Alternatively, if the community plays a significant role and plant species are flexible, we should be able to observe differences in the realised niche a plant species occupies across communities. 
+If community context plays a relatively small role, or species are inflexible in regards to these factors, we would expect plants of the same species to fill similar "pollination niches" across different communities.
+Alternatively, if the community plays a significant role and plant species are flexible, we should be able to observe differences in the pollination niche a plant species occupies across communities. 
 To test this, we first used a principal component analysis (PCA) of the four ecological factors (number of shared pollinators, floral abundance, visit potential, and trait originality). 
 We scaled factors across the whole study to ensure that the PCA space does not change according to the species present in each community. 
-We define a species' niche in a community as its coordinates in PCA space. 
-For each species that was present in two or more communities, we then calculated (*i*) the median distance between the strategies that the species uses in different communities and (*ii*) the area of the convex hull defined by these points in the first two principal components (only for species present in three or more communities).
+We define a species' pollination niche in a community as its coordinates in PCA space. 
+For each species that was present in two or more communities, we then calculated (*i*) the median distance between the points that correspond to the niches species occupies in different communities and (*ii*) the area of the convex hull defined by these points in the first two principal components (only for species present in three or more communities).
 We then compared the magnitude of these two metrics to those obtained with 99 Monte Carlo randomizations in which we replaced the strategy of the focal plant species by that of another randomly selected species in the dataset.

### 2019-11-28 paper/manuscript.Rmd
Edits to the results

@@
 
-We then examined the potential roles played in pollen deposition by four ecological factors (number of shared pollinators, abundance, mean visit potential, and functional originality). 
+We first examined the potential roles played in pollen deposition by four ecological factors (number of shared pollinators, abundance, mean visit potential, and functional originality). 
 We found that our models of pollen deposition had high explanatory power (the coefficient of determination R^2^ ranged between `r min(r2_values$r2c_min)` and `r max(r2_values$r2c_max)`) although a large portion of the explanatory power came from the random effects (Table \@ref(S-tab:table-R2)).
-As determined by AICc, the random structure best supported by the data was the one that fit an intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community to which they belong).
+As determined by AICc, the random structure best supported by the data was the one that fit a separate intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community to which they belong).
 This structure was best for both the models of conspecific and heterospecific pollen (Table \@ref(S-tab:table-aic-random-models)).
@@
 We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
-That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
+That is, strategies that were associated with an increase in conspecific pollen deposition were also associated with an increase in heterospecific pollen deposition. 
 Specifically, the plants' mean visit potential had a positive effect on pollen deposition (Fig. \@ref(fig:fig-average-qual-quant)b). 
@@
 
-We used a PCA of the ecological factors--species matrix to investigate whether plants' "strategy" towards pollen deposition is similar across communities or whether they are flexible and therefore a reflection of the community context.
+We used a PCA of the ecological factors--species matrix to investigate whether plants' strategies towards pollen deposition is similar across communities or whether they are flexible and therefore a reflection of the community context.
 The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Fig. \@ref(fig:fig-pca)a). 

### 2019-11-28 paper/manuscript.Rmd
Edits to discussion

@@
 Second, we found that the way these factors shape pollen deposition for a species could be dramatically different across communities. 
-For instance, while in a particular community a plant species could show high levels of pollinator sharing and relatively low trait differentiation, the same species in another community can have relatively high trait differentiation and low levels of pollinator sharing.
-Our findings highlight that trade-offs can at least partially explain the coexistence of facilitative and competitive effects of animal-mediated pollination in the pollination service--both the short and the long term.
+For instance, while a plant species in a particular community could show high levels of pollinator sharing and relatively low trait differentiation, the same species in another community can have relatively high trait differentiation and low levels of pollinator sharing.
+Our findings highlight that trade-offs can at least partially explain the coexistence of facilitative and competitive effects of animal-mediated pollination in the pollination service.
 
 The trade-offs involved in attaining high-quality pollination service (and more broadly between facilitation and competition) are likely to arise when plants simultaneously maximise the deposition of conspecific pollen and minimise that of heterospecific pollen.
-In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable, not only due to costs to male fitness [@muchhala_interspecific_2012; @morales_interspecific_2008], but also because, as we show here, sharing pollinators reduces both the quantity and purity of the conspecific pollen deposited.
+In the short term, being a specialist and sharing no pollinators might reduce competition [@muchhala_competition_2010] and hence be preferable. 
+This may be due to both costs to male fitness [@muchhala_interspecific_2012; @morales_interspecific_2008], and also, as we show here, because sharing pollinators reduces both the quantity and purity of the conspecific pollen deposited.
 However, over long periods of time, there could be a risk associated with a specialist plant having few pollinators [@ricketts_tropical_2004]. 
@@
 First, in a mutualism context, it is also possible that trait originality could come at the cost of being less ‘apparent’ to pollinators [@reverte_pollinators_2016]. 
-Second, the negative relationship between originality and generalism  [@carvalheiro_potential_2014] has been shown to depend on plant abundance [@coux_linking_2016], with generalist species being able also to have original traits only when they are abundant enough to provide a valuable reward to make visiting worthwhile to pollinators.
+Second, the negative relationship between originality and generalism  [@carvalheiro_potential_2014] has been shown to depend on plant abundance [@coux_linking_2016], with generalist species being able to have original traits only when they are also abundant enough to provide a valuable reward to make visiting worthwhile to pollinators.
 
@@
 Our results corroborate the importance that two-species studies have ascribed to visitation and abundance [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008], 
-but they also suggest that [because visitation, pollen production and abundance are usually correlated; @sargent_role_2006] balancing the pros and cons of sharing pollinators at the community level is not trivial and might even be partially responsible for the diversity of plant-pollinator communities [@benadi_frequency_2018].
+but they also suggest that [because visitation, pollen production and abundance are usually correlated; @sargent_role_2006] balancing the pros and cons of sharing pollinators at the community level is not trivial.
+The fact that no species can easily outcompete others for pollination might be partially responsible for the diversity of plant-pollinator communities [@benadi_frequency_2018].
 
 We observed, as expected, that the effects of pollen deposition can vary widely among species. 
-For instance, while the fitness of some plant species can be hurt even by low amounts of heterospecific pollen, for others, fitness can instead be limited by the amount of conspecific pollen [@campbell_mechanism_1985; @arceo-gomez_interactive_2019].
+For instance, the fitness of some plant species can be hurt even by low amounts of heterospecific pollen, while the fitness of others can instead be limited by the amount of conspecific pollen [@campbell_mechanism_1985; @arceo-gomez_interactive_2019].
 Alternatively, plant species can also differ substantially in the extent to which self- vs. outcross-pollen differ in their value for fertilization. 
@@
 Furthermore, from a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
-On the one hand, our results suggest that introduced plants that increase the relative originality of natives (e.g. through distinct phenology) might have positive effects [@gibson_can_2012]. 
+On the one hand, our results suggest that plants that increase the relative originality of natives (e.g. through distinct phenology) might have positive effects [@gibson_can_2012]. 
 On the other, because different niches can lead to different outcomes across communities, our results also highlight the difficulties involved in predicting whether the introduced plant species will facilitate or compete with neighbours [@bartomeus_contrasting_2008].
@@
 
-Overall, using empirical data on pollen deposition, we show that at the community level sharing pollinators has a smaller effect on pollen deposition than what we expected based on experimental studies with a handful species.
+Overall, using empirical data on pollen deposition, we show at the community level that sharing pollinators has a smaller effect on pollen deposition than what we expected based on experimental studies with a handful species.
 Other factors that underpin community dynamics (abundance, traits, visitation) also influence patterns of pollination quantity and purity. 
-The interrelatedness of these factors and the flexibility of species to position themselves within these factors means that their contributions to the quality of the pollination service should not and cannot be understood in isolation.
-All factors we analysed involve substantial trade-offs in pollen deposition in the short and likely also in the longer term. 
-These trade-offs emphasise the competitive nature of pollination. 
+The interrelatedness of these factors, and the flexibility of species to position themselves across them, means that their contributions to the quality of the pollination service cannot be understood in isolation.
+All of the factors we analysed involve substantial trade-offs in pollen deposition in the short and likely also in the long term. 
+These trade-offs emphasise the inherently competitive nature of pollination. 
 However, many of the widely used theoretical models of plant-pollinator communities do not account for the adverse effects of sharing pollinators [but see @rohr_structural_2014 and similar]. 
-We propose that achieving a better understanding of species coexistence and how pollination support plant biodiversity will require seeing them as both mutualistic and competitive communities [@johnson_coexistence_2019].
-
-<!-- theprotagonist pollen deposition is  widely held that competition for pollination is pervasive in pollination communities.  -->
-<!-- The potential strategies to minimise competition are likely to involve strong trade-offs in the pollination service both in the short and long-term.  -->
-<!-- Specifically, although not sharing pollinators and being functionally unique reduces competition for pollination by increasing the quantity and purity of conspecific pollen deposition.  --> 
-<!-- Remarkably, this increase is surprisingly small when compared to the effect of relative abundance and visitation.  -->
-<!-- Interestingly, these two factors also involve the largest trade-offs between increasing deposition of conspecific pollen and reducing that of heterospecific pollen.  -->
-<!-- Most remarkably, despite large differences in the quantity and purity of conspecific pollen deposition among species, our results provide solid evidence that competition for pollination is inherently a community process and the same species can occupy different niches in different communities.
--->
-<!-- Overall, species coexistence is not solely determined by direct and indirect mutualistic relationships, but also strongly shaped by the multiple intertwined ecological factors that shape competition for pollination at the community level.
--->
+We therefore propose that achieving a better understanding of species coexistence and how pollination supports plant biodiversity will require seeing them as both mutualistic and competitive communities [@johnson_coexistence_2019].
 

### 2019-11-28 paper/manuscript.Rmd
Stop using niche and stick to strategy throughout

@@
 Our second objective was to tease apart whether and how these factors that might affect pollen deposition might change across communities species are present.
-If community context plays a relatively small role, or species are inflexible in regards to these factors, we would expect plants of the same species to fill similar "pollination niches" across different communities.
-Alternatively, if the community plays a significant role and plant species are flexible, we should be able to observe differences in the pollination niche a plant species occupies across communities. 
+If community context plays a relatively small role, or species are inflexible in regards to these factors, we would expect plants of the same species to use similar "strategies" across different communities.
+Alternatively, if the community plays a significant role and plant species are flexible, we should be able to observe differences in the strategy a plant species uses across communities. 
 To test this, we first used a principal component analysis (PCA) of the four ecological factors (number of shared pollinators, floral abundance, visit potential, and trait originality). 
 We scaled factors across the whole study to ensure that the PCA space does not change according to the species present in each community. 
-We define a species' pollination niche in a community as its coordinates in PCA space. 
-For each species that was present in two or more communities, we then calculated (*i*) the median distance between the points that correspond to the niches species occupies in different communities and (*ii*) the area of the convex hull defined by these points in the first two principal components (only for species present in three or more communities).
+We define a species' strategy in a community as its coordinates in PCA space. 
+For each species that was present in two or more communities, we then calculated (*i*) the median distance between the points that correspond to the strategy a species uses in different communities and (*ii*) the area of the convex hull defined by these points in the first two principal components (only for species present in three or more communities).
 We then compared the magnitude of these two metrics to those obtained with 99 Monte Carlo randomizations in which we replaced the strategy of the focal plant species by that of another randomly selected species in the dataset.
@@
 The graph shows the relative importance calculated as the sum of the Akaike weights of the candidate models that included the selected factor.
-(b) The association between ecological factors and heterospecific pollen tended to align with their association with conspecific pollen.
+(b) The association between ecological factors and heterospecific pollen (lighter line) tended to align with their association with conspecific pollen (darker line).
 Visit potential and functional originality had a positive association with pollen deposition, while floral abundance and the number of shared pollinators had a negative association.
@@
 When we locate the species that were sampled in more than one community in the first two PCA components (Fig.
-\@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other.
+\@ref(fig:fig-pca)b), we observe that the positions of any given species do not tend to be close to each other.
 Indeed, when we measured the median distance between the plants' coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` species analysed (Fig.
@@
 (a) The two first components explain a large proportion of the total variance.
-(b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points, which represent the strategy (the particular combination of ecological factors) of that species in its community, do not seem to be grouped by plant species.
+(b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points—which represent the strategy (the particular combination of ecological factors) of that species in its community—do not seem to be grouped by plant species.
 (c) This was confirmed using Monte Carlo randomizations of the median distance between strategies of a plant species.
@@
 Importantly, we show here that the balances between costs and benefits are determined not only by species identity but also by the community to which plants belong. 
-Specifically, most plant species appear to be flexible enough to adopt markedly different niches in different communities. 
+Specifically, most plant species appear to be flexible enough to adopt markedly different "strategies" in different communities. 
 From an evolutionary perspective, our results suggest that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history.
@@
 On the one hand, our results suggest that plants that increase the relative originality of natives (e.g. through distinct phenology) might have positive effects [@gibson_can_2012]. 
-On the other, because different niches can lead to different outcomes across communities, our results also highlight the difficulties involved in predicting whether the introduced plant species will facilitate or compete with neighbours [@bartomeus_contrasting_2008].
+On the other, because different strategies can lead to different outcomes across communities, our results also highlight the difficulties involved in predicting whether the introduced plant species will facilitate or compete with neighbours [@bartomeus_contrasting_2008].
 Other factors that we were unable to measure (e.g.

### 2019-11-28 paper/draft-info.Rmd
Formatting for Ecology
Update draft info

@@
 title: "Draft information"
-subtitle: "version: draft-8.0"
+subtitle: "version: draft-8.1"
 date: "2019-11-24"
@@
 
-## Changes since the last draft
+## Changes since the last major draft
 
@@
 * Updated title
+* Grammar, typos, and language
+
+## To-do
+
+* Update supplementary information

### 2019-11-28 paper/manuscript.Rmd
Figure captions only accept valid latex characters

@@
 (a) The two first components explain a large proportion of the total variance.
-(b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points—which represent the strategy (the particular combination of ecological factors) of that species in its community—do not seem to be grouped by plant species.
+(b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points---which represent the strategy (the particular combination of ecological factors) of that species in its community---do not seem to be grouped by plant species.
 (c) This was confirmed using Monte Carlo randomizations of the median distance between strategies of a plant species.

### 2019-11-29 paper/manuscript.Rmd
Figures at the end should not include captions

@@
   - \usepackage{endfloat}
+  - \usepackage{caption}
+  - \captionsetup{labelsep=none,textformat=empty}
+editor_options: 
+  chunk_output_type: console
 ---
@@
 \@ref(fig:fig-pca)c).
+
 ```{r fig-pca, fig.width=3.57, fig.height=6.65, out.width="3.57in", out.height="6.65in",  out.extra="center", fig.cap="The flexibility of plant strategies.

### 2019-12-04 paper/manuscript.Rmd
Format for biorxiv

--- 2019-11-28 paper/manuscript.Rmd
@@
 fontsize: 12pt
-# classoption: a4paper
+classoption: a4paper
 # geometry: 
@@
   - \usepackage[export]{adjustbox}
-  - \usepackage{endfloat}
+  # - \usepackage{endfloat}
+  - \usepackage{caption}
+  # - \captionsetup{labelsep=none,textformat=empty}
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-**Content type:** Research article.
+<!-- **Content type:** Research article. -->
 
-**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.
+<!-- **Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text. -->
 
-**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.
+<!-- **Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes. -->
 
-**Number of references:** `r n_references`
+<!-- **Number of references:** `r n_references` -->
 

### 2019-12-04 paper/supp-info.Rmd
Fix typo in figure legend supp info
Update title in supp info

@@
 ---
-title: "Community context determines competition vs. facilitation trade-offs in pollination systems"
+title: "The trade-offs of sharing pollinators: pollination service is determined by the community context"
 subtitle: "Supplementary information"
@@
 Only candidate formulas with a $\\Delta AICc < 4$ for either conspecific or heterospecific pollen are shown.
-Models candidates are arranged in decreasing order of support.
+Model candidates are arranged in decreasing order of support.
 Although relative abundance, the number of shared pollinators, and the visit potential were all positively correlated, the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables.

### 2020-02-10 paper/manuscript.Rmd
Changes to Methods

@@
 
-Our first objective was to investigate the relative contribution that different ecological factors have on pollen deposition. 
+Our first objective was to investigate the relative contribution that different ecological factors make on pollen deposition. 
 Generally speaking, we expect that any factor that increases the amount of conspecific pollen deposited in stigmas, both in quantity and purity relative to heterospecific pollen, also has a positive effect on the pollination service.
-Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit potential---a metric that combines the amount and type of pollen carried by floral visitors and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010].
+Specifically, we investigated the effect of (*i*) a plant's number of pollinator species that are shared with other plant species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit potential---a metric that combines the amount and type of pollen carried by floral visitors and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010].
 See *Data Analysis* section below for more details on these four factors.
@@
 To do this, we examined the pollen loads present on the floral visitors collected [@marrero_exotic_2017]. 
-When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level when possible and to pollen complexes when it was not. 
+When the pollen count on an individual insect was estimated to be less than 2,000 grains, we identified every grain to the species level when possible and to pollen complexes when it was not. 
 When the pollen count was above 2,000 grains, we classified approximately 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
-Finally, we also recorded morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region.
+Finally, we also recorded morphological traits for the plants in the transects that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, phenology, and whether the species is native in the study region.
 More details can be found in Marrero *et al.* (2014 and 2017).
@@
 To investigate the impact of ecological factors on pollination services, we used two sets of linear mixed models (LMM) with bootstrap resampling.
-The response variables for these model sets were the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination. 
-We used LMMs in which pollen loads were log-transformed because these models offered a better fit than equivalent GLMMs with Poisson (or quasi-Poisson) error structure. 
+The response variables for these model sets were the number of conspecific or heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination. 
+We used LMMs in which pollen loads were log-transformed because these models offered a better fit than equivalent GLMMs with Poisson error structure. 
 Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].
@@
 We then calculated the mean visit potential of pollinator species *i* to plant species *j* as \[o_{ij} = \frac{v_{ij}}{v_i} \frac{p_{ji}}{p_j},\] where *v~ij~* is the observed number of visits by *i* to *j*, *p~ji~* is the number of pollen grains from *j* attached to *i*, *v~i~* is the total number of visits performed by *i*, and *p~j~* is the total number of grains carried by *j*.
-We log-transformed the number of shared pollinators, floral abundance, and visit potential before including them in the model.
+We log-transformed the number of shared pollinators, floral abundance, and visit potential before including them in the model to improve convergence of the models.
 
@@
 
-Our second objective was to tease apart whether and how these factors that might affect pollen deposition might change across communities species are present.
+Our second objective was to tease apart whether and how these factors that might affect pollen deposition might change across communities in which the species are present.
 If community context plays a relatively small role, or species are inflexible in regards to these factors, we would expect plants of the same species to use similar "strategies" across different communities.

### 2020-02-10 paper/manuscript.Rmd
Specify that we use a One-tailed monte carlo test

@@
 For each species that was present in two or more communities, we then calculated (*i*) the median distance between the points that correspond to the strategy a species uses in different communities and (*ii*) the area of the convex hull defined by these points in the first two principal components (only for species present in three or more communities).
-We then compared the magnitude of these two metrics to those obtained with 99 Monte Carlo randomizations in which we replaced the strategy of the focal plant species by that of another randomly selected species in the dataset.
+Using a one-tailed Monte Carlo test, we then tested wether the magnitude of these two metrics was smaller to those obtained with 99 randomizations in which we replaced the strategy of the focal plant species by that of another randomly selected species in the dataset.
 

### 2020-02-10 paper/manuscript.Rmd
Changes to the Results

@@
 
-We first examined the potential roles played in pollen deposition by four ecological factors (number of shared pollinators, abundance, mean visit potential, and functional originality). 
+We examined the potential roles played in pollen deposition by four ecological factors (number of shared pollinators, abundance, mean visit potential, and functional originality). 
 We found that our models of pollen deposition had high explanatory power (the coefficient of determination R^2^ ranged between `r min(r2_values$r2c_min)` and `r max(r2_values$r2c_max)`) although a large portion of the explanatory power came from the random effects (Table \@ref(S-tab:table-R2)).

### 2020-02-10 paper/manuscript.Rmd
Removed potentially contentious statements in the discussion

@@
 
-We observed, as expected, that the effects of pollen deposition can vary widely among species. 
-For instance, the fitness of some plant species can be hurt even by low amounts of heterospecific pollen, while the fitness of others can instead be limited by the amount of conspecific pollen [@campbell_mechanism_1985; @arceo-gomez_interactive_2019].
-Alternatively, plant species can also differ substantially in the extent to which self- vs. outcross-pollen differ in their value for fertilization. 
-The difference can be particularly relevant for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy).
+<!-- We observed, as expected, that the effects of pollen deposition can vary widely among species.  -->
+<!-- For instance, the fitness of some plant species can be hurt even by low amounts of heterospecific pollen, while the fitness of others can instead be limited by the amount of conspecific pollen [@campbell_mechanism_1985; @arceo-gomez_interactive_2019].
+-->
+<!-- Alternatively, plant species can also differ substantially in the extent to which self- vs. outcross-pollen differ in their value for fertilization.  -->
+<!-- The difference can be particularly relevant for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy).
+-->
+<!-- Despite the stark differences among plants sensitivity to pollen deposition, we still detected  -->
 
@@
 From an evolutionary perspective, our results suggest that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history.
-Furthermore, from a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
+<!-- Furthermore, from a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants.  -->
 On the one hand, our results suggest that plants that increase the relative originality of natives (e.g. through distinct phenology) might have positive effects [@gibson_can_2012]. 

### 2020-02-12 paper/manuscript.Rmd
Minor edits to the discussion
Some format adjustments for submission to Ecology

@@
 fontsize: 12pt
-classoption: a4paper
-# geometry: 
-  # - textwidth=33em
-  # - textheight=48\baselineskip
+geometry:
+  - textwidth=6.5in
+  - textheight=9in
 header-includes:
@@
   # - \captionsetup{labelsep=none,textformat=empty}
+  - \usepackage{ragged2e}
 editor_options: 
@@
 
-<!-- **Short title:** Competition/facilitation in pollination -->
+**Running head:** Competition/facilitation in pollination
 
-<!-- **Content type:** Research article. -->
+<!-- **Article type:** Report. -->
 
@@
 
-**Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.
+<!-- **Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design. -->
 
@@
 **Keywords:** `r keywords`
-
-\clearpage
 
@@
 To ensure long-term survival, it is thus likely that plants also need to balance this risk with the costs of sharing pollinators [@aizen_specialization_2012].
+Among others, these risk may include the local exinction of its pollinators, a reduction of insurance or portfolio effects, and, unless plants specialise on abundant, generalist pollinators, an inability to sustain large population sizes.
 One possible solution is to share pollinators *and* have original traits---as we show that trait originality is generally beneficial to pollen deposition and it is commonly thought that species that are further from others in trait space benefit from reduced competition.

### 2020-02-12 paper/supp-info.Rmd
Some format adjustments for submission to Ecology

@@
     toc: false
+fontsize: 12pt
 header-includes:

### 2020-02-19 paper/manuscript.Rmd
Actual left aligned
Legends at the end and no markers in text

@@
   - \usepackage[export]{adjustbox}
-  # - \usepackage{endfloat}
+  - \usepackage[nomarkers]{endfloat}
   - \usepackage{caption}
-  # - \captionsetup{labelsep=none,textformat=empty}
+  - \captionsetup{labelsep=none,textformat=empty}
   - \usepackage{ragged2e}
@@
 \clearpage
+\RaggedRight
 

### 2020-02-19 paper/manuscript.Rmd
Don't separate abstract page
Include references suggested by Hugo

@@
 
-\clearpage
 \RaggedRight
@@
 All else being equal, provided pollen is viable and compatible [@ramsey_pollen_2000; @de_jong_plant_1992; @dafni_pollen_2000], the higher the quantity of conspecific pollen and its purity (relative to heterospecific pollen), the better the pollination service received by the focal plant.
-As such, measuring conspecific and heterospecific pollen deposition provides a good indication of the potential levels of facilitation and competition a plant population might experience.
+As such, despite the complex processes involved with pollen transfer [@ashman_pollen_2020], measuring conspecific and heterospecific pollen deposition provides a good indication of the potential levels of facilitation and competition a plant population might experience.
 
@@
 This evidence aligns with the notion that a species that interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly [@thebault_does_2008; @bascompte_asymmetric_2006; @vazquez_species_2007].
-If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012; @carvalheiro_potential_2014].
+If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012; @carvalheiro_potential_2014; @bergamo_pollinatormediated_2020].
 Alternatively, it might also be the case that abundance (for example, in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
-Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987; @feldman_when_2004] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators [@stavert_plant_2019].
+Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987; @feldman_when_2004; @bergamo_pollinatormediated_2020] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators [@stavert_plant_2019].
 In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount of conspecific pollen relative to heterospecific pollen.
@@
 Other factors that we were unable to measure (e.g.
-pollinator behaviour and densities or the spatial context) have also been shown to play a role in the outcome of animal-mediated pollination [@ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009; @thomson_effects_2019].
+pollinator behaviour and densities or the spatial context) have also been shown to play a role in the outcome of animal-mediated pollination [@ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009; @thomson_effects_2019; @ashman_pollen_2020].
 Nevertheless, our results indicate that the strategies a plant might use to successfully minimise competition for pollination (or maximise facilitation) must be determined relative to other species in the community, rather than an absolute property of the species itself.

### 2020-02-22 paper/cover-letter.Rnw
Edit cover letter for Ecology

@@
 
-Although the idea that plants can compete for pollinators or facilitate each other has been on the table for a long time, a definitive answer has not been reached yet.
-Many of the key theoretical papers on mutualistic communities\autocite{bascompte_asymmetric_2006, bastolla_architecture_2009, rohr_structural_2014} almost always focus on the inherently beneficial aspects of plant-pollinator interactions.
-Empirical work has often mirrored this focus, though a few community-level studies\autocite{tur_evaluating_2016, aizen_reproductive_2010} have explored the extent to which plants who share pollinators compete or facilitate each other.
-Importantly, these studies only measured the deposition of pollen, whereas plants can modulate competition by partitioning their pollination niche in many ways, such as through flowering time, attractiveness, or how they attach pollen to pollinators.
-We, therefore, quantified, for the first time, the true pollination niche of plants, by incorporating measures of visitation, pollen transfer, floral abundance, phenology, and traits.
+It has been known for long that plants that share pollinators can compete or facilitate each other.
+Multiple studies show that some ecological factors like abundance, traits, visitation, and pollen transfer can shape these indirect interactions between plants because they provide ways to partition plants' pollination niche.
+However, the generalisation of such findings to the scale of ecological communities has been elusive.
+It is mainly because the effect of these ecological factors has been studied chiefly within species pairs or a handful of species, at most.
+The few studies that have explored competition and facilitation at the community level have mainly focused on the patterns of pollen deposition or seed set, without taking into account the complex ways ecological factors may interact with pollen deposition.
+Here, we study the patterns of pollen deposition at the community level and incorporate measures of visitation, pollen transfer, floral abundance, phenology, and traits.
 
-In this manuscript, we show that the realised pollination niche (which can also be viewed as a plant species' strategy to minimise competition for pollination) is strongly determined by the community to which it belongs.
-Furthermore, we show that even in pollination there is no such thing as a free lunch, and plants need to balance multiple trade-offs when minimising competition for pollination.
+By studying these ecological factors together, we show two things.
+First, that at the community level, there is no such thing as a free lunch, and plants need to balance multiple trade-offs when optimising pollen deposition.
 On the one hand, factors that increase the quantity of pollen deposited by animals may also decrease its purity (and vice-versa).
-On the other, factors that increase both the quantity and purity do so only mildly and potentially only in the short-term.
+On the other hand, factors that on the surface increase both the quantity and purity of pollen deposition may be beneficial in the short-term but risky in the long term.
+Second, we show that the strategies plant species use to optimise pollen deposition, are likely to be flexible and depend on the community context.
 
 This work provides fundamental understanding of plant reproductive biology, while also \emph{calling for a shift in the way we think about pollination in community ecology}, especially from a theoretical perspective.
-In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is really a fluid dance between competition and facilitation.
-Some lessons might also be applicable to other biological complex systems where facilitation and competition might be at odds like plant-frugivore and plant-fungus interactions.
-Thus, we believe that this manuscript will be interesting to the broad readership of Proceedings B.
+In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is a fluid dance between competition and facilitation.
+Some lessons might also apply to other biological complex systems where facilitation and competition might be at odds like plant-frugivore and plant-fungus interactions.
+Thus, we believe that this manuscript will be interesting to the broad readership of Ecology.
 
-Lastly, please note that the data used in this manuscript have been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors.
+Lastly, please note that the data used in this manuscript have been previously published by one of the co-authors\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017}.
 However, the enclosed work represents a novel contribution from all involved.
 
-Thank you for your consideration.
+Thanks for your consideration.
 \bigskip
@@
 Fernando Cagua,
-Hugo Marrero,
-Jason Tylianakis \&
-Daniel Stouffer
 

### 2020-02-22 paper/draft-info.Rmd
Update draft info

--- 2019-07-04 paper/draft-info.Rmd
@@
 title: "Draft information"
-subtitle: "version: draft-7.4"
-date: "2019-07-05"
+subtitle: "version: draft-9.0"
+date: "2020-02-23"
 # author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
@@
 
-* Adjusted cover letter and minimum format requirements to submit to Proceedings B
+* Removed some weak text from Discussion. 
+* Minor edits everywhere
+* Formatted for submission to Ecology

### 2020-03-09 paper/cover-letter.Rnw
12 pt and letter size for Cover letter
dbs edits to the cover letter

@@
 % Letter class
-\documentclass[11pt, a4paper]{letter}
+\documentclass[12pt]{letter}
 \usepackage{hyperref}
@@
 We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Ecology}.
-The main goal of this study is to explore the balance between competition and facilitation in plants belonging to the same pollination community.
 
-It has been known for long that plants that share pollinators can compete or facilitate each other.
+The main goal of our study is to explore the balance between competition and facilitation in plants belonging to the same pollination community.
+It has been known for some time that plants that share pollinators can indirectly compete with or facilitate each other.
 Multiple studies show that some ecological factors like abundance, traits, visitation, and pollen transfer can shape these indirect interactions between plants because they provide ways to partition plants' pollination niche.
 However, the generalisation of such findings to the scale of ecological communities has been elusive.
-It is mainly because the effect of these ecological factors has been studied chiefly within species pairs or a handful of species, at most.
+This is mainly because the effect of these ecological factors has been studied chiefly within species pairs or, at most, for a handful of species.
 The few studies that have explored competition and facilitation at the community level have mainly focused on the patterns of pollen deposition or seed set, without taking into account the complex ways ecological factors may interact with pollen deposition.
-Here, we study the patterns of pollen deposition at the community level and incorporate measures of visitation, pollen transfer, floral abundance, phenology, and traits.
+Here, we instead study the patterns of pollen deposition at the community level and incorporate measures of visitation, pollen transfer, floral abundance, phenology, and traits.
 
-By studying these ecological factors together, we show two things.
-First, that at the community level, there is no such thing as a free lunch, and plants need to balance multiple trade-offs when optimising pollen deposition.
+By studying all of these ecological factors together, we have two main results.
+First, at the community level, there is no such thing as a free lunch, and plants need to balance multiple trade-offs when optimising pollen deposition.
 On the one hand, factors that increase the quantity of pollen deposited by animals may also decrease its purity (and vice-versa).
-On the other hand, factors that on the surface increase both the quantity and purity of pollen deposition may be beneficial in the short-term but risky in the long term.
+On the other hand, factors that increase both the quantity and purity of pollen deposition may be beneficial in the short-term but risky in the long term.
 Second, we show that the strategies plant species use to optimise pollen deposition, are likely to be flexible and depend on the community context.
 
-This work provides fundamental understanding of plant reproductive biology, while also \emph{calling for a shift in the way we think about pollination in community ecology}, especially from a theoretical perspective.
+Our work provides fundamental understanding of plant reproductive biology, while also \emph{calling for a shift in the way we think about pollination in community ecology}, particularly from a theoretical perspective.
 In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is a fluid dance between competition and facilitation.
 Some lessons might also apply to other biological complex systems where facilitation and competition might be at odds like plant-frugivore and plant-fungus interactions.
-Thus, we believe that this manuscript will be interesting to the broad readership of Ecology.
+Thus, we believe that this manuscript will be interesting to the broad readership of \emph{Ecology}.
 

### 2020-03-11 paper/cover-letter.Rnw
Add sentence to cover letter

@@
 On the other hand, factors that increase both the quantity and purity of pollen deposition may be beneficial in the short-term but risky in the long term.
-Second, we show that the strategies plant species use to optimise pollen deposition, are likely to be flexible and depend on the community context.
+Second, we show that the strategies plant species use to optimise pollen deposition, are likely to be flexible.
+This emphasises the importance of the community context for pollen deposition, in particular, and competition for pollination, in general.
 

### 2020-03-28 paper/cover-letter.Rnw
Update manuscript to fit format requirements of The American Naturalist

@@
 }
-\date{July 5, 2019}
+\date{March 28, 2020}
 %-----------------------------------------------------------------------------%
@@
     Editorial Office,\\
-    Ecology
+    The American Naturalist
 }
@@
 
-We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Ecology}.
+We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{The American Naturalist}.
 
@@
 Some lessons might also apply to other biological complex systems where facilitation and competition might be at odds like plant-frugivore and plant-fungus interactions.
-Thus, we believe that this manuscript will be interesting to the broad readership of \emph{Ecology}.
+Thus, we believe that this manuscript will be interesting to the readership of \emph{The American Naturalist}.
 
-Lastly, please note that the data used in this manuscript have been previously published by one of the co-authors\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017}.
+Please note that the data used in this manuscript have been previously published by one of the co-authors\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017}.
 However, the enclosed work represents a novel contribution from all involved.
+Lastly, we would like to bring to your attention that an earlier version of this manuscript has been published as a preprint\autocite{cagua_trade-offs_2019}.
 
@@
 \hfill
-Fernando Cagua,
+Fernando Cagua
 

### 2020-03-28 paper/manuscript.Rmd
Update running head
Update manuscript to fit format requirements of The American Naturalist

@@
 title: "The trade-offs of sharing pollinators: pollination service is determined by the community context"
-author: 
-  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
-  - "Hugo J. Marrero^2^ ([hugomarrero@gmail.com](hugomarrero@gmail.com))"
-  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
-  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
+#author: 
+#  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
+#  - "Hugo J. Marrero^2^ ([hugomarrero@gmail.com](hugomarrero@gmail.com))"
+#  - "Jason M. Tylianakis^1^ #([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
+#  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
 bibliography: bibliography.bib
-csl: ecology.csl
+csl: the-american-naturalist.csl
 output: #word_document
@@
   - \usepackage[export]{adjustbox}
-  - \usepackage[nomarkers]{endfloat}
-  - \usepackage{caption}
-  - \captionsetup{labelsep=none,textformat=empty}
-  - \usepackage{ragged2e}
+#  - \usepackage[nomarkers]{endfloat}
+#  - \usepackage{caption}
+#  - \captionsetup{labelsep=none,textformat=empty}
+#  - \usepackage{ragged2e}
 editor_options: 
@@
 
-^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand
+<!-- ^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand -->
 
-^2^ Centro de Recursos Naturales Renovables de las Zonas Semiáridas, CONICET, Camino de la Carrindanga Km. 7, 8000 Bahía Blanca, Argentina
+<!-- ^2^ Centro de Recursos Naturales Renovables de las Zonas Semiáridas, CONICET, Camino de la Carrindanga Km. 7, 8000 Bahía Blanca, Argentina -->
 
-**Running head:** Competition/facilitation in pollination
+<!-- **Running head:** The trade-offs of sharing pollinators -->
 
-<!-- **Article type:** Report. -->
+**Manuscript type:** Article.
 
-<!-- **Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text. -->
+**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.
 
@@
 
-**Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153).
+<!-- **Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153). -->
 
@@
 
-\RaggedRight
+<!-- \RaggedRight -->
+
+**Keywords:** `r keywords`
+
+\clearpage
 
@@
 
-**Keywords:** `r keywords`
+\clearpage
 
@@
 
-# Acknowledgements
+<!-- # Acknowledgements -->
 
-`r paste(drake::readd(acknowledgements), collapse = "")`
+<!-- `r paste(drake::readd(acknowledgements), collapse = "")` -->
 
